### 2017-09-07 ms.tex
initial draft and comparison fig

\documentclass[twocolumn]{aastex61}

\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}

\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\JWST}{\project{JWST}}
\newcommand{\HST}{\project{HST}}
\newcommand{\Spitzer}{\project{Spitzer}}

%% Reintroduced the \received and \accepted commands from AASTeX v5.2
%\received{July 1, 2016}
%\revised{September 27, 2016}
%\accepted{\today}
\submitjournal{ApJ}

\shorttitle{Phase Curves of WASP-103b}
\shortauthors{Kreidberg et al.}

\begin{document}

\title{Phase Curves of WASP-103b}

\correspondingauthor{Laura Kreidberg}
\email{laura.kreidberg@cfa.harvard.edu}

\author{Laura Kreidberg}
\affiliation{Harvard Society of Fellows\
78 Mt. Auburn St.\\
Cambridge, MA 02138, USA}
\affiliation{Harvard-Smithsonian Center for Astrophysics\
60 Garden St.\\
Cambridge, MA 02138}
\nocollaboration

\author{Vivien Parmentier}
\affiliation{Department of Planetary Sciences and Lunar and Planetary Laboratory, The University of Arizona}
\nocollaboration

\author{Michael R. Line}
\affiliation{Arizona State University}
\nocollaboration

\author{Mick\"{a}el Bonnefoy}
\affiliation{Universit\'{e} Grenoble Alpes}
\nocollaboration

\author{Jacqueline K. Faherty}
\affiliation{American Museum of Natural History}
\nocollaboration

\author{Kevin B. Stevenson}
\affiliation{Space Telescope Science Institute}
\nocollaboration

\author{Gregory L. Henry}
\affiliation{Center of Excellence in Information Systems, Tennessee State University}
\nocollaboration

\author{Keivan Stassun}
\affiliation{Vanderbilt University}
\nocollaboration

\author{Jacob L. Bean}
\affiliation{University of Chicago}
\nocollaboration

\author{Jonathan Fortney}
\affiliation{University of California Santa Cruz}
\nocollaboration

\author{Adam Showman}
\affiliation{Department of Planetary Sciences and Lunar and Planetary Laboratory, The University of Arizona}
\nocollaboration

\author{Jean-Michel D\'{e}sert}
\affiliation{University of Amsterdam}

\begin{abstract}
WASP-103b is a short-period hot Jupiter.
\end{abstract}

\keywords{planets and satellites: individual (WASP-107b), planets and satellites: atmospheres}

\section{Introduction} \label{sec:intro}
Planets are inherently 3D objects. Short period, tidally locked planets are intensely irradiated on the day side, which can lead to dramatic

The challenge is to reveal this structure at great distances, when we cannot spatially resolve the photosphere of the planet.

Phase curves!

\section{Observations and Data Reduction}
We observed two full-orbit phase curves of WASP-103b with \HST/WFC3 and one each with \Spitzer/IRAC at 3.6 and 4.5 $\mu$m. We also reduced two additional WFC3 secondary eclipse observations from \HST Program FIXME (PI: M. Zhao).

\subsection{\HST/WFC3}
The \emph{HST} observations consisted of two visits on 26-27 February and 2-3 August 2015. Each visit was 15 orbits in duration and spanned 23 hours. We took a direct image of the star with the F126N filter at the beginning of each orbit to determine the wavelength solution. The remainder of the orbit consisted of time-series spectroscopy with the G141 grism and the 256 x 256 pixel subarray. We used the SPARS10/NSAMP = 15 read-out mode, which has an exposure time of 103 seconds. The exposures were taken with the spatial scan observing mode with a scan rate of 0.03"/s, alternating between forward and backward scanning on the detector to diminish overhead time. The scan height was 25 pixels and the peak counts were 30k photoelectrons per pixel. We collected a total of 18 spatial scan exposures per orbit.  Our analysis also uses secondary eclipse observations of WASP-103b from \emph{HST} program 13660 (PI: M. Zhao), which obtained time series spectroscopy with the G141 grism using a similar setup. Further description of the observational design for this program is given in Star Cartier (in prep).

We reduced the data from both programs using a custom pipeline that has been developed for past analyses of WFC3 data \citep[for details see][]{kreidberg14a, kreidberg14b, kreidberg15a}. The raw data exhibit time-dependent systematic trends typically seen in WFC3 light curves, which we correct using a systematics model of the form:

\begin{equation}
 F_\mathrm{sys}(t) = (c\,S(t) + v_1\,t_\mathrm{v} + v_2\,t_\mathrm{v})(1 - \exp(-a\,t_\mathrm{orb} - b))
\end{equation}

\noindent where $t_\mathrm{v}$ is time elapsed since the first exposure in a visit and $t_\mathrm{orb}$ is time since the first exposure in an orbit. $S(t)$ is a scale factor equal to 1 for exposures with spatial scanning in the forward direction and $s$ for reverse scans. In the fit, $c$, $v_1$, $v_2$, $a$, $b$, and $s$ are free parameters. The first orbit in each visit shows larger systematic trends than subsequent orbits, so we exclude these data in our final analysis \citep[a common practice; see e.g.][]{kreidberg14a}.

We fit the systematics model simultaneously with the physical parameters for the system. The complete model is

\begin{equation}
F(t) = F_\mathrm{sys}(t)\left[T(t) + (E(t) - 1)(1 + A\cos(2\pi(t - \theta)/P))\right]
\label{eq:model}
\end{equation}

\noindent where $T(t)$ is a transit model, $E(t)$ is an eclipse model, $P$ is the planet orbital period, and $A$ and $\theta$ are free parameters to fit the amplitude and offset for the thermal phase variation. The free parameters for the transit and eclipse model are the planet-to-star radius ratio $r_p/r_s$, the planet-to-star flux ratio $f_p/f_s$, and a linear limb darkening parameter. The eclipse model is normalized such that the flux during eclipse is 1 and out of eclipse is $f_p/f_s$, and the transit model is normalized to unity out of transit. The planet's orbital parameters are poorly constrained by the WFC3 light curve due to incomplete phase coverage, so we fix the inclination to $i = 84.54^\circ$, the semi-major axis to stellar radius $a/R_s  = 2.925$, based on the best fit to the \emph{Spitzer} Channel 2 light curve (described below).  We use the orbital period $P = 0.925545613$ day, and time of inferior conjunction $t_0 = 2456836.2964455$ from \cite{southworth15}.  All free parameters were assumed to have a common value for both \emph{HST} visits, with the exception of $c$, $v_1$ and $v_2$, which were allowed to vary between visits. We explored adding an additional cosine term to model the thermal phase variation, but the additional degrees of freedom are not justified according to the Bayesian Information Criterion (BIC). The transit and eclipse models were calculated with the \texttt{batman} package \citep{kreidberg15a}. %Figure\;\ref{fig:w103_hst} shows the fitted broadband phase curve.

\subsection{\Spitzer}
he \emph{Spitzer} observations had the following setup. Each phase curve observation consisted of 30 hours of time series photometry, which covered a full orbital revolution of the planet. The observations were timed to contain two eclipses with three hours of baseline on either side. We used 12 s exposures to maximize the duty cycle without saturating the detector. The dominant systematic in high-precision Spitzer time series is the intrapixel effect (variations in flux caused by imprecise pointing). To minimize this effect, we used PCRS peak-up to improve the pointing accuracy. We began each observations with a 30-minute position settling period, followed by three Astronomical Observation Requests (AORs) of equal duration. At the beginning of each AOR, the telescope was repointed to position the target in the ``sweet spot" of the detector.

We reduced the data using the POET pipeline and fit the systematics with the BLISS mapping technique \citep{stevenson12}. This technique creates a map of the intrapixel sensitivity while simultaneously fitting for other systematics and the physical parameters of the system. In addition to the intrapixel sensitivity map, we fit the data for a linear trend in time and used the same transit, eclipse, and phase variation model as in Equation%\;\ref{eq:model}.

We tested the light curve fits for time-correlated noise by calculating the root mean square (rms) of the fit for a range of bin sizes. For white noise, the rms should decrease as the square root of the number of points in the bin. The 4.5 $\mu$m phase curve data follow this trend; however, the 3.6 $\mu$m data have larger than expected rms at large bin sizes. The time-correlated noise is also noticeable in the residuals to the light curve fit %(Figure\;\ref{fig:w103_spitzer}). 
To account for additional uncertainty due to the correlated noise in this channel, we use the wavelet technique of \cite{carter09}.

\section{Light Curve Analysis}

\section{Composition of the Atmosphere}

\subsection{Retrieval}

\acknowledgments
We thank a lot of people. Caroline Morley, Thomas Beatty, Ming Zhao, Kim Star Cartier.

\bibliographystyle{aasjournal}
\bibliography{ms.bib}

\end{document}

### 2017-09-20 ms.tex
data reduction

@@
 We observed two full-orbit phase curves of WASP-103b with \HST/WFC3 and one each with \Spitzer/IRAC at 3.6 and 4.5 $\mu$m.
-We also reduced two additional WFC3 secondary eclipse observations from \HST Program FIXME (PI: M.
+We also reduced two additional WFC3 secondary eclipse observations from \HST Program 13660 (PI: M.
 Zhao).
@@
 Each visit was 15 orbits in duration and spanned 23 hours.
-We took a direct image of the star with the F126N filter at the beginning of each orbit to determine the wavelength solution.
-The remainder of the orbit consisted of time-series spectroscopy with the G141 grism and the 256 x 256 pixel subarray.
+We took a direct image of the star with the F126N filter at the beginning of each orbit to determine the wavelength solution zero-point.
+The remainder of the orbit consisted of time-series spectroscopy with the G141 grism ($1.1 - 1.7$ $\mu$m) and the 256 x 256 pixel subarray.
 We used the SPARS10/NSAMP = 15 read-out mode, which has an exposure time of 103 seconds.
-The exposures were taken with the spatial scan observing mode with a scan rate of 0.03"/s, alternating between forward and backward scanning on the detector to diminish overhead time.
-The scan height was 25 pixels and the peak counts were 30k photoelectrons per pixel.
+To optimize the duty cycle of the observations, we used the spatial scan observing mode with a scan rate of 0.03"/s, alternating between forward and backward scanning on the detector.
+The scan height was 25 pixels and the peak counts were 35k photoelectrons per pixel.
 We collected a total of 18 spatial scan exposures per orbit.
-Our analysis also uses secondary eclipse observations of WASP-103b from \emph{HST} program 13660 (PI: M.
-Zhao), which obtained time series spectroscopy with the G141 grism using a similar setup.
-Further description of the observational design for this program is given in Star Cartier (in prep).
+The two eclipses observations from Program 13660 had a similar observing setup.
 
-We reduced the data from both programs using a custom pipeline that has been developed for past analyses of WFC3 data \citep[for details see][]{kreidberg14a, kreidberg14b, kreidberg15a}.
+We reduced the data from both programs using a custom pipeline developed for past analyses of WFC3 data \citep[for details see][]{kreidberg14a, kreidberg14b, kreidberg15a}.
+Briefly, we use the optimal extraction algorithm of \cite{horne86} to extract each up-the-ramp sample (or ``stripe") separately.
+The stripes are then summed to create the final spectrum.
+For each stripe, the extraction window is 24 pixels high and centered on the stripe midpoint.
+We estimate the background from the median of a region of the detector that is uncontaminated by the target spectrum (rows 5-50).
+The typical background counts are low (10-15 photoelctrons per pixel, roughly 0.03\% of the peak counts from the target star).
+We note that the extracted spectrum includes flux from a nearby star, which is separated from WASP-103 by less than two pixels \citep[0.2"][]{wollert15}.
+We account for the contaminating flux later in the analysis.
+
+\subsection{\Spitzer}
+he \emph{Spitzer} observations had the following setup.
+Each phase curve observation consisted of 30 hours of time series photometry, which covered a full orbital revolution of the planet.
+The observations were timed to contain two eclipses with three hours of baseline on either side.
+We used 12 s exposures to maximize the duty cycle without saturating the detector.
+The dominant systematic in high-precision Spitzer time series is the intrapixel effect (variations in flux caused by imprecise pointing).
+To minimize this effect, we used PCRS peak-up to improve the pointing accuracy.
+We began each observations with a 30-minute position settling period, followed by three Astronomical Observation Requests (AORs) of equal duration.
+At the beginning of each AOR, the telescope was repointed to position the target in the ``sweet spot" of the detector.
+
+We reduced the data using the POET pipeline and fit the systematics with the BLISS mapping technique \citep{stevenson12}.
+This technique creates a map of the intrapixel sensitivity while simultaneously fitting for other systematics and the physical parameters of the system.
+In addition to the intrapixel sensitivity map, we fit the data for a linear trend in time and used the same transit, eclipse, and phase variation model as in Equation%\;\ref{eq:model}.
+
+We tested the light curve fits for time-correlated noise by calculating the root mean square (rms) of the fit for a range of bin sizes.
+For white noise, the rms should decrease as the square root of the number of points in the bin.
+The 4.5 $\mu$m phase curve data follow this trend; however, the 3.6 $\mu$m data have larger than expected rms at large bin sizes.
+The time-correlated noise is also noticeable in the residuals to the light curve fit %(Figure\;\ref{fig:w103_spitzer}).
+To account for additional uncertainty due to the correlated noise in this channel, we use the wavelet technique of \cite{carter09}.
+
+\section{Light Curve Fits}
+which orbits/data
+
 The raw data exhibit time-dependent systematic trends typically seen in WFC3 light curves, which we correct using a systematics model of the form:
@@
 
-\subsection{\Spitzer}
-he \emph{Spitzer} observations had the following setup.
-Each phase curve observation consisted of 30 hours of time series photometry, which covered a full orbital revolution of the planet.
-The observations were timed to contain two eclipses with three hours of baseline on either side.
-We used 12 s exposures to maximize the duty cycle without saturating the detector.
-The dominant systematic in high-precision Spitzer time series is the intrapixel effect (variations in flux caused by imprecise pointing).
-To minimize this effect, we used PCRS peak-up to improve the pointing accuracy.
-We began each observations with a 30-minute position settling period, followed by three Astronomical Observation Requests (AORs) of equal duration.
-At the beginning of each AOR, the telescope was repointed to position the target in the ``sweet spot" of the detector.
-
-We reduced the data using the POET pipeline and fit the systematics with the BLISS mapping technique \citep{stevenson12}.
-This technique creates a map of the intrapixel sensitivity while simultaneously fitting for other systematics and the physical parameters of the system.
-In addition to the intrapixel sensitivity map, we fit the data for a linear trend in time and used the same transit, eclipse, and phase variation model as in Equation%\;\ref{eq:model}.
-
-We tested the light curve fits for time-correlated noise by calculating the root mean square (rms) of the fit for a range of bin sizes.
-For white noise, the rms should decrease as the square root of the number of points in the bin.
-The 4.5 $\mu$m phase curve data follow this trend; however, the 3.6 $\mu$m data have larger than expected rms at large bin sizes.
-The time-correlated noise is also noticeable in the residuals to the light curve fit %(Figure\;\ref{fig:w103_spitzer}).
-To account for additional uncertainty due to the correlated noise in this channel, we use the wavelet technique of \cite{carter09}.
-
-\section{Light Curve Analysis}
-
 \section{Composition of the Atmosphere}

### 2017-09-20 ms.tex
data reduction

@@
 \section{Introduction} \label{sec:intro}
-Planets are inherently 3D objects. Short period, tidally locked planets are intensely irradiated on the day side, which can lead to dramatic
+It is a truism to say that planets are three-dimensional objects, but worth exploring the specific challenges.
+Short period, tidally locked planets are intensely irradiated on the day side, which can lead to dramatic
 
@@
 We observed two full-orbit phase curves of WASP-103b with \HST/WFC3 and one each with \Spitzer/IRAC at 3.6 and 4.5 $\mu$m.
-We also reduced two additional WFC3 secondary eclipse observations from \HST Program 13660 (PI: M.
+We also reduced two additional WFC3 secondary eclipse observations from \HST\ Program 13660 (PI: M.
 Zhao).
@@
 \subsection{\HST/WFC3}
-The \emph{HST} observations consisted of two visits on 26-27 February and 2-3 August 2015.
+The \HST\ observations consisted of two visits on 26-27 February and 2-3 August 2015.
 Each visit was 15 orbits in duration and spanned 23 hours.
@@
 The typical background counts are low (10-15 photoelctrons per pixel, roughly 0.03\% of the peak counts from the target star).
-We note that the extracted spectrum includes flux from a nearby star, which is separated from WASP-103 by less than two pixels \citep[0.2"][]{wollert15}.
+We note that the extracted spectrum includes flux from a nearby star, which is separated from WASP-103 by less than two pixels \citep[0.2";][]{wollert15}.
 We account for the contaminating flux later in the analysis.
@@
 \subsection{\Spitzer}
-he \emph{Spitzer} observations had the following setup.
+The \Spitzer\ observations had the following setup.
 Each phase curve observation consisted of 30 hours of time series photometry, which covered a full orbital revolution of the planet.
@@
 We used 12 s exposures to maximize the duty cycle without saturating the detector.
-The dominant systematic in high-precision Spitzer time series is the intrapixel effect (variations in flux caused by imprecise pointing).
-To minimize this effect, we used PCRS peak-up to improve the pointing accuracy.
+The data volume is relatively low for this exposure time, so we read out the full array.
+To minimize the intrapixel effect (variations in flux caused by imprecise pointing), we did not dither and also used PCRS peak-up to improve the pointing accuracy.
 We began each observations with a 30-minute position settling period, followed by three Astronomical Observation Requests (AORs) of equal duration.
@@
 
-We reduced the data using the POET pipeline and fit the systematics with the BLISS mapping technique \citep{stevenson12}.
-This technique creates a map of the intrapixel sensitivity while simultaneously fitting for other systematics and the physical parameters of the system.
-In addition to the intrapixel sensitivity map, we fit the data for a linear trend in time and used the same transit, eclipse, and phase variation model as in Equation%\;\ref{eq:model}.
-
-We tested the light curve fits for time-correlated noise by calculating the root mean square (rms) of the fit for a range of bin sizes.
-For white noise, the rms should decrease as the square root of the number of points in the bin.
-The 4.5 $\mu$m phase curve data follow this trend; however, the 3.6 $\mu$m data have larger than expected rms at large bin sizes.
-The time-correlated noise is also noticeable in the residuals to the light curve fit %(Figure\;\ref{fig:w103_spitzer}).
-To account for additional uncertainty due to the correlated noise in this channel, we use the wavelet technique of \cite{carter09}.
+The data were reduced with the POET pipeline \citep{stevenson12}.
+We performed aperture photometry with an aperture size of 2.75 pixels (chosen from a grid of apertures between 2 and 4 pixels to minimize the residual noise in the light curve fits).
+We masked pixels that were flagged in the bad pixel mask provided in the ancillary data for the observations.
+The target centroid was determined with a two-dimensional Gaussian fit.
+We estimated and subtracted the background from an annulus with a radius of 7 to 15 pixels from the centroid.
+As for the \HST\ observations, the contaminating flux from the nearby star is included in the final photometry and corrected in the light curve fits.
 
@@
 which orbits/data
+
+\subsection{Phase-Resolved Spectra}
+
+\subsection{Comparison of Thermal Phase Variation Models}
 
@@
 
+and fit the systematics with the BLISS mapping technique \citep{stevenson12}.
+This technique creates a map of the intrapixel sensitivity while simultaneously fitting for other systematics and the physical parameters of the system.
+In addition to the intrapixel sensitivity map, we fit the data for a linear trend in time and used the same transit, eclipse, and phase variation model as in Equation%\;\ref{eq:model}.
+
 \section{Composition of the Atmosphere}
@@
 
+\section{Comparison with GCMs}
+
+\section{Comparison with Brown Dwarfs and Directly Imaged Planets}
+
 \acknowledgments
-We thank a lot of people. Caroline Morley, Thomas Beatty, Ming Zhao, Kim Star Cartier.
+We thank a lot of people. Caroline Morley, Thomas Beatty, Ming Zhao, Kim Star Cartier, Hannah Diamond-Lowe, Nick Cowan (make him a coauthor?)
 

### 2017-10-01 ms.tex
intro

@@
 \section{Introduction} \label{sec:intro}
-It is a truism to say that planets are three-dimensional objects, but worth exploring the specific challenges.
-Short period, tidally locked planets are intensely irradiated on the day side, which can lead to dramatic
+It is a truism to say that planets are round.
+The.
+And yet planets' roundness gives rise to a host of complications:  atmospheric circulation, variable , gradients in chemistry, cloud formation and evaporation, and time-dependent phenomena (weather).
 
-The challenge is to reveal this structure at great distances, when we cannot spatially resolve the photosphere of the planet.
+It is a challenge is to reveal this structure at great distances, when we cannot spatially resolve the photosphere of the planet.
+Most observations of exoplanet atmospheres are sensitive to a single isolated region  -- either the terminator, for transmission spectroscopy, or the disk-integrated dayside, for emission spectroscopy.
+The solution to this problem is to observe phase curves of tidally-locked planets, which monitor the brightness of the planet over its entire orbit.
+As the orbital phase changes, the observer
 
-Phase curves!
+The first phase curve was observed with \Spitzer\ for the hot Jupiter HD 189733b by \citep{knutson??}, and was followed by FIXME more (with IRAC).
+Several trends emerged from these measurements, including eastward shifted hotspots (which suggest super-rotating equatorial jets), larger day-night temperature contrast for shorter period planets (ref), .
+The first spectroscopic phase curve was measured with Hubble's Wide Field Camera 3 (WFC3) by \citep{stevenson???} for the hot Jupiter WASP-43b.
+Found low albedo, offset hotspot, water visible at other phases,
+
+In parallel with these observations, there have been major advances in the theory of exoplanet atmospheres in three-dimensions.
+Global circulation models (GCMs) are now capable of self-consistent radiative transfer and atmospheric dynamics (refs) and are beginning to include clouds (refs?).
+
+In addition to GCMs, work on the inverse problem Cowan - how to get maps, .
+SPIDERMAN, an open-source Python package designed to take any temperature or brightness map of a planet and output the corresponding phase curve, so that we can readily connect GCMs to phase curve observations.
+
+In this paper we present \HST\ and \Spitzer\ phase curve observations of WASP-103b, a hot Jupiter with a mass of X, radius of Y, period of Z (cite discovery paper).
+These properties are similar to WASP-43b, except that WASP-103b has a much (FIXME vs FIXME K) thanks to its hot F??
+star host.
+By comparing the phase curves of these two planets, we can test the effect of irradiation on the climate of the planet.
+
+The structure of the paper is as follows:
 
@@
 
+\subsection{Photometric Monitoring}
+
 \section{Light Curve Fits}
 which orbits/data
+ellipsoidal variations/doppler beaming
 

### 2017-10-07 ms.tex
photometry

@@
 \section{Observations and Data Reduction}
-We observed two full-orbit phase curves of WASP-103b with \HST/WFC3 and one each with \Spitzer/IRAC at 3.6 and 4.5 $\mu$m.
-We also reduced two additional WFC3 secondary eclipse observations from \HST\ Program 13660 (PI: M.
+We observed two full-orbit phase curves of WASP-103b with \HST/WFC3 and one each with \Spitzer/IRAC at 3.6 and 4.5 $\mu$m (from HST Program 14050 and Spitzer Program 11099).
+We also reduced two \HST/WFC3 secondary eclipse observations of WASP-103b from \HST\ Program 13660 (PI: M.
 Zhao).
@@
 \subsection{\HST/WFC3}
-The \HST\ observations consisted of two visits on 26-27 February and 2-3 August 2015.
+The \HST\ phase curve observations consisted of two visits on 26-27 February and 2-3 August 2015.
 Each visit was 15 orbits in duration and spanned 23 hours.
@@
 We collected a total of 18 spatial scan exposures per orbit.
-The two eclipses observations from Program 13660 had a similar observing setup.
+The two eclipse observations from Program 13660 had a similar observing setup.
 
@@
 We estimate the background from the median of a region of the detector that is uncontaminated by the target spectrum (rows 5-50).
-The typical background counts are low (10-15 photoelctrons per pixel, roughly 0.03\% of the peak counts from the target star).
+The typical background counts are low (10-15 photoelectrons per pixel, roughly 0.03\% of the peak counts from the target star).
 We note that the extracted spectrum includes flux from a nearby star, which is separated from WASP-103 by less than two pixels \citep[0.2";][]{wollert15}.
-We account for the contaminating flux later in the analysis.
+Our extracted spectrum includes flux from this star, which we account for later in the analysis.
 
@@
 The \Spitzer\ observations had the following setup.
-Each phase curve observation consisted of 30 hours of time series photometry, which covered a full orbital revolution of the planet.
-The observations were timed to contain two eclipses with three hours of baseline on either side.
+Each phase curve observation consisted of 30 hours of time series photometry, beginning three hours prior to one secondary eclipse and ending three hours after a second eclipse.
 We used 12 s exposures to maximize the duty cycle without saturating the detector.
@@
 We estimated and subtracted the background from an annulus with a radius of 7 to 15 pixels from the centroid.
-As for the \HST\ observations, the contaminating flux from the nearby star is included in the final photometry and corrected in the light curve fits.
+As for the \HST\ observations, the contaminating flux from the nearby star is included in the final photometry and corrected later in the light curve fits.
 
 \subsection{Photometric Monitoring}
+We monitored WASP-103's photometric variability over 158 nights during 2014 - 2016 with the Tennessee State University Celestron 14-inch (C14) automated imaging telescope (AIT), located at Fairborn Observatory in southern Arizona \citep[see, e.g.,][]{h1999, ehf2003}.
+The observations of WASP-103 were made in the Cousins R passband with an SBIG STL-1001E CCD camera.
+Each observation consisted of 4--10 consecutive exposures on WASP-103 along with several dozen comparison stars in the same field.
+The individual consecutive frames were co-added and reduced to differential magnitudes (i.e., WASP-103 minus the mean brightness of the six best comparison stars).
+The nightly observations were corrected for bias, flat-fielding, pier-side offset, and differential atmospheric extinction.
+
+The photometric analyses are summarized for each observing season in Table\,\ref{tab:photometry}.
+The standard deviation of WASP-103's brightness in each season is given in column~4.
+The mean of the three standard deviations is 0.0058~mag, which is very comparable to the mean standard deviation of the six comparison stars (0.0055~mag).
+To maximize the possibility of detection WASP-103's rotation, we normalized the photometry such that each observing season has the same mean, thereby removing long-term variability in WASP-103 and/or the comparison stars.
+We performed a periodogram analysis of the normalized dataset.
+Figure\,\ref{fig:photometry} shows the frequency spectrum and the phase curve computed with the best frequency, respectively.
+We also performed a least-squares fit to the data to determine the best fit sine curve.
+The best fit period is 6.814 days, which agrees closely with the estimated stellar rotation period of 6.855 days \citep{getal2014}.
+The variability amplitude is 0.005~mag, which has FIXME impact on our analysis here.
+
+%The apparent low amplitude variability is likely due to rotational modulation in the visibility of weak, magnetic surface features \citep[see, e.g.,][]{hfh1995}.
+
+%This implies there can be very little night-to-night variability in WASP-103.
+The three seasonal mean brightness values given in column 5 scatter about their grand mean with a standard deviation of 0.0036 mag, but we note that the most discrepant mean is from the third season, for which we have only partial coverage.
+Therefore, our results do not completely rule out low-level, year-to-year variability of 0.001~mag or so.
+
+%We performed periodogram analyses of the individual observing seasons and the complete dataset and found no significant periodicity.
+To maximize the possibility of detecting a rotation signal in WASP-103, we normalized the dataset by adding a constant offset to the second and third observing seasons to have the same mean as the first.
+%To first order, this removes possible long-term variability in WASP-103 and/or the comparison stars as well as any uncorrected, long-term systemmatic effects.
+It is the normalized data that are plotted in the top panel of Fig.~1.
+
+%We performed a least-squares fit to the data with a sine curve with trial frequencies between 0.005 and 0.95 c/d, corresponding to periods between one and 200 days.
+The goodness of fit at each frequency is measured as the reduction factor in the variance of the original data.
+The result suggests low-amplitude brightness variability in WASP-103 with a period near 6.814 days.
+
+\begin{figure}
+\includegraphics[width = 0.5\textwidth]{Figures/photometry.eps}
+\caption{$Top$: The normalized nightly Cousins $R$ band photometric dataset for WASP-103, acquired with the C14 automated imaging telescope at Fairborn Observatory.
+Vertical dashed lines denote separate observing seasons.
+Gaps are due to target visibility and the Arizona monsoon season (July - September).
+$Middle$: The frequency spectrum of the normalized dataset suggests low-amplitude variability with a period of 6.814~days.
+$Bottom$: The normalized dataset phased to the 6.814-day period, which we interpret as the stellar rotation period.
+A least-squares sine fit to the 6.814-day rotation period gives a peak-to-peak amplitude of just 0.005~mag.}
+\label{fig:photometry}
+\end{figure}
+
+\begin{deluxetable}{ccccc}
+	%\tabletypesize{\small}
+	\tablenum{1}
+	\tablewidth{0pt}
+	\tablecaption{Summary of Photometric Observations of WASP-103}
+	\tablehead{
+		\colhead{Observing} & \colhead{} & \colhead{Date Range} &
+		\colhead{Sigma} & \colhead{Seasonal Mean}  \\
+
+		\colhead{Season} & \colhead{$N_{obs}$} & \colhead{(HJD $-$ 2,400,000)} &
+		\colhead{(mag)} & \colhead{(mag)}}%   \\
+
+	%	\colhead{(1)} & \colhead{(2)} & \colhead{(3)} &
+	%	\colhead{(4)} & \colhead{(5)}  
+	\startdata
+	   2014   &  59 & 56722--56972 & 0.0057 & $0.9546\pm0.0007$  \\
+	   2015   &  73 & 57028--57335 & 0.0062 & $0.9549\pm0.0007$  \\
+	   2016   &  26 & 57385--57451 & 0.0055 & $0.9485\pm0.0011$  \\
+	\enddata
+	\label{tab:photometry}
+\end{deluxetable}
+
+\subsection{Retrieval}
 

### 2017-10-08 ms.tex
model

@@
 
-\title{Phase Curves of WASP-103b}
+\title{Global Climate of the Ultra-Hot Jupiter WASP-103b from \HST\ and Spitzer Phase Curve Observations}
 
@@
 By comparing the phase curves of these two planets, we can test the effect of irradiation on the climate of the planet.
+
+Talk about other WFC3 papers (Star Cartier, etc)
 
@@
 	\tablewidth{0pt}
-	\tablecaption{Summary of Photometric Observations of WASP-103}
+	\tablecaption{Photometric Observations of WASP-103}
 	\tablehead{
 		\colhead{Observing} & \colhead{} & \colhead{Date Range} &
-		\colhead{Sigma} & \colhead{Seasonal Mean}  \\
+	\colhead{Sigma} & \colhead{Seasonal Mean} }% \\
 
-		\colhead{Season} & \colhead{$N_{obs}$} & \colhead{(HJD $-$ 2,400,000)} &
-		\colhead{(mag)} & \colhead{(mag)}}%   \\
+%		\colhead{Season} & \colhead{$N_{obs}$} & \colhead{(HJD $-$ 2,400,000)} &
+%		\colhead{(mag)} & \colhead{(mag)}}%   \\
 
@@
 
-\subsection{Retrieval}
+\section{Light Curve Fits}
+We fit the \HST\ and \Spitzer\ phase curves independently. For each light curve fit, we used a two-component model:
+ one component models the physical signal (the planet's thermal phase variation) and the other models the instrument systematics.
 
-\section{Light Curve Fits}
-which orbits/data
+\subsection{Physical Model}
+We explored several different models for the planet's thermal phase variation.
+
+two-temperature model, with a uniform dayside temperature $T_d$ and a uniform nightside temperature $T_n$.
+also temperature map generated with spherical harmonics, the most general.
+Physically-motivated kinematic model from \cite{zhang16}, which has just three free parameters (the nightside temperature $T_n$, the change in temperature from day-to-night side $\Delta_T$, and the ratio of radiative to advective timescales $\xi$).
+The kinematic model makes several simplifying assumptions (e.g, that the wind speed and direction are constant), but it reproduces GCM simulations fairly well.
+
+We also fit a sine curve.
+
+\subsubsection{Ellipsoidal Variations and Doppler Beaming}
 ellipsoidal variations/doppler beaming
 
-\subsection{Phase-Resolved Spectra}
+\subsection{Systematics Models}
+Both the \HST\ and \Spitzer\ phase curves have systematic noise caused by variations in the sensitivity of the instrument over time.
+For the WFC3 data, the dominant systematic is an orbit-long exponential trend due to charge traps filling up over successive exposures \citep{zhu17}.
+For \Spitzer\, the intrapixel sensitivity effect is the primary source of noise.
+The detector's pixels do not have uniform sensitivity, so slight changes in telescope pointing cause the recorded flux to vary.
 
-\subsection{Comparison of Thermal Phase Variation Models}
-
+\subsubsection{\HST\ Systematics}
 The raw data exhibit time-dependent systematic trends typically seen in WFC3 light curves, which we correct using a systematics model of the form:
@@
 
+\subsubsection{\Spitzer\ Systematics}
 and fit the systematics with the BLISS mapping technique \citep{stevenson12}.
@@
 In addition to the intrapixel sensitivity map, we fit the data for a linear trend in time and used the same transit, eclipse, and phase variation model as in Equation%\;\ref{eq:model}.
+
+which orbits/data
+
+\subsection{Phase-Resolved Spectra}
+
+\subsection{Comparison of Thermal Phase Variation Models}
 

### 2017-10-09 ms.tex
phase curve fig

@@
 
-\shorttitle{Phase Curves of WASP-103b}
+\shorttitle{Phase Curves of WASP-103\lowercase{b}}
 \shortauthors{Kreidberg et al.}
@@
 
-\title{Global Climate of the Ultra-Hot Jupiter WASP-103b from \HST\ and Spitzer Phase Curve Observations}
+\title{Global Climate of the Ultra-Hot Jupiter WASP-103\lowercase{b} from \HST\ and Spitzer Phase Curve Observations}
 
@@
 \section{Light Curve Fits}
-We fit the \HST\ and \Spitzer\ phase curves independently. For each light curve fit, we used a two-component model:
- one component models the physical signal (the planet's thermal phase variation) and the other models the instrument systematics.
+We fit a two-component model to the full-orbit phase curves.
+One component models the planet signal (the thermal phase variation and transit), and the other component is a systematics model for changes in the instrument sensitivity.
+For each light curve, we fit the physical and systematic component simultaneously.
 
-\subsection{Physical Model}
+\subsection{Thermal Phase Variation Models}
 We explored several different models for the planet's thermal phase variation.
+The simplest model was a sine curve, which has been used for many past analyses of exoplanet phase curves \citep[e.g.]{FIXME}.
+
+We also fit climate maps using the open-source Python package \texttt{SPIDERMAN}.
+This package allows users to input a climate map (temperature or brightness as a function of latitude and longitude), and outputs a the thermal phase curve.
+The code is optimized to calculate
 
@@
 ellipsoidal variations/doppler beaming
+
+\begin{figure*}
+\includegraphics[width = 1.0\textwidth]{Figures/phase_curves.pdf}
+\caption{WASP-103b phase curve observations from \HST/WFC3 (top) and \Spitzer/IRAC (middle and bottom).
+For clarity, the data are phase-folded on the planet's orbital period and binned in 30 uniformly spaced bins between 0 and 1.
+The left column shows the phase curves with systematic noise removed (black points) compared to the best fit model (black line).
+The shading denotes the  1\,$\sigma$ confidence interval on the best fit.
+We include the transits in the fit, but they are not displayed in this figure.
+The right-hand column shows the binned residuals for the best-fit light curve.}
+\label{fig:phasecurves}
+\end{figure*}
 
@@
 
+\section{Results}
+
 \subsection{Phase-Resolved Spectra}
+After fitting
+
+We note that the phase-resolved spectra do not significantly change based on which model we assume for the
 

### 2017-10-09 Figures/phase_curves.py

@@ -6,6 +6,7 @@ import matplotlib.gridspec as gridspec
 from pylab import *
 from matplotlib import rc
 import spiderman_lc
+import transit_lc
 from lc_fit import Model, LightCurveData
 
 rc('font',**{'family':'sans-serif','sans-serif':['Arial']})
@@ -13,16 +14,18 @@ rc('font',**{'family':'sans-serif','sans-serif':['Arial']})
 def quantile(x, q):
         return np.percentile(x, 100. * q)
 
-gs = gridspec.GridSpec(3, 2, hspace=0.0, wspace = 0.0)
+plt.figure(figsize = (7.5,4))
+
+gs = gridspec.GridSpec(3, 2, hspace=0.1, wspace = 0.05)
 
 # plots HST white light phase curve
 bestfits = ["/Users/lkreidberg/Desktop/Projects/Observations/HST/WASP103_HST_all/PHYSICAL_MODEL_WHITE_MCMC/bestfit_white.pic"]
 mcmcs =  ["/Users/lkreidberg/Desktop/Projects/Observations/HST/WASP103_HST_all/PHYSICAL_MODEL_WHITE_MCMC/mcmc_out_white.npy"]
 
-phasebins = np.linspace(0., 1., 40)
+phasebins = np.linspace(0., 1., 30)
 nbins = len(phasebins) - 1
 
-every_N = 10000
+every_N = 1000
 
 for ii, f in enumerate(bestfits):
 	ax = plt.subplot(gs[ii, 0])
@@ -37,8 +40,8 @@ for ii, f in enumerate(bestfits):
 	t0 = 2457080.64041702 
 	t = np.linspace(t0, t0+ per, 1000)
 	models = np.zeros((len(t), mcmc.shape[0]))
-	for i in range(len(mcmc)): models[:, i] = spiderman_lc.lc(t, 0.115, T_s[i], 1.1e-6, 1.7e-6, xi[i], T_n[i], delta_T[i], 0., True)
-	print "hard coding in rp and wavelength for spiderman model"
+	for i in range(len(mcmc)): models[:, i] = spiderman_lc.lc(t, np.median(rp), T_s[i], 1.1e-6, 1.7e-6, xi[i], T_n[i], delta_T[i], 0., True)*transit_lc.lc(t, np.median(rp))
[…]

### 2017-10-09 ms.tex
models

@@
 
-We reduced the data from both programs using a custom pipeline developed for past analyses of WFC3 data \citep[for details see][]{kreidberg14a, kreidberg14b, kreidberg15a}.
+We reduced the data from both programs using a custom pipeline developed for past analyses of WFC3 data \citep[for details see][]{kreidberg14a, kreidberg14b, kreidberg15b}.
 Briefly, we use the optimal extraction algorithm of \cite{horne86} to extract each up-the-ramp sample (or ``stripe") separately.
@@
 We fit a two-component model to the full-orbit phase curves.
-One component models the planet signal (the thermal phase variation and transit), and the other component is a systematics model for changes in the instrument sensitivity.
-For each light curve, we fit the physical and systematic component simultaneously.
+One component models the astrophysical signal (the planet's thermal phase variation and transit), and the other component models the systematic noise introduced by changes in the instrument sensitivity.
+For each light curve, we fit the physical and systematic components simultaneously.
 
-\subsection{Thermal Phase Variation Models}
-We explored several different models for the planet's thermal phase variation.
-The simplest model was a sine curve, which has been used for many past analyses of exoplanet phase curves \citep[e.g.]{FIXME}.
+\subsection{Astrophysical Signal}
+We assume the astrophysical signal $F_\mathrm{physical}(t)$ has the following form:
 
-We also fit climate maps using the open-source Python package \texttt{SPIDERMAN}.
-This package allows users to input a climate map (temperature or brightness as a function of latitude and longitude), and outputs a the thermal phase curve.
-The code is optimized to calculate
+\begin{equation}
+	F_\mathrm{physical}(t) = T(t) \times P(t) \times E(t)
+\end{equation}
 
-two-temperature model, with a uniform dayside temperature $T_d$ and a uniform nightside temperature $T_n$.
-also temperature map generated with spherical harmonics, the most general.
-Physically-motivated kinematic model from \cite{zhang16}, which has just three free parameters (the nightside temperature $T_n$, the change in temperature from day-to-night side $\Delta_T$, and the ratio of radiative to advective timescales $\xi$).
-The kinematic model makes several simplifying assumptions (e.g, that the wind speed and direction are constant), but it reproduces GCM simulations fairly well.
+where $T(t)$ is the transit model, $P(t)$ is the thermal phase variation, and $E(t)$ is the ellipsoidal variation.
 
-We also fit a sine curve.
+The transit model is calculated with the \texttt{batman} package \citep{kreidberg15a}.
+The free parameters for the transit fit are the planet radius $r_p$, orbital inclination $i$, the ratio of semi-major axis to stellar radius $a/R_s$, and a linear stellar limb darkening parameter $u$.
+We fixed the orbital period $P = 0.925545613$ day and time of inferior conjunction $t_0 = 2456836.2964455$, based on \cite{southworth15}.
+We found that the system parameters were poorly constrained for the \HST/WFC3 phase curve (due to incomplete phase coverage) and \Spitzer\ Channel 1 phase curve (due to correlated noise), so we fixed the the inclination to $i = 84.54^\circ$ and the semi-major axis to stellar radius $a/R_s  = 2.925$, based on the best fit to the \emph{Spitzer} Channel 2 light curve.
 
-\subsubsection{Ellipsoidal Variations and Doppler Beaming}
-ellipsoidal variations/doppler beaming
+We explored several different models for the planet's thermal phase variation $P(t)$, using climate maps from the open-source Python package \texttt{SPIDERMAN}.
+This package allows users to input a climate map (temperature or brightness as a function of latitude and longitude), and generate the corresponding thermal phase curve over a specified wavelength range.
+We tested three different maps:  a two-temperature map, with a uniform dayside temperature $T_d$ and a uniform nightside temperature $T_n$; a map generated with spherical harmonics; and the physically-motivated kinematic model from \cite{zhang16}, which has just three free parameters (the nightside temperature $T_n$, the change in temperature from day-to-night side $\Delta_T$, and the ratio of radiative to advective timescales $\xi$).
+These models each have different strengths.
+The kinematic model incorporates the most prior knowledge of physics, and even though it makes several simplifying assumptions (e.g, that the wind speed and direction are constant), it reproduces GCM simulations fairly well.
+The spherical harmonics map is the most flexible and makes the fewest assumptions about the true climate.
+The two-temperature model is the simplest and has the fewest free parameters.
+For comparison, we also fit the phase variation with a sinusoid, which has been used for many past analyses of exoplanet phase curves \citep[e.g.]{FIXME}.  We found FIXME.
+
+In addition to the changing temperature of the planet's surface, the visible surface area also is expected to change as a function of orbital phase.
+WASP-103b is so close to its host star that it is likely tidally distorted and partially filling its Roche lobe \citep{gillon14}, which introduces ellipsoidal variations $E(t)$ in the light curve.
+Our light curves are not precise enough to detect the ellipsoidal variability, but we include a model prediction $E(t)$ to avoid introducing any bias in the thermal phase variation.
+We predict $E(t)$ using FIXME.
+FIXME doppler beaming?
 
@@
 
-\subsection{Systematics Models}
+\subsection{Systematics}
 Both the \HST\ and \Spitzer\ phase curves have systematic noise caused by variations in the sensitivity of the instrument over time.
@@
 The eclipse model is normalized such that the flux during eclipse is 1 and out of eclipse is $f_p/f_s$, and the transit model is normalized to unity out of transit.
-The planet's orbital parameters are poorly constrained by the WFC3 light curve due to incomplete phase coverage, so we fix the inclination to $i = 84.54^\circ$, the semi-major axis to stellar radius $a/R_s  = 2.925$, based on the best fit to the \emph{Spitzer} Channel 2 light curve (described below).
-We use the orbital period $P = 0.925545613$ day, and time of inferior conjunction $t_0 = 2456836.2964455$ from \cite{southworth15}.
+
 All free parameters were assumed to have a common value for both \emph{HST} visits, with the exception of $c$, $v_1$ and $v_2$, which were allowed to vary between visits.

### 2017-10-10 ms.tex
systematics

@@
 We fit a two-component model to the full-orbit phase curves.
-One component models the astrophysical signal (the planet's thermal phase variation and transit), and the other component models the systematic noise introduced by changes in the instrument sensitivity.
+One component models the astrophysical signal (the planet's thermal phase variation and transit), and the other component models the systematic noise introduced by changes in instrument sensitivity over time.
 For each light curve, we fit the physical and systematic components simultaneously.
+For the \HST\ data, where we observed two light curves, we constrain the physical parameters to be the same for both, but allow some of the systematics parameters to vary (see \S\,\ref{sec:hst_sys}).
 
@@
 We assume the astrophysical signal $F_\mathrm{physical}(t)$ has the following form:
-
 \begin{equation}
@@
 \end{equation}
+where $T(t)$ is the transit model, $P(t)$ is the thermal phase variation, and $E(t)$ is ellipsoidal variation (change in the apparent radius of the planet with orbital phase due to tidal distortion).
 
-where $T(t)$ is the transit model, $P(t)$ is the thermal phase variation, and $E(t)$ is the ellipsoidal variation.
-
-The transit model is calculated with the \texttt{batman} package \citep{kreidberg15a}.
-The free parameters for the transit fit are the planet radius $r_p$, orbital inclination $i$, the ratio of semi-major axis to stellar radius $a/R_s$, and a linear stellar limb darkening parameter $u$.
-We fixed the orbital period $P = 0.925545613$ day and time of inferior conjunction $t_0 = 2456836.2964455$, based on \cite{southworth15}.
-We found that the system parameters were poorly constrained for the \HST/WFC3 phase curve (due to incomplete phase coverage) and \Spitzer\ Channel 1 phase curve (due to correlated noise), so we fixed the the inclination to $i = 84.54^\circ$ and the semi-major axis to stellar radius $a/R_s  = 2.925$, based on the best fit to the \emph{Spitzer} Channel 2 light curve.
+We calculate the transit model with the \texttt{batman} package \citep{kreidberg15a}.
+The free parameters are the planet radius $r_p$, orbital inclination $i$, the ratio of semi-major axis to stellar radius $a/R_s$, and a linear stellar limb darkening parameter $u$.
+We fixed the orbital period to $P = 0.925545613$ day and time of inferior conjunction to $t_0 = 2456836.2964455$, based on estimates from \cite{southworth15}.
+We found that the system parameters were poorly constrained for the \HST/WFC3 phase curve (due to incomplete phase coverage) and \Spitzer\ Channel 1 phase curve (due to correlated noise), so for those light curves we fixed the the inclination to $i = 84.54^\circ$ and the semi-major axis to stellar radius $a/R_s  = 2.925$, based on the best fit to the \emph{Spitzer} Channel 2 light curve.
 
@@
 The two-temperature model is the simplest and has the fewest free parameters.
-For comparison, we also fit the phase variation with a sinusoid, which has been used for many past analyses of exoplanet phase curves \citep[e.g.]{FIXME}.  We found FIXME.
+In addition to these maps, we also fit the phase variation with a sinusoid, which has been used for many past analyses of exoplanet phase curves \citep[e.g.]{FIXME}.
+%We explored adding an additional sine term to model the thermal phase variation, but the additional degrees of freedom are not justified according to the Bayesian Information Criterion (BIC).
 
@@
 Both the \HST\ and \Spitzer\ phase curves have systematic noise caused by variations in the sensitivity of the instrument over time.
-For the WFC3 data, the dominant systematic is an orbit-long exponential trend due to charge traps filling up over successive exposures \citep{zhu17}.
-For \Spitzer\, the intrapixel sensitivity effect is the primary source of noise.
+For the \HST/WFC3 data, the dominant systematic is an orbit-long exponential trend due to charge traps filling up over successive exposures \citep{zhu17}.
+For \Spitzer\, the primary source of noise is the intrapixel sensitivity effect.
 The detector's pixels do not have uniform sensitivity, so slight changes in telescope pointing cause the recorded flux to vary.
@@
 \subsubsection{\HST\ Systematics}
-The raw data exhibit time-dependent systematic trends typically seen in WFC3 light curves, which we correct using a systematics model of the form:
-
+\label{sec:hst_sys}
+We fit for the WFC3 systematics using an analytic model of the form:
 \begin{equation}
@@
 \end{equation}
-
-\noindent where $t_\mathrm{v}$ is time elapsed since the first exposure in a visit and $t_\mathrm{orb}$ is time since the first exposure in an orbit.
+where $t_\mathrm{v}$ is time elapsed since the first exposure in a visit and $t_\mathrm{orb}$ is time since the first exposure in an orbit.
 $S(t)$ is a scale factor equal to 1 for exposures with spatial scanning in the forward direction and $s$ for reverse scans.
@@
 The first orbit in each visit shows larger systematic trends than subsequent orbits, so we exclude these data in our final analysis \citep[a common practice; see e.g.][]{kreidberg14a}.
-
-We fit the systematics model simultaneously with the physical parameters for the system. The complete model is
-
-\begin{equation}
-F(t) = F_\mathrm{sys}(t)\left[T(t) + (E(t) - 1)(1 + A\cos(2\pi(t - \theta)/P))\right]
-\label{eq:model}
-\end{equation}
-
-\noindent where $T(t)$ is a transit model, $E(t)$ is an eclipse model, $P$ is the planet orbital period, and $A$ and $\theta$ are free parameters to fit the amplitude and offset for the thermal phase variation.
-The free parameters for the transit and eclipse model are the planet-to-star radius ratio $r_p/r_s$, the planet-to-star flux ratio $f_p/f_s$, and a linear limb darkening parameter.
-The eclipse model is normalized such that the flux during eclipse is 1 and out of eclipse is $f_p/f_s$, and the transit model is normalized to unity out of transit.
+FIXME: what other orbits did we exclude?
+did we drop the first exposure?
 
 All free parameters were assumed to have a common value for both \emph{HST} visits, with the exception of $c$, $v_1$ and $v_2$, which were allowed to vary between visits.
-We explored adding an additional cosine term to model the thermal phase variation, but the additional degrees of freedom are not justified according to the Bayesian Information Criterion (BIC).
-The transit and eclipse models were calculated with the \texttt{batman} package \citep{kreidberg15a}.
-%Figure\;\ref{fig:w103_hst} shows the fitted broadband phase curve.
 
 \subsubsection{\Spitzer\ Systematics}
-and fit the systematics with the BLISS mapping technique \citep{stevenson12}.
+We fit the \Spitzer\ systematics with the BLISS mapping technique \citep{stevenson12}.
 This technique creates a map of the intrapixel sensitivity while simultaneously fitting for other systematics and the physical parameters of the system.
-In addition to the intrapixel sensitivity map, we fit the data for a linear trend in time and used the same transit, eclipse, and phase variation model as in Equation%\;\ref{eq:model}.
-
-which orbits/data
-
+In addition to the intrapixel sensitivity map, we fit the data for a linear trend in time.
 \section{Results}
+We achieved
 
 \subsection{Phase-Resolved Spectra}
-After fitting
+We used the best-fit phase curves (with systematics removed) to generate phase-resolved emission spectra.
+We binned each phase curve in FIXME evenly spaced intervals between phase FIXME and FIXME.
+In each phase bin, we estimated the planet-to-star flux by taking the mean value of the data points in the bin.
+To estimate the uncertainty, we took the standard deviation of the points in the bin and added it in quadrature to the standard deviation of the data points during secondary eclipse (phase FIXME to FIXME).
+This procedure accounts for the uncertainty in the baseline stellar flux (which we measure during secondary eclipse).
+
+To estimate the dayside planet-to-star flux, we did FIXME.
 
@@
 \subsection{Comparison of Thermal Phase Variation Models}
+All four of the thermal phase variation models we consider (two-temperature, kinematic, spherical harmonics, and sinusoid) provide good fits to the observed phase curves.
+Table FIXME summarized the goodness of fit
 
-\section{Composition of the Atmosphere}
+\section{Retrieval}
 
-\subsection{Retrieval}
+\subsection{Bond Albedo}
 
@@
 \section{Comparison with Brown Dwarfs and Directly Imaged Planets}
+cite Tremblin et al. 2017 ? (https://arxiv.org/pdf/1710.02640.pdf)
+
+\section{Discussion and Conclusions}
 

### 2017-10-12 ms.tex
systematics

@@
 Each visit was 15 orbits in duration and spanned 23 hours.
+The last half of orbit 15 in each visit was used for a gyro bias update and does not produce useable science data.
 We took a direct image of the star with the F126N filter at the beginning of each orbit to determine the wavelength solution zero-point.
@@
 \section{Light Curve Fits}
-We fit a two-component model to the full-orbit phase curves.
+We fit a two-component model to the light curves.
 One component models the astrophysical signal (the planet's thermal phase variation and transit), and the other component models the systematic noise introduced by changes in instrument sensitivity over time.
-For each light curve, we fit the physical and systematic components simultaneously.
+For each light curve, we fit the physical and systematic components simultaneously, such that the total observed flux as a function of time is given by $F(t) = F_\mathrm{physical}(t) \times F_\mathrm{sys}(t)$.
 For the \HST\ data, where we observed two light curves, we constrain the physical parameters to be the same for both, but allow some of the systematics parameters to vary (see \S\,\ref{sec:hst_sys}).
@@
 \end{equation}
-where $T(t)$ is the transit model, $P(t)$ is the thermal phase variation, and $E(t)$ is ellipsoidal variation (change in the apparent radius of the planet with orbital phase due to tidal distortion).
+where $T(t)$ is the transit model, $P(t)$ is the thermal phase variation, $E(t)$ is ellipsoidal variation (change in the apparent radius of the planet with orbital phase due to tidal distortion), and $\alpha(\lambda)$ is the dilution from the companion star (FIXME).
 
@@
 We found that the system parameters were poorly constrained for the \HST/WFC3 phase curve (due to incomplete phase coverage) and \Spitzer\ Channel 1 phase curve (due to correlated noise), so for those light curves we fixed the the inclination to $i = 84.54^\circ$ and the semi-major axis to stellar radius $a/R_s  = 2.925$, based on the best fit to the \emph{Spitzer} Channel 2 light curve.
+(FIXME: looks like we used Southworth?)
 
@@
 The two-temperature model is the simplest and has the fewest free parameters.
-In addition to these maps, we also fit the phase variation with a sinusoid, which has been used for many past analyses of exoplanet phase curves \citep[e.g.]{FIXME}.
+In addition to these maps, we also fit the phase variation with a sinusoid, which has been used for many past analyses of exoplanet phase curves (FIXME).
 %We explored adding an additional sine term to model the thermal phase variation, but the additional degrees of freedom are not justified according to the Bayesian Information Criterion (BIC).
 
-In addition to the changing temperature of the planet's surface, the visible surface area also is expected to change as a function of orbital phase.
+In addition to the changing temperature of the planet's surface, the visible surface area is also expected to change as a function of orbital phase.
 WASP-103b is so close to its host star that it is likely tidally distorted and partially filling its Roche lobe \citep{gillon14}, which introduces ellipsoidal variations $E(t)$ in the light curve.
 Our light curves are not precise enough to detect the ellipsoidal variability, but we include a model prediction $E(t)$ to avoid introducing any bias in the thermal phase variation.
-We predict $E(t)$ using FIXME.
+We model $E(t)$ using the analytic expression from \cite{leconte11}, which
+
 FIXME doppler beaming?
+
+\begin{figure}
+\includegraphics[width = 0.5\textwidth]{Figures/ellipsoidal.pdf}
+\caption{Projected area of the planet as a function of orbital phase.}
+\label{fig:ellipsoidal}
+\end{figure}
+
+\subsection{Systematics}
+Both the \HST\ and \Spitzer\ phase curves have systematic noise caused by variations in the sensitivity of the instrument over time.
+For the \HST/WFC3 data, the dominant systematic is an orbit-long exponential trend due to charge traps filling up over successive exposures \citep{long15, zhu17}.
+For \Spitzer\, the primary source of noise is the intrapixel sensitivity effect.
+The detector's pixels do not have uniform sensitivity, so slight changes in telescope pointing cause the recorded flux to vary.
+
+\subsubsection{\HST\ Systematics}
+\label{sec:hst_sys}
+We fit the WFC3 systematics using an analytic model of the form:
+\begin{equation}
+ F_\mathrm{sys}(t) = (c\,S(t) + v_1\,t_\mathrm{v} + v_2\,t_\mathrm{v}^2)(1 - \exp(-a\,t_\mathrm{orb} - b))
+\end{equation}
+where $t_\mathrm{v}$ is time elapsed since the first exposure in a visit and $t_\mathrm{orb}$ is time since the first exposure in an orbit.
+$S(t)$ is a scale factor equal to 1 for exposures with spatial scanning in the forward direction and $s$ for reverse scans.
+The orbit-long ramp parameters are consistent for all the visits, so we constrained $a$, $b$, and $s$ to have the same value for all visits in the final fit.
+The visit-long trends are not consistent, so $c$, $v_1$, and $v_2$ were allowed to vary between visits.
+We fixed $v_2$ to zero for the two secondary eclipse observations from Program 13360, since the visit-long trend for shorter observations is fit well by a linear slope.
+
+Some segments of the data exhibit stronger systematics than others, so we exclude these data in our final analysis.
+We drop the first orbit from every visit and the first exposure from every orbit \citep[following common practice; see e.g.][]{kreidberg14a}.
+We also discard exposures from the last half of orbit 15 from the phase curve observations, which were taken in staring mode to enable a gyro bias update.
+Since we observed two phase curves, we have complete orbital phase coverage the planet despite discarding some data.
+
+\subsubsection{\Spitzer\ Systematics}
+We fit the \Spitzer\ systematics with the BLISS mapping technique \citep{stevenson12}.
+This technique creates a map of the intrapixel sensitivity while simultaneously fitting for other systematics and the physical parameters of the system.
+In addition to the intrapixel sensitivity map, we fit the data for a linear trend in time.
+
+\begin{figure}
+\includegraphics[width = 0.5\textwidth]{Figures/systematics.pdf}
+\caption{Raw light curves.}
+\label{fig:systematics}
+\end{figure}
+
+\section{Results}
+We achieved
 
@@
 \end{figure*}
-
-\subsection{Systematics}
-Both the \HST\ and \Spitzer\ phase curves have systematic noise caused by variations in the sensitivity of the instrument over time.
-For the \HST/WFC3 data, the dominant systematic is an orbit-long exponential trend due to charge traps filling up over successive exposures \citep{zhu17}.
-For \Spitzer\, the primary source of noise is the intrapixel sensitivity effect.
-The detector's pixels do not have uniform sensitivity, so slight changes in telescope pointing cause the recorded flux to vary.
-
-\subsubsection{\HST\ Systematics}
-\label{sec:hst_sys}
-We fit for the WFC3 systematics using an analytic model of the form:
-\begin{equation}
- F_\mathrm{sys}(t) = (c\,S(t) + v_1\,t_\mathrm{v} + v_2\,t_\mathrm{v})(1 - \exp(-a\,t_\mathrm{orb} - b))
-\end{equation}
-where $t_\mathrm{v}$ is time elapsed since the first exposure in a visit and $t_\mathrm{orb}$ is time since the first exposure in an orbit.
-$S(t)$ is a scale factor equal to 1 for exposures with spatial scanning in the forward direction and $s$ for reverse scans.
-In the fit, $c$, $v_1$, $v_2$, $a$, $b$, and $s$ are free parameters.
-The first orbit in each visit shows larger systematic trends than subsequent orbits, so we exclude these data in our final analysis \citep[a common practice; see e.g.][]{kreidberg14a}.
-FIXME: what other orbits did we exclude?
-did we drop the first exposure?
-
-All free parameters were assumed to have a common value for both \emph{HST} visits, with the exception of $c$, $v_1$ and $v_2$, which were allowed to vary between visits.
-
-\subsubsection{\Spitzer\ Systematics}
-We fit the \Spitzer\ systematics with the BLISS mapping technique \citep{stevenson12}.
-This technique creates a map of the intrapixel sensitivity while simultaneously fitting for other systematics and the physical parameters of the system.
-In addition to the intrapixel sensitivity map, we fit the data for a linear trend in time.
-\section{Results}
-We achieved
 

### 2017-10-12 Figures/proj_area.py

@@ -1,0 +1,46 @@
+import numpy as np
+from matplotlib import rc
+import matplotlib.pyplot as plt
+import seaborn as sns
+sns.set_context("talk")
+sns.set_style("white")
+sns.set_style("ticks", {"xtick.direction":"in", "ytick.direction":"in"})
+
+rc('font',**{'family':'sans-serif','sans-serif':['Arial']})
+
+plt.figure(figsize=(6,3))
+
+def proj_area(phi, inc):
+        R0 = 1.07e8             #planet radius in m
+        p = 0.00117             # planet-to-star mass ratio
+        r = 2.9695e9            #orbital separation in m
+        kn = 0.653              #from table B5 of Leconte et al. 2011
+        n = 1.005
+        qn = kn*(1.- n/5.)      #n 
+
+
+        alpha1 = 2.5*qn*R0**3/(p*r**3)
+        alpha2 = -1.25*qn*R0**3/(p*r**3)
+        alpha3 = alpha2
+
+        a1 = R0*(1+alpha1)
+        a2 = R0*(1+alpha2)
+        a3 = R0*(1+alpha3)
+
+        return  np.sqrt(a3**2*np.sin(inc)**2*(a1**2*np.sin(phi)**2+a2**2*np.cos(phi)**2)+ a1**2*a2**2*np.cos(inc)**2)/(a2*a3)
+
+
+phi = np.linspace(0., 2.*np.pi, 1000)
+inc = 1.523
+
+area = proj_area(phi, inc)
+
+plt.plot(phi/(2.*np.pi), area)
+
+plt.xlabel("Orbital phase") 
+plt.ylabel("Relative area")
+
+plt.xlim(0,1)
+plt.tight_layout()
+plt.savefig("ellipsoidal.pdf")
+plt.show()

### 2017-10-17 ms.tex
caption

@@
 We used the SPARS10/NSAMP = 15 read-out mode, which has an exposure time of 103 seconds.
-To optimize the duty cycle of the observations, we used the spatial scan observing mode with a scan rate of 0.03"/s, alternating between forward and backward scanning on the detector.
-The scan height was 25 pixels and the peak counts were 35k photoelectrons per pixel.
+To optimize the duty cycle of the observations, we used the spatial scan observing mode with a scan rate of 0.03 arcsec/s, alternating between forward and backward scanning on the detector.
+The scan height was 25 pixels and the peak counts were $35\times10^3$ photoelectrons per pixel.
 We collected a total of 18 spatial scan exposures per orbit.
@@
 We fit a two-component model to the light curves.
-One component models the astrophysical signal (the planet's thermal phase variation and transit), and the other component models the systematic noise introduced by changes in instrument sensitivity over time.
+One component models the astrophysical signal (the planet's thermal phase variation and transit), and the other component models the systematic noise introduced by time-dependent changes in instrument performance.
 For each light curve, we fit the physical and systematic components simultaneously, such that the total observed flux as a function of time is given by $F(t) = F_\mathrm{physical}(t) \times F_\mathrm{sys}(t)$.
-For the \HST\ data, where we observed two light curves, we constrain the physical parameters to be the same for both, but allow some of the systematics parameters to vary (see \S\,\ref{sec:hst_sys}).
+For the \HST\ data, where we observed two phase curves and two additional eclipses, we constrain the physical parameters to be the same for all visits, but allow some of the systematics parameters to vary (for more details see \S\,\ref{sec:hst_sys}).
+We fit the WFC3 band-integrated (``white" light curve"), as well as the spectroscopic light curves (FIXME describe).
 
@@
 These models each have different strengths.
-The kinematic model incorporates the most prior knowledge of physics, and even though it makes several simplifying assumptions (e.g, that the wind speed and direction are constant), it reproduces GCM simulations fairly well.
+The kinematic model incorporates the most prior knowledge of physics, and even though it makes several simplifying assumptions (e.g, that the wind speed and direction are constant), it closely reproduces GCM simulations over a wide parameter space \citep{zhang16}.
 The spherical harmonics map is the most flexible and makes the fewest assumptions about the true climate.
@@
 \includegraphics[width = 0.5\textwidth]{Figures/ellipsoidal.pdf}
-\caption{Projected area of the planet as a function of orbital phase.}
+\caption{Projected area of the planet as a function of orbital phase, normalized to unity at phase zero. The area variation was predicted analytically using the model from \citep{leconte11}.}
 \label{fig:ellipsoidal}
@@
 where $t_\mathrm{v}$ is time elapsed since the first exposure in a visit and $t_\mathrm{orb}$ is time since the first exposure in an orbit.
-$S(t)$ is a scale factor equal to 1 for exposures with spatial scanning in the forward direction and $s$ for reverse scans.
+$S(t)$ is a scale factor equal to 1 for exposures with spatial scanning in the forward direction and $s$ for reverse scans, to account for the upstream-downstream effect (FIXME).
 The orbit-long ramp parameters are consistent for all the visits, so we constrained $a$, $b$, and $s$ to have the same value for all visits in the final fit.
-The visit-long trends are not consistent, so $c$, $v_1$, and $v_2$ were allowed to vary between visits.
+The visit-long trends differ from visit to visit, so $c$, $v_1$, and $v_2$ were allowed to vary between visits.
 We fixed $v_2$ to zero for the two secondary eclipse observations from Program 13360, since the visit-long trend for shorter observations is fit well by a linear slope.
@@
 \includegraphics[width = 0.5\textwidth]{Figures/systematics.pdf}
-\caption{Raw light curves.}
+\caption{Raw light curves for WASP-103b observed with \HST/WFC3 (top panel) and \Spitzer/IRAC (bottom two panels).
+The data points are indicated with black dots.
+The \HST\ data are unbinned, and the Spitzer data are binned in time segments of FIXME minutes with error bars indicating the bin standard deviation.
+The colored lines show the best fit models, which include the astrophysical signal and instrument systematics.
+The gray lines indicate the contribution from the instrument systematics alone (which would be observed for a source with constant brightness and no planet).
+For visual clarity, we corrected the \HST\ data for the upstream-downstream effect, separated the four visits by adding a flux offset, and zoomed in on the phase variation, so the transits are not displayed in the panel.}
 \label{fig:systematics}
@@
 \section{Results}
-We achieved
+We achieved good quality fits!
 

### 2017-10-19 ms.tex
correlated noise figure
post fire'

@@
 
+\begin{figure}
+\includegraphics[width = 0.5\textwidth]{Figures/rms.pdf}
+\caption{Root mean square (rms) variability in the light curves as a function of bin size (black lines) compared to the expected rms from photon noise (colored lines).
+The central wavelength of the light curve is indicated in the upper right corner of each panel.
+With the exception of the \Spitzer\ 3.6 $\mu$m channel, the rms for the light curves bins down in agreement with predictions from the photon noise.}
+\label{fig:rms}
+\end{figure}
+
 \begin{figure*}
@@
 
+\subsection{Hotspot Offset}
+
 \section{Retrieval}

### 2017-10-20 Figures/hst_maptemp.py
new fig

@@ -1,153 +1,0 @@
-import numpy as np
-import scipy.interpolate as spi
-from mpl_toolkits.basemap import Basemap
-import matplotlib.pyplot as plt
-import matplotlib as mpl
-import spiderman as sp
-import pickle
-from lc_fit import Model, LightCurveData
-
-mpl.rcParams['font.sans-serif'] = 'Arial'
-mpl.rcParams['font.size'] = 14
-mpl.rcParams['lines.linewidth'] = 1.4
-
-#return blackbody spectral radiance as a function of wavelength lambda (in m) and temperature T (Kelvin)
-def bb(l, T):
-	h = 6.6261e-34   #J/s
-	c = 2.9979e8       #m/s
-	k = 1.38065e-23     #J/K
-	return 2*h*c**2/(l**5*(np.exp(h*c/(l*k*T)-1)))
-
-def get_T(relative):
-	l = 1.4e-6
-	Ts = 6110.
-	rprs = 0.11092
-	T = np.arange(10, 4000, 10)
-	rel = bb(l, T)/bb(l, Ts)*rprs**2
-	diff = np.abs(rel - relative)
-	return T[diff == np.min(diff)]
-
-def convert_to_T(flux):
-	Ts = 6110. 
-	l = 1.4e-6
-	n, m = flux.shape
-	T = np.zeros_like(flux)
-	for i in range(m):
-		for j in range(n):
-			relative = flux[i,j]
-			if relative > 0: T[i,j] = get_T(relative)
-			else: 
-                                print relative
-                                T[i,j] = 0.
-	return T
-
-def initialize_params(spider_params):
-    spider_params.n_layers= 5
-    spider_params.t0= 200               # Central time of PRIMARY transit [days]
-    spider_params.per= 0.81347753       # Period [days]
-    spider_params.a_abs= 0.01526        # The absolute value of the semi-major axis [AU]
-    spider_params.inc= 82.33            # Inclination [degrees]
-    spider_params.ecc= 0.0              # Eccentricity
-    spider_params.w= 90                 # Argument of periastron
-    spider_params.rp= 0.111            # Planet to star radius ratio
-    spider_params.a= 4.855              # Semi-major axis scaled by stellar radius
-    spider_params.p_u1= 0               # Planetary limb darkening parameter
[…]

### 2017-10-24 Figures/fit_table.py
table

@@ -1,9 +1,7 @@
 import numpy as np
 from lc_fit import Model, LightCurveData
-import pickle
-
+import pickle 
 #zhang, hotspot, spherical
-
 ch1_chi2 = [0.9, 0.9, 0.9]
 chi1_aic = [7131.0, 7107.4, 7096.7]
 chi1_bic = [7075.2, 7058.5, 7040.9]
@@ -11,7 +9,6 @@ chi1_bic = [7075.2, 7058.5, 7040.9]
 ch2_chi2 = [1.07, 1.07277, 1.07215]
 chi2_aic = [8345.95, 8355.5, 8331.6]
 chi2_bic = [8401.61, 8384.2, 8387.3]
-
 
 # bset fits for WFC3
 wfc3_chi2 = []
@@ -21,12 +18,50 @@ wfc3_bic = []
 models = ["zhang", "hotspot_t", "spherical"]
 path = "WFC3_best_fits/"
 for i, model in enumerate(models):
-
 	p = pickle.load(open(path+"bestfit_"+model+".pic", "rb")) 
 
 	d, m, par = p[0], p[1], p[2]            #stores data,  model, and best fit parameters into d, m, & par
 	wfc3_bic.append(m.bic)
 	wfc3_chi2.append(m.chi2)
+	bic = m.chi2 + d.nfree_param*np.log(d.npoints)
+	aic = m.chi2 + 2.*d.nfree_param
+	print m.chi2red, bic, aic
 
-print wfc3_bic
-print wfc3_chi2
+#Temperatures:
+#HST:
+#model, Tmin, Tmax =  zhang 1942.83470024 3884.44683954
+#model, Tmin, Tmax =  hotspot_t 0.0 2860.2228932
+#model, Tmin, Tmax =  spherical 1232.97287197 3213.68213304
+
+wfc3_tmin = [1943, 0, 1233]
+wfc3_tmax = [3884, 2860, 3214]
+
+#Spitzer Ch 2
+#model, Tmin, Tmax =  zhang 1719.0 4257.78308959
+#model, Tmin, Tmax =  hotspot_t 1380.0 3305.0e
+#model, Tmin, Tmax =  spherical 930.545006798 3775.38559767
+ch2_tmin = [1719., 1380, 930]
+ch2_tmax = [4257, 3305, 3775]
+
+#Spitzer Ch 1
+#model, Tmin, Tmax =  zhang 1952.0 3672.60664016
[…]

### 2017-10-25 ms.tex
spectra blah
new fig
table
table!
formula

@@
 
+\author{Kevin B. Stevenson}
+\affiliation{Space Telescope Science Institute}
+\nocollaboration
+
+\author{Tom Louden}
+\affiliation{University of Warwick}
+\nocollaboration
+
 \author{Mick\"{a}el Bonnefoy}
@@
 \affiliation{American Museum of Natural History}
-\nocollaboration
-
-\author{Kevin B. Stevenson}
-\affiliation{Space Telescope Science Institute}
 \nocollaboration
@@
 
-%The apparent low amplitude variability is likely due to rotational modulation in the visibility of weak, magnetic surface features \citep[see, e.g.,][]{hfh1995}.
-
-%This implies there can be very little night-to-night variability in WASP-103.
-The three seasonal mean brightness values given in column 5 scatter about their grand mean with a standard deviation of 0.0036 mag, but we note that the most discrepant mean is from the third season, for which we have only partial coverage.
-Therefore, our results do not completely rule out low-level, year-to-year variability of 0.001~mag or so.
-
-%We performed periodogram analyses of the individual observing seasons and the complete dataset and found no significant periodicity.
-To maximize the possibility of detecting a rotation signal in WASP-103, we normalized the dataset by adding a constant offset to the second and third observing seasons to have the same mean as the first.
-%To first order, this removes possible long-term variability in WASP-103 and/or the comparison stars as well as any uncorrected, long-term systemmatic effects.
-It is the normalized data that are plotted in the top panel of Fig.~1.
-
-%We performed a least-squares fit to the data with a sine curve with trial frequencies between 0.005 and 0.95 c/d, corresponding to periods between one and 200 days.
-The goodness of fit at each frequency is measured as the reduction factor in the variance of the original data.
-The result suggests low-amplitude brightness variability in WASP-103 with a period near 6.814 days.
-
 \begin{figure}
@@
 For the \HST\ data, where we observed two phase curves and two additional eclipses, we constrain the physical parameters to be the same for all visits, but allow some of the systematics parameters to vary (for more details see \S\,\ref{sec:hst_sys}).
-We fit the WFC3 band-integrated (``white" light curve"), as well as the spectroscopic light curves (FIXME describe).
+We fit the WFC3 band-integrated (``white" light curve"), as well as spectroscopic light curves created from 10 wavelength bins uniformly spaced at $0.05 \mu$m intervals.
 
@@
 \begin{equation}
-	F_\mathrm{physical}(t) = T(t) \times P(t) \times E(t) 
+	F_\mathrm{physical}(t) = F_s (1 + \alpha) \times T(t) + F_p(t) 
 \end{equation}
-where $T(t)$ is the transit model, $P(t)$ is the thermal phase variation, $E(t)$ is ellipsoidal variation (change in the apparent radius of the planet with orbital phase due to tidal distortion), and $\alpha(\lambda)$ is the dilution from the companion star (FIXME).
+where $F_s$ is the stellar flux, $T(t)$ is the transit model (the fraction of the stellar disk that is visible), $\alpha$ is additional fractional flux from the companion star, and $F_p(t)$ is the planet flux.
+FIXME what is alhpha.
+The flux from the planet is given by
+\begin{equation}
+F_p(t) = \pi I(t)[R(t)]^2
+\end{equation}
+where $I(t)$ is the disk-integrated planet intensity and $R(t)$ is the planet's effective radius (which changes with orbital phase due to tidal distortion).
 
 We calculate the transit model with the \texttt{batman} package \citep{kreidberg15a}.
-The free parameters are the planet radius $r_p$, orbital inclination $i$, the ratio of semi-major axis to stellar radius $a/R_s$, and a linear stellar limb darkening parameter $u$.
-We fixed the orbital period to $P = 0.925545613$ day and time of inferior conjunction to $t_0 = 2456836.2964455$, based on estimates from \cite{southworth15}.
-We found that the system parameters were poorly constrained for the \HST/WFC3 phase curve (due to incomplete phase coverage) and \Spitzer\ Channel 1 phase curve (due to correlated noise), so for those light curves we fixed the the inclination to $i = 84.54^\circ$ and the semi-major axis to stellar radius $a/R_s  = 2.925$, based on the best fit to the \emph{Spitzer} Channel 2 light curve.
-(FIXME: looks like we used Southworth?)
+Many of the physical parameters are tightly constrained by \cite{southworth15}, so we fixed the orbital period, time of inferior conjunction, orbital inclination, and ratio of semi-major axis to stellar radius to the previously published values ($P = 0.925545613$ day, $t_0 = 2456836.2964455 \mathrm{BJD_{TDB}}$, $i = 87.3^\circ$, and $a/R_s = 2.999$).
+As a test, we fit for these parameters with the Spitzer Channel 2 light curve, which has the best phase coverage and least systematic noise of the three data sets.
+We found that the transit parameters are consistent with the \cite{southworth15} results, so we proceeded with the remainder of the analysis holding those parameters fixed.
+The free parameters for the transit model were the transit depth $r_p$ and a linear limb darkening parameter $u$.
 
@@
 
+\begin{deluxetable}{lllllll}
+\tablecolumns{7}
+\tablewidth{0pt}:
+\tablecaption{Model Comparison \label{table:models}}
+\tablehead{
+\colhead{Data Set} & \colhead{Model} & \colhead{$T_\mathrm{min}$} & \colhead{$T_\mathrm{max}$} & \colhead{$\chi^2$} & \colhead{$\Delta$ AIC} & \colhead{$\Delta$ BIC}}
+\startdata
+WFC3 & Sph. Harmonics & 1212 & 3190 & 949.6 & 0.0 & 0.0 \\
+\, & Kinematic & 1955 & 3910 & 961.6 & 12.0 & 12.0 \\
+\, & Two Temp. & 0 & 2837 & 999.4 & 47.7 & 43.3 \\
+Ch 1 & Sph. Harmonics & 1277 & 3442 & 0.9 & 0.0 & 0.0 \\
+\, & Kinematic & 1952 & 3672 & 0.9 & 34.3 & 34.3 \\
+\, & Two Temp. & 1427 & 3039 & 0.9 & 10.7 & 17.6 \\
+Ch 2 & Sph. Harmonics & 930 & 3775 & 1.1 & 0.0 & 3.1 \\
+\, & Kinematic & 1719 & 4257 & 1.1 & 14.35 & 17.41 \\
+\, & Two Temp. & 1380 & 3305 & 1.1 & 23.9 & 0.0 \\
+\enddata
+\vspace{-0.8cm}
+\tablecomments{comments}
+\end{deluxetable}
+
 \begin{figure}
@@
 
+\begin{figure}
+\includegraphics[width = 0.5\textwidth]{Figures/dayside_spectrum.pdf}
+\caption{Dayside emission spectrum.}
+\label{fig:dayside}
+\end{figure}
+
+\begin{figure*}
+\includegraphics[width = 1.0\textwidth]{Figures/emission_spectra.pdf}
+\caption{Phase-resolved emission spectra.}
+\label{fig:spectra}
+\end{figure*}
+
 \subsection{Phase-Resolved Spectra}
@@
 
+\begin{figure*}
+\includegraphics[width = 1.0\textwidth]{Figures/hst_model_comparison.pdf}
+\caption{Left: fits to the broadband WFC3 phase curve. Right: best fit temperature maps.}
+\label{fig:model_comparison}
+\end{figure*}
+
 \subsection{Hotspot Offset}
@@
 \section{Comparison with GCMs}
+
+\section{Comparison of T/P Profiles}
 

### 2017-10-25 Figures/rms.py

@@ -80,8 +80,12 @@ for ii, f in enumerate(files):
     rms, stderr, binsz, rmserr = computeRMS(resid, maxnbins = None, binstep = 1, isrmserr = True)
 
     normfactor = stderr[0]
+    #normfactor = m.rms_predicted
+
     plt.loglog(binsz, rms/normfactor, color='black', lw=1.5, label='Fit RMS')    # our noise
     plt.loglog(binsz, stderr/normfactor, color='blue', ls='-', lw=2, label='Std. Err.') # expected noise
+
+    #plt.axhline(m.rms_predicted/normfactor, linestyle = 'dashed')
 
     plt.gca().set_xticks([1, 10])
     plt.gca().set_xticklabels([1, 10])

### 2017-10-25 ms.tex
DO NOT FORGET TO PUSH YOUR CHANGDS

@@
 For the \HST\ data, where we observed two phase curves and two additional eclipses, we constrain the physical parameters to be the same for all visits, but allow some of the systematics parameters to vary (for more details see \S\,\ref{sec:hst_sys}).
-We fit the WFC3 band-integrated (``white" light curve"), as well as spectroscopic light curves created from 10 wavelength bins uniformly spaced at $0.05 \mu$m intervals.
+We fit the WFC3 band-integrated (``white" light curve"), as well as spectroscopic light curves created from 10 wavelength bins uniformly spaced at $0.05\,\mu$m intervals between $1.15$ and $1.65\,\mu$m.
 
 \subsection{Astrophysical Signal}
-We assume the astrophysical signal $F_\mathrm{physical}(t)$ has the following form:
+We assume the measured astrophysical signal $F_\mathrm{physical}$ has the following form:
 \begin{equation}
-	F_\mathrm{physical}(t) = F_s (1 + \alpha) \times T(t) + F_p(t) 
+	F_\mathrm{physical}(t, \lambda) \propto F_s(\lambda) (1 + \alpha(\lambda)) \times T(t, \lambda) + F_p(t, \lambda) 
 \end{equation}
-where $F_s$ is the stellar flux, $T(t)$ is the transit model (the fraction of the stellar disk that is visible), $\alpha$ is additional fractional flux from the companion star, and $F_p(t)$ is the planet flux.
-FIXME what is alhpha.
+where $F_s(\lambda)$ is the stellar flux as a function of wavelength, $\alpha(\lambda)$ is the additional fractional flux from the companion star, $T(t, \lambda)$ is the transit model (the fraction of the stellar disk that is visible at time $t$), and $F_p(t, \lambda)$ is the disk-integrated planet flux.
+These terms are described in more detail below.
+We assume the stellar flux $F_s(\lambda)$ is a $6110\,\mathrm{K}$ blackbody \citep{gillon14}.
 The flux from the planet is given by
 \begin{equation}
-F_p(t) = \pi I(t)[R(t)]^2
+F_p(t) = I(t, \lambda)[R(t)]^2
 \end{equation}
-where $I(t)$ is the disk-integrated planet intensity and $R(t)$ is the planet's effective radius (which changes with orbital phase due to tidal distortion).
+where $I$ is the disk-integrated planet intensity and $R$ is the planet's effective area (which changes with orbital phase due to tidal distortion).
+In our final fit, we divide by the total stellar flux (primary and background stars), such that the astrophysical signal is:
+\begin{equation}
+	F_\mathrm{physical}(t) = T(t) + F_p(t, \lambda) /[F_s(\lambda) (1 + \alpha (\lambda))]
+\end{equation}
 
-We calculate the transit model with the \texttt{batman} package \citep{kreidberg15a}.
+We calculate the transit model $T(t)$ with the \texttt{batman} package \citep{kreidberg15a}.
 Many of the physical parameters are tightly constrained by \cite{southworth15}, so we fixed the orbital period, time of inferior conjunction, orbital inclination, and ratio of semi-major axis to stellar radius to the previously published values ($P = 0.925545613$ day, $t_0 = 2456836.2964455 \mathrm{BJD_{TDB}}$, $i = 87.3^\circ$, and $a/R_s = 2.999$).
@@
 
-We explored several different models for the planet's thermal phase variation $P(t)$, using climate maps from the open-source Python package \texttt{SPIDERMAN}.
-This package allows users to input a climate map (temperature or brightness as a function of latitude and longitude), and generate the corresponding thermal phase curve over a specified wavelength range.
+We explored several different models for the planet's disk-integrated intensity $I(t, \lambda)$, using climate maps from the open-source Python package \texttt{SPIDERMAN} \citep{louden17}.
+This package allows users to input a climate map (temperature or brightness as a function of latitude and longitude), and generate the corresponding planet-to-star flux for an observation at time $t$, over a specified wavelength range.
 We tested three different maps: a two-temperature map, with a uniform dayside temperature $T_d$ and a uniform nightside temperature $T_n$; a map generated with spherical harmonics; and the physically-motivated kinematic model from \cite{zhang16}, which has just three free parameters (the nightside temperature $T_n$, the change in temperature from day-to-night side $\Delta_T$, and the ratio of radiative to advective timescales $\xi$).
@@
 The spherical harmonics map is the most flexible and makes the fewest assumptions about the true climate.
-The two-temperature model is the simplest and has the fewest free parameters.
-In addition to these maps, we also fit the phase variation with a sinusoid, which has been used for many past analyses of exoplanet phase curves (FIXME).
+The two-temperature model is the simplest and easiest to compare to one-dimensional models of the dayside, which assume a uniform temperature/pressure profile.
+In all cases, we assumed that the planet is tidally locked, such that each orbital revolution corresponds to one complete rotation on its spin axis.
+%In addition to these maps, we also fit the phase variation with a sinusoid, which has been used for many past analyses of exoplanet phase curves (FIXME).
 %We explored adding an additional sine term to model the thermal phase variation, but the additional degrees of freedom are not justified according to the Bayesian Information Criterion (BIC).
 
-In addition to the changing temperature of the planet's surface, the visible surface area is also expected to change as a function of orbital phase.
-WASP-103b is so close to its host star that it is likely tidally distorted and partially filling its Roche lobe \citep{gillon14}, which introduces ellipsoidal variations $E(t)$ in the light curve.
-Our light curves are not precise enough to detect the ellipsoidal variability, but we include a model prediction $E(t)$ to avoid introducing any bias in the thermal phase variation.
+In addition to temperature, the planet's visible surface area $[R(t)]^2$ is also expected to vary with orbital phase due to tidal distortion \citep{gillon14}.
+In the observed light curve, changes in planet radius are degenerate with changes in temperature.
+To address the possible effects of radius variability on our data, we predict the variation using the analytic formula from \cite{leconte11b}, equation B.9, which computes the projected area of a triaxial ellipsoid.
+We assume a Love number $\kappa_n = 0.653$ based on Table B.5 of \cite{leconte11a}, for a highly irradiated, $1.5 R_\mathrm{J}$ planet aged 5 Gyr.
+The predicted ellipsoidal variability is shown in Figure\,\ref{fig:ellipsoidal}.
+At quadrature, the project radius is $8\%$ larger than at phase zero (mid-transit).
+FIXME: say this doesn't matter.
+
+FIXME: say what the dilution factor is.
+%Our light curves are not precise enough to detect the ellipsoidal variability, but we include a model prediction $E(t)$ to avoid introducing any bias in the thermal phase variation.
 We model $E(t)$ using the analytic expression from \cite{leconte11}, which
-
-FIXME doppler beaming?
+%FIXME doppler beaming?
 
@@
 \includegraphics[width = 0.5\textwidth]{Figures/ellipsoidal.pdf}
-\caption{Projected area of the planet as a function of orbital phase, normalized to unity at phase zero. The area variation was predicted analytically using the model from \citep{leconte11}.}
+\caption{Projected area of the planet as a function of orbital phase, normalized to unity at phase zero. The area variation was predicted analytically using the model from \citep{leconte11b}.}
 \label{fig:ellipsoidal}

### 2017-10-26 ms.tex
reorg

@@
 \begin{equation}
-	F_\mathrm{physical}(t, \lambda) \propto F_s(\lambda) (1 + \alpha(\lambda)) \times T(t, \lambda) + F_p(t, \lambda) 
+	%F_\mathrm{physical}(\lambda, t) = F_s(\lambda) (1 + \alpha(\lambda)) \times T(\lambda, t) + F_p(\lambda, t) 
+	F_\mathrm{physical}(\lambda, t) =  T(\lambda, t) + c(\lambda, t) \times F_p/F_s(\lambda, t)
 \end{equation}
-where $F_s(\lambda)$ is the stellar flux as a function of wavelength, $\alpha(\lambda)$ is the additional fractional flux from the companion star, $T(t, \lambda)$ is the transit model (the fraction of the stellar disk that is visible at time $t$), and $F_p(t, \lambda)$ is the disk-integrated planet flux.
-These terms are described in more detail below.
-We assume the stellar flux $F_s(\lambda)$ is a $6110\,\mathrm{K}$ blackbody \citep{gillon14}.
-The flux from the planet is given by
-\begin{equation}
-F_p(t) = I(t, \lambda)[R(t)]^2
-\end{equation}
-where $I$ is the disk-integrated planet intensity and $R$ is the planet's effective area (which changes with orbital phase due to tidal distortion).
-In our final fit, we divide by the total stellar flux (primary and background stars), such that the astrophysical signal is:
-\begin{equation}
-	F_\mathrm{physical}(t) = T(t) + F_p(t, \lambda) /[F_s(\lambda) (1 + \alpha (\lambda))]
-\end{equation}
+where $T(\lambda, t)$ is the transit model (the fraction of the stellar disk that is visible at time $t$), $F_p/F_s(\lambda, t)$ is the disk-integrated planet-to-star flux, and $c$ is a correction factor for companion star dilution and the planet's tidal distortion.
 
-We calculate the transit model $T(t)$ with the \texttt{batman} package \citep{kreidberg15a}.
+We calculated the transit model $T(t)$ with the \texttt{batman} package \citep{kreidberg15a}.
 Many of the physical parameters are tightly constrained by \cite{southworth15}, so we fixed the orbital period, time of inferior conjunction, orbital inclination, and ratio of semi-major axis to stellar radius to the previously published values ($P = 0.925545613$ day, $t_0 = 2456836.2964455 \mathrm{BJD_{TDB}}$, $i = 87.3^\circ$, and $a/R_s = 2.999$).
@@
 
-We explored several different models for the planet's disk-integrated intensity $I(t, \lambda)$, using climate maps from the open-source Python package \texttt{SPIDERMAN} \citep{louden17}.
-This package allows users to input a climate map (temperature or brightness as a function of latitude and longitude), and generate the corresponding planet-to-star flux for an observation at time $t$, over a specified wavelength range.
+We calculated the planet-to-star flux $F_p/F_s$ with the \texttt{SPIDERMAN} package \citep{louden17}.
+This package allows users to input a climate map (temperature or brightness as a function of latitude and longitude), and generate the corresponding flux ratio for an observation at time $t$.
+In our fit, we assumed the star is a FIXME PHOENIX model.
 We tested three different maps: a two-temperature map, with a uniform dayside temperature $T_d$ and a uniform nightside temperature $T_n$; a map generated with spherical harmonics; and the physically-motivated kinematic model from \cite{zhang16}, which has just three free parameters (the nightside temperature $T_n$, the change in temperature from day-to-night side $\Delta_T$, and the ratio of radiative to advective timescales $\xi$).
-These models each have different strengths.
-The kinematic model incorporates the most prior knowledge of physics, and even though it makes several simplifying assumptions (e.g, that the wind speed and direction are constant), it closely reproduces GCM simulations over a wide parameter space \citep{zhang16}.
-The spherical harmonics map is the most flexible and makes the fewest assumptions about the true climate.
-The two-temperature model is the simplest and easiest to compare to one-dimensional models of the dayside, which assume a uniform temperature/pressure profile.
-In all cases, we assumed that the planet is tidally locked, such that each orbital revolution corresponds to one complete rotation on its spin axis.
-%In addition to these maps, we also fit the phase variation with a sinusoid, which has been used for many past analyses of exoplanet phase curves (FIXME).
-%We explored adding an additional sine term to model the thermal phase variation, but the additional degrees of freedom are not justified according to the Bayesian Information Criterion (BIC).
 
-In addition to temperature, the planet's visible surface area $[R(t)]^2$ is also expected to vary with orbital phase due to tidal distortion \citep{gillon14}.
-In the observed light curve, changes in planet radius are degenerate with changes in temperature.
-To address the possible effects of radius variability on our data, we predict the variation using the analytic formula from \cite{leconte11b}, equation B.9, which computes the projected area of a triaxial ellipsoid.
+%We assume the stellar flux $F_s(\lambda)$ is a $6110\,\mathrm{K}$ blackbody \citep{gillon14}.  (FIXME - use a PHOENIX model instead). 
+We scaled the planet-to-star flux by a correction factor $c$ to account for dilution from the companion star and ellipsoidal variability due to the planet's tidal distortion.
+The correction factor took the form:
+\begin{equation}
+	c(\lambda, t) = (1 + \alpha(\lambda))A(t)
+\end{equation}
+where $\alpha(\lambda)$ is the additional fractional flux from the companion star and $A(t)$ is the sky-projected area of the planet.
+We estimated $\alpha(\lambda)$ based on the best fit spectral energy distribution from \cite{cartier16}.
+The companion star contributes FIXME percent of the flux at FIXME $\mu$m.
+We calculated $A(t)$ using the analytic formula from \cite{leconte11b}, equation B.9, which computes the projected area of a triaxial ellipsoid.
 We assume a Love number $\kappa_n = 0.653$ based on Table B.5 of \cite{leconte11a}, for a highly irradiated, $1.5 R_\mathrm{J}$ planet aged 5 Gyr.
@@
 At quadrature, the project radius is $8\%$ larger than at phase zero (mid-transit).
-FIXME: say this doesn't matter.
+%FIXME: say this doesn't matter.
+%In addition to temperature, the planet's visible surface area $[R(t)]^2$ is also expected to vary with orbital phase due to tidal distortion \citep{gillon14}.
+In the observed light curve, changes in planet radius are degenerate with changes in temperature.
 
-FIXME: say what the dilution factor is.
+%We explored adding an additional sine term to model the thermal phase variation, but the additional degrees of freedom are not justified according to the Bayesian Information Criterion (BIC).
+
 %Our light curves are not precise enough to detect the ellipsoidal variability, but we include a model prediction $E(t)$ to avoid introducing any bias in the thermal phase variation.
@@
 \subsection{Comparison of Thermal Phase Variation Models}
+%These models each have different strengths: the kinematic model incorporates the most prior knowledge of physics, and even though it makes several simplifying assumptions (e.g, that the wind speed and direction are constant), it closely reproduces GCM simulations over a wide parameter space \citep{zhang16}.
+The spherical harmonics map is the most flexible and makes the fewest assumptions about the true climate.
+The two-temperature model is the simplest and easiest to compare to one-dimensional models of the dayside, which assume a uniform temperature/pressure profile.
+In all cases, we assumed that the planet is tidally locked, such that each orbital revolution corresponds to one complete rotation on its spin axis.
+%In addition to these maps, we also fit the phase variation with a sinusoid, which has been used for many past analyses of exoplanet phase curves (FIXME).
 All four of the thermal phase variation models we consider (two-temperature, kinematic, spherical harmonics, and sinusoid) provide good fits to the observed phase curves.

### 2017-10-26 Figures/dayside_espec.py

@@ -13,7 +13,7 @@ import seaborn as sns
 from astropy.convolution import Gaussian1DKernel, convolve
 g = Gaussian1DKernel(stddev=20)
 
-sns.set_context("paper", font_scale=1.0)
+sns.set_context("paper", font_scale=1.2)
 sns.set_style("white")
 sns.set_style("ticks", {"xtick.direction":"in", "ytick.direction":"in"})
 
@@ -32,10 +32,6 @@ def best_fit_bb(w, y, e, rprs):
 	Tbest = 0.	
 	Tstar = 6110.
 	w = np.array(w)
-
-	#w, y, e = w[0:10], y[0:10], e[0:10]
-	#w, y, e = w[11], y[11], e[11]
-	#print "just fitting WFC3 data"
 
 	#get stellar spectrum
 	star = np.genfromtxt("wasp103_sed_fluxes.out")
@@ -82,15 +78,9 @@ for i, f in enumerate(files):
 	nvisit = 4
 	T_s, xi, T_n, delta_T, per, t0, eclipse =  par[d.par_order['T_s']*nvisit], par[d.par_order['xi']*nvisit], par[d.par_order['T_n']*nvisit], \
 		par[d.par_order['delta_T']*nvisit], par[d.par_order['per']*nvisit], par[d.par_order['t0']*nvisit], False
-	bestfit = np.array(spiderman_lc.lc(d.time, 0.115, T_s, d.l1, d.l2, xi, T_n, delta_T, d.dilution, eclipse))
+	bestfit = np.array(spiderman_lc.lc(d.time, 0.1127, T_s, d.l1, d.l2, xi, T_n, delta_T, d.dilution, eclipse))
 	bestfit = bestfit[ind]
 
-	#print d.wavelength, T_n, delta_T
-
-	#t_eclipse = np.linspace(0.45, 0.55, 100)*per + t0
-	#bestfit_eclipse = np.array(spiderman_lc.lc(t_eclipse, 0.115, T_s, d.l1, d.l2, xi, T_n, delta_T, eclipse))
-	#LK note: this only makes a difference of 3 ppm
-	
 	#calculates uncertainty for in-eclipse points
 	ind1 = (phase>=0.46)&(phase<=0.55)
 	sig1 = np.sqrt(np.sum(err[ind1]**2)/sum(ind1)**2)
[…]

### 2017-10-26 ms.tex
notes

@@
 We calculated $A(t)$ using the analytic formula from \cite{leconte11b}, equation B.9, which computes the projected area of a triaxial ellipsoid.
-We assume a Love number $\kappa_n = 0.653$ based on Table B.5 of \cite{leconte11a}, for a highly irradiated, $1.5 R_\mathrm{J}$ planet aged 5 Gyr.
+We estimated the ellipsoid properties using Table B.3 of \cite{leconte11a}, assuming the planet radius is 1.5 $R_\mathrm{Jup}$ and age is 5 Gyr.
 The predicted ellipsoidal variability is shown in Figure\,\ref{fig:ellipsoidal}.
-At quadrature, the project radius is $8\%$ larger than at phase zero (mid-transit).
+At quadrature, the projected radius is $8\%$ larger than at phase zero (mid-transit).
 %FIXME: say this doesn't matter.

### 2017-10-27 Figures/spectra_table.py
big ol' table

@@ -3,50 +3,6 @@ import numpy as np
 import matplotlib.pyplot as plt
 import os, glob
 from lc_fit import Model, LightCurveData
-#import read_spectra_from_Vivien as rs
-import matplotlib.gridspec as gridspec
-from pylab import *
-from matplotlib import rc, ticker
-import seaborn as sns
-
-sns.set_context("notebook", font_scale = 1.3)
-sns.set_style("white")
-sns.set_style("ticks", {"xtick.direction":"in", "ytick.direction":"in"})
-
-rc('font',**{'family':'sans-serif','sans-serif':['Arial']})
-
-def blackbody(l,T): 
-	h = 6.62607e-34   #J/s
-        c = 2.997925e8       #m/s
-        k = 1.38065e-23     #J/K
-        return 2*h*c**2/(l**5*(np.exp(h*c/(l*k*T))-1))                 #[W/sr/m^3]
-
-def best_fit_bb(w, y, e, rprs):
-	Ts = np.linspace(300, 3600, 300)
-	chibest = 10000.
-	Tbest = 0.	
-	Tstar = 6110.
-	w = np.array(w)
-
-	#w, y, e = w[0:10], y[0:10], e[0:10]
-	#w, y, e = w[10], y[10], e[10]
-#	w, y, e = w[11], y[11], e[11]
-
-	#get stellar spectrum
-	star = np.genfromtxt("wasp103_sed_fluxes.out")
-	star_bb = np.interp(w, star[:,0], star[:,1])*1.e24/(w*np.pi*4.)
-
-	for T in Ts:
-		model = blackbody(w*1.0e-6, T)/star_bb*rprs**2
-		chi2 = np.sum((y - model)**2/e**2)
-		if chi2 < chibest: 
-			chibest, Tbest = chi2, T
-	waves_hires = np.linspace(1.0, 5.0, 100)
-	star_bb_hires = np.interp(waves_hires, star[:,0], star[:,1])*1.e24/(waves_hires*np.pi*4.)
-	outfile = open("temperatures.txt", "a")
-	print>>outfile,  Tbest
-	outfile.close()
-	return waves_hires, blackbody(waves_hires*1.0e-6, Tbest)/star_bb_hires*rprs**2
 
 
 path  = "WFC3_best_fits/spec_fits/"		#zhang model
[…]

### 2017-10-27 Figures/fit_table.py
reran with phoenix models

@@ -21,7 +21,7 @@ for i, model in enumerate(models):
 	p = pickle.load(open(path+"bestfit_"+model+".pic", "rb")) 
 
 	d, m, par = p[0], p[1], p[2]            #stores data,  model, and best fit parameters into d, m, & par
-	wfc3_chi2.append(m.chi2)
+	wfc3_chi2.append(m.chi2red)
 	wfc3_bic.append(m.chi2 + d.nfree_param*np.log(d.npoints))
 	wfc3_aic.append(m.chi2 + 2.*d.nfree_param)
 #	print m.chi2red, bic, aic
@@ -32,11 +32,11 @@ wfc3_bic = np.array(wfc3_bic)
 
 #Temperatures:
 #HST:
-#model, Tmin, Tmax =  zhang 1955.79103244 3910.35135096
-#model, Tmin, Tmax =  hotspot_t 0.0 2837.28405252
-#model, Tmin, Tmax =  spherical 1211.72127487 3190.7163225
-wfc3_tmin = np.array([1955, 0, 1212])
-wfc3_tmax = np.array([3910, 2837, 3190])
+#model, Tmin, Tmax =  zhang 1979.6612603 3958.07678595
+#model, Tmin, Tmax =  hotspot_t 0.0 2887.11857794
+#model, Tmin, Tmax =  spherical 1213.50410565 3251.37484203
+wfc3_tmin = np.array([1980, 0, 1214])
+wfc3_tmax = np.array([3958, 2887, 3251])
 
 #Spitzer Ch 2
 #model, Tmin, Tmax =  zhang 1719.0 4257.78308959
@@ -46,11 +46,11 @@ ch2_tmin = np.array([1719, 1380, 930])
 ch2_tmax = np.array([4257, 3305, 3775])
 
 #Spitzer Ch 1
-#model, Tmin, Tmax =  zhang 1952.0 3672.60664016
-#model, Tmin, Tmax =  hotspot_t 1427.0 3039.0
-#model, Tmin, Tmax =  spherical 1277.04246551 3441.94916745
-ch1_tmin = np.array([1952, 1427, 1277])
-ch1_tmax = np.array([3672, 3039, 3442])
+#model, Tmin, Tmax =  zhang 1955.0 3675.62794318
+#model, Tmin, Tmax =  hotspot_t 1429.0 3041.0
+#model, Tmin, Tmax =  spherical 1280.4447703 3444.26296074
[…]

### 2017-10-27 Figures/lc_fit.py

@@ -8,7 +8,7 @@ import glob
 import os
 from astropy.io import ascii
 import getopt
-#import seaborn as sns
+import seaborn as sns
 import matplotlib
 import matplotlib.cm as cm
 from datetime import datetime
@@ -19,9 +19,9 @@ import batman
 import pickle
 import spiderman
 
-#sns.set_context("talk")
-#sns.set_style("white")
-#sns.set_style("ticks", {"xtick.direction":"in", "ytick.direction":"in"})
+sns.set_context("talk")
+sns.set_style("white")
+sns.set_style("ticks", {"xtick.direction":"in", "ytick.direction":"in"})
 matplotlib.rcParams.update({'lines.markeredgewidth':0.3})
 matplotlib.rcParams.update({'axes.formatter.useoffset':False})
 
@@ -134,8 +134,8 @@ class LightCurveData:
 				else: nfree_param += nvisit
 		nfree_param -= 2	#subtracts 2 because we're fixing v2 at 0 for zhao data
 
-		#zhao_data = pickle.load(open("zhao_data_pickles_10bins/zhao_data_"+"{0:0.3f}".format(wavelength)+".p", "rb"))
-		zhao_data = pickle.load(open("zhao_data_pickles_white/zhao_data_white.p", "rb"))
+		if flags['fit-white']: zhao_data = pickle.load(open("zhao_data_pickles_white/zhao_data_white.p", "rb"))
+		else: zhao_data = pickle.load(open("zhao_data_pickles_6bins/zhao_data_"+"{0:0.3f}".format(wavelength)+".p", "rb"))
 		print "choosing zhao pickles by hand; make sure you specified the right file"
 		print "specifying prior on T_n and delta_T_cloud by hand - indices could be wrong later!"
 
@@ -162,7 +162,9 @@ class LightCurveData:
 		else:
 			self.l1 = (self.wavelength - 0.0225)*1.0e-6	#specific to 12 bins!
 			self.l2 = (self.wavelength + 0.0225)*1.0e-6
+		self.stellar_grid = spiderman.stellar_grid.gen_grid(self.l1, self.l2)
 		print "specifying l1 and l2 by hand - FIXME"
[…]

### 2017-10-27 ms.tex
big ol' table
reran with phoenix models
spitzer systematics

@@
 We calculated the transit model $T(t)$ with the \texttt{batman} package \citep{kreidberg15a}.
-Many of the physical parameters are tightly constrained by \cite{southworth15}, so we fixed the orbital period, time of inferior conjunction, orbital inclination, and ratio of semi-major axis to stellar radius to the previously published values ($P = 0.925545613$ day, $t_0 = 2456836.2964455 \mathrm{BJD_{TDB}}$, $i = 87.3^\circ$, and $a/R_s = 2.999$).
+Many of the physical parameters are tightly constrained by \cite{southworth15}, so we fixed the orbital period, time of inferior conjunction, orbital inclination, and ratio of semi-major axis to stellar radius to the previously published values ($P = 0.925545613$ day, $t_0 = 2456836.2964455\,\mathrm{BJD_{TDB}}$, $i = 87.3^\circ$, and $a/R_s = 2.999$).
 As a test, we fit for these parameters with the Spitzer Channel 2 light curve, which has the best phase coverage and least systematic noise of the three data sets.
@@
 This package allows users to input a climate map (temperature or brightness as a function of latitude and longitude), and generate the corresponding flux ratio for an observation at time $t$.
-In our fit, we assumed the star is a FIXME PHOENIX model.
+In our fit, we calculated the stellar flux with a PHOENIX model \citep{husser13} interpolated to an effective temperature of $6110\,\mathrm{K}$ \citep{gillon14}.
 We tested three different maps: a two-temperature map, with a uniform dayside temperature $T_d$ and a uniform nightside temperature $T_n$; a map generated with spherical harmonics; and the physically-motivated kinematic model from \cite{zhang16}, which has just three free parameters (the nightside temperature $T_n$, the change in temperature from day-to-night side $\Delta_T$, and the ratio of radiative to advective timescales $\xi$).
@@
 \begin{equation}
-	c(\lambda, t) = (1 + \alpha(\lambda))A(t)
+	c(\lambda, t) = [1 + \alpha(\lambda)]A(t)
 \end{equation}
@@
 \includegraphics[width = 0.5\textwidth]{Figures/ellipsoidal.pdf}
-\caption{Projected area of the planet as a function of orbital phase, normalized to unity at phase zero. The area variation was predicted analytically using the model from \citep{leconte11b}.}
+\caption{Projected area of the planet as a function of orbital phase, normalized to unity at phase zero. The area variation was predicted analytically using the model from \cite{leconte11b}.}
 \label{fig:ellipsoidal}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width = 0.5\textwidth]{Figures/systematics.pdf}
+\caption{Raw light curves for WASP-103b observed with \HST/WFC3 (top panel) and \Spitzer/IRAC (bottom two panels).
+The data points are indicated with black dots.
+The \HST\ data are unbinned, and the Spitzer data are binned in time segments of FIXME minutes with error bars indicating the bin standard deviation.
+The colored lines show the best fit models, which include the astrophysical signal and instrument systematics.
+The gray lines indicate the contribution from the instrument systematics alone (which would be observed for a source with constant brightness and no planet).
+For visual clarity, we corrected the \HST\ data for the upstream-downstream effect, separated the four visits by adding a flux offset, and zoomed in on the phase variation, so the transits are not displayed in the panel.}
+\label{fig:systematics}
 \end{figure}
@@
 The detector's pixels do not have uniform sensitivity, so slight changes in telescope pointing cause the recorded flux to vary.
+In Figure\,\ref{fig:systematics}, we show the raw light curves before systematic noise was removed.
+The systematics have comparable amplitude to the thermal phase variation signal, so they must be carefully corrected to recover the underlying planet-to-star flux.
 
@@
 \subsubsection{\Spitzer\ Systematics}
-We fit the \Spitzer\ systematics with the BLISS mapping technique \citep{stevenson12}.
-This technique creates a map of the intrapixel sensitivity while simultaneously fitting for other systematics and the physical parameters of the system.
-In addition to the intrapixel sensitivity map, we fit the data for a linear trend in time.
+We fit the \Spitzer\ systematics with the POET pipeline using the BLISS mapping technique \citep{stevenson12}.
+This approach creates a map of the intrapixel sensitivity while simultaneously fitting for other systematics and the physical parameters of the system.
+The sensitivity map is determined by bilinear interpolation over a grid of knots centered on the stellar flux.
+Each knot's sensitivity is calculated from the residuals to the light curve fit: the higher the flux values for data points near a given knot, the higher the detector sensitivity is at that position.
+To avoid overfitting, we chose the grid scale such that bilinear interpolation performed better than nearest neighbor interpolation.
+For the $3.6\,\mu$m data, the grid scale was 0.008 pixel in both $x$ and $y$.
+For $4.5\,\mu$m, the scale was 0.022 pixel.
 
-\begin{figure}
-\includegraphics[width = 0.5\textwidth]{Figures/systematics.pdf}
-\caption{Raw light curves for WASP-103b observed with \HST/WFC3 (top panel) and \Spitzer/IRAC (bottom two panels).
-The data points are indicated with black dots.
-The \HST\ data are unbinned, and the Spitzer data are binned in time segments of FIXME minutes with error bars indicating the bin standard deviation.
-The colored lines show the best fit models, which include the astrophysical signal and instrument systematics.
-The gray lines indicate the contribution from the instrument systematics alone (which would be observed for a source with constant brightness and no planet).
-For visual clarity, we corrected the \HST\ data for the upstream-downstream effect, separated the four visits by adding a flux offset, and zoomed in on the phase variation, so the transits are not displayed in the panel.}
-\label{fig:systematics}
-\end{figure}
+In addition to the intrapixel sensitivity variation, we fit the data for a linear trend in time.
+We tested a quadratic trend but did not find significant evidence for the additional model complexity based on the Bayesisan information criterion (BIC).
+
+\begin{figure*}
+\includegraphics[width = 1.0\textwidth]{Figures/phase_curves.pdf}
+\caption{WASP-103b phase curve observations from \HST/WFC3 (top) and \Spitzer/IRAC (middle and bottom).
+For clarity, the data are phase-folded on the planet's orbital period and binned in 30 uniformly spaced bins between 0 and 1.
+The left column shows the phase curves with systematic noise removed (black points) compared to the best fit model (black line).
+The shading denotes the  1\,$\sigma$ confidence interval on the best fit.
+We include the transits in the fit, but they are not displayed in this figure.
+The right-hand column shows the binned residuals for the best-fit light curve.}
+\label{fig:phasecurves}
+\end{figure*}
 
 \section{Results}
-We achieved good quality fits!
+The fitted light curves are shown in Figure\,\ref{fig:phasecurves}.
+This figure shows results from the kinematic model for the thermal phase variation and has instrument systematics removed.
+The peak planet-to-star flux ranges from 1.5 parts-per-thousand (ppt) in the WFC3 bandpass to 5 ppt in \Spitzer Channel 2.
+The planet flux changes significantly with orbital phase in all three of the data sets, suggesting a strong gradient from dayside to nightside temperature.
+The peak brightness occurs near phase 0.5.
+
+\subsection{Goodness of Fit}
+We performed a number of tests of the quality of the light curve fits. First, we calculated the root-mean-square (rms) of the fit residuals and compared it to the expectations for photon noise alone.
+
+Second, we tested whether the rms decreases white noise bin size.  Figure\,\ref{fig:rms} shows the binned residuals compared to expectations for white noise (uncorrelated in time).
+
+Third, we calculated $\chi^2$, AIC, BIC.
+
+\begin{deluxetable*}{llllllllllll}
+\tablecolumns{12}
+\tablewidth{0pt}:
+\tablecaption{Phase-Resolved Emission Spectra \label{table:spectra}}
+\tablehead{
+\colhead{$\lambda$} & \colhead{Dilution} & \colhead{0.1} & \colhead{0.2} & \colhead{0.3} & \colhead{0.4} & \colhead{0.6} & \colhead{0.7} & \colhead{0.8} & \colhead{0.9} & \colhead{X} & \colhead{Y}}
+\startdata
+1.175 & 0.10 & $ 179 \pm 79 $ & $ 411 \pm 77 $ & $ 647 \pm 80 $ & $ 1143 \pm 65 $ & $ -15 \pm 66 $ & $ 142 \pm 67 $ & $ 1063 \pm 64 $ & $ 710 \pm 73 $ & $ 412 \pm 78 $ & $ 177 \pm 79 $ \\ 
+1.225 & 0.11 & $ 188 \pm 76 $ & $ 398 \pm 74 $ & $ 928 \pm 77 $ & $ 1276 \pm 62 $ & $ 120 \pm 64 $ & $ 42 \pm 65 $ & $ 1216 \pm 62 $ & $ 888 \pm 71 $ & $ 539 \pm 75 $ & $ 280 \pm 76 $ \\ 
+1.275 & 0.11 & $ 166 \pm 76 $ & $ 379 \pm 74 $ & $ 869 \pm 77 $ & $ 1323 \pm 62 $ & $ 139 \pm 64 $ & $ -8 \pm 65 $ & $ 1282 \pm 62 $ & $ 814 \pm 71 $ & $ 515 \pm 75 $ & $ 247 \pm 76 $ \\ 
+1.325 & 0.11 & $ 266 \pm 75 $ & $ 432 \pm 73 $ & $ 904 \pm 76 $ & $ 1357 \pm 62 $ & $ 4 \pm 63 $ & $ 144 \pm 64 $ & $ 1267 \pm 61 $ & $ 925 \pm 70 $ & $ 552 \pm 74 $ & $ 333 \pm 75 $ \\ 
+1.375 & 0.12 & $ 189 \pm 81 $ & $ 514 \pm 78 $ & $ 928 \pm 82 $ & $ 1376 \pm 66 $ & $ 131 \pm 67 $ & $ 52 \pm 68 $ & $ 1411 \pm 65 $ & $ 954 \pm 75 $ & $ 461 \pm 79 $ & $ 292 \pm 81 $ \\ 
+1.425 & 0.13 & $ 238 \pm 79 $ & $ 532 \pm 76 $ & $ 1198 \pm 79 $ & $ 1431 \pm 64 $ & $ 40 \pm 66 $ & $ 185 \pm 66 $ & $ 1511 \pm 64 $ & $ 1063 \pm 73 $ & $ 605 \pm 77 $ & $ 338 \pm 79 $ \\ 
+1.475 & 0.14 & $ 191 \pm 81 $ & $ 527 \pm 79 $ & $ 1068 \pm 82 $ & $ 1460 \pm 66 $ & $ 90 \pm 68 $ & $ 105 \pm 69 $ & $ 1392 \pm 66 $ & $ 1090 \pm 75 $ & $ 580 \pm 80 $ & $ 268 \pm 81 $ \\ 
+1.525 & 0.14 & $ 143 \pm 84 $ & $ 478 \pm 81 $ & $ 1048 \pm 85 $ & $ 1429 \pm 69 $ & $ 103 \pm 70 $ & $ 88 \pm 71 $ & $ 1367 \pm 68 $ & $ 943 \pm 77 $ & $ 607 \pm 82 $ & $ 291 \pm 84 $ \\ 
+1.575 & 0.15 & $ 367 \pm 88 $ & $ 761 \pm 85 $ & $ 1088 \pm 89 $ & $ 1581 \pm 72 $ & $ 96 \pm 73 $ & $ 125 \pm 74 $ & $ 1503 \pm 71 $ & $ 1107 \pm 81 $ & $ 754 \pm 86 $ & $ 422 \pm 88 $ \\ 
+1.625 & 0.16 & $ 359 \pm 93 $ & $ 565 \pm 90 $ & $ 1169 \pm 94 $ & $ 1590 \pm 76 $ & $ 45 \pm 78 $ & $ 181 \pm 79 $ & $ 1593 \pm 75 $ & $ 1142 \pm 86 $ & $ 542 \pm 91 $ & $ 351 \pm 93 $ \\ 
+3.6 & 0.17 & $ 1148 \pm 333 $ & $ 3633 \pm 330 $ & $ 4487 \pm 320 $ & $ 4107 \pm 314 $ & $ 661 \pm 324 $ & $ 373 \pm 324 $ & $ 3495 \pm 315 $ & $ 3720 \pm 330 $ & $ 2102 \pm 331 $ & $ 1431 \pm 334 $ \\
+4.5 & 0.16 & $ 1586 \pm 220 $ & $ 3468 \pm 214 $ & $ 4188 \pm 190 $ & $ 5334 \pm 179 $ & $ 466 \pm 200 $ & $ 757 \pm 200 $ & $ 4904 \pm 183 $ & $ 3626 \pm 214 $ & $ 2575 \pm 217 $ & $ 1057 \pm 221 $ \\
+\enddata
+\vspace{-0.8cm}
+\tablecomments{comments}
+\end{deluxetable*}
 
@@
 \tablehead{
-\colhead{Data Set} & \colhead{Model} & \colhead{$T_\mathrm{min}$} & \colhead{$T_\mathrm{max}$} & \colhead{$\chi^2$} & \colhead{$\Delta$ AIC} & \colhead{$\Delta$ BIC}}
+\colhead{Data} & \colhead{Model} & \colhead{$T_\mathrm{min}$} & \colhead{$T_\mathrm{max}$} & \colhead{$\chi^2$} & \colhead{$\Delta_\mathrm{AIC}$} & \colhead{$\Delta_\mathrm{BIC}$}}
 \startdata
-WFC3 & Sph. Harmonics & 1212 & 3190 & 949.6 & 0.0 & 0.0 \\
-\, & Kinematic & 1955 & 3910 & 961.6 & 12.0 & 12.0 \\
-\, & Two Temp. & 0 & 2837 & 999.4 & 47.7 & 43.3 \\
-Ch 1 & Sph. Harmonics & 1277 & 3442 & 0.9 & 0.0 & 0.0 \\
-\, & Kinematic & 1952 & 3672 & 0.9 & 34.3 & 34.3 \\
-\, & Two Temp. & 1427 & 3039 & 0.9 & 10.7 & 17.6 \\
-Ch 2 & Sph. Harmonics & 930 & 3775 & 1.1 & 0.0 & 3.1 \\
-\, & Kinematic & 1719 & 4257 & 1.1 & 14.35 & 17.41 \\
-\, & Two Temp. & 1380 & 3305 & 1.1 & 23.9 & 0.0 \\
+WFC3 & Sph. Harmonics & 1214 & 3251 & 1.5 & 0.0 & 0.0 \\
+\, & Kinematic & 1980 & 3958 & 1.6 & 11.8 & 11.8 \\
+\, & Two Temp. & 0 & 2887 & 1.6 & 47.7 & 43.2 \\
+Ch 1 & Sph. Harmonics & 1280 & 3444 & 0.9 & 0.0 & 0.0 \\
+\, & Kinematic & 1955 & 3675 & 0.9 & 34.3 & 34.3 \\
+\, & Two Temp. & 1429 & 3041 & 0.9 & 10.7 & 17.6 \\
+Ch 2 & Sph. Harmonics & 902 & 3786 & 1.1 & 0.0 & 3.1 \\
+\, & Kinematic & 1703 & 4276 & 1.1 & 14.35 & 17.41 \\
+\, & Two Temp. & 1361 & 3311 & 1.1 & 23.9 & 0.0 \\
 \enddata
@@
 
-\begin{figure*}
-\includegraphics[width = 1.0\textwidth]{Figures/phase_curves.pdf}
-\caption{WASP-103b phase curve observations from \HST/WFC3 (top) and \Spitzer/IRAC (middle and bottom).
-For clarity, the data are phase-folded on the planet's orbital period and binned in 30 uniformly spaced bins between 0 and 1.
-The left column shows the phase curves with systematic noise removed (black points) compared to the best fit model (black line).
-The shading denotes the  1\,$\sigma$ confidence interval on the best fit.
-We include the transits in the fit, but they are not displayed in this figure.
-The right-hand column shows the binned residuals for the best-fit light curve.}
-\label{fig:phasecurves}
-\end{figure*}
-
 \begin{figure}
@@
 \end{figure*}
-
-\subsection{Phase-Resolved Spectra}
-We used the best-fit phase curves (with systematics removed) to generate phase-resolved emission spectra.
-We binned each phase curve in FIXME evenly spaced intervals between phase FIXME and FIXME.
-In each phase bin, we estimated the planet-to-star flux by taking the mean value of the data points in the bin.
-To estimate the uncertainty, we took the standard deviation of the points in the bin and added it in quadrature to the standard deviation of the data points during secondary eclipse (phase FIXME to FIXME).
-This procedure accounts for the uncertainty in the baseline stellar flux (which we measure during secondary eclipse).
-
-To estimate the dayside planet-to-star flux, we did FIXME.
-
-We note that the phase-resolved spectra do not significantly change based on which model we assume for the
 
@@
 \subsection{Hotspot Offset}
+
+\subsection{Phase-Resolved Spectra}
+We used the best-fit phase curves (with systematics removed) to generate phase-resolved emission spectra.
+We binned each phase curve in FIXME evenly spaced intervals between phase FIXME and FIXME.
+In each phase bin, we estimated the planet-to-star flux by taking the mean value of the data points in the bin.
+To estimate the uncertainty, we took the standard deviation of the points in the bin and added it in quadrature to the standard deviation of the data points during secondary eclipse (phase FIXME to FIXME).
+This procedure accounts for the uncertainty in the baseline stellar flux (which we measure during secondary eclipse).
+
+To estimate the dayside planet-to-star flux, we did FIXME.
+
+We note that the phase-resolved spectra do not significantly change based on which model we assume for the
 

### 2017-10-27 Figures/fit_table.py

@@ -39,11 +39,11 @@ wfc3_tmin = np.array([1980, 0, 1214])
 wfc3_tmax = np.array([3958, 2887, 3251])
 
 #Spitzer Ch 2
-#model, Tmin, Tmax =  zhang 1719.0 4257.78308959
-#model, Tmin, Tmax =  hotspot_t 1380.0 3305.0e
-#model, Tmin, Tmax =  spherical 930.545006798 3775.38559767
-ch2_tmin = np.array([1719, 1380, 930])
-ch2_tmax = np.array([4257, 3305, 3775])
+#model, Tmin, Tmax =  zhang 1703.0 4276.80767467
+#model, Tmin, Tmax =  hotspot_t 1361.0 3311.0
+#model, Tmin, Tmax =  spherical 902.401726015 3786.1376002
+ch2_tmin = np.array([1703, 1361, 902])
+ch2_tmax = np.array([4276, 3311, 3786])
 
 #Spitzer Ch 1
 #model, Tmin, Tmax =  zhang 1955.0 3675.62794318

### 2017-10-28 ms.tex
description of spectra

@@
 
-We calculated the planet-to-star flux $F_p/F_s$ with the \texttt{SPIDERMAN} package \citep{louden17}.
+We calculated the planet-to-star flux $F_p/F_s$ in two different ways.
+First, we fit a sinusoid with a period equal to the planet's orbital period.
+The free parameters were the sine curve amplitude and phase offset.
+For the second approach, we used the \texttt{SPIDERMAN} package \citep{louden17} to model $F_p/F_s$.
 This package allows users to input a climate map (temperature or brightness as a function of latitude and longitude), and generate the corresponding flux ratio for an observation at time $t$.
 In our fit, we calculated the stellar flux with a PHOENIX model \citep{husser13} interpolated to an effective temperature of $6110\,\mathrm{K}$ \citep{gillon14}.
-We tested three different maps: a two-temperature map, with a uniform dayside temperature $T_d$ and a uniform nightside temperature $T_n$; a map generated with spherical harmonics; and the physically-motivated kinematic model from \cite{zhang16}, which has just three free parameters (the nightside temperature $T_n$, the change in temperature from day-to-night side $\Delta_T$, and the ratio of radiative to advective timescales $\xi$).
+For the planet flux, we tested three different maps: a two-temperature map, with a uniform dayside temperature $T_d$ and a uniform nightside temperature $T_n$; a map generated with spherical harmonics; and the physically-motivated kinematic model from \cite{zhang16}, which has just three free parameters (the nightside temperature $T_n$, the change in temperature from day-to-night side $\Delta_T$, and the ratio of radiative to advective timescales $\xi$).
 
-%We assume the stellar flux $F_s(\lambda)$ is a $6110\,\mathrm{K}$ blackbody \citep{gillon14}.  (FIXME - use a PHOENIX model instead). 
 We scaled the planet-to-star flux by a correction factor $c$ to account for dilution from the companion star and ellipsoidal variability due to the planet's tidal distortion.
@@
 where $\alpha(\lambda)$ is the additional fractional flux from the companion star and $A(t)$ is the sky-projected area of the planet.
-We estimated $\alpha(\lambda)$ based on the best fit spectral energy distribution from \cite{cartier16}.
+We estimated $\alpha(\lambda)$ based on the best fit spectral energy distribution from \cite{cartier17}.
 The companion star contributes FIXME percent of the flux at FIXME $\mu$m.
@@
 \subsubsection{\Spitzer\ Systematics}
-We fit the \Spitzer\ systematics with the POET pipeline using the BLISS mapping technique \citep{stevenson12}.
+We fit the \Spitzer\ systematics with the POET pipeline, which uses the BLISS mapping technique \citep{stevenson12}.
 This approach creates a map of the intrapixel sensitivity while simultaneously fitting for other systematics and the physical parameters of the system.
@@
 \subsection{Goodness of Fit}
-We performed a number of tests of the quality of the light curve fits. First, we calculated the root-mean-square (rms) of the fit residuals and compared it to the expectations for photon noise alone.
+We performed several tests of the quality of the light curve fits.
+First we predicted the level of scatter in the light curves based on photon and read noise, then compared this value to the root-mean-square (rms) of the fit residuals.
+The fit rms was within FIXME percent of the expected noise level in the WFC3 spectroscopic light curves and \Spitzer\ Channel 2 (expected rms of 450 and FIXME ppm).
+The
 
-Second, we tested whether the rms decreases white noise bin size.  Figure\,\ref{fig:rms} shows the binned residuals compared to expectations for white noise (uncorrelated in time).
+Second, we tested whether the fit rms decreases as expected when the light curve in binned in time.
+If the noise is ``white" (uncorrelated in time), the residuals are expected to decrease by a factor of $\sqrt{N}$, where $N$ is the number of points in a bin.
+Figure\,\ref{fig:rms} shows the binned residuals compared to expectations for white noise.
+The \HST/WFC3 and \Spitzer\ Channel 2 light curves agree well with expectations, whereas \Spitzer\ Channel 1 shows higher noise than expected as bin size increases.
+This test confirms the existence of time-correlated noise in the Channel 1 light curve that can be seen by eye in the residuals in Figure\,\ref{fig:phasecurves}.
+Both \Spitzer\ channels use the same detector, but Channel 1 data are more susceptible to time-correlated noise because the the point spread function is narrower at shorter wavelengths, making intrapixel sensitivity variations more pronounced.
 
-Third, we calculated $\chi^2$, AIC, BIC.
+Third, we calculated several goodness of fit statistics. $\chi^2$, AIC, BIC.
+
+\begin{figure}
+\includegraphics[width = 0.5\textwidth]{Figures/rms.pdf}
+\caption{Root mean square (rms) variability in the light curves as a function of bin size (black lines) compared to the expected rms from photon noise (colored lines).
+The central wavelength of the light curve is indicated in the upper right corner of each panel.
+With the exception of the \Spitzer\ 3.6 $\mu$m channel, the rms for the light curves bins down in agreement with predictions from the photon noise.}
+\label{fig:rms}
+\end{figure}
+
+\begin{deluxetable}{lllllll}
+\tablecolumns{7}
+\tablewidth{0pt}:
+\tablecaption{Model Comparison \label{table:models}}
+\tablehead{
+\colhead{Data} & \colhead{Model} & \colhead{$T_\mathrm{min}$} & \colhead{$T_\mathrm{max}$} & \colhead{$\chi^2$} & \colhead{$\Delta_\mathrm{AIC}$} & \colhead{$\Delta_\mathrm{BIC}$}}
+\startdata
+WFC3 & Harmonics & 1214 & 3251 & 1.5 & 0.0 & 0.0 \\
+\, & Kinematic & 1980 & 3958 & 1.6 & 11.8 & 11.8 \\
+\, & Two Temp. & 0 & 2887 & 1.6 & 47.7 & 43.2 \\
+Ch 1 & Harmonics & 1280 & 3444 & 0.9 & 0.0 & 0.0 \\
+\, & Kinematic & 1955 & 3675 & 0.9 & 34.3 & 34.3 \\
+\, & Two Temp. & 1429 & 3041 & 0.9 & 10.7 & 17.6 \\
+Ch 2 & Harmonics & 902 & 3786 & 1.1 & 0.0 & 3.1 \\
+\, & Kinematic & 1703 & 4276 & 1.1 & 14.35 & 17.41 \\
+\, & Two Temp. & 1361 & 3311 & 1.1 & 23.9 & 0.0 \\
+\enddata
+\vspace{-0.8cm}
+\tablecomments{comments}
+\end{deluxetable}
+
+\subsection{Phase-Resolved Spectra}
+We used the best-fit phase curves (with systematics removed) to generate phase-resolved emission spectra.
+Since our model does not fit eclipse depth as a free parameter, we estimated the dayside emission spectrum as follows.
+We used \texttt{SPIDERMAN}'s eclipse\_depth method to calculate the average planet-to-star flux for the best-fit model during secondary eclipse.
+To estimate uncertainties, we took the standard deviation of the residuals of the in-eclipse data points, then added this value in quadrature to the standard deviation of the residuals of the out-of-eclipse data.
+This summed error accounts for the uncertainty in the baseline flux.
+
+For the other orbital phases, we binned the light curve (with systematics removed) in eight intervals of about 0.1 in orbital phase, with endpoints at phases $0.06, 0.15, 0.25, 0.35, 0.44$ and $0.56, 0.65, 0.75, 0.85, 0.94$.
+These endpoints were chosen to ensure that there is no contribution from in-transit or in-eclipse data.
+In each phase bin, we estimated the planet-to-star flux from the mean value of the data points in the bin.
+To estimate the uncertainty, we took the standard deviation of the points in the bin and added it in quadrature to the standard deviation of the data points during secondary eclipse (phase $0.46-0.54$).
+This sum accounts for the uncertainty in the stellar flux (measured during secondary eclipse).
+The phase-resolved emission spectra are shown in Figure\,\ref{fig:spectra} and listed in Table\,\ref{table:spectra}.
+
+To test that the phase-resolved spectra are robust to different approaches for fitting the data, we compared the spectra for all four of the thermal phase variation models (sinusoid, kinematic, spherical harmonics, and two temperature).
+We found that the choice of model does not significantly change the results.
+The emission spectra are insensitive to the models because they are estimated directly from the data (after systematics have been removed).
+Since systematic noise is not strongly correlated with the thermal phase variation, the systematics-divided data are nearly identical for all the models.
+This point is illustrated in Figure\,\ref{fig:model_comparison} for the broadband WFC3 light curve.
+In most phase bins, the planet-to-star flux agrees well within one sigma for all the models.
+
+\begin{figure*}
+\includegraphics[width = 1.0\textwidth]{Figures/emission_spectra.pdf}
+\caption{Phase-resolved emission spectra.}
+\label{fig:spectra}
+\end{figure*}
+
+\begin{figure*}
+\includegraphics[width = 1.0\textwidth]{Figures/hst_model_comparison.pdf}
+\caption{Left: fits to the broadband WFC3 phase curve. Right: best fit temperature maps.}
+\label{fig:model_comparison}
+\end{figure*}
 
@@
 
-\begin{deluxetable}{lllllll}
-\tablecolumns{7}
-\tablewidth{0pt}:
-\tablecaption{Model Comparison \label{table:models}}
-\tablehead{
-\colhead{Data} & \colhead{Model} & \colhead{$T_\mathrm{min}$} & \colhead{$T_\mathrm{max}$} & \colhead{$\chi^2$} & \colhead{$\Delta_\mathrm{AIC}$} & \colhead{$\Delta_\mathrm{BIC}$}}
-\startdata
-WFC3 & Sph. Harmonics & 1214 & 3251 & 1.5 & 0.0 & 0.0 \\
-\, & Kinematic & 1980 & 3958 & 1.6 & 11.8 & 11.8 \\
-\, & Two Temp. & 0 & 2887 & 1.6 & 47.7 & 43.2 \\
-Ch 1 & Sph. Harmonics & 1280 & 3444 & 0.9 & 0.0 & 0.0 \\
-\, & Kinematic & 1955 & 3675 & 0.9 & 34.3 & 34.3 \\
-\, & Two Temp. & 1429 & 3041 & 0.9 & 10.7 & 17.6 \\
-Ch 2 & Sph. Harmonics & 902 & 3786 & 1.1 & 0.0 & 3.1 \\
-\, & Kinematic & 1703 & 4276 & 1.1 & 14.35 & 17.41 \\
-\, & Two Temp. & 1361 & 3311 & 1.1 & 23.9 & 0.0 \\
-\enddata
-\vspace{-0.8cm}
-\tablecomments{comments}
-\end{deluxetable}
-
-\begin{figure}
-\includegraphics[width = 0.5\textwidth]{Figures/rms.pdf}
-\caption{Root mean square (rms) variability in the light curves as a function of bin size (black lines) compared to the expected rms from photon noise (colored lines).
-The central wavelength of the light curve is indicated in the upper right corner of each panel.
-With the exception of the \Spitzer\ 3.6 $\mu$m channel, the rms for the light curves bins down in agreement with predictions from the photon noise.}
-\label{fig:rms}
-\end{figure}
-
 \begin{figure}
@@
 
-\begin{figure*}
-\includegraphics[width = 1.0\textwidth]{Figures/emission_spectra.pdf}
-\caption{Phase-resolved emission spectra.}
-\label{fig:spectra}
-\end{figure*}
+\subsection{Comparison of Thermal Phase Variation Models}
+All four of the thermal phase variation models we consider (two-temperature, kinematic, spherical harmonics, and sinusoid) provide good fits to the observed phase curves.
+Table FIXME summarized the goodness of fit
 
-\subsection{Comparison of Thermal Phase Variation Models}
-%These models each have different strengths: the kinematic model incorporates the most prior knowledge of physics, and even though it makes several simplifying assumptions (e.g, that the wind speed and direction are constant), it closely reproduces GCM simulations over a wide parameter space \citep{zhang16}.
+These models each have different strengths: the kinematic model incorporates the most prior knowledge of physics, and even though it makes several simplifying assumptions (e.g, that the wind speed and direction are constant), it closely reproduces GCM simulations over a wide parameter space \citep{zhang16}.
 The spherical harmonics map is the most flexible and makes the fewest assumptions about the true climate.
@@
 %In addition to these maps, we also fit the phase variation with a sinusoid, which has been used for many past analyses of exoplanet phase curves (FIXME).
-All four of the thermal phase variation models we consider (two-temperature, kinematic, spherical harmonics, and sinusoid) provide good fits to the observed phase curves.
-Table FIXME summarized the goodness of fit
-
-\begin{figure*}
-\includegraphics[width = 1.0\textwidth]{Figures/hst_model_comparison.pdf}
-\caption{Left: fits to the broadband WFC3 phase curve. Right: best fit temperature maps.}
-\label{fig:model_comparison}
-\end{figure*}
 
 \subsection{Hotspot Offset}
-
-\subsection{Phase-Resolved Spectra}
-We used the best-fit phase curves (with systematics removed) to generate phase-resolved emission spectra.
-We binned each phase curve in FIXME evenly spaced intervals between phase FIXME and FIXME.
-In each phase bin, we estimated the planet-to-star flux by taking the mean value of the data points in the bin.
-To estimate the uncertainty, we took the standard deviation of the points in the bin and added it in quadrature to the standard deviation of the data points during secondary eclipse (phase FIXME to FIXME).
-This procedure accounts for the uncertainty in the baseline stellar flux (which we measure during secondary eclipse).
-
-To estimate the dayside planet-to-star flux, we did FIXME.
-
-We note that the phase-resolved spectra do not significantly change based on which model we assume for the
 

### 2017-10-28 ms.tex
model comparison

@@
 For the planet flux, we tested three different maps: a two-temperature map, with a uniform dayside temperature $T_d$ and a uniform nightside temperature $T_n$; a map generated with spherical harmonics; and the physically-motivated kinematic model from \cite{zhang16}, which has just three free parameters (the nightside temperature $T_n$, the change in temperature from day-to-night side $\Delta_T$, and the ratio of radiative to advective timescales $\xi$).
+In all cases, we assumed that the planet is tidally locked, such that each orbital revolution corresponds to one complete rotation on its spin axis.
 
@@
 \subsection{Comparison of Thermal Phase Variation Models}
-All four of the thermal phase variation models we consider (two-temperature, kinematic, spherical harmonics, and sinusoid) provide good fits to the observed phase curves.
-Table FIXME summarized the goodness of fit
-
-These models each have different strengths: the kinematic model incorporates the most prior knowledge of physics, and even though it makes several simplifying assumptions (e.g, that the wind speed and direction are constant), it closely reproduces GCM simulations over a wide parameter space \citep{zhang16}.
+We compared four different models for the thermal phase variation: a sinusoid and three temperature maps.
+The sinusoid has been the most widely used model for thermal phase variation in previous analyses of thermal phase curves \citep{FIXME} and directly fits the phase variation amplitude and offset from the substellar point.
+Fitting temperature maps (two-temperature, kinematic, and spherical harmonics) is a new approach enabled by the \texttt{SPIDERMAN} package.
+The three maps each have different strengths: the kinematic model incorporates the most prior knowledge of physics, and even though it makes several simplifying assumptions (e.g, that the wind speed and direction are constant), it closely reproduces GCM simulations over a wide parameter space \citep{zhang16}.
 The spherical harmonics map is the most flexible and makes the fewest assumptions about the true climate.
 The two-temperature model is the simplest and easiest to compare to one-dimensional models of the dayside, which assume a uniform temperature/pressure profile.
-In all cases, we assumed that the planet is tidally locked, such that each orbital revolution corresponds to one complete rotation on its spin axis.
-%In addition to these maps, we also fit the phase variation with a sinusoid, which has been used for many past analyses of exoplanet phase curves (FIXME).
+
+All of the models provide good fits to the observed phase curves.
+Table\,\ref{tab:model_comparison} summarized the goodness of fit according to the reduced $\chi^2$, Bayesian information criterion (BIC), and Aikike information criterion (AIC).
+These metrics for assessing fit quality are .
+The AIC penalizes model complexity relatively LESS?
+than the BIC.
+Spherical harmonics provide the best fit most of the time.
+
+The kinematic model overpredicts the nightside flux. Model is not very flexible because nightside flux is assumed to be constant.
+The two temperature model overpredicts the flux at quadrature and underpredicts the dayside.
+
+What is the difference in min/max temperature?
 

### 2017-10-29 ms.tex
moel selection

@@
 The \HST/WFC3 and \Spitzer\ Channel 2 light curves agree well with expectations, whereas \Spitzer\ Channel 1 shows higher noise than expected as bin size increases.
-This test confirms the existence of time-correlated noise in the Channel 1 light curve that can be seen by eye in the residuals in Figure\,\ref{fig:phasecurves}.
+This test confirms the presence of time-correlated noise in the Channel 1 light curve that can be seen by eye in the residuals in Figure\,\ref{fig:phasecurves}.
 Both \Spitzer\ channels use the same detector, but Channel 1 data are more susceptible to time-correlated noise because the the point spread function is narrower at shorter wavelengths, making intrapixel sensitivity variations more pronounced.
 
-Third, we calculated several goodness of fit statistics. $\chi^2$, AIC, BIC.
+The reduced $\chi^2$ values for the fits are near unity. FIXME when you have them all.
+%Third, we calculated several goodness of fit statistics. $\chi^2$, AIC, BIC.
 
@@
 
-\begin{deluxetable}{lllllll}
-\tablecolumns{7}
+\begin{deluxetable}{llllll}
+	\tablecolumns{6}
 	\tablewidth{0pt}:
-\tablecaption{Model Comparison \label{table:models}}
+	\tablecaption{Model Comparison \label{table:model_comparison}}
 	\tablehead{
-\colhead{Data} & \colhead{Model} & \colhead{$T_\mathrm{min}$} & \colhead{$T_\mathrm{max}$} & \colhead{$\chi^2$} & \colhead{$\Delta_\mathrm{AIC}$} & \colhead{$\Delta_\mathrm{BIC}$}}
+	\colhead{Data} & \colhead{Model} & \colhead{$T_\mathrm{min}$} & \colhead{$T_\mathrm{max}$} & \colhead{$\Delta_\mathrm{AIC}$} & \colhead{$\Delta_\mathrm{BIC}$}}
 		\startdata
-WFC3 & Harmonics & 1214 & 3251 & 1.5 & 0.0 & 0.0 \\
-\, & Kinematic & 1980 & 3958 & 1.6 & 11.8 & 11.8 \\
-\, & Two Temp. & 0 & 2887 & 1.6 & 47.7 & 43.2 \\
-Ch 1 & Harmonics & 1280 & 3444 & 0.9 & 0.0 & 0.0 \\
-\, & Kinematic & 1955 & 3675 & 0.9 & 34.3 & 34.3 \\
-\, & Two Temp. & 1429 & 3041 & 0.9 & 10.7 & 17.6 \\
-Ch 2 & Harmonics & 902 & 3786 & 1.1 & 0.0 & 3.1 \\
-\, & Kinematic & 1703 & 4276 & 1.1 & 14.35 & 17.41 \\
-\, & Two Temp. & 1361 & 3311 & 1.1 & 23.9 & 0.0 \\
+		WFC3 & Sph. Harmonics & 1214 & 3251 & 0.0 & 0.0 \\
+		\, & Kinematic & 1980 & 3958 & 11.8 & 11.8 \\
+		\, & Two Temp. & 0 & 2887 & 47.7 & 43.2 \\
+		Ch 1 & Sph. Harmonics & 1280 & 3444 & 0.0 & 0.0 \\
+		\, & Kinematic & 1955 & 3675 & 34.3 & 34.3 \\
+		\, & Two Temp. & 1429 & 3041 & 10.7 & 17.6 \\
+		Ch 2 & Sph. Harmonics & 902 & 3786 & 0.0 & 3.1 \\
+		\, & Kinematic & 1703 & 4276 & 14.35 & 17.41 \\
+		\, & Two Temp. & 1361 & 3311 & 23.9 & 0.0 \\
 		\enddata
@@
 
-All of the models provide good fits to the observed phase curves.
-Table\,\ref{tab:model_comparison} summarized the goodness of fit according to the reduced $\chi^2$, Bayesian information criterion (BIC), and Aikike information criterion (AIC).
-These metrics for assessing fit quality are .
-The AIC penalizes model complexity relatively LESS?
-than the BIC.
-Spherical harmonics provide the best fit most of the time.
+All of the models provide reasonable fits to the data, but they yield signficantly different temperature maps.
+Table\,\ref{tab:model_comparison} lists the minimum and maximum temperatures for the best fit models to the WFC3 broadband and two Spitzer phase curves.
+We also list the Bayesian information criterion (BIC) and Aikike information criterion (AIC) values for the fits.
+Both of these statistics are an approximation of the Bayesian evidence for a given model, but the BIC penalizes model complexity relatively more than the AIC \citep{kass95}.
+
+Spherical harmonics generally provide the best fit according to the AIC and BIC.
+
+While the spherical harmonics model generally produces the best fits according to both the BIC and the AIC,
 

### 2017-10-29 ms.tex
model compare

@@
 	\tablewidth{0pt}:
-	\tablecaption{Model Comparison \label{table:model_comparison}}
+	\tablecaption{Model Comparison \label{table:models}}
 	\tablehead{
@@
 		\, & Two Temp. & 0 & 2887 & 47.7 & 43.2 \\
-		Ch 1 & Sph. Harmonics & 1280 & 3444 & 0.0 & 0.0 \\
-		\, & Kinematic & 1955 & 3675 & 34.3 & 34.3 \\
-		\, & Two Temp. & 1429 & 3041 & 10.7 & 17.6 \\
-		Ch 2 & Sph. Harmonics & 902 & 3786 & 0.0 & 3.1 \\
-		\, & Kinematic & 1703 & 4276 & 14.35 & 17.41 \\
-		\, & Two Temp. & 1361 & 3311 & 23.9 & 0.0 \\
+		\, & Sinusoid & -- & -- & 17.7 & 13.2 \\
+		Ch 1 & Sph. Harmonics & 1280 & 3444 & 48.0 & 0.0 \\
+		\, & Kinematic & 1955 & 3675 & 82.3 & 34.3 \\
+		\, & Two Temp. & 1429 & 3041 & 58.7 & 17.6 \\
+		\, & Sinusoid & -- & -- & 0.0 & 98.4 \\
+		Ch 2 & Sph. Harmonics & 902 & 3786 & 2.2 & 3.1 \\
+		\, & Kinematic & 1703 & 4276 & 16.55 & 17.41 \\
+		\, & Two Temp. & 1361 & 3311 & 26.1 & 0.0 \\
+		\, & Sinusoid & -- & -- & 0.0 & 49.6 \\
 		\enddata
@@
 This point is illustrated in Figure\,\ref{fig:model_comparison} for the broadband WFC3 light curve.
-In most phase bins, the planet-to-star flux agrees well within one sigma for all the models.
+In most phase bins, the planet-to-star flux agrees to well within one sigma for all the models.
 
@@
 
-All of the models provide reasonable fits to the data, but they yield signficantly different temperature maps.
+All of the models provide reasonable fits to the data, with $\chi^2_\nu$ near unity, but they yield significantly different temperature maps.
 Table\,\ref{tab:model_comparison} lists the minimum and maximum temperatures for the best fit models to the WFC3 broadband and two Spitzer phase curves.
-We also list the Bayesian information criterion (BIC) and Aikike information criterion (AIC) values for the fits.
-Both of these statistics are an approximation of the Bayesian evidence for a given model, but the BIC penalizes model complexity relatively more than the AIC \citep{kass95}.
+We also list the Bayesian information criterion (BIC) and Aikike information criterion (AIC) values for the fits \citep[a $\Delta$BIC value greater than 10 constitutes strong evidence against a given model;][]{kass95}.
 
-Spherical harmonics generally provide the best fit according to the AIC and BIC.
+%Both of these statistics are an approximation of the Bayesian evidence for a given model, but the BIC penalizes model complexity relatively more than the AIC \citep{kass95}.
 
-While the spherical harmonics model generally produces the best fits according to both the BIC and the AIC,
+The best fit model is either a sinusoid or spherical harmonics, depending on which criterion is used for model selection.
+The BIC generally favors the simpler spherical harmonics model because it penalizes model complexity relatively more than the AIC \citep{kass95}.
+The sinusoid has eight free parameters (amplitude, phase offset, eclipse duration, ingress/egress duration, and midpoint and depth for each of two eclipses), whereas the spherical harmonics model has four (for degree two).
+The kinematic and two temperature models tend to perform significantly worse ($\Delta$BIC and $\Delta$AIC greater than 10).
+As illustrated in Figure\,\ref{fig:model_comparison}, the kinematic model overpredicts the nightside flux, whereas the two temperature model overpredicts the flux at quadrature and underpredicts the dayside.
+%The spherical harmonics model is strongly favored for most of the data sets according to the AIC and BIC.
+It has slightly more free parameters than the other models (four, versus three for the kinematic model and two for the two-temperature model).
 
-The kinematic model overpredicts the nightside flux. Model is not very flexible because nightside flux is assumed to be constant.
-The two temperature model overpredicts the flux at quadrature and underpredicts the dayside.
+We compared the planet's minimum and maximum temperature for the three climate maps by computing the temperatures over a $100\times100$ grid in latitude and longitude.
+The kinematic model has the hottest dayside temperature and the two-temperature model has the smallest.
+The differences in peak temperature for the models we consider ranges from $630\,\mathrm{K}$ for \Spitzer\ Channel 1 to $1070\,\mathrm{K}$ for the broadband WFC3 light curve.
+The minimum nightside temperature is also model-dependent: for the WFC3 data, the two-temperature model predicts a nightside temperature of zero Kelvin, whereas the best fit kinematic model has a nightside temperature of $1980\,\mathrm{K}$.
+%For the WFC3 data, the peak temperature ranges from $2890$ to $3960$ K, and the minimum ranges from $0$ to $1980$ K.
 
-What is the difference in min/max temperature?
+These differences arise because the kinematic model allows a steep temperature gradient on the dayside, so the substellar point is much hotter than the terminator, whereas the two temperature map imposes a constant dayside temperature.
+The spherical harmonics model has an intermediate temperature gradient, and fits the data the best.
+However, this model may not be physically realistic: on the nightside, it produces higher temperatures at the poles than at the equator, contrary to predictions from GCM (FIXME define?) simulations.
+
+The typical uncertainty is FIXME (run MCMC, say the systematic range is larger than the error bars).
+
+%The spherical harmonics model fits better according to the BIC and the AIC; however, it yields higher temperatures at the poles than at the equator, which does not agree with predictions from GCM simulations \citep{FIXME}.
 
 \subsection{Hotspot Offset}
+The location of peak brightness of the phase curve is a proxy for the efficiency of thermal reradiation to space and relative to heat transport by advection (the radiative-to-advective timescale).
+The faster the reradiation, the less heat can be redistributed to the nightside.
+We compared the measured hotspot offset for the different models and found FIXME.
 
 \section{Retrieval}
+We performed an atmospheric retrieval to determine the composition and thermal structure of the atmosphere of WASP-103b.
+We used the CHIMERA retrieval suite \citep{FIXME}, as well as.
+Briefly, the CHIMERA model fits for the atmospheric metallicity and carbon-to-oxygen ratio, assuming the atmosphere is in thermochemical equilibrium.
+The temperature-pressure profile is FIXME.
+We included opacity from the dominant absorbing species expected at the temperatures and pressures on WASP-103b, including FIXME.
+Previous analyses of emission spectra of the hottest planets have not included Hminus opacity, but we find that it has a significant effect on our results.
+
+We also performed a simple grid search where we varied X.
+
+\subsection{Thermal Inversion}
 

### 2017-10-29 Figures/fit_table.py

@@ -2,20 +2,20 @@ import numpy as np
 from lc_fit import Model, LightCurveData
 import pickle 
 #zhang, hotspot, spherical
-ch1_chi2 = np.array([0.9, 0.9, 0.9])
-ch1_aic = np.array([7131.0, 7107.4, 7096.7])
-ch1_bic = np.array([7075.2, 7058.5, 7040.9])
+ch1_chi2 = np.array([0.9, 0.9, 0.9, 0.9])
+ch1_aic = np.array([7131.0, 7107.4, 7096.7, 7048.7])
+ch1_bic = np.array([7075.2, 7058.5, 7040.9, 7139.3])
 
-ch2_chi2 = np.array([1.1, 1.1, 1.1])
-ch2_aic = np.array([8345.95, 8355.5, 8331.6])
-ch2_bic = np.array([8401.61, 8384.2, 8387.3])
+ch2_chi2 = np.array([1.1, 1.1, 1.1, 1.1])
+ch2_aic = np.array([8345.95, 8355.5, 8331.6, 8329.4])
+ch2_bic = np.array([8401.61, 8384.2, 8387.3, 8433.8])
 
 # bset fits for WFC3
 wfc3_chi2 = []
 wfc3_aic = []
 wfc3_bic = []
 
-models = ["zhang", "hotspot_t", "spherical"]
+models = ["zhang", "hotspot_t", "spherical", "sincos"]
 path = "WFC3_best_fits/"
 for i, model in enumerate(models):
 	p = pickle.load(open(path+"bestfit_"+model+".pic", "rb")) 
@@ -35,22 +35,22 @@ wfc3_bic = np.array(wfc3_bic)
 #model, Tmin, Tmax =  zhang 1979.6612603 3958.07678595
 #model, Tmin, Tmax =  hotspot_t 0.0 2887.11857794
 #model, Tmin, Tmax =  spherical 1213.50410565 3251.37484203
-wfc3_tmin = np.array([1980, 0, 1214])
-wfc3_tmax = np.array([3958, 2887, 3251])
+wfc3_tmin = np.array([1980, 0, 1214, 0])
+wfc3_tmax = np.array([3958, 2887, 3251, 0])
 
 #Spitzer Ch 2
 #model, Tmin, Tmax =  zhang 1703.0 4276.80767467
 #model, Tmin, Tmax =  hotspot_t 1361.0 3311.0
[…]

### 2017-12-07 ms.tex
water abundance plot
spherical harmonics
expected rms

@@
 \subsection{\Spitzer}
-The \Spitzer\ observations had the following setup.
+We also obtained \Spitzer/IRAC observations with 3.6 and 4.5 $\mu$m photometric filters (referred to as Channel 1 and Channel 2, respectively).
+The observations had the following setup.
 Each phase curve observation consisted of 30 hours of time series photometry, beginning three hours prior to one secondary eclipse and ending three hours after a second eclipse.
@@
 The data points are indicated with black dots.
-The \HST\ data are unbinned, and the Spitzer data are binned in time segments of FIXME minutes with error bars indicating the bin standard deviation.
+The \HST\ data are unbinned, and the Spitzer data are binned in time segments of 15 minutes with error bars indicating the bin standard deviation.
 The colored lines show the best fit models, which include the astrophysical signal and instrument systematics.
@@
 where $t_\mathrm{v}$ is time elapsed since the first exposure in a visit and $t_\mathrm{orb}$ is time since the first exposure in an orbit.
-$S(t)$ is a scale factor equal to 1 for exposures with spatial scanning in the forward direction and $s$ for reverse scans, to account for the upstream-downstream effect (FIXME).
+$S(t)$ is a scale factor equal to 1 for exposures with spatial scanning in the forward direction and $s$ for reverse scans, to account for the upstream-downstream effect \citep{mccullough12}.
 The orbit-long ramp parameters are consistent for all the visits, so we constrained $a$, $b$, and $s$ to have the same value for all visits in the final fit.
@@
 We performed several tests of the quality of the light curve fits.
-First we predicted the level of scatter in the light curves based on photon and read noise, then compared this value to the root-mean-square (rms) of the fit residuals.
-The fit rms was within FIXME percent of the expected noise level in the WFC3 spectroscopic light curves and \Spitzer\ Channel 2 (expected rms of 450 and FIXME ppm).
-The
+First we predicted the level of scatter in the light curves based on photon noise alone, then compared this value to the root-mean-square (rms) of the fit residuals.
+The expected photon-limited rms for the WFC3 spectrosopic light curves ranges from 430 - 530 parts per million (ppm).
+The measured rms was typically within 5\% of expectations for all spectroscopic channels, regardless of which brightness distribution was used to model the thermal phase variation.
+The band-integrated WFC3 light curve has slighty larger rms than predicted (175 versus 122 ppm).
+There are a number of possible origins for this discrepancy, including imperfect background subtraction, variation in the position of the spatial scan on the detector, loss of flux outside the extraction window, and imperfect modeling of the astrophysical signal or instrument systematics.
+However, our analysis of the composition and thermal structure of the planet's atmosphere is based on the wavelength-dependent data (which reach the photon limit), so we do not further explore the small excess noise in the white light curve.
 
-Second, we tested whether the fit rms decreases as expected when the light curve in binned in time.
-If the noise is ``white" (uncorrelated in time), the residuals are expected to decrease by a factor of $\sqrt{N}$, where $N$ is the number of points in a bin.
+The Spitzer 4.5 $\mu$m light curve rms is within 10\% of the photon noise limit (691 versus 640 ppm). The 3.6 $\mu$m light curve has significantly larger rms (797 versus 470 ppm).
+
+%Spitzer expected rms calculated from Figures/systematics.py
+%Ch1: rms obs, exp (ppm) 796.931457529 470.309808368
+%Ch2: rms obs, exp (ppm) 691.221416885 639.675550854
+
+In addition to calculated the fit rms compared to the photon noise, we also tested for the presence of red noise based on whether the rms decreases as expected when the light curve in binned in time.
+If the noise is white (uncorrelated in time), the residuals are expected to decrease by a factor of $\sqrt{N}$, where $N$ is the number of points in a bin.
 Figure\,\ref{fig:rms} shows the binned residuals compared to expectations for white noise.
@@
 
+%\begin{figure}
+%	\includegraphics[width = 1.0\textwidth]{WASP-103b-Solar-NoClouds-Photo-abundances-Water-CO-4.5microns-smooth.pdf}
+%\caption{Water.}
+%\label{fig:dayside}
+%\end{figure}
+
 \section{Comparison of T/P Profiles}

### 2017-12-08 ms.tex
GCM

@@
 In addition to the intrapixel sensitivity variation, we fit the data for a linear trend in time.
-We tested a quadratic trend but did not find significant evidence for the additional model complexity based on the Bayesisan information criterion (BIC).
+We tested a quadratic trend but did not find significant evidence for the additional model complexity based on the Bayesian information criterion (BIC).
+
+As discussed in \S \ref{label:fitquality}, the 3.6 $\mu$m light curve exhibits time correlated noise.
+To account for this additional source of error, we fit the wavelet model from \cite{carter09} (simultaneously with the other fit parameters).
+FIXME: describe wavelets.
 
@@
 This figure shows results from the kinematic model for the thermal phase variation and has instrument systematics removed.
-The peak planet-to-star flux ranges from 1.5 parts-per-thousand (ppt) in the WFC3 bandpass to 5 ppt in \Spitzer Channel 2.
+Broadly speaking, the phase curves show large amplitude phase variation, ranging from 1.5 parts-per-thousand (ppt) in the WFC3 bandpass to 5 ppt in \Spitzer\ Channel 2.
 The planet flux changes significantly with orbital phase in all three of the data sets, suggesting a strong gradient from dayside to nightside temperature.
 The peak brightness occurs near phase 0.5.
+In this section we discuss the quality
 
@@
 First we predicted the level of scatter in the light curves based on photon noise alone, then compared this value to the root-mean-square (rms) of the fit residuals.
-The expected photon-limited rms for the WFC3 spectrosopic light curves ranges from 430 - 530 parts per million (ppm).
-The measured rms was typically within 5\% of expectations for all spectroscopic channels, regardless of which brightness distribution was used to model the thermal phase variation.
-The band-integrated WFC3 light curve has slighty larger rms than predicted (175 versus 122 ppm).
+The Spitzer 4.5 $\mu$m light curve rms is within 10\% of the expected photon noise limit (691 versus 640 ppm), whereas the 3.6 $\mu$m light curve has significantly larger rms (797 versus 470 ppm), due to time-correlated red noise (discussed below).
+The expected photon-limited rms for the WFC3 spectrosopic light curves ranges from 430 - 530 parts per million (ppm), and the measured rms was typically within 5\% of expectations for all spectroscopic channels.
+For the WFC3 band- integrated white light curve, the rms was slightly larger than predicted (175 versus 122 ppm).
 There are a number of possible origins for this discrepancy, including imperfect background subtraction, variation in the position of the spatial scan on the detector, loss of flux outside the extraction window, and imperfect modeling of the astrophysical signal or instrument systematics.
 However, our analysis of the composition and thermal structure of the planet's atmosphere is based on the wavelength-dependent data (which reach the photon limit), so we do not further explore the small excess noise in the white light curve.
-
-The Spitzer 4.5 $\mu$m light curve rms is within 10\% of the photon noise limit (691 versus 640 ppm). The 3.6 $\mu$m light curve has significantly larger rms (797 versus 470 ppm).
 
@@
 To estimate uncertainties, we took the standard deviation of the residuals of the in-eclipse data points, then added this value in quadrature to the standard deviation of the residuals of the out-of-eclipse data.
-This summed error accounts for the uncertainty in the baseline flux.
+This quadrature sum accounts for the uncertainty in the baseline flux.
 
@@
 In each phase bin, we estimated the planet-to-star flux from the mean value of the data points in the bin.
-To estimate the uncertainty, we took the standard deviation of the points in the bin and added it in quadrature to the standard deviation of the data points during secondary eclipse (phase $0.46-0.54$).
-This sum accounts for the uncertainty in the stellar flux (measured during secondary eclipse).
+To estimate the uncertainty, we took the standard deviation of the points in the bin and added it in quadrature to the standard deviation of the data points during secondary eclipse (phase $0.46-0.54$), to account for the uncertainty in baseline stellar flux.
 The phase-resolved emission spectra are shown in Figure\,\ref{fig:spectra} and listed in Table\,\ref{table:spectra}.
@@
 The emission spectra are insensitive to the models because they are estimated directly from the data (after systematics have been removed).
-Since systematic noise is not strongly correlated with the thermal phase variation, the systematics-divided data are nearly identical for all the models.
+Since systematic noise is not strongly correlated with the astrophysical signal, the systematics-divided data are nearly identical for all the models.
 This point is illustrated in Figure\,\ref{fig:model_comparison} for the broadband WFC3 light curve.
@@
 Table\,\ref{tab:model_comparison} lists the minimum and maximum temperatures for the best fit models to the WFC3 broadband and two Spitzer phase curves.
-We also list the Bayesian information criterion (BIC) and Aikike information criterion (AIC) values for the fits \citep[a $\Delta$BIC value greater than 10 constitutes strong evidence against a given model;][]{kass95}.
+We also list the  information criterion (BIC) and Aikike information criterion (AIC) values for the fits \citep[a $\Delta$BIC value greater than 10 constitutes strong evidence against a given model;][]{kass95}.
 

### 2017-12-08 Figures/systematics.py

@@ -120,7 +120,7 @@ for ii, f in enumerate(bestfits):
 #	print (abscissa[1] - abscissa[0])*24.*60.	#time between exposures
 	print "rms obs, exp (ppm)", 1.0e6*np.std((binfluxuc - bestfit)/binfluxuc), 1.e6/np.sqrt(np.median(binfluxuc*fluxconv[ii]))
 
-	plt.text(0.8, 0.986*np.median(binfluxuc), observation[ii])
+	plt.text(0.8, 0.986*np.median(binfluxuc)*fluxconv[ii], observation[ii])
 
 	plt.xlim(-0.1, 1.3)
 	

### 2017-12-08 ms.tex
retrieval results

@@
 
-\title{Global Climate of the Ultra-Hot Jupiter WASP-103\lowercase{b} from \HST\ and Spitzer Phase Curve Observations}
+\title{Global Climate and Atmosphere Composition of the Ultra-Hot Jupiter WASP-103\lowercase{b} from \HST\ and Spitzer Phase Curve Observations}
 
@@
 
-\section{Retrieval}
-We performed an atmospheric retrieval to determine the composition and thermal structure of the atmosphere of WASP-103b.
-We used the CHIMERA retrieval suite \citep{FIXME}, as well as.
-Briefly, the CHIMERA model fits for the atmospheric metallicity and carbon-to-oxygen ratio, assuming the atmosphere is in thermochemical equilibrium.
-The temperature-pressure profile is FIXME.
-We included opacity from the dominant absorbing species expected at the temperatures and pressures on WASP-103b, including FIXME.
-Previous analyses of emission spectra of the hottest planets have not included Hminus opacity, but we find that it has a significant effect on our results.
+\section{Atmospheric Composition}
+Since the phase-resolved spectra are consistent with blackbodies (except for the Spitzer 4.5 $\mu$m broadband photometry point), we opted for a simple grid-based retrieval of the planet's atmospheric properties, similar to the grid search used in Mansfield et al.
+and Arcangeli et al.
+(in prep).
+We generated a grid from one-dimensional forward models of the atmosphere over a broad range of metallicities, carbon-to-oxygen ratios (C/O), and stellar irradiation (\textbf{Mike: elaborate}).
+The forward models compute self-consistent, radiative-convective temperature-pressure (T-P) profiles, and the molecular abundances are calculated in each atmospheric layer assuming thermochemical equilibrium.
+We included opacity from the major absorbers expected for a hot Jupiter atmosphere (FIXME: Mike, what molecules are included?).
+Notably, in contrast to many previous studies of the hottest planets, we also included opacity from H-, which is expected because water dissociates (FIXME: what temperatures?).
+Using these opacities and T-P profiles, we calculated thermal emission spectra over the full grid using the CHIMERA retrieval suite.
+We then explored the grid with an MCMC chain using the \texttt{emcee} package \citep{foremanmackey13} (FIXME: elaborate).
 
-We also performed a simple grid search where we varied X.
+The best fit atmospheric metallicity is FIXME and 
+The 68\% confidence interval for a
 
-\subsection{Thermal Inversion}
+When we do not include H- opacity, FIXME what happens?
 
-\subsection{Bond Albedo}
+\subsection{Climate}
+Heat redistribution, Bond albedo, inversions
+
+%\subsection{Bond Albedo}
 
@@
 \section{Discussion and Conclusions}
+One-dimensional retrieval is probably wrong, since we showed the dayside may have a large temperature gradient -> should work on this in the future.
+
+H- is important.
+
+How does composition compare to other HJs.
 

### 2017-12-18 ms.tex
gcm

@@
 Notably, in contrast to many previous studies of the hottest planets, we also included opacity from H-, which is expected because water dissociates (FIXME: what temperatures?).
-Using these opacities and T-P profiles, we calculated thermal emission spectra over the full grid using the CHIMERA retrieval suite.
+We Using these opacities and T-P profiles, we calculated thermal emission spectra over the full grid using the CHIMERA retrieval suite.
 We then explored the grid with an MCMC chain using the \texttt{emcee} package \citep{foremanmackey13} (FIXME: elaborate).
@@
 \section{Comparison with GCMs}
+To explore the three-dimensional effects of atmospheric dynamics, we ran several GCM models to compare with the measured phase-resolved spectra. We used the SPARC
 
@@
 
+There are many factors contributing to the blackbody spectra --
+weak water xsec contrast, isothermal pt, H-, and dissociated water
+
 H- is important.

### 2017-12-18 ms.tex
retrieval results

@@
 
+Over the WFC3 bandpass, the phase-resolved spectra are featureless and consistent with blackbodies (with best fit $\chi^2_\nu$ ranging from $0.5-1.3$).
+However, the \Spitzer\ data, particularly at 4.5 $\mu$m, are discrepant with the best fit blackbody by $3-5\,\sigma$ at most orbital phases, indicating the presence of infrared molecular absorption or emission features.
+We investigate possible atmospheric compositions and temperature structures in \S\,\ref{sec:composition}.
+
 \begin{figure*}
@@
 
-\section{Atmospheric Composition}
-Since the phase-resolved spectra are consistent with blackbodies (except for the Spitzer 4.5 $\mu$m broadband photometry point), we opted for a simple grid-based retrieval of the planet's atmospheric properties, similar to the grid search used in Mansfield et al.
+\subsection{Clouds?}
+
+\section{Retrieved Atmospheric Composition and Thermal Structure}
+\label{sec:composition}
+Since the phase-resolved spectra do not show spectrally resolved molecular features, we opted for a simple grid-based retrieval of the planet's atmospheric properties, similar to the grid search used in Mansfield et al.
 and Arcangeli et al.
@@
 The forward models compute self-consistent, radiative-convective temperature-pressure (T-P) profiles, and the molecular abundances are calculated in each atmospheric layer assuming thermochemical equilibrium.
-We included opacity from the major absorbers expected for a hot Jupiter atmosphere (FIXME: Mike, what molecules are included?).
-Notably, in contrast to many previous studies of the hottest planets, we also included opacity from H-, which is expected because water dissociates (FIXME: what temperatures?).
-We Using these opacities and T-P profiles, we calculated thermal emission spectra over the full grid using the CHIMERA retrieval suite.
-We then explored the grid with an MCMC chain using the \texttt{emcee} package \citep{foremanmackey13} (FIXME: elaborate).
+We included opacity from the major absorbers expected for a hot Jupiter atmosphere, including H$_2$O, CO, CO$_2$, TiO, and VO (\textbf{Mike: what others?}).
+Notably, in contrast to many previous studies of the hottest planets, we also included opacity from H-, which is expected because water dissociates at temperatures .
+Using these opacities and T-P profiles, we calculated thermal emission spectra over the full grid using the CHIMERA retrieval suite.
+We then explored the grid with an MCMC chain using the \texttt{emcee} package \citep{foremanmackey13}, and interpolated in the grid to calculate the likelihood at each model step.
+We retrieved the composition for dayside emission spectrum and at FIXME phases
 
-The best fit atmospheric metallicity is FIXME and 
-The 68\% confidence interval for a
+\subsection{Dayside}
+We show the retrieved metallicity and C/O in Figure\,\ref{fig:composition}.
+The best fit metallicity is $23^{+29}_{-13}\times$ solar, somewhat higher than expected based on Jupiter's metal enrichment \citep[$3-5\times$ solar][]{wong04} and the trend toward decreasing metallicity with increasing planet mass observed for the Solar System and exoplanets \cite[e.g.][]{kreidberg14}.
+However, planet population synthesis models predict some scatter in atmospheric metallicity.
+Planets near WASP-103b's mass ($1.5\,M_\mathrm{Jup}$) are expected to have metallicities ranging from $1-10\times$ solar \citep{mordasini16}.
+Our result for WASP-103b lies on the upper end of this range, and may be indicative of intrinsic scatter in the mass-atmospheric metallicity relation.
 
-When we do not include H- opacity, FIXME what happens?
+The retrieved C/O is consistent with solar, with a $1\sigma$ confidence interval of $0.54 - 0.85$.
+We infer an upper limit on C/O of 0.9 at $3\,\sigma$ confidence, driven by the fact that the atmospheric chemistry is expected to change dramatically when C/O exceeds unity.
+For a carbon-rich composition, the equilibrium abundance of methane relative to CO increases by orders of magnitude compared to an oxygen-rich  composition \citep[e.g.][]{madhusudhan11}.
+The \Spitzer\ eclipse depths are sensitive to the relative abundance of these species, so we can confidently rule out a carbon-rich composition in spite of the lack of spectrally resolved features.
+Thermal structure.
+
+We note that an important caveat for our results is that the best fit model is not a perfect fit to the data (with $\chi_\nu = 1.77$), so the uncertainties produced by the MCMC may be underestimated.
+Furthermore, the inferred C/O and metallicity are highly sensitive to the large planet-to-star flux at \Spitzer $4.5\mu$m, which is the worst fit data point.
+(With this point removed, the fit quality is significantly improved: $\chi_\nu = 1.17$).
+The dominant absorbing species over the $4.5\,\mu$m bandpass is CO, so to fit this point the model tends to favor super-solar metallicities and C/O.
+Given that the result is driven by a single photometric band and there are no resolved molecular features to constrain the absorbers that are present or the temperature-pressure profile, we caution against over-interpreting these results until wider spectral coverage is available.
+
+Figure\,\ref{fig:TP} shows the retrieved temperature pressure profiles for the dayside. They exhibit a
+
+As a test of our modeling approach, we also performed a retrieval in which the T/P profile was allowed to vary. 
+No H- ?
+
+\subsection{Other Orbital Phases}
+We also modeled the
 

### 2017-12-18 Figures/dayside_espec.py

@@ -33,6 +33,8 @@ def best_fit_bb(w, y, e, rprs):
 	Tstar = 6110.
 	w = np.array(w)
 
+#	w, y, e, = w[0:10], y[0:10], e[0:10]
+
 	#get stellar spectrum
 	star = np.genfromtxt("wasp103_sed_fluxes.out")
 	star_bb = np.interp(w, star[:,0], star[:,1])*1.e24/(w*np.pi*4.)
@@ -49,7 +51,7 @@ def best_fit_bb(w, y, e, rprs):
 	star_bb_hires = np.interp(waves_hires, star[:,0], star[:,1])*1.e24/(waves_hires*np.pi*4.)
 	#star_bb_hires = blackbody(waves_hires*1.0e-6, Tstar) 
 	#print "Best fit blackbody temp, chisq, and outliers: ", Tbest, chibest/(len(e)-1), outliers
-	print "Best fit blackbody temp: ", Tbest
+	print "Best fit blackbody temp, chi2: ", Tbest, chibest/(len(y) - 1.)
 	return waves_hires, blackbody(waves_hires*1.0e-6, Tbest)/star_bb_hires*rprs**2
 
 
@@ -88,6 +90,8 @@ for i, f in enumerate(files):
 
 	fpfs[i] = np.mean(bestfit[ind1])
 	fp_err[i] = np.sqrt(sig1**2 + sig2**2)
+
+print dilution
 
 i+= 1
 #add Spitzer Ch 1
@@ -184,12 +188,15 @@ model_hires *= 1.e3
 plt.plot(wave_hires, model_hires, color='0.5', label='blackbody', linestyle = 'dashed', zorder = -20)
 	
 
-
 #fits from Mike
-wl,y_low_2sig, y_low_1sig, y_median, y_high_1sig, y_high_2sig=pickle.load(open("Retrieval/WASP103b_DAYSIDE_NOMINAL_spec.pic", "rb"))
-plt.fill_between(wl[::-1], convolve(y_low_2sig, g), convolve(y_high_2sig,g), color = 'orange', alpha = 0.5, zorder = -11)
-plt.fill_between(wl[::-1], convolve(y_low_1sig, g), convolve(y_high_1sig,g), color = 'orange', alpha = 0.5, zorder = -10)
-plt.plot(wl[::-1], convolve(y_median, g), zorder = -9, label = 'best fit')
[…]

### 2017-12-19 ms.tex
andrew

@@
 
+\begin{figure}
+\includegraphics[width = 0.5\textwidth]{Figures/WASP-103b_grid_DAYSIDE_stair_pairs_02.pdf}
+\caption{Posterior distributions for WASP-103b's atmospheric heat redistribution, metallicity, and C/O, from a retrieval of the dayside emission spectrum.
+The histograms on the diagonal show the marginalized distribution of each parameter, with dashed lines indicating the median and surrounding 68\% confidence interval.
+The colored shading on the off-diagonal panels indicates FIXME.
+The blue lines correspond to solar metallicity (1) and C/O (0.54).}
+\label{fig:composition}
+\end{figure}
+
 \subsection{Dayside}
@@
 The \Spitzer\ eclipse depths are sensitive to the relative abundance of these species, so we can confidently rule out a carbon-rich composition in spite of the lack of spectrally resolved features.
+
 Thermal structure.
@@
 We note that an important caveat for our results is that the best fit model is not a perfect fit to the data (with $\chi_\nu = 1.77$), so the uncertainties produced by the MCMC may be underestimated.
-Furthermore, the inferred C/O and metallicity are highly sensitive to the large planet-to-star flux at \Spitzer $4.5\mu$m, which is the worst fit data point.
+Furthermore, the inferred C/O and metallicity are highly sensitive to the planet-to-star flux at \Spitzer $4.5\mu$m, which is the worst fit data point.
 (With this point removed, the fit quality is significantly improved: $\chi_\nu = 1.17$).
 The dominant absorbing species over the $4.5\,\mu$m bandpass is CO, so to fit this point the model tends to favor super-solar metallicities and C/O.
-Given that the result is driven by a single photometric band and there are no resolved molecular features to constrain the absorbers that are present or the temperature-pressure profile, we caution against over-interpreting these results until wider spectral coverage is available.
+Given that the result is driven by a single photometric band and there are no resolved molecular features to constrain the temperature-pressure profile or which absorbers are present, we caution against over-interpreting these results until wider spectral coverage is available.
 

### 2017-12-19 ms.tex
dayside retrieval

@@
 
-\section{Retrieved Atmospheric Composition and Thermal Structure}
+\section{Retrieval of Atmospheric Composition and Thermal Structure}
 \label{sec:composition}
-Since the phase-resolved spectra do not show spectrally resolved molecular features, we opted for a simple grid-based retrieval of the planet's atmospheric properties, similar to the grid search used in Mansfield et al.
+Since the phase-resolved spectra do not show spectrally resolved molecular features, we opted for a simple grid-based fit to the planet's atmospheric properties, similar to the grid search used in Mansfield et al.
 and Arcangeli et al.
 (in prep).
-We generated a grid from one-dimensional forward models of the atmosphere over a broad range of metallicities, carbon-to-oxygen ratios (C/O), and stellar irradiation (\textbf{Mike: elaborate}).
-The forward models compute self-consistent, radiative-convective temperature-pressure (T-P) profiles, and the molecular abundances are calculated in each atmospheric layer assuming thermochemical equilibrium.
-We included opacity from the major absorbers expected for a hot Jupiter atmosphere, including H$_2$O, CO, CO$_2$, TiO, and VO (\textbf{Mike: what others?}).
-Notably, in contrast to many previous studies of the hottest planets, we also included opacity from H-, which is expected because water dissociates at temperatures .
+We generated a grid from one-dimensional forward models of the atmosphere over a broad range of metallicities, carbon-to-oxygen ratios (C/O), and stellar irradiation.
+The stellar spectrum is scaled in intensity over the grid to model the unknown heat redistribution for the planet; i.e., a lower dayside irradiation is equivalent to more efficient heat transport to the nightside.
+
+At each point in the grid, we compute forward models to determine self-consistent, radiative-convective temperature-pressure (T-P) profiles.
+We determine the molecular abundances in each atmospheric layer assuming thermochemical equilibrium.
+We include opacity from the major absorbers expected for a hot Jupiter atmosphere, including H$_2$O, CO, CO$_2$, TiO, and VO (\textbf{Mike: what others?}).
+Notably, in contrast to many previous studies of the hottest planets, we also included opacity from H-, which is expected because water dissociates at dayisde photospheric temperature and pressure (3000 K, 0.1 bar).
 Using these opacities and T-P profiles, we calculated thermal emission spectra over the full grid using the CHIMERA retrieval suite.
@@
 \includegraphics[width = 0.5\textwidth]{Figures/WASP-103b_grid_DAYSIDE_stair_pairs_02.pdf}
-\caption{Posterior distributions for WASP-103b's atmospheric heat redistribution, metallicity, and C/O, from a retrieval of the dayside emission spectrum.
+\caption{Posterior distributions for WASP-103b's atmospheric heat redistribution, metallicity, and C/O, from a grid-based fit to the dayside emission spectrum.
 The histograms on the diagonal show the marginalized distribution of each parameter, with dashed lines indicating the median and surrounding 68\% confidence interval.
@@
 \subsection{Dayside}
-We show the retrieved metallicity and C/O in Figure\,\ref{fig:composition}.
-The best fit metallicity is $23^{+29}_{-13}\times$ solar, somewhat higher than expected based on Jupiter's metal enrichment \citep[$3-5\times$ solar][]{wong04} and the trend toward decreasing metallicity with increasing planet mass observed for the Solar System and exoplanets \cite[e.g.][]{kreidberg14}.
+The main characteristics of the dayside emission spectrum are: (1) it is blackbody-like at WFC3 wavelengths, and (2) in the \Spitzer\ bands, the planet-to-star flux is significantly higher than predicted for the best fit blackbody, indicating an emission feature.
+The best fit spectrum reproduces these data fairly well, with $\chi^2_\nu$ = 1.77.
+The WFC3 and Spitzer $3.6\,\mu$m points are fit better ($\chi^2_\nu$  = 1.17 for these data alone), but the $4.5\,\mu$m point is in tension with the model at FIXME $\sigma$.
+The best fit model has a moderately enhanced metallicity ($23\times$ solar), carbon-to-oxygen equal to 0.76, poor heat redistribution, and a thermal inversion (temperature increasing with altitude).
+
+Figure\,\ref{fig:opacities} show the opacity contributions of key absorbers for the best fit.
+In the optical (which we do not observe directly), there is strong absorption by TiO/VO, which heats the upper atmosphere and causes a thermal inversion.
+In the near-infrared, the dominant absorbers are H$_2$O and H-.
+The observed spectrum is featureless at these wavelengths, due to a combination of factors: water is partially dissociated in the photosphere, leading to a drop in abundance of FIXME.
+It also produces H- opacity (single H atoms bind with free electrons), which dominates spectral features from H$_2$O at wavelengths shorter than FIXME $\mu$m.
+Water is also an efficient coolant, so lower water abundance leads to a more isothermal photosphere and weakens the features even more.
+Taken together, all these factors conspire to produce a nearly featureless spectrum from $1.1 - 1.7\,\mu$m.
+Finally, in the infrared the dominant absorber is CO, which produces the emission feature at \Spitzer\ wavelengths.
+
+Figure\,\ref{fig:composition} shows the posterior distributions from the grid retrieval.
+We infer a range in metallicity of $23^{+29}_{-13}\times$ solar, somewhat higher than expected based on Jupiter's metal enrichment \citep[$3-5\times$ solar][]{wong04} and the trend toward decreasing metallicity with increasing planet mass observed for the Solar System and exoplanets \cite[e.g.][]{kreidberg14b}.
 However, planet population synthesis models predict some scatter in atmospheric metallicity.
-Planets near WASP-103b's mass ($1.5\,M_\mathrm{Jup}$) are expected to have metallicities ranging from $1-10\times$ solar \citep{mordasini16}.
+Planets near WASP-103b's mass ($1.5\,M_\mathrm{Jup}$) are expected to have metallicities ranging from roughly $1-10\times$ solar \citep{mordasini16}.
 Our result for WASP-103b lies on the upper end of this range, and may be indicative of intrinsic scatter in the mass-atmospheric metallicity relation.
@@
 For a carbon-rich composition, the equilibrium abundance of methane relative to CO increases by orders of magnitude compared to an oxygen-rich  composition \citep[e.g.][]{madhusudhan11}.
-The \Spitzer\ eclipse depths are sensitive to the relative abundance of these species, so we can confidently rule out a carbon-rich composition in spite of the lack of spectrally resolved features.
+Our \Spitzer\ eclipse depths are sensitive to the relative abundance of these species, so we can confidently rule out a carbon-rich composition in spite of the lack of spectrally resolved features.
 
-Thermal structure.
+We infer a heat redistribution $f = 0.4^{+0.03}_{-0.02}$.
+The $f$ parameter is allowed to range from 0 (isotropic heat distribution) to 0.5 (dayside emission only).
+Our estimate of $f$ is close to the maximum, indicating inefficient transport of heat to the nightside.
+Poor heat transport is observed in other very hot planets as well, due to damping of heat-propagating waves by fast radiative cooling or frictional drag in a partially ionized atmosphere \citep{komacek16}.
+The heat redistribution is correlated with atmospheric metallicity (\textbf{Mike: why is this?}).
+In addition to poor heat redistribution, the atmosphere has a thermal inversion on the dayside caused by TiO/VO absorption.
+We show a selection of 100 randomly selected dayside T-P profiles in Figure FIXME.
+(\textbf{Mike: do the models without TiO/VO still have inversions?
+What pressures are we sensitive to?}).
 
 We note that an important caveat for our results is that the best fit model is not a perfect fit to the data (with $\chi_\nu = 1.77$), so the uncertainties produced by the MCMC may be underestimated.
-Furthermore, the inferred C/O and metallicity are highly sensitive to the planet-to-star flux at \Spitzer $4.5\mu$m, which is the worst fit data point.
-(With this point removed, the fit quality is significantly improved: $\chi_\nu = 1.17$).
-The dominant absorbing species over the $4.5\,\mu$m bandpass is CO, so to fit this point the model tends to favor super-solar metallicities and C/O.
-Given that the result is driven by a single photometric band and there are no resolved molecular features to constrain the temperature-pressure profile or which absorbers are present, we caution against over-interpreting these results until wider spectral coverage is available.
-
-Figure\,\ref{fig:TP} shows the retrieved temperature pressure profiles for the dayside. They exhibit a
-
-As a test of our modeling approach, we also performed a retrieval in which the T/P profile was allowed to vary. 
-No H- ?
+Furthermore, the inferred C/O and metallicity are highly sensitive to the planet-to-star flux at \Spitzer\ $4.5\mu$m, which is the worst fit data point.
+To fit this data point, the model favors super-solar metallicities and C/O, which drive up the CO abundance (the dominant absorber at $4.5\,\mu$m).
+Given that the result hinges on a single photometric band and there are no spectrally resolved molecular features to constrain the temperature-pressure profile or which absorbers are present, we caution against over-interpreting these results until wider spectral coverage is available.
+%As a test of our modeling approach, we also performed a retrieval in which the T/P profile was allowed to vary.
 
@@
 
+Cite Feng et al. 2016.
+
 H- is important.
@@
 How does composition compare to other HJs.
+The spectrum is similar to observations of several other ultra-hot Jupiters \citep[][]{arcangeli18, mansfield18}, but qualitatively different from slightly cooler planets, which show water absorption features in the near-infared \citep[e.g.][]{kreidberg14b, line16}.
 

### 2017-12-19 ms.tex
blackbody fit

@@
 
-Over the WFC3 bandpass, the phase-resolved spectra are featureless and consistent with blackbodies (with best fit $\chi^2_\nu$ ranging from $0.5-1.3$).
-However, the \Spitzer\ data, particularly at 4.5 $\mu$m, are discrepant with the best fit blackbody by $3-5\,\sigma$ at most orbital phases, indicating the presence of infrared molecular absorption or emission features.
-We investigate possible atmospheric compositions and temperature structures in \S\,\ref{sec:composition}.
-
 \begin{figure*}
@@
 
+%\section{Analysis}
+%In this section we describe the interpretation of the data using simple blackbody models, a 1-D grid-based retrieval, and 3-D general circulation models (GCMs).
+
 \subsection{Hotspot Offset}
@@
 
-\section{Retrieval of Atmospheric Composition and Thermal Structure}
+\section{Atmospheric Composition and Thermal Structure}
 \label{sec:composition}
+To interpret the phase-resolved spectra, we performed two model fits.
+First, we modeled the planet flux as a simple blackbody to estimate the dayside brightness temperature and test for significant absorption or emission features.
+We then performed a more sophisticated grid-based retrieval to evaluate the atmospheric composition and thermal structure.
+
+\subsection{Blackbody Fits}
+A blackbody is the simplest model for the planet's thermal emission and provide a useful first evaluation of the atmospheric properties.
+The best fit blackbodies are shown in Figures \ref{fig:spectra} and \ref{fig:dayside}.
+This model performs well for some orbital phases, with $\chi^2_\nu$ ranging from 0.9 to 1.1 for phases $\phi = 0.1, 0.7, \mathrm{and} 0.8$.
+At other phases the blackbody model is a poorer fit, particularly to the \Spitzer\ data.
+For most of the eastern hemisphere to just past the substellar point (phases $0.2 - 0.6$), the \Spitzer\ eclipse depths are larger than predicted for the best fit blackbody, suggesting the presence of an emission feature.
+On the nightside (phase $0.9$), the \Spitzer\ $4.5\,\mu$m eclipse depth is \emph{smaller} than predicted, suggesting an absorption feature.
+These differences hint at changing thermal structure with longitude in the atmosphere.
+
+We also fit blackbody models to the WFC3 data only, and found that they provide an excellent fit at all phases except the dayside.
+The $\chi^2_\nu$ values range from 0.5 to 1.4, with a median of 0.9.
+On the other hand, the dayside spectrum is inconsistent with a blackbody ($chi^2_\nu$ = 5.0).
+(FIXME: what features are there?).
+The dayside spectrum has higher signal-to-noise than the other phases thanks to the two secondary eclipse observations from \citep{cartier17}, so it is not surprising that a more complex model is required.
+In Table\,\ref{tab:depths} we report the best fit temperatures for the WFC3 data blackbody fits.
+
+%Over the WFC3 bandpass, the phase-resolved spectra are featureless and consistent with blackbodies (with best fit $\chi^2_\nu$ ranging from $0.5-1.3$).
+However, the \Spitzer\ data, particularly at 4.5 $\mu$m, are discrepant with the best fit blackbody by $3-5\,\sigma$ at most orbital phases, indicating the presence of infrared molecular absorption or emission features.
+We investigate possible atmospheric compositions and temperature structures in \S\,\ref{sec:composition}.
+
+\subsection{Grid-Based Retrieval}
 Since the phase-resolved spectra do not show spectrally resolved molecular features, we opted for a simple grid-based fit to the planet's atmospheric properties, similar to the grid search used in Mansfield et al.
@@
 
-\subsection{Dayside}
+\subsubsection{Dayside}
 The main characteristics of the dayside emission spectrum are: (1) it is blackbody-like at WFC3 wavelengths, and (2) in the \Spitzer\ bands, the planet-to-star flux is significantly higher than predicted for the best fit blackbody, indicating an emission feature.
@@
 
-\subsection{Other Orbital Phases}
-We also modeled the
+\subsubsection{Other Orbital Phases}
+We also fit the nightside spectrum with the grid-based retrieval.
 
@@
 
-\section{Comparison with GCMs}
+\subsection{Comparison with GCMs}
 To explore the three-dimensional effects of atmospheric dynamics, we ran several GCM models to compare with the measured phase-resolved spectra. We used the SPARC
@@
 %\end{figure}
-
-\section{Comparison of T/P Profiles}
 

### 2017-12-19 Figures/dayside_espec.py

@@ -33,7 +33,7 @@ def best_fit_bb(w, y, e, rprs):
 	Tstar = 6110.
 	w = np.array(w)
 
-#	w, y, e, = w[0:10], y[0:10], e[0:10]
+	w, y, e, = w[0:10], y[0:10], e[0:10]
 
 	#get stellar spectrum
 	star = np.genfromtxt("wasp103_sed_fluxes.out")
@@ -49,7 +49,6 @@ def best_fit_bb(w, y, e, rprs):
 			chibest, Tbest, outliers = chi2, T, (y-model)/e
 	waves_hires = np.linspace(1.0, 5.0, 100)
 	star_bb_hires = np.interp(waves_hires, star[:,0], star[:,1])*1.e24/(waves_hires*np.pi*4.)
-	#star_bb_hires = blackbody(waves_hires*1.0e-6, Tstar) 
 	#print "Best fit blackbody temp, chisq, and outliers: ", Tbest, chibest/(len(e)-1), outliers
 	print "Best fit blackbody temp, chi2: ", Tbest, chibest/(len(y) - 1.)
 	return waves_hires, blackbody(waves_hires*1.0e-6, Tbest)/star_bb_hires*rprs**2
@@ -70,7 +69,6 @@ for i, f in enumerate(files):
 	
 	waves.append(d.wavelength)
 	dilution.append(d.dilution)
-
 
 	ind = d.err < 9.0e7			#indices of outliers
 	
@@ -238,9 +236,8 @@ plt.xlim(3, 5)
 plt.ylim(3.5,7)
 
 
-print "ERRORS & WARNINGS"
-print "hard coding rprs for calculating best fit bb - is this right?"
-print "hard coding dilution in spitzer bandpass - are we also supposed to do this for WFC3?"
+print "NOTE:"
+print "you are hard coding rprs for calculating best fit bb"
 plt.tight_layout()
 plt.savefig("dayside_spectrum.pdf")
 plt.show()

### 2017-12-20 ms.tex
nightside

@@
 The best fit blackbodies are shown in Figures \ref{fig:spectra} and \ref{fig:dayside}.
-This model performs well for some orbital phases, with $\chi^2_\nu$ ranging from 0.9 to 1.1 for phases $\phi = 0.1, 0.7, \mathrm{and} 0.8$.
+This model performs well for some orbital phases, with $\chi^2_\nu$ ranging from 0.9 to 1.1 for phases $\phi = 0.1, 0.7$ and $0.8$.
 At other phases the blackbody model is a poorer fit, particularly to the \Spitzer\ data.
-For most of the eastern hemisphere to just past the substellar point (phases $0.2 - 0.6$), the \Spitzer\ eclipse depths are larger than predicted for the best fit blackbody, suggesting the presence of an emission feature.
+For phases $0.2 - 0.6$, the \Spitzer\ eclipse depths are larger than predicted for the best fit blackbody, suggesting the presence of an emission feature.
 On the nightside (phase $0.9$), the \Spitzer\ $4.5\,\mu$m eclipse depth is \emph{smaller} than predicted, suggesting an absorption feature.
@@
 
-We also fit blackbody models to the WFC3 data only, and found that they provide an excellent fit at all phases except the dayside.
-The $\chi^2_\nu$ values range from 0.5 to 1.4, with a median of 0.9.
-On the other hand, the dayside spectrum is inconsistent with a blackbody ($chi^2_\nu$ = 5.0).
-(FIXME: what features are there?).
-The dayside spectrum has higher signal-to-noise than the other phases thanks to the two secondary eclipse observations from \citep{cartier17}, so it is not surprising that a more complex model is required.
-In Table\,\ref{tab:depths} we report the best fit temperatures for the WFC3 data blackbody fits.
+We also fit blackbody models to the WFC3 data only, and found that they provide a good fit at all orbital phases.
+The $\chi^2_\nu$ values range from 0.5 to 1.6, with a median of 0.9.
+The best fit effective temperatures range from 1920 Kelvin on the nightside to 2980 Kelvin on the dayside.
+We report the best fit temperatures with uncertainties in Table\,\ref{tab:depths}.
+The dayside spectrum is the poorest fit by the blackbody model.
+This finding is not a surprise because the dayside has higher signal-to-noise than the other orbital phases, thanks to the two secondary eclipse observations from \citep{cartier17}.
+The more sophisticated grid-based retrieval provides a better fit to the dayside.
 
@@
 
-\subsubsection{Dayside}
+\subsubsection{Dayside Spectrum}
 The main characteristics of the dayside emission spectrum are: (1) it is blackbody-like at WFC3 wavelengths, and (2) in the \Spitzer\ bands, the planet-to-star flux is significantly higher than predicted for the best fit blackbody, indicating an emission feature.
@@
 
-Figure\,\ref{fig:opacities} show the opacity contributions of key absorbers for the best fit.
-In the optical (which we do not observe directly), there is strong absorption by TiO/VO, which heats the upper atmosphere and causes a thermal inversion.
+Figure\,\ref{fig:opacities} shows the opacity contributions of key absorbers for the best fit.
+In the optical (which we do not observe directly), there is strong absorption by TiO/VO.
 In the near-infrared, the dominant absorbers are H$_2$O and H-.
@@
 
-Figure\,\ref{fig:composition} shows the posterior distributions from the grid retrieval.
-We infer a range in metallicity of $23^{+29}_{-13}\times$ solar, somewhat higher than expected based on Jupiter's metal enrichment \citep[$3-5\times$ solar][]{wong04} and the trend toward decreasing metallicity with increasing planet mass observed for the Solar System and exoplanets \cite[e.g.][]{kreidberg14b}.
+The TiO/VO absorption heats the upper atmosphere, resulting in a thermal inversion.
+Figure\,\ref{fig:TP} shows a selection of 100 randomly selected dayside T-P profiles.
+The profiles are nearly isothermal over a pressure range of $1-10^{-2}$ bars, with a median temperature near 2900 Kelvin.
+The temperature increases over $10^{-2} - 10^{-3}$ bars to 3500 Kelvin, and then begins to decrease again at pressures below $10^{-3}$ bar.
+FIXME: where are the contribution functions for the different instruments?
+
+In Figure\,\ref{fig:composition}, we show the posterior distributions from the grid retrieval.
+We infer a range in metallicity of $23^{+29}_{-13}\times$ solar, somewhat higher than expected based on Jupiter's metal enrichment \citep[$3-5\times$ solar;][]{wong04} and the trend toward decreasing metallicity with increasing planet mass observed for the Solar System and exoplanets \cite[e.g.][]{kreidberg14b}.
 However, planet population synthesis models predict some scatter in atmospheric metallicity.
@@
 The heat redistribution is correlated with atmospheric metallicity (\textbf{Mike: why is this?}).
-In addition to poor heat redistribution, the atmosphere has a thermal inversion on the dayside caused by TiO/VO absorption.
-We show a selection of 100 randomly selected dayside T-P profiles in Figure FIXME.
-(\textbf{Mike: do the models without TiO/VO still have inversions?
-What pressures are we sensitive to?}).
 
 We note that an important caveat for our results is that the best fit model is not a perfect fit to the data (with $\chi_\nu = 1.77$), so the uncertainties produced by the MCMC may be underestimated.
-Furthermore, the inferred C/O and metallicity are highly sensitive to the planet-to-star flux at \Spitzer\ $4.5\mu$m, which is the worst fit data point.
+Furthermore, the inferred C/O and metallicity are highly sensitive to the planet-to-star flux at \Spitzer\ $4.5\,\mu$m, which is the worst fit data point.
 To fit this data point, the model favors super-solar metallicities and C/O, which drive up the CO abundance (the dominant absorber at $4.5\,\mu$m).
@@
 
-\subsubsection{Other Orbital Phases}
-We also fit the nightside spectrum with the grid-based retrieval.
+\begin{figure}
+\includegraphics[width = 0.5\textwidth]{Figures/TP.pdf}
+\caption{Dayside temperature-pressure profiles from the grid retrieval (red lines) compared to the profile from the substellar point for the FIXME GCM.}
+\label{fig:TP}
+\end{figure}
 
-\subsection{Climate}
-Heat redistribution, Bond albedo, inversions
+\subsubsection{Nightside Spectrum}
+We also fit the nightside spectrum (phase $0.1$) with the grid-based retrieval.
+The best fit spectrum has a non-inverted temperature pressure profile.
+At 1\,$\sigma$ confidence, the metallicity is $15 - 240\times$ solar and the C/O is unbounded over the full prior range (FIXME).
+The atmospheric composition is consistent with results from the dayside spectrum.
+
+This agreement is an encouraging sanity check; however, there are several model assumptions that may result in artificially tight constraints on the atmospheric properties.
+One challenge in modeling the nightside spectrum is that the shape of the T-P profile is unknown.
+Our model assumes a scaled stellar irradiation at the top of the atmosphere, but in reality, the heat source is advection from the dayside.
+Another caveat is that the model is not self-consistent: the energy leaving the dayside is not constrained to equal the energy entering the nightside.
+We do not pursue this, but note these for future phase curve observations that are sensitive to spectral Future work is needed to develop a self-consistent 2-D retrieval method to fit phase curve.
+
+%\subsection{Climate}
+%Heat redistribution, Bond albedo, inversions
 

### 2017-12-21 ms.tex
units for BDs

@@
 \subsection{Photometric Monitoring}
-We monitored WASP-103's photometric variability over 158 nights during 2014 - 2016 with the Tennessee State University Celestron 14-inch (C14) automated imaging telescope (AIT), located at Fairborn Observatory in southern Arizona \citep[see, e.g.,][]{h1999, ehf2003}.
+We monitored WASP-103's photometric variability over 158 nights during 2014 - 2016 with the Tennessee State University Celestron 14-inch (C14) automated imaging telescope (AIT), located at Fairborn Observatory in southern Arizona \citep[][]{henry99}.
 The observations of WASP-103 were made in the Cousins R passband with an SBIG STL-1001E CCD camera.
@@
 \begin{deluxetable}{ccccc}
+\label{tab:photometry}
 	%\tabletypesize{\small}
@@
 	\enddata
-	\label{tab:photometry}
 \end{deluxetable}
@@
 In our fit, we calculated the stellar flux with a PHOENIX model \citep{husser13} interpolated to an effective temperature of $6110\,\mathrm{K}$ \citep{gillon14}.
-For the planet flux, we tested three different maps: a two-temperature map, with a uniform dayside temperature $T_d$ and a uniform nightside temperature $T_n$; a map generated with spherical harmonics; and the physically-motivated kinematic model from \cite{zhang16}, which has just three free parameters (the nightside temperature $T_n$, the change in temperature from day-to-night side $\Delta_T$, and the ratio of radiative to advective timescales $\xi$).
+For the planet flux, we tested three different maps: a two-temperature map, with a uniform dayside temperature $T_d$ and a uniform nightside temperature $T_n$; a map generated with spherical harmonics; and the physically-motivated kinematic model from \cite{zhang17}, which has just three free parameters (the nightside temperature $T_n$, the change in temperature from day-to-night side $\Delta_T$, and the ratio of radiative to advective timescales $\xi$).
 In all cases, we assumed that the planet is tidally locked, such that each orbital revolution corresponds to one complete rotation on its spin axis.
@@
 We estimated $\alpha(\lambda)$ based on the best fit spectral energy distribution from \cite{cartier17}.
-The companion star contributes FIXME percent of the flux at FIXME $\mu$m.
+The companion star contributes $10-16\%$ of the flux over the wavelength range $1 - 5\,\mu$m.
 We calculated $A(t)$ using the analytic formula from \cite{leconte11b}, equation B.9, which computes the projected area of a triaxial ellipsoid.
@@
 Both the \HST\ and \Spitzer\ phase curves have systematic noise caused by variations in the sensitivity of the instrument over time.
-For the \HST/WFC3 data, the dominant systematic is an orbit-long exponential trend due to charge traps filling up over successive exposures \citep{long15, zhu17}.
+For the \HST/WFC3 data, the dominant systematic is an orbit-long exponential trend due to charge traps filling up over successive exposures \citep{long15, zhou17}.
 For \Spitzer\, the primary source of noise is the intrapixel sensitivity effect.
@@
 
-As discussed in \S \ref{label:fitquality}, the 3.6 $\mu$m light curve exhibits time correlated noise.
+As discussed in \S \ref{sec:fitquality}, the 3.6 $\mu$m light curve exhibits time correlated noise.
 To account for this additional source of error, we fit the wavelet model from \cite{carter09} (simultaneously with the other fit parameters).
@@
 \begin{figure*}
-\includegraphics[width = 1.0\textwidth]{Figures/phase_curves.pdf}
+\includegraphics[width = 1.0\textwidth]{Figures/phase_curves_spherical.pdf}
 \caption{WASP-103b phase curve observations from \HST/WFC3 (top) and \Spitzer/IRAC (middle and bottom).
 For clarity, the data are phase-folded on the planet's orbital period and binned in 30 uniformly spaced bins between 0 and 1.
-The left column shows the phase curves with systematic noise removed (black points) compared to the best fit model (black line).
-The shading denotes the  1\,$\sigma$ confidence interval on the best fit.
-We include the transits in the fit, but they are not displayed in this figure.
-The right-hand column shows the binned residuals for the best-fit light curve.}
+The left column shows the phase curves with systematic noise removed (black points) compared to the best fit spherical harmonics model (colored lines).
+The error bars denote $1\,\sigma$ uncertainties (in some cases, the errors are smaller than the data points).
+%The shading denotes the  1\,$\sigma$ confidence interval on the best fit. 
+We include the transits in the fit, but they are not displayed in this figure. The right-hand column shows the binned residuals for the best-fit light curve.}
 \label{fig:phasecurves}
@@
 \subsection{Goodness of Fit}
+\label{sec:fitquality}
 We performed several tests of the quality of the light curve fits.
@@
 \begin{deluxetable}{llllll}
+\label{tab:model_comparison}
 	\tablecolumns{6}
@@
 This quadrature sum accounts for the uncertainty in the baseline flux.
+To account for red noise in the \Spitzer\ $3.6\,\mu$ light curve, we use the approach of \cite{pont06} to determine the red noise contribution on the timescale of the eclipse.
+We add the estimated red noise in quadrature, which increases the uncertainty on planet-to-star flux by a factor of $2.5$.
 
@@
 To estimate the uncertainty, we took the standard deviation of the points in the bin and added it in quadrature to the standard deviation of the data points during secondary eclipse (phase $0.46-0.54$), to account for the uncertainty in baseline stellar flux.
+For the $3.6\mu$m data, we also add red noise on the timescale of a phase bin, following \cite{pont06}.
 The phase-resolved emission spectra are shown in Figure\,\ref{fig:spectra} and listed in Table\,\ref{table:spectra}.
@@
 \includegraphics[width = 1.0\textwidth]{Figures/emission_spectra.pdf}
-\caption{Phase-resolved emission spectra.}
+\caption{Phase-resolved emission spectra (points) compared to the best fit blackbody (blue line) and the FIXME GCM.
+Phases $\phi = 0.5$ and $0.0$ are centered on the substellar and anti-stellar points, respectively.}
 \label{fig:spectra}
@@
 We compared four different models for the thermal phase variation: a sinusoid and three temperature maps.
-The sinusoid has been the most widely used model for thermal phase variation in previous analyses of thermal phase curves \citep{FIXME} and directly fits the phase variation amplitude and offset from the substellar point.
-Fitting temperature maps (two-temperature, kinematic, and spherical harmonics) is a new approach enabled by the \texttt{SPIDERMAN} package.
-The three maps each have different strengths: the kinematic model incorporates the most prior knowledge of physics, and even though it makes several simplifying assumptions (e.g, that the wind speed and direction are constant), it closely reproduces GCM simulations over a wide parameter space \citep{zhang16}.
-The spherical harmonics map is the most flexible and makes the fewest assumptions about the true climate.
-The two-temperature model is the simplest and easiest to compare to one-dimensional models of the dayside, which assume a uniform temperature/pressure profile.
+The sinusoid has been widely used to model phase variation in previous analyses \citep[e.g.][]{knutson09, stevenson14}.
+One advantage of the sinusoid model is that it directly fits the phase variation amplitude and offset from the substellar point, and can be inverted to map the climate \citep{cowan08}.
+Fitting temperature maps directly is a new approach enabled by the \texttt{SPIDERMAN} package.
+We consider three parameterizations for the temperature map, which each have different strengths.
+One is a physically-motivated kinematic model that closely reproduces GCM simulations \citep{zhang17}.
+The second parameterization is a spherical harmonic map, which is the most flexible model we consider and makes the fewest assumptions about the true climate.
+The third model has just two free parameters, a dayside temperature and a nightside temperature.
+This model is easiest to compare to one-dimensional forward models of the dayside, which assume a uniform temperature/pressure profile.
 
@@
 
-%\section{Analysis}
-%In this section we describe the interpretation of the data using simple blackbody models, a 1-D grid-based retrieval, and 3-D general circulation models (GCMs).
-
 \subsection{Hotspot Offset}
@@
 
-\subsection{Clouds?}
+%\subsection{Clouds?}
 
@@
 The dayside spectrum is the poorest fit by the blackbody model.
-This finding is not a surprise because the dayside has higher signal-to-noise than the other orbital phases, thanks to the two secondary eclipse observations from \citep{cartier17}.
+This finding is not a surprise because the dayside has higher signal-to-noise than the other orbital phases, thanks to the two secondary eclipse observations from \cite{cartier17}.
 The more sophisticated grid-based retrieval provides a better fit to the dayside.
@@
 We then explored the grid with an MCMC chain using the \texttt{emcee} package \citep{foremanmackey13}, and interpolated in the grid to calculate the likelihood at each model step.
-We retrieved the composition for dayside emission spectrum and at FIXME phases
+We fit this model to the dayside and nightside emission spectra (phases $\phi = 0.5$ and $0.1$).
 
@@
 The histograms on the diagonal show the marginalized distribution of each parameter, with dashed lines indicating the median and surrounding 68\% confidence interval.
-The colored shading on the off-diagonal panels indicates FIXME.
-The blue lines correspond to solar metallicity (1) and C/O (0.54).}
+\textbf{Mike: what percentiles does the colored shading correspond to?} The blue lines correspond to solar metallicity (1) and C/O (0.54).}
 \label{fig:composition}
@@
 The best fit spectrum reproduces these data fairly well, with $\chi^2_\nu$ = 1.77.
-The WFC3 and Spitzer $3.6\,\mu$m points are fit better ($\chi^2_\nu$  = 1.17 for these data alone), but the $4.5\,\mu$m point is in tension with the model at FIXME $\sigma$.
+The WFC3 and Spitzer $3.6\,\mu$m points are fit better ($\chi^2_\nu$  = 1.17 for these data alone), but the $4.5\,\mu$m point is higher than the best fit model by $2.9\,\sigma$.
 The best fit model has a moderately enhanced metallicity ($23\times$ solar), carbon-to-oxygen equal to 0.76, poor heat redistribution, and a thermal inversion (temperature increasing with altitude).
@@
 The temperature increases over $10^{-2} - 10^{-3}$ bars to 3500 Kelvin, and then begins to decrease again at pressures below $10^{-3}$ bar.
-FIXME: where are the contribution functions for the different instruments?
+(\textbf{Mike: what are the contribution functions?}).
 
@@
 The best fit spectrum has a non-inverted temperature pressure profile.
-At 1\,$\sigma$ confidence, the metallicity is $15 - 240\times$ solar and the C/O is unbounded over the full prior range (FIXME).
+At 1\,$\sigma$ confidence, the metallicity is $15 - 240\times$ solar and the C/O is unbounded over the full prior range (\textbf{Mike: what priors did you use?}).
 The atmospheric composition is consistent with results from the dayside spectrum.
@@
 Another caveat is that the model is not self-consistent: the energy leaving the dayside is not constrained to equal the energy entering the nightside.
-We do not pursue this, but note these for future phase curve observations that are sensitive to spectral Future work is needed to develop a self-consistent 2-D retrieval method to fit phase curve.
+Further work is needed to develop a fully self-consistent 2-D retrieval method.
 
@@
 \subsection{Comparison with GCMs}
-To explore the three-dimensional effects of atmospheric dynamics, we ran several GCM models to compare with the measured phase-resolved spectra. We used the SPARC
+To explore the three-dimensional effects of atmospheric dynamics, we ran several GCM models to compare with the measured phase-resolved spectra.
 

### 2017-12-21 Figures/get_dayside_espec.py

@@ -1,0 +1,244 @@
+import numpy as np
+import pickle
+import matplotlib.pyplot as plt
+import os, glob
+from lc_fit import Model, LightCurveData
+#import read_spectra_from_Vivien as rs
+import matplotlib.gridspec as gridspec
+from pylab import *
+from matplotlib import rc
+import spiderman_lc
+from matplotlib import ticker
+import seaborn as sns
+from astropy.convolution import Gaussian1DKernel, convolve
+g = Gaussian1DKernel(stddev=20)
+
+sns.set_context("paper", font_scale=1.2)
+sns.set_style("white")
+sns.set_style("ticks", {"xtick.direction":"in", "ytick.direction":"in"})
+
+
+rc('font',**{'family':'sans-serif','sans-serif':['Arial']})
+
+def blackbody(l,T): 
+	h = 6.62607e-34   #J/s
+        c = 2.997925e8       #m/s
+        k = 1.38065e-23     #J/K
+        return 2*h*c**2/(l**5*(np.exp(h*c/(l*k*T))-1))                 #[W/sr/m^3]
+
+def best_fit_bb(w, y, e, rprs):
+	Ts = np.linspace(300, 3600, 300)
+	chibest = 10000.
+	Tbest = 0.	
+	Tstar = 6110.
+	w = np.array(w)
+
+	#w, y, e, = w[0:10], y[0:10], e[0:10]
+
+	#get stellar spectrum
+	star = np.genfromtxt("wasp103_sed_fluxes.out")
+	star_bb = np.interp(w, star[:,0], star[:,1])*1.e24/(w*np.pi*4.)
+        #Tstar = 6110.
+        #star_bb = blackbody(w*1.0e-6, Tstar)
+	outliers = 0.
+
+	for T in Ts:
+		model = blackbody(w*1.0e-6, T)/star_bb*rprs**2
+		chi2 = np.sum((y - model)**2/e**2)
+		if chi2 < chibest: 
+			chibest, Tbest, outliers = chi2, T, (y-model)/e
+	waves_hires = np.linspace(1.0, 5.0, 100)
+	star_bb_hires = np.interp(waves_hires, star[:,0], star[:,1])*1.e24/(waves_hires*np.pi*4.)
[…]

### 2017-12-21 Figures/phase_curves_spherical.py

@@ -191,9 +191,14 @@ for ii, f in enumerate(bestfits):
 	ax.set_xticklabels([])
 	plt.ylim(-1, 6.)
 	plt.xlim(0,1)
+        
+        ax.set_yticks([0, 2, 4, 6])
+        ax.yaxis.set_minor_locator(FixedLocator(np.array([1, 3, 5])))
 	
 	if ii ==0: 
-		plt.ylabel("Planet-to-star flux (ppt)", fontsize = 12, labelpad = 10)
+		plt.ylabel("Planet-to-star flux (ppt)", fontsize = 12, labelpad = 12)
+                ax.xaxis.set_major_locator(FixedLocator(np.array([0.1, 0.3, 0.5, 0.7, 0.9])))
+                ax.xaxis.set_minor_locator(FixedLocator(np.array([0., 0.2, 0.4, 0.6, 0.8, 1.])))
 		ax.set_xticklabels([])
 		ax.text(0.03, 3.8, 'Spitzer Ch 1\n3.6 $\mu$m', fontsize=10)
 	if ii == 1: 

### 2017-12-21 Figures/phased_espec.py

@@ -145,7 +145,8 @@ for ii in range(1,len(bins)-1):
 	ind = (t>bins[ii-1])&(t < bins[ii])
 	binned_resid[ii] = np.mean(resid[ind]) 
 	sigma = np.sqrt(np.sum(err[ind]**2)/sum(ind)**2)
-#print "sr, sw", np.sqrt(np.std(binned_resid[1::])**2 -  sigma**2), sigma
+print "sr, sw", np.sqrt(np.std(binned_resid[1::])**2 -  sigma**2), sigma
+print "sr/sw", np.sqrt(np.std(binned_resid[1::])**2 -  sigma**2)/sigma
 # s^2 = sw^2 + sr^2
 sr = np.sqrt(np.std(binned_resid[1::])**2 -  sigma**2)
 

### 2017-12-22 ms.tex
comparison ifurge

@@
 \section{Introduction} \label{sec:intro}
+The planets and moons of the Solar System possess a rich variety of -- weather, temperature var
+
 It is a truism to say that planets are round.
@@
 \section{Comparison with Brown Dwarfs and Directly Imaged Planets}
+WASP-103b is so highly irradiated that its photospheric temperature ($2000 - 3000$ K) is comparable to that of low mass stars.
+However, it is heated asymmetrically, its rotation rate is FIXME faster, and its surface gravity is lower.
+To assess the effects of these comparative study with other objects of similar temperature, including field brown dwarfs and young directly imaged companions.
+
+Sample of directly imaged planets
+
 cite Tremblin et al. 2017 ? (https://arxiv.org/pdf/1710.02640.pdf)

### 2017-12-22 Figures/blackbody.py

@@ -1,0 +1,14 @@
+import numpy as np
+import matplotlib.pyplot as plt
+from astropy import modeling
+
+w = np.linspace(1, 2, 10)
+flux = modeling.blackbody.blackbody_lambda(w*1.e4, 6100.)       #wavelength in angstroms
+# return units: math:`erg \\; cm^{-2} s^{-1} \\mathring{A}^{-1} sr^{-1}
+
+flux = flux*4.*np.pi*1.e4*w        #multiplies by 4 pi steradians * 10000. angstroms/micron * micron
+
+scale = 1.863e17  #(470 pc/jupiter radius)^2
+plt.plot(w, flux/scale*1.e-3)
+
+plt.show()

### 2017-12-27 ms.tex
gcm

@@
 \subsection{Comparison with GCMs}
-To explore the three-dimensional effects of atmospheric dynamics, we ran several GCM models to compare with the measured phase-resolved spectra.
+To explore the three-dimensional effects of atmospheric dynamics, we ran several GCM models to compare with the measured phase-resolved spectra. (\textbf{Vivien: paragraph describing GCM}).
+
+Figure\,\ref{fig:gcmcomparison} shows GCM predictions compared to the best fit model to the WFC3 phase curve.
+The WFC3 bandpass is near the peak of the planet's thermal emission, so it provides a good test of whether the GCM reproduces the properties of the planet.
+Our nominal model was a cloud-free, solar composition atmosphere with TiO/VO opacity and no added drag.
+This model qualitatively reproduces some features of the data, such as the large day-night temperature contrast; however, it predicts a larger offset in peak brightness from the substellar point than we observe.
+
+To achieve a better fit to the data, we varied the nominal model parameters.
+We tested models with enhanced metallicity ([Fe/H] = 0.5), no TiO/VO, and added atmospheric drag.
+Lorentz drag can occur in the hottest exoplanet atmospheres, which may be partially ionized and coupled to the background magnetic field.
+We parameterized the drag (\textbf{Vivien: how did you model drag?}), with timescales were $\tau_\mathrm{drag} = 10^3, 10^4$ and $10^6$ s.
+
+The models with added drag more closely reproduce the small hotspot offset that is observed.
+The main effect of drag is to slow down advection of heat to the nightside, which shifts the peak brightness closer to the substellar point.
+The best fit WFC3 phase curve has a hotspot offset of FIXME.
+The drag models have offsets of $0.2$ and $2.3$ degrees for $\tau_\mathrm{drag} = 10^3$ and $10^4$ s, compared to $15$ degrees for the nominal GCM.
+The drag models also provide a good match to the observed dayside flux, for drag timescales in the range $\tau_\mathrm{drag} = 10^3 - 10^4$ s.
+However, the drag models underestimate the flux at longitudes away from the substellar point, predicting a flux FIXME less than what is observed.
+\textbf{Vivien: are these fast drag timescales even reasonable?}).
+
+Water dissociation!
+
+\begin{figure}
+\includegraphics[width = 0.5\textwidth]{Figures/gcm_comparison.pdf}
+\caption{GCM predictions (colored lines) compared to the best fit model for the WFC3 white light phase curve (black line).
+The nominal model is solar composition, cloud-free, with TiO/VO opacity and no drag.
+The models are multiplied by the predicted ellipsoidal variability of the planet.}
+\label{fig:gcmcomparison}
+\end{figure}
 
@@
 cite Tremblin et al. 2017 ? (https://arxiv.org/pdf/1710.02640.pdf)
+
+\begin{figure*}
+\includegraphics[width = 1.0\textwidth]{Figures/spectra_comparison.pdf}
+\caption{Spectra for WASP-103b (left column) compared to brown dwarfs (middle) and directly imaged companions (right).
+The WASP-103b spectra are from the nightside (phase 0.1, top row), quadrature (phase 0.25, middle) and the dayside (phase 0.5, bottom).
+Each row shows spectra from objects of comparable temperature.
+The dotted gray line corresponds to the best fit blackbody.
+Effective temperatures are listed in the upper right corners.}
+\label{fig:planetstarcomparison}
+\end{figure*}
 

### 2017-12-27 Figures/blackbody.py

@@ -1,14 +1,0 @@
-import numpy as np
-import matplotlib.pyplot as plt
-from astropy import modeling
-
-w = np.linspace(1, 2, 10)
-flux = modeling.blackbody.blackbody_lambda(w*1.e4, 6100.)       #wavelength in angstroms
-# return units: math:`erg \\; cm^{-2} s^{-1} \\mathring{A}^{-1} sr^{-1}
-
-flux = flux*4.*np.pi*1.e4*w        #multiplies by 4 pi steradians * 10000. angstroms/micron * micron
-
-scale = 1.863e17  #(470 pc/jupiter radius)^2
-plt.plot(w, flux/scale*1.e-3)
-
-plt.show()

### 2017-12-27 Figures/compare_stellar_spectra.py

@@ -1,23 +1,0 @@
-import numpy as np
-import matplotlib.pyplot as plt
-
-
-def blackbody(l,T): 
-	h = 6.62607e-34   #J/s
-        c = 2.997925e8       #m/s
-        k = 1.38065e-23     #J/K
-        return 2*h*c**2/(l**5*(np.exp(h*c/(l*k*T))-1))                 #[W/sr/m^3]
-
-w = np.linspace(1.1, 1.7, 100)
-w = np.linspace(5, 10, 100)
-star = np.genfromtxt("wasp103_sed_fluxes.out")
-star_bb = np.interp(w, star[:,0], star[:,1])*1.e24/(w*np.pi*4.)
-plt.plot(w, star_bb)
-
-Tstar = 6110.
-star_bb = blackbody(w*1.0e-6, Tstar)
-plt.plot(w, star_bb)
-
-#plt.gca().set_yscale('log')
-
-plt.show()

### 2017-12-27 Figures/comparison_new.py

@@ -1,169 +1,0 @@
-import numpy as np
-import matplotlib.pyplot as plt
-import matplotlib.gridspec as gridspec
-import pyfits
-from astropy import units as u
-
-def blackbody(l,T): 
-	h = 6.62607e-34   #J/s
-	c = 2.997925e8       #m/s
-	k = 1.38065e-23     #J/K
-	#return 2*h*c**2/(l**5*(np.exp(h*c/(l*k*T))-1))			#[W/sr/m^3]
-	return 2*h*c**2/(l**5*(np.exp(h*c/(l*k*T))-1))*np.pi/1.e6	#[W/m^2/micron]
-
-gs = gridspec.GridSpec(3, 3, hspace=0.1, wspace=0.3)
-
-ylo = [0, 5, 12]
-yhi = [6, 15, 33]
-
-#bbcolor = "#d9544d"	#light red
-bbcolor = "#75bbfd"
-mcolor = "#3c4142"
-
-#WASP-103b spectra
-path = "W103_spectra/"
-Ts = [1911., 2408., 2921.] 
-files = ["phase_0.10_wfc3.txt", "phase_0.25_wfc3.txt", "phase_0.5_wfc3.txt"]
-
-star = np.genfromtxt(path+"wasp103_sed_fluxes.out")
-star_wave = star[:,0]	#[microns]
-star_flux = star[:,1]	#[ergs/s/cm^2]	
-star_flux = star_flux/1.e3/star_wave	#[W/m^2/micron]
-star_flux = star_flux*2.1074e20		#scale by r^2/d^2, w/ rstar = 1.436 Rs, d = 470 pc (from exoplanet.eu)
-
-depth = 0.01195				#transit depth
-scale = 1.e5
-
-labels = ["nightside", "quadrature", "dayside"]
-
-for i, f in enumerate(files):
-	ax = plt.subplot(gs[i,0])
-
-	w = np.linspace(1.0, 1.8, 100)*1.e-6
-	T = Ts[i]
-	flux = blackbody(w, T)/scale
-	plt.plot(w*1e6, flux)
-    	plt.plot(w*1e6, flux, color = 'w', linewidth=0., label = labels[i])
-
-	d = np.genfromtxt(path+files[i]) 
-	w = d[:,0]
-	fs = np.interp(w, star_wave, star_flux)
-	fp = d[:,1]*fs/depth/scale		#divide by depth to account for difference in rp vs rs
-	fp_err = d[:,2]*fs/depth/scale
-	
[…]

### 2017-12-27 Figures/gcm_comparison.py

@@ -3,11 +3,23 @@ import numpy as np
 import os, glob
 from lc_fit import Model, LightCurveData
 import pickle
+import seaborn as sns
+from scipy.interpolate import interp1d
+
+sns.set_context("paper")
+sns.set_style("white")
+sns.set_style("ticks", {"xtick.direction":"in", "ytick.direction":"in"})
 
 gcm_path = "./Vivien_models2"
 gcms = glob.glob(os.path.join(gcm_path, "PC*PT.dat"))
 
-labels = ["NoTiO", "Drag1", "Drag2", "Drag3", "Met0.5", "TiO"]
+labels = ["$\\tau_\mathrm{drag} = 10^4$ s", "$\\tau_\mathrm{drag} = 10^3$ s", "[Fe/H] = 0.5", "nominal GCM"]
+
+plt.figure(figsize = (4, 2.5))
+
+#colors = ["#be0119", "#f97306", "#04d9ff", "#0165fc"]
+colors = ["#be0119", "#f97306", "#6dedfd", "#0165fc"]
+ls = [":", "--", "-.", "-"]
 
 
 def proj_area(phi, inc):
@@ -32,16 +44,25 @@ def proj_area(phi, inc):
 
 inc = 1.523
 
-plt.subplot(211)
 #plot gcms
 for i, g in enumerate(gcms):
     print g,
     model = np.genfromtxt(g, delimiter = ',') 
     phi = model[:,0]/360.*2.*np.pi
     area = proj_area(phi, inc)
-    plt.plot(model[:,0]/360. +0.5, model[:,5]*1e3, label = labels[i])
-    print (np.max(model[:,5]) - np.min(model[:,1]))*1e3
-    
+    plt.plot(model[:,0]/360. +0.5, model[:,5]*1e3*area, label = labels[i], color = colors[i], linestyle = ls[i])
+    ind = model[:,5] == np.max(model[:,5])
+
+    x, y = model[:,0]/360. + 0.5, model[:,5]
+    f = interp1d(x, y, kind = 'cubic')
+    xnew = np.linspace(0, 1, 1000)
+    ynew = f(xnew)
+    ind = ynew == np.max(ynew)
+    offset = xnew[ind]
+    print "hotspot offset", (offset - 0.5)*360.
+
+    #print "hotspot offset", model[ind,0]/360 + 0.5
+    #print (np.max(model[:,5]) - np.min(model[:,1]))*1e3
 
 
[…]

### 2017-12-27 Figures/hst_model_comparison.py

@@ -189,7 +189,7 @@ cb.set_label("Temperature (Kelvin)")
 models = ["spherical", "hotspot_t", 'zhang']
 path = "WFC3_best_fits/"
 waverange = [1.1e-6, 1.7e-6]                    #WFC3
-colors = ['#02ccfe', 'blue', '#ff7855'] 
+colors = ['#02ccfe', 'purple', '#ff7855'] 
 grays = ['0.7', '0.5', '0.6']
 labels = ["Sph. harmonics",  "Two temp.", "Kinematic"] 
 #linestyle = ['-', '-.', ':']

### 2017-12-27 Figures/spectra_comparison.py

@@ -4,7 +4,7 @@ import matplotlib.gridspec as gridspec
 from astropy import modeling
 import seaborn as sns
 
-sns.set_context("talk")
+sns.set_context("paper")
 sns.set_style("white")
 sns.set_style("ticks", {"xtick.direction":"in", "ytick.direction":"in"})
 
@@ -48,9 +48,10 @@ star_flux = star[:,1]	                        #[ergs/s/cm^2]
 star_flux = star_flux*(470/10.)**2		#convert to absolute flux (10 pc)
 
 labels = ["nightside", "quadrature", "dayside"]
-ylo = [0., 0.9, 3.]
-yhi = [1.1, 2.3, 4.3]
+ylo = [0., 0.9, 2.8]
+yhi = [1.15, 2.3, 4.3]
 
+plt.figure(figsize = (7.5, 3.5))
 #data_w, data, data_err; C; model_w, model
 
 for i, f in enumerate(files):
@@ -113,7 +114,7 @@ for i, f in enumerate(files):
     plt.xlim(1.0,1.75)
     plt.ylim(ylo[i], yhi[i])
 
-    if i != 2: plt.gca().set_xticks([])
+    if i != 2: plt.gca().set_xticklabels([])
     if i == 2: plt.xlabel("Wavelength (microns)")
     if i == 0 : plt.title("Brown dwarfs")	
 
@@ -148,7 +149,7 @@ for i, f in enumerate(files):
     plt.xlim(1.0,1.75)
     plt.ylim(ylo[i], yhi[i])
 
-    if i != 2: plt.gca().set_xticks([])
+    if i != 2: plt.gca().set_xticklabels([])
     if i == 0: plt.title("Imaged planets")
 
 #plt.tight_layout()

### 2017-12-27 Figures/test_unit_conversion.py

@@ -1,153 +1,0 @@
-import numpy as np
-import matplotlib.pyplot as plt
-import matplotlib.gridspec as gridspec
-from astropy import modeling
-import seaborn as sns
-
-sns.set_context("talk")
-sns.set_style("white")
-sns.set_style("ticks", {"xtick.direction":"in", "ytick.direction":"in"})
-
-def rescale(data, model):
-    ind = data > 1.e-20
-    data, model = data[ind], model[ind]
-    #data = np.ma.array(data, mask = ind)
-    scale = np.linspace(0.01, 10, 1000.)
-    chi2best, scalebest = 1.e10, -1.
-    for s in scale:
-        chi2 = np.sum((data - model*s)**2)
-        if chi2 < chi2best:
-                chi2best = chi2
-                scalebest = s
-    return scalebest
-
-
-gs = gridspec.GridSpec(3, 3, hspace=0.1, wspace=0.3)
-C = 1.e10                               #normalization constant for plotting
-
-#WASP-103b spectra
-path = "W103_spectra/"
-#Ts = [1911., 2408., 2921.] 
-Ts = [1922., 2408., 2982.]
-files = ["phase_0.10_wfc3.txt", "phase_0.25_wfc3.txt", "phase_0.5_wfc3.txt"]
-
-star = np.genfromtxt(path+"wasp103_sed_fluxes.out")
-star_wave = star[:,0]	                        #[microns]
-star_flux = star[:,1]	                        #[ergs/s/cm^2]	
-star_flux = star_flux*(470/10.)**2		#convert to absolute flux (10 pc)
-
-
-labels = ["nightside", "quadrature", "dayside"]
-
-for i, f in enumerate(files):
-	ax = plt.subplot(gs[i,0])
-
-	d = np.genfromtxt(path+files[i]) 
-        fs = np.interp(d[:,0], star_wave, star_flux)
-	fp = d[:,1]*fs
-	fp_err = d[:,2]*fs
-	
-        plt.errorbar(d[:,0], fp*C, yerr = fp_err*C, fmt = '.k', zorder=100)
-	
-    	#plt.plot(w, fp, linewidth = 0., label = str(Ts[i])+ " K")
-
-        w = np.linspace(1, 1.75, 20)
[…]

### 2017-12-28 ms.tex
gcm

@@
 \includegraphics[width = 1.0\textwidth]{Figures/hst_model_comparison.pdf}
-\caption{Left: fits to the broadband WFC3 phase curve. Right: best fit temperature maps.}
+\caption{\textbf{Left:} fits to the broadband WFC3 phase curve compared to a GCM.
+The colored lines correspond to different temperature maps fit to the data, and the dashed gray line is from the $\tau_\mathrm{drag} = 10^3$ GCM.
+We also show the planet-to-star flux corresponding to each map (points).
+The planet-to-star flux is model-dependent due to slight degeneracies with the instrument systematic model.
+\textbf{Right:} temperature maps from the best fit models and the GCM at 0.1 bar.}
 \label{fig:model_comparison}
@@
 We include opacity from the major absorbers expected for a hot Jupiter atmosphere, including H$_2$O, CO, CO$_2$, TiO, and VO (\textbf{Mike: what others?}).
-Notably, in contrast to many previous studies of the hottest planets, we also included opacity from H-, which is expected because water dissociates at dayisde photospheric temperature and pressure (3000 K, 0.1 bar).
+Notably, in contrast to many previous studies of the hottest planets, we also included opacity from H-, which is expected because water dissociates at dayside photospheric temperature and pressure (3000 K, 0.1 bar).
 Using these opacities and T-P profiles, we calculated thermal emission spectra over the full grid using the CHIMERA retrieval suite.
@@
 The drag models also provide a good match to the observed dayside flux, for drag timescales in the range $\tau_\mathrm{drag} = 10^3 - 10^4$ s.
-However, the drag models underestimate the flux at longitudes away from the substellar point, predicting a flux FIXME less than what is observed.
+However, the drag models underestimate the flux at longitudes away from the substellar point, predicting 20\% less flux than is observed at quadrature.
 \textbf{Vivien: are these fast drag timescales even reasonable?}).
 
-Water dissociation!
+We also compared the GCM output to the temperature maps retrieved with \texttt{spiderman}.
+Figure\,\ref{fig:model_comparison} shows the 0.1 bar temperature map for the $\tau_\mathrm{drag} = 10^3$ GCM compared to the best it models.
+The GCM has a minimum and maximum temperature of $920$ and $3360$ K, which is most comparable to the fit from the spherical harmonic model.
+The GCM nightside temperatures are around $300$ K cooler than the spherical harmonics fit,
+
+. The polar regions are the most discrepant, with temperatures are about $1000$ K cooler in the GCM than the spherical harmonics model.
+
+The GCMs also provide insight into what molecules are present in which parts of the atmosphere.
+As discussed in \S\,\ref{sec:composition}, water dissociation and H- opacity are needed to explain the dayside emission spectrum.
+Figure\,\ref{fig:gcmcomposition} shows the photospheric abundances of H$_2$O and H- compared to the predicted temperature for the $\tau_\mathrm{drag} = 10^3$ GCM.
+The water abundance drops by $\sim10$ at the substellar point, and the H- opacity increases by $\sim100$.
+
+\textbf{Vivien: did you run a cloudy model?}
 
@@
 
-%\begin{figure}
-%	\includegraphics[width = 1.0\textwidth]{WASP-103b-Solar-NoClouds-Photo-abundances-Water-CO-4.5microns-smooth.pdf}
-%\caption{Water.}
-%\label{fig:dayside}
-%\end{figure}
+\begin{figure*}
+	\includegraphics[width = 1.0\textwidth]{Figures/GCM_abundances.eps}
+\caption{Abundances of key molecular species for different viewing geometries, from the $\tau_\mathrm{drag} = 10^3$ GCM.}
+\label{fig:GCMabundance}
+\end{figure*}
 

### 2017-12-28 ms.tex
clean up

@@
 	\tablecaption{Model Comparison \label{table:models}}
-	\tablehead{
-	\colhead{Data} & \colhead{Model} & \colhead{$T_\mathrm{min}$} & \colhead{$T_\mathrm{max}$} & \colhead{$\Delta_\mathrm{AIC}$} & \colhead{$\Delta_\mathrm{BIC}$}}
+	\tablehead{\colhead{Data} & \colhead{Model} & \colhead{$T_\mathrm{min}$} & \colhead{$T_\mathrm{max}$} & \colhead{$\Delta_\mathrm{AIC}$} & \colhead{$\Delta_\mathrm{BIC}$}}
 		\startdata
@@
 \includegraphics[width = 1.0\textwidth]{Figures/emission_spectra.pdf}
-\caption{Phase-resolved emission spectra (points) compared to the best fit blackbody (blue line) and the FIXME GCM.
+\caption{Phase-resolved emission spectra (points) compared to the best fit blackbody (blue line) and the GCM with $\tau_\mathrm{drag} = 10^3$ s.
 Phases $\phi = 0.5$ and $0.0$ are centered on the substellar and anti-stellar points, respectively.}
@@
 \includegraphics[width = 1.0\textwidth]{Figures/hst_model_comparison.pdf}
-\caption{\textbf{Left:} fits to the broadband WFC3 phase curve compared to a GCM.
+\caption{\textbf{Left:} Fits to the broadband WFC3 phase curve compared to a GCM.
 The colored lines correspond to different temperature maps fit to the data, and the dashed gray line is from the $\tau_\mathrm{drag} = 10^3$ GCM.
-We also show the planet-to-star flux corresponding to each map (points).
-The planet-to-star flux is model-dependent due to slight degeneracies with the instrument systematic model.
-\textbf{Right:} temperature maps from the best fit models and the GCM at 0.1 bar.}
+We also show the planet-to-star flux corresponding to each map (points), which is model-dependent due to slight degeneracies with the instrument systematic model.
+\textbf{Right:} Temperature maps from the best fit models and the GCM at 0.1 bar.}
 \label{fig:model_comparison}
@@
 
-\begin{deluxetable*}{llllllllllll}
-\tablecolumns{12}
+\begin{deluxetable*}{lllllllllll}
+	\tablecolumns{11}
 	\tablewidth{0pt}:
@@
 	\tablehead{
-\colhead{$\lambda$} & \colhead{Dilution} & \colhead{0.1} & \colhead{0.2} & \colhead{0.3} & \colhead{0.4} & \colhead{0.6} & \colhead{0.7} & \colhead{0.8} & \colhead{0.9} & \colhead{X} & \colhead{Y}}
+	\colhead{$\lambda$} & \colhead{Dilution} & \colhead{$\phi = 0.1$} & \colhead{$\phi = 0.2$} & \colhead{$\phi = 0.3$} & \colhead{$\phi = 0.4$} & \colhead{$\phi = 0.5$} & \colhead{$\phi = 0.6$} & \colhead{$\phi = 0.7$} & \colhead{$\phi = 0.8$} & \colhead{$\phi = 0.9$}}
 		\startdata
-1.175 & 0.10 & $ 179 \pm 79 $ & $ 411 \pm 77 $ & $ 647 \pm 80 $ & $ 1143 \pm 65 $ & $ -15 \pm 66 $ & $ 142 \pm 67 $ & $ 1063 \pm 64 $ & $ 710 \pm 73 $ & $ 412 \pm 78 $ & $ 177 \pm 79 $ \\ 
-1.225 & 0.11 & $ 188 \pm 76 $ & $ 398 \pm 74 $ & $ 928 \pm 77 $ & $ 1276 \pm 62 $ & $ 120 \pm 64 $ & $ 42 \pm 65 $ & $ 1216 \pm 62 $ & $ 888 \pm 71 $ & $ 539 \pm 75 $ & $ 280 \pm 76 $ \\ 
-1.275 & 0.11 & $ 166 \pm 76 $ & $ 379 \pm 74 $ & $ 869 \pm 77 $ & $ 1323 \pm 62 $ & $ 139 \pm 64 $ & $ -8 \pm 65 $ & $ 1282 \pm 62 $ & $ 814 \pm 71 $ & $ 515 \pm 75 $ & $ 247 \pm 76 $ \\ 
-1.325 & 0.11 & $ 266 \pm 75 $ & $ 432 \pm 73 $ & $ 904 \pm 76 $ & $ 1357 \pm 62 $ & $ 4 \pm 63 $ & $ 144 \pm 64 $ & $ 1267 \pm 61 $ & $ 925 \pm 70 $ & $ 552 \pm 74 $ & $ 333 \pm 75 $ \\ 
-1.375 & 0.12 & $ 189 \pm 81 $ & $ 514 \pm 78 $ & $ 928 \pm 82 $ & $ 1376 \pm 66 $ & $ 131 \pm 67 $ & $ 52 \pm 68 $ & $ 1411 \pm 65 $ & $ 954 \pm 75 $ & $ 461 \pm 79 $ & $ 292 \pm 81 $ \\ 
-1.425 & 0.13 & $ 238 \pm 79 $ & $ 532 \pm 76 $ & $ 1198 \pm 79 $ & $ 1431 \pm 64 $ & $ 40 \pm 66 $ & $ 185 \pm 66 $ & $ 1511 \pm 64 $ & $ 1063 \pm 73 $ & $ 605 \pm 77 $ & $ 338 \pm 79 $ \\ 
-1.475 & 0.14 & $ 191 \pm 81 $ & $ 527 \pm 79 $ & $ 1068 \pm 82 $ & $ 1460 \pm 66 $ & $ 90 \pm 68 $ & $ 105 \pm 69 $ & $ 1392 \pm 66 $ & $ 1090 \pm 75 $ & $ 580 \pm 80 $ & $ 268 \pm 81 $ \\ 
-1.525 & 0.14 & $ 143 \pm 84 $ & $ 478 \pm 81 $ & $ 1048 \pm 85 $ & $ 1429 \pm 69 $ & $ 103 \pm 70 $ & $ 88 \pm 71 $ & $ 1367 \pm 68 $ & $ 943 \pm 77 $ & $ 607 \pm 82 $ & $ 291 \pm 84 $ \\ 
-1.575 & 0.15 & $ 367 \pm 88 $ & $ 761 \pm 85 $ & $ 1088 \pm 89 $ & $ 1581 \pm 72 $ & $ 96 \pm 73 $ & $ 125 \pm 74 $ & $ 1503 \pm 71 $ & $ 1107 \pm 81 $ & $ 754 \pm 86 $ & $ 422 \pm 88 $ \\ 
-1.625 & 0.16 & $ 359 \pm 93 $ & $ 565 \pm 90 $ & $ 1169 \pm 94 $ & $ 1590 \pm 76 $ & $ 45 \pm 78 $ & $ 181 \pm 79 $ & $ 1593 \pm 75 $ & $ 1142 \pm 86 $ & $ 542 \pm 91 $ & $ 351 \pm 93 $ \\ 
-3.6 & 0.17 & $ 1148 \pm 333 $ & $ 3633 \pm 330 $ & $ 4487 \pm 320 $ & $ 4107 \pm 314 $ & $ 661 \pm 324 $ & $ 373 \pm 324 $ & $ 3495 \pm 315 $ & $ 3720 \pm 330 $ & $ 2102 \pm 331 $ & $ 1431 \pm 334 $ \\
-4.5 & 0.16 & $ 1586 \pm 220 $ & $ 3468 \pm 214 $ & $ 4188 \pm 190 $ & $ 5334 \pm 179 $ & $ 466 \pm 200 $ & $ 757 \pm 200 $ & $ 4904 \pm 183 $ & $ 3626 \pm 214 $ & $ 2575 \pm 217 $ & $ 1057 \pm 221 $ \\
+		1.175 & 0.10 & $ 179 \pm 79 $ & $ 411 \pm 77 $ & $ 647 \pm 80 $ & $ 1143 \pm 65 $ & $ 1259 \pm 47 $ & $ 1063 \pm 64 $ & $ 710 \pm 73 $ & $ 412 \pm 78 $ & $ 177 \pm 79 $ \\ 
+		1.225 & 0.11 & $ 188 \pm 76 $ & $ 398 \pm 74 $ & $ 928 \pm 77 $ & $ 1276 \pm 62 $ & $ 1448 \pm 46 $ & $ 1216 \pm 62 $ & $ 888 \pm 71 $ & $ 539 \pm 75 $ & $ 280 \pm 76 $ \\ 
+		1.275 & 0.11 & $ 166 \pm 76 $ & $ 379 \pm 74 $ & $ 869 \pm 77 $ & $ 1323 \pm 62 $ & $ 1480 \pm 46 $ & $ 1282 \pm 62 $ & $ 814 \pm 71 $ & $ 515 \pm 75 $ & $ 247 \pm 76 $ \\ 
+		1.325 & 0.11 & $ 266 \pm 75 $ & $ 432 \pm 73 $ & $ 904 \pm 76 $ & $ 1357 \pm 62 $ & $ 1498 \pm 45 $ & $ 1267 \pm 61 $ & $ 925 \pm 70 $ & $ 552 \pm 74 $ & $ 333 \pm 75 $ \\ 
+		1.375 & 0.12 & $ 189 \pm 81 $ & $ 514 \pm 78 $ & $ 928 \pm 82 $ & $ 1376 \pm 66 $ & $ 1611 \pm 48 $ & $ 1411 \pm 65 $ & $ 954 \pm 75 $ & $ 461 \pm 79 $ & $ 292 \pm 81 $ \\ 
+		1.425 & 0.13 & $ 238 \pm 79 $ & $ 532 \pm 76 $ & $ 1198 \pm 79 $ & $ 1431 \pm 64 $ & $ 1718 \pm 47 $ & $ 1511 \pm 64 $ & $ 1063 \pm 73 $ & $ 605 \pm 77 $ & $ 338 \pm 79 $ \\ 
+		1.475 & 0.14 & $ 191 \pm 81 $ & $ 527 \pm 79 $ & $ 1068 \pm 82 $ & $ 1460 \pm 66 $ & $ 1667 \pm 48 $ & $ 1392 \pm 66 $ & $ 1090 \pm 75 $ & $ 580 \pm 80 $ & $ 268 \pm 81 $ \\ 
+		1.525 & 0.14 & $ 143 \pm 84 $ & $ 478 \pm 81 $ & $ 1048 \pm 85 $ & $ 1429 \pm 69 $ & $ 1623 \pm 50 $ & $ 1367 \pm 68 $ & $ 943 \pm 77 $ & $ 607 \pm 82 $ & $ 291 \pm 84 $ \\ 
+		1.575 & 0.15 & $ 367 \pm 88 $ & $ 761 \pm 85 $ & $ 1088 \pm 89 $ & $ 1581 \pm 72 $ & $ 1749 \pm 52 $ & $ 1503 \pm 71 $ & $ 1107 \pm 81 $ & $ 754 \pm 86 $ & $ 422 \pm 88 $ \\ 
+		1.625 & 0.16 & $ 359 \pm 93 $ & $ 565 \pm 90 $ & $ 1169 \pm 94 $ & $ 1590 \pm 76 $ & $ 1843 \pm 56 $ & $ 1593 \pm 75 $ & $ 1142 \pm 86 $ & $ 542 \pm 91 $ & $ 351 \pm 93 $ \\ 
+		3.6 & 0.17 & $ 1148 \pm 333 $ & $ 3633 \pm 330 $ & $ 4487 \pm 320 $ & $ 4107 \pm 314 $ & $ 4458 \pm 383 $ & $ 3495 \pm 315 $ & $ 3720 \pm 330 $ & $ 2102 \pm 331 $ & $ 1431 \pm 334 $ \\ 
+		4.5 & 0.16 & $ 1586 \pm 220 $ & $ 3468 \pm 214 $ & $ 4188 \pm 190 $ & $ 5334 \pm 179 $ & $ 5686 \pm 138 $ & $ 4904 \pm 183 $ & $ 3626 \pm 214 $ & $ 2575 \pm 217 $ & $ 1057 \pm 221 $ \\ 
 		\enddata
@@
 \includegraphics[width = 0.5\textwidth]{Figures/dayside_spectrum.pdf}
-\caption{Dayside emission spectrum.}
+\caption{Dayside emission spectrum (points) compared to the best fit 1-D model (blue line) with $1\,\sigma$ uncertainty shaded in orange. We also show a blackbody model (fit to the WFC3 data only).}
 \label{fig:dayside}
@@
 The spherical harmonics model has an intermediate temperature gradient, and fits the data the best.
-However, this model may not be physically realistic: on the nightside, it produces higher temperatures at the poles than at the equator, contrary to predictions from GCM (FIXME define?) simulations.
+However, this model may not be physically realistic: on the nightside, it produces higher temperatures at the poles than at the equator, contrary to predictions from GCMs (which we discuss in \S\,\ref{sec:gcm}).
 
-The typical uncertainty is FIXME (run MCMC, say the systematic range is larger than the error bars).
+%The typical uncertainty is FIXME (run MCMC, say the systematic range is larger than the error bars).
 
@@
 The best fit effective temperatures range from 1920 Kelvin on the nightside to 2980 Kelvin on the dayside.
-We report the best fit temperatures with uncertainties in Table\,\ref{tab:depths}.
+We report the best fit temperatures with uncertainties in Table\,\ref{table:teffs}.
 The dayside spectrum is the poorest fit by the blackbody model.
@@
 
+\begin{deluxetable}{lll}
+	\tablecolumns{3}
+	\tablewidth{0pt}:
+	\tablecaption{Phase-resolved Effective Temperature \label{table:teffs}}
+	\tablehead{
+	\colhead{Phase} & \colhead{Effective Temperature} & \colhead{$\chi^2_\nu$}}
+		\startdata
+		0.1 & $ 1919 \pm 40 $ & 0.6 \\
+		0.2 & $ 2256 \pm 24 $ & 0.8 \\
+		0.3 & $ 2651 \pm 17 $ & 1.2 \\
+		0.4 & $ 2906 \pm 11 $ & 0.8 \\
+		0.5 & $ 3013 \pm 8 $ & 1.6 \\
+		0.6 & $ 2885 \pm 12 $ & 1.3 \\
+		0.7 & $ 2636 \pm 16 $ & 0.9 \\
+		0.8 & $ 2313 \pm 23 $ & 1.1 \\
+		0.9 & $ 2027 \pm 36 $ & 0.5 \\
+		\enddata
+		\vspace{-0.8cm}
+		\tablecomments{comments}
+	\end{deluxetable}
 %Over the WFC3 bandpass, the phase-resolved spectra are featureless and consistent with blackbodies (with best fit $\chi^2_\nu$ ranging from $0.5-1.3$).
@@
 \subsection{Comparison with GCMs}
+\label{sec:gcm}
 To explore the three-dimensional effects of atmospheric dynamics, we ran several GCM models to compare with the measured phase-resolved spectra. (\textbf{Vivien: paragraph describing GCM}).

### 2017-12-28 Figures/phased_espec.py

@@ -22,7 +22,7 @@ def blackbody(l,T):
         return 2*h*c**2/(l**5*(np.exp(h*c/(l*k*T))-1))                 #[W/sr/m^3]
 
 def best_fit_bb(w, y, e, rprs):
-	Ts = np.linspace(300, 3600, 300)
+	Ts = np.linspace(1900, 3600, 10000)
 	chibest = 10000.
 	Tbest = 0.	
 	Tstar = 6110.
@@ -37,17 +37,23 @@ def best_fit_bb(w, y, e, rprs):
 	#get stellar spectrum
 	star = np.genfromtxt("wasp103_sed_fluxes.out")
 	star_bb = np.interp(w, star[:,0], star[:,1])*1.e24/(w*np.pi*4.)
+        chis = []
 
 	for T in Ts:
 		model = blackbody(w*1.0e-6, T)/star_bb*rprs**2
 		chi2 = np.sum((y - model)**2/e**2)
+                chis.append(chi2)
 		if chi2 < chibest: 
 			chibest, Tbest, resid = chi2, T, (y - model)/e
 	waves_hires = np.linspace(1.0, 5.0, 100)
 	star_bb_hires = np.interp(waves_hires, star[:,0], star[:,1])*1.e24/(waves_hires*np.pi*4.)
 
 	outfile = open("temperatures.txt", "a")
-	print "T, chi2", Tbest, chibest/(len(y) - 1)#, resid
+
+        idx = (np.abs(chis-(chibest+1.))).argmin()
+        onesigma = Tbest - Ts[idx]
+       # print "T, chi2", Tbest, "+/-", onesigma, chibest/(len(y) - 1)#, resid
+        print '{0:d}'.format(int(Tbest)),  '{0:d}'.format(int(np.abs(onesigma))), '{0:0.1f}'.format(chibest/(len(y) - 1)),
 	print>>outfile,  Tbest
 	outfile.close()
 	return waves_hires, blackbody(waves_hires*1.0e-6, Tbest)/star_bb_hires*rprs**2
@@ -222,10 +228,12 @@ for i in range(1, k):
 
                 if counter < 5: 
                     plt.plot(GCM[:,0], GCM[:,counter]*1e3, color = 'r')
-                    print counter, phase
+                    #print counter, phase
+                    print phase
                 else: 
                     plt.plot(GCM[:,0], GCM[:,counter+1]*1e3, color = 'r', label = 'GCM')
-                    print counter + 1, phase
[…]

### 2017-12-28 ms.tex
comparison

@@
 \includegraphics[width = 0.5\textwidth]{Figures/dayside_spectrum.pdf}
-\caption{Dayside emission spectrum (points) compared to the best fit 1-D model (blue line) with $1\,\sigma$ uncertainty shaded in orange. We also show a blackbody model (fit to the WFC3 data only).}
+\caption{Dayside emission spectrum (points) compared to the best fit 1-D model (blue line) with $1\,\sigma$ uncertainty shaded in orange.
+We also show the best fit blackbody (fit to the WFC3 data only).}
 \label{fig:dayside}
@@
 
-\subsection{Comparison with GCMs}
+\section{Comparison with GCMs}
 \label{sec:gcm}
@@
 
-\section{Comparison with Brown Dwarfs and Directly Imaged Planets}
+\section{Comparison with Brown Dwarfs and Directly Imaged Companions}
 WASP-103b is so highly irradiated that its photospheric temperature ($2000 - 3000$ K) is comparable to that of low mass stars.
-However, it is heated asymmetrically, its rotation rate is FIXME faster, and its surface gravity is lower.
-To assess the effects of these comparative study with other objects of similar temperature, including field brown dwarfs and young directly imaged companions.
+However, the planet's other properties (surface gravity, rotation rate, irradiation) are different.
+To explore the effects of varying these parameters, we compared the spectra of WASP-103b to brown dwarfs and young directly imaged companions.
 
-Sample of directly imaged planets
+We selected spectra from WASP-103b at three orbital phases: dayside ($\phi = 0.5$), quadrature ($\phi = 0.25$), and nightside ($\phi = 0.1$), and compared them to sources with comparable effective temperature.
+Figure\,\ref{fig:planetstarcomparison} shows the flux-calibrated spectra (assuming a distance of 10 pc).
+
+The directly imaged spectra are taken from \cite{2008ApJ...689L.153L}, \cite{2010ApJ...719..497L}, \cite{2010A&A...512A..52B}, \cite{2011ApJ...729..139W} , \cite{2014A&A...562A.127B}, \cite{2011ApJ...730...42L}, \cite{2013ApJ...773...63A}, \cite{2016A&A...587A..56M}, \cite{2013ApJ...772...79A}, and \cite{2008ApJ...673L.185B}.
+They are calibrated\footnote{Apart for PZ Tel B whose flux calibration is detailed in \cite{2016A&A...587A..56M}.}in absolute flux using published H-band photometry \citep{2008ApJ...689L.153L, 2014A&A...562A.127B, 2011ApJ...729..139W, 2005A&A...430.1027C, 2011ApJ...730...42L, 2013ApJ...773...63A, 2003tmc..book.....C,2009A&A...506..799B} and distances \cite{2016A&A...595A...1G, 2007A&A...474..653V, 1999AJ....117..354D, 1999AJ....117.2381P}, a flux-calibrated spectrum of Vega \citep{1985A&A...151..399M, 1985IAUS..111..225H}, and the corresponding filter passbands.
+The brown dwarf spectra \textbf{Jackie: describe catalog of brown dwarf spectra and flux calibration}.
+
+The main spectral feature over the wavelength range we consider is water.
+To quantitatively compare the water feature amplitude for different objects, we define an amplitude $A = (R_\mathrm{1.3} - R_\mathrm{1.5})/F_\mathrm{1.3}$, where $F_\mathrm{X}$ is the average flux in a wavelength bin $0.1\,\mu$m wide centered on a wavelength $X$, and $R_\mathrm{X}$ is the bin-averaged residual from the best fit blackbody.
+These intervals were chosen such that all of the data have complete spectral coverage over the bin.
+
+%DI companions: 1RXSJ160929.1-210524b, J1610-1913B, TWA22A
+%Age, logg, teff
+%WASP-103b - logg = 3.2
 

### 2017-12-28 Figures/spectra_comparison.py

@@ -8,6 +8,12 @@ sns.set_context("paper")
 sns.set_style("white")
 sns.set_style("ticks", {"xtick.direction":"in", "ytick.direction":"in"})
 
+def weighted_mean(data, err):                #calculates the weighted mean for data points data with variances err
+        weights = 1.0/err
+        mu = np.sum(data*weights)/np.sum(weights)
+        var = 1.0/np.sum(weights)
+        return [mu, var]                #returns weighted mean and variance
+
 def get_blackbody_model(model_w, data_w, data, T):
     unit_conversion = 1.2533e19                                        #(10 pc/jupiter radius)^2
 
@@ -36,6 +42,8 @@ gs = gridspec.GridSpec(3, 3, hspace=0.1, wspace=0.3)
 #plotting parameters
 C = 1.e10                                               #normalization constant for plotting
 model_w = np.linspace(1, 1.75, 20)
+#l1, l2, l3, l4 = 1.15, 1.35, 1.4, 1.55
+l1, l2, l3, l4 = 1.3, 1.34, 1.51, 1.55
 
 #WASP-103b spectra
 path = "W103_spectra/"
@@ -54,6 +62,7 @@ yhi = [1.15, 2.3, 4.3]
 plt.figure(figsize = (7.5, 3.5))
 #data_w, data, data_err; C; model_w, model
 
+print "W103b"
 for i, f in enumerate(files):
     ax = plt.subplot(gs[i,0])
 
@@ -70,6 +79,8 @@ for i, f in enumerate(files):
     #fit blackbody model
     model = get_blackbody_model(model_w, data_w, data, Ts[i])
     plt.plot(model_w, model*C, color = '0.5', linestyle = 'dotted', zorder  = -1)
+    plt.fill_betweenx(np.linspace(ylo[i], yhi[i], 3), l1, l2, color = '0.9', zorder = -20)
+    plt.fill_betweenx(np.linspace(ylo[i], yhi[i], 3), l3, l4, color = '0.9', zorder = -20)
 
     #labels and axes
     plt.legend(loc = 'upper right', handlelength = 0., frameon=False)
@@ -80,6 +91,12 @@ for i, f in enumerate(files):
 
     if i != 2: plt.gca().set_xticklabels([])
[…]

### 2017-12-29 Figures/H2Oamp_table.py
table

@@ -1,0 +1,32 @@
+import numpy as np
+
+h2o_amp = np.genfromtxt("h2o_amp_1.15_1.3_1.35_1.55.txt")
+amp = h2o_amp[:,0]
+amp_e = h2o_amp[:,1]
+
+print "\\begin{deluxetable}{llllll}"
+print "\\tablecolumns{6}"
+print "\\tablewidth{0pt}:"
+print "\\tablecaption{Water feature amplitude \label{table:h2o_amp}}"
+print "\\tablehead{"
+print "\colhead{\,} & \colhead{Object} & \colhead{$T_\mathrm{eff}$} & \colhead{logg} & \colhead{Wide Amp} & \colhead{Narrow Amp}}"
+print "\startdata"
+
+names = ["W103b night", "W103b quadrature", "W103b dayside", "1320+0409", "0428-2253", "0003-2822", "1RXSJ160929.1", "J1610-1913B", "TWA22A"]
+objects = ["Hot Jupiter", "\,", "\,", "Brown Dwarf", "\,", "\,", "Imaged Companion", "\,", "\,"]
+Teff = [1922, 2408, 2982, 1875, 2429, 2889, 1800, 2400, 3000]
+Teff_e = [0, 0, 0, 70, 80, 80, 0, 0, 0] 
+logg = [3.20, 3.20, 3.20, 5.19, 5.22, 5.18, 0, 0, 0]
+logg_e = [0.04, 0.04, 0.04, 0.16, 0.09, 0.04, 0, 0, 0]
+
+#category (e.g. "BDs"), object, H2O amp1, H2O amp2, teff, logg, rotation period?
+
+n = 9           #nine objects
+
+for i in range(n): print objects[i], "&", names[i], "&", "$", int(Teff[i]), "\\pm", int(Teff_e[i]), "$", "&", "$", logg[i], "\\pm", logg_e[i], "$", "&", "$", amp[i], "\\pm", amp_e[i], "$", "&", "$", amp[i], "\\pm", amp_e[i], "$",  "\\\\"
+
+print "\enddata"
+print "\\vspace{-0.8cm}"
+print "\\tablecomments{comments}"
+print "\end{deluxetable}"
+

### 2017-12-29 Figures/spectra_comparison.py

@@ -42,8 +42,8 @@ gs = gridspec.GridSpec(3, 3, hspace=0.1, wspace=0.3)
 #plotting parameters
 C = 1.e10                                               #normalization constant for plotting
 model_w = np.linspace(1, 1.75, 20)
-#l1, l2, l3, l4 = 1.3, 1.34, 1.51, 1.55
-l1, l2, l3, l4 = 1.15, 1.32, 1.36, 1.55
+l1, l2, l3, l4 = 1.2, 1.34, 1.49, 1.65
+#l1, l2, l3, l4 = 1.15, 1.3, 1.35, 1.55
 
 #WASP-103b spectra
 path = "W103_spectra/"
@@ -100,8 +100,8 @@ for i, f in enumerate(files):
     A, A_err = weighted_mean(data[ind1], data_err[ind1])
     B, B_err  = weighted_mean(data[ind2], data_err[ind2])
     modelmeanA, modelmeanB = np.mean(model[ind1_m]), np.mean(model[ind2_m])
-    A, B = A - modelmeanA.value, B - modelmeanB.value
-    print "amplitude", '{0:0.4f}'.format((A - B)/A), '{0:0.4f}'.format(np.abs(B/A)*np.sqrt((A_err/A)**2 + (B_err/B)**2))
+    #A, B = A - modelmeanA.value, B - modelmeanB.value
+    print '{0:0.4f}'.format((A - B)/A), '{0:0.4f}'.format(np.abs(B/A)*np.sqrt((A_err/A)**2 + (B_err/B)**2))
 
 #Brown dwarf spectra
 
@@ -152,8 +152,8 @@ for i, f in enumerate(files):
     A, A_err = weighted_mean(data[ind1], data_err[ind1])
     B, B_err  = weighted_mean(data[ind2], data_err[ind2])
     modelmeanA, modelmeanB = np.mean(model[ind1_m]), np.mean(model[ind2_m])
-    A, B = A - modelmeanA.value, B - modelmeanB.value
-    print "amplitude", '{0:0.4f}'.format((A - B)/A), '{0:0.4f}'.format(np.abs(B/A)*np.sqrt((A_err/A)**2 + (B_err/B)**2))
+    #A, B = A - modelmeanA.value, B - modelmeanB.value
+    print '{0:0.4f}'.format((A - B)/A), '{0:0.4f}'.format(np.abs(B/A)*np.sqrt((A_err/A)**2 + (B_err/B)**2))
 
[…]

### 2017-12-29 ms.tex
table

@@
 
+\begin{figure}
+\includegraphics[width = 0.5\textwidth]{Figures/xsec_FULL.pdf}
+\caption{Opacities.}
+\label{fig:opacities}
+\end{figure}
+
+\subsubsection{Dayside Spectrum}
+
 The TiO/VO absorption heats the upper atmosphere, resulting in a thermal inversion.
@@
 To explore the effects of varying these parameters, we compared the spectra of WASP-103b to brown dwarfs and young directly imaged companions.
+The object properties are summarized in Table\,\ref{tab:sources}.
 
@@
 
-The directly imaged spectra are taken from \cite{2008ApJ...689L.153L}, \cite{2010ApJ...719..497L}, \cite{2010A&A...512A..52B}, \cite{2011ApJ...729..139W} , \cite{2014A&A...562A.127B}, \cite{2011ApJ...730...42L}, \cite{2013ApJ...773...63A}, \cite{2016A&A...587A..56M}, \cite{2013ApJ...772...79A}, and \cite{2008ApJ...673L.185B}.
-They are calibrated\footnote{Apart for PZ Tel B whose flux calibration is detailed in \cite{2016A&A...587A..56M}.}in absolute flux using published H-band photometry \citep{2008ApJ...689L.153L, 2014A&A...562A.127B, 2011ApJ...729..139W, 2005A&A...430.1027C, 2011ApJ...730...42L, 2013ApJ...773...63A, 2003tmc..book.....C,2009A&A...506..799B} and distances \cite{2016A&A...595A...1G, 2007A&A...474..653V, 1999AJ....117..354D, 1999AJ....117.2381P}, a flux-calibrated spectrum of Vega \citep{1985A&A...151..399M, 1985IAUS..111..225H}, and the corresponding filter passbands.
+%TWA 22A - Bonnefoy+2014 (Bonnefoy 09), RXS - Lafren 08,10 (H magfrom Lafren 08), J1610 - Aller+13
+%dist: teixeira08, 
+The directly imaged spectra are taken from \cite{wahhaj11, aller13, bonnefoy14}.
+They are calibrated in absolute flux using published H-band photometry \citep{wahhaj11, bonnefoy09, aller13} and distances \citep{gaia16}, a flux-calibrated spectrum of Vega \citep{1985A&A...151..399M, 1985IAUS..111..225H}, and the corresponding filter passbands.
 The brown dwarf spectra \textbf{Jackie: describe catalog of brown dwarf spectra and flux calibration}.
@@
 
+\begin{deluxetable*}{llCCCC}
+	\tablecolumns{6}
+	\tablewidth{0pt}:
+	\tablecaption{Source Properties \label{table:sources}}
+	\tablehead{
+	\colhead{\,} & \colhead{Object} & \colhead{$T_\mathrm{eff}$} & \colhead{logg} & \colhead{H$_2$O A$_1$} & \colhead{H$_2$O A$_2$}}
+		\startdata
+		Hot Jupiter & W103b night & 1922 \pm 40 & 3.2 \pm 0.04 & 0.07 \pm 1.8\mathrm{e}-01 & -0.00 \pm 1.6\mathrm{e}-01 \\
+		\, & W103b quadrature & 2408 \pm 20 & 3.2 \pm 0.04 & -0.14 \pm 7.8\mathrm{e}-02 & -0.01 \pm 6.7\mathrm{e}-02 \\
+		\, & W103b dayside & 2982 \pm 10 & 3.2 \pm 0.04 & 0.04 \pm 1.4\mathrm{e}-02 & 0.15 \pm 1.2\mathrm{e}-02 \\
+		Brown Dwarf & 2MASS J1320+0409 & 1875 \pm 70 & 5.19 \pm 0.16 & 0.21 \pm 6.3\mathrm{e}-04 & -0.06 \pm 5.0\mathrm{e}-04 \\
+		\, & 2MASS J0428-2253 & 2429 \pm 80 & 5.22 \pm 0.09 & 0.16 \pm 1.2\mathrm{e}-04 & -0.03 \pm 1.0\mathrm{e}-04 \\
+		\, & 2MASS J0003-2822 & 2889 \pm 80 & 5.18 \pm 0.04 & 0.26 \pm 1.3\mathrm{e}-04 & 0.10 \pm 1.1\mathrm{e}-04 \\
+		Imaged Companion & CD-35 2722\tablenotemark{3} & 1800 \pm 100 & 4.5 \pm 0.5 & - & 0.15 \pm 1.0\mathrm{e}-05 \\
+		\, & USco 1610-1913B\tablenotemark{2} & 2400 \pm 150 & - & 0.27 \pm 2.0\mathrm{e}-04 & 0.19 \pm 2.2\mathrm{e}-04 \\
+		\, & TWA 22A\tablenotemark{3} & 3000 \pm 100 & 4.5 \pm 0.5 & - & 0.29 \pm 2.0\mathrm{e}-05 \\
+		\enddata
+	\tablenotetext{1}{\cite{wahhaj11}}
+	\tablenotetext{2}{\cite{aller13}}
+	\tablenotetext{3}{\cite{bonnefoy14}}
+	\end{deluxetable*}
+
 \section{Discussion and Conclusions}

### 2017-12-29 ms.tex
intro

@@
 \section{Introduction} \label{sec:intro}
-The planets and moons of the Solar System possess a rich variety of -- weather, temperature var
+The planets and moons of the Solar System are complex systems, with differences in climate and atmospheric composition.
 
-It is a truism to say that planets are round.
+Tidally locked exoplanets are an extreme example of this variation, with a hot, continuously irradiated dayside and a much colder nightside.
+
+a wide range of climate, weather, topography, atmospheres mediating the exchange of radiation
+
+%It is a truism to say that planets are round.
 The.
@@
 
-It is a challenge is to reveal this structure at great distances, when we cannot spatially resolve the photosphere of the planet.
-Most observations of exoplanet atmospheres are sensitive to a single isolated region  -- either the terminator, for transmission spectroscopy, or the disk-integrated dayside, for emission spectroscopy.
-The solution to this problem is to observe phase curves of tidally-locked planets, which monitor the brightness of the planet over its entire orbit.
-As the orbital phase changes, the observer
+It is a challenge is to reveal this structure for exoplanets at great distances, when we cannot spatially resolve the photosphere.
+Most observations of exoplanet atmospheres use techniques that are sensitive to one average region  -- either the terminator, for transmission spectroscopy, or the disk-integrated dayside, for emission spectroscopy.
 
-The first phase curve was observed with \Spitzer\ for the hot Jupiter HD 189733b by \citep{knutson??}, and was followed by FIXME more (with IRAC).
+The solution to this problem is to observe phase curves of tidally-locked planets, which monitor the brightness of the planet over its entire orbit. As the orbital phase changes, the observer
+
+The first phase curve was observed with \Spitzer\ for the hot Jupiter HD 189733b by \citep{knutson07}, which revealed a modest day-night temperature contrast of 300 Kelvin
+
+and was followed by FIXME more (with IRAC).
 Several trends emerged from these measurements, including eastward shifted hotspots (which suggest super-rotating equatorial jets), larger day-night temperature contrast for shorter period planets (ref), .
@@
 
-In this paper we present \HST\ and \Spitzer\ phase curve observations of WASP-103b, a hot Jupiter with a mass of X, radius of Y, period of Z (cite discovery paper).
+Thermal emission spectra of other super-hot Jupiters
+
+WASP-103b is an ideal candidate for phase curve observations, with an orbital period of just FIXME hours \citep{gillon14}.
+Its equilibrium temperature is FIXME K, .
+The atmosphere of WASP-103b has been characterized with transmission and emission spectroscopy \citep{southworth16, cartier17, lendl17}.
+The thermal emission spectrum is featureless
+
+In this paper we present the spectroscopic phase curve observations of WASP-103b. Our data observed with \HST/WFC3  
+%, a hot Jupiter with a mass of X, radius of Y, period of Z (cite discovery paper).
 These properties are similar to WASP-43b, except that WASP-103b has a much (FIXME vs FIXME K) thanks to its hot F??
@@
 
-%DI companions: 1RXSJ160929.1-210524b, J1610-1913B, TWA22A
-%Age, logg, teff
-%WASP-103b - logg = 3.2
-
-cite Tremblin et al. 2017 ? (https://arxiv.org/pdf/1710.02640.pdf)
-
 \begin{figure*}
@@
 		\, & 2MASS J0003-2822 & 2889 \pm 80 & 5.18 \pm 0.04 & 0.26 \pm 1.3\mathrm{e}-04 & 0.10 \pm 1.1\mathrm{e}-04 \\
-		Imaged Companion & CD-35 2722\tablenotemark{3} & 1800 \pm 100 & 4.5 \pm 0.5 & - & 0.15 \pm 1.0\mathrm{e}-05 \\
+		Imaged Companion & CD-35 2722\tablenotemark{1} & 1800 \pm 100 & 4.5 \pm 0.5 & - & 0.15 \pm 1.0\mathrm{e}-05 \\
 		\, & USco 1610-1913B\tablenotemark{2} & 2400 \pm 150 & - & 0.27 \pm 2.0\mathrm{e}-04 & 0.19 \pm 2.2\mathrm{e}-04 \\

### 2017-12-29 Figures/H2Oamp_table.py

@@ -8,7 +8,7 @@ amp2 = h2o_amp2[:,0]
 amp2_e = h2o_amp2[:,1]
 
 
-names = ["W103b night", "W103b quadrature", "W103b dayside", "2MASS J1320+0409", "2MASS J0428-2253", "2MASS J0003-2822", "CD-35 2722\\tablenotemark{3}", "USco 1610-1913B\\tablenotemark{2}", "TWA 22A\\tablenotemark{3}"]
+names = ["W103b night", "W103b quadrature", "W103b dayside", "2MASS J1320+0409", "2MASS J0428-2253", "2MASS J0003-2822", "CD-35 2722\\tablenotemark{1}", "USco 1610-1913B\\tablenotemark{2}", "TWA 22A\\tablenotemark{3}"]
 
 
 objects = ["Hot Jupiter", "\,", "\,", "Brown Dwarf", "\,", "\,", "Imaged Companion", "\,", "\,"]

### 2017-12-30 ms.tex
intro

@@
 \newcommand{\Spitzer}{\project{Spitzer}}
+\newcommand{\Kepler}{\project{Kepler}}
 
@@
 \begin{abstract}
-WASP-103b is a short-period hot Jupiter.
+	We present thermal phase curve measurements for the hot Jupiter WASP-103b observed with \emph{Hubble}/Wide Field Camera 3 and \emph{Spitzer}/IRAC.
+The dayside planet-to-star flux ranges from FIXME to FIXME at $1.1 - 4.5\,\mu$m.
+The phase curves are symmetric and large amplitude, indicative of poor heat redistribution.
+We fit the phase curves with the SPIDERMAN package to determine the brightness distribution in the photosphere, and find the peak dayside temperature ranges from FIXME to FIXME depending on model.
+We also generate phase-resolved spectra, which are consistent with blackbody models for the planet's emission at near-infrared wavelengths, but show strong emission features in the \Spitzer\ bands.
+We attribute these features to CO emission and a thermal inversion.
+The retrieved atmospheric composition is more metal-enriched than other hot Jupiters (FIXME).
+The carbon-to-oxygen ratio is consistent with solar composition.
+The absence of water features is due to BLAH.
+We compare the phase curves to general circulation models and find that atmospheric drag is required.
+We also compare the spectra to brown dwarfs and young directly imaged companions and find that the water features are significantly diminished in amplitude.
+power of phase curve observations to elucidate the three-dimensional structure of exoplanet atmospheres.
 \end{abstract}
@@
 \section{Introduction} \label{sec:intro}
-The planets and moons of the Solar System are complex systems, with differences in climate and atmospheric composition.
+Planets are round, rotating, and irradiated on one hemisphere at a time -- all of which contribute to rich spatial structure in their climate and atmospheric composition.
+Short period, tidally locked planets are an extreme example, with hot, continuously illuminated daysides.
+This asymmetry is expected to produce large gradients in temperature, chemistry, and cloud coverage with longitude \citep{showman09, kataria16, parmentier16}.
 
-Tidally locked exoplanets are an extreme example of this variation, with a hot, continuously irradiated dayside and a much colder nightside.
+Extrasolar planets are so distant that they are not spatially resolved, so the only way to reveal this variation is to measure a phase curve.
+Phase curve observations consist of continuous monitoring of the planet-to-star flux ratio over a complete orbital revolution of the planet, which exposes different longitudes at each orbital phase.
+The first phase curve was observed with \Spitzer\ for the hot Jupiter HD 189733b by \citep{knutson07}, followed by additional \Spitzer\ observations for about a dozen more systems \citep{parmentier17}.
+\Kepler\ enabled the first measurements of phase curves at optical wavelengths \citep[e.g.]{esteves15}.
+\cite{stevenson14} observed the first \emph{spectroscopic} phase curve for WASP-43b with \emph{Hubble}/Wide Field Camera 3 (\HST/WFC3) in the near-infrared.
+These observations had fairly good agreement with 3D GCM predictions, eastward-shifted peak brightness and more efficient heat redistribution for cooler planets.
+FIXME: say after Spitzer that results agree with GCM. Elaborate after esteves15 that the optical phase curves are sensitive to clouds.
 
-a wide range of climate, weather, topography, atmospheres mediating the exchange of radiation
+In this paper we present spectroscopic phase curve observations of the hot Jupiter WASP-103b.
+This planet is an ideal target for thermal phase curve observations, with an orbital period of 22 hours and an equilibrium temperature of 2500 K \citep{gillon14}.
+The dayside thermal emission of WASP-103b was detected by \cite{cartier17}
 
-%It is a truism to say that planets are round.
-The.
-And yet planets' roundness gives rise to a host of complications:  atmospheric circulation, variable , gradients in chemistry, cloud formation and evaporation, and time-dependent phenomena (weather).
-
-It is a challenge is to reveal this structure for exoplanets at great distances, when we cannot spatially resolve the photosphere.
-Most observations of exoplanet atmospheres use techniques that are sensitive to one average region  -- either the terminator, for transmission spectroscopy, or the disk-integrated dayside, for emission spectroscopy.
-
-The solution to this problem is to observe phase curves of tidally-locked planets, which monitor the brightness of the planet over its entire orbit. As the orbital phase changes, the observer
-
-The first phase curve was observed with \Spitzer\ for the hot Jupiter HD 189733b by \citep{knutson07}, which revealed a modest day-night temperature contrast of 300 Kelvin
-
-and was followed by FIXME more (with IRAC).
-Several trends emerged from these measurements, including eastward shifted hotspots (which suggest super-rotating equatorial jets), larger day-night temperature contrast for shorter period planets (ref), .
-The first spectroscopic phase curve was measured with Hubble's Wide Field Camera 3 (WFC3) by \citep{stevenson???} for the hot Jupiter WASP-43b.
-Found low albedo, offset hotspot, water visible at other phases,
-
-In parallel with these observations, there have been major advances in the theory of exoplanet atmospheres in three-dimensions.
-Global circulation models (GCMs) are now capable of self-consistent radiative transfer and atmospheric dynamics (refs) and are beginning to include clouds (refs?).
-
-In addition to GCMs, work on the inverse problem Cowan - how to get maps, .
-SPIDERMAN, an open-source Python package designed to take any temperature or brightness map of a planet and output the corresponding phase curve, so that we can readily connect GCMs to phase curve observations.
+	spin-orbit alignment: 2016ApJ...823...29A
 
@@
 
-WASP-103b is an ideal candidate for phase curve observations, with an orbital period of just FIXME hours \citep{gillon14}.
-Its equilibrium temperature is FIXME K, .
-The atmosphere of WASP-103b has been characterized with transmission and emission spectroscopy \citep{southworth16, cartier17, lendl17}.
-The thermal emission spectrum is featureless
+The atmosphere of WASP-103b has been characterized with transmission and emission spectroscopy \citep{southworth16, cartier17, lendl17}. The thermal emission spectrum is featureless
 
-In this paper we present the spectroscopic phase curve observations of WASP-103b. Our data observed with \HST/WFC3  
 %, a hot Jupiter with a mass of X, radius of Y, period of Z (cite discovery paper).
@@
 By comparing the phase curves of these two planets, we can test the effect of irradiation on the climate of the planet.
-
-Talk about other WFC3 papers (Star Cartier, etc)
-
-The structure of the paper is as follows:
 
@@
 
-How does composition compare to other HJs.
+How does composition compare to other HJs (esp W43b)
 The spectrum is similar to observations of several other ultra-hot Jupiters \citep[][]{arcangeli18, mansfield18}, but qualitatively different from slightly cooler planets, which show water absorption features in the near-infared \citep[e.g.][]{kreidberg14b, line16}.

### 2017-12-30 ms.tex
intro

@@
 This asymmetry is expected to produce large gradients in temperature, chemistry, and cloud coverage with longitude \citep{showman09, kataria16, parmentier16}.
-
+FIXME we want to understand this, heat circulation and atmospheric dynamics, and also to put transmission and emission spectra in context.
 Extrasolar planets are so distant that they are not spatially resolved, so the only way to reveal this variation is to measure a phase curve.
 Phase curve observations consist of continuous monitoring of the planet-to-star flux ratio over a complete orbital revolution of the planet, which exposes different longitudes at each orbital phase.
+
 The first phase curve was observed with \Spitzer\ for the hot Jupiter HD 189733b by \citep{knutson07}, followed by additional \Spitzer\ observations for about a dozen more systems \citep{parmentier17}.
-\Kepler\ enabled the first measurements of phase curves at optical wavelengths \citep[e.g.]{esteves15}.
+These observations revealed large day-night temperature contrasts (in excess of FIXME K), and eastward shifted peak brightness due to heat circulation.
+These measurements were complemented by optical phase curves from \Kepler\, which are sensitive to reflected light \citep[e.g.]{esteves15}.
+FIXME clouds.
 \cite{stevenson14} observed the first \emph{spectroscopic} phase curve for WASP-43b with \emph{Hubble}/Wide Field Camera 3 (\HST/WFC3) in the near-infrared.
 These observations had fairly good agreement with 3D GCM predictions, eastward-shifted peak brightness and more efficient heat redistribution for cooler planets.
-FIXME: say after Spitzer that results agree with GCM. Elaborate after esteves15 that the optical phase curves are sensitive to clouds.
 

### 2018-01-02 ms.tex
intro

--- 2017-12-30 ms.tex
@@
 power of phase curve observations to elucidate the three-dimensional structure of exoplanet atmospheres.
+
+inversion on the dayside but not on the nightside
 \end{abstract}
@@
 Short period, tidally locked planets are an extreme example, with hot, continuously illuminated daysides.
-This asymmetry is expected to produce large gradients in temperature, chemistry, and cloud coverage with longitude \citep{showman09, kataria16, parmentier16}.
+This asymmetry is expected to produce large gradients in temperature, chemistry, and cloud coverage with longitude \citep{showman09, kataria16, parmentier16}, and provides an opportunity to learn about atmospheric dynamics in a very different regime from the Solar System planets.
 
-Extrasolar planets are so distant that they are not spatially resolved, so the only way to reveal this variation is to measure a phase curve.
+Exoplanets are so distant that they are not spatially resolved, so the only way to reveal inhomogeneity in their atmospheres is to measure a phase curve.
 Phase curve observations consist of continuous monitoring of the planet-to-star flux ratio over a complete orbital revolution of the planet, which exposes different longitudes at each orbital phase.
-The first phase curve was observed with \Spitzer\ for the hot Jupiter HD 189733b by \citep{knutson07}, followed by additional \Spitzer\ observations for about a dozen more systems \citep{parmentier17}.
-\Kepler\ enabled the first measurements of phase curves at optical wavelengths \citep[e.g.]{esteves15}.
-\cite{stevenson14} observed the first \emph{spectroscopic} phase curve for WASP-43b with \emph{Hubble}/Wide Field Camera 3 (\HST/WFC3) in the near-infrared.
-These observations had fairly good agreement with 3D GCM predictions, eastward-shifted peak brightness and more efficient heat redistribution for cooler planets.
-FIXME: say after Spitzer that results agree with GCM. Elaborate after esteves15 that the optical phase curves are sensitive to clouds.
+The first phase curve was observed with \Spitzer\ for the hot Jupiter HD 189733b by \citep{knutson07}, followed by additional \Spitzer\ observations for about a dozen more systems \citep[cataloged in][]{parmentier17}.
+The observations revealed large day-night temperature contrasts (in excess of 300 K), and eastward shifted peak brightness due to heat circulation, as predicted by 3D models \citep{showman09}.
+These infrared measurements were complemented by optical phase curves from \Kepler\, which show evidence for reflected light from patchy and variable dayside clouds with a range of compositions \citep{demory13, hu15, armstrong16, parmentier16}.
+A \emph{spectroscopic} phase curve was observed for WASP-43b with \emph{Hubble}/Wide Field Camera 3 (\HST/WFC3) in the near-infrared, which provided the first phase-resolved measurements of an exoplanet's water abundance and thermal structure \citep{stevenson14, stevenson17}.
 
-In this paper we present spectroscopic phase curve observations of the hot Jupiter WASP-103b.
-This planet is an ideal target for thermal phase curve observations, with an orbital period of 22 hours and an equilibrium temperature of 2500 K \citep{gillon14}.
-The dayside thermal emission of WASP-103b was detected by \cite{cartier17}
+In this paper we present spectroscopic phase curve observations of the hot Jupiter WASP-103b, measured with \HST/WFC3 and Spitzer/IRAC.
+This planet is an ideal target for phase curve observations, with an orbital period of just 22 hours and an equilbrium temperature of 2500 K \citep{gillon14}.
+Previous observations of WASP-103b's atmosphere revealed a blackbody-like dayside emission spectrum, with possible evidence for a $K_\mathrm{S}$-band emission feature \citep{cartier17, delrez18}.
+The shape of the optical transmission spectrum is disputed, with some evidence for strong sodium and potassium absorption features that are consistent with expectations for a cloud-free atmosphere \citep{lendl17}, but other observations indicating a large optical scattering slope that is not fit well by theoretical models \citep{southworth16}.
 
-	spin-orbit alignment: 2016ApJ...823...29A
+WASP-103b is an archetype of the class of ultra-hot Jupiters (with dayside temperatures $>2000\,\mathrm{K}$).
+Observations of the near-IR thermal emission spectra of these objects have been puzzling: some show absorption features, some show emission features, and some are consistent with blackbody models \citep{madhusudhan11, crossfield12, stevenson14b, haynes15, evans16, beatty17a, beatty17b, }.
+A variety of explanations have been proposed, including low metallicity or carbon-to-oxygen ratios \citep{madhusudhan11, cartier17}, which would TiO/VO heating of the upper atmosphere, .
 
-Thermal emission spectra of other super-hot Jupiters
+Our phase-curve observations of provide the first 3D constraints on temperature structure of a planets.
 
-The atmosphere of WASP-103b has been characterized with transmission and emission spectroscopy \citep{southworth16, cartier17, lendl17}. The thermal emission spectrum is featureless
+%	spin-orbit alignment: 2016ApJ...823...29A
 
-%, a hot Jupiter with a mass of X, radius of Y, period of Z (cite discovery paper).
-These properties are similar to WASP-43b, except that WASP-103b has a much (FIXME vs FIXME K) thanks to its hot F??
-star host.
-By comparing the phase curves of these two planets, we can test the effect of irradiation on the climate of the planet.
+%are featureless (consistent with a blackbody model for the planet), others show water absorption features, and water emission \citep{evans16}.
+Isothermal in the near-IR \citep{crossfield12, stevenson14, }.
+Some have absortion features in near-IR \citep{kreidberg14b, line16}
+
+Fortney 08
+
+Phase curve observation to provide context for the global thermal structure of the planet.
 
@@
 We collected a total of 18 spatial scan exposures per orbit.
-The two eclipse observations from Program 13660 had a similar observing setup.
+The two eclipse observations from Program 13660 had a similar observing setup \citep[described in detail in][]{cartier17}.
 
@@
 The typical background counts are low (10-15 photoelectrons per pixel, roughly 0.03\% of the peak counts from the target star).
-We note that the extracted spectrum includes flux from a nearby star, which is separated from WASP-103 by less than two pixels \citep[0.2";][]{wollert15}.
+We note that the extracted spectrum includes flux from a nearby companion star, which is separated from WASP-103 by less than two pixels \citep[0.2";][]{wollert15}.
 Our extracted spectrum includes flux from this star, which we account for later in the analysis.
@@
 The data volume is relatively low for this exposure time, so we read out the full array.
-To minimize the intrapixel effect (variations in flux caused by imprecise pointing), we did not dither and also used PCRS peak-up to improve the pointing accuracy.
+To minimize the intrapixel effect (variations in flux caused by imprecise pointing), we did not dither and also used PCRS peak-up\footnote{\url{http://irsa.ipac.caltech.edu/data/SPITZER/docs/irac/pcrs\_obs.shtml}} to improve the pointing accuracy.
 We began each observations with a 30-minute position settling period, followed by three Astronomical Observation Requests (AORs) of equal duration.
@@
 We also performed a least-squares fit to the data to determine the best fit sine curve.
-The best fit period is 6.814 days, which agrees closely with the estimated stellar rotation period of 6.855 days \citep{getal2014}.
+The best fit period is 6.814 days, which agrees closely with the estimated stellar rotation period of 6.855 days \citep{gillon14}.
 The variability amplitude is 0.005~mag, which has FIXME impact on our analysis here.
@@
 Many of the physical parameters are tightly constrained by \cite{southworth15}, so we fixed the orbital period, time of inferior conjunction, orbital inclination, and ratio of semi-major axis to stellar radius to the previously published values ($P = 0.925545613$ day, $t_0 = 2456836.2964455\,\mathrm{BJD_{TDB}}$, $i = 87.3^\circ$, and $a/R_s = 2.999$).
-As a test, we fit for these parameters with the Spitzer Channel 2 light curve, which has the best phase coverage and least systematic noise of the three data sets.
+As a test, we fit for these parameters with the \Spitzer\ Channel 2 light curve, which has the best phase coverage and least systematic noise of the three data sets.
 We found that the transit parameters are consistent with the \cite{southworth15} results, so we proceeded with the remainder of the analysis holding those parameters fixed.
@@
 We estimated $\alpha(\lambda)$ based on the best fit spectral energy distribution from \cite{cartier17}.
-The companion star contributes $10-16\%$ of the flux over the wavelength range $1 - 5\,\mu$m.
-We calculated $A(t)$ using the analytic formula from \cite{leconte11b}, equation B.9, which computes the projected area of a triaxial ellipsoid.
+The companion star contribution ranges from $10\%$ at $1.1\,\mu$m to $16\%$ at $4.5\,\mu$m.
+(FIXME: what is the error?)  We calculated $A(t)$ using the analytic formula from \cite{leconte11b}, equation B.9, which computes the projected area of a triaxial ellipsoid.
 We estimated the ellipsoid properties using Table B.3 of \cite{leconte11a}, assuming the planet radius is 1.5 $R_\mathrm{Jup}$ and age is 5 Gyr.
@@
 The fitted light curves are shown in Figure\,\ref{fig:phasecurves}.
-This figure shows results from the kinematic model for the thermal phase variation and has instrument systematics removed.
+This figure shows results from the spherical harmonics model for the thermal phase variation and has instrument systematics removed.
 Broadly speaking, the phase curves show large amplitude phase variation, ranging from 1.5 parts-per-thousand (ppt) in the WFC3 bandpass to 5 ppt in \Spitzer\ Channel 2.
-The planet flux changes significantly with orbital phase in all three of the data sets, suggesting a strong gradient from dayside to nightside temperature.
-The peak brightness occurs near phase 0.5.
-In this section we discuss the quality
+The planet flux changes significantly with orbital phase in all three of the data sets, suggesting a strong gradient from dayside to nightside temperature, and peak brightness occurs near phase 0.5.
+In this section, we describe the phase curve fits and the phase-resolved spectra.
+FIXME
 
@@
 
+\subsection{Comparison with Previous Observations}
+Cartier, Delrez.
+
 \subsection{Hotspot Offset}
@@
 On the nightside (phase $0.9$), the \Spitzer\ $4.5\,\mu$m eclipse depth is \emph{smaller} than predicted, suggesting an absorption feature.
-These differences hint at changing thermal structure with longitude in the atmosphere.
+These differences suggest changing thermal structure with longitude in the atmosphere.
 
@@
 There are many factors contributing to the blackbody spectra --
-weak water xsec contrast, isothermal pt, H-, and dissociated water
+weak water xsec contrast, isothermal pt, H-, and dissociated water, gravity (cite T. Beatty)
 
@@
 
+eclipse mapping to break degeneracy in models
+
+We rule out the low metallicity and or high C/O models
+
+confirm prediction that TiO is present in the hottest planets
+
 \acknowledgments

### 2018-01-02 ms.tex
fixmes

@@
 The dayside planet-to-star flux ranges from FIXME to FIXME at $1.1 - 4.5\,\mu$m.
-The phase curves are symmetric and large amplitude, indicative of poor heat redistribution.
+The phase curves are symmetric and large amplitude, indicative of poor redistribution.
 We fit the phase curves with the SPIDERMAN package to determine the brightness distribution in the photosphere, and find the peak dayside temperature ranges from FIXME to FIXME depending on model.
@@
 Previous observations of WASP-103b's atmosphere revealed a blackbody-like dayside emission spectrum, with possible evidence for a $K_\mathrm{S}$-band emission feature \citep{cartier17, delrez18}.
-The shape of the optical transmission spectrum is disputed, with some evidence for strong sodium and potassium absorption features that are consistent with expectations for a cloud-free atmosphere \citep{lendl17}, but other observations indicating a large optical scattering slope that is not fit well by theoretical models \citep{southworth16}.
+The optical transmission spectrum shows evidence for strong sodium and potassium absorption features that are consistent with expectations for a cloud-free atmosphere \citep{lendl17}.%, though other observations have shown a large optical scattering slope that is not fit well by theoretical models \citep{southworth16}.
 
-WASP-103b is an archetype of the class of ultra-hot Jupiters (with dayside temperatures $>2000\,\mathrm{K}$).
-Observations of the near-IR thermal emission spectra of these objects have been puzzling: some show absorption features, some show emission features, and some are consistent with blackbody models \citep{madhusudhan11, crossfield12, stevenson14b, haynes15, evans16, beatty17a, beatty17b, }.
-A variety of explanations have been proposed, including low metallicity or carbon-to-oxygen ratios \citep{madhusudhan11, cartier17}, which would TiO/VO heating of the upper atmosphere, .
+WASP-103b is an archetype of the class of ultra-hot Jupiters (with orbital periods of about one day and dayside temperatures typically $>2000\,\mathrm{K}$).
+Observations of the thermal emission spectra of these objects have been puzzling.
+In the near-infrared, where water is the dominant absorber, some spectra show water absorption features, some show emission features, and some are consistent with blackbody models \citep{madhusudhan11, crossfield12, stevenson14b, haynes15, evans16, beatty17a, beatty17b, sheppard17, arcangeli18, mansfield18}.
+A variety of explanations were proposed for these results, including low metallicity or high carbon-to-oxygen compositions, dayside clouds, and isothermal or inverted temperature profiles caused by TiO/VO absorption in the upper atmosphere.
+Recently, \cite{arcangeli18} showed that water dissociation on the hot dayside plays an important role in the atmospheres of these ultra-hot planets and may be responsible for some of the blackbody-like near-IR spectra.
+In this work, we put these results in context investigate the global thermal structure of WASP-103b over a range of temperatures.
+FIXME
 
-Our phase-curve observations of provide the first 3D constraints on temperature structure of a planets.
+The structure of the paper is the following: in \S\,\ref{sec:observations} we describe the observations and data reduction.
+\S\,\ref{sec:fits} details the models fit to the phase curves.
+\S\,\ref{sec:results} we discuss results, including the phase-resolved spectra, a comparison of thermal phase variation models, and FIXME.
+In \S\,\ref{sec:gcm} and \ref{sec:comparison}, we compare the observations to GCM predictions and spectra from similar temperature stars and directly imaged companions.
+\S\,\ref{sec:discussion} concludes.
 
@@
 
-%are featureless (consistent with a blackbody model for the planet), others show water absorption features, and water emission \citep{evans16}.
-Isothermal in the near-IR \citep{crossfield12, stevenson14, }.
-Some have absortion features in near-IR \citep{kreidberg14b, line16}
+%Fortney 08
 
-Fortney 08
-
-Phase curve observation to provide context for the global thermal structure of the planet.
+%Phase curve observation to provide context for the global thermal structure of the planet.
 
 \section{Observations and Data Reduction}
+\label{sec:observations}
 We observed two full-orbit phase curves of WASP-103b with \HST/WFC3 and one each with \Spitzer/IRAC at 3.6 and 4.5 $\mu$m (from HST Program 14050 and Spitzer Program 11099).
@@
 The best fit period is 6.814 days, which agrees closely with the estimated stellar rotation period of 6.855 days \citep{gillon14}.
-The variability amplitude is 0.005~mag, which has FIXME impact on our analysis here.
+The variability amplitude is 0.005~mag.
+Based on the formalism in \cite{zellem17}, we calculate that this variability will bias the measured eclipse depth by $\lesssim10$\,ppm from epoch to epoch, which is well below the photon-limited precision of our measurements.
 
@@
 \section{Light Curve Fits}
+\label{sec:fits}
 We fit a two-component model to the light curves.
@@
 \begin{equation}
-	%F_\mathrm{physical}(\lambda, t) = F_s(\lambda) (1 + \alpha(\lambda)) \times T(\lambda, t) + F_p(\lambda, t) 
 	F_\mathrm{physical}(\lambda, t) =  T(\lambda, t) + c(\lambda, t) \times F_p/F_s(\lambda, t)
@@
 The companion star contribution ranges from $10\%$ at $1.1\,\mu$m to $16\%$ at $4.5\,\mu$m.
-(FIXME: what is the error?)  We calculated $A(t)$ using the analytic formula from \cite{leconte11b}, equation B.9, which computes the projected area of a triaxial ellipsoid.
+The uncertainty on the companion star flux contribution is less than 1\%, which introduces negligible error in the estimated planet-to-star-flux compared to the photon noise.
+We calculated $A(t)$ using the analytic formula from \cite{leconte11b}, equation B.9, which computes the projected area of a triaxial ellipsoid.
 We estimated the ellipsoid properties using Table B.3 of \cite{leconte11a}, assuming the planet radius is 1.5 $R_\mathrm{Jup}$ and age is 5 Gyr.
@@
 At quadrature, the projected radius is $8\%$ larger than at phase zero (mid-transit).
-%FIXME: say this doesn't matter.
-%In addition to temperature, the planet's visible surface area $[R(t)]^2$ is also expected to vary with orbital phase due to tidal distortion \citep{gillon14}.
-In the observed light curve, changes in planet radius are degenerate with changes in temperature.
-
-%We explored adding an additional sine term to model the thermal phase variation, but the additional degrees of freedom are not justified according to the Bayesian Information Criterion (BIC).
-
-%Our light curves are not precise enough to detect the ellipsoidal variability, but we include a model prediction $E(t)$ to avoid introducing any bias in the thermal phase variation.
-We model $E(t)$ using the analytic expression from \cite{leconte11}, which
-%FIXME doppler beaming?
+We also considered the effects of Doppler beaming and found that it contributes less than 10 ppm variability to the measured flux \citep{loeb03}.
 
@@
 For $4.5\,\mu$m, the scale was 0.022 pixel.
-
 In addition to the intrapixel sensitivity variation, we fit the data for a linear trend in time.
@@
 
-As discussed in \S \ref{sec:fitquality}, the 3.6 $\mu$m light curve exhibits time correlated noise.
+%As discussed in \S \ref{sec:fitquality}, the 3.6 $\mu$m light curve exhibits time correlated noise.
 To account for this additional source of error, we fit the wavelet model from \cite{carter09} (simultaneously with the other fit parameters).
-FIXME: describe wavelets.
+We fit
+%We explored adding an additional sine term to model the thermal phase variation, but the additional degrees of freedom are not justified according to the Bayesian Information Criterion (BIC).
 
@@
 \section{Results}
+\label{sec:results}
 The fitted light curves are shown in Figure\,\ref{fig:phasecurves}.
@@
 There are a number of possible origins for this discrepancy, including imperfect background subtraction, variation in the position of the spatial scan on the detector, loss of flux outside the extraction window, and imperfect modeling of the astrophysical signal or instrument systematics.
-However, our analysis of the composition and thermal structure of the planet's atmosphere is based on the wavelength-dependent data (which reach the photon limit), so we do not further explore the small excess noise in the white light curve.
+However, our analysis of the composition and thermal structure of the planet's atmosphere is based on the wavelength-dependent data (where we reach the photon limit), so we do not further explore the small excess noise in the white light curve.
 
@@
 Both \Spitzer\ channels use the same detector, but Channel 1 data are more susceptible to time-correlated noise because the the point spread function is narrower at shorter wavelengths, making intrapixel sensitivity variations more pronounced.
-
-The reduced $\chi^2$ values for the fits are near unity. FIXME when you have them all.
-%Third, we calculated several goodness of fit statistics. $\chi^2$, AIC, BIC.
 
@@
 
-. The polar regions are the most discrepant, with temperatures are about $1000$ K cooler in the GCM than the spherical harmonics model.
+. The polar regions are the most discrepant, with temperatures are about $1000$ K cooler in the GCM than the spherical harmonics model. FIXME
 
@@
 The nominal model is solar composition, cloud-free, with TiO/VO opacity and no drag.
-The models are multiplied by the predicted ellipsoidal variability of the planet.}
+The models are corrected for the predicted ellipsoidal variability of the planet.}
 \label{fig:gcmcomparison}
@@
 \section{Comparison with Brown Dwarfs and Directly Imaged Companions}
+\label{sec:comparison}
 WASP-103b is so highly irradiated that its photospheric temperature ($2000 - 3000$ K) is comparable to that of low mass stars.
@@
 \section{Discussion and Conclusions}
+\label{sec:discussion}
 One-dimensional retrieval is probably wrong, since we showed the dayside may have a large temperature gradient -> should work on this in the future.

### 2018-01-03 ms.tex
clean up retrieval section

@@
 Cambridge, MA 02138}
-\nocollaboration
 
@@
 \affiliation{Department of Planetary Sciences and Lunar and Planetary Laboratory, The University of Arizona}
-\nocollaboration
 
@@
 \affiliation{Arizona State University}
-\nocollaboration
 
@@
 \affiliation{Space Telescope Science Institute}
-\nocollaboration
 
@@
 \affiliation{University of Warwick}
-\nocollaboration
 
@@
 \affiliation{Universit\'{e} Grenoble Alpes}
-\nocollaboration
 
@@
 \affiliation{American Museum of Natural History}
-\nocollaboration
 
@@
 \affiliation{Center of Excellence in Information Systems, Tennessee State University}
-\nocollaboration
 
@@
 \affiliation{Vanderbilt University}
-\nocollaboration
 
@@
 \affiliation{University of Chicago}
-\nocollaboration
 
@@
 \affiliation{University of California Santa Cruz}
-\nocollaboration
 
@@
 	\tablecolumns{11}
-	\tablewidth{0pt}:
+	\tablewidth{0pt}
 	\tablecaption{Phase-Resolved Emission Spectra \label{table:spectra}}
@@
 \subsection{Comparison with Previous Observations}
-Cartier, Delrez.
+We compared our results to the dayside emission spectrum reported by \cite{cartier17}, which is based on a Gaussian process analysis of two secondary eclipses from \HST/WFC3.
+The shape of their spectrum is consistent with what we find, but their eclipse depths are 125 ppm smaller on average.
+In their analysis, \cite{cartier17} noted that the Gaussian process fit produces smaller eclipse depths than a parametric fit (also by 125 ppm).
+One explanation for this difference is that the Gaussian process models some of the astrophysical signal.
+If the planet's thermal phase variation is absorbed into the instrument systematic model, the measured eclipse depths would be lower by about 100 ppm.
+Since our analysis accounts for the thermal phase variation, it is more likely to provide a robust estimate of the secondary eclipse depths.
+Our estimated uncertainties are a factor of four smaller than those reported in \cite{cartier17}, which is consistent with photon-limited expectations (our data set includes two additional eclipses, a factor of five longer out-of-eclipse baseline, and has 60\% larger wavelength bins).
+
+We also compared our dayside spectrum to the $z'$ and $K_\mathrm{S}$-band secondary eclipse depths reported in \cite{delrez18}.
+The $z'$ eclipse is $1.0\,\sigma$ lower than our best fit blackbody spectrum (described in \S\,\ref{sec:composition}), and the $K_\mathrm{S}$ measurement is higher than the model by $2.5\,\sigma$.
+Since these results are consistent with (but less precise than) the WFC3 data, we do not include them in our analysis of the atmospheric composition, but we encourage additional measurements in the $K_\mathrm{S}$ band to confidently determine whether an emission feature is present at those wavelengths.
 
@@
 At other phases the blackbody model is a poorer fit, particularly to the \Spitzer\ data.
-For phases $0.2 - 0.6$, the \Spitzer\ eclipse depths are larger than predicted for the best fit blackbody, suggesting the presence of an emission feature.
+For phases $0.2 - 0.6$, the \Spitzer\ eclipse depths are significantly larger than predicted for the best fit blackbody, suggesting the presence of an emission feature.
 On the nightside (phase $0.9$), the \Spitzer\ $4.5\,\mu$m eclipse depth is \emph{smaller} than predicted, suggesting an absorption feature.
-These differences suggest changing thermal structure with longitude in the atmosphere.
+These differences indicate changes in thermal structure with longitude in the atmosphere.
 
@@
 This finding is not a surprise because the dayside has higher signal-to-noise than the other orbital phases, thanks to the two secondary eclipse observations from \cite{cartier17}.
-The more sophisticated grid-based retrieval provides a better fit to the dayside.
+The more sophisticated grid-based retrieval (described in the next section) provides a better fit to the dayside.
 
@@
 \subsection{Grid-Based Retrieval}
-Since the phase-resolved spectra do not show spectrally resolved molecular features, we opted for a simple grid-based fit to the planet's atmospheric properties, similar to the grid search used in Mansfield et al.
-and Arcangeli et al.
-(in prep).
+Since the phase-resolved spectra do not show spectrally resolved molecular features, we opted for a simple grid-based fit to the planet's atmospheric properties, similar to the grid search used in \cite{arcangeli18, mansfield18}.
 We generated a grid from one-dimensional forward models of the atmosphere over a broad range of metallicities, carbon-to-oxygen ratios (C/O), and stellar irradiation.
@@
 At each point in the grid, we compute forward models to determine self-consistent, radiative-convective temperature-pressure (T-P) profiles.
-We determine the molecular abundances in each atmospheric layer assuming thermochemical equilibrium.
-We include opacity from the major absorbers expected for a hot Jupiter atmosphere, including H$_2$O, CO, CO$_2$, TiO, and VO (\textbf{Mike: what others?}).
-Notably, in contrast to many previous studies of the hottest planets, we also included opacity from H-, which is expected because water dissociates at dayside photospheric temperature and pressure (3000 K, 0.1 bar).
-Using these opacities and T-P profiles, we calculated thermal emission spectra over the full grid using the CHIMERA retrieval suite.
-We then explored the grid with an MCMC chain using the \texttt{emcee} package \citep{foremanmackey13}, and interpolated in the grid to calculate the likelihood at each model step.
+(\textbf{Mike: citations?}) We determine the molecular abundances in each atmospheric layer assuming thermochemical equilibrium \citep[calculated with the NASA CEA routine;][]{gordon94}.
+We include opacity from the major absorbers expected for a hot Jupiter atmosphere, including H$_2$O, CO, CO$_2$, TiO, VO, FeH, and H$_2$-H$_2$ CIA.
+Notably, in contrast to many previous studies of the hottest planets, we also included opacity from H-, which is an important absorber at temperatures above 2500 K \citep{arcangeli18}.
+Using these opacities and T-P profiles, we calculated thermal emission spectra over the full grid using the CHIMERA retrieval suite \citep[described in][]{line13a, line14}.
+We then explored the grid with an MCMC chain using the \texttt{emcee} package \citep{foremanmackey13} and interpolated in the grid to calculate the likelihood at each model step.
 We fit this model to the dayside and nightside emission spectra (phases $\phi = 0.5$ and $0.1$).
@@
 \caption{Posterior distributions for WASP-103b's atmospheric heat redistribution, metallicity, and C/O, from a grid-based fit to the dayside emission spectrum.
-The histograms on the diagonal show the marginalized distribution of each parameter, with dashed lines indicating the median and surrounding 68\% confidence interval.
-\textbf{Mike: what percentiles does the colored shading correspond to?} The blue lines correspond to solar metallicity (1) and C/O (0.54).}
+The histograms on the diagonal show the marginalized distribution of each parameter, with dashed lines indicating the median and surrounding 68\% credible interval.
+The blue lines correspond to solar metallicity (1) and C/O (0.54).
+The 2D histograms mark the 1, 2, and 3$\,\sigma$ credible regions in dark, medium, and light blue, respectively.}
 \label{fig:composition}
@@
 The best fit spectrum reproduces these data fairly well, with $\chi^2_\nu$ = 1.77.
-The WFC3 and Spitzer $3.6\,\mu$m points are fit better ($\chi^2_\nu$  = 1.17 for these data alone), but the $4.5\,\mu$m point is higher than the best fit model by $2.9\,\sigma$.
+The largest contribution to the $\chi^2$ value is the $4.5\,\mu$m eclipse depth, which is larger than the best fit model prediction by $2.9\,\sigma$.
+When the $4.5\,\mu$m point is removed, the fit has $\chi^2_\nu = 1.17$.
 The best fit model has a moderately enhanced metallicity ($23\times$ solar), carbon-to-oxygen equal to 0.76, poor heat redistribution, and a thermal inversion (temperature increasing with altitude).
@@
 Figure\,\ref{fig:opacities} shows the opacity contributions of key absorbers for the best fit.
-In the optical (which we do not observe directly), there is strong absorption by TiO/VO.
-In the near-infrared, the dominant absorbers are H$_2$O and H-.
-The observed spectrum is featureless at these wavelengths, due to a combination of factors: water is partially dissociated in the photosphere, leading to a drop in abundance of FIXME.
-It also produces H- opacity (single H atoms bind with free electrons), which dominates spectral features from H$_2$O at wavelengths shorter than FIXME $\mu$m.
-Water is also an efficient coolant, so lower water abundance leads to a more isothermal photosphere and weakens the features even more.
+In the optical (which we do not observe directly), there is strong absorption by TiO, VO, and FeH.
+In the near-infrared, the H$_2$O, H-, and hydrides/oxides all contribute to the opacity, leading to nearly constant opacity over the WFC3 wavelength range.
+In cooler atmospheres, water is the dominant absorber over this bandpass, but in WASP-103b, H$_2$O is partially dissociated in the photosphere, leading to a drop in abundance by a factor of $\sim10$ (see Figure\,\ref{fig:summary}).
+Water also has intrinsically weaker features at high temperature \citep{tinetti12}.
+Finally, water is an efficient coolant, so lower water abundance leads to a more isothermal photosphere, which further weakens the contrast in and out of the water band in the observed spectrum.
+On top of this, there is significant H- opacity from single H atoms bound with free electrons, which fills in the opacity at wavelengths shorter than $1.5\,\mu$m.
 Taken together, all these factors conspire to produce a nearly featureless spectrum from $1.1 - 1.7\,\mu$m.
@@
 \includegraphics[width = 0.5\textwidth]{Figures/xsec_FULL.pdf}
-\caption{Opacities.}
+\caption{Abundance weighted absorption cross-sections illustrating the important opacity sources at the photospheric pressure level (5 mbar).
+The strong CO feature at 4.5\,$\mu$m contributes to the high planet-to-star flux at that wavelength.
+Water, hydrides/oxides, and the H- bound-free opacities all play a role in shaping the \HST/WFC3 spectrum.}
 \label{fig:opacities}
@@
 
-\subsubsection{Dayside Spectrum}
-
-The TiO/VO absorption heats the upper atmosphere, resulting in a thermal inversion.
-Figure\,\ref{fig:TP} shows a selection of 100 randomly selected dayside T-P profiles.
+Figure\,\ref{fig:summary} shows a summary of the temperature-pressure profile and abundances for the best fit model.
+The T-P profile is inverted, with temperature increasing from 2800 to 3500 K over the pressure range $10^{-2} - 10^{-3}$ bar.
+The  thermal inversion is driven by absorption of optical light by oxides and hydrides in the upper atmosphere.
+The contribution functions FIXME
+%Figure\,\ref{fig:TP} shows a selection of 100 randomly selected dayside T-P profiles.
 The profiles are nearly isothermal over a pressure range of $1-10^{-2}$ bars, with a median temperature near 2900 Kelvin.
 The temperature increases over $10^{-2} - 10^{-3}$ bars to 3500 Kelvin, and then begins to decrease again at pressures below $10^{-3}$ bar.
-(\textbf{Mike: what are the contribution functions?}).
 
@@
 Poor heat transport is observed in other very hot planets as well, due to damping of heat-propagating waves by fast radiative cooling or frictional drag in a partially ionized atmosphere \citep{komacek16}.
-The heat redistribution is correlated with atmospheric metallicity (\textbf{Mike: why is this?}).
+The heat redistribution is correlated with atmospheric metallicity because increasing metallicity pushes the photosphere to higher, cooler pressure levels (\textbf{Mike: does this make sense, since the atmosphere has a thermal inversion?}).
 
@@
 \begin{figure}
-\includegraphics[width = 0.5\textwidth]{Figures/TP.pdf}
-\caption{Dayside temperature-pressure profiles from the grid retrieval (red lines) compared to the profile from the substellar point for the FIXME GCM.}
-\label{fig:TP}
+\includegraphics[width = 0.5\textwidth]{Figures/atmosphere_summary.pdf}
+\caption{Summary of the 1D self-consistent model atmosphere fits.
+The temperature-pressure profile (top axis) is indicated by the 1-sigma spread of 500 randomly drawn T-P profiles from the posterior (light red) and a representative fit, with $f$=0.4, [M/H]=1.5, and C/O=0.7 (dark red).
+The normalized thermal emission contribution functions for the \Spitzer\ points are shown in solid red, the WFC3 in-water band ($1.33-1.48\,\mu$m) in dark blue, and WFC3 out-of-water-band in light blue.
+The observations probe between $\sim0.01$ and 0.001 bar, just above the tropopause region of the atmosphere where the temperature is increasing.
+The dashed curves are thermochemical equilibrium mixing ratios for important absorbers computed along the representative fit's self-consistent T-P profile.
+Note the rapid dissociation of water above the $\sim10$ mbar level where the inversion begins.}
+\label{fig:summary}
 \end{figure}
@@
 \acknowledgments
-We thank a lot of people. Caroline Morley, Thomas Beatty, Ming Zhao, Kim Star Cartier, Hannah Diamond-Lowe, Nick Cowan (make him a coauthor?)
+Some of the data presented in this paper were obtained from the Mikulski Archive for Space Telescopes (MAST).
+STScI is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS5-26555.
+Support for MAST for non-HST data is provided by the NASA Office of Space Science via grant NNX13AC07G and by other grants and contracts.
+This work also made use of the Python packages  SciPy and NumPy \citep{jones_scipy_2001, van2011numpy}.
+The authors are grateful for helpful conversations with Caroline Morley, Thomas Beatty, Ming Zhao, Kim Star Cartier, Hannah Diamond-Lowe, and Nick Cowan.
+We also thank the organizers of the 2016 Santa Cruz Kavli Summer Program and the 2017 Ringberg Atmospheres of Disks and Planets meeting for facilitating many discussions and collaborations.
 

### 2018-01-04 ms.tex
amplitudes/offsets

@@
 
-\subsection{Hotspot Offset}
+\subsection{Phase Curve Amplitude and Hotspot Offset}
 The location of peak brightness of the phase curve is a proxy for the efficiency of thermal reradiation to space and relative to heat transport by advection (the radiative-to-advective timescale).

### 2018-01-04 ms.tex
amps/offs

@@
 We also show the planet-to-star flux corresponding to each map (points), which is model-dependent due to slight degeneracies with the instrument systematic model.
-\textbf{Right:} Temperature maps from the best fit models and the GCM at 0.1 bar.}
+\textbf{Right:} Temperature maps from the best fit models and the GCM at 0.1 bar.
+FIXME say here what the temperature difference is at substellar point.}
 \label{fig:model_comparison}
@@
 
+FIXME what is the weighted mean amplitude and offset for the WFC3 data? are they all consistent?
+
+\begin{deluxetable}{LLL}
+	\tablecolumns{3}
+	\tablewidth{0pt}:
+	\tablecaption{Phase Curve Properties \label{table:amps_offsets}}
+	\tablehead{
+	\colhead{Wavelength} & \colhead{Amplitude} & \colhead{Offset}}
+		\startdata
+		1.175 & 0.89 \pm 0.17 & -0.3 \pm 1.3 \\
+		1.225 & 1.11 \pm 0.27 & -1.8 \pm 1.3 \\
+		1.275 & 0.88 \pm 0.17 & 1.1 \pm 1.4 \\
+		1.325 & 0.92 \pm 0.17 & 0.6 \pm 1.4 \\
+		1.375 & 0.82 \pm 0.14 & 1.8 \pm 1.5 \\
+		1.425 & 0.91 \pm 0.16 & 1.6 \pm 1.4 \\
+		1.475 & 0.83 \pm 0.13 & 2.5 \pm 1.4 \\
+		1.525 & 1.04 \pm 0.19 & 0.3 \pm 1.2 \\
+		1.575 & 0.99 \pm 0.19 & -0.3 \pm 1.3 \\
+		1.625 & 0.86 \pm 0.18 & -1.8 \pm 1.2 \\
+		\enddata
+	\end{deluxetable}
+
 %\subsection{Clouds?}
-
 \section{Atmospheric Composition and Thermal Structure}

### 2018-01-04 ms.tex
amp off

--- 2018-01-03 ms.tex
@@
 
+\subsection{Best Fits and Uncertainties}
+To determine the best fits, we performed a least-squares $\chi^2$ minimization for each wavelength and model.
+For a subset of these cases, we also performed a Markov chain Monte Carlo (MCMC) analysis to estimate parameter uncertainties.
+We used \texttt{emcee} \citep{foremanmackey13} to fit the \HST/WFC3 light curves and differential evolution Monte Carlo for the \Spitzer\ fits \citep{braak06}.
+We ran the MCMC until convergence according to the Gelman-Rubin statistic FIXME.
+MCMC techniques only produce robust uncertainties when the noise is normally distributed and white, so to account for correlated noise in the $3.6\,\mu$m light curve we fit the wavelet model from \cite{carter09} (simultaneously with the other model parameters).
+We used a Haar wavelet and let the power spectral density of the red noise vary, following \cite{diamond-lowe14}.
+In our final fit, the noise power spectrum $1/f^\gamma$ had $\gamma = 1.1 \pm 0.1$.
+
 \begin{figure*}
@@
 The expected photon-limited rms for the WFC3 spectrosopic light curves ranges from 430 - 530 parts per million (ppm), and the measured rms was typically within 5\% of expectations for all spectroscopic channels.
-For the WFC3 band- integrated white light curve, the rms was slightly larger than predicted (175 versus 122 ppm).
+For the WFC3 band-integrated white light curve, the rms was slightly larger than predicted (175 versus 122 ppm).
 There are a number of possible origins for this discrepancy, including imperfect background subtraction, variation in the position of the spatial scan on the detector, loss of flux outside the extraction window, and imperfect modeling of the astrophysical signal or instrument systematics.
@@
 
-\subsection{Hotspot Offset}
-The location of peak brightness of the phase curve is a proxy for the efficiency of thermal reradiation to space and relative to heat transport by advection (the radiative-to-advective timescale).
-The faster the reradiation, the less heat can be redistributed to the nightside.
-We compared the measured hotspot offset for the different models and found FIXME.
+\subsection{Phase Curve Amplitudes and Hotspot Offsets}
+The shape of a phase curve can be summarized with two parameters: the amplitude of thermal phase variation (minimum to maximum brightness, divided by the secondary eclipse depth) and the location of peak brightness (typically called a ``hotspot offset" and measured in degrees eastward of the substellar point).
+Larger amplitudes and smaller offsets are both indicative of inefficient heat transport to the nightside.
+
+Table\,\ref{table:amps_offsets} lists the estimated amplitudes and offsets for the phase curve fits (median and $1\,\sigma$ credible interval).
+These values are from the sine curve model for the thermal phase variation, which directly fits for the amplitude and hotspot offset.
+For the WFC3 phase curves, the amplitudes are consistent with unity and the offsets are consistent with zero.
+We note that some of the spectroscopic channels have amplitudes greater than unity, which is physically impossible (the planet cannot emit negative flux).
+As a sanity check, we take the weighted average over the WFC3 channels and find an average amplitude of $0.91\pm0.02$, which shows that at higher precision the results are physical and agree well with the large amplitudes observed for other hot planets \citep{komacek16}.
+The \Spitzer\ phase curves also have large amplitudes (near 0.85) and hotspot offsets consistent with zero.
+
+\begin{deluxetable}{LLL}
+	\tablecolumns{3}
+	\tablewidth{0pt}:
+	\tablecaption{Phase Curve Properties \label{table:amps_offsets}}
+	\tablehead{
+	\colhead{Wavelength} & \colhead{Amplitude} & \colhead{Offset (degrees)}}
+		\startdata
+		1.175 & 1.11 \pm 0.27 & 1.8 \pm 1.3 \\
+		1.225 & 0.88 \pm 0.17 & -1.1 \pm 1.4 \\
+		1.275 & 0.92 \pm 0.17 & -0.6 \pm 1.4 \\
+		1.325 & 0.82 \pm 0.14 & -1.8 \pm 1.5 \\
+		1.375 & 0.91 \pm 0.16 & -1.6 \pm 1.4 \\
+		1.425 & 0.83 \pm 0.13 & -2.5 \pm 1.4 \\
+		1.475 & 1.04 \pm 0.19 & -0.3 \pm 1.2 \\
+		1.525 & 0.99 \pm 0.19 & 0.3 \pm 1.3 \\
+		1.575 & 0.86 \pm 0.18 & 1.8 \pm 1.2 \\
+		1.625 & 0.89 \pm 0.17 & 0.3 \pm 1.3 \\
+		3.6 & 0.86 \pm 0.13 & 2.0 \pm 0.7 \\
+		4.5 & 0.83 \pm 0.05 & 1.0 \pm 0.4 \\
+		\enddata
+\end{deluxetable}
 
 %\subsection{Clouds?}
-
 \section{Atmospheric Composition and Thermal Structure}
@@
 
-\begin{deluxetable}{lll}
+\begin{deluxetable}{LLL}
 	\tablecolumns{3}
@@
 	\tablehead{
-	\colhead{Phase} & \colhead{Effective Temperature} & \colhead{$\chi^2_\nu$}}
+	\colhead{Orbital Phase} & \colhead{$T_\mathrm{eff}$} & \colhead{$\chi^2_\nu$}}
 		\startdata
-		0.1 & $ 1919 \pm 40 $ & 0.6 \\
-		0.2 & $ 2256 \pm 24 $ & 0.8 \\
-		0.3 & $ 2651 \pm 17 $ & 1.2 \\
-		0.4 & $ 2906 \pm 11 $ & 0.8 \\
-		0.5 & $ 3013 \pm 8 $ & 1.6 \\
-		0.6 & $ 2885 \pm 12 $ & 1.3 \\
-		0.7 & $ 2636 \pm 16 $ & 0.9 \\
-		0.8 & $ 2313 \pm 23 $ & 1.1 \\
-		0.9 & $ 2027 \pm 36 $ & 0.5 \\
+		0.06 - 0.15 & 1919 \pm 40 & 0.6 \\
+		0.15 - 0.25 & 2256 \pm 24 & 0.8 \\
+		0.25 - 0.35 & 2651 \pm 17 & 1.2 \\
+		0.35 - 0.44 & 2906 \pm 11 & 0.8 \\
+		0.44 - 0.56 & 3013 \pm 8 & 1.6 \\
+		0.56 - 0.65 & 2885 \pm 12 & 1.3 \\
+		0.65 - 0.75 & 2636 \pm 16 & 0.9 \\
+		0.75 - 0.85 & 2313 \pm 23 & 1.1 \\
+		0.85 - 0.94 & 2027 \pm 36 & 0.5 \\
 		\enddata
@@
 	\end{deluxetable}
-%Over the WFC3 bandpass, the phase-resolved spectra are featureless and consistent with blackbodies (with best fit $\chi^2_\nu$ ranging from $0.5-1.3$).
-However, the \Spitzer\ data, particularly at 4.5 $\mu$m, are discrepant with the best fit blackbody by $3-5\,\sigma$ at most orbital phases, indicating the presence of infrared molecular absorption or emission features.
-We investigate possible atmospheric compositions and temperature structures in \S\,\ref{sec:composition}.
 
@@
 
-Figure\,\ref{fig:opacities} shows the opacity contributions of key absorbers for the best fit.
+Figure\,\ref{fig:opacities} shows the opacity contributions of key absorbers for the best fit model.
 In the optical (which we do not observe directly), there is strong absorption by TiO, VO, and FeH.
-In the near-infrared, the H$_2$O, H-, and hydrides/oxides all contribute to the opacity, leading to nearly constant opacity over the WFC3 wavelength range.
-In cooler atmospheres, water is the dominant absorber over this bandpass, but in WASP-103b, H$_2$O is partially dissociated in the photosphere, leading to a drop in abundance by a factor of $\sim10$ (see Figure\,\ref{fig:summary}).
+In the near-infrared, H$_2$O, H-, and hydrides/oxides all contribute to the opacity, leading to nearly constant opacity over the WFC3 wavelength range.
+In cooler atmospheres, water is the dominant absorber over this bandpass \citep[e.g.][]{kreidberg14b, line16}, but in WASP-103b, H$_2$O is partially dissociated in the photosphere, leading to a drop in abundance by a factor of $\sim10$ (see Figure\,\ref{fig:summary}).
 Water also has intrinsically weaker features at high temperature \citep{tinetti12}.
-Finally, water is an efficient coolant, so lower water abundance leads to a more isothermal photosphere, which further weakens the contrast in and out of the water band in the observed spectrum.
+Water is also an efficient coolant, so lower water abundance leads to a more isothermal photosphere, which further weakens the contrast in and out of the water band.
 On top of this, there is significant H- opacity from single H atoms bound with free electrons, which fills in the opacity at wavelengths shorter than $1.5\,\mu$m.
@@
 The  thermal inversion is driven by absorption of optical light by oxides and hydrides in the upper atmosphere.
-The contribution functions FIXME
-%Figure\,\ref{fig:TP} shows a selection of 100 randomly selected dayside T-P profiles.
-The profiles are nearly isothermal over a pressure range of $1-10^{-2}$ bars, with a median temperature near 2900 Kelvin.
-The temperature increases over $10^{-2} - 10^{-3}$ bars to 3500 Kelvin, and then begins to decrease again at pressures below $10^{-3}$ bar.
+The observations are sensitive to pressures of $\sim0.01 - 0.001$ bar, which spans the tropopause, where temperature begins to increase and the water abundance drops by more than an order of magnitude.
 
@@
 For a carbon-rich composition, the equilibrium abundance of methane relative to CO increases by orders of magnitude compared to an oxygen-rich  composition \citep[e.g.][]{madhusudhan11}.
-Our \Spitzer\ eclipse depths are sensitive to the relative abundance of these species, so we can confidently rule out a carbon-rich composition in spite of the lack of spectrally resolved features.
+Our \Spitzer\ eclipse depths are sensitive to the relative abundance of these species, so we can confidently rule out a carbon-rich composition despite the lack of spectrally resolved features.
 
@@
 The WFC3 bandpass is near the peak of the planet's thermal emission, so it provides a good test of whether the GCM reproduces the properties of the planet.
-Our nominal model was a cloud-free, solar composition atmosphere with TiO/VO opacity and no added drag.
-This model qualitatively reproduces some features of the data, such as the large day-night temperature contrast; however, it predicts a larger offset in peak brightness from the substellar point than we observe.
-
-To achieve a better fit to the data, we varied the nominal model parameters.
-We tested models with enhanced metallicity ([Fe/H] = 0.5), no TiO/VO, and added atmospheric drag.
+Our nominal GCM was a cloud-free, solar composition atmosphere with TiO/VO opacity and no added drag.
+We also ran models with enhanced metallicity ([Fe/H] = 0.5), no TiO/VO, and added atmospheric drag.
 Lorentz drag can occur in the hottest exoplanet atmospheres, which may be partially ionized and coupled to the background magnetic field.
@@
 
+This model qualitatively reproduces some features of the data, such as the large day-night temperature contrast; however, it predicts a larger offset in peak brightness from the substellar point than we observe.
 The models with added drag more closely reproduce the small hotspot offset that is observed.
@@
 
+what do the hot spot offsets and amplitudes mean?
+
 \acknowledgments

### 2018-01-04 Figures/amp_offset_table.py

@@ -1,24 +1,43 @@
 import numpy as np
 
+def weighted_mean(data, err):                #calculates the weighted mean for data points data with variances err
+    weights = 1.0/err
+    mu = np.sum(data*weights)/np.sum(weights)
+    var = 1.0/np.sum(weights)
+    return [mu, var]                #returns weighted mean and variance
 
-print "\\begin{deluxetable}{LLL}"
+
+"\\begin{deluxetable}{LLL}"
 print "\\tablecolumns{3}"
 print "\\tablewidth{0pt}:"
 print "\\tablecaption{Phase Curve Properties \label{table:amps_offsets}}"
 print "\\tablehead{"
-print "\colhead{Wavelength} & \colhead{Amplitude} & \colhead{Offset}}"
+print "\colhead{Wavelength} & \colhead{Amplitude} & \colhead{Offset (Degrees)}}"
 print "\startdata"
 
 
 d = np.genfromtxt("WFC3_amplitudes_offsets.txt")
 #columns: 1) phase shift, 2-3)phase shift err, 4) amp, 5-6) amp err, 7) fpfs, 8-9) fpfs_err
 
-off, off_err = d[:,1]*180./np.pi, (d[:,2]+ d[:,3])/2.*180./np.pi
+off, off_err = -1.*d[:,1]*180./np.pi, (d[:,2]+ d[:,3])/2.*180./np.pi
 amp, amp_err = d[:,4], (d[:,5]+d[:,6])/2.
+
 fpfs, fpfs_err = d[:,7], (d[:,8]+d[:,9])/2.
 wave = np.linspace(1.175, 1.625, 10)
 
+print "WFC3 average amplitude = ", weighted_mean(amp, amp_err) 
+print "WFC3 average offset = ", weighted_mean(off, off_err)
+
 for i in range(len(d)): print wave[i], "&",  '{0:0.2f}'.format(amp[i]), "\\pm", '{0:0.2f}'.format(amp_err[i]), "&", '{0:0.1f}'.format(off[i]), "\\pm", '{0:0.1f}'.format(off_err[i]),  "\\\\"
+
+#Spitzer data
+wave = np.array([3.6, 4.5])
+off = np.array([2.0, 1.0])
+off_err = np.array([0.7, 0.4])
+amp = np.array([0.86, 0.83])
+amp_err = np.array([0.13, 0.05])
+
[…]

### 2018-01-04 Figures/gcm_comparison.py

@@ -53,15 +53,17 @@ for i, g in enumerate(gcms):
     plt.plot(model[:,0]/360. +0.5, model[:,5]*1e3*area, label = labels[i], color = colors[i], linestyle = ls[i])
     plt.plot(model[:,0]/360. +1.5, model[:,5]*1e3*area, color = colors[i], linestyle = ls[i])
 
-    print "model quadrature", np.interp(0.25, model[:,0]/360. +0.5, model[:,5]*1e3*area) 
+    #print "model quadrature", np.interp(0.25, model[:,0]/360. +0.5, model[:,5]*1e3*area) 
 
-    x, y = model[:,0]/360. + 0.5, model[:,5]
-    f = interp1d(x, y, kind = 'cubic')
-    xnew = np.linspace(0, 1, 1000)
-    ynew = f(xnew)
-    ind = ynew == np.max(ynew)
-    offset = xnew[ind]
-    #print "hotspot offset", (offset - 0.5)*360.
+    for col in [5,6,7]:
+        x, y = model[:,0]/360. + 0.5, model[:,col]
+        f = interp1d(x, y, kind = 'cubic')
+        xnew = np.linspace(0, 1, 1000)
+        ynew = f(xnew)
+        ind = ynew == np.max(ynew)
+        offset = xnew[ind]
+        print ((offset - 0.5)*360.)[0], (np.max(ynew) - np.min(ynew))/np.max(ynew),
+    print ""
 
 
 

### 2018-01-04 Figures/get_Spitzer_amplitudes_offsets.py

@@ -1,0 +1,64 @@
+import numpy as np
+import pickle
+import matplotlib.pyplot as plt
+
+#return 1.+p.amp1[v_num]*np.cos(2.*np.pi*(t-p.theta1[v_num])/p.per[v_num])  //HST
+
+#IND(y,i) = c1a*cos(2*pi*(IND(x,i)-c1o)/p) + c                              //Spitzer
+
+#p = 0.925545613
+p = 9.2554e-01
+depth, depth_err =  4.85018804e-03, 2.16170975e-04
+c1a, c1a_err =  2.00086275e-03, 9.82717991e-05
+c1o, c1o_err =  5.32560819e-01, 6.58478628e-03
+
+toffset = 2457162.
+
+offset = (((c1o + toffset)/p)%1)*180./np.pi
+phase_offset = ((c1o+toffset)/p)%1
+
+#print "CH2 offset in degrees", offset, "+/-", c1o_err*180./np.pi
+#print "Ch2 offset in phase", phase_offset
+#print "is there truncation error in the period? this is a problem for toffset >> p"
+
+pic = pickle.load(open("spitzer_ch2_sine_bestfit.pic", "rb"))
+
+plt.subplot(211)
+plt.plot(pic[0], pic[3])
+x = np.linspace(0, p, 100)
+#plt.plot(x/p, 1. - c1a*np.cos(2*np.pi*(x-phase_offset*p)/p)) 
+
+#guess is more accurate!!
+guess2 = 0.017
+y =  1. - c1a*np.cos(2*np.pi*(x+guess2)/p)
+plt.plot(x/p, 1. - c1a*np.cos(2*np.pi*(x+guess2)/p)) 
+print "ch2 offset by eye = ", guess2/p*180./np.pi, "+/-", c1o_err*180./np.pi
+print "ch2 amplitude = ", c1a*2./depth, "+/-", c1a*2./depth*np.sqrt((c1a_err/c1a)**2 + (depth_err/depth)**2) 
+#print "ch2 guess amplitude = ", (y.max() - y.min())/depth  #it's exactly the same
+
+plt.ylim(0.997, 1.003)
+
+
+#Ch 1
+depth, depth_err =  3.68401784e-03, 2.99006690e-04
+c1a, c1a_err = 1.84589958e-03, 2.37261751e-04
+c1o, c1o_err = 1.46311670e-01, 1.17483920e-02
+
+toffset = 2457170.7
[…]

### 2018-01-04 Figures/get_WFC3_amplitudes_offsets.py

@@ -23,7 +23,5 @@ ind3 = 1        #fpfs
 
 for f in files:
         d = np.load(f)
-        print f[32+offset:36+offset], np.median(d[:,ind]), np.median(d[:,ind]) - quantile(d[:,ind], 0.16), quantile(d[:,ind], 0.84) - np.median(d[:,ind]), np.median(d[:,ind2]), np.median(d[:,ind2]) - quantile(d[:,ind2], 0.16), quantile(d[:,ind2], 0.84) - np.median(d[:,ind2]), np.median(d[:, ind3]), np.median(d[:,ind3]) - quantile(d[:,ind3], 0.16), quantile(d[:,ind3], 0.84) - np.median(d[:,ind3])
-#       print f[32+offset:36+offset], np.median(d[:,ind2])*np.median(d[:,ind3]) #phase amplitude
-        #print f[32+offset:36+offset], np.median(d[:,ind3]), np.std(d[:,ind3])   #phase amplitude
-        #need to do error propagation to get uncertainties
+        #print f[32+offset:36+offset], np.median(d[:,ind]), np.median(d[:,ind]) - quantile(d[:,ind], 0.16), quantile(d[:,ind], 0.84) - np.median(d[:,ind]), np.median(d[:,ind2]), np.median(d[:,ind2]) - quantile(d[:,ind2], 0.16), quantile(d[:,ind2], 0.84) - np.median(d[:,ind2]), np.median(d[:, ind3]), np.median(d[:,ind3]) - quantile(d[:,ind3], 0.16), quantile(d[:,ind3], 0.84) - np.median(d[:,ind3])
+        print f[32+offset:36+offset], np.median(d[:,ind]), np.median(d[:,ind2]), np.median(d[:,ind3])

### 2018-01-04 Figures/teffs_table.py

@@ -2,20 +2,22 @@ import numpy as np
 
 teffs = np.genfromtxt("teffs.txt")
 
-print "\\begin{deluxetable}{lll}"
+print "\\begin{deluxetable}{LLL}"
 print "\\tablecolumns{3}"
 print "\\tablewidth{0pt}:"
 print "\\tablecaption{Phase-resolved Effective Temperature \label{table:teffs}}"
 print "\\tablehead{"
-print "\colhead{Phase} & \colhead{Effective Temperature} & \colhead{$\chi^2_\\nu$}}"
+print "\colhead{Orbital Phase} & \colhead{$T_\mathrm{eff}$} & \colhead{$\chi^2_\\nu$}}"
 print "\startdata"
 
 T = teffs[:,0]
 err = teffs[:,1]
 chi2 = teffs[:,2]
 phase = teffs[:,3]
+phase1 = np.array([0.06, 0.15, 0.25, 0.35, 0.44, 0.56, 0.65, 0.75, 0.85])
+phase2 = np.array([0.15, 0.25, 0.35, 0.44, 0.56, 0.65, 0.75, 0.85, 0.94])
 
-for i in range(len(teffs)): print phase[i], "&", "$", int(T[i]), "\\pm", int(err[i]), "$", "&", chi2[i],  "\\\\"
+for i in range(len(teffs)): print phase1[i], "-", phase2[i],  "&", int(T[i]), "\\pm", int(err[i]), "&", chi2[i],  "\\\\"
 
 print "\enddata"
 print "\\vspace{-0.8cm}"

### 2018-01-04 ms.tex
gcm comparison

@@
 	\tablecolumns{6}
-	\tablewidth{0pt}:
+	\tablewidth{0pt}
 	\tablecaption{Model Comparison \label{table:models}}
@@
 
-\begin{deluxetable}{LLL}
-	\tablecolumns{3}
+\begin{deluxetable}{llLL}
+	\tablecolumns{4}
 	\tablewidth{0pt}:
@@
 	\tablehead{
-	\colhead{Wavelength} & \colhead{Amplitude} & \colhead{Offset (degrees)}}
+		\colhead{Bandpass} & \colhead{Source} & \colhead{Amplitude} & \colhead{Offset)}\\
+	\colhead{\,} & \colhead{\,} & \colhead{\,} & \colhead{(Degrees)}}
 		\startdata
-		1.175 & 1.11 \pm 0.27 & 1.8 \pm 1.3 \\
-		1.225 & 0.88 \pm 0.17 & -1.1 \pm 1.4 \\
-		1.275 & 0.92 \pm 0.17 & -0.6 \pm 1.4 \\
-		1.325 & 0.82 \pm 0.14 & -1.8 \pm 1.5 \\
-		1.375 & 0.91 \pm 0.16 & -1.6 \pm 1.4 \\
-		1.425 & 0.83 \pm 0.13 & -2.5 \pm 1.4 \\
-		1.475 & 1.04 \pm 0.19 & -0.3 \pm 1.2 \\
-		1.525 & 0.99 \pm 0.19 & 0.3 \pm 1.3 \\
-		1.575 & 0.86 \pm 0.18 & 1.8 \pm 1.2 \\
-		1.625 & 0.89 \pm 0.17 & 0.3 \pm 1.3 \\
-		3.6 & 0.86 \pm 0.13 & 2.0 \pm 0.7 \\
-		4.5 & 0.83 \pm 0.05 & 1.0 \pm 0.4 \\
+		WFC3 & data & 0.91 \pm 0.02 & -0.3 \pm 0.1 \\
+		\, & nominal GCM & 0.89 & 15.32 \\
+		\, & [Fe/H] = 0.5 GCM & 0.84 & 19.64 \\
+		\, & $\tau_\mathrm{drag4}$ GCM & 0.97 & 2.34 \\
+		\, & $\tau_\mathrm{drag3}$ GCM & 0.99 & 0.18 \\
+		Spitzer 3.6 $\mu$m & data & 0.86 \pm 0.13 & 2.0 \pm 0.7 \\
+		\, & nominal GCM & 0.78 & 9.19 \\
+		\, & [Fe/H] = 0.5 GCM & 0.72 & 12.79 \\
+		\, & $\tau_\mathrm{drag4}$ GCM & 0.86 & 0.90 \\
+		\, & $\tau_\mathrm{drag3}$ GCM & 0.97 & 0.18 \\
+		Spitzer 4.5 $\mu$m & data & 0.83 \pm 0.05 & 1.0 \pm 0.4 \\
+		\, & nominal GCM & 0.79 & 8.11 \\
+		\, & [Fe/H] = 0.5 GCM & 0.73 & 11.35 \\
+		\, & $\tau_\mathrm{drag4}$ GCM & 0.85 & 0.90 \\
+		\, & $\tau_\mathrm{drag3}$ GCM & 0.93 & 0.18 \\
 		\enddata
@@
 	\tablecolumns{3}
-	\tablewidth{0pt}:
+	\tablewidth{0pt}
 	\tablecaption{Phase-resolved Effective Temperature \label{table:teffs}}
@@
 
-This model qualitatively reproduces some features of the data, such as the large day-night temperature contrast; however, it predicts a larger offset in peak brightness from the substellar point than we observe.
+To assess how well the GCM predictions reproduce the data, we calculate the amplitude and hot spot offset for all the models (listed in Table\,\ref{tab:amps_offs}).
+The models with drag fit better, with phase variation amplitude near unity and a hot spot offset near zero for all three band-passes.
+The nominal model and metal-enhanced composition ([Fe/H] = 0.5) both have a phase curve offset that is too large (
+
+However, in the WFC3 bandpass the drag models underestimate the flux at longitudes away from the substellar point.
+For example, the FIXME model predicts 20\% less flux than is observed at quadrature.
+\textbf{Vivien: are these fast drag timescales even reasonable?}).
+
+FIXME: change taudrag3 label. change text about unphysical phase curve ampltiude
+
+%This model qualitatively reproduces some features of the data, such as the large day-night temperature contrast; however, it predicts a larger offset in peak brightness from the substellar point than we observe.
 The models with added drag more closely reproduce the small hotspot offset that is observed.
@@
 The drag models also provide a good match to the observed dayside flux, for drag timescales in the range $\tau_\mathrm{drag} = 10^3 - 10^4$ s.
-However, the drag models underestimate the flux at longitudes away from the substellar point, predicting 20\% less flux than is observed at quadrature.
-\textbf{Vivien: are these fast drag timescales even reasonable?}).
 
@@
 	\tablecolumns{6}
-	\tablewidth{0pt}:
+	\tablewidth{0pt}
 	\tablecaption{Source Properties \label{table:sources}}

### 2018-01-04 Figures/amp_offset_table.py

@@ -6,16 +6,6 @@ def weighted_mean(data, err):                #calculates the weighted mean for d
     var = 1.0/np.sum(weights)
     return [mu, var]                #returns weighted mean and variance
 
-
-"\\begin{deluxetable}{LLL}"
-print "\\tablecolumns{3}"
-print "\\tablewidth{0pt}:"
-print "\\tablecaption{Phase Curve Properties \label{table:amps_offsets}}"
-print "\\tablehead{"
-print "\colhead{Wavelength} & \colhead{Amplitude} & \colhead{Offset (Degrees)}}"
-print "\startdata"
-
-
 d = np.genfromtxt("WFC3_amplitudes_offsets.txt")
 #columns: 1) phase shift, 2-3)phase shift err, 4) amp, 5-6) amp err, 7) fpfs, 8-9) fpfs_err
 
@@ -25,10 +15,26 @@ amp, amp_err = d[:,4], (d[:,5]+d[:,6])/2.
 fpfs, fpfs_err = d[:,7], (d[:,8]+d[:,9])/2.
 wave = np.linspace(1.175, 1.625, 10)
 
-print "WFC3 average amplitude = ", weighted_mean(amp, amp_err) 
-print "WFC3 average offset = ", weighted_mean(off, off_err)
+amp, amp_err = weighted_mean(amp, amp_err) 
+off, off_err = weighted_mean(off, off_err)
 
-for i in range(len(d)): print wave[i], "&",  '{0:0.2f}'.format(amp[i]), "\\pm", '{0:0.2f}'.format(amp_err[i]), "&", '{0:0.1f}'.format(off[i]), "\\pm", '{0:0.1f}'.format(off_err[i]),  "\\\\"
+gcm_wfc3 = np.genfromtxt("gcm_amp_off_wfc3.txt")
+models = ["nominal GCM", "[Fe/H] = 0.5 GCM", "$\\tau_\mathrm{drag4}$ GCM", "$\\tau_\mathrm{drag3}$ GCM"]
+
+print "\\begin{deluxetable}{llLL}"
+print "\\tablecolumns{4}"
+print "\\tablewidth{0pt}:"
+print "\\tablecaption{Phase Curve Properties \label{table:amps_offsets}}"
+print "\\tablehead{"
[…]

### 2018-01-04 Figures/gcm_comparison.py

@@ -55,14 +55,17 @@ for i, g in enumerate(gcms):
 
     #print "model quadrature", np.interp(0.25, model[:,0]/360. +0.5, model[:,5]*1e3*area) 
 
-    for col in [5,6,7]:
-        x, y = model[:,0]/360. + 0.5, model[:,col]
-        f = interp1d(x, y, kind = 'cubic')
-        xnew = np.linspace(0, 1, 1000)
-        ynew = f(xnew)
-        ind = ynew == np.max(ynew)
-        offset = xnew[ind]
-        print ((offset - 0.5)*360.)[0], (np.max(ynew) - np.min(ynew))/np.max(ynew),
+    #for col in [5,6,7]:
+    #col = 5
+    #col =6
+    col = 7
+    x, y = model[:,0]/360. + 0.5, model[:,col]
+    f = interp1d(x, y, kind = 'cubic')
+    xnew = np.linspace(0, 1, 1000)
+    ynew = f(xnew)
+    ind = ynew == np.max(ynew)
+    offset = xnew[ind]
+    print ((offset - 0.5)*(-360.))[0], (np.max(ynew) - np.min(ynew))/np.max(ynew),
     print ""
 
 

### 2018-01-05 ms.tex
reorg

@@
 We ran the MCMC until convergence according to the Gelman-Rubin statistic FIXME.
-MCMC techniques only produce robust uncertainties when the noise is normally distributed and white, so to account for correlated noise in the $3.6\,\mu$m light curve we fit the wavelet model from \cite{carter09} (simultaneously with the other model parameters).
+MCMC techniques only produce robust uncertainties when the noise is normally distributed and white, so to account for correlated noise in the $3.6\,\mu$m light curve (described in \S\,\ref{sec:fitquality}) we fit the wavelet model from \cite{carter09} (simultaneously with the other model parameters).
 We used a Haar wavelet and let the power spectral density of the red noise vary, following \cite{diamond-lowe14}.
 In our final fit, the noise power spectrum $1/f^\gamma$ had $\gamma = 1.1 \pm 0.1$.
-
-\begin{figure*}
-\includegraphics[width = 1.0\textwidth]{Figures/phase_curves_spherical.pdf}
-\caption{WASP-103b phase curve observations from \HST/WFC3 (top) and \Spitzer/IRAC (middle and bottom).
-For clarity, the data are phase-folded on the planet's orbital period and binned in 30 uniformly spaced bins between 0 and 1.
-The left column shows the phase curves with systematic noise removed (black points) compared to the best fit spherical harmonics model (colored lines).
-The error bars denote $1\,\sigma$ uncertainties (in some cases, the errors are smaller than the data points).
-%The shading denotes the  1\,$\sigma$ confidence interval on the best fit.
-We include the transits in the fit, but they are not displayed in this figure. The right-hand column shows the binned residuals for the best-fit light curve.}
-\label{fig:phasecurves}
-\end{figure*}
-
-\section{Results}
-\label{sec:results}
-The fitted light curves are shown in Figure\,\ref{fig:phasecurves}.
-This figure shows results from the spherical harmonics model for the thermal phase variation and has instrument systematics removed.
-Broadly speaking, the phase curves show large amplitude phase variation, ranging from 1.5 parts-per-thousand (ppt) in the WFC3 bandpass to 5 ppt in \Spitzer\ Channel 2.
-The planet flux changes significantly with orbital phase in all three of the data sets, suggesting a strong gradient from dayside to nightside temperature, and peak brightness occurs near phase 0.5.
-In this section, we describe the phase curve fits and the phase-resolved spectra.
-FIXME
 
@@
 
+\begin{figure*}
+\includegraphics[width = 1.0\textwidth]{Figures/phase_curves_spherical.pdf}
+\caption{WASP-103b phase curve observations from \HST/WFC3 (top) and \Spitzer/IRAC (middle and bottom).
+For clarity, the data are phase-folded on the planet's orbital period and binned in 30 uniformly spaced bins between 0 and 1.
+The left column shows the phase curves with systematic noise removed (black points) compared to the best fit spherical harmonics model (colored lines).
+The error bars denote $1\,\sigma$ uncertainties (in some cases, the errors are smaller than the data points).
+%The shading denotes the  1\,$\sigma$ confidence interval on the best fit.
+We include the transits in the fit, but they are not displayed in this figure. The right-hand column shows the binned residuals for the best-fit light curve.}
+\label{fig:phasecurves}
+\end{figure*}
+
+\section{Results}
+\label{sec:results}
+The fitted light curves are shown in Figure\,\ref{fig:phasecurves}.
+This figure shows results from the spherical harmonics model for the thermal phase variation and has instrument systematics removed.
+Broadly speaking, the phase curves show large amplitude phase variation, ranging from 1.5 parts-per-thousand (ppt) in the WFC3 bandpass to 5 ppt in \Spitzer\ Channel 2.
+The planet flux changes significantly with orbital phase in all three of the data sets, suggesting a strong gradient from dayside to nightside temperature, and peak brightness occurs near phase 0.5.
+In this section, we quantitatively characterize the phase curve shape, split the data into phase resolved spectra, evaluate different different temperature maps, and compare with previous observations of the dayside thermal emission spectrum.
+
 \begin{deluxetable}{llllll}
@@
 		\tablecomments{comments}
+\end{deluxetable}
+
+\subsection{Phase Curve Amplitudes and Hotspot Offsets}
+The shape of a phase curve can be summarized with two parameters: the amplitude of thermal phase variation (minimum to maximum brightness, divided by the secondary eclipse depth) and the location of peak brightness (typically called a ``hotspot offset" and measured in degrees eastward of the substellar point).
+Larger amplitudes and smaller offsets are both indicative of inefficient heat transport to the nightside.
+
+Table\,\ref{table:amps_offsets} lists the estimated amplitudes and offsets for the phase curve fits (median and $1\,\sigma$ credible interval).
+These values are from the sine curve model for the thermal phase variation, which fits directly for the amplitude and hotspot offset.
+For the WFC3 phase curves, the amplitudes are consistent with unity and the offsets are consistent with zero.
+We note that some of the spectroscopic channels have amplitudes greater than unity, which is physically impossible (the planet cannot emit negative flux).
+As a sanity check, we take the weighted average over the WFC3 channels and find an average amplitude of $0.91\pm0.02$, which shows that at higher precision the results are physical and agree well with the large amplitudes observed for other hot planets \citep{komacek16}.
+The \Spitzer\ phase curves also have large amplitudes (near 0.85) and hotspot offsets consistent with zero.
+
+\begin{deluxetable}{llLL}
+	\tablecolumns{4}
+	\tablewidth{0pt}:
+	\tablecaption{Phase Curve Properties \label{table:amps_offsets}}
+	\tablehead{
+		\colhead{Bandpass} & \colhead{Source} & \colhead{Amplitude} & \colhead{Offset)}\\
+	\colhead{\,} & \colhead{\,} & \colhead{\,} & \colhead{(Degrees)}}
+		\startdata
+		WFC3 & data & 0.91 \pm 0.02 & -0.3 \pm 0.1 \\
+		\, & nominal GCM & 0.89 & 15.32 \\
+		\, & [Fe/H] = 0.5 GCM & 0.84 & 19.64 \\
+		\, & $\tau_\mathrm{drag4}$ GCM & 0.97 & 2.34 \\
+		\, & $\tau_\mathrm{drag3}$ GCM & 0.99 & 0.18 \\
+		Spitzer 3.6 $\mu$m & data & 0.86 \pm 0.13 & 2.0 \pm 0.7 \\
+		\, & nominal GCM & 0.78 & 9.19 \\
+		\, & [Fe/H] = 0.5 GCM & 0.72 & 12.79 \\
+		\, & $\tau_\mathrm{drag4}$ GCM & 0.86 & 0.90 \\
+		\, & $\tau_\mathrm{drag3}$ GCM & 0.97 & 0.18 \\
+		Spitzer 4.5 $\mu$m & data & 0.83 \pm 0.05 & 1.0 \pm 0.4 \\
+		\, & nominal GCM & 0.79 & 8.11 \\
+		\, & [Fe/H] = 0.5 GCM & 0.73 & 11.35 \\
+		\, & $\tau_\mathrm{drag4}$ GCM & 0.85 & 0.90 \\
+		\, & $\tau_\mathrm{drag3}$ GCM & 0.93 & 0.18 \\
+		\enddata
 	\end{deluxetable}
@@
 \includegraphics[width = 1.0\textwidth]{Figures/emission_spectra.pdf}
-\caption{Phase-resolved emission spectra (points) compared to the best fit blackbody (blue line) and the GCM with $\tau_\mathrm{drag} = 10^3$ s.
+\caption{Phase-resolved emission spectra (points) compared to the best fit blackbody (blue line) and the GCM with $\tau_\mathrm{drag3}$ s.
 Phases $\phi = 0.5$ and $0.0$ are centered on the substellar and anti-stellar points, respectively.}
@@
 \caption{\textbf{Left:} Fits to the broadband WFC3 phase curve compared to a GCM.
-The colored lines correspond to different temperature maps fit to the data, and the dashed gray line is from the $\tau_\mathrm{drag} = 10^3$ GCM.
+The colored lines correspond to different temperature maps fit to the data, and the dashed gray line is from the $\tau_\mathrm{drag3}$ GCM.
 We also show the planet-to-star flux corresponding to each map (points), which is model-dependent due to slight degeneracies with the instrument systematic model.
@@
 Since these results are consistent with (but less precise than) the WFC3 data, we do not include them in our analysis of the atmospheric composition, but we encourage additional measurements in the $K_\mathrm{S}$ band to confidently determine whether an emission feature is present at those wavelengths.
-
-\subsection{Phase Curve Amplitudes and Hotspot Offsets}
-The shape of a phase curve can be summarized with two parameters: the amplitude of thermal phase variation (minimum to maximum brightness, divided by the secondary eclipse depth) and the location of peak brightness (typically called a ``hotspot offset" and measured in degrees eastward of the substellar point).
-Larger amplitudes and smaller offsets are both indicative of inefficient heat transport to the nightside.
-
-Table\,\ref{table:amps_offsets} lists the estimated amplitudes and offsets for the phase curve fits (median and $1\,\sigma$ credible interval).
-These values are from the sine curve model for the thermal phase variation, which directly fits for the amplitude and hotspot offset.
-For the WFC3 phase curves, the amplitudes are consistent with unity and the offsets are consistent with zero.
-We note that some of the spectroscopic channels have amplitudes greater than unity, which is physically impossible (the planet cannot emit negative flux).
-As a sanity check, we take the weighted average over the WFC3 channels and find an average amplitude of $0.91\pm0.02$, which shows that at higher precision the results are physical and agree well with the large amplitudes observed for other hot planets \citep{komacek16}.
-The \Spitzer\ phase curves also have large amplitudes (near 0.85) and hotspot offsets consistent with zero.
-
-\begin{deluxetable}{llLL}
-	\tablecolumns{4}
-	\tablewidth{0pt}:
-	\tablecaption{Phase Curve Properties \label{table:amps_offsets}}
-	\tablehead{
-		\colhead{Bandpass} & \colhead{Source} & \colhead{Amplitude} & \colhead{Offset)}\\
-	\colhead{\,} & \colhead{\,} & \colhead{\,} & \colhead{(Degrees)}}
-		\startdata
-		WFC3 & data & 0.91 \pm 0.02 & -0.3 \pm 0.1 \\
-		\, & nominal GCM & 0.89 & 15.32 \\
-		\, & [Fe/H] = 0.5 GCM & 0.84 & 19.64 \\
-		\, & $\tau_\mathrm{drag4}$ GCM & 0.97 & 2.34 \\
-		\, & $\tau_\mathrm{drag3}$ GCM & 0.99 & 0.18 \\
-		Spitzer 3.6 $\mu$m & data & 0.86 \pm 0.13 & 2.0 \pm 0.7 \\
-		\, & nominal GCM & 0.78 & 9.19 \\
-		\, & [Fe/H] = 0.5 GCM & 0.72 & 12.79 \\
-		\, & $\tau_\mathrm{drag4}$ GCM & 0.86 & 0.90 \\
-		\, & $\tau_\mathrm{drag3}$ GCM & 0.97 & 0.18 \\
-		Spitzer 4.5 $\mu$m & data & 0.83 \pm 0.05 & 1.0 \pm 0.4 \\
-		\, & nominal GCM & 0.79 & 8.11 \\
-		\, & [Fe/H] = 0.5 GCM & 0.73 & 11.35 \\
-		\, & $\tau_\mathrm{drag4}$ GCM & 0.85 & 0.90 \\
-		\, & $\tau_\mathrm{drag3}$ GCM & 0.93 & 0.18 \\
-		\enddata
-	\end{deluxetable}
 
@@
 \label{sec:gcm}
-To explore the three-dimensional effects of atmospheric dynamics, we ran several GCM models to compare with the measured phase-resolved spectra. (\textbf{Vivien: paragraph describing GCM}).
+To explore the three-dimensional effects of atmospheric dynamics, we ran several GCM models to compare with the measured phase-resolved spectra.
+(\textbf{Vivien: paragraph describing GCM}).
+Our nominal GCM was a cloud-free, solar composition atmosphere with TiO/VO opacity and no added drag.
+We also ran models with enhanced metallicity ([Fe/H] = 0.5), no TiO/VO, and added atmospheric drag.
+Lorentz drag can occur in the hottest exoplanet atmospheres, which may be partially ionized and coupled to the background magnetic field.
+We parameterized the drag (\textbf{Vivien: how did you model drag?}), with timescales of $\tau_\mathrm{drag} = 10^3$ and $10^4$ s, which we label $\tau_\mathrm{drag3}$ and $\tau_\mathrm{drag4}$.
+
+To assess how well the GCM predictions reproduce the data, we calculate the amplitude and hot spot offset for all the models (listed in Table\,\ref{tab:amps_offs}).
+The models with drag included are generally better fits, with phase variation amplitude near unity and a hot spot offset near zero for all three band-passes.
+The nominal model and metal-enhanced composition ([Fe/H] = 0.5) both have a phase curve offset that is too large (
 
@@
 The WFC3 bandpass is near the peak of the planet's thermal emission, so it provides a good test of whether the GCM reproduces the properties of the planet.
-Our nominal GCM was a cloud-free, solar composition atmosphere with TiO/VO opacity and no added drag.
-We also ran models with enhanced metallicity ([Fe/H] = 0.5), no TiO/VO, and added atmospheric drag.
-Lorentz drag can occur in the hottest exoplanet atmospheres, which may be partially ionized and coupled to the background magnetic field.
-We parameterized the drag (\textbf{Vivien: how did you model drag?}), with timescales were $\tau_\mathrm{drag} = 10^3, 10^4$ and $10^6$ s.
-
-To assess how well the GCM predictions reproduce the data, we calculate the amplitude and hot spot offset for all the models (listed in Table\,\ref{tab:amps_offs}).
-The models with drag fit better, with phase variation amplitude near unity and a hot spot offset near zero for all three band-passes.
-The nominal model and metal-enhanced composition ([Fe/H] = 0.5) both have a phase curve offset that is too large (
 
@@
 We also compared the GCM output to the temperature maps retrieved with \texttt{spiderman}.
-Figure\,\ref{fig:model_comparison} shows the 0.1 bar temperature map for the $\tau_\mathrm{drag} = 10^3$ GCM compared to the best it models.
+Figure\,\ref{fig:model_comparison} shows the 0.1 bar temperature map for the $\tau_\mathrm{drag3}$ GCM compared to the best it models.
 The GCM has a minimum and maximum temperature of $920$ and $3360$ K, which is most comparable to the fit from the spherical harmonic model.
@@
 As discussed in \S\,\ref{sec:composition}, water dissociation and H- opacity are needed to explain the dayside emission spectrum.
-Figure\,\ref{fig:gcmcomposition} shows the photospheric abundances of H$_2$O and H- compared to the predicted temperature for the $\tau_\mathrm{drag} = 10^3$ GCM.
+Figure\,\ref{fig:gcmcomposition} shows the photospheric abundances of H$_2$O and H- compared to the predicted temperature for the $\tau_\mathrm{drag3}$ GCM.
 The water abundance drops by $\sim10$ at the substellar point, and the H- opacity increases by $\sim100$.
@@
 	\includegraphics[width = 1.0\textwidth]{Figures/GCM_abundances.eps}
-\caption{Abundances of key molecular species for different viewing geometries, from the $\tau_\mathrm{drag} = 10^3$ GCM.}
+\caption{Abundances of key molecular species for different viewing geometries, from the $\tau_\mathrm{drag3}$ GCM.}
 \label{fig:GCMabundance}

### 2018-01-05 ms.tex
gcm done

@@
 
-%	spin-orbit alignment: 2016ApJ...823...29A
-
 %Fortney 08
-
-%Phase curve observation to provide context for the global thermal structure of the planet.
 
@@
 \begin{deluxetable}{ccccc}
-\label{tab:photometry}
-	%\tabletypesize{\small}
-	\tablenum{1}
 	\tablewidth{0pt}
-	\tablecaption{Photometric Observations of WASP-103}
+	\tablecaption{Photometric Observations of WASP-103 \label{tab:photometry}}
 	\tablehead{
 		\colhead{Observing} & \colhead{} & \colhead{Date Range} &
-	\colhead{Sigma} & \colhead{Seasonal Mean} }% \\
-
-%		\colhead{Season} & \colhead{$N_{obs}$} & \colhead{(HJD $-$ 2,400,000)} &
-%		\colhead{(mag)} & \colhead{(mag)}}%   \\
-
-	%	\colhead{(1)} & \colhead{(2)} & \colhead{(3)} &
-	%	\colhead{(4)} & \colhead{(5)}  
+	\colhead{Sigma} & \colhead{Seasonal Mean} }
 	\startdata
@@
 
-%As discussed in \S \ref{sec:fitquality}, the 3.6 $\mu$m light curve exhibits time correlated noise.
-To account for this additional source of error, we fit the wavelet model from \cite{carter09} (simultaneously with the other fit parameters).
-We fit
 %We explored adding an additional sine term to model the thermal phase variation, but the additional degrees of freedom are not justified according to the Bayesian Information Criterion (BIC).
@@
 The error bars denote $1\,\sigma$ uncertainties (in some cases, the errors are smaller than the data points).
-%The shading denotes the  1\,$\sigma$ confidence interval on the best fit.
-We include the transits in the fit, but they are not displayed in this figure. The right-hand column shows the binned residuals for the best-fit light curve.}
+We include the transits in the fit, but they are not displayed in this figure.
+The right-hand column shows the binned residuals for the best-fit light curve.}
 \label{fig:phasecurves}
@@
 
-\begin{deluxetable}{llllll}
-\label{tab:model_comparison}
-	\tablecolumns{6}
-	\tablewidth{0pt}
-	\tablecaption{Model Comparison \label{table:models}}
-	\tablehead{\colhead{Data} & \colhead{Model} & \colhead{$T_\mathrm{min}$} & \colhead{$T_\mathrm{max}$} & \colhead{$\Delta_\mathrm{AIC}$} & \colhead{$\Delta_\mathrm{BIC}$}}
-		\startdata
-		WFC3 & Sph. Harmonics & 1214 & 3251 & 0.0 & 0.0 \\
-		\, & Kinematic & 1980 & 3958 & 11.8 & 11.8 \\
-		\, & Two Temp. & 0 & 2887 & 47.7 & 43.2 \\
-		\, & Sinusoid & -- & -- & 17.7 & 13.2 \\
-		Ch 1 & Sph. Harmonics & 1280 & 3444 & 48.0 & 0.0 \\
-		\, & Kinematic & 1955 & 3675 & 82.3 & 34.3 \\
-		\, & Two Temp. & 1429 & 3041 & 58.7 & 17.6 \\
-		\, & Sinusoid & -- & -- & 0.0 & 98.4 \\
-		Ch 2 & Sph. Harmonics & 902 & 3786 & 2.2 & 3.1 \\
-		\, & Kinematic & 1703 & 4276 & 16.55 & 17.41 \\
-		\, & Two Temp. & 1361 & 3311 & 26.1 & 0.0 \\
-		\, & Sinusoid & -- & -- & 0.0 & 49.6 \\
-		\enddata
-		\vspace{-0.8cm}
-		\tablecomments{comments}
-\end{deluxetable}
-
 \subsection{Phase Curve Amplitudes and Hotspot Offsets}
 The shape of a phase curve can be summarized with two parameters: the amplitude of thermal phase variation (minimum to maximum brightness, divided by the secondary eclipse depth) and the location of peak brightness (typically called a ``hotspot offset" and measured in degrees eastward of the substellar point).
-Larger amplitudes and smaller offsets are both indicative of inefficient heat transport to the nightside.
+Table\,\ref{table:amps_offsets} lists the estimated amplitudes and hotspot offsets (median and $1\,\sigma$ credible interval) for the band-integrated WFC3 phase curve and both \Spitzer\ channels.
+The estimates are from the sine curve model for the thermal phase variation, which fits directly for the amplitude and offset.
 
-Table\,\ref{table:amps_offsets} lists the estimated amplitudes and offsets for the phase curve fits (median and $1\,\sigma$ credible interval).
-These values are from the sine curve model for the thermal phase variation, which fits directly for the amplitude and hotspot offset.
-For the WFC3 phase curves, the amplitudes are consistent with unity and the offsets are consistent with zero.
+For all three phase curves, the hotspot offset is consistent with zero degrees, indicative of a fast radiative-to-advective timescale (the incident flux is reradiated to space faster than it is advected around to the nightside).
+Fast radiative timescales are precicted at high temperatures, and small hotspot offsets are also observed for other very hot Jupiters \citep{komacek17}.
+The phase curve amplitudes are large (near 0.8 - 0.9), as expected for an atmosphere with inefficient heat redistribution.
+In \S\,\ref{sec:gcm} we compare these results to expectations from 3D GCMs.
+
+%For the WFC3 phase curves, the amplitudes are consistent with unity and the offsets are consistent with zero.
 We note that some of the spectroscopic channels have amplitudes greater than unity, which is physically impossible (the planet cannot emit negative flux).
@@
 	\tablecolumns{4}
-	\tablewidth{0pt}:
+	\tablewidth{0pt}
 	\tablecaption{Phase Curve Properties \label{table:amps_offsets}}
 	\tablehead{
-		\colhead{Bandpass} & \colhead{Source} & \colhead{Amplitude} & \colhead{Offset)}\\
+		\colhead{Bandpass} & \colhead{Source} & \colhead{Amplitude} & \colhead{Offset}\\
 	\colhead{\,} & \colhead{\,} & \colhead{\,} & \colhead{(Degrees)}}
@@
 \begin{figure*}
+\includegraphics[width = 1.0\textwidth]{Figures/hst_model_comparison.pdf}
+\caption{\textbf{Left:} Fits to the broadband WFC3 phase curve compared to a GCM.
+The colored lines correspond to different temperature maps fit to the data, and the dashed gray line is from the $\tau_\mathrm{drag3}$ GCM.
+We also show the planet-to-star flux corresponding to each map (points), which is model-dependent due to slight degeneracies with the instrument systematic model.
+\textbf{Right:} Temperature maps from the best fit models and the GCM at a representative photospheric pressure of 0.01 bar.}
+\label{fig:model_comparison}
+\end{figure*}
+
+\begin{figure*}
 \includegraphics[width = 1.0\textwidth]{Figures/emission_spectra.pdf}
@@
 \label{fig:spectra}
-\end{figure*}
-
-\begin{figure*}
-\includegraphics[width = 1.0\textwidth]{Figures/hst_model_comparison.pdf}
-\caption{\textbf{Left:} Fits to the broadband WFC3 phase curve compared to a GCM.
-The colored lines correspond to different temperature maps fit to the data, and the dashed gray line is from the $\tau_\mathrm{drag3}$ GCM.
-We also show the planet-to-star flux corresponding to each map (points), which is model-dependent due to slight degeneracies with the instrument systematic model.
-\textbf{Right:} Temperature maps from the best fit models and the GCM at 0.1 bar.
-FIXME say here what the temperature difference is at substellar point.}
-\label{fig:model_comparison}
 \end{figure*}
@@
 
-\subsection{Comparison of Thermal Phase Variation Models}
-We compared four different models for the thermal phase variation: a sinusoid and three temperature maps.
-The sinusoid has been widely used to model phase variation in previous analyses \citep[e.g.][]{knutson09, stevenson14}.
-One advantage of the sinusoid model is that it directly fits the phase variation amplitude and offset from the substellar point, and can be inverted to map the climate \citep{cowan08}.
-Fitting temperature maps directly is a new approach enabled by the \texttt{SPIDERMAN} package.
-We consider three parameterizations for the temperature map, which each have different strengths.
-One is a physically-motivated kinematic model that closely reproduces GCM simulations \citep{zhang17}.
-The second parameterization is a spherical harmonic map, which is the most flexible model we consider and makes the fewest assumptions about the true climate.
-The third model has just two free parameters, a dayside temperature and a nightside temperature.
-This model is easiest to compare to one-dimensional forward models of the dayside, which assume a uniform temperature/pressure profile.
-
+\subsection{Climate}
+We fit three different models to characterize the planet's climate: a two-temperature map, the physically-motivated kinematic model of \citep{zhang17}, and a spherical harmonic map.
+We also fit the thermal phase variation with a sinusoid, which can be inverted to map the climate \citep{cowan08}.
 All of the models provide reasonable fits to the data, with $\chi^2_\nu$ near unity, but they yield significantly different temperature maps.
-Table\,\ref{tab:model_comparison} lists the minimum and maximum temperatures for the best fit models to the WFC3 broadband and two Spitzer phase curves.
+Table\,\ref{table:model_comparison} lists the minimum and maximum temperatures for the best fit models to the WFC3 broadband and two Spitzer phase curves.
 We also list the  information criterion (BIC) and Aikike information criterion (AIC) values for the fits \citep[a $\Delta$BIC value greater than 10 constitutes strong evidence against a given model;][]{kass95}.
-
-%Both of these statistics are an approximation of the Bayesian evidence for a given model, but the BIC penalizes model complexity relatively more than the AIC \citep{kass95}.
 
@@
 As illustrated in Figure\,\ref{fig:model_comparison}, the kinematic model overpredicts the nightside flux, whereas the two temperature model overpredicts the flux at quadrature and underpredicts the dayside.
-%The spherical harmonics model is strongly favored for most of the data sets according to the AIC and BIC.
-It has slightly more free parameters than the other models (four, versus three for the kinematic model and two for the two-temperature model).
 
@@
 The minimum nightside temperature is also model-dependent: for the WFC3 data, the two-temperature model predicts a nightside temperature of zero Kelvin, whereas the best fit kinematic model has a nightside temperature of $1980\,\mathrm{K}$.
-%For the WFC3 data, the peak temperature ranges from $2890$ to $3960$ K, and the minimum ranges from $0$ to $1980$ K.
-
 These differences arise because the kinematic model allows a steep temperature gradient on the dayside, so the substellar point is much hotter than the terminator, whereas the two temperature map imposes a constant dayside temperature.
@@
 
+\begin{deluxetable}{llllll}
+	\tablecolumns{6}
+	\tablewidth{0pt}
+	\tablecaption{Model Comparison \label{table:model_comparison}}
+	\tablehead{\colhead{Data} & \colhead{Model} & \colhead{$T_\mathrm{min}$} & \colhead{$T_\mathrm{max}$} & \colhead{$\Delta_\mathrm{AIC}$} & \colhead{$\Delta_\mathrm{BIC}$}}
+		\startdata
+		WFC3 & Sph. Harmonics & 1214 & 3251 & 0.0 & 0.0 \\
+		\, & Kinematic & 1980 & 3958 & 11.8 & 11.8 \\
+		\, & Two Temp. & 0 & 2887 & 47.7 & 43.2 \\
+		\, & Sinusoid & -- & -- & 17.7 & 13.2 \\
+		Ch 1 & Sph. Harmonics & 1280 & 3444 & 48.0 & 0.0 \\
+		\, & Kinematic & 1955 & 3675 & 82.3 & 34.3 \\
+		\, & Two Temp. & 1429 & 3041 & 58.7 & 17.6 \\
+		\, & Sinusoid & -- & -- & 0.0 & 98.4 \\
+		Ch 2 & Sph. Harmonics & 902 & 3786 & 2.2 & 3.1 \\
+		\, & Kinematic & 1703 & 4276 & 16.55 & 17.41 \\
+		\, & Two Temp. & 1361 & 3311 & 26.1 & 0.0 \\
+		\, & Sinusoid & -- & -- & 0.0 & 49.6 \\
+		\enddata
+		\vspace{-0.8cm}
+		\tablecomments{comments}
+\end{deluxetable}
+
 %The typical uncertainty is FIXME (run MCMC, say the systematic range is larger than the error bars).
-
-%The spherical harmonics model fits better according to the BIC and the AIC; however, it yields higher temperatures at the poles than at the equator, which does not agree with predictions from GCM simulations \citep{FIXME}.
 
@@
 \label{sec:composition}
-To interpret the phase-resolved spectra, we performed two model fits.
+We characterized the planet's atmospheric composition by fitting 1D models to the phase-resolved emission spectra.
 First, we modeled the planet flux as a simple blackbody to estimate the dayside brightness temperature and test for significant absorption or emission features.
-We then performed a more sophisticated grid-based retrieval to evaluate the atmospheric composition and thermal structure.
+We then performed a more sophisticated grid-based retrieval to estimate the atmospheric metallicity, carbon-to-oxygen ratio, and thermal structure.
 
@@
 At each point in the grid, we compute forward models to determine self-consistent, radiative-convective temperature-pressure (T-P) profiles.
-(\textbf{Mike: citations?}) We determine the molecular abundances in each atmospheric layer assuming thermochemical equilibrium \citep[calculated with the NASA CEA routine;][]{gordon94}.
+We determine the molecular abundances in each atmospheric layer assuming thermochemical equilibrium \citep[calculated with the NASA CEA routine;][]{gordon94}.
 We include opacity from the major absorbers expected for a hot Jupiter atmosphere, including H$_2$O, CO, CO$_2$, TiO, VO, FeH, and H$_2$-H$_2$ CIA.
@@
 We fit this model to the dayside and nightside emission spectra (phases $\phi = 0.5$ and $0.1$).
-
-\begin{figure}
-\includegraphics[width = 0.5\textwidth]{Figures/WASP-103b_grid_DAYSIDE_stair_pairs_02.pdf}
-\caption{Posterior distributions for WASP-103b's atmospheric heat redistribution, metallicity, and C/O, from a grid-based fit to the dayside emission spectrum.
-The histograms on the diagonal show the marginalized distribution of each parameter, with dashed lines indicating the median and surrounding 68\% credible interval.
-The blue lines correspond to solar metallicity (1) and C/O (0.54).
-The 2D histograms mark the 1, 2, and 3$\,\sigma$ credible regions in dark, medium, and light blue, respectively.}
-\label{fig:composition}
-\end{figure}
 
@@
 The best fit model has a moderately enhanced metallicity ($23\times$ solar), carbon-to-oxygen equal to 0.76, poor heat redistribution, and a thermal inversion (temperature increasing with altitude).
+
+\begin{figure}
+\includegraphics[width = 0.5\textwidth]{Figures/xsec_FULL.pdf}
+\caption{Abundance weighted absorption cross-sections illustrating the important opacity sources at the photospheric pressure level (5 mbar).
+The strong CO feature at 4.5\,$\mu$m contributes to the high planet-to-star flux at that wavelength.
+Water, hydrides/oxides, and the H- bound-free opacities all play a role in shaping the \HST/WFC3 spectrum.}
+\label{fig:opacities}
+\end{figure}
 
@@
 
-\begin{figure}
-\includegraphics[width = 0.5\textwidth]{Figures/xsec_FULL.pdf}
-\caption{Abundance weighted absorption cross-sections illustrating the important opacity sources at the photospheric pressure level (5 mbar).
-The strong CO feature at 4.5\,$\mu$m contributes to the high planet-to-star flux at that wavelength.
-Water, hydrides/oxides, and the H- bound-free opacities all play a role in shaping the \HST/WFC3 spectrum.}
-\label{fig:opacities}
-\end{figure}
-
 Figure\,\ref{fig:summary} shows a summary of the temperature-pressure profile and abundances for the best fit model.
@@
 The observations are sensitive to pressures of $\sim0.01 - 0.001$ bar, which spans the tropopause, where temperature begins to increase and the water abundance drops by more than an order of magnitude.
-
-In Figure\,\ref{fig:composition}, we show the posterior distributions from the grid retrieval.
-We infer a range in metallicity of $23^{+29}_{-13}\times$ solar, somewhat higher than expected based on Jupiter's metal enrichment \citep[$3-5\times$ solar;][]{wong04} and the trend toward decreasing metallicity with increasing planet mass observed for the Solar System and exoplanets \cite[e.g.][]{kreidberg14b}.
-However, planet population synthesis models predict some scatter in atmospheric metallicity.
-Planets near WASP-103b's mass ($1.5\,M_\mathrm{Jup}$) are expected to have metallicities ranging from roughly $1-10\times$ solar \citep{mordasini16}.
-Our result for WASP-103b lies on the upper end of this range, and may be indicative of intrinsic scatter in the mass-atmospheric metallicity relation.
-
-The retrieved C/O is consistent with solar, with a $1\sigma$ confidence interval of $0.54 - 0.85$.
-We infer an upper limit on C/O of 0.9 at $3\,\sigma$ confidence, driven by the fact that the atmospheric chemistry is expected to change dramatically when C/O exceeds unity.
-For a carbon-rich composition, the equilibrium abundance of methane relative to CO increases by orders of magnitude compared to an oxygen-rich  composition \citep[e.g.][]{madhusudhan11}.
-Our \Spitzer\ eclipse depths are sensitive to the relative abundance of these species, so we can confidently rule out a carbon-rich composition despite the lack of spectrally resolved features.
-
-We infer a heat redistribution $f = 0.4^{+0.03}_{-0.02}$.
-The $f$ parameter is allowed to range from 0 (isotropic heat distribution) to 0.5 (dayside emission only).
-Our estimate of $f$ is close to the maximum, indicating inefficient transport of heat to the nightside.
-Poor heat transport is observed in other very hot planets as well, due to damping of heat-propagating waves by fast radiative cooling or frictional drag in a partially ionized atmosphere \citep{komacek16}.
-The heat redistribution is correlated with atmospheric metallicity because increasing metallicity pushes the photosphere to higher, cooler pressure levels (\textbf{Mike: does this make sense, since the atmosphere has a thermal inversion?}).
-
-We note that an important caveat for our results is that the best fit model is not a perfect fit to the data (with $\chi_\nu = 1.77$), so the uncertainties produced by the MCMC may be underestimated.
-Furthermore, the inferred C/O and metallicity are highly sensitive to the planet-to-star flux at \Spitzer\ $4.5\,\mu$m, which is the worst fit data point.
-To fit this data point, the model favors super-solar metallicities and C/O, which drive up the CO abundance (the dominant absorber at $4.5\,\mu$m).
-Given that the result hinges on a single photometric band and there are no spectrally resolved molecular features to constrain the temperature-pressure profile or which absorbers are present, we caution against over-interpreting these results until wider spectral coverage is available.
-%As a test of our modeling approach, we also performed a retrieval in which the T/P profile was allowed to vary.
 
@@
 \end{figure}
+
+In Figure\,\ref{fig:composition}, we show the posterior distributions from the grid retrieval.
+We infer a range in metallicity of $23^{+29}_{-13}\times$ solar, somewhat higher than expected based on Jupiter's metal enrichment \citep[$3-5\times$ solar;][]{wong04} and the trend toward decreasing metallicity with increasing planet mass observed for the Solar System and exoplanets \cite[e.g.][]{kreidberg14b}.
+However, planet population synthesis models predict some scatter in atmospheric metallicity.
+Planets near WASP-103b's mass ($1.5\,M_\mathrm{Jup}$) are expected to have metallicities ranging from roughly $1-10\times$ solar \citep{mordasini16}.
+Our result for WASP-103b lies on the upper end of this range, and may be indicative of intrinsic scatter in the mass-atmospheric metallicity relation.
+
+\begin{figure}
+\includegraphics[width = 0.5\textwidth]{Figures/WASP-103b_grid_DAYSIDE_stair_pairs_02.pdf}
+\caption{Posterior distributions for WASP-103b's atmospheric heat redistribution, metallicity, and C/O, from a grid-based fit to the dayside emission spectrum.
+The histograms on the diagonal show the marginalized distribution of each parameter, with dashed lines indicating the median and surrounding 68\% credible interval.
+The blue lines correspond to solar metallicity (1) and C/O (0.54).
+The 2D histograms mark the 1, 2, and 3$\,\sigma$ credible regions in dark, medium, and light blue, respectively.}
+\label{fig:composition}
+\end{figure}
+
+The retrieved C/O is consistent with solar, with a $1\sigma$ confidence interval of $0.54 - 0.85$.
+We infer an upper limit on C/O of 0.9 at $3\,\sigma$ confidence, driven by the fact that the atmospheric chemistry is expected to change dramatically when C/O exceeds unity.
+For a carbon-rich composition, the equilibrium abundance of methane relative to CO increases by orders of magnitude compared to an oxygen-rich  composition \citep[e.g.][]{madhusudhan11}.
+Our \Spitzer\ eclipse depths are sensitive to the relative abundance of these species, so we can confidently rule out a carbon-rich composition despite the lack of spectrally resolved features.
+
+We infer a heat redistribution $f = 0.4^{+0.03}_{-0.02}$.
+The $f$ parameter is allowed to range from 0 (isotropic heat distribution) to 0.5 (dayside emission only).
+Our estimate of $f$ is close to the maximum, indicating inefficient transport of heat to the nightside.
+Poor heat transport is observed in other very hot planets as well, due to damping of heat-propagating waves by fast radiative cooling or frictional drag in a partially ionized atmosphere \citep{komacek17}.
+The heat redistribution is correlated with atmospheric metallicity because increasing metallicity pushes the photosphere to higher pressure levels.
+
+We note that an important caveat for our results is that the best fit model is not a perfect fit to the data (with $\chi_\nu = 1.77$), so the uncertainties produced by the MCMC may be underestimated.
+Furthermore, the inferred C/O and metallicity are highly sensitive to the planet-to-star flux at \Spitzer\ $4.5\,\mu$m, which is the worst fit data point.
+To fit this data point, the model favors super-solar metallicities and C/O, which drive up the CO abundance (the dominant absorber at $4.5\,\mu$m).
+Given that the result hinges on a single photometric band and there are no spectrally resolved molecular features to constrain the temperature-pressure profile or which absorbers are present, we caution against over-interpreting these results until wider spectral coverage is available.
+
+%As a test of our modeling approach, we also performed a retrieval in which the T/P profile was allowed to vary.
 
@@
 
-%\subsection{Climate}
-%Heat redistribution, Bond albedo, inversions
-
-%\subsection{Bond Albedo}
-
 \section{Comparison with GCMs}
@@
 To explore the three-dimensional effects of atmospheric dynamics, we ran several GCM models to compare with the measured phase-resolved spectra.
-(\textbf{Vivien: paragraph describing GCM}).
+(\textbf{Vivien: add text describing GCM}).
 Our nominal GCM was a cloud-free, solar composition atmosphere with TiO/VO opacity and no added drag.
@@
 Lorentz drag can occur in the hottest exoplanet atmospheres, which may be partially ionized and coupled to the background magnetic field.
-We parameterized the drag (\textbf{Vivien: how did you model drag?}), with timescales of $\tau_\mathrm{drag} = 10^3$ and $10^4$ s, which we label $\tau_\mathrm{drag3}$ and $\tau_\mathrm{drag4}$.
+We parameterized the drag (\textbf{Vivien: how did you model drag?}), with timescales of $\tau_\mathrm{drag} = 10^3$ and $10^4$ s.
+We label the drag models $\tau_\mathrm{drag3}$ and $\tau_\mathrm{drag4}$, respectively.
 
-To assess how well the GCM predictions reproduce the data, we calculate the amplitude and hot spot offset for all the models (listed in Table\,\ref{tab:amps_offs}).
-The models with drag included are generally better fits, with phase variation amplitude near unity and a hot spot offset near zero for all three band-passes.
-The nominal model and metal-enhanced composition ([Fe/H] = 0.5) both have a phase curve offset that is too large (
+To assess how well the GCM predictions reproduce the data, we calculated the amplitude and hot spot offset for all the models (listed in Table\,\ref{table:amps_offsets}).
+The observed hotspot offsets ($0.3 - 2.0$ degrees) are best reproduced by the $\tau_\mathrm{drag3}$ and $\tau_\mathrm{drag4}$ models, which have small offsets due to slower wind speeds.
+The nominal and metal-enhanced GCMs both have offsets that are too large (10-20 degrees).
+On the other hand, the drag models do not match the observed phase curve amplitudes (with values near unity, in contrast to the 0.8 - 0.9 that is observed).
+As shown in Figure\,\ref{fig:gcmcomparison}, the drag models predict the dayside planet-to-star flux fairly accurately, but underestimate the planet-to-star flux away from the substellar point.
+(\textbf{Vivien and others: how do we heat up the nightside to match the data better?})
 
-Figure\,\ref{fig:gcmcomparison} shows GCM predictions compared to the best fit model to the WFC3 phase curve.
-The WFC3 bandpass is near the peak of the planet's thermal emission, so it provides a good test of whether the GCM reproduces the properties of the planet.
-
-However, in the WFC3 bandpass the drag models underestimate the flux at longitudes away from the substellar point.
-For example, the FIXME model predicts 20\% less flux than is observed at quadrature.
-\textbf{Vivien: are these fast drag timescales even reasonable?}).
-
-FIXME: change taudrag3 label. change text about unphysical phase curve ampltiude
-
-%This model qualitatively reproduces some features of the data, such as the large day-night temperature contrast; however, it predicts a larger offset in peak brightness from the substellar point than we observe.
-The models with added drag more closely reproduce the small hotspot offset that is observed.
-The main effect of drag is to slow down advection of heat to the nightside, which shifts the peak brightness closer to the substellar point.
-The best fit WFC3 phase curve has a hotspot offset of FIXME.
-The drag models have offsets of $0.2$ and $2.3$ degrees for $\tau_\mathrm{drag} = 10^3$ and $10^4$ s, compared to $15$ degrees for the nominal GCM.
-The drag models also provide a good match to the observed dayside flux, for drag timescales in the range $\tau_\mathrm{drag} = 10^3 - 10^4$ s.
-
-We also compared the GCM output to the temperature maps retrieved with \texttt{spiderman}.
-Figure\,\ref{fig:model_comparison} shows the 0.1 bar temperature map for the $\tau_\mathrm{drag3}$ GCM compared to the best it models.
-The GCM has a minimum and maximum temperature of $920$ and $3360$ K, which is most comparable to the fit from the spherical harmonic model.
-The GCM nightside temperatures are around $300$ K cooler than the spherical harmonics fit,
-
-. The polar regions are the most discrepant, with temperatures are about $1000$ K cooler in the GCM than the spherical harmonics model. FIXME
+We also compared the GCM output to temperature maps retrieved with \texttt{spiderman}.
+Figure\,\ref{fig:model_comparison} shows the 0.01 bar temperature map for the $\tau_\mathrm{drag3}$ GCM compared to the best fit models.
+At this pressure, the GCM has minimum and maximum temperatures of $580$ and $3520$ K.
+The temperature gradient from the dayside to the terminator is intermediate between the kinematic and spherical harmonics models.
+The GCM predicts a cooler nightside than all models except the two-temperature model.
+We note that the GCM does not provide a perfect fit to the data, whereas multiple \texttt{spiderman} maps fit quite well, with large differences in temperature between them (see Table
+\,\ref{table:model_comparison}). Determining which models (if any) accurately describe the climate will require higher precision phase curves and/or eclipse mapping \citep[e.g.][]{dewit12}.
 
@@
 As discussed in \S\,\ref{sec:composition}, water dissociation and H- opacity are needed to explain the dayside emission spectrum.
-Figure\,\ref{fig:gcmcomposition} shows the photospheric abundances of H$_2$O and H- compared to the predicted temperature for the $\tau_\mathrm{drag3}$ GCM.
+Figure\,\ref{fig:gcmcomparison} shows the photospheric abundances of H$_2$O and H- compared to the predicted temperature for the $\tau_\mathrm{drag3}$ GCM.
 The water abundance drops by $\sim10$ at the substellar point, and the H- opacity increases by $\sim100$.
-
-\textbf{Vivien: did you run a cloudy model?}
+By contrast, CO remains intact throughout the atmosphere.
+Our observations are not precise enough to detect water features on the nightside of the planet (see \S\,\ref{sec:comparison}, but future high precision data may be sensitive to these features, and will help constrain the strength of horizontal transport in the atmosphere \citep{agundez14}.
 
@@
 To explore the effects of varying these parameters, we compared the spectra of WASP-103b to brown dwarfs and young directly imaged companions.
-The object properties are summarized in Table\,\ref{tab:sources}.
+The object properties are summarized in Table\,\ref{table:sources}.
 
@@
 Figure\,\ref{fig:planetstarcomparison} shows the flux-calibrated spectra (assuming a distance of 10 pc).
-
-%TWA 22A - Bonnefoy+2014 (Bonnefoy 09), RXS - Lafren 08,10 (H magfrom Lafren 08), J1610 - Aller+13
-%dist: teixeira08, 
 The directly imaged spectra are taken from \cite{wahhaj11, aller13, bonnefoy14}.
@@
 \acknowledgments
-Some of the data presented in this paper were obtained from the Mikulski Archive for Space Telescopes (MAST).
+The data presented in this paper were obtained from the Mikulski Archive for Space Telescopes (MAST) and the NASA/IPAC Infrared Science Archive.
 STScI is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS5-26555.
-Support for MAST for non-HST data is provided by the NASA Office of Space Science via grant NNX13AC07G and by other grants and contracts.
+The Infrared Science Archive is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration.
 This work also made use of the Python packages  SciPy and NumPy \citep{jones_scipy_2001, van2011numpy}.

### 2018-01-05 Figures/gcm_comparison.py

@@ -70,7 +70,8 @@ for i, g in enumerate(gcms):
 
 
 
-f = "./WFC3_best_fits/old_white_fits/bestfit_spherical.pic"
+#f = "./WFC3_best_fits/old_white_fits/bestfit_spherical.pic"
+f = "./WFC3_best_fits//bestfit_sincos.pic"
 p = pickle.load(open(f, 'rb'))
 d, m, par = p[0], p[1], p[2]		#stores data,  model, and best fit parameters into d, m, & par
 dilution = d.dilution + 1.

### 2018-01-05 ms.tex
adding summary

@@
 In the near-infrared, where water is the dominant absorber, some spectra show water absorption features, some show emission features, and some are consistent with blackbody models \citep{madhusudhan11, crossfield12, stevenson14b, haynes15, evans16, beatty17a, beatty17b, sheppard17, arcangeli18, mansfield18}.
-A variety of explanations were proposed for these results, including low metallicity or high carbon-to-oxygen compositions, dayside clouds, and isothermal or inverted temperature profiles caused by TiO/VO absorption in the upper atmosphere.
+A variety of explanations have been proposed for these results, including low metallicity or high carbon-to-oxygen compositions, dayside clouds, and isothermal or inverted temperature profiles caused by TiO/VO absorption in the upper atmosphere.
 Recently, \cite{arcangeli18} showed that water dissociation on the hot dayside plays an important role in the atmospheres of these ultra-hot planets and may be responsible for some of the blackbody-like near-IR spectra.
@@
 In \S\,\ref{sec:gcm} and \ref{sec:comparison}, we compare the observations to GCM predictions and spectra from similar temperature stars and directly imaged companions.
-\S\,\ref{sec:discussion} concludes.
+\S\,\ref{sec:summary} concludes.
 
@@
 
-The main spectral feature over the wavelength range we consider is water.
-To quantitatively compare the water feature amplitude for different objects, we define an amplitude $A = (R_\mathrm{1.3} - R_\mathrm{1.5})/F_\mathrm{1.3}$, where $F_\mathrm{X}$ is the average flux in a wavelength bin $0.1\,\mu$m wide centered on a wavelength $X$, and $R_\mathrm{X}$ is the bin-averaged residual from the best fit blackbody.
-These intervals were chosen such that all of the data have complete spectral coverage over the bin.
-
 \begin{figure*}
 \includegraphics[width = 1.0\textwidth]{Figures/spectra_comparison.pdf}
-\caption{Spectra for WASP-103b (left column) compared to brown dwarfs (middle) and directly imaged companions (right).
+\caption{Flux-calibrated spectra for WASP-103b (left column) compared to brown dwarfs (middle) and directly imaged companions (right), assuming a distance of 10 pc.
 The WASP-103b spectra are from the nightside (phase 0.1, top row), quadrature (phase 0.25, middle) and the dayside (phase 0.5, bottom).
@@
 The dotted gray line corresponds to the best fit blackbody.
-Effective temperatures are listed in the upper right corners.}
+Effective temperatures are listed in the upper right corners.
+The wavelength bins used to calculate the water feature amplitude $A_1$ are shaded in gray.}
 \label{fig:planetstarcomparison}
 \end{figure*}
+
+The main spectral feature over the wavelength range we consider is water.
+To quantitatively compare the water feature amplitude for different objects, we define an amplitude $A = (F_{\lambda_1, \lambda_2} - F_{\lambda_3, \lambda_4})/F_{\lambda_1,\lambda_2}$, where $F_{\lambda_x, \lambda_y}$ is the weighted mean flux in a wavelength bin $x - y$.
+We calculated the water feature amplitude for two choices of wavelength bins.
+For the first, $A_1$, we considered data in and out of the water band, with $\lambda_{1,2,3,4} = 1.15, 1.3, 1.35, 1.5\,\mu$m.
+The ground-based direct imaging data doesn't span this entire wavelength, so we also define an amplitude $A_2$ with $\lambda_{1,2,3,4} = 1.2, 1.35, 1.5, 1.65\,\mu$m.
+The estimated amplitudes and uncertainties are listed in Table\,\ref{table:sources}.
+
+For WASP-103b, $A_1$ is consistent with zero at all three orbital phases. The brown dwarfs have similar
 
@@
 
-\section{Discussion and Conclusions}
-\label{sec:discussion}
-One-dimensional retrieval is probably wrong, since we showed the dayside may have a large temperature gradient -> should work on this in the future.
+\section{Summary}
+\label{sec:summary}
+We observed thermal phase curves of the hot Jupiter WASP-103b measured with \HST/WFC3 time series spectroscopy ($1.15 - 1.65\,\mu$m) and \Spitzer/IRAC broadband photometry ($3.6$ and $4.6\,mu$m bands).
 
-There are many factors contributing to the blackbody spectra --
-weak water xsec contrast, isothermal pt, H-, and dissociated water, gravity (cite T. Beatty)
+\begin{itemize}
+	\item{We fit the climate using the \texttt{spiderman} package \citep{louden17}}
+	\item{The phase curves have large amplitude ($0.8 -0.9\times$ secondary eclipse depth)}
+	\item{The phase-resolved spectra are consistent with a blackbody model, but there is an emission feature at \Spitzer\ wavelengths. Why is it isothermal? cite Beatty} 
+	\item{We characterized the composition with a 1D grid-based retrieval. The atmospheric metallicity is super-solar () and > 1 at $3\,\sigma$ confidence. larger than  } 
+	\item{We compared the phase curves to 3D GCM predictions}
+	\item{We compared the spectra to brown dwarfs and directly imaged companions of similar temperature}
+\end{itemize}
 
-Cite Feng et al. 2016.
+%Cite Feng et al. 2016.
 
-H- is important.
+%H- is important.
 
-How does composition compare to other HJs (esp W43b)
-The spectrum is similar to observations of several other ultra-hot Jupiters \citep[][]{arcangeli18, mansfield18}, but qualitatively different from slightly cooler planets, which show water absorption features in the near-infared \citep[e.g.][]{kreidberg14b, line16}.
+%How does composition compare to other HJs (esp W43b)
+%The spectrum is similar to observations of several other ultra-hot Jupiters \citep[][]{arcangeli18, mansfield18}, but qualitatively different from slightly cooler planets, which show water absorption features in the near-infared \citep[e.g.][]{kreidberg14b, line16}.
 
-eclipse mapping to break degeneracy in models
+%eclipse mapping to break degeneracy in models
 
-We rule out the low metallicity and or high C/O models
+%We rule out the low metallicity and or high C/O models
 
-confirm prediction that TiO is present in the hottest planets
+%confirm prediction that TiO is present in the hottest planets
 
-what do the hot spot offsets and amplitudes mean?
+%what do the hot spot offsets and amplitudes mean?
 

### 2018-01-05 ms.tex
summary

@@
 	\includegraphics[width = 1.0\textwidth]{Figures/GCM_abundances.eps}
-\caption{Abundances of key molecular species for different viewing geometries, from the $\tau_\mathrm{drag3}$ GCM.}
+	\caption{Row (1): photospheric temperatures for the $\tau_\mathrm{drag3}$ GCM for different viewing geometries.
+The substellar point corresponds to $\alpha = 0$ and the antistellar point is $\alpha = \pm 180$.
+Row (2) indicates the ratio of pressures probed in and out of the water band.
+On the dayside, the opacity out of the water band is filled in by absorption from H- and TiO/VO.
+Rows (3-4) show the abundances of H$_2$O and H-.
+The dayside temperatures, water dissociates and the photospheric abundance drops by $\sim10$.
+}
 \label{fig:GCMabundance}
@@
 \label{sec:summary}
-We observed thermal phase curves of the hot Jupiter WASP-103b measured with \HST/WFC3 time series spectroscopy ($1.15 - 1.65\,\mu$m) and \Spitzer/IRAC broadband photometry ($3.6$ and $4.6\,mu$m bands).
+We observed thermal phase curves of the hot Jupiter WASP-103b measured with \HST/WFC3 time series spectroscopy ($1.15 - 1.65\,\mu$m) and \Spitzer/IRAC broadband photometry ($3.6$ and $4.6\,\mu$m bands).
 
 \begin{itemize}
-	\item{We fit the climate using the \texttt{spiderman} package \citep{louden17}}
-	\item{The phase curves have large amplitude ($0.8 -0.9\times$ secondary eclipse depth)}
-	\item{The phase-resolved spectra are consistent with a blackbody model, but there is an emission feature at \Spitzer\ wavelengths. Why is it isothermal? cite Beatty} 
-	\item{We characterized the composition with a 1D grid-based retrieval. The atmospheric metallicity is super-solar () and > 1 at $3\,\sigma$ confidence. larger than  } 
-	\item{We compared the phase curves to 3D GCM predictions}
-	\item{We compared the spectra to brown dwarfs and directly imaged companions of similar temperature}
+	\item{The phase curves have large amplitudes ($0.8 -0.9\times$ the secondary eclipse depth), and small offsets in peak brightness from the substellar point (consistent with zero degrees at all wavelengths).
+These characteristics indicate inefficient redistribution of heat to the nightside, as seen in other very hot Jupiters \citep{komacek17}.}
+	\item{We fit the phase variation with the \texttt{spiderman} package \citep{louden17} to evaluate different models of the planets climate.
+A spherical harmonic temperature map generally provides the best fit to the data; however, all the maps produce reasonable fits ($\chi^2_\nu$ near unity), and there are large differences in temperature between them ($> 1000$ K).
+Breaking the degeneracy between different climate maps will require higher precision phase curves and/or secondary eclipse mapping \citep[e.g.][]{dewit12}.}
+	\item{We calculated phase-resolved spectra in ten orbital phase bins.
+The \HST/WFC3 spectra are consistent with  blackbody emission from the planet at all orbital phases.
+The best fit effective temperatures ranges from 1920 K (phase $\phi = 0.1$) to 3010 K on the dayside.
+We attribute the absence of water features at WFC3 wavelengths to (1) H$_2$O dissociation on the dayside, (2) additional near-IR opacity from H-, TiO/VO and FeH, (3) a small temperature gradient at the pressure levels probed by the data.
+The \Spitzer\ data are \emph{not} consistent with a blackbody: there is an infrared emission feature at phases where the substellar point is visible ($\phi = 0.2 - 0.7$), which transitions to an absorption feature on the nightside ($\phi = -0.1 - 0.1$).
+We attribute these features to CO and changing thermal structure from the dayside to the nightside.}
+	\item{We characterized the composition with a 1D grid-based retrieval that assumes thermochemical and radiative-convective equilibrium.
+The atmosphere is moderately metal-enriched ($23^{+29}_{-13}\times$ solar; and $>1\times$ solar at $3\,\sigma$ confidence).
+This value is somewhat higher than what is observed for other gas giants and predicted by models \citep[e.g.][]{wong04, kreidberg14b, mordasini16}, and may be indicative of intrinsic scatter in the relationship between atmospheric metallicity and planet mass.
+However, the metallicity is strongly sensitive to the $4.5\,\mu$m \Spitzer\ eclipse depth, and additional observations would be useful in confirming the metal enhancement.
+In addition to metallicity, we also infer an upper limit on the carbon-to-oxygen ratio of 0.9 ($3\,\sigma$ confidence).
+This estimate agrees with expectations from planet formation models that pollution from water ice in planetesimals leads to $\mathrm{C/O} < 1$ in gas giant atmospheres \citep{mordasini16, espinoza17}.
+The best fit temperature pressure profile has a thermal inversion from $\sim10^{-2} - 10^{-3}$ bars due to TiO/VO absorption at high altitudes.}
+	\item{We ran several 3D GCMs to compare to the data, including a nominal model with a cloud-free, solar composition, a metal-enriched model ([Fe/H] = 0.5), and two models with Lorentz drag.
+The GCMs with Lorentz drag have slower wind speeds and provide the best match to the data small hotspot offsets that are observed, but they underpredict the palent's nightside flux.}
+	\item{We compared the spectra of WASP-103b at phases 0.5 (dayside0, 0.25 (quadrature), and 0.1 (nightside) to brown dwarfs and directly imaged companions of similar temperature.
+Both the brown dwarfs and imaged companions show evidence for water features, as defined by FIXME spectral index.
+Cite Beatty }
 \end{itemize}
+
+Future observations with JWST
+planets are round and complicated
 

### 2018-01-07 ms.tex
abstract

@@
 \author{Laura Kreidberg}
-\affiliation{Harvard Society of Fellows\
-78 Mt. Auburn St.\\
-Cambridge, MA 02138, USA}
 \affiliation{Harvard-Smithsonian Center for Astrophysics\
@@
 Cambridge, MA 02138}
+\affiliation{Harvard Society of Fellows}
 
@@
 \begin{abstract}
-	We present thermal phase curve measurements for the hot Jupiter WASP-103b observed with \emph{Hubble}/Wide Field Camera 3 and \emph{Spitzer}/IRAC.
-The dayside planet-to-star flux ranges from FIXME to FIXME at $1.1 - 4.5\,\mu$m.
-The phase curves are symmetric and large amplitude, indicative of poor redistribution.
-We fit the phase curves with the SPIDERMAN package to determine the brightness distribution in the photosphere, and find the peak dayside temperature ranges from FIXME to FIXME depending on model.
-We also generate phase-resolved spectra, which are consistent with blackbody models for the planet's emission at near-infrared wavelengths, but show strong emission features in the \Spitzer\ bands.
-We attribute these features to CO emission and a thermal inversion.
-The retrieved atmospheric composition is more metal-enriched than other hot Jupiters (FIXME).
-The carbon-to-oxygen ratio is consistent with solar composition.
-The absence of water features is due to BLAH.
-We compare the phase curves to general circulation models and find that atmospheric drag is required.
-We also compare the spectra to brown dwarfs and young directly imaged companions and find that the water features are significantly diminished in amplitude.
-power of phase curve observations to elucidate the three-dimensional structure of exoplanet atmospheres.
-
-inversion on the dayside but not on the nightside
+	We present thermal phase curve measurements for the hot Jupiter WASP-103b observed with \emph{Hubble}/WFC3 and \emph{Spitzer}/IRAC.
+The dayside planet-to-star flux is $0.151\pm0.015\%$, $0.446\pm0.38\%$, and $0.569\pm0.014\%$ in bandpasses centered at $1.4$, $3.6$, and $4.5\mu$m, respectively.
+The phase curves have large amplitudes and negligible hotspot offsets, indicative of poor heat redistribution to the nightside.
+We fit the phase variation with a range of climate maps and find they all provide reasonable fits to the data, but have large degeneracies in temperature (up to 1000 K for a given latitude/longitude).
+The phase-resolved spectra are consistent with blackbodies in the WFC3 bandpass, with effective temperatures ranging from 2000 K on the nightside to 3000 K on the dayside.
+However, the dayside spectrum has a strong feature in the \Spitzer\ bands, which we attribute to CO emission and a thermal inversion.
+The emission feature is not present on the nightside, indicating changing thermal structure with longitude.
+We retrieved the atmospheric composition with a 1D thermochemical equilibrium model and found the composition is moderately metal-enriched ($\mathrm{[Fe/H]} =  23^{+29}_{-13}\times$ solar), and the carbon-to-oxygen ratio is below 0.9 at $3\,\sigma$ confidence.
+In contrast to other hot Jupiters, we do not detect significant water absorption, which we attribute to H$_2$O dissociation and additional opacity from H- and TiO/VO.
+We compare the phase curves to 3D general circulation models and find that atmospheric drag is required to explain the small hotspot offsets, but that these models overpredict the phase curve amplitude.
+We also compare the WASP-103b spectra to brown dwarfs and young directly imaged companions and find they have significantly larger water features, indicating that surface gravity and irradiation environment play an important role in shaping the spectra of hot Jupiters.
 \end{abstract}
@@
 The free parameters were the sine curve amplitude and phase offset.
-For the second approach, we used the \texttt{SPIDERMAN} package \citep{louden17} to model $F_p/F_s$.
+For the second approach, we used the \texttt{spiderman} package \citep{louden17} to model $F_p/F_s$.
 This package allows users to input a climate map (temperature or brightness as a function of latitude and longitude), and generate the corresponding flux ratio for an observation at time $t$.
@@
 This figure shows results from the spherical harmonics model for the thermal phase variation and has instrument systematics removed.
-Broadly speaking, the phase curves show large amplitude phase variation, ranging from 1.5 parts-per-thousand (ppt) in the WFC3 bandpass to 5 ppt in \Spitzer\ Channel 2.
+Broadly speaking, the phase curves show large dayside planet-to-star flux values, ranging from $0.151\pm0.015\%$, $0.446\pm0.38\%$, and $0.569\pm0.014\%$ in the WFC3 white light curve, and \Spitzer\ $3.6$, and $4.5\mu$m bandpasses, respectively.
 The planet flux changes significantly with orbital phase in all three of the data sets, suggesting a strong gradient from dayside to nightside temperature, and peak brightness occurs near phase 0.5.
@@
 Since our model does not fit eclipse depth as a free parameter, we estimated the dayside emission spectrum as follows.
-We used \texttt{SPIDERMAN}'s eclipse\_depth method to calculate the average planet-to-star flux for the best-fit model during secondary eclipse.
+We used \texttt{spiderman}'s eclipse\_depth method to calculate the average planet-to-star flux for the best-fit model during secondary eclipse.
 To estimate uncertainties, we took the standard deviation of the residuals of the in-eclipse data points, then added this value in quadrature to the standard deviation of the residuals of the out-of-eclipse data.
 This quadrature sum accounts for the uncertainty in the baseline flux.
-To account for red noise in the \Spitzer\ $3.6\,\mu$ light curve, we use the approach of \cite{pont06} to determine the red noise contribution on the timescale of the eclipse.
+To account for red noise in the \Spitzer\ $3.6\,\mu$m light curve, we use the approach of \cite{pont06} to determine the red noise contribution on the timescale of the eclipse.
 We add the estimated red noise in quadrature, which increases the uncertainty on planet-to-star flux by a factor of $2.5$.
@@
 \includegraphics[width = 1.0\textwidth]{Figures/emission_spectra.pdf}
-\caption{Phase-resolved emission spectra (points) compared to the best fit blackbody (blue line) and the GCM with $\tau_\mathrm{drag3}$ s.
+\caption{Phase-resolved emission spectra (points) compared to the best fit blackbody (blue line) and the GCM with $\tau_\mathrm{drag3}$.
 Phases $\phi = 0.5$ and $0.0$ are centered on the substellar and anti-stellar points, respectively.}
@@
 	\tablehead{
-	\colhead{Orbital Phase} & \colhead{$T_\mathrm{eff}$} & \colhead{$\chi^2_\nu$}}
+	\colhead{Orbital Phase} & \colhead{$T_\mathrm{eff}$ (K)} & \colhead{$\chi^2_\nu$}}
 		\startdata
@@
 The nominal and metal-enhanced GCMs both have offsets that are too large (10-20 degrees).
-On the other hand, the drag models do not match the observed phase curve amplitudes (with values near unity, in contrast to the 0.8 - 0.9 that is observed).
-As shown in Figure\,\ref{fig:gcmcomparison}, the drag models predict the dayside planet-to-star flux fairly accurately, but underestimate the planet-to-star flux away from the substellar point.
+On the other hand, the phase curve amplitudes are better matched by the nominal GCM than either of the drag models.
+The most precise observed amplitude is $0.91\pm0.02$ (in the WFC3 bandpass), which is significantly smaller than the amplitudes predicted by the drag models (0.97, 0.99).
+As shown in Figure\,\ref{fig:gcmcomparison}, this large amplitude causes the drag models to underestimate the planet-to-star flux away from the substellar point.
 (\textbf{Vivien and others: how do we heat up the nightside to match the data better?})
@@
 By contrast, CO remains intact throughout the atmosphere.
-Our observations are not precise enough to detect water features on the nightside of the planet (see \S\,\ref{sec:comparison}, but future high precision data may be sensitive to these features, and will help constrain the strength of horizontal transport in the atmosphere \citep{agundez14}.
+Our observations are not precise enough to detect water features on the nightside of the planet (see \S\,\ref{sec:comparison}), but future high precision data may be sensitive to these features, and will help constrain the strength of horizontal transport in the atmosphere \citep{agundez14}.
 
@@
 
-The main spectral feature over the wavelength range we consider is water.
-To quantitatively compare the water feature amplitude for different objects, we define an amplitude $A = (F_{\lambda_1, \lambda_2} - F_{\lambda_3, \lambda_4})/F_{\lambda_1,\lambda_2}$, where $F_{\lambda_x, \lambda_y}$ is the weighted mean flux in a wavelength bin $x - y$.
+We compared the spectra over the wavelength range $1.1 - 1.7\mu$m.
+The dominant opacity source over this range is water, which has a forest of absorption lines near 1.4\,$\mu$m.
+Spectra for the brown dwarfs and imaged companions have noticeable features in the water band, whereas WASP-103b does not.
+To quantitatively compare the water feature amplitude for different objects, we define an amplitude $A = (F_{1,2} - F_{3,4})/F_{1,2}$, where $F_{1,2}$ is the weighted mean flux in a wavelength bin $\lambda_1 - \lambda_2$.
 We calculated the water feature amplitude for two choices of wavelength bins.
 For the first, $A_1$, we considered data in and out of the water band, with $\lambda_{1,2,3,4} = 1.15, 1.3, 1.35, 1.5\,\mu$m.
-The ground-based direct imaging data doesn't span this entire wavelength, so we also define an amplitude $A_2$ with $\lambda_{1,2,3,4} = 1.2, 1.35, 1.5, 1.65\,\mu$m.
+The ground-based direct imaging data doesn't span this entire wavelength range, so we also define an amplitude $A_2$ with $\lambda_{1,2,3,4} = 1.2, 1.35, 1.5, 1.65\,\mu$m.
 The estimated amplitudes and uncertainties are listed in Table\,\ref{table:sources}.
 
-For WASP-103b, $A_1$ is consistent with zero at all three orbital phases. The brown dwarfs have similar
+The $A_1$ and $A_2$ values are significantly lower for WASP-103b at dayside and quadrature than for brown dwarfs and imaged companions of similar temperature.
+WASP-103b typically has $A_1$ and $A_2$ consistent with zero, indicating no water absorption (in agreement with the analysis in \S\,\ref{sec:results} that showed water is depleted in the photosphere).
+By contrast, the brown dwarfs and young companions have significant water features, with drops in flux of about 20\% in the water band.
+This is not surprising: stars in the temperature range $2000 - 3000\,\mathrm{K}$ are well known to have prominent water features \citep{kirkpatrick93}.
+Based on the grid retrieval of WASP-103b's atmospheric composition, there are two reasons WASP-103b would exhibit different behavior at the same temperature.
+First, the atmosphere of WASP-103b is irradiated from above rather than below, leading to a more isothermal temperature profile and weaking spectral features.
+In addition, WASP-103b also has much lower surface gravity (log$g$ = 3.2 versus 4-5 for stars), which pushes the photosphere to lower pressures, where water dissociates more readily (\textbf{Mike: need a reference for this}).
+These factors are not relevant on the nightside, and WASP-103b may have water absorption features there; however, the current data are not precise enough to distinguish between a blackbody spectrum versus water features like those seen in the other objects.
 
@@
 	\tablehead{
-	\colhead{\,} & \colhead{Object} & \colhead{$T_\mathrm{eff}$} & \colhead{logg} & \colhead{H$_2$O A$_1$} & \colhead{H$_2$O A$_2$}}
+	\colhead{\,} & \colhead{Object} & \colhead{$T_\mathrm{eff}$ (K)} & \colhead{log\,$g$ (cgs)} & \colhead{H$_2$O A$_1$} & \colhead{H$_2$O A$_2$}}
 		\startdata
@@
 We observed thermal phase curves of the hot Jupiter WASP-103b measured with \HST/WFC3 time series spectroscopy ($1.15 - 1.65\,\mu$m) and \Spitzer/IRAC broadband photometry ($3.6$ and $4.6\,\mu$m bands).
+Here we summarize our conclusions about the atmosphere based on these measurements.
 
 \begin{itemize}
+	\item{The dayside secondary eclipse depths are FIXME, implying a dayside effective temperature of FIXME, making WASP-103b among the hottest hot Jupiters ever observed.}
 	\item{The phase curves have large amplitudes ($0.8 -0.9\times$ the secondary eclipse depth), and small offsets in peak brightness from the substellar point (consistent with zero degrees at all wavelengths).
 These characteristics indicate inefficient redistribution of heat to the nightside, as seen in other very hot Jupiters \citep{komacek17}.}
-	\item{We fit the phase variation with the \texttt{spiderman} package \citep{louden17} to evaluate different models of the planets climate.
-A spherical harmonic temperature map generally provides the best fit to the data; however, all the maps produce reasonable fits ($\chi^2_\nu$ near unity), and there are large differences in temperature between them ($> 1000$ K).
+	\item{We fit the phase variation with the \texttt{spiderman} package \citep{louden17} to evaluate different models of the planet's climate, including a two-temperature map, a physically-motivated kinematic map, and spherical harmonics.
+The spherical harmonic temperature map generally provides the best fit to the data; however, all the maps produce reasonable fits ($\chi^2_\nu$ near unity), and there are large differences in temperature between them (up to 1000 K at a given latitude/longitude).
 Breaking the degeneracy between different climate maps will require higher precision phase curves and/or secondary eclipse mapping \citep[e.g.][]{dewit12}.}
@@
 The \Spitzer\ data are \emph{not} consistent with a blackbody: there is an infrared emission feature at phases where the substellar point is visible ($\phi = 0.2 - 0.7$), which transitions to an absorption feature on the nightside ($\phi = -0.1 - 0.1$).
-We attribute these features to CO and changing thermal structure from the dayside to the nightside.}
+We attribute these features to CO absorption and changing thermal structure from the dayside to the nightside.}
 	\item{We characterized the composition with a 1D grid-based retrieval that assumes thermochemical and radiative-convective equilibrium.
@@
 	\item{We ran several 3D GCMs to compare to the data, including a nominal model with a cloud-free, solar composition, a metal-enriched model ([Fe/H] = 0.5), and two models with Lorentz drag.
-The GCMs with Lorentz drag have slower wind speeds and provide the best match to the data small hotspot offsets that are observed, but they underpredict the palent's nightside flux.}
-	\item{We compared the spectra of WASP-103b at phases 0.5 (dayside0, 0.25 (quadrature), and 0.1 (nightside) to brown dwarfs and directly imaged companions of similar temperature.
-Both the brown dwarfs and imaged companions show evidence for water features, as defined by FIXME spectral index.
-Cite Beatty }
+The GCMs with Lorentz drag have slower wind speeds and provide the best match to the data small hotspot offsets that are observed, but they underpredict the planet's nightside flux.}
+	\item{We compared the spectra of WASP-103b at phases 0.5 (dayside), 0.25 (quadrature), and 0.1 (nightside) to brown dwarfs and directly imaged companions of similar temperature.
+We quantify the strength of the water feature and find that both brown dwarfs and imaged companions show evidence for water absorption at $1.4\,\mu$m, whereas WASP-103b does not.
+We attribute the difference to two factors: WASP-103b's irradiation environment, which changes the temperature pressure profile, and its low surface gravity, which pushes the photosphere to higher altitudes where water dissociates more easily.}
 \end{itemize}

### 2018-01-07 Figures/get_average_WFC3_eclipse_depth.py

@@ -1,0 +1,13 @@
+import numpy as np
+
+def weighted_mean(data, err):            #calculates the weighted mean for data points data with std devs. err
+	ind = err != 0.0
+        weights = 1.0/err[ind]**2
+        mu = np.sum(data[ind]*weights)/np.sum(weights)
+        var = 1.0/np.sum(weights)
+        return [mu, np.sqrt(var)]                
+
+
+d = np.genfromtxt("espec_dayside.txt")
+
+print weighted_mean(d[0:10,1], d[0:10,2])

### 2018-01-07 ms.tex
fussing

@@
 We retrieved the atmospheric composition with a 1D thermochemical equilibrium model and found the composition is moderately metal-enriched ($\mathrm{[Fe/H]} =  23^{+29}_{-13}\times$ solar), and the carbon-to-oxygen ratio is below 0.9 at $3\,\sigma$ confidence.
-In contrast to other hot Jupiters, we do not detect significant water absorption, which we attribute to H$_2$O dissociation and additional opacity from H- and TiO/VO.
+In contrast to other hot Jupiters, we do not detect significant water absorption, which we attribute to partial H$_2$O dissociation and additional opacity from H- and TiO/VO.
 We compare the phase curves to 3D general circulation models and find that atmospheric drag is required to explain the small hotspot offsets, but that these models overpredict the phase curve amplitude.

### 2018-01-08 ms.tex
first draft

@@
 %\accepted{\today}
-\submitjournal{ApJ}
+%\submitjournal{ApJ}
+%\date{today}
 
@@
 \author{Laura Kreidberg}
-\affiliation{Harvard-Smithsonian Center for Astrophysics\
-60 Garden St.\\
-Cambridge, MA 02138}
-\affiliation{Harvard Society of Fellows}
+\affiliation{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138}
+\affiliation{Harvard Society of Fellows, 78 Mount Auburn Street, Cambridge, MA 02138}
+
+\author{Michael R. Line}
+\affiliation{School of Earth \& Space Exploration, Arizona State University, Tempe AZ 85287, USA}
 
 \author{Vivien Parmentier}
-\affiliation{Department of Planetary Sciences and Lunar and Planetary Laboratory, The University of Arizona}
-
-\author{Michael R. Line}
-\affiliation{Arizona State University}
+\affiliation{Aix Marseille Univ, CNRS, LAM, Laboratoire d’Astrophysique de Marseille, Marseille, France}
 
 \author{Kevin B. Stevenson}
-\affiliation{Space Telescope Science Institute}
+\affiliation{Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD 21218, USA}
 
 \author{Tom Louden}
-\affiliation{University of Warwick}
+\affiliation{Department of Physics, University of Warwick, Coventry, CV4 7AL, UK}
 
 \author{Mick\"{a}el Bonnefoy}
-\affiliation{Universit\'{e} Grenoble Alpes}
+\affiliation{Univ. Grenoble Alpes, IPAG, F-38000 Grenoble, France. CNRS, IPAG, F-38000 Grenoble, France}
 
 \author{Jacqueline K. Faherty}
-\affiliation{American Museum of Natural History}
+\affiliation{American Museum of Natural History, Department of Astrophysics, Central Park West at 79th Street, New York, NY 10034, USA}
 
 \author{Gregory L. Henry}
-\affiliation{Center of Excellence in Information Systems, Tennessee State University}
+\affiliation{Center of Excellence in Information Systems, Tennessee State University, Nashville, TN 37209, USA}
 
 \author{Keivan Stassun}
-\affiliation{Vanderbilt University}
+\affiliation{Vanderbilt University, Dept. of Physics and Astronomy, 6301 Stevenson Center Ln, Nashville TN, 37235, USA}
 
 \author{Jacob L. Bean}
-\affiliation{University of Chicago}
+\affiliation{Department of Astronomy \& Astrophysics, University of Chicago, 5640 S. Ellis Avenue, Chicago, IL 60637, USA}
 
-\author{Jonathan Fortney}
-\affiliation{University of California Santa Cruz}
+\author{Jonathan J. Fortney}
+\affiliation{Department of Astronomy and Astrophysics, University of California, Santa Cruz, CA 95064}
 
-\author{Adam Showman}
-\affiliation{Department of Planetary Sciences and Lunar and Planetary Laboratory, The University of Arizona}
+\author{Adam P. Showman}
+\affiliation{Department of Planetary Sciences and Lunar and Planetary Laboratory, University of Arizona, Tucson, Arizona 85721, USA
+}
 
 \author{Jean-Michel D\'{e}sert}
-\affiliation{University of Amsterdam}
+\affiliation{Anton Pannekoek Institute for Astronomy, University of Amsterdam, Science Park 904, 1098 XH Amsterdam, The Netherlands}
 
@@
 However, the dayside spectrum has a strong feature in the \Spitzer\ bands, which we attribute to CO emission and a thermal inversion.
-The emission feature is not present on the nightside, indicating changing thermal structure with longitude.
+The emission feature is not present on the nightside, suggesting changing thermal structure with longitude.
 We retrieved the atmospheric composition with a 1D thermochemical equilibrium model and found the composition is moderately metal-enriched ($\mathrm{[Fe/H]} =  23^{+29}_{-13}\times$ solar), and the carbon-to-oxygen ratio is below 0.9 at $3\,\sigma$ confidence.
@@
 We also compare the WASP-103b spectra to brown dwarfs and young directly imaged companions and find they have significantly larger water features, indicating that surface gravity and irradiation environment play an important role in shaping the spectra of hot Jupiters.
+These results highlight the 3D structure of exoplanet atmospheres and illustrate the importance of phase curve observations for understanding their complex chemistry and physics.
 \end{abstract}
@@
 Recently, \cite{arcangeli18} showed that water dissociation on the hot dayside plays an important role in the atmospheres of these ultra-hot planets and may be responsible for some of the blackbody-like near-IR spectra.
-In this work, we put these results in context investigate the global thermal structure of WASP-103b over a range of temperatures.
-FIXME
+In this work, we put these results in context by investigating the global thermal structure and composition of the ultra-hot Jupiter WASP-103b.
 
@@
 \S\,\ref{sec:fits} details the models fit to the phase curves.
-\S\,\ref{sec:results} we discuss results, including the phase-resolved spectra, a comparison of thermal phase variation models, and FIXME.
+\S\,\ref{sec:results} we discuss results, including the phase curve amplitudes and hotspot offsets, the phase-resolved spectra, and estimates of the planet's climate.
 In \S\,\ref{sec:gcm} and \ref{sec:comparison}, we compare the observations to GCM predictions and spectra from similar temperature stars and directly imaged companions.
@@
 We used \texttt{emcee} \citep{foremanmackey13} to fit the \HST/WFC3 light curves and differential evolution Monte Carlo for the \Spitzer\ fits \citep{braak06}.
-We ran the MCMC until convergence according to the Gelman-Rubin statistic FIXME.
-MCMC techniques only produce robust uncertainties when the noise is normally distributed and white, so to account for correlated noise in the $3.6\,\mu$m light curve (described in \S\,\ref{sec:fitquality}) we fit the wavelet model from \cite{carter09} (simultaneously with the other model parameters).
+We ran the MCMC until convergence according to the Gelman-Rubin statistic.
+MCMC techniques only produce robust uncertainties when the noise is normally distributed and white, so to account for correlated noise in the $3.6\,\mu$m light curve (described in \S\,\ref{sec:fitquality}) we fit the wavelet model from \cite{carter09} simultaneously with the other model parameters.
 We used a Haar wavelet and let the power spectral density of the red noise vary, following \cite{diamond-lowe14}.
@@
 
-This agreement is an encouraging sanity check; however, there are several model assumptions that may result in artificially tight constraints on the atmospheric properties.
+This agreement is an encouraging sanity check; however, there are several model assumptions that may result in artificially tight constraints on the atmospheric properties on the nightside.
 One challenge in modeling the nightside spectrum is that the shape of the T-P profile is unknown.
@@
 Rows (3-4) show the abundances of H$_2$O and H-.
-The dayside temperatures, water dissociates and the photospheric abundance drops by $\sim10$.
+At dayside temperatures, water dissociates and the photospheric abundance drops by $\sim10$.
 }
@@
 		\startdata
-		Hot Jupiter & W103b night & 1922 \pm 40 & 3.2 \pm 0.04 & 0.07 \pm 1.8\mathrm{e}-01 & -0.00 \pm 1.6\mathrm{e}-01 \\
-		\, & W103b quadrature & 2408 \pm 20 & 3.2 \pm 0.04 & -0.14 \pm 7.8\mathrm{e}-02 & -0.01 \pm 6.7\mathrm{e}-02 \\
-		\, & W103b dayside & 2982 \pm 10 & 3.2 \pm 0.04 & 0.04 \pm 1.4\mathrm{e}-02 & 0.15 \pm 1.2\mathrm{e}-02 \\
-		Brown Dwarf & 2MASS J1320+0409 & 1875 \pm 70 & 5.19 \pm 0.16 & 0.21 \pm 6.3\mathrm{e}-04 & -0.06 \pm 5.0\mathrm{e}-04 \\
-		\, & 2MASS J0428-2253 & 2429 \pm 80 & 5.22 \pm 0.09 & 0.16 \pm 1.2\mathrm{e}-04 & -0.03 \pm 1.0\mathrm{e}-04 \\
-		\, & 2MASS J0003-2822 & 2889 \pm 80 & 5.18 \pm 0.04 & 0.26 \pm 1.3\mathrm{e}-04 & 0.10 \pm 1.1\mathrm{e}-04 \\
+		Hot Jupiter & W103b night & 1920 \pm 40 & 3.2 \pm 0.04 & 0.07 \pm 1.8\mathrm{e}-01 & -0.00 \pm 1.6\mathrm{e}-01 \\
+		\, & W103b quadrature & 2410 \pm 20 & 3.2 \pm 0.04 & -0.14 \pm 7.8\mathrm{e}-02 & -0.01 \pm 6.7\mathrm{e}-02 \\
+		\, & W103b dayside & 3010 \pm 10 & 3.2 \pm 0.04 & 0.04 \pm 1.4\mathrm{e}-02 & 0.15 \pm 1.2\mathrm{e}-02 \\
+		Brown Dwarf & 2MASS J1320+0409 & 1880 \pm 70 & 5.19 \pm 0.16 & 0.21 \pm 6.3\mathrm{e}-04 & -0.06 \pm 5.0\mathrm{e}-04 \\
+		\, & 2MASS J0428-2253 & 2430 \pm 80 & 5.22 \pm 0.09 & 0.16 \pm 1.2\mathrm{e}-04 & -0.03 \pm 1.0\mathrm{e}-04 \\
+		\, & 2MASS J0003-2822 & 2890 \pm 80 & 5.18 \pm 0.04 & 0.26 \pm 1.3\mathrm{e}-04 & 0.10 \pm 1.1\mathrm{e}-04 \\
 		Imaged Companion & CD-35 2722\tablenotemark{1} & 1800 \pm 100 & 4.5 \pm 0.5 & - & 0.15 \pm 1.0\mathrm{e}-05 \\
@@
 \begin{itemize}
-	\item{The dayside secondary eclipse depths are FIXME, implying a dayside effective temperature of FIXME, making WASP-103b among the hottest hot Jupiters ever observed.}
+	\item{The dayside planet-to-star flux is $0.151\pm0.015\%$, $0.446\pm0.38\%$, and $0.569\pm0.014\%$ in the WFC3 bandpass, \Spitzer\ $3.6$, and \Spitzer\ $4.5\mu$m, respectively.
+The best fit blackbody to the WFC3 dayside spectrum has an effective temperature of $3013 \pm 8$ K, making WASP-103b among the hottest hot Jupiters ever observed.}
 	\item{The phase curves have large amplitudes ($0.8 -0.9\times$ the secondary eclipse depth), and small offsets in peak brightness from the substellar point (consistent with zero degrees at all wavelengths).
@@
 	\item{We compared the spectra of WASP-103b at phases 0.5 (dayside), 0.25 (quadrature), and 0.1 (nightside) to brown dwarfs and directly imaged companions of similar temperature.
-We quantify the strength of the water feature and find that both brown dwarfs and imaged companions show evidence for water absorption at $1.4\,\mu$m, whereas WASP-103b does not.
-We attribute the difference to two factors: WASP-103b's irradiation environment, which changes the temperature pressure profile, and its low surface gravity, which pushes the photosphere to higher altitudes where water dissociates more easily.}
+We quantify the strength of the water feature and find that both brown dwarfs and imaged companions show evidence for water absorption at $1.4\,\mu$m, whereas the WASP-103b dayside and quadrature spectra do not.
+We attribute the difference to two factors: WASP-103b's irradiation environment, which changes the temperature pressure profile, and its low surface gravity, which pushes the photosphere to higher altitudes where water dissociates more easily.
+The WASP-103b nightside spectra have larger uncertainties and are consistent with the water feature amplitudes for other objects; higher precision phase curves are needed to detect water on the nightside.}
 \end{itemize}
 
-Future observations with JWST
-planets are round and complicated
+These results provide a first look at the global composition and thermal structure of WASP-103b.
+The planet is complex, with changes in temperature profile with longitude and possible gradients in composition from dayside to nightside.
+These findings highlight the 3D nature of exoplanets, and illustrate the importance of phase curve observations for developing a comprehensive understanding of their atmospheric chemistry and physics.
 
@@
 
-%H- is important.
-
-%How does composition compare to other HJs (esp W43b)
-%The spectrum is similar to observations of several other ultra-hot Jupiters \citep[][]{arcangeli18, mansfield18}, but qualitatively different from slightly cooler planets, which show water absorption features in the near-infared \citep[e.g.][]{kreidberg14b, line16}.
-
-%eclipse mapping to break degeneracy in models
-
-%We rule out the low metallicity and or high C/O models
-
 %confirm prediction that TiO is present in the hottest planets
-
-%what do the hot spot offsets and amplitudes mean?
 
@@
 The authors are grateful for helpful conversations with Caroline Morley, Thomas Beatty, Ming Zhao, Kim Star Cartier, Hannah Diamond-Lowe, and Nick Cowan.
-We also thank the organizers of the 2016 Santa Cruz Kavli Summer Program and the 2017 Ringberg Atmospheres of Disks and Planets meeting for facilitating many discussions and collaborations.
+We also thank the organizers of the 2016 Santa Cruz Kavli Summer Program and the 2017 Ringberg Atmospheres of Disks and Planets meeting for facilitating productive discussion and collaboration.
 

### 2018-01-17 ms.tex
incorporating comments

@@
 
-\author{Gregory L. Henry}
+\author{Gregory W. Henry}
 \affiliation{Center of Excellence in Information Systems, Tennessee State University, Nashville, TN 37209, USA}
@@
 The emission feature is not present on the nightside, suggesting changing thermal structure with longitude.
-We retrieved the atmospheric composition with a 1D thermochemical equilibrium model and found the composition is moderately metal-enriched ($\mathrm{[Fe/H]} =  23^{+29}_{-13}\times$ solar), and the carbon-to-oxygen ratio is below 0.9 at $3\,\sigma$ confidence.
+We retrieved the atmospheric composition with a 1D thermochemical equilibrium model and found the composition is moderately metal-enriched ($\mathrm{[M/H]} =  23^{+29}_{-13}\times$ solar), and the carbon-to-oxygen ratio is below 0.9 at $3\,\sigma$ confidence.
 In contrast to other hot Jupiters, we do not detect significant water absorption, which we attribute to partial H$_2$O dissociation and additional opacity from H- and TiO/VO.
@@
 The observations revealed large day-night temperature contrasts (in excess of 300 K), and eastward shifted peak brightness due to heat circulation, as predicted by 3D models \citep{showman09}.
-These infrared measurements were complemented by optical phase curves from \Kepler\, which show evidence for reflected light from patchy and variable dayside clouds with a range of compositions \citep{demory13, hu15, armstrong16, parmentier16}.
+These infrared measurements were complemented by optical phase curves from \Kepler\ that show evidence for reflected light from patchy and variable dayside clouds with a range of compositions \citep{demory13, hu15, armstrong16, parmentier16}.
 A \emph{spectroscopic} phase curve was observed for WASP-43b with \emph{Hubble}/Wide Field Camera 3 (\HST/WFC3) in the near-infrared, which provided the first phase-resolved measurements of an exoplanet's water abundance and thermal structure \citep{stevenson14, stevenson17}.
@@
 
-WASP-103b is an archetype of the class of ultra-hot Jupiters (with orbital periods of about one day and dayside temperatures typically $>2000\,\mathrm{K}$).
+WASP-103b is an archetype of the class of ultra-hot Jupiters, with orbital periods of about one day and dayside temperatures typically $>2000\,\mathrm{K}$ FIXME \citep[e.g.
+WASP-12b, WASP-18b, WASP-19b, WASP-33b, WASP-43b, WASP-121b][]{}.
 Observations of the thermal emission spectra of these objects have been puzzling.
@@
 \S\,\ref{sec:fits} details the models fit to the phase curves.
-\S\,\ref{sec:results} we discuss results, including the phase curve amplitudes and hotspot offsets, the phase-resolved spectra, and estimates of the planet's climate.
-In \S\,\ref{sec:gcm} and \ref{sec:comparison}, we compare the observations to GCM predictions and spectra from similar temperature stars and directly imaged companions.
+In \S\,\ref{sec:results} we discuss results, including the phase curve amplitudes and hotspot offsets, the phase-resolved spectra, and estimates of the planet's climate.
+In \S\,\ref{sec:gcm} and \ref{sec:comparison}, we compare the observations to general circulation model (GCM) predictions and spectra from similar temperature stars and directly imaged companions.
 \S\,\ref{sec:summary} concludes.
@@
 To minimize the intrapixel effect (variations in flux caused by imprecise pointing), we did not dither and also used PCRS peak-up\footnote{\url{http://irsa.ipac.caltech.edu/data/SPITZER/docs/irac/pcrs\_obs.shtml}} to improve the pointing accuracy.
-We began each observations with a 30-minute position settling period, followed by three Astronomical Observation Requests (AORs) of equal duration.
+We began each observation with a 30-minute position settling period, followed by three Astronomical Observation Requests (AORs) of equal duration.
 At the beginning of each AOR, the telescope was repointed to position the target in the ``sweet spot" of the detector.
@@
 The mean of the three standard deviations is 0.0058~mag, which is very comparable to the mean standard deviation of the six comparison stars (0.0055~mag).
-To maximize the possibility of detection WASP-103's rotation, we normalized the photometry such that each observing season has the same mean, thereby removing long-term variability in WASP-103 and/or the comparison stars.
-We performed a periodogram analysis of the normalized dataset.
-Figure\,\ref{fig:photometry} shows the frequency spectrum and the phase curve computed with the best frequency, respectively.
-We also performed a least-squares fit to the data to determine the best fit sine curve.
-The best fit period is 6.814 days, which agrees closely with the estimated stellar rotation period of 6.855 days \citep{gillon14}.
-The variability amplitude is 0.005~mag.
+To maximize the possibility of detecting WASP-103b's rotation, we normalized the photometry such that each observing season has the same mean, thereby removing any long-term variability in WASP-103 and/or the comparison stars (Figure\,\ref{fig:photometry}, top panel).
+We performed a periodogram analysis of the normalized data set based on least-squares fitting of sine curves.
+The resulting frequency spectrum and the phase curve computed with the best period are shown in the middle and lower panels of Figure\,\ref{fig:photometry} respectively.
+The best-fit period is 6.814 days, which agrees closely with the estimated stellar rotation period of 6.855 days of \citep{gillon14}.
+The peak-to-peak variability amplitude is 0.005 mag.
 Based on the formalism in \cite{zellem17}, we calculate that this variability will bias the measured eclipse depth by $\lesssim10$\,ppm from epoch to epoch, which is well below the photon-limited precision of our measurements.
@@
 For the \HST\ data, where we observed two phase curves and two additional eclipses, we constrain the physical parameters to be the same for all visits, but allow some of the systematics parameters to vary (for more details see \S\,\ref{sec:hst_sys}).
-We fit the WFC3 band-integrated (``white" light curve"), as well as spectroscopic light curves created from 10 wavelength bins uniformly spaced at $0.05\,\mu$m intervals between $1.15$ and $1.65\,\mu$m.
+We fit the WFC3 band-integrated ``white" light curve, as well as spectroscopic light curves created from 10 wavelength bins uniformly spaced at $0.05\,\mu$m intervals between $1.15$ and $1.65\,\mu$m.
 
@@
 We also discard exposures from the last half of orbit 15 from the phase curve observations, which were taken in staring mode to enable a gyro bias update.
-Since we observed two phase curves, we have complete orbital phase coverage the planet despite discarding some data.
+Since we observed two phase curves, we have complete orbital phase coverage of the planet despite discarding some data.
 
@@
 
-In addition to calculated the fit rms compared to the photon noise, we also tested for the presence of red noise based on whether the rms decreases as expected when the light curve in binned in time.
+In addition to calculating the fit rms compared to the photon noise, we also tested for the presence of red noise based on whether the rms decreases as expected when the light curve in binned in time.
 If the noise is white (uncorrelated in time), the residuals are expected to decrease by a factor of $\sqrt{N}$, where $N$ is the number of points in a bin.
@@
 The planet flux changes significantly with orbital phase in all three of the data sets, suggesting a strong gradient from dayside to nightside temperature, and peak brightness occurs near phase 0.5.
-In this section, we quantitatively characterize the phase curve shape, split the data into phase resolved spectra, evaluate different different temperature maps, and compare with previous observations of the dayside thermal emission spectrum.
+In this section, we quantitatively characterize the phase curve shape, split the data into phase resolved spectra, evaluate different temperature maps, and compare with previous observations of the dayside thermal emission spectrum.
 
@@
 We also show the planet-to-star flux corresponding to each map (points), which is model-dependent due to slight degeneracies with the instrument systematic model.
-\textbf{Right:} Temperature maps from the best fit models and the GCM at a representative photospheric pressure of 0.01 bar.}
+\textbf{Right:} Temperature maps from the best fit models and the GCM at a pressure of 0.01 bar.}
 \label{fig:model_comparison}
@@
 \includegraphics[width = 0.5\textwidth]{Figures/dayside_spectrum.pdf}
-\caption{Dayside emission spectrum (points) compared to the best fit 1-D model (blue line) with $1\,\sigma$ uncertainty shaded in orange.
-We also show the best fit blackbody (fit to the WFC3 data only).}
+\caption{Dayside planet-to-star flux (points) compared to the best fit 1-D model (blue line) with $1\,\sigma$ uncertainty shaded in orange.
+We also show the best fit blackbody model for the planet (fit to the WFC3 data only).}
 \label{fig:dayside}
@@
 \subsection{Climate}
-We fit three different models to characterize the planet's climate: a two-temperature map, the physically-motivated kinematic model of \citep{zhang17}, and a spherical harmonic map.
+We fit three different models to characterize the planet's climate: a two-temperature map, the physically-motivated kinematic model of \cite{zhang17}, and a spherical harmonic map.
 We also fit the thermal phase variation with a sinusoid, which can be inverted to map the climate \citep{cowan08}.
@@
 We compared the planet's minimum and maximum temperature for the three climate maps by computing the temperatures over a $100\times100$ grid in latitude and longitude.
-The kinematic model has the hottest dayside temperature and the two-temperature model has the smallest.
+The kinematic model has the hottest dayside temperature, and the two-temperature model has the smallest.
 The differences in peak temperature for the models we consider ranges from $630\,\mathrm{K}$ for \Spitzer\ Channel 1 to $1070\,\mathrm{K}$ for the broadband WFC3 light curve.
@@
 These differences arise because the kinematic model allows a steep temperature gradient on the dayside, so the substellar point is much hotter than the terminator, whereas the two temperature map imposes a constant dayside temperature.
-The spherical harmonics model has an intermediate temperature gradient, and fits the data the best.
+The spherical harmonics model has an intermediate temperature gradient and fits the data the best.
 However, this model may not be physically realistic: on the nightside, it produces higher temperatures at the poles than at the equator, contrary to predictions from GCMs (which we discuss in \S\,\ref{sec:gcm}).
@@
 \subsection{Blackbody Fits}
-A blackbody is the simplest model for the planet's thermal emission and provide a useful first evaluation of the atmospheric properties.
-The best fit blackbodies are shown in Figures \ref{fig:spectra} and \ref{fig:dayside}.
+A blackbody is the simplest model for the planet's thermal emission and provides a useful first evaluation of the atmospheric properties.
+The best-fit blackbodies are shown in Figures \ref{fig:spectra} and \ref{fig:dayside}.
 This model performs well for some orbital phases, with $\chi^2_\nu$ ranging from 0.9 to 1.1 for phases $\phi = 0.1, 0.7$ and $0.8$.
 At other phases the blackbody model is a poorer fit, particularly to the \Spitzer\ data.
-For phases $0.2 - 0.6$, the \Spitzer\ eclipse depths are significantly larger than predicted for the best fit blackbody, suggesting the presence of an emission feature.
+For phases $0.2 - 0.6$, the \Spitzer\ eclipse depths are significantly larger than predicted for the best fit blackbody, suggesting the presence of an emission feature (due to CO, as we discuss in \S\,\ref{sec:retrieval}).
 On the nightside (phase $0.9$), the \Spitzer\ $4.5\,\mu$m eclipse depth is \emph{smaller} than predicted, suggesting an absorption feature.
@@
 \subsection{Grid-Based Retrieval}
+\label{sec:retrieval}
 Since the phase-resolved spectra do not show spectrally resolved molecular features, we opted for a simple grid-based fit to the planet's atmospheric properties, similar to the grid search used in \cite{arcangeli18, mansfield18}.
@@
 The main characteristics of the dayside emission spectrum are: (1) it is blackbody-like at WFC3 wavelengths, and (2) in the \Spitzer\ bands, the planet-to-star flux is significantly higher than predicted for the best fit blackbody, indicating an emission feature.
-The best fit spectrum reproduces these data fairly well, with $\chi^2_\nu$ = 1.77.
+The best-fit spectrum reproduces these data fairly well, with $\chi^2_\nu$ = 1.77.
 The largest contribution to the $\chi^2$ value is the $4.5\,\mu$m eclipse depth, which is larger than the best fit model prediction by $2.9\,\sigma$.
@@
 On top of this, there is significant H- opacity from single H atoms bound with free electrons, which fills in the opacity at wavelengths shorter than $1.5\,\mu$m.
-Taken together, all these factors conspire to produce a nearly featureless spectrum from $1.1 - 1.7\,\mu$m.
+Taken together, all these factors add up to produce a nearly featureless spectrum from $1.1 - 1.7\,\mu$m.
 Finally, in the infrared the dominant absorber is CO, which produces the emission feature at \Spitzer\ wavelengths.
@@
 Figure\,\ref{fig:planetstarcomparison} shows the flux-calibrated spectra (assuming a distance of 10 pc).
-The directly imaged spectra are taken from \cite{wahhaj11, aller13, bonnefoy14}.
-They are calibrated in absolute flux using published H-band photometry \citep{wahhaj11, bonnefoy09, aller13} and distances \citep{gaia16}, a flux-calibrated spectrum of Vega \citep{1985A&A...151..399M, 1985IAUS..111..225H}, and the corresponding filter passbands.
+The directly imaged spectra are for the sources CD-35 2722, USco 1610-1913B, and TWA 22A and are taken from \cite{wahhaj11, aller13, bonnefoy14}.
+They are calibrated in absolute flux using published H-band photometry \citep{wahhaj11, aller13, bonnefoy09} and distances \citep{gaia16, teixeira09}, a flux-calibrated spectrum of Vega \citep{1985A&A...151..399M, 1985IAUS..111..225H}, and the corresponding filter passbands.
 The brown dwarf spectra \textbf{Jackie: describe catalog of brown dwarf spectra and flux calibration}.
@@
 We compared the spectra over the wavelength range $1.1 - 1.7\mu$m.
-The dominant opacity source over this range is water, which has a forest of absorption lines near 1.4\,$\mu$m.
+The dominant spectral features over this range are expected to come from water, which has a forest of absorption lines near 1.4\,$\mu$m.
 Spectra for the brown dwarfs and imaged companions have noticeable features in the water band, whereas WASP-103b does not.
@@
 	\item{We ran several 3D GCMs to compare to the data, including a nominal model with a cloud-free, solar composition, a metal-enriched model ([Fe/H] = 0.5), and two models with Lorentz drag.
-The GCMs with Lorentz drag have slower wind speeds and provide the best match to the data small hotspot offsets that are observed, but they underpredict the planet's nightside flux.}
+The GCMs with Lorentz drag have slower wind speeds and provide the best match to the small hotspot offsets that are observed, but they underpredict the planet's nightside flux.}
 	\item{We compared the spectra of WASP-103b at phases 0.5 (dayside), 0.25 (quadrature), and 0.1 (nightside) to brown dwarfs and directly imaged companions of similar temperature.
@@
 The planet is complex, with changes in temperature profile with longitude and possible gradients in composition from dayside to nightside.
-These findings highlight the 3D nature of exoplanets, and illustrate the importance of phase curve observations for developing a comprehensive understanding of their atmospheric chemistry and physics.
+These findings highlight the 3D nature of exoplanets and illustrate the importance of phase curve observations for developing a comprehensive understanding of their atmospheric chemistry and physics.
 

### 2018-01-18 ms.tex
more comments

@@
 
-\title{Global Climate and Atmosphere Composition of the Ultra-Hot Jupiter WASP-103\lowercase{b} from \HST\ and Spitzer Phase Curve Observations}
+\title{Global Climate and Atmospheric Composition of the Ultra-Hot Jupiter WASP-103\lowercase{b} from \HST\ and Spitzer Phase Curve Observations}
 
@@
 We fit the phase variation with a range of climate maps and find they all provide reasonable fits to the data, but have large degeneracies in temperature (up to 1000 K for a given latitude/longitude).
-The phase-resolved spectra are consistent with blackbodies in the WFC3 bandpass, with effective temperatures ranging from 2000 K on the nightside to 3000 K on the dayside.
+The phase-resolved spectra are consistent with blackbodies in the WFC3 bandpass, with brightness temperatures ranging from 2000 K on the nightside to 3000 K on the dayside.
 However, the dayside spectrum has a strong feature in the \Spitzer\ bands, which we attribute to CO emission and a thermal inversion.
@@
 To optimize the duty cycle of the observations, we used the spatial scan observing mode with a scan rate of 0.03 arcsec/s, alternating between forward and backward scanning on the detector.
-The scan height was 25 pixels and the peak counts were $35\times10^3$ photoelectrons per pixel.
+The scan height was 25 pixels and the peak counts were $3.5\times10^4$ photoelectrons per pixel.
 We collected a total of 18 spatial scan exposures per orbit.
@@
 The target centroid was determined with a two-dimensional Gaussian fit.
+The target remains centered near the sweet spot for the entire AOR in each observation, with a maximum drift of 0.1 pixels.
 We estimated and subtracted the background from an annulus with a radius of 7 to 15 pixels from the centroid.
@@
 The peak-to-peak variability amplitude is 0.005 mag.
-Based on the formalism in \cite{zellem17}, we calculate that this variability will bias the measured eclipse depth by $\lesssim10$\,ppm from epoch to epoch, which is well below the photon-limited precision of our measurements.
+Based on the formalism in \cite{zellem17}, we calculate that this variability will bias the measured eclipse depth by $\lesssim10$\,parts per million (ppm) from epoch to epoch, which is well below the photon-limited precision of our measurements.
 
@@
 This package allows users to input a climate map (temperature or brightness as a function of latitude and longitude), and generate the corresponding flux ratio for an observation at time $t$.
-In our fit, we calculated the stellar flux with a PHOENIX model \citep{husser13} interpolated to an effective temperature of $6110\,\mathrm{K}$ \citep{gillon14}.
+In our fit, we calculated the stellar flux with a PHOENIX model \citep{husser13} interpolated to an brightness temperature of $6110\,\mathrm{K}$ \citep{gillon14}, solar metallicity, and log\,$g$ of 4.5 (in cgs units).
 For the planet flux, we tested three different maps: a two-temperature map, with a uniform dayside temperature $T_d$ and a uniform nightside temperature $T_n$; a map generated with spherical harmonics; and the physically-motivated kinematic model from \cite{zhang17}, which has just three free parameters (the nightside temperature $T_n$, the change in temperature from day-to-night side $\Delta_T$, and the ratio of radiative to advective timescales $\xi$).
@@
 The Spitzer 4.5 $\mu$m light curve rms is within 10\% of the expected photon noise limit (691 versus 640 ppm), whereas the 3.6 $\mu$m light curve has significantly larger rms (797 versus 470 ppm), due to time-correlated red noise (discussed below).
-The expected photon-limited rms for the WFC3 spectrosopic light curves ranges from 430 - 530 parts per million (ppm), and the measured rms was typically within 5\% of expectations for all spectroscopic channels.
+The expected photon-limited rms for the WFC3 spectrosopic light curves ranges from 430 - 530 ppm, and the measured rms was typically within 5\% of expectations for all spectroscopic channels.
 For the WFC3 band-integrated white light curve, the rms was slightly larger than predicted (175 versus 122 ppm).
@@
 
-For all three phase curves, the hotspot offset is consistent with zero degrees, indicative of a fast radiative-to-advective timescale (the incident flux is reradiated to space faster than it is advected around to the nightside).
-Fast radiative timescales are precicted at high temperatures, and small hotspot offsets are also observed for other very hot Jupiters \citep{komacek17}.
+For all three phase curves, the hotspot offset is consistent with zero degrees, indicative of a small ratio of radiative to advective timescales (the incident flux is reradiated to space faster than it is advected around to the nightside).
+Fast radiative timescales are precicted at high temperatures, and small hotspot offsets are also observed for other very hot Jupiters \citep{perez13, komacek16, komacek17}.
 The phase curve amplitudes are large (near 0.8 - 0.9), as expected for an atmosphere with inefficient heat redistribution.
@@
 		\, & nominal GCM & 0.89 & 15.32 \\
-		\, & [Fe/H] = 0.5 GCM & 0.84 & 19.64 \\
+		\, & [M/H] = 0.5 GCM & 0.84 & 19.64 \\
 		\, & $\tau_\mathrm{drag4}$ GCM & 0.97 & 2.34 \\
@@
 		\, & nominal GCM & 0.78 & 9.19 \\
-		\, & [Fe/H] = 0.5 GCM & 0.72 & 12.79 \\
+		\, & [M/H] = 0.5 GCM & 0.72 & 12.79 \\
 		\, & $\tau_\mathrm{drag4}$ GCM & 0.86 & 0.90 \\
@@
 		\, & nominal GCM & 0.79 & 8.11 \\
-		\, & [Fe/H] = 0.5 GCM & 0.73 & 11.35 \\
+		\, & [M/H] = 0.5 GCM & 0.73 & 11.35 \\
 		\, & $\tau_\mathrm{drag4}$ GCM & 0.85 & 0.90 \\
@@
 The emission spectra are insensitive to the models because they are estimated directly from the data (after systematics have been removed).
-Since systematic noise is not strongly correlated with the astrophysical signal, the systematics-divided data are nearly identical for all the models.
+Since the systematic noise is not strongly correlated with the astrophysical signal, the systematics-divided data are nearly identical for all the models.
 This point is illustrated in Figure\,\ref{fig:model_comparison} for the broadband WFC3 light curve.
@@
 The spherical harmonics model has an intermediate temperature gradient and fits the data the best.
-However, this model may not be physically realistic: on the nightside, it produces higher temperatures at the poles than at the equator, contrary to predictions from GCMs (which we discuss in \S\,\ref{sec:gcm}).
+However, this model may not be physically realistic: on the nightside, it produces much higher temperatures at the poles than at the equator, contrary to predictions from GCMs (which we discuss in \S\,\ref{sec:gcm}).
 
@@
 We compared our results to the dayside emission spectrum reported by \cite{cartier17}, which is based on a Gaussian process analysis of two secondary eclipses from \HST/WFC3.
-The shape of their spectrum is consistent with what we find, but their eclipse depths are 125 ppm smaller on average.
+The shape of their spectrum is consistent with what we find, but their eclipse depths are 125 ppm smaller on average (a difference of about 10\%).
 In their analysis, \cite{cartier17} noted that the Gaussian process fit produces smaller eclipse depths than a parametric fit (also by 125 ppm).
@@
 The $\chi^2_\nu$ values range from 0.5 to 1.6, with a median of 0.9.
-The best fit effective temperatures range from 1920 Kelvin on the nightside to 2980 Kelvin on the dayside.
+The best fit brightness temperatures range from 1920 Kelvin on the nightside to 2980 Kelvin on the dayside.
 We report the best fit temperatures with uncertainties in Table\,\ref{table:teffs}.
@@
 	\tablewidth{0pt}
-	\tablecaption{Phase-resolved Effective Temperature \label{table:teffs}}
+	\tablecaption{Phase-resolved Brightness Temperature \label{table:teffs}}
 	\tablehead{
-	\colhead{Orbital Phase} & \colhead{$T_\mathrm{eff}$ (K)} & \colhead{$\chi^2_\nu$}}
+	\colhead{Orbital Phase} & \colhead{$T_\mathrm{b}$ (K)} & \colhead{$\chi^2_\nu$}}
 		\startdata
@@
 For a carbon-rich composition, the equilibrium abundance of methane relative to CO increases by orders of magnitude compared to an oxygen-rich  composition \citep[e.g.][]{madhusudhan11}.
-Our \Spitzer\ eclipse depths are sensitive to the relative abundance of these species, so we can confidently rule out a carbon-rich composition despite the lack of spectrally resolved features.
+Our \Spitzer\ eclipse depths are sensitive to the relative abundance of these species, so we can confidently rule out a carbon-rich composition despite the lack of spectrally resolved features (assuming the atmosphere is in chemical equilibrium).
 
@@
 Our nominal GCM was a cloud-free, solar composition atmosphere with TiO/VO opacity and no added drag.
-We also ran models with enhanced metallicity ([Fe/H] = 0.5), no TiO/VO, and added atmospheric drag.
+We also ran models with enhanced metallicity ([M/H] = 0.5), no TiO/VO, and added atmospheric drag.
 Lorentz drag can occur in the hottest exoplanet atmospheres, which may be partially ionized and coupled to the background magnetic field.
@@
 
-We selected spectra from WASP-103b at three orbital phases: dayside ($\phi = 0.5$), quadrature ($\phi = 0.25$), and nightside ($\phi = 0.1$), and compared them to sources with comparable effective temperature.
+We selected spectra from WASP-103b at three orbital phases: dayside ($\phi = 0.5$), quadrature ($\phi = 0.25$), and nightside ($\phi = 0.1$), and compared them to sources with comparable brightness temperature.
 Figure\,\ref{fig:planetstarcomparison} shows the flux-calibrated spectra (assuming a distance of 10 pc).
@@
 For the first, $A_1$, we considered data in and out of the water band, with $\lambda_{1,2,3,4} = 1.15, 1.3, 1.35, 1.5\,\mu$m.
-The ground-based direct imaging data doesn't span this entire wavelength range, so we also define an amplitude $A_2$ with $\lambda_{1,2,3,4} = 1.2, 1.35, 1.5, 1.65\,\mu$m.
+The ground-based direct imaging data do not span this entire wavelength range, so we also define an amplitude $A_2$ with $\lambda_{1,2,3,4} = 1.2, 1.35, 1.5, 1.65\,\mu$m.
 The estimated amplitudes and uncertainties are listed in Table\,\ref{table:sources}.
@@
 	\item{The dayside planet-to-star flux is $0.151\pm0.015\%$, $0.446\pm0.38\%$, and $0.569\pm0.014\%$ in the WFC3 bandpass, \Spitzer\ $3.6$, and \Spitzer\ $4.5\mu$m, respectively.
-The best fit blackbody to the WFC3 dayside spectrum has an effective temperature of $3013 \pm 8$ K, making WASP-103b among the hottest hot Jupiters ever observed.}
+The best fit blackbody to the WFC3 dayside spectrum has an brightness temperature of $3013 \pm 8$ K, making WASP-103b among the hottest hot Jupiters ever observed.}
 	\item{The phase curves have large amplitudes ($0.8 -0.9\times$ the secondary eclipse depth), and small offsets in peak brightness from the substellar point (consistent with zero degrees at all wavelengths).
@@
 The \HST/WFC3 spectra are consistent with  blackbody emission from the planet at all orbital phases.
-The best fit effective temperatures ranges from 1920 K (phase $\phi = 0.1$) to 3010 K on the dayside.
+The best fit brightness temperatures ranges from 1920 K (phase $\phi = 0.1$) to 3010 K on the dayside.
 We attribute the absence of water features at WFC3 wavelengths to (1) H$_2$O dissociation on the dayside, (2) additional near-IR opacity from H-, TiO/VO and FeH, (3) a small temperature gradient at the pressure levels probed by the data.
@@
 \acknowledgments
+Support for \textit{HST} program GO-15050 was provided by NASA through a grant from the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS 5-26555.
+Support for \textit{Spitzer} program 11099 was provided by NASA through an award issued by JPL/Caltech.
 The data presented in this paper were obtained from the Mikulski Archive for Space Telescopes (MAST) and the NASA/IPAC Infrared Science Archive.
@@
 We also thank the organizers of the 2016 Santa Cruz Kavli Summer Program and the 2017 Ringberg Atmospheres of Disks and Planets meeting for facilitating productive discussion and collaboration.
+J.L.B. acknowledges support from the David and Lucile Packard Foundation.
 

### 2018-01-18 Figures/amp_offset_table.py

@@ -19,7 +19,7 @@ amp, amp_err = weighted_mean(amp, amp_err)
 off, off_err = weighted_mean(off, off_err)
 
 gcm_wfc3 = np.genfromtxt("gcm_amp_off_wfc3.txt")
-models = ["nominal GCM", "[Fe/H] = 0.5 GCM", "$\\tau_\mathrm{drag4}$ GCM", "$\\tau_\mathrm{drag3}$ GCM"]
+models = ["nominal GCM", "[M/H] = 0.5 GCM", "$\\tau_\mathrm{drag4}$ GCM", "$\\tau_\mathrm{drag3}$ GCM"]
 
 print "\\begin{deluxetable}{llLL}"
 print "\\tablecolumns{4}"

### 2018-01-18 Figures/phased_espec.py

@@ -30,9 +30,9 @@ def best_fit_bb(w, y, e, rprs):
 
 	w = np.array(w)
 
-	w, y, e = w[0:10], y[0:10], e[0:10]
-#	w, y, e = w[10], y[10], e[10]
-#	w, y, e = w[11], y[11], e[11]
+#	w, y, e = w[0:10], y[0:10], e[0:10]     #WFC3 data only
+#	w, y, e = w[10], y[10], e[10]           #spitzer ch1
+	w, y, e = w[11], y[11], e[11]           #spitzer ch2
 
 	#get stellar spectrum
 	star = np.genfromtxt("wasp103_sed_fluxes.out")
@@ -52,8 +52,8 @@ def best_fit_bb(w, y, e, rprs):
 
         idx = (np.abs(chis-(chibest+1.))).argmin()
         onesigma = Tbest - Ts[idx]
-       # print "T, chi2", Tbest, "+/-", onesigma, chibest/(len(y) - 1)#, resid
-        print '{0:d}'.format(int(Tbest)),  '{0:d}'.format(int(np.abs(onesigma))), '{0:0.1f}'.format(chibest/(len(y) - 1)),
+        #print '{0:d}'.format(int(Tbest)),  '{0:d}'.format(int(np.abs(onesigma))), '{0:0.1f}'.format(chibest/(len(y) - 1)),
+        print '{0:d}'.format(int(Tbest)),  '{0:d}'.format(int(np.abs(onesigma))) 
 	print>>outfile,  Tbest
 	outfile.close()
 	return waves_hires, blackbody(waves_hires*1.0e-6, Tbest)/star_bb_hires*rprs**2
@@ -102,6 +102,7 @@ for f in files:
 		#calculates uncertainty for phase bin
 		ind2 = (phase >= phasebins[j-1]) & (phase < phasebins[j])
 		sig2 = np.sqrt(np.sum(err[ind2]**2)/sum(ind2)**2)
+	#	print "std, se",  np.sqrt(np.sum(err[ind2]**2)/sum(ind2)**2), np.sqrt(np.sum(err[ind2]**2)/(sum(ind2)-1)**2)            #difference of 1 ppm for std vs ste
 
 		spectra[i, j-1, 0] = np.mean(data_corr[ind2])
 		spectra[i, j-1, 1] = np.sqrt(sig1**2 + sig2**2)		#quadrature add uncertainties from baseline and bin 

### 2018-01-18 Figures/test_significance_of_features.py

@@ -1,0 +1,7 @@
+import numpy as np
+
+wfc3 = np.genfromtxt("teffs.txt")
+spt = np.genfromtxt("teffs_ch2.txt")
+
+
+for i in range(len(wfc3)): print (wfc3[i,0] - spt[i,0])/np.sqrt(wfc3[i,1]**2 + spt[i,1]**2)

### 2018-01-18 ms.tex
comments

@@
 
-\begin{figure}
-\includegraphics[width = 0.5\textwidth]{Figures/dayside_spectrum.pdf}
-\caption{Dayside planet-to-star flux (points) compared to the best fit 1-D model (blue line) with $1\,\sigma$ uncertainty shaded in orange.
-We also show the best fit blackbody model for the planet (fit to the WFC3 data only).}
+\begin{figure*}
+\includegraphics[width = 1.0\textwidth]{Figures/twopanel_dayside_spectrum.pdf}
+\caption{Dayside planet-to-star flux (points) compared to a blackbody model (dashed gray line) and the best fit 1D model (blue line, with $1\,\sigma$ uncertainty shaded in orange) for the \HST/WFC3 data (left) and Spitzer (right).
+The 1D model was fit to all the data simultaneously, but the blackbody was fit to the WFC3 data only.
+The best fit 1D model binned at the resolution of the \Spitzer\ data is indicated by blue squares (right).
+}
 \label{fig:dayside}
-\end{figure}
+\end{figure*}
 

### 2018-01-18 Figures/test_significance_of_features.py

@@ -1,6 +1,6 @@
 import numpy as np
 
-wfc3 = np.genfromtxt("teffs.txt")
+wfc3 = np.genfromtxt("teffs_nodayside.txt")
 spt = np.genfromtxt("teffs_ch2.txt")
 
 

### 2018-01-18 ms.tex
magnetic drag

@@
 
-WASP-103b is an archetype of the class of ultra-hot Jupiters, with orbital periods of about one day and dayside temperatures typically $>2000\,\mathrm{K}$ FIXME \citep[e.g.
-WASP-12b, WASP-18b, WASP-19b, WASP-33b, WASP-43b, WASP-121b][]{}.
-Observations of the thermal emission spectra of these objects have been puzzling.
+WASP-103b is an archetype of the class of ultra-hot Jupiters, with orbital periods of about one day and dayside temperatures typically $>2000\,\mathrm{K}$.
+These very hot planets were initially predicted to have inverted temperature pressure profiles due to strong optical absorption by TiO/VO in the upper atmospheres \citep{hubeny03, fortney08}; however, observations of their thermal emission spectra have been puzzling.
 In the near-infrared, where water is the dominant absorber, some spectra show water absorption features, some show emission features, and some are consistent with blackbody models \citep{madhusudhan11, crossfield12, stevenson14b, haynes15, evans16, beatty17a, beatty17b, sheppard17, arcangeli18, mansfield18}.
-A variety of explanations have been proposed for these results, including low metallicity or high carbon-to-oxygen compositions, dayside clouds, and isothermal or inverted temperature profiles caused by TiO/VO absorption in the upper atmosphere.
+A variety of explanations have been proposed for these results, including low metallicity or high carbon-to-oxygen compositions, dayside clouds, and finely tuned isothermal temperature pressure profiles.
 Recently, \cite{arcangeli18} showed that water dissociation on the hot dayside plays an important role in the atmospheres of these ultra-hot planets and may be responsible for some of the blackbody-like near-IR spectra.
@@
 \S\,\ref{sec:summary} concludes.
-
-%Fortney 08
 
@@
 Lorentz drag can occur in the hottest exoplanet atmospheres, which may be partially ionized and coupled to the background magnetic field.
-We parameterized the drag (\textbf{Vivien: how did you model drag?}), with timescales of $\tau_\mathrm{drag} = 10^3$ and $10^4$ s.
-We label the drag models $\tau_\mathrm{drag3}$ and $\tau_\mathrm{drag4}$, respectively.
+We included Rayleigh drag forces in the GCM, which are proportional to the wind speed scaled by a time constant \citep[$F_\mathrm{drag} \propto -v/\tau_\mathrm{drag}$;][]{menou09}.
+We assumed the drag timescale is uniform throughout the atmosphere and considered two cases: $\tau_\mathrm{drag} = 10^3$ and $10^4$ s, which we label $\tau_\mathrm{drag3}$ and $\tau_\mathrm{drag4}$, respectively.
 
@@
 As shown in Figure\,\ref{fig:gcmcomparison}, this large amplitude causes the drag models to underestimate the planet-to-star flux away from the substellar point.
-(\textbf{Vivien and others: how do we heat up the nightside to match the data better?})
+There are several physical processes not included in the GCM that could contribute to a hotter nightside, including shocks, longitude-dependent drag, latent heat released from H2 recombination.
+
+To check that fast drag timescales of order $10^3 - 10^4$\,s are physically realistic, we computed the free electron abundance due to ionized metals for the $\tau_\mathrm{drag3}$ GCM.
+Using the order-of-magnitude expression from \cite{perna10} (Equation 12), we estimate a drag timescale at the substellar point of $\tau_\mathrm{drag}  = 2\times10^4/B^2$ s, where $B$ is the magnetic field in Gauss.
+We assume a temperature and pressure of 3359 K and 0.11 bar, and that the magnetic field is perpendicular to the flow.
+To reach a drag timescale of $10^3$\,s, a magnetic field stronger than 4 Gauss is required.
+This value is comparable to Jupiter's magnetic field strength of 5-10 Gauss \citep{bagenal04}.
 
@@
 The GCM predicts a cooler nightside than all models except the two-temperature model.
-We note that the GCM does not provide a perfect fit to the data, whereas multiple \texttt{spiderman} maps fit quite well, with large differences in temperature between them (see Table
-\,\ref{table:model_comparison}). Determining which models (if any) accurately describe the climate will require higher precision phase curves and/or eclipse mapping \citep[e.g.][]{dewit12}.
+We note that the GCM does not provide a perfect fit to the data, whereas multiple \texttt{spiderman} maps fit quite well, with large differences in temperature between them (see Table \,\ref{table:model_comparison}).
+Determining which models (if any) accurately describe the climate will require higher precision phase curves and/or eclipse mapping \citep[e.g.][]{dewit12}.
 

### 2018-01-19 ms.tex
JM comments

@@
 
+\author{Jacob Arcangeli}
+\affiliation{Anton Pannekoek Institute for Astronomy, University of Amsterdam, Science Park 904, 1098 XH Amsterdam, The Netherlands}
+
 \begin{abstract}
@@
 However, the dayside spectrum has a strong feature in the \Spitzer\ bands, which we attribute to CO emission and a thermal inversion.
-The emission feature is not present on the nightside, suggesting changing thermal structure with longitude.
-We retrieved the atmospheric composition with a 1D thermochemical equilibrium model and found the composition is moderately metal-enriched ($\mathrm{[M/H]} =  23^{+29}_{-13}\times$ solar), and the carbon-to-oxygen ratio is below 0.9 at $3\,\sigma$ confidence.
-In contrast to other hot Jupiters, we do not detect significant water absorption, which we attribute to partial H$_2$O dissociation and additional opacity from H- and TiO/VO.
+The emission feature is not present on the nightside, suggesting changes in thermal structure with longitude.
+We retrieved the atmospheric composition with a 1D self-consistent modeling technique and found the atmosphere is moderately metal-enriched ($\mathrm{[M/H]} =  23^{+29}_{-13}\times$ solar), and the carbon-to-oxygen ratio is below 0.9 at $3\,\sigma$ confidence.
+In contrast to cooler hot Jupiters, we do not detect significant water absorption, which we attribute to partial H$_2$O dissociation and additional opacity from H- and TiO/VO.
 We compare the phase curves to 3D general circulation models and find that atmospheric drag is required to explain the small hotspot offsets, but that these models overpredict the phase curve amplitude.
-We also compare the WASP-103b spectra to brown dwarfs and young directly imaged companions and find they have significantly larger water features, indicating that surface gravity and irradiation environment play an important role in shaping the spectra of hot Jupiters.
+We also compare the WASP-103b spectra to brown dwarfs and young directly imaged companions and find these more massive and self-luminous objects have significantly larger water features, indicating that surface gravity and irradiation environment play an important role in shaping the spectra of hot Jupiters.
 These results highlight the 3D structure of exoplanet atmospheres and illustrate the importance of phase curve observations for understanding their complex chemistry and physics.
@@
 Phase curve observations consist of continuous monitoring of the planet-to-star flux ratio over a complete orbital revolution of the planet, which exposes different longitudes at each orbital phase.
-The first phase curve was observed with \Spitzer\ for the hot Jupiter HD 189733b by \citep{knutson07}, followed by additional \Spitzer\ observations for about a dozen more systems \citep[cataloged in][]{parmentier17}.
-The observations revealed large day-night temperature contrasts (in excess of 300 K), and eastward shifted peak brightness due to heat circulation, as predicted by 3D models \citep{showman09}.
-These infrared measurements were complemented by optical phase curves from \Kepler\ that show evidence for reflected light from patchy and variable dayside clouds with a range of compositions \citep{demory13, hu15, armstrong16, parmentier16}.
+The first phase curve of an exoplanet was observed with \Spitzer\ for the hot Jupiter HD 189733b by \cite{knutson07}, followed by additional \Spitzer\ observations for about a dozen more systems \citep[cataloged in][]{parmentier17}.
+The observations revealed large day-night temperature contrasts (in excess of 300 K), and eastward shifted peak brightness due to heat circulation, as predicted by 3D models \citep{showman02}.
+These infrared measurements were complemented by optical phase curves from \Kepler\ that show evidence for reflected light from patchy and variable dayside clouds with a range of compositions \citep{borucki09, demory13, hu15, armstrong16, parmentier16}.
 A \emph{spectroscopic} phase curve was observed for WASP-43b with \emph{Hubble}/Wide Field Camera 3 (\HST/WFC3) in the near-infrared, which provided the first phase-resolved measurements of an exoplanet's water abundance and thermal structure \citep{stevenson14, stevenson17}.
@@
 Previous observations of WASP-103b's atmosphere revealed a blackbody-like dayside emission spectrum, with possible evidence for a $K_\mathrm{S}$-band emission feature \citep{cartier17, delrez18}.
-The optical transmission spectrum shows evidence for strong sodium and potassium absorption features that are consistent with expectations for a cloud-free atmosphere \citep{lendl17}.%, though other observations have shown a large optical scattering slope that is not fit well by theoretical models \citep{southworth16}.
+The optical transmission spectrum shows evidence for sodium and potassium absorption features that are consistent with expectations for a cloud-free atmosphere \citep{lendl17}.%, though other observations have shown a large optical scattering slope that is not fit well by theoretical models \citep{southworth16}.
 
 WASP-103b is an archetype of the class of ultra-hot Jupiters, with orbital periods of about one day and dayside temperatures typically $>2000\,\mathrm{K}$.
-These very hot planets were initially predicted to have inverted temperature pressure profiles due to strong optical absorption by TiO/VO in the upper atmospheres \citep{hubeny03, fortney08}; however, observations of their thermal emission spectra have been puzzling.
+These very hot planets were initially predicted to have inverted temperature pressure profiles due to strong optical absorption by TiO/VO in the upper atmospheres \citep{hubeny03, fortney08}; however, observations of their emission spectra have been inconclusive on their thermal structure and composition.
 In the near-infrared, where water is the dominant absorber, some spectra show water absorption features, some show emission features, and some are consistent with blackbody models \citep{madhusudhan11, crossfield12, stevenson14b, haynes15, evans16, beatty17a, beatty17b, sheppard17, arcangeli18, mansfield18}.
 A variety of explanations have been proposed for these results, including low metallicity or high carbon-to-oxygen compositions, dayside clouds, and finely tuned isothermal temperature pressure profiles.
-Recently, \cite{arcangeli18} showed that water dissociation on the hot dayside plays an important role in the atmospheres of these ultra-hot planets and may be responsible for some of the blackbody-like near-IR spectra.
+Recently, \cite{arcangeli18} showed that water dissociation and H- opacity on the hot dayside play an important role in the atmospheres of these ultra-hot planets and may be responsible for some of the blackbody-like near-IR spectra.
 In this work, we put these results in context by investigating the global thermal structure and composition of the ultra-hot Jupiter WASP-103b.
@@
 \label{sec:observations}
-We observed two full-orbit phase curves of WASP-103b with \HST/WFC3 and one each with \Spitzer/IRAC at 3.6 and 4.5 $\mu$m (from HST Program 14050 and Spitzer Program 11099).
+We observed two full-orbit phase curves of WASP-103b with \HST/WFC3 and one each with \Spitzer/IRAC at 3.6 and 4.5 $\mu$m (from HST Program 14050 and Spitzer Program 11099, PI: L.
+Kreidberg).
 We also reduced two \HST/WFC3 secondary eclipse observations of WASP-103b from \HST\ Program 13660 (PI: M.
@@
 We note that the extracted spectrum includes flux from a nearby companion star, which is separated from WASP-103 by less than two pixels \citep[0.2";][]{wollert15}.
-Our extracted spectrum includes flux from this star, which we account for later in the analysis.
+We account for this contamination later in the analysis.
 
@@
 We estimated and subtracted the background from an annulus with a radius of 7 to 15 pixels from the centroid.
-As for the \HST\ observations, the contaminating flux from the nearby star is included in the final photometry and corrected later in the light curve fits.
+The contaminating flux from the nearby star is within the same pixel as the target, so we included it in the photometry and corrected it in the light curve fits.
 
@@
 We found that the choice of model does not significantly change the results.
-The emission spectra are insensitive to the models because they are estimated directly from the data (after systematics have been removed).
 Since the systematic noise is not strongly correlated with the astrophysical signal, the systematics-divided data are nearly identical for all the models.
 This point is illustrated in Figure\,\ref{fig:model_comparison} for the broadband WFC3 light curve.
-In most phase bins, the planet-to-star flux agrees to well within one sigma for all the models.
+For all phase bins, the estimated planet-to-star flux agrees to better than one sigma for all the models.
 
@@
 	\tablewidth{0pt}
-	\tablecaption{Phase-Resolved Emission Spectra \label{table:spectra}}
+	\tablecaption{Phase-Resolved Emission Spectra\tablenotemark{1} \label{table:spectra}}
 	\tablehead{
@@
 		\vspace{-0.8cm}
-		\tablecomments{comments}
+		\tablenotetext{1}{The planet-to-star flux in each phase bin $\phi$ is in units of ppm.}
 	\end{deluxetable*}
@@
 We generated a grid from one-dimensional forward models of the atmosphere over a broad range of metallicities, carbon-to-oxygen ratios (C/O), and stellar irradiation.
-The stellar spectrum is scaled in intensity over the grid to model the unknown heat redistribution for the planet; i.e., a lower dayside irradiation is equivalent to more efficient heat transport to the nightside.
+The flux at the top of the atmosphere is scaled in intensity over the grid to model the unknown heat redistribution for the planet; i.e., a lower dayside irradiation is equivalent to more efficient heat transport to the nightside.
 
@@
 The \HST/WFC3 spectra are consistent with  blackbody emission from the planet at all orbital phases.
-The best fit brightness temperatures ranges from 1920 K (phase $\phi = 0.1$) to 3010 K on the dayside.
-We attribute the absence of water features at WFC3 wavelengths to (1) H$_2$O dissociation on the dayside, (2) additional near-IR opacity from H-, TiO/VO and FeH, (3) a small temperature gradient at the pressure levels probed by the data.
-The \Spitzer\ data are \emph{not} consistent with a blackbody: there is an infrared emission feature at phases where the substellar point is visible ($\phi = 0.2 - 0.7$), which transitions to an absorption feature on the nightside ($\phi = -0.1 - 0.1$).
+The best fit brightness temperatures ranges from $1920\pm40$ K (phase $\phi = 0.1$) to $3010\pm10$ K on the dayside.
+We attribute the absence of water features at WFC3 wavelengths to (1) H$_2$O dissociation on the dayside, (2) additional near-IR opacity from H-, TiO/VO and FeH, (3) a small temperature gradient at the pressure levels probed by the data.}
+\item{The \Spitzer\ data are \emph{not} consistent with a blackbody: there is an infrared emission feature at phases where the substellar point is visible ($\phi = 0.2 - 0.7$), which transitions to an absorption feature on the nightside ($\phi = -0.1 - 0.1$).
 We attribute these features to CO absorption and changing thermal structure from the dayside to the nightside.}

### 2018-01-19 Figures/hst_model_comparison.py

@@ -255,6 +255,7 @@ for i, model in enumerate(models):
 
 	#plt.errorbar(bin_average, (bindata-1.)*1e3*dilution, yerr = binsigma*1e3, linestyle='none', marker = '.', color = colors[i], ecolor = 'k', zorder = 10, alpha = 0.8)
 	plt.plot(bin_average, (bindata-1.)*1e3*dilution,  linestyle = 'none', marker ='.', color = colors[i], zorder = 10, alpha = 0.8)
+        pickle.dump( [bin_average, (bindata-1.), binsigma], open(model+".p", "wb" ) )
 
         plt.plot(phase, (bestfit-1.)*1e3*dilution, color = colors[i], label = labels[i], alpha = 1.0, linestyle = linestyle[i])
 

### 2018-01-19 ms.tex
fix fig 7

@@
 
-\keywords{planets and satellites: individual (WASP-107b), planets and satellites: atmospheres}
+\keywords{planets and satellites: individual (WASP-103b), planets and satellites: atmospheres}
 
@@
 This package allows users to input a climate map (temperature or brightness as a function of latitude and longitude), and generate the corresponding flux ratio for an observation at time $t$.
-In our fit, we calculated the stellar flux with a PHOENIX model \citep{husser13} interpolated to an brightness temperature of $6110\,\mathrm{K}$ \citep{gillon14}, solar metallicity, and log\,$g$ of 4.5 (in cgs units).
+In our fit, we calculated the stellar flux with a PHOENIX model \citep{husser13} interpolated to a brightness temperature of $6110\,\mathrm{K}$ \citep{gillon14}, solar metallicity, and log\,$g$ of 4.5 (in cgs units).
 For the planet flux, we tested three different maps: a two-temperature map, with a uniform dayside temperature $T_d$ and a uniform nightside temperature $T_n$; a map generated with spherical harmonics; and the physically-motivated kinematic model from \cite{zhang17}, which has just three free parameters (the nightside temperature $T_n$, the change in temperature from day-to-night side $\Delta_T$, and the ratio of radiative to advective timescales $\xi$).
@@
 		\enddata
-		\vspace{-0.8cm}
 		\tablenotetext{1}{The planet-to-star flux in each phase bin $\phi$ is in units of ppm.}
+		%\vspace{-0.8cm}
 	\end{deluxetable*}
@@
 	\item{The dayside planet-to-star flux is $0.151\pm0.015\%$, $0.446\pm0.38\%$, and $0.569\pm0.014\%$ in the WFC3 bandpass, \Spitzer\ $3.6$, and \Spitzer\ $4.5\mu$m, respectively.
-The best fit blackbody to the WFC3 dayside spectrum has an brightness temperature of $3013 \pm 8$ K, making WASP-103b among the hottest hot Jupiters ever observed.}
+The best fit blackbody to the WFC3 dayside spectrum has a brightness temperature of $3013 \pm 8$ K, making WASP-103b among the hottest hot Jupiters ever observed.}
 	\item{The phase curves have large amplitudes ($0.8 -0.9\times$ the secondary eclipse depth), and small offsets in peak brightness from the substellar point (consistent with zero degrees at all wavelengths).

### 2018-01-19 ms.tex
fixes

@@
 \includegraphics[width = 1.0\textwidth]{Figures/twopanel_dayside_spectrum.pdf}
-\caption{Dayside planet-to-star flux (points) compared to a blackbody model (dashed gray line) and the best fit 1D model (blue line, with $1\,\sigma$ uncertainty shaded in orange) for the \HST/WFC3 data (left) and Spitzer (right).
+\caption{Dayside planet-to-star flux (points) compared to a blackbody model for the planet (dashed gray line) and the best fit 1D model (blue line, with $1\,\sigma$ uncertainty shaded in orange) for the \HST/WFC3 data (left) and Spitzer (right).
 The 1D model was fit to all the data simultaneously, but the blackbody was fit to the WFC3 data only.
-The best fit 1D model binned at the resolution of the \Spitzer\ data is indicated by blue squares (right).
-}
+The best fit 1D model binned at the resolution of the \Spitzer\ data is indicated by blue squares (right).}
 \label{fig:dayside}
@@
 We also thank the organizers of the 2016 Santa Cruz Kavli Summer Program and the 2017 Ringberg Atmospheres of Disks and Planets meeting for facilitating productive discussion and collaboration.
-J.L.B. acknowledges support from the David and Lucile Packard Foundation.
+J.L.B.
+acknowledges support from the David and Lucile Packard Foundation.
+J.M.D.
+acknowledges support from the European Research Council (ERC) under the programme Exo-Atmos (grant agreement no.
+679633).
 

### 2018-01-24 ms.tex
add spitzer

@@
 
-\title{Global Climate and Atmospheric Composition of the Ultra-Hot Jupiter WASP-103\lowercase{b} from \HST\ and Spitzer Phase Curve Observations}
+\title{Global Climate and Atmospheric Composition of the Ultra-Hot Jupiter WASP-103\lowercase{b} from \HST\ and \Spitzer\ Phase Curve Observations}
 
@@
 	We present thermal phase curve measurements for the hot Jupiter WASP-103b observed with \emph{Hubble}/WFC3 and \emph{Spitzer}/IRAC.
-The dayside planet-to-star flux is $0.151\pm0.015\%$, $0.446\pm0.38\%$, and $0.569\pm0.014\%$ in bandpasses centered at $1.4$, $3.6$, and $4.5\mu$m, respectively.
+The dayside planet-to-star flux ratio is $0.151\pm0.015\%$, $0.446\pm0.038\%$, and $0.569\pm0.014\%$ in bandpasses centered at $1.4$, $3.6$, and $4.5\mu$m, respectively.
 The phase curves have large amplitudes and negligible hotspot offsets, indicative of poor heat redistribution to the nightside.
@@
 Each phase curve observation consisted of 30 hours of time series photometry, beginning three hours prior to one secondary eclipse and ending three hours after a second eclipse.
-We used 12 s exposures to maximize the duty cycle without saturating the detector.
-The data volume is relatively low for this exposure time, so we read out the full array.
+We read out the full array and used 12 s exposures to maximize the duty cycle without saturating the detector.
 To minimize the intrapixel effect (variations in flux caused by imprecise pointing), we did not dither and also used PCRS peak-up\footnote{\url{http://irsa.ipac.caltech.edu/data/SPITZER/docs/irac/pcrs\_obs.shtml}} to improve the pointing accuracy.
@@
 
-The data were reduced with the POET pipeline \citep{stevenson12}.
+The data were reduced with the POET pipeline \citep{stevenson12, cubillos13}.
 We performed aperture photometry with an aperture size of 2.75 pixels (chosen from a grid of apertures between 2 and 4 pixels to minimize the residual noise in the light curve fits).
@@
 This test confirms the presence of time-correlated noise in the Channel 1 light curve that can be seen by eye in the residuals in Figure\,\ref{fig:phasecurves}.
-Both \Spitzer\ channels use the same detector, but Channel 1 data are more susceptible to time-correlated noise because the the point spread function is narrower at shorter wavelengths, making intrapixel sensitivity variations more pronounced.
+Both \Spitzer\ channels use the same detector, but Channel 1 data are more susceptible to time-correlated noise because the the point spread function is further undersampled at shorter wavelengths, making intrapixel sensitivity variations more pronounced.
 
@@
 To test that the phase-resolved spectra are robust to different approaches for fitting the data, we compared the spectra for all four of the thermal phase variation models (sinusoid, kinematic, spherical harmonics, and two temperature).
-We found that the choice of model does not significantly change the results.
+We found that the choice of model does not significantly change the estimated planet-to-star flux values.
 Since the systematic noise is not strongly correlated with the astrophysical signal, the systematics-divided data are nearly identical for all the models.
@@
 	\item{The dayside planet-to-star flux is $0.151\pm0.015\%$, $0.446\pm0.38\%$, and $0.569\pm0.014\%$ in the WFC3 bandpass, \Spitzer\ $3.6$, and \Spitzer\ $4.5\mu$m, respectively.
-The best fit blackbody to the WFC3 dayside spectrum has a brightness temperature of $3013 \pm 8$ K, making WASP-103b among the hottest hot Jupiters ever observed.}
+The best fit blackbody to the WFC3 dayside spectrum has a brightness temperature of $3013 \pm 8$ K, making WASP-103b among the hottest exoplanets ever observed.}
 	\item{The phase curves have large amplitudes ($0.8 -0.9\times$ the secondary eclipse depth), and small offsets in peak brightness from the substellar point (consistent with zero degrees at all wavelengths).

### 2018-01-24 Figures/gcm_comparison.py

@@ -15,7 +15,7 @@ gcms = glob.glob(os.path.join(gcm_path, "PC*PT.dat"))
 
 labels = ["$\\tau_\mathrm{drag} = 10^4$ s", "$\\tau_\mathrm{drag} = 10^3$ s", "[Fe/H] = 0.5", "nominal GCM"]
 
-plt.figure(figsize = (4, 2.5))
+plt.figure(figsize = (4, 6))
 
 #colors = ["#be0119", "#f97306", "#04d9ff", "#0165fc"]
 colors = ["#be0119", "#f97306", "#6dedfd", "#0165fc"]
@@ -42,6 +42,7 @@ def proj_area(phi, inc):
         return  np.sqrt(a3**2*np.sin(inc)**2*(a1**2*np.sin(phi)**2+a2**2*np.cos(phi)**2)+ a1**2*a2**2*np.cos(inc)**2)/(a2*a3)
 
 
+plt.subplot(311)
 inc = 1.523
 
 #plot gcms
@@ -50,7 +51,7 @@ for i, g in enumerate(gcms):
     model = np.genfromtxt(g, delimiter = ',') 
     phi = model[:,0]/360.*2.*np.pi
     area = proj_area(phi, inc)
-    plt.plot(model[:,0]/360. +0.5, model[:,5]*1e3*area, label = labels[i], color = colors[i], linestyle = ls[i])
+    l1, = plt.plot(model[:,0]/360. +0.5, model[:,5]*1e3*area, label = labels[i], color = colors[i], linestyle = ls[i])
     plt.plot(model[:,0]/360. +1.5, model[:,5]*1e3*area, color = colors[i], linestyle = ls[i])
 
     #print "model quadrature", np.interp(0.25, model[:,0]/360. +0.5, model[:,5]*1e3*area) 
@@ -86,19 +87,126 @@ bestfit = m.bestfit[ind]
 ind = np.argsort(phase)
 err, phase, data_corr, bestfit = err[ind], phase[ind], data_corr[ind], bestfit[ind] #sorts by phase
 
-plt.plot(phase, (bestfit-1.)*1e3*dilution, color = '0.2', label = 'best fit')
+#plt.plot(phase, (bestfit-1.)*1e3*dilution, color = '0.2', label = 'best fit')
+plt.plot(phase, (bestfit-1.)*1e3*dilution, color = '0.2')
 plt.plot(phase + 1., (bestfit-1.)*1e3*dilution, color = '0.2') 
 
[…]

### 2018-01-24 ms.tex
comments

@@
 \newcommand{\Kepler}{\project{Kepler}}
+
+\usepackage{graphicx}
 
@@
 We retrieved the atmospheric composition with a 1D self-consistent modeling technique and found the atmosphere is moderately metal-enriched ($\mathrm{[M/H]} =  23^{+29}_{-13}\times$ solar), and the carbon-to-oxygen ratio is below 0.9 at $3\,\sigma$ confidence.
-In contrast to cooler hot Jupiters, we do not detect significant water absorption, which we attribute to partial H$_2$O dissociation and additional opacity from H- and TiO/VO.
+In contrast to cooler hot Jupiters, we do not detect significant water absorption, which we attribute to partial H$_2$O dissociation and additional opacity from H- and trace amounts of hydrides/oxides.
 We compare the phase curves to 3D general circulation models and find that atmospheric drag is required to explain the small hotspot offsets, but that these models overpredict the phase curve amplitude.
@@
 The observations revealed large day-night temperature contrasts (in excess of 300 K), and eastward shifted peak brightness due to heat circulation, as predicted by 3D models \citep{showman02}.
-These infrared measurements were complemented by optical phase curves from \Kepler\ that show evidence for reflected light from patchy and variable dayside clouds with a range of compositions \citep{borucki09, demory13, hu15, armstrong16, parmentier16}.
+These infrared measurements were complemented by optical phase curves from \Kepler\ that show evidence for reflected light from patchy and possibly variable dayside clouds with a range of compositions \citep{borucki09, demory13, hu15, armstrong16, parmentier16}.
 A \emph{spectroscopic} phase curve was observed for WASP-43b with \emph{Hubble}/Wide Field Camera 3 (\HST/WFC3) in the near-infrared, which provided the first phase-resolved measurements of an exoplanet's water abundance and thermal structure \citep{stevenson14, stevenson17}.
@@
 The predicted ellipsoidal variability is shown in Figure\,\ref{fig:ellipsoidal}.
-At quadrature, the projected radius is $8\%$ larger than at phase zero (mid-transit).
+At quadrature, the projected area is $8\%$ larger than at phase zero (mid-transit).
 We also considered the effects of Doppler beaming and found that it contributes less than 10 ppm variability to the measured flux \citep{loeb03}.
@@
 
-For all three phase curves, the hotspot offset is consistent with zero degrees, indicative of a small ratio of radiative to advective timescales (the incident flux is reradiated to space faster than it is advected around to the nightside).
-Fast radiative timescales are precicted at high temperatures, and small hotspot offsets are also observed for other very hot Jupiters \citep{perez13, komacek16, komacek17}.
+For all three phase curves, the hotspot offset is consistent with zero degrees, which could indicate a small ratio of radiative to advective timescales (the incident flux is reradiated to space faster than it is advected around to the nightside).
+Fast radiative timescales are predicted at high temperatures, and small hotspot offsets are also observed for other very hot Jupiters \citep{perez13, komacek16, komacek17}.
 The phase curve amplitudes are large (near 0.8 - 0.9), as expected for an atmosphere with inefficient heat redistribution.
@@
 We used the best-fit phase curves (with systematics removed) to generate phase-resolved emission spectra.
-Since our model does not fit eclipse depth as a free parameter, we estimated the dayside emission spectrum as follows.
+Since the \texttt{spiderman} thermal phase variation models do not fit for eclipse depth as a free parameter, we estimated the dayside emission spectrum as follows.
 We used \texttt{spiderman}'s eclipse\_depth method to calculate the average planet-to-star flux for the best-fit model during secondary eclipse.
@@
 
-To test that the phase-resolved spectra are robust to different approaches for fitting the data, we compared the spectra for all four of the thermal phase variation models (sinusoid, kinematic, spherical harmonics, and two temperature).
-We found that the choice of model does not significantly change the estimated planet-to-star flux values.
+To test that the phase-resolved planet-to-star flux values are robust to different approaches for fitting the phase curves, we compared the estimated planet-to-star flux for all four of the thermal phase variation models (sinusoid, kinematic, spherical harmonics, and two temperature).
+We found that the choice of model does not significantly change the estimated planet-to-star flux ratios.
 Since the systematic noise is not strongly correlated with the astrophysical signal, the systematics-divided data are nearly identical for all the models.
@@
 \begin{figure*}
-\includegraphics[width = 1.0\textwidth]{Figures/hst_model_comparison.pdf}
-\caption{\textbf{Left:} Fits to the broadband WFC3 phase curve compared to a GCM.
-The colored lines correspond to different temperature maps fit to the data, and the dashed gray line is from the $\tau_\mathrm{drag3}$ GCM.
-We also show the planet-to-star flux corresponding to each map (points), which is model-dependent due to slight degeneracies with the instrument systematic model.
-\textbf{Right:} Temperature maps from the best fit models and the GCM at a pressure of 0.01 bar.}
-\label{fig:model_comparison}
+\includegraphics[width = 1.0\textwidth]{Figures/emission_spectra.pdf}
+\caption{Phase-resolved planet-to-star flux ratios (points) compared to the best fit blackbody (blue line) and the GCM with $\tau_\mathrm{drag3}$.
+Phases $\phi = 0.5$ and $0.0$ are centered on the substellar and anti-stellar points, respectively.
+The blackbody model is fit to the \HST/WFC3 data only.}
+\label{fig:spectra}
 \end{figure*}
@@
 \begin{figure*}
-\includegraphics[width = 1.0\textwidth]{Figures/emission_spectra.pdf}
-\caption{Phase-resolved emission spectra (points) compared to the best fit blackbody (blue line) and the GCM with $\tau_\mathrm{drag3}$.
-Phases $\phi = 0.5$ and $0.0$ are centered on the substellar and anti-stellar points, respectively.}
-\label{fig:spectra}
+\includegraphics[width = 1.0\textwidth, trim={1.5cm 0 0.5cm 0},clip]{Figures/hst_model_comparison.pdf}
+\caption{\textbf{Left:} Fits to the broadband WFC3 phase curve compared to a GCM.
+The colored lines correspond to different temperature maps fit to the data, and the dashed gray line is from the $\tau_\mathrm{drag3}$ GCM.
+We also show the measured planet-to-star flux for each map (points), which is model-dependent due to slight degeneracies with the instrument systematic model.
+\textbf{Right:} Temperature maps from the best fit models and the GCM at a pressure of 0.01 bar.}
+\label{fig:model_comparison}
 \end{figure*}
@@
 We fit three different models to characterize the planet's climate: a two-temperature map, the physically-motivated kinematic model of \cite{zhang17}, and a spherical harmonic map.
-We also fit the thermal phase variation with a sinusoid, which can be inverted to map the climate \citep{cowan08}.
+We also fit the thermal phase variation with a sinusoid, which can be inverted to map the climate \citep{cowan08, cowan17}.
 All of the models provide reasonable fits to the data, with $\chi^2_\nu$ near unity, but they yield significantly different temperature maps.
@@
 The kinematic and two temperature models tend to perform significantly worse ($\Delta$BIC and $\Delta$AIC greater than 10).
-As illustrated in Figure\,\ref{fig:model_comparison}, the kinematic model overpredicts the nightside flux, whereas the two temperature model overpredicts the flux at quadrature and underpredicts the dayside.
+As illustrated in Figure\,\ref{fig:model_comparison}, the kinematic model is larger than the observed planet-to-star flux on the nightside, whereas the two temperature model overpredicts the flux at quadrature and underpredicts the dayside.
 
@@
 One explanation for this difference is that the Gaussian process models some of the astrophysical signal.
-If the planet's thermal phase variation is absorbed into the instrument systematic model, the measured eclipse depths would be lower by about 100 ppm.
+If the planet's thermal phase variation is absorbed into the instrument systematic model, the measured eclipse depths would be lower by about 100 ppm (see Figure\,\ref{fig:model_comparison}).
 Since our analysis accounts for the thermal phase variation, it is more likely to provide a robust estimate of the secondary eclipse depths.
@@
 We also compared our dayside spectrum to the $z'$ and $K_\mathrm{S}$-band secondary eclipse depths reported in \cite{delrez18}.
-The $z'$ eclipse is $1.0\,\sigma$ lower than our best fit blackbody spectrum (described in \S\,\ref{sec:composition}), and the $K_\mathrm{S}$ measurement is higher than the model by $2.5\,\sigma$.
+The $z'$ (0.9 $\mu$m) eclipse is $1.0\,\sigma$ lower than our best fit blackbody spectrum (described in \S\,\ref{sec:composition}), and the $K_\mathrm{S}$ (2.1 $\mu$m) measurement is higher than the model by $2.5\,\sigma$.
 Since these results are consistent with (but less precise than) the WFC3 data, we do not include them in our analysis of the atmospheric composition, but we encourage additional measurements in the $K_\mathrm{S}$ band to confidently determine whether an emission feature is present at those wavelengths.
@@
 	\tablehead{
-	\colhead{Orbital Phase} & \colhead{$T_\mathrm{b}$ (K)} & \colhead{$\chi^2_\nu$}}
+	\colhead{Orbital Phase} & \colhead{$T_\mathrm{b}$\tablenotemark{1} (K)} & \colhead{$\chi^2_\nu$}}
 		\startdata
@@
 		\enddata
-		\vspace{-0.8cm}
-		\tablecomments{comments}
+		\tablenotetext{1}{Brightness temperatures were fit using the WFC3 data only.}
 	\end{deluxetable}
@@
 \label{sec:retrieval}
-Since the phase-resolved spectra do not show spectrally resolved molecular features, we opted for a simple grid-based fit to the planet's atmospheric properties, similar to the grid search used in \cite{arcangeli18, mansfield18}.
-We generated a grid from one-dimensional forward models of the atmosphere over a broad range of metallicities, carbon-to-oxygen ratios (C/O), and stellar irradiation.
-The flux at the top of the atmosphere is scaled in intensity over the grid to model the unknown heat redistribution for the planet; i.e., a lower dayside irradiation is equivalent to more efficient heat transport to the nightside.
+To infer abundances from the dayside spectrum, we use a self-consistent grid-based method (ScCHIMERA) similar to that employed in \cite{arcangeli18, mansfield18}.
+We generated a grid from one-dimensional forward models of the atmosphere over a broad range of metallicities (M/H), carbon-to-oxygen ratios (C/O), and stellar irradiation ($f$).
+The $f$ parameter is a scaling for the flux at the top of the atmosphere.
+The input stellar sectrum is scaled in intensity over the grid to model the unknown heat redistribution for the planet; i.e., a lower dayside irradiation $f$ is equivalent to more efficient heat transport to the nightside.
 
@@
 We include opacity from the major absorbers expected for a hot Jupiter atmosphere, including H$_2$O, CO, CO$_2$, TiO, VO, FeH, and H$_2$-H$_2$ CIA.
-Notably, in contrast to many previous studies of the hottest planets, we also included opacity from H-, which is an important absorber at temperatures above 2500 K \citep{arcangeli18}.
+Notably, in contrast to most prior atmospheric retrievals for the hottest planets, we also included opacity from H-, which is an important absorber at temperatures above 2500 K \citep{arcangeli18, parmentier18}.
 Using these opacities and T-P profiles, we calculated thermal emission spectra over the full grid using the CHIMERA retrieval suite \citep[described in][]{line13a, line14}.
 We then explored the grid with an MCMC chain using the \texttt{emcee} package \citep{foremanmackey13} and interpolated in the grid to calculate the likelihood at each model step.
+The priors were uniform over the ranges $0.2 \le f \le 2.8$, $-1\le \log{\mathrm{M/H}} \le 2.5$, and $-1 \le \log{\mathrm{C/O}} \le 0.95$.
 We fit this model to the dayside and nightside emission spectra (phases $\phi = 0.5$ and $0.1$).
@@
 Water also has intrinsically weaker features at high temperature \citep{tinetti12}.
-Water is also an efficient coolant, so lower water abundance leads to a more isothermal photosphere, which further weakens the contrast in and out of the water band.
 On top of this, there is significant H- opacity from single H atoms bound with free electrons, which fills in the opacity at wavelengths shorter than $1.5\,\mu$m.
+Finally, the sharp vertical gradient in water abundance results in water becoming optically thick over a very narrow range in pressure, where temperature is nearly constant.
 Taken together, all these factors add up to produce a nearly featureless spectrum from $1.1 - 1.7\,\mu$m.
@@
 The T-P profile is inverted, with temperature increasing from 2800 to 3500 K over the pressure range $10^{-2} - 10^{-3}$ bar.
-The  thermal inversion is driven by absorption of optical light by oxides and hydrides in the upper atmosphere.
+The thermal inversion is probably driven by absorption of optical light by oxides and hydrides in the upper atmosphere and the absence of cooling by water molecules (which have dissociated).
 The observations are sensitive to pressures of $\sim0.01 - 0.001$ bar, which spans the tropopause, where temperature begins to increase and the water abundance drops by more than an order of magnitude.
@@
 \begin{figure}
-\includegraphics[width = 0.5\textwidth]{Figures/WASP-103b_grid_DAYSIDE_stair_pairs_02.pdf}
+\includegraphics[width = 0.5\textwidth]{Figures/WASP-103b_grid_DAYSIDE_stair_pairs.pdf}
 \caption{Posterior distributions for WASP-103b's atmospheric heat redistribution, metallicity, and C/O, from a grid-based fit to the dayside emission spectrum.
@@
 
-We infer a heat redistribution $f = 0.4^{+0.03}_{-0.02}$.
-The $f$ parameter is allowed to range from 0 (isotropic heat distribution) to 0.5 (dayside emission only).
-Our estimate of $f$ is close to the maximum, indicating inefficient transport of heat to the nightside.
+We infer a heat redistribution $f = 2.49^{+0.14}_{-0.15}$.
+An $f$ parameter of unity represents isotropic heat distribution, whereas $f = 2$ corresponds to dayside emission only.
+Our estimate of $f$ is FIXME (ask Mike how $f$ can be above maximum.
+could it be the inversion?), indicating inefficient transport of heat to the nightside.
 Poor heat transport is observed in other very hot planets as well, due to damping of heat-propagating waves by fast radiative cooling or frictional drag in a partially ionized atmosphere \citep{komacek17}.
-The heat redistribution is correlated with atmospheric metallicity because increasing metallicity pushes the photosphere to higher pressure levels.
+The heat redistribution is strongly correlated with atmospheric metallicity because increasing metallicity  shifts the T-P profile to lower pressures, resulting in hotter temperatures at a given pressure level (equivalent to less efficient heat redistribution).
 
@@
 The best fit spectrum has a non-inverted temperature pressure profile.
-At 1\,$\sigma$ confidence, the metallicity is $15 - 240\times$ solar and the C/O is unbounded over the full prior range (\textbf{Mike: what priors did you use?}).
+At 1\,$\sigma$ confidence, the metallicity is $15 - 240\times$ solar and the C/O is unbounded over the full prior range.
 The atmospheric composition is consistent with results from the dayside spectrum.
@@
 This agreement is an encouraging sanity check; however, there are several model assumptions that may result in artificially tight constraints on the atmospheric properties on the nightside.
-One challenge in modeling the nightside spectrum is that the shape of the T-P profile is unknown.
+One challenge in modeling the nightside spectrum is that the physical processes shaping the T-P profile are unknown.
 Our model assumes a scaled stellar irradiation at the top of the atmosphere, but in reality, the heat source is advection from the dayside.
@@
 To assess how well the GCM predictions reproduce the data, we calculated the amplitude and hot spot offset for all the models (listed in Table\,\ref{table:amps_offsets}).
-The observed hotspot offsets ($0.3 - 2.0$ degrees) are best reproduced by the $\tau_\mathrm{drag3}$ and $\tau_\mathrm{drag4}$ models, which have small offsets due to slower wind speeds.
+The observed hotspot offsets ($0.3 - 2.0$ degrees) are best reproduced by the $\tau_\mathrm{drag3}$ and $\tau_\mathrm{drag4}$ models, which have small offsets due to changes in the wind pattern.
+In the drag models, the winds shift from a substellar to an antistellar flow rather than an equatorial jet.
 The nominal and metal-enhanced GCMs both have offsets that are too large (10-20 degrees).
@@
 As shown in Figure\,\ref{fig:gcmcomparison}, this large amplitude causes the drag models to underestimate the planet-to-star flux away from the substellar point.
+(FIXME: this is all comparison to WFC3 phase curve; add comparison to Spitzer too).
 There are several physical processes not included in the GCM that could contribute to a hotter nightside, including shocks, longitude-dependent drag, latent heat released from H2 recombination.
@@
 \includegraphics[width = 0.5\textwidth]{Figures/gcm_comparison.pdf}
-\caption{GCM predictions (colored lines) compared to the best fit model for the WFC3 white light phase curve (black line).
+\caption{GCM predictions (colored lines) compared to the best fit model for the WFC3 white light, \Spitzer 3.6, and \Spitzer\ 4.5 micron phase curves (black lines, top to bottom).
 The nominal model is solar composition, cloud-free, with TiO/VO opacity and no drag.
@@
 However, the planet's other properties (surface gravity, rotation rate, irradiation) are different.
-To explore the effects of varying these parameters, we compared the spectra of WASP-103b to brown dwarfs and young directly imaged companions.
-The object properties are summarized in Table\,\ref{table:sources}.
+To explore the effects of varying these parameters, we selected spectra from WASP-103b at three orbital phases: dayside ($\phi = 0.5$), quadrature ($\phi = 0.25$), and nightside ($\phi = 0.1$), and compared them to brown dwarfs and young directly imaged companions with comparable brightness temperatures.
 
-We selected spectra from WASP-103b at three orbital phases: dayside ($\phi = 0.5$), quadrature ($\phi = 0.25$), and nightside ($\phi = 0.1$), and compared them to sources with comparable brightness temperature.
-Figure\,\ref{fig:planetstarcomparison} shows the flux-calibrated spectra (assuming a distance of 10 pc).
+We also used three brown dwarfs/low mass stars for comparison.
+We chose the field sources: 2MASS J13204427+0409045, (1320+0409) an optical L3, 2MASS J04285096-2253227 (0428-2253) an optical L0.5 and 2MASS J00034227-2822410 (0003-2822) an optical M8 \citep[see][]{filippazzo15}.
+We then used all currently available photometric, astrometric, and spectroscopic data for each source to evaluate fundamental parameters such as mass, $T_\mathrm{eff}$ and log $g$ \citep{filippazzo15, faherty16} and create flux-calibrated spectral energy distributions.
+For 1320+0409 we used SDSS, WISE and 2MASS photometry along with the optical spectrum from \cite{reid08}, the near infrared spectrum from \cite{bardalez14}, and the parallax reported in \cite{2012ApJ...752...56F}.
+For 0428-2253 we used 2MASS, DENIS and WISE photometry along with the optical spectrum from \cite{2003A&A...403..929K} the near infrared spectrum from \cite{bardalez14} and the parallax reported in \cite{2014AJ...147...94D}, and for 0003-2822 we used 2MASS and WISE photometry along with the optical spectrum from \cite{2007AJ...133..439C} the near infrared spectrum from \cite{2018AJ...155...34C}, and the parallax reported in \cite{2010AJ...139..176F}.
+Coincidentally, both 1320+0409 and 0003-2822 are widely separated ($> 2000$ AU) companions to K2 and G8 stars respectively.
+All data was gathered from the Brown Dwarfs in New York City (BDNYC) database \citep{filippazzo16}\footnote{The BDNYC Database: \url{http://database.bdnyc.org/}}.
+At the assumed field ages of each source, 0003-2822 would be above the nuclear burning boundary (star) while 1320+0409 would be below (brown dwarf).
+0428-2253 is likely a star but at a slightly younger field age could be a brown dwarf.
+
 The directly imaged spectra are for the sources CD-35 2722, USco 1610-1913B, and TWA 22A and are taken from \cite{wahhaj11, aller13, bonnefoy14}.
 They are calibrated in absolute flux using published H-band photometry \citep{wahhaj11, aller13, bonnefoy09} and distances \citep{gaia16, teixeira09}, a flux-calibrated spectrum of Vega \citep{1985A&A...151..399M, 1985IAUS..111..225H}, and the corresponding filter passbands.
-The brown dwarf spectra \textbf{Jackie: describe catalog of brown dwarf spectra and flux calibration}.
 
@@
 
+The system properties for all the objects are summarized in Table\,\ref{table:sources}.
+Figure\,\ref{fig:planetstarcomparison} shows the flux-calibrated spectra (assuming a distance of 10 pc).
 We compared the spectra over the wavelength range $1.1 - 1.7\mu$m.
@@
 This is not surprising: stars in the temperature range $2000 - 3000\,\mathrm{K}$ are well known to have prominent water features \citep{kirkpatrick93}.
-Based on the grid retrieval of WASP-103b's atmospheric composition, there are two reasons WASP-103b would exhibit different behavior at the same temperature.
-First, the atmosphere of WASP-103b is irradiated from above rather than below, leading to a more isothermal temperature profile and weaking spectral features.
-In addition, WASP-103b also has much lower surface gravity (log$g$ = 3.2 versus 4-5 for stars), which pushes the photosphere to lower pressures, where water dissociates more readily (\textbf{Mike: need a reference for this}).
-These factors are not relevant on the nightside, and WASP-103b may have water absorption features there; however, the current data are not precise enough to distinguish between a blackbody spectrum versus water features like those seen in the other objects.
+Based on the grid retrieval of WASP-103b's atmospheric composition, there are several reasons WASP-103b would exhibit different behavior at the same temperature.
+WASP-103b is irradiated from above rather than below, changing the shape of the temperature-pressure profile.
+In addition, WASP-103b also has much lower surface gravity (log$g$ = 3.2 versus 4-5 for stars), which pushes the photosphere to lower pressures, where water dissociates more readily \citep{arcangeli18}.
+These factors are not relevant on the nightside, and 3D models predict that WASP-103b has nightside water absorption features; however, the current data are not precise enough to distinguish between a blackbody spectrum versus water features like those seen in the other objects.
 
@@
 The best fit brightness temperatures ranges from $1920\pm40$ K (phase $\phi = 0.1$) to $3010\pm10$ K on the dayside.
-We attribute the absence of water features at WFC3 wavelengths to (1) H$_2$O dissociation on the dayside, (2) additional near-IR opacity from H-, TiO/VO and FeH, (3) a small temperature gradient at the pressure levels probed by the data.}
+We attribute the absence of water features at WFC3 wavelengths to (1) H$_2$O dissociation on the dayside and (2) additional near-IR opacity from H-, TiO/VO and FeH.}
 \item{The \Spitzer\ data are \emph{not} consistent with a blackbody: there is an infrared emission feature at phases where the substellar point is visible ($\phi = 0.2 - 0.7$), which transitions to an absorption feature on the nightside ($\phi = -0.1 - 0.1$).
@@
 	\item{We ran several 3D GCMs to compare to the data, including a nominal model with a cloud-free, solar composition, a metal-enriched model ([Fe/H] = 0.5), and two models with Lorentz drag.
-The GCMs with Lorentz drag have slower wind speeds and provide the best match to the small hotspot offsets that are observed, but they underpredict the planet's nightside flux.}
+The GCMs with Lorentz drag have different circulation patterns and provide the best match to the small hotspot offsets that are observed, but they underpredict the planet's nightside flux.}
 	\item{We compared the spectra of WASP-103b at phases 0.5 (dayside), 0.25 (quadrature), and 0.1 (nightside) to brown dwarfs and directly imaged companions of similar temperature.
@@
 The planet is complex, with changes in temperature profile with longitude and possible gradients in composition from dayside to nightside.
-These findings highlight the 3D nature of exoplanets and illustrate the importance of phase curve observations for developing a comprehensive understanding of their atmospheric chemistry and physics.
+These findings highlight the 3D nature of exoplanets and illustrate the importance of phase curve observations to develop a comprehensive understanding of their atmospheric chemistry and physics.
 

### 2018-01-24 Figures/hst_model_comparison.py

@@ -197,12 +197,12 @@ plt.gca().set_yticklabels([])
 plt.xlabel("Longitude (deg)")
 
 
-
 #formatting
 ax = plt.subplot(gs[0:2, 4])
 plt.gca().set_visible(False)
 cb = fig.colorbar(im, alpha = 0.8, aspect = 30, fraction = 1) 
 cb.set_label("Temperature (Kelvin)")
+
 
 ###############################
 # plot best fits	      #
@@ -288,6 +288,8 @@ plt.ylabel("Planet-to-star flux (ppt)")
 plt.ylim(-0.2, 2)
 plt.xlim(0,1)
 
+#gs.tight_layout(fig, rect = [0., 0., 1., 1.])
 plt.savefig('hst_model_comparison.pdf')
 
-plt.show()
+
+#plt.show()

### 2018-01-24 Figures/phase_curves_spherical.py

@@ -65,7 +65,7 @@ for ii, f in enumerate(bestfits):
 
 	plt.errorbar(bin_average, (bindata-1.)*1e3*dilution, yerr = binsigma*1e3, fmt = '.k')
 	#plt.plot(phase, (bestfit-1.)*1e3*dilution, color = 'k', label = 'best fit', zorder=20, linewidth = 1.0)
-	plt.plot(phase, (bestfit-1.)*1e3*dilution, color = 'b', label = 'best fit', zorder=-1) 
+	plt.plot(phase, (bestfit-1.)*1e3*dilution, color = 'b', label = 'best fit', zorder=-1, alpha = 0.8, linewidth = 2.0)
 
 	##### plot mcmc
 	"""mcmc = np.load(mcmcs[ii])
@@ -111,7 +111,7 @@ for ii, f in enumerate(bestfits):
 
 	ax = plt.subplot(gs[ii, 1])
 	resid = data_corr - bestfit 
-	plt.axhline(0, color='0.5', zorder=-10)
+	plt.axhline(0, color='0.5', zorder=-10, linewidth = 2.)
 	plt.errorbar(bin_average, (bindata - binbestfit)*1e3, yerr = binsigma*1e3, fmt = '.k')
 	plt.ylim(-0.2,0.2)
 	plt.xlim(0,1)
@@ -185,7 +185,7 @@ for ii, f in enumerate(bestfits):
 
 	plt.errorbar(bin_average, (bindata-1.)*1e3*(1.+dilution[ii]), yerr = binsigma*1e3, fmt = '.k')
 	#plt.plot(phase, (bestfit-1.)*1e3*(1.+dilution[ii]), color = 'k', label = 'best fit')
-	plt.plot(phase, (bestfit-1.)*1e3*(1.+dilution[ii]), color = colors[ii], label = 'best fit')
+	plt.plot(phase, (bestfit-1.)*1e3*(1.+dilution[ii]), color = colors[ii], label = 'best fit', alpha = 0.8, linewidth = 2.0)
 
 
 	ax.set_xticklabels([])
@@ -214,7 +214,7 @@ for ii, f in enumerate(bestfits):
 
 	ax = plt.subplot(gs[ii+1, 1])
 	binresid = bindata - binbestfit
-	plt.axhline(0, color='0.5', zorder = -10)
+	plt.axhline(0, color='0.5', zorder = -10, linewidth = 2.)
[…]

### 2018-01-25 ms.tex
edits

@@
 We began each observation with a 30-minute position settling period, followed by three Astronomical Observation Requests (AORs) of equal duration.
-At the beginning of each AOR, the telescope was repointed to position the target in the ``sweet spot" of the detector.
+At the beginning of each AOR, the telescope was repointed to position the target in the ``sweet spot" of the detector, where the response is fairly uniform over the pixel.
 
@@
 This package allows users to input a climate map (temperature or brightness as a function of latitude and longitude), and generate the corresponding flux ratio for an observation at time $t$.
-In our fit, we calculated the stellar flux with a PHOENIX model \citep{husser13} interpolated to a brightness temperature of $6110\,\mathrm{K}$ \citep{gillon14}, solar metallicity, and log\,$g$ of 4.5 (in cgs units).
+In our fit, we calculated the stellar flux with a PHOENIX model \citep{husser13} interpolated to an effective temperature of $6110\,\mathrm{K}$ \citep{gillon14}, solar metallicity, and log\,$g$ of 4.5 (in cgs units).
 For the planet flux, we tested three different maps: a two-temperature map, with a uniform dayside temperature $T_d$ and a uniform nightside temperature $T_n$; a map generated with spherical harmonics; and the physically-motivated kinematic model from \cite{zhang17}, which has just three free parameters (the nightside temperature $T_n$, the change in temperature from day-to-night side $\Delta_T$, and the ratio of radiative to advective timescales $\xi$).
@@
 At quadrature, the projected area is $8\%$ larger than at phase zero (mid-transit).
-We also considered the effects of Doppler beaming and found that it contributes less than 10 ppm variability to the measured flux \citep{loeb03}.
+Using the analytic expression from \cite{loeb03}, we estimated the effect of Doppler beaming and found that it contributes less than 10 ppm variability to the measured flux.
 
@@
 We ran the MCMC until convergence according to the Gelman-Rubin statistic.
+We initialized the MCMC chain on the best fit parameters and discarded the first 10\% of the chain as burn-in.
 MCMC techniques only produce robust uncertainties when the noise is normally distributed and white, so to account for correlated noise in the $3.6\,\mu$m light curve (described in \S\,\ref{sec:fitquality}) we fit the wavelet model from \cite{carter09} simultaneously with the other model parameters.
@@
 
-The best fit model is either a sinusoid or spherical harmonics, depending on which criterion is used for model selection.
+%The best fit model is either a sinusoid or spherical harmonics, depending on which criterion is used for model selection.
 The BIC generally favors the simpler spherical harmonics model because it penalizes model complexity relatively more than the AIC \citep{kass95}.
-The sinusoid has eight free parameters (amplitude, phase offset, eclipse duration, ingress/egress duration, and midpoint and depth for each of two eclipses), whereas the spherical harmonics model has four (for degree two).
+The sinusoid has four free parameters (amplitude, phase offset, and eclipse midpoint and depth), whereas the spherical harmonics model has four (for degree two).
 The kinematic and two temperature models tend to perform significantly worse ($\Delta$BIC and $\Delta$AIC greater than 10).
@@
 \tablewidth{0pt}
-	\tablecaption{Model Comparison \label{table:model_comparison}}
-	\tablehead{\colhead{Data} & \colhead{Model} & \colhead{$T_\mathrm{min}$} & \colhead{$T_\mathrm{max}$} & \colhead{$\Delta_\mathrm{AIC}$} & \colhead{$\Delta_\mathrm{BIC}$}}
+\tablecaption{Model Comparison \label{table:models}}
+\tablehead{
+\colhead{Data} & \colhead{Model} & \colhead{$T_\mathrm{min}$} & \colhead{$T_\mathrm{max}$} & \colhead{$\Delta_\mathrm{AIC}$} & \colhead{$\Delta_\mathrm{BIC}$}}
 \startdata
 WFC3 & Sph. Harmonics & 1214 & 3251 & 0.0 & 0.0 \\
-		\, & Kinematic & 1980 & 3958 & 11.8 & 11.8 \\
-		\, & Two Temp. & 0 & 2887 & 47.7 & 43.2 \\
-		\, & Sinusoid & -- & -- & 17.7 & 13.2 \\
-		Ch 1 & Sph. Harmonics & 1280 & 3444 & 48.0 & 0.0 \\
-		\, & Kinematic & 1955 & 3675 & 82.3 & 34.3 \\
-		\, & Two Temp. & 1429 & 3041 & 58.7 & 17.6 \\
-		\, & Sinusoid & -- & -- & 0.0 & 98.4 \\
-		Ch 2 & Sph. Harmonics & 902 & 3786 & 2.2 & 3.1 \\
-		\, & Kinematic & 1703 & 4276 & 16.55 & 17.41 \\
-		\, & Two Temp. & 1361 & 3311 & 26.1 & 0.0 \\
-		\, & Sinusoid & -- & -- & 0.0 & 49.6 \\
+\, & Kinematic & 1980 & 3958 & 14.0 & 14.0 \\
+\, & Two Temp. & 0 & 2887 & 49.8 & 45.4 \\
+\, & Sinusoid & -- & -- & 19.8 & 15.4 \\
+Ch 1 & Sph. Harmonics & 1280 & 3444 & 49.0 & 0.0 \\
+\, & Kinematic & 1955 & 3675 & 83.3 & 34.3 \\
+\, & Two Temp. & 1429 & 3041 & 59.7 & 17.6 \\
+\, & Sinusoid & -- & -- & 0.0 & 76.6 \\
+Ch 2 & Sph. Harmonics & 902 & 3786 & 7.9 & 2.3 \\
+\, & Kinematic & 1703 & 4276 & 20.8 & 15.2 \\
+\, & Two Temp. & 1361 & 3311 & 12.5 & 0.0 \\
+\, & Sinusoid & -- & -- & 0.0 & 22.3 \\
 \enddata
@@
 \end{deluxetable}
-
-%The typical uncertainty is FIXME (run MCMC, say the systematic range is larger than the error bars).
 
@@
 
-%\subsection{Clouds?}
+\subsection{Transmission Spectrum}
+The transmission spectrum is challenging to measure due to contaminating flux from the planet's nightside. We will report WASP-103b's transmission spectrum in a companion paper. The 
+FIXME
+
 \section{Atmospheric Composition and Thermal Structure}
@@
 In cooler atmospheres, water is the dominant absorber over this bandpass \citep[e.g.][]{kreidberg14b, line16}, but in WASP-103b, H$_2$O is partially dissociated in the photosphere, leading to a drop in abundance by a factor of $\sim10$ (see Figure\,\ref{fig:summary}).
-Water also has intrinsically weaker features at high temperature \citep{tinetti12}.
+Water also has intrinsically weaker features at high temperature \citep[e.g.][]{tinetti12}.
 On top of this, there is significant H- opacity from single H atoms bound with free electrons, which fills in the opacity at wavelengths shorter than $1.5\,\mu$m.
@@
 However, planet population synthesis models predict some scatter in atmospheric metallicity.
-Planets near WASP-103b's mass ($1.5\,M_\mathrm{Jup}$) are expected to have metallicities ranging from roughly $1-10\times$ solar \citep{mordasini16}.
+Planets near WASP-103b's mass ($1.5\,M_\mathrm{Jup}$) are expected to have metallicities ranging from roughly $1-10\times$ solar \citep{fortney13, mordasini16}.
 Our result for WASP-103b lies on the upper end of this range, and may be indicative of intrinsic scatter in the mass-atmospheric metallicity relation.
@@
 The atmosphere is moderately metal-enriched ($23^{+29}_{-13}\times$ solar; and $>1\times$ solar at $3\,\sigma$ confidence).
-This value is somewhat higher than what is observed for other gas giants and predicted by models \citep[e.g.][]{wong04, kreidberg14b, mordasini16}, and may be indicative of intrinsic scatter in the relationship between atmospheric metallicity and planet mass.
+This value is somewhat higher than what is observed for other gas giants \citep[e.g.][]{wong04, kreidberg14b}, but may be indicative of intrinsic scatter in the relationship between atmospheric metallicity and planet mass predicted by theoretical models \citep{fortney13, mordasini16}.
 However, the metallicity is strongly sensitive to the $4.5\,\mu$m \Spitzer\ eclipse depth, and additional observations would be useful in confirming the metal enhancement.

### 2018-01-25 Figures/fit_table.py

@@ -1,14 +1,18 @@
 import numpy as np
 from lc_fit import Model, LightCurveData
 import pickle 
-#zhang, hotspot, spherical
+
+#get Spitzer AIC/BIC values from results.txt 
+
+#zhang, hotspot, spherical, sincos
 ch1_chi2 = np.array([0.9, 0.9, 0.9, 0.9])
-ch1_aic = np.array([7131.0, 7107.4, 7096.7, 7048.7])
-ch1_bic = np.array([7075.2, 7058.5, 7040.9, 7139.3])
+ch1_aic = np.array([7131.0, 7107.4, 7096.7, 7047.7])
+ch1_bic = np.array([7075.2, 7058.5, 7040.9, 7117.5])
 
 ch2_chi2 = np.array([1.1, 1.1, 1.1, 1.1])
-ch2_aic = np.array([8345.95, 8355.5, 8331.6, 8329.4])
-ch2_bic = np.array([8401.61, 8384.2, 8387.3, 8433.8])
+ch2_aic = np.array([8666.2, 8657.9, 8653.3, 8645.4])
+ch2_bic = np.array([8722.0, 8706.8, 8709.1, 8729.1])
+
 
 # bset fits for WFC3
 wfc3_chi2 = []

### 2018-01-26 ms.tex
edits

@@
 The mean of the three standard deviations is 0.0058~mag, which is very comparable to the mean standard deviation of the six comparison stars (0.0055~mag).
-To maximize the possibility of detecting WASP-103b's rotation, we normalized the photometry such that each observing season has the same mean, thereby removing any long-term variability in WASP-103 and/or the comparison stars (Figure\,\ref{fig:photometry}, top panel).
+To maximize the possibility of detecting WASP-103's rotation, we normalized the photometry such that each observing season has the same mean, thereby removing any long-term variability in WASP-103 and/or the comparison stars (Figure\,\ref{fig:photometry}, top panel).
 We performed a periodogram analysis of the normalized data set based on least-squares fitting of sine curves.
 The resulting frequency spectrum and the phase curve computed with the best period are shown in the middle and lower panels of Figure\,\ref{fig:photometry} respectively.
-The best-fit period is 6.814 days, which agrees closely with the estimated stellar rotation period of 6.855 days of \citep{gillon14}.
+The best-fit period is 6.814 days, which agrees closely with the estimated stellar rotation period of 6.855 days \citep[based on the projected stellar rotation velocity reported in][]{gillon14}.
 The peak-to-peak variability amplitude is 0.005 mag.
@@
 The free parameters for the transit model were the transit depth $r_p$ and a linear limb darkening parameter $u$.
+More complex limb darkening laws with additional free parameters were not merited according to the Bayesian Information Criterion (BIC).
 
@@
 In addition to the intrapixel sensitivity variation, we fit the data for a linear trend in time.
-We tested a quadratic trend but did not find significant evidence for the additional model complexity based on the Bayesian information criterion (BIC).
-
-%We explored adding an additional sine term to model the thermal phase variation, but the additional degrees of freedom are not justified according to the Bayesian Information Criterion (BIC).
+We tested a quadratic trend but did not find significant evidence for the additional model complexity based on the BIC.
 
@@
 We used the best-fit phase curves (with systematics removed) to generate phase-resolved emission spectra.
-Since the \texttt{spiderman} thermal phase variation models do not fit for eclipse depth as a free parameter, we estimated the dayside emission spectrum as follows.
+Since the \texttt{spiderman} thermal phase variation models fit the temperature of the planet rather than the eclipse depth directly, we estimated the dayside emission spectrum as follows.
 We used \texttt{spiderman}'s eclipse\_depth method to calculate the average planet-to-star flux for the best-fit model during secondary eclipse.
@@
 The shape of their spectrum is consistent with what we find, but their eclipse depths are 125 ppm smaller on average (a difference of about 10\%).
-In their analysis, \cite{cartier17} noted that the Gaussian process fit produces smaller eclipse depths than a parametric fit (also by 125 ppm).
-One explanation for this difference is that the Gaussian process models some of the astrophysical signal.
-If the planet's thermal phase variation is absorbed into the instrument systematic model, the measured eclipse depths would be lower by about 100 ppm (see Figure\,\ref{fig:model_comparison}).
-Since our analysis accounts for the thermal phase variation, it is more likely to provide a robust estimate of the secondary eclipse depths.
+A likely explanation for this difference is that the \cite{cartier17} analysis does not include the planet's thermal phase variation, so that the Gaussian process models it as an instrument systematic.
+If the phase variation is absorbed into the systematic model, the measured eclipse depths would be biased low by about 100 ppm (see Figure\,\ref{fig:model_comparison}).
 Our estimated uncertainties are a factor of four smaller than those reported in \cite{cartier17}, which is consistent with photon-limited expectations (our data set includes two additional eclipses, a factor of five longer out-of-eclipse baseline, and has 60\% larger wavelength bins).
+
+%In their analysis, \cite{cartier17} noted that the Gaussian process fit produces smaller eclipse depths than a parametric fit (also by 125 ppm).
 
@@
 The main characteristics of the dayside emission spectrum are: (1) it is blackbody-like at WFC3 wavelengths, and (2) in the \Spitzer\ bands, the planet-to-star flux is significantly higher than predicted for the best fit blackbody, indicating an emission feature.
-The best-fit spectrum reproduces these data fairly well, with $\chi^2_\nu$ = 1.77.
+The best-fit spectrum reproduces these data fairly well, with $\chi^2_\nu$ = 1.77 (for 9 degrees of freedom).
 The largest contribution to the $\chi^2$ value is the $4.5\,\mu$m eclipse depth, which is larger than the best fit model prediction by $2.9\,\sigma$.
-When the $4.5\,\mu$m point is removed, the fit has $\chi^2_\nu = 1.17$.
+When the $4.5\,\mu$m point is removed, the fit has $\chi^2_\nu = 1.17$ (8 degrees of freedom).
 The best fit model has a moderately enhanced metallicity ($23\times$ solar), carbon-to-oxygen equal to 0.76, poor heat redistribution, and a thermal inversion (temperature increasing with altitude).

### 2018-01-29 ms.tex
temperature table

@@
 Planets are round, rotating, and irradiated on one hemisphere at a time -- all of which contribute to rich spatial structure in their climate and atmospheric composition.
-Short period, tidally locked planets are an extreme example, with hot, continuously illuminated daysides.
+Short period, tidally locked planets are an extreme example, with one hot, continuously illuminated side.
 This asymmetry is expected to produce large gradients in temperature, chemistry, and cloud coverage with longitude \citep{showman09, kataria16, parmentier16}, and provides an opportunity to learn about atmospheric dynamics in a very different regime from the Solar System planets.
 
-Exoplanets are so distant that they are not spatially resolved, so the only way to reveal inhomogeneity in their atmospheres is to measure a phase curve.
-Phase curve observations consist of continuous monitoring of the planet-to-star flux ratio over a complete orbital revolution of the planet, which exposes different longitudes at each orbital phase.
+Exoplanets are so distant that they are not spatially resolved from their host stars, but it is still possible to reveal inhomogeneities in their atmospheres.
+One approach is to measure a phase curve, which consists of continuous monitoring of the planet-to-star flux ratio over a complete orbital revolution of the planet.
+This observation is sensitive to different longitudes at each orbital phase of the planet.
 The first phase curve of an exoplanet was observed with \Spitzer\ for the hot Jupiter HD 189733b by \cite{knutson07}, followed by additional \Spitzer\ observations for about a dozen more systems \citep[cataloged in][]{parmentier17}.
@@
 \subsection{Photometric Monitoring}
-We monitored WASP-103's photometric variability over 158 nights during 2014 - 2016 with the Tennessee State University Celestron 14-inch (C14) automated imaging telescope (AIT), located at Fairborn Observatory in southern Arizona \citep[][]{henry99}.
+To assess how stellar activity might impact the phase curve observations, we monitored WASP-103's photometric variability over 158 nights during 2014 - 2016 with the Tennessee State University Celestron 14-inch (C14) automated imaging telescope (AIT), located at Fairborn Observatory in southern Arizona \citep[][]{henry99}.
 The observations of WASP-103 were made in the Cousins R passband with an SBIG STL-1001E CCD camera.
@@
 To maximize the possibility of detecting WASP-103's rotation, we normalized the photometry such that each observing season has the same mean, thereby removing any long-term variability in WASP-103 and/or the comparison stars (Figure\,\ref{fig:photometry}, top panel).
-We performed a periodogram analysis of the normalized data set based on least-squares fitting of sine curves.
+To estimate the stellar rotation period, we performed a periodogram analysis of the normalized data set based on least-squares fitting of sine curves.
 The resulting frequency spectrum and the phase curve computed with the best period are shown in the middle and lower panels of Figure\,\ref{fig:photometry} respectively.
@@
 $Middle$: The frequency spectrum of the normalized dataset suggests low-amplitude variability with a period of 6.814~days.
-$Bottom$: The normalized dataset phased to the 6.814-day period, which we interpret as the stellar rotation period.
+$Bottom$: The normalized dataset phased to the 6.814-day period, which we interpret as rotational modulation of a star spot or spots.
 A least-squares sine fit to the 6.814-day rotation period gives a peak-to-peak amplitude of just 0.005~mag.}
@@
 \end{equation}
-where $T(\lambda, t)$ is the transit model (the fraction of the stellar disk that is visible at time $t$), $F_p/F_s(\lambda, t)$ is the disk-integrated planet-to-star flux, and $c$ is a correction factor for companion star dilution and the planet's tidal distortion.
+where $\lambda$ is wavelength, $T(\lambda, t)$ is the transit model (the fraction of the stellar disk that is visible at time $t$), $F_p/F_s(\lambda, t)$ is the disk-integrated planet-to-star flux, and $c$ is a correction factor for companion star dilution and the planet's tidal distortion.
 
@@
 In our fit, we calculated the stellar flux with a PHOENIX model \citep{husser13} interpolated to an effective temperature of $6110\,\mathrm{K}$ \citep{gillon14}, solar metallicity, and log\,$g$ of 4.5 (in cgs units).
-For the planet flux, we tested three different maps: a two-temperature map, with a uniform dayside temperature $T_d$ and a uniform nightside temperature $T_n$; a map generated with spherical harmonics; and the physically-motivated kinematic model from \cite{zhang17}, which has just three free parameters (the nightside temperature $T_n$, the change in temperature from day-to-night side $\Delta_T$, and the ratio of radiative to advective timescales $\xi$).
+For the planet flux, we tested three different maps: a two-temperature map, with a uniform dayside temperature $T_d$ and a uniform nightside temperature $T_n$; a spherical harmonic maps of degree two (with four free parameters); and the physically-motivated kinematic model from \cite{zhang17}, which has just three free parameters (the nightside temperature $T_n$, the change in temperature from day-to-night side $\Delta_T$, and the ratio of radiative to advective timescales $\xi$).
 In all cases, we assumed that the planet is tidally locked, such that each orbital revolution corresponds to one complete rotation on its spin axis.
@@
 \caption{Phase-resolved planet-to-star flux ratios (points) compared to the best fit blackbody (blue line) and the GCM with $\tau_\mathrm{drag3}$.
-Phases $\phi = 0.5$ and $0.0$ are centered on the substellar and anti-stellar points, respectively.
+Phases $\phi=0.5$ and $0.0$ correspond to times of secondary eclipse and transit, when the substellar and antistellar points are respectively aimed at Earth.
 The blackbody model is fit to the \HST/WFC3 data only.}
@@
 
-\begin{deluxetable}{llllll}
-\tablecolumns{6}
+\begin{deluxetable}{llllllll}
+	\tablecolumns{8}
 	\tablewidth{0pt}
@@
 	\tablehead{
-\colhead{Data} & \colhead{Model} & \colhead{$T_\mathrm{min}$} & \colhead{$T_\mathrm{max}$} & \colhead{$\Delta_\mathrm{AIC}$} & \colhead{$\Delta_\mathrm{BIC}$}}
+	\colhead{Data} & \colhead{Model} & \colhead{$T_\mathrm{min}$} & \colhead{$T_\mathrm{max}$} & \colhead{$\overline{T}_\mathrm{night}$} & \colhead{$\overline{T}_\mathrm{day}$} &\colhead{$\Delta_\mathrm{AIC}$} & \colhead{$\Delta_\mathrm{BIC}$}}
 		\startdata
-WFC3 & Sph. Harmonics & 1214 & 3251 & 0.0 & 0.0 \\
-\, & Kinematic & 1980 & 3958 & 14.0 & 14.0 \\
-\, & Two Temp. & 0 & 2887 & 49.8 & 45.4 \\
-\, & Sinusoid & -- & -- & 19.8 & 15.4 \\
-Ch 1 & Sph. Harmonics & 1280 & 3444 & 49.0 & 0.0 \\
-\, & Kinematic & 1955 & 3675 & 83.3 & 34.3 \\
-\, & Two Temp. & 1429 & 3041 & 59.7 & 17.6 \\
-\, & Sinusoid & -- & -- & 0.0 & 76.6 \\
-Ch 2 & Sph. Harmonics & 902 & 3786 & 7.9 & 2.3 \\
-\, & Kinematic & 1703 & 4276 & 20.8 & 15.2 \\
-\, & Two Temp. & 1361 & 3311 & 12.5 & 0.0 \\
-\, & Sinusoid & -- & -- & 0.0 & 22.3 \\
+		WFC3 & Sph. Harmonics & 1214 & 3251 & 1820 & 2622 & 0.0 & 0.0 \\
+		\, & Kinematic & 1980 & 3958 & 1980 & 2777 & 14.0 & 14.0 \\
+		\, & Two Temp. & 0 & 2887 & 0 & 2887 & 49.8 & 45.4 \\
+		\, & Sinusoid & -- & -- & -- & -- & 19.8 & 15.4 \\
+		Ch 1 & Sph. Harmonics & 1280 & 3444 & 1936 & 2786 & 49.0 & 0.0 \\
+		\, & Kinematic & 1955 & 3675 & 1999 & 2656 & 83.3 & 34.3 \\
+		\, & Two Temp. & 1429 & 3041 & 1429 & 3025 & 59.7 & 17.6 \\
+		\, & Sinusoid & -- & -- & -- & -- & 0.0 & 76.6 \\
+		Ch 2 & Sph. Harmonics & 902 & 3786 & 1753 & 2920 & 7.9 & 2.3 \\
+		\, & Kinematic & 1703 & 4276 & 1711 & 2740 & 20.8 & 15.2 \\
+		\, & Two Temp. & 1361 & 3311 & 1361 & 3292 & 12.5 & 0.0 \\
+		\, & Sinusoid & -- & -- & -- & -- & 0.0 & 22.3 \\
 		\enddata
@@
 \includegraphics[width = 0.5\textwidth]{Figures/atmosphere_summary.pdf}
-\caption{Summary of the 1D self-consistent model atmosphere fits.
+\caption{Summary of the 1D self-consistent model atmosphere fits to the dayside emission spectrum.
 The temperature-pressure profile (top axis) is indicated by the 1-sigma spread of 500 randomly drawn T-P profiles from the posterior (light red) and a representative fit, with $f$=0.4, [M/H]=1.5, and C/O=0.7 (dark red).
@@
 \label{sec:gcm}
-To explore the three-dimensional effects of atmospheric dynamics, we ran several GCM models to compare with the measured phase-resolved spectra.
+To explore the three-dimensional effects of atmospheric dynamics, we ran several GCMs to compare with the measured phase-resolved spectra.
 (\textbf{Vivien: add text describing GCM}).
@@
 	\caption{Row (1): photospheric temperatures for the $\tau_\mathrm{drag3}$ GCM for different viewing geometries.
-The substellar point corresponds to $\alpha = 0$ and the antistellar point is $\alpha = \pm 180$.
+The orbital phase $\alpha=0$ corresponds to secondary eclipse (when the substellar point faces Earth) and $\alpha=180$ corresponds to transit (when the antistellar point faces Earth).
 Row (2) indicates the ratio of pressures probed in and out of the water band.
@@
 Rows (3-4) show the abundances of H$_2$O and H-.
-At dayside temperatures, water dissociates and the photospheric abundance drops by $\sim10$.
-}
+At dayside temperatures, water dissociates and the photospheric abundance drops by $\sim10$.}
 \label{fig:GCMabundance}

### 2018-01-29 Figures/fit_table.py

@@ -41,6 +41,12 @@ wfc3_bic = np.array(wfc3_bic)
 #model, Tmin, Tmax =  spherical 1213.50410565 3251.37484203
 wfc3_tmin = np.array([1980, 0, 1214, 0])
 wfc3_tmax = np.array([3958, 2887, 3251, 0])
+#from get_mean_daynight_temp.py 
+#zhang: dayside, nightside average =  2776.64415413 1979.6612603
+#hotspot: dayside, nightside average =  2867.87112076 0.0
+#spherical: dayside, nightside average =  2621.83263714 1820.2805918
+wfc3_daymu = np.array([2777, 2887, 2622, 0])
+wfc3_nightmu = np.array([1980, 0, 1820, 0])
 
 #Spitzer Ch 2
 #model, Tmin, Tmax =  zhang 1703.0 4276.80767467
@@ -48,6 +54,12 @@ wfc3_tmax = np.array([3958, 2887, 3251, 0])
 #model, Tmin, Tmax =  spherical 902.401726015 3786.1376002
 ch2_tmin = np.array([1703, 1361, 902, 0])
 ch2_tmax = np.array([4276, 3311, 3786, 0])
+#from spitzer_maptemp.py
+#zhang daymu, nightmu, min, max 2740.48761346 1711.12738853 1703.0 4287.03108111
+#hotspot_t daymu, nightmu, min, max 3291.5 1361.0 1361.0 3311.0
+#spherical daymu, nightmu, min, max 2919.98921277 1752.56989088 895.304735881 3786.3843194
+ch2_daymu = np.array([2740, 3292, 2920, 0])
+ch2_nightmu = np.array([1711, 1361, 1753, 0])
 
 #Spitzer Ch 1
 #model, Tmin, Tmax =  zhang 1955.0 3675.62794318
@@ -55,47 +67,53 @@ ch2_tmax = np.array([4276, 3311, 3786, 0])
 #model, Tmin, Tmax =  spherical 1280.4447703 3444.26296074
 ch1_tmin = np.array([1955, 1429, 1280, 0])
 ch1_tmax = np.array([3675, 3041, 3444, 0])
+#from spitzer_maptemp.py
+#zhang daymu, nightmu, min, max 2656.25693185 1998.88866205 1955.0 3699.89072043
[…]

### 2018-01-29 Figures/gcm_comparison.py

@@ -113,7 +113,7 @@ plt.errorbar(bin_average, (bindata-1.)*1e3*dilution, yerr = binsigma*1e3, fmt = 
 
 plt.xlim(0, 1.1)
 plt.ylim(-0.1, 2.3)
-plt.ylabel("Planet-to-star flux (ppt)")
+plt.ylabel("Planet-to-star flux ($\\times10^{-3}$)")
 plt.xlabel("Phase")
 
 first_legend = plt.legend(handles=[l1, l2, l3, l4], loc='upper right', frameon=True)
@@ -138,7 +138,7 @@ for i, g in enumerate(gcms):
 
 plt.xlim(0, 1.1)
 plt.ylim(-0.6, 5.5)
-plt.ylabel("Planet-to-star flux (ppt)")
+plt.ylabel("Planet-to-star flux ($\\times10^{-3}$)")
 plt.xlabel("Phase")
 
 plt.gca().text(0.05, 4., 'Spitzer\nCh 1', fontsize=10)
@@ -156,7 +156,7 @@ for i, g in enumerate(gcms):
 
 plt.xlim(0, 1.1)
 plt.ylim(-0.6, 6.3)
-plt.ylabel("Planet-to-star flux (ppt)")
+plt.ylabel("Planet-to-star flux ($\\times10^{-3}$)")
 plt.xlabel("Phase")
 
 plt.gca().text(0.05, 4.5, 'Spitzer\nCh 2', fontsize=10)

### 2018-01-29 Figures/hst_bestfit.py

@@ -62,7 +62,7 @@ for i, model in enumerate(models):
 
 plt.legend(loc = 'upper left', frameon=False, fontsize=12)
 plt.xlabel("Orbital phase")
-plt.ylabel("Planet-to-star flux (ppt)")
+plt.ylabel("Planet-to-star flux ($\\times10^{-3}$)")
 plt.ylim(-0.2, 2)
 plt.xlim(0,1)
 plt.tight_layout()

### 2018-01-29 Figures/hst_model_comparison.py

@@ -284,7 +284,7 @@ ax.legend(handles,labels,loc='upper left', frameon = False, fontsize = 11)
 
 
 plt.xlabel("Orbital phase")
-plt.ylabel("Planet-to-star flux (ppt)")
+plt.ylabel("Planet-to-star flux ($\\times10^{-3}$)")
 plt.ylim(-0.2, 2)
 plt.xlim(0,1)
 

### 2018-01-29 Figures/two_panel_dayside_espec.py

@@ -107,7 +107,7 @@ plt.errorbar(x, y*1e3, e*1e3, fmt = 'ok')
 plt.legend(loc = 'lower right', frameon=True, fontsize = 10)
 plt.gca().text(0.07, 0.83, 'HST/WFC3', transform=ax.transAxes)
 
-plt.ylabel("Planet-to-star flux (ppt)")
+plt.ylabel("Planet-to-star flux ($\\times1-^{-3}$)")
 plt.xlabel("Wavelength (microns)")
 
 

### 2018-01-29 ms.tex
editss'

@@
 		\colhead{Observing} & \colhead{} & \colhead{Date Range} &
-	\colhead{Sigma} & \colhead{Seasonal Mean} }
+	\colhead{Sigma} & \colhead{Seasonal Mean} \\
+		& \colhead{\,} & \colhead{\,} & \colhead{(mag)} & \colhead{(mag)}}
 	\startdata
@@
 We generated a grid from one-dimensional forward models of the atmosphere over a broad range of metallicities (M/H), carbon-to-oxygen ratios (C/O), and stellar irradiation ($f$).
-The $f$ parameter is a scaling for the flux at the top of the atmosphere.
-The input stellar sectrum is scaled in intensity over the grid to model the unknown heat redistribution for the planet; i.e., a lower dayside irradiation $f$ is equivalent to more efficient heat transport to the nightside.
+The $f$ parameter is a scaling factor for the stellar flux at the top of the atmosphere, where $f=1$ corresponds to full heat redistribution and $f=2$ is equivalent to only allowing the dayside to re-radiate.
+%The input stellar sectrum is scaled in intensity over the grid to model the unknown heat redistribution for the planet; i.e., a lower dayside irradiation $f$ is equivalent to more efficient heat transport to the nightside.
 
@@
 \includegraphics[width = 0.5\textwidth]{Figures/xsec_FULL.pdf}
-\caption{Abundance weighted absorption cross-sections illustrating the important opacity sources at the photospheric pressure level (5 mbar).
+\caption{Abundance weighted absorption cross-sections illustrating the important opacity sources at the photospheric pressure and temperature (5 mbar, 3036 K).
 The strong CO feature at 4.5\,$\mu$m contributes to the high planet-to-star flux at that wavelength.
@@
 An $f$ parameter of unity represents isotropic heat distribution, whereas $f = 2$ corresponds to dayside emission only.
-Our estimate of $f$ is FIXME (ask Mike how $f$ can be above maximum.
-could it be the inversion?), indicating inefficient transport of heat to the nightside.
-Poor heat transport is observed in other very hot planets as well, due to damping of heat-propagating waves by fast radiative cooling or frictional drag in a partially ionized atmosphere \citep{komacek17}.
+We estimate $f > 2$, indicating a thermal inversion and likely inefficient transport of heat to the nightside.
+%Poor heat transport is observed in other very hot planets as well, due to damping of heat-propagating waves by fast radiative cooling or frictional drag in a partially ionized atmosphere \citep{komacek17}.
 The heat redistribution is strongly correlated with atmospheric metallicity because increasing metallicity  shifts the T-P profile to lower pressures, resulting in hotter temperatures at a given pressure level (equivalent to less efficient heat redistribution).
@@
 \includegraphics[width = 1.0\textwidth]{Figures/spectra_comparison.pdf}
-\caption{Flux-calibrated spectra for WASP-103b (left column) compared to brown dwarfs (middle) and directly imaged companions (right), assuming a distance of 10 pc.
+\caption{Flux-calibrated spectra for WASP-103b (left column) compared to observed spectra for brown dwarfs (middle) and directly imaged companions (right), assuming a distance of 10 pc.
 The WASP-103b spectra are from the nightside (phase 0.1, top row), quadrature (phase 0.25, middle) and the dayside (phase 0.5, bottom).

### 2018-01-29 Figures/hst_model_comparison.py

@@ -80,7 +80,7 @@ def initialize_params(spider_params):
     spider_params.T_s = 6110.		# Temperature of the star
     return spider_params
 
-models = ["hotspot_t", "zhang", "spherical"]
+models = ["hotspot_t", "zhang", "spherical"] 
 labels = ["Two temp.", "Kinematic", "Sph. harmonics"] 
 path = "WFC3_best_fits/"
 waverange = [1.1e-6, 1.7e-6]                    #Spitzer Ch 2
@@ -125,7 +125,7 @@ for i, model in enumerate(models):
   	sph2 = par[d.par_order['sph2']*d.nvisit]
   	sph3 = par[d.par_order['sph3']*d.nvisit]
         spider_params.sph = [sph0, sph1, sph2, sph3]
-	print spider_params.sph
+	#print spider_params.sph
 
     elif model == "hotspot_t":
 	spider_params.la0 = 0.
@@ -133,6 +133,9 @@ for i, model in enumerate(models):
 	spider_params.size = 90.
 	spider_params.spot_T = par[d.par_order['spot_T']*d.nvisit]
 	spider_params.p_T = par[d.par_order['p_T']*d.nvisit]
+
+    elif model == "sincos":
+	print "AHHH"
         
     else:
         print "model not supported"
@@ -208,14 +211,14 @@ cb.set_label("Temperature (Kelvin)")
 # plot best fits	      #
 ###############################
 
-#models = ["hotspot_t", "zhang", "spherical"]
-#labels = ["Two temp.", "Kinematic", "Sph. harmonics"] 
+models = ["hotspot_t", "zhang", "spherical", "sincos"]
+labels = ["Two temp.", "Kinematic", "Sph. harmonics", "Sinusoid"] 
 path = "WFC3_best_fits/"
 waverange = [1.1e-6, 1.7e-6]                    #WFC3
-colors = ['#82cafc', '#ff7855', 'purple'] 
+colors = ['#82cafc', '#ff7855', 'purple', 'red'] 
 grays = ['0.7', '0.5', '0.6']
 #linestyle = ['-', '-.', ':']
-linestyle = ['-', '-', '-']
+linestyle = ['-', '-', '-', '-']
 
 phasebins = np.linspace(0., 1., 50)
 nbins = len(phasebins) - 1
@@ -257,7 +260,7 @@ for i, model in enumerate(models):
[…]

### 2018-01-30 Figures/compare_stellar_spectra.py
compare spectra

@@ -1,0 +1,17 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+#Vivien spectrum - col = wavelength (microns), flux at 1 AU, in W/m2/micron, flux at stellar surface, erg/cm2/sec/Hz 
+d = np.genfromtxt("W103-6110K-1.22Ms-1.22Rs.dat")
+d[:,1] = d[:,1]*d[:,0]
+plt.plot(d[:,0], d[:,1], label = "Vivien")
+print d[:,1].max()
+
+#Keivan spectrum, micron, [ergs/s/cm^2]  
+d = np.genfromtxt("wasp103_sed_fluxes.out")
+plt.plot(d[:,0], d[:,1], label = "Keivan")
+plt.xlim(0,5)
+plt.legend(loc= 'upper right')
+print d[:,1].max()
+
+plt.show()

### 2018-02-01 ms.tex
compare spectra
transmission spectrum

@@
 \subsection{Transmission Spectrum}
-The transmission spectrum is challenging to measure due to contaminating flux from the planet's nightside. We will report WASP-103b's transmission spectrum in a companion paper. The 
-FIXME
+Each phase curve observation includes a transit of WASP-103b. The transmission spectrum is challenging to measure robustly due to contaminating flux from the planet's nightside. 
+\begin{figure}
+\includegraphics[width = 0.5\textwidth]{Figures/w103b_transmission_spectrum.pdf}
+\caption{Transmission spectrum of WASP-103b.}
+\label{fig:tspec}
+\end{figure}
 
@@
 \begin{figure*}
-	\includegraphics[width = 1.0\textwidth]{Figures/GCM_abundances.eps}
+	\includegraphics[width = 1.0\textwidth]{Figures/GCM_abundances.pdf}
 	\caption{Row (1): photospheric temperatures for the $\tau_\mathrm{drag3}$ GCM for different viewing geometries.
 The orbital phase $\alpha=0$ corresponds to secondary eclipse (when the substellar point faces Earth) and $\alpha=180$ corresponds to transit (when the antistellar point faces Earth).
-Row (2) indicates the ratio of pressures probed in and out of the water band.
+FIXME: Row (2) indicates the ratio of pressures probed in and out of the water band.
 On the dayside, the opacity out of the water band is filled in by absorption from H- and TiO/VO.
@@
 For 1320+0409 we used SDSS, WISE and 2MASS photometry along with the optical spectrum from \cite{reid08}, the near infrared spectrum from \cite{bardalez14}, and the parallax reported in \cite{2012ApJ...752...56F}.
-For 0428-2253 we used 2MASS, DENIS and WISE photometry along with the optical spectrum from \cite{2003A&A...403..929K} the near infrared spectrum from \cite{bardalez14} and the parallax reported in \cite{2014AJ...147...94D}, and for 0003-2822 we used 2MASS and WISE photometry along with the optical spectrum from \cite{2007AJ...133..439C} the near infrared spectrum from \cite{2018AJ...155...34C}, and the parallax reported in \cite{2010AJ...139..176F}.
+For 0428-2253 we used 2MASS, DENIS and WISE photometry along with the optical spectrum from \cite{2003A&A...403..929K} the near infrared spectrum from \cite{bardalez14} and the parallax reported in \cite{2014AJ....147...94D}, and for 0003-2822 we used 2MASS and WISE photometry along with the optical spectrum from \cite{2007AJ....133..439C} the near infrared spectrum from \cite{2018AJ....155...34C}, and the parallax reported in \cite{2010AJ....139..176F}.
 Coincidentally, both 1320+0409 and 0003-2822 are widely separated ($> 2000$ AU) companions to K2 and G8 stars respectively.
-All data was gathered from the Brown Dwarfs in New York City (BDNYC) database \citep{filippazzo16}\footnote{The BDNYC Database: \url{http://database.bdnyc.org/}}.
+All data was gathered from the Brown Dwarfs in New York City (BDNYC) database \citep{filippazzo15}\footnote{The BDNYC Database: \url{http://database.bdnyc.org/}}.
 At the assumed field ages of each source, 0003-2822 would be above the nuclear burning boundary (star) while 1320+0409 would be below (brown dwarf).

### 2018-02-01 ms.tex
fixed figure

@@
 \subsection{Transmission Spectrum}
-Each phase curve observation includes a transit of WASP-103b. The transmission spectrum is challenging to measure robustly due to contaminating flux from the planet's nightside. 
+Each phase curve observation includes a transit of WASP-103b.
+To measure the wavelength-dependent transit depths (the transmission spectrum), we select a subset of each phase curve.
+The subset includes the transit and additional baseline on either side, such that the total light curve has twice the duration of the transit.
+Over this short duration, there is negligible curvature in the light curve due to the planet's thermal phase variation.
+We fit the data with a transit model, which has free parameters for the planet-to-star radius and a linear limb darkening parameter.
+We fit for the instrument systematics using the same parameters as the phase curve fits, except that we modeled the visit-long systematic as a linear trend in time (which is sufficient for the shorter duration).
+The advantage of fitting the transits separately from the full phase curves is that the resultant transit depths are not dependent on how the phase variation is modeled.
+We do not model the transit in the \Spitzer\,$3.6\mu$m channel, since it is challenging to robustly estimate the contribution of correlated noise in the subset of data we model here.
+FIXME
+
+We show the measured transmission spectrum in Figure,\ref{fig:tspec}.
+The spectrum is biased by flux contamination from the planet's nightside; to correct for nightside emission, we estimate the planet-to-star flux ratio and subtract it from the transit depth.
+We calculate planet-to-star flux assuming a FIXME PHOENIX model for the star, a blackbody for the planet, and a planet-to-star radius ratio of FIXME.
+We consider two plausible nightside temperatures (1400 and 2000 K), which encompass the range of mean nightside temperatures calculated from the phase variation models (Table\,\ref{tab:FIXME}).
+We also show the uncorrected transit depths.
+For the uncorrected data, there is an offset between the \HST\ and \Spitzer\ data of about 10 atmospheric scale heights, much larger than expected from theoretical models.
+FIXME show GCM in this figure.
+Water abundance?
+
 \begin{figure}
 \includegraphics[width = 0.5\textwidth]{Figures/w103b_transmission_spectrum.pdf}
-\caption{Transmission spectrum of WASP-103b.}
+\caption{The transmission spectrum of WASP-103b (points) for a range of assumptions about the planet's nightside temperature.
+The gray points correspond to no correction for the nightside flux.
+The blue and red points assume the average nightside photospheric temperature is 1400 and 2000 K, respectively.
+The atmospheric scale height assumes FIXME.}
 \label{fig:tspec}

### 2018-02-01 Figures/phased_espec.py

@@ -23,44 +23,47 @@ def blackbody(l,T):
         return 2*h*c**2/(l**5*(np.exp(h*c/(l*k*T))-1))                 #[W/sr/m^3]
 
 def best_fit_bb(w, y, e, rprs):
-	Ts = np.linspace(1000, 3600, 10000)
-	chibest = 10000.
-	Tbest = 0.	
-	Tstar = 6110.
-	resid = 0.
+    Ts = np.linspace(1000, 3600, 10000)
+    chibest = 10000.
+    Tbest = 0.  
+    Tstar = 6110.
+    resid = 0.
 
-	w = np.array(w)
+    w = np.array(w)
 
-	w, y, e = w[0:10], y[0:10], e[0:10]     #WFC3 data only
-#	w, y, e = w[10], y[10], e[10]           #spitzer ch1
-#	w, y, e = w[11], y[11], e[11]           #spitzer ch2
+    w, y, e = w[0:10], y[0:10], e[0:10]     #WFC3 data only
+    #   w, y, e = w[10], y[10], e[10]           #spitzer ch1
+    #   w, y, e = w[11], y[11], e[11]           #spitzer ch2
 
-	#get stellar spectrum
-        g = Gaussian1DKernel(stddev=150)
-        star = np.genfromtxt("W103-6110K-1.22Ms-1.22Rs.dat")       #W/m2/micron (column 1)
-	star_bb = np.interp(w, star[:,0], convolve(star[:,1]*22423.,g))
+    #get stellar spectrum
+    g = Gaussian1DKernel(stddev=150)
+    star = np.genfromtxt("W103-6110K-1.22Ms-1.22Rs.dat")       #W/m2/micron (column 1)
+    star_bb = np.interp(w, star[:,0], convolve(star[:,1]*22423.,g))
+    #star = np.genfromtxt("wasp103_sed_fluxes.out")
+    #star_bb = np.interp(w, star[:,0], star[:,1])*1.e24/(w*np.pi*4.)
+    chis = []
 
-        chis = []
+    for T in Ts:
+        #model = blackbody(w*1.0e-6, T)/star_bb*rprs**2
+        model = (np.pi/1.e6)*blackbody(w*1.0e-6, T)/star_bb*rprs**2
+        chi2 = np.sum((y - model)**2/e**2)
+        chis.append(chi2)
+        if chi2 < chibest: chibest, Tbest, resid = chi2, T, (y - model)/e
 
-	for T in Ts:
[…]

### 2018-02-01 Figures/temp.py

@@ -1,0 +1,276 @@
+import pickle
+import numpy as np
+import matplotlib.pyplot as plt
+import os, glob
+from lc_fit import Model, LightCurveData
+#import read_spectra_from_Vivien as rs
+import matplotlib.gridspec as gridspec
+from pylab import *
+from matplotlib import rc, ticker
+import seaborn as sns
+from astropy.convolution import Gaussian1DKernel, convolve
+
+sns.set_context("notebook", font_scale = 1.5)
+sns.set_style("white")
+sns.set_style("ticks", {"xtick.direction":"in", "ytick.direction":"in"})
+
+rc('font',**{'family':'sans-serif','sans-serif':['Arial']})
+
+def blackbody(l,T): 
+	h = 6.62607e-34   #J/s
+        c = 2.997925e8       #m/s
+        k = 1.38065e-23     #J/K
+        return 2*h*c**2/(l**5*(np.exp(h*c/(l*k*T))-1))                 #[W/sr/m^3]
+
+def best_fit_bb(w, y, e, rprs):
+    Ts = np.linspace(1000, 3600, 10000)
+    chibest = 10000.
+    Tbest = 0.  
+    Tstar = 6110.
+    resid = 0.
+
+    w = np.array(w)
+
+    w, y, e = w[0:10], y[0:10], e[0:10]     #WFC3 data only
+    #   w, y, e = w[10], y[10], e[10]           #spitzer ch1
+    #   w, y, e = w[11], y[11], e[11]           #spitzer ch2
+
+    #get stellar spectrum
+    star = np.genfromtxt("wasp103_sed_fluxes.out")
+    star_bb = np.interp(w, star[:,0], star[:,1])*1.e24/(w*np.pi*4.)
+    chis = []
+
+    for T in Ts:
+        model = blackbody(w*1.0e-6, T)/star_bb*rprs**2
+        chi2 = np.sum((y - model)**2/e**2)
+        chis.append(chi2)
+        if chi2 < chibest: chibest, Tbest, resid = chi2, T, (y - model)/e
+
+    waves_hires = np.linspace(1.0, 5.0, 100)
+    star_bb_hires = np.interp(waves_hires, star[:,0], star[:,1])*1.e24/(waves_hires*np.pi*4.)
+
[…]

### 2018-02-03 ms.tex
made tb consistent with vivien's assumptions

@@
 A blackbody is the simplest model for the planet's thermal emission and provides a useful first evaluation of the atmospheric properties.
+To calculate the best fit blackbody model, we assumed a planet-to-star radius ratio of 0.1063 and used a NEXTGEN (FIXME) stellar spectrum with effective temperature 6110 K.
 The best-fit blackbodies are shown in Figures \ref{fig:spectra} and \ref{fig:dayside}.
@@
 We also fit blackbody models to the WFC3 data only, and found that they provide a good fit at all orbital phases.
-The $\chi^2_\nu$ values range from 0.5 to 1.6, with a median of 0.9.
-The best fit brightness temperatures range from 1920 Kelvin on the nightside to 2980 Kelvin on the dayside.
+The $\chi^2_\nu$ values range from 0.5 to 2.4, with a median of 0.9.
+The best fit brightness temperatures range from $1917 \pm 43$ Kelvin on the nightside to $3011 \pm 8$ Kelvin on the dayside.
 We report the best fit temperatures with uncertainties in Table\,\ref{table:teffs}.
@@
 	\tablehead{
-	\colhead{Orbital Phase} & \colhead{$T_\mathrm{b}$\tablenotemark{1} (K)} & \colhead{$\chi^2_\nu$}}
+	\colhead{Orbital Phase} & \colhead{$T_\mathrm{b}$\tablenotemark{1}} & \colhead{$\chi^2_\nu$}}
 		\startdata
-		0.06 - 0.15 & 1919 \pm 40 & 0.6 \\
-		0.15 - 0.25 & 2256 \pm 24 & 0.8 \\
-		0.25 - 0.35 & 2651 \pm 17 & 1.2 \\
-		0.35 - 0.44 & 2906 \pm 11 & 0.8 \\
-		0.44 - 0.56 & 3013 \pm 8 & 1.6 \\
-		0.56 - 0.65 & 2885 \pm 12 & 1.3 \\
-		0.65 - 0.75 & 2636 \pm 16 & 0.9 \\
-		0.75 - 0.85 & 2313 \pm 23 & 1.1 \\
-		0.85 - 0.94 & 2027 \pm 36 & 0.5 \\
+		0.06 - 0.15 & 1917 \pm 43 & 0.7 \\
+		0.15 - 0.25 & 2254 \pm 25 & 0.8 \\
+		0.25 - 0.35 & 2650 \pm 17 & 1.4 \\
+		0.35 - 0.44 & 2905 \pm 11 & 1.1 \\
+		0.44 - 0.56 & 3011 \pm 8 & 2.4 \\
+		0.56 - 0.65 & 2884 \pm 11 & 1.7 \\
+		0.65 - 0.75 & 2634 \pm 16 & 1.1 \\
+		0.75 - 0.85 & 2312 \pm 23 & 1.2 \\
+		0.85 - 0.94 & 2025 \pm 34 & 0.5 \\
 		\enddata
+		\vspace{-0.8cm}
 		\tablenotetext{1}{Brightness temperatures were fit using the WFC3 data only.}

### 2018-02-03 Figures/phased_espec.py

@@ -226,7 +226,7 @@ for i in range(1, k):
 		outfile.close()
 
 
-		rprs = 0.1127
+		rprs = 0.1093
 		#print "phase", phase
 		wave_hires, model_hires = best_fit_bb(waves, (spectra[:,i-1,0]-1.)*(1+np.array(dilution)), spectra[:,i-1,1], rprs)
 		model_hires *= 1.e3

### 2018-02-03 Figures/teffs_table.py

@@ -5,10 +5,10 @@ teffs = np.genfromtxt("teffs.txt")
 
 print "\\begin{deluxetable}{LLL}"
 print "\\tablecolumns{3}"
-print "\\tablewidth{0pt}:"
-print "\\tablecaption{Phase-resolved Effective Temperature \label{table:teffs}}"
+print "\\tablewidth{0pt}"
+print "\\tablecaption{Phase-resolved Brightness Temperature \label{table:teffs}}"
 print "\\tablehead{"
-print "\colhead{Orbital Phase} & \colhead{$T_\mathrm{eff}$} & \colhead{$\chi^2_\\nu$}}"
+print "\colhead{Orbital Phase} & \colhead{$T_\mathrm{b}$} & \colhead{$\chi^2_\\nu$}}"
 print "\startdata"
 
 T = teffs[:,0]

### 2018-02-03 Figures/two_panel_dayside_espec.py

@@ -65,7 +65,7 @@ def best_fit_bb(w, y, e, rprs):
         plt.axhline(chibest+1)
         plt.show()"""
         onesigma = Tbest - Ts[idx]
-	print "Best fit blackbody temp, chi2: ", Tbest,  "+/-", onesigma, chibest/(len(y) - 1.)
+	print "Best fit blackbody temp, chi2: ", Tbest,  "+/-", onesigma, chibest/(len(y) - 1.), outliers
 	return waves_hires, np.pi/1.e6*blackbody(waves_hires*1.0e-6, Tbest)/star_bb_hires*rprs**2
 
 
@@ -98,7 +98,7 @@ GCM = np.genfromtxt("Vivien_models2/SpectralPC-Phi-TiO-NoClouds-Drag3-NEW-OPA-NE
 plt.plot(GCM[:,0], GCM[:,5]*1e3, color = '#380282', label = "$\\tau_\mathrm{drag3}$ GCM", linestyle = 'dotted')
 
 #get best fit blackbody
-rprs = 0.1127
+rprs = 0.1093
 wave_bb, bb = best_fit_bb(data_wl, data, data_err, rprs)
 plt.plot(wave_bb, bb*1e3, linestyle = 'dashed', color = '.5', zorder = -10, label = "blackbody planet")
 

### 2018-02-06 ms.tex
using same stellar spectrum as vivien

@@
 The spectrum is biased by flux contamination from the planet's nightside; to correct for nightside emission, we estimate the planet-to-star flux ratio and subtract it from the transit depth.
-We calculate planet-to-star flux assuming a FIXME PHOENIX model for the star, a blackbody for the planet, and a planet-to-star radius ratio of FIXME.
+We calculate planet-to-star flux assuming a NextGen spectrum for the star (interpolated to $T_\mathrm{eff} = 6110$ K), a blackbody for the planet, and a planet-to-star radius ratio of 0.1063.
 We consider two plausible nightside temperatures (1400 and 2000 K), which encompass the range of mean nightside temperatures calculated from the phase variation models (Table\,\ref{tab:FIXME}).
@@
 The gray points correspond to no correction for the nightside flux.
-The blue and red points assume the average nightside photospheric temperature is 1400 and 2000 K, respectively.
+The blue and red points are the corrected for an average nightside photospheric temperature is 1400 and 2000 K, respectively.
 The atmospheric scale height assumes FIXME.}
@@
 A blackbody is the simplest model for the planet's thermal emission and provides a useful first evaluation of the atmospheric properties.
-To calculate the best fit blackbody model, we assumed a planet-to-star radius ratio of 0.1063 and used a NEXTGEN (FIXME) stellar spectrum with effective temperature 6110 K.
+To calculate the best fit blackbody model, we assumed a planet-to-star radius ratio of 0.1063 and used a NextGen stellar spectrum interpolated to an effective temperature of 6110 K \citep{allard12}.
 The best-fit blackbodies are shown in Figures \ref{fig:spectra} and \ref{fig:dayside}.
@@
 
-\begin{deluxetable}{LLL}
-	\tablecolumns{3}
+\begin{deluxetable}{LLLLL}
+	\tablecolumns{5}
 	\tablewidth{0pt}
-	\tablecaption{Phase-resolved Brightness Temperature \label{table:teffs}}
+	\tablecaption{Phase-resolved Brightness Temperatures \label{table:teffs}}
 	\tablehead{
-	\colhead{Orbital Phase} & \colhead{$T_\mathrm{b}$\tablenotemark{1}} & \colhead{$\chi^2_\nu$}}
+		\colhead{Orbital Phase} & \colhead{$T_\mathrm{b}$} & \colhead{$T_\mathrm{b}$} & \colhead{$T_\mathrm{b}$} & \colhead{$\chi^2_\nu$}\tablenotemark{1} \\
+	\colhead{\,} & \colhead{WFC3} & \colhead{Ch. 1} & \colhead{Ch. 2} & \colhead{(9 dof)}}
 		\startdata
-		0.06 - 0.15 & 1917 \pm 43 & 0.7 \\
-		0.15 - 0.25 & 2254 \pm 25 & 0.8 \\
-		0.25 - 0.35 & 2650 \pm 17 & 1.4 \\
-		0.35 - 0.44 & 2905 \pm 11 & 1.1 \\
-		0.44 - 0.56 & 3011 \pm 8 & 2.4 \\
-		0.56 - 0.65 & 2884 \pm 11 & 1.7 \\
-		0.65 - 0.75 & 2634 \pm 16 & 1.1 \\
-		0.75 - 0.85 & 2312 \pm 23 & 1.2 \\
-		0.85 - 0.94 & 2025 \pm 34 & 0.5 \\
+		0.06 - 0.15 & 1917 \pm 43 & 1674 \pm 177 & 1677 \pm 102 & 0.7 \\
+		0.15 - 0.25 & 2254 \pm 25 & 2821 \pm 136 & 2486 \pm 87 & 0.8 \\
+		0.25 - 0.35 & 2650 \pm 17 & 3170 \pm 128 & 2772 \pm 74 & 1.4 \\
+		0.35 - 0.44 & 2905 \pm 11 & 3016 \pm 128 & 3216 \pm 68 & 1.1 \\
+		0.44 - 0.56 & 3011 \pm 8 & 3158 \pm 153 & 3350 \pm 53 & 2.4 \\
+		0.56 - 0.65 & 2884 \pm 11 & 2764 \pm 133 & 3051 \pm 70 & 1.7 \\
+		0.65 - 0.75 & 2634 \pm 16 & 2857 \pm 135 & 2550 \pm 85 & 1.1 \\
+		0.75 - 0.85 & 2312 \pm 23 & 2153 \pm 151 & 2117 \pm 91 & 1.2 \\
+		0.85 - 0.94 & 2025 \pm 34 & 1825 \pm 167 & 1414 \pm 113 & 0.5 \\
 		\enddata
-		\vspace{-0.8cm}
-		\tablenotetext{1}{Brightness temperatures were fit using the WFC3 data only.}
+		\tablenotetext{1}{$\chi^2_\nu$ values are for the fits to the WFC3 data only.}
 	\end{deluxetable}

### 2018-02-06 Figures/dayside_espec_no_1D.py

@@ -1,0 +1,159 @@
+import numpy as np
+import pickle
+import matplotlib.pyplot as plt
+import os, glob
+from lc_fit import Model, LightCurveData
+#import read_spectra_from_Vivien as rs
+import matplotlib.gridspec as gridspec
+from pylab import *
+from matplotlib import rc
+import spiderman_lc
+from matplotlib import ticker
+import seaborn as sns
+from astropy.convolution import Gaussian1DKernel, convolve
+
+sns.set_context("paper", font_scale=1.2)
+sns.set_style("white")
+sns.set_style("ticks", {"xtick.direction":"in", "ytick.direction":"in"})
+
+
+rc('font',**{'family':'sans-serif','sans-serif':['Arial']})
+
+def blackbody(l,T): 
+	h = 6.62607e-34   #J/s
+        c = 2.997925e8       #m/s
+        k = 1.38065e-23     #J/K
+        return 2*h*c**2/(l**5*(np.exp(h*c/(l*k*T))-1))                 #[W/sr/m^3]
+
+def best_fit_bb(w, y, e, rprs):
+	Ts = np.linspace(2900., 3500, 10000)
+	chibest = 10000.
+	Tbest = 0.	
+	Tstar = 6110.
+	w = np.array(w)
+
+	w, y, e, = w[0:10], y[0:10], e[0:10]
+	#w, y, e, = w[10], y[10], e[10]              #spitzer Ch 1
+	#w, y, e, = w[11], y[11], e[11]              #Spitzer Ch 2
+
+	#get stellar spectrum
+	#star = np.genfromtxt("wasp103_sed_fluxes.out")
+	#star_bb = np.interp(w, star[:,0], star[:,1])*1.e24/(w*np.pi*4.)
+
+        g = Gaussian1DKernel(stddev=150)
+        star = np.genfromtxt("W103-6110K-1.22Ms-1.22Rs.dat")       #W/m2/micron (column 1)
+	star_bb = np.interp(w, star[:,0], convolve(star[:,1]*22423.,g))
+
+	outliers = 0.
+        chis = []
+
+	for T in Ts:
+		model = (np.pi/1.e6)*blackbody(w*1.0e-6, T)/star_bb*rprs**2
+		chi2 = np.sum((y - model)**2/e**2)
+                chis.append(chi2)
[…]

### 2018-02-06 Figures/gcm_comparison.py

@@ -162,7 +162,6 @@ plt.xlabel("Phase")
 plt.gca().text(0.05, 4.5, 'Spitzer\nCh 2', fontsize=10)
 
 
-
 #plot spitzer best fits and data
 
 dilution = np.array([0.1712, 0.1587])

### 2018-02-06 Figures/gcm_comparison_spherical_harmonics.py

@@ -1,0 +1,212 @@
+import matplotlib.pyplot as plt
+import numpy as np
+import os, glob
+from lc_fit import Model, LightCurveData
+import pickle
+import seaborn as sns
+from scipy.interpolate import interp1d
+
+sns.set_context("paper")
+sns.set_style("white")
+sns.set_style("ticks", {"xtick.direction":"in", "ytick.direction":"in"})
+
+gcm_path = "./Vivien_models2"
+gcms = glob.glob(os.path.join(gcm_path, "PC*PT.dat"))
+
+labels = ["$\\tau_\mathrm{drag} = 10^4$ s", "$\\tau_\mathrm{drag} = 10^3$ s", "[Fe/H] = 0.5", "nominal GCM"]
+colors = ["#be0119", "#f97306", "#6dedfd", "#0165fc"]
+ls = [":", "--", "-.", "-"]
+
+plt.figure(figsize = (4, 6))
+
+
+
+def proj_area(phi, inc):
+        R0 = 1.07e8             #planet radius in m
+        p = 0.00117             # planet-to-star mass ratio
+        r = 2.9695e9            #orbital separation in m
+        kn = 0.653              #from table B5 of Leconte et al. 2011
+        n = 1.005
+        qn = kn*(1.- n/5.)      #n 
+
+
+        alpha1 = 2.5*qn*R0**3/(p*r**3)
+        alpha2 = -1.25*qn*R0**3/(p*r**3)
+        alpha3 = alpha2
+
+        a1 = R0*(1+alpha1)
+        a2 = R0*(1+alpha2)
+        a3 = R0*(1+alpha3)
+
+        return  np.sqrt(a3**2*np.sin(inc)**2*(a1**2*np.sin(phi)**2+a2**2*np.cos(phi)**2)+ a1**2*a2**2*np.cos(inc)**2)/(a2*a3)
+
+
+plt.subplot(311)
+inc = 1.523
+
+#plot gcms
+for i, g in enumerate(gcms):
+    print g,
+    model = np.genfromtxt(g, delimiter = ',') 
+    phi = model[:,0]/360.*2.*np.pi
+    area = proj_area(phi, inc)
+    plt.plot(model[:,0]/360. +0.5, model[:,5]*1e3*area, color = colors[i], linestyle = ls[i])
[…]

### 2018-02-06 Figures/get_amps_offs_allmodels.py

@@ -1,0 +1,16 @@
+import pickle
+import numpy as np
+import matplotlib.pyplot as plt
+import os, glob
+from lc_fit import Model, LightCurveData
+import matplotlib.gridspec as gridspec
+from pylab import *
+from astropy.convolution import Gaussian1DKernel, convolve
+
+path  = "WFC3_best_fits/"
+files = glob.glob(os.path.join(path, "bestfit*.pic"))		
+for f in files:
+	p = pickle.load(open(f, 'rb'))
+	d, m = p[0], p[1]			
+        ind = m.bestfit == np.max(m.bestfit)
+        print m.phase[ind]

### 2018-02-06 Figures/test_significance_of_features.py

@@ -1,6 +1,6 @@
 import numpy as np
 
-wfc3 = np.genfromtxt("teffs_nodayside.txt")
+wfc3 = np.genfromtxt("teffs.txt")
 spt = np.genfromtxt("teffs_ch2.txt")
 
 

### 2018-02-07 ms.tex
correct rprs, NextGen spectrum

@@
 The advantage of fitting the transits separately from the full phase curves is that the resultant transit depths are not dependent on how the phase variation is modeled.
-We do not model the transit in the \Spitzer\,$3.6\mu$m channel, since it is challenging to robustly estimate the contribution of correlated noise in the subset of data we model here.
+%We do not model the transit in the \Spitzer\,$3.6\mu$m channel, since it is challenging to robustly estimate the contribution of correlated noise in the subset of data we model here.
 FIXME
@@
 We calculate planet-to-star flux assuming a NextGen spectrum for the star (interpolated to $T_\mathrm{eff} = 6110$ K), a blackbody for the planet, and a planet-to-star radius ratio of 0.1063.
-We consider two plausible nightside temperatures (1400 and 2000 K), which encompass the range of mean nightside temperatures calculated from the phase variation models (Table\,\ref{tab:FIXME}).
+We consider two plausible nightside temperatures (1400 and 2000 K), which encompass the range of mean nightside temperatures calculated from the phase variation models (Table\,\ref{tab:models}).
 We also show the uncorrected transit depths.
@@
 The blue and red points are the corrected for an average nightside photospheric temperature is 1400 and 2000 K, respectively.
-The atmospheric scale height assumes FIXME.}
+The atmospheric scale height is $5.5\times10^6$ m, assuming a mean molecular weight of 2.3 amu, surface gravity $g = 15.85 m/s^2$, and a temperature $T = 2410$ K.}
 \label{fig:tspec}

### 2018-02-07 Figures/phase_curves_spherical.py

@@ -20,9 +20,8 @@ plt.figure(figsize = (7.5,4.5))
 gs = gridspec.GridSpec(3, 2, hspace=0.1, wspace = 0.05)
 
 # plots HST white light phase curve
-#bestfits = ["/Users/lkreidberg/Desktop/Projects/Observations/HST/WASP103_HST_all/SPHERICAL_MCMC/bestfit_1.23.pic"]
-bestfits = ["./WFC3_best_fits/old_white_fits/bestfit_spherical.pic"]
-#mcmcs =  ["/Users/lkreidberg/Desktop/Projects/Observations/HST/WASP103_HST_all/SPHERICAL_MCMC/flatchain1_2017_10_27_22:36:091.225.npy"]
+#bestfits = ["./WFC3_best_fits/old_white_fits/bestfit_spherical.pic"]
+bestfits = ["./WFC3_best_fits/bestfit_spherical.pic"]
 
 phasebins = np.linspace(0., 1., 30)
 nbins = len(phasebins) - 1
@@ -64,34 +63,7 @@ for ii, f in enumerate(bestfits):
 			bin_average[j-1] = (phasebins[j-1]+phasebins[j])/2.
 
 	plt.errorbar(bin_average, (bindata-1.)*1e3*dilution, yerr = binsigma*1e3, fmt = '.k')
-	#plt.plot(phase, (bestfit-1.)*1e3*dilution, color = 'k', label = 'best fit', zorder=20, linewidth = 1.0)
 	plt.plot(phase, (bestfit-1.)*1e3*dilution, color = 'b', label = 'best fit', zorder=-1, alpha = 0.8, linewidth = 2.0)
-
-	##### plot mcmc
-	"""mcmc = np.load(mcmcs[ii])
-	mcmc = mcmc[::every_N]
-	rp, sph0, sph1, sph2, sph3 = mcmc[:,0], np.median(mcmc[:, 16]), 0., np.median(mcmc[:, 17]), np.median(mcmc[:, 18])
-	sph = [sph0, sph1, sph2, sph3]
-
-	
-	l1, l2 = d.l1, d.l2
-	stellar_grid = spiderman.stellar_grid.gen_grid(l1,l2,logg=4.5)
-
-	per =  0.925545613
-	t0 = 2457080.64041702 
-	t = np.linspace(t0, t0+ per, 1000)
-	models = np.zeros((len(t), mcmc.shape[0]))
-	for i in range(len(mcmc)): 
[…]

### 2018-02-07 Figures/transmission_spectrum.py

@@ -47,8 +47,16 @@ for i, Tp in enumerate(temps):
 	sp_dilution = 0.16
 	nightside_bin = np.interp(4.5*1e4, bb_planet.wave, nightside) 
 	if Tp == 0: nightside_bin = 0
-	#plt.errorbar(4.5, sp*(1+sp_dilution), sp_err, fmt = '.r')
 	plt.errorbar(4.5, sp*(1+sp_dilution) - nightside_bin, yerr = sp_err, xerr = 0.5, linestyle = 'none', color = colors[i], marker = '.', alpha = 0.7)
+
+	# Spitzer Ch 1
+	sp, sp_err = 0.10944, 0.0015
+	sp_err = sp*sp_err*2.
+	sp = sp**2
+	sp_dilution = 0.17
+	nightside_bin = np.interp(3.6*1e4, bb_planet.wave, nightside) 
+	if Tp == 0: nightside_bin = 0
+	plt.errorbar(3.6, sp*(1+sp_dilution) - nightside_bin, yerr = sp_err, xerr = 0.5, linestyle = 'none', color = colors[i], marker = '.', alpha = 0.7)
 
 plt.gca().set_xscale('log')
 
@@ -63,7 +71,7 @@ plt.legend(loc = 'upper left')
 plt.xlabel("Wavelength (microns)")
 plt.ylabel("Transit Depth")
 plt.axhline(mean, linestyle = 'dotted', zorder = -10)
-ymin, ymax= 0.0128, 0.0147
+ymin, ymax= 0.0126, 0.0147
 plt.ylim(ymin, ymax)
 
 #scale height
@@ -73,7 +81,7 @@ plt.ylim(ymin, ymax)
 
 x2 = plt.gca().twinx()
 scaleheight = 1.2e-4 
-plt.plot(d[:,0], np.linspace(0, ymax - ymin, len(d[:,0]))/scaleheight, linewidth=0.)
+plt.plot(d[:,0], np.linspace(0, ymax - ymin, len(d[:,0]))/scaleheight - (mean-ymin)/scaleheight, linewidth=0.)
 plt.ylabel("scale heights")
 
 plt.tight_layout()

### 2018-02-08 ms.tex
table

@@
 	\startdata
-		WFC3 & Sph. Harmonics & 1214 & 3251 & 1820 & 2622 & 0.0 & 0.0 \\
-		\, & Kinematic & 1980 & 3958 & 1980 & 2777 & 14.0 & 14.0 \\
-		\, & Two Temp. & 0 & 2887 & 0 & 2887 & 49.8 & 45.4 \\
-		\, & Sinusoid & -- & -- & -- & -- & 19.8 & 15.4 \\
-		Ch 1 & Sph. Harmonics & 1280 & 3444 & 1936 & 2786 & 49.0 & 0.0 \\
-		\, & Kinematic & 1955 & 3675 & 1999 & 2656 & 83.3 & 34.3 \\
-		\, & Two Temp. & 1429 & 3041 & 1429 & 3025 & 59.7 & 17.6 \\
-		\, & Sinusoid & -- & -- & -- & -- & 0.0 & 76.6 \\
-		Ch 2 & Sph. Harmonics & 902 & 3786 & 1753 & 2920 & 7.9 & 2.3 \\
-		\, & Kinematic & 1703 & 4276 & 1711 & 2740 & 20.8 & 15.2 \\
-		\, & Two Temp. & 1361 & 3311 & 1361 & 3292 & 12.5 & 0.0 \\
+	WFC3 & Sph. Harmonics & 1227 & 3237 & 1822 & 2636 & 0.0 & 0.0 \\
+	\, & Kinematic & 1977 & 3953 & 1977 & 2769 & 14.1 & 14.1 \\
+	\, & Two Temp. & 0 & 2879 & 0 & 2879 & 46.3 & 41.9 \\
+	\, & Sinusoid & -- & -- & -- & -- & 21.0 & 16.5 \\
+	Ch 1 & Sph. Harmonics & 1269 & 3391 & 1912 & 2741 & 0.0 & 49.0 \\
+	\, & Kinematic & 1932 & 3630 & 1975 & 2614 & 34.2 & 83.4 \\
+	\, & Two Temp. & 1418 & 2990 & 1418 & 2990 & 17.6 & 59.7 \\
+	\, & Sinusoid & -- & -- & -- & -- & 76.6 & 0.0 \\
+	Ch 2 & Sph. Harmonics & 888 & 3714 & 1729 & 2864 & 7.9 & 2.3 \\
+	\, & Kinematic & 1614 & 3931 & 1621 & 2544 & 20.8 & 15.2 \\
+	\, & Two Temp. & 1344 & 3241 & 1344 & 3241 & 12.5 & 0.0 \\
 	\, & Sinusoid & -- & -- & -- & -- & 0.0 & 22.3 \\
@@
 \caption{The transmission spectrum of WASP-103b (points) for a range of assumptions about the planet's nightside temperature.
-The gray points correspond to no correction for the nightside flux.
-The blue and red points are the corrected for an average nightside photospheric temperature is 1400 and 2000 K, respectively.
-The atmospheric scale height is $5.5\times10^6$ m, assuming a mean molecular weight of 2.3 amu, surface gravity $g = 15.85 m/s^2$, and a temperature $T = 2410$ K.}
+The gray points are not corrected for planet nightside flux, whereas the blue and red points are corrected for an average nightside photospheric temperature of 1400 and 2000 K, respectively.
+The dotted line corresponds to the mean transit depth (assuming $T_\mathrm{night} = 2000$ K).
+Atmospheric scale height $H$ is shown on the right y-axis, where $H = 5.5\times10^6$ m (assuming a mean molecular weight of 2.3 atomic mass units, surface gravity $g = 15.85$ m/s$^2$, and a temperature $T = 2410$ K).}
 \label{fig:tspec}

### 2018-02-08 Figures/fit_table.py

@@ -6,8 +6,8 @@ import pickle
 
 #zhang, hotspot, spherical, sincos
 ch1_chi2 = np.array([0.9, 0.9, 0.9, 0.9])
-ch1_aic = np.array([7131.0, 7107.4, 7096.7, 7047.7])
-ch1_bic = np.array([7075.2, 7058.5, 7040.9, 7117.5])
+ch1_aic = np.array([7075.1, 7058.5, 7040.9, 7117.5])
+ch1_bic = np.array([7131.1, 7107.4, 7096.7, 7047.7])
 
 ch2_chi2 = np.array([1.1, 1.1, 1.1, 1.1])
 ch2_aic = np.array([8666.2, 8657.9, 8653.3, 8645.4])
@@ -46,30 +46,25 @@ wfc3_daymu = np.array([2769, 2879, 2636, 0])
 wfc3_nightmu = np.array([1977, 0, 1822, 0])
 
 #Spitzer Ch 2
-#model, Tmin, Tmax =  zhang 1703.0 4276.80767467
-#model, Tmin, Tmax =  hotspot_t 1361.0 3311.0
-#model, Tmin, Tmax =  spherical 902.401726015 3786.1376002
-ch2_tmin = np.array([1703, 1361, 902, 0])
-ch2_tmax = np.array([4276, 3311, 3786, 0])
 #from spitzer_maptemp.py
-#zhang daymu, nightmu, min, max 2740.48761346 1711.12738853 1703.0 4287.03108111
-#hotspot_t daymu, nightmu, min, max 3291.5 1361.0 1361.0 3311.0
-#spherical daymu, nightmu, min, max 2919.98921277 1752.56989088 895.304735881 3786.3843194
-ch2_daymu = np.array([2740, 3292, 2920, 0])
-ch2_nightmu = np.array([1711, 1361, 1753, 0])
+#zhang daymu, nightmu, min, max 2544.42433961 1621.25879891 1614.0 3931.36778946
+#hotspot_t daymu, nightmu, min, max 3222.03 1344.0 1344.0 3241.0
+#spherical daymu, nightmu, min, max 2864.26860292 1728.83922558 888.59900134 3713.55482549
+ch2_daymu = np.array([2544, 3241, 2864, 0])
+ch2_nightmu = np.array([1621, 1344, 1729, 0])
+ch2_tmin = np.array([1614, 1344, 888, 0])
+ch2_tmax = np.array([3931, 3241, 3714, 0])
 
 #Spitzer Ch 1
[…]

### 2018-02-08 ms.tex
get rid of aic

@@
 \includegraphics[width = 1.0\textwidth]{Figures/emission_spectra.pdf}
-\caption{Phase-resolved planet-to-star flux ratios (points) compared to the best fit blackbody (blue line) and the GCM with $\tau_\mathrm{drag3}$.
+\caption{Phase-resolved planet-to-star flux ratios (points) compared to the best fit blackbody (blue line) and the GCM with $\tau_\mathrm{drag4}$.
 Phases $\phi=0.5$ and $0.0$ correspond to times of secondary eclipse and transit, when the substellar and antistellar points are respectively aimed at Earth.
@@
 \caption{\textbf{Left:} Fits to the broadband WFC3 phase curve compared to a GCM.
-The colored lines correspond to different temperature maps fit to the data, and the dashed gray line is from the $\tau_\mathrm{drag3}$ GCM.
+The colored lines correspond to different temperature maps fit to the data, and the dashed gray line is from the $\tau_\mathrm{drag4}$ GCM.
 We also show the measured planet-to-star flux for each map (points), which is model-dependent due to slight degeneracies with the instrument systematic model.
@@
 
-\begin{deluxetable}{llllllll}
-	\tablecolumns{8}
+\begin{deluxetable}{lllllll}
+	\tablecolumns{7}
 	\tablewidth{0pt}
@@
 	\tablehead{
-	\colhead{Data} & \colhead{Model} & \colhead{$T_\mathrm{min}$} & \colhead{$T_\mathrm{max}$} & \colhead{$\overline{T}_\mathrm{night}$} & \colhead{$\overline{T}_\mathrm{day}$} &\colhead{$\Delta_\mathrm{AIC}$} & \colhead{$\Delta_\mathrm{BIC}$}}
+	\colhead{Data} & \colhead{Model} & \colhead{$T_\mathrm{min}$} & \colhead{$T_\mathrm{max}$} & \colhead{$\overline{T}_\mathrm{night}$} & \colhead{$\overline{T}_\mathrm{day}$} & \colhead{$\Delta_\mathrm{BIC}$}}
 		\startdata
-	WFC3 & Sph. Harmonics & 1227 & 3237 & 1822 & 2636 & 0.0 & 0.0 \\
-	\, & Kinematic & 1977 & 3953 & 1977 & 2769 & 14.1 & 14.1 \\
-	\, & Two Temp. & 0 & 2879 & 0 & 2879 & 46.3 & 41.9 \\
-	\, & Sinusoid & -- & -- & -- & -- & 21.0 & 16.5 \\
-	Ch 1 & Sph. Harmonics & 1269 & 3391 & 1912 & 2741 & 0.0 & 49.0 \\
-	\, & Kinematic & 1932 & 3630 & 1975 & 2614 & 34.2 & 83.4 \\
-	\, & Two Temp. & 1418 & 2990 & 1418 & 2990 & 17.6 & 59.7 \\
-	\, & Sinusoid & -- & -- & -- & -- & 76.6 & 0.0 \\
-	Ch 2 & Sph. Harmonics & 888 & 3714 & 1729 & 2864 & 7.9 & 2.3 \\
-	\, & Kinematic & 1614 & 3931 & 1621 & 2544 & 20.8 & 15.2 \\
-	\, & Two Temp. & 1344 & 3241 & 1344 & 3241 & 12.5 & 0.0 \\
-	\, & Sinusoid & -- & -- & -- & -- & 0.0 & 22.3 \\
+		WFC3 & Sph. Harmonics & 1227 & 3237 & 1822 & 2636 & 0.0 \\
+		\, & Kinematic & 1977 & 3953 & 1977 & 2769 & 14.1 \\
+		\, & Two Temp. & 0 & 2879 & 0 & 2879 & 41.9 \\
+		\, & Sinusoid & -- & -- & -- & -- & 16.5 \\
+		Ch 1 & Sph. Harmonics & 1269 & 3391 & 1912 & 2741 & 0.0 \\
+		\, & Kinematic & 1932 & 3630 & 1975 & 2614 & 34.4 \\
+		\, & Two Temp. & 1418 & 2990 & 1418 & 2990 & 10.7 \\
+		\, & Sinusoid & -- & -- & -- & -- & 24.7 \\
+		Ch 2 & Sph. Harmonics & 888 & 3714 & 1729 & 2864 & 2.3 \\
+		\, & Kinematic & 1614 & 3931 & 1621 & 2544 & 15.2 \\
+		\, & Two Temp. & 1344 & 3241 & 1344 & 3241 & 0.0 \\
+		\, & Sinusoid & -- & -- & -- & -- & 22.3 \\
 		\enddata
@@
 We fit the data with a transit model, which has free parameters for the planet-to-star radius and a linear limb darkening parameter.
-We fit for the instrument systematics using the same parameters as the phase curve fits, except that we modeled the visit-long systematic as a linear trend in time (which is sufficient for the shorter duration).
+The orbital parameters (inclination, $a/R_s$, period, and time of central transit) were fixed at previously published values listed in \S\,\ref{sec:fits}.
+We fit for the instrument systematics using the same model as for the phase curve fits, except that we modeled the visit-long systematic as a linear trend in time (which is sufficient for the shorter duration).
 The advantage of fitting the transits separately from the full phase curves is that the resultant transit depths are not dependent on how the phase variation is modeled.
-%We do not model the transit in the \Spitzer\,$3.6\mu$m channel, since it is challenging to robustly estimate the contribution of correlated noise in the subset of data we model here.
-FIXME
 
-We show the measured transmission spectrum in Figure,\ref{fig:tspec}.
+We show the measured transmission spectrum in Figure\,\ref{fig:tspec}.
 The spectrum is biased by flux contamination from the planet's nightside; to correct for nightside emission, we estimate the planet-to-star flux ratio and subtract it from the transit depth.
-We calculate planet-to-star flux assuming a NextGen spectrum for the star (interpolated to $T_\mathrm{eff} = 6110$ K), a blackbody for the planet, and a planet-to-star radius ratio of 0.1063.
-We consider two plausible nightside temperatures (1400 and 2000 K), which encompass the range of mean nightside temperatures calculated from the phase variation models (Table\,\ref{tab:models}).
+We calculate planet-to-star flux assuming a NextGen spectrum for the star (interpolated to $T_\mathrm{eff} = 6110$ K), a blackbody for the planet, and a planet-to-star radius ratio of 0.1146.
+We consider two plausible nightside temperatures (1500 and 2000 K), which encompass most of the mean nightside temperatures estimated from the phase variation models (Table\,\ref{table:models}).
 We also show the uncorrected transit depths.
-For the uncorrected data, there is an offset between the \HST\ and \Spitzer\ data of about 10 atmospheric scale heights, much larger than expected from theoretical models.
-FIXME show GCM in this figure.
-Water abundance?
+For the uncorrected data, there is an offset between the \HST\ and \Spitzer\ data of about 10 atmospheric scale heights.
+
+The spectrum is inconsistent with a flat line at $3.2\,\sigma$ confidence, and the slope is much larger than expected from theoretical models (FIXME show GCM).
+For nightside temperatures of 1500 and 2000 K, the spectrum is consistent with a flat line to within $1.3\,\sigma$.
+The mean transit depths are $1.3431 \pm 0.0029$,  $1.3360 \pm 0.0029$, and $1.3078 \pm 0.0029\%$ for assumed nightside temperatures of 0, 1500, and 2000 K.
+Of these, only the 2000 K model yields a transit depth consistent with the measurement of \cite{lendl17} at shorter wavelengths where nightside contamination is negligible ($1.3092 \pm 0.0114$\%).
+FIXME: could we see water at higher precision?
 
@@
 A blackbody is the simplest model for the planet's thermal emission and provides a useful first evaluation of the atmospheric properties.
-To calculate the best fit blackbody model, we assumed a planet-to-star radius ratio of 0.1063 and used a NextGen stellar spectrum interpolated to an effective temperature of 6110 K \citep{allard12}.
+To calculate the best fit blackbody model, we assumed a planet-to-star radius ratio of 0.1146 and used a NextGen stellar spectrum interpolated to an effective temperature of 6110 K \citep{allard12}.
 The best-fit blackbodies are shown in Figures \ref{fig:spectra} and \ref{fig:dayside}.
@@
 
-To check that fast drag timescales of order $10^3 - 10^4$\,s are physically realistic, we computed the free electron abundance due to ionized metals for the $\tau_\mathrm{drag3}$ GCM.
+To check that fast drag timescales of order $10^3 - 10^4$\,s are physically realistic, we computed the free electron abundance due to ionized metals for the $\tau_\mathrm{drag4}$ GCM.
 Using the order-of-magnitude expression from \cite{perna10} (Equation 12), we estimate a drag timescale at the substellar point of $\tau_\mathrm{drag}  = 2\times10^4/B^2$ s, where $B$ is the magnetic field in Gauss.
 We assume a temperature and pressure of 3359 K and 0.11 bar, and that the magnetic field is perpendicular to the flow.
-To reach a drag timescale of $10^3$\,s, a magnetic field stronger than 4 Gauss is required.
+To reach a drag timescale of $10^4$\,s, a magnetic field stronger than $\sim1$ Gauss is required.
 This value is comparable to Jupiter's magnetic field strength of 5-10 Gauss \citep{bagenal04}.
@@
 We also compared the GCM output to temperature maps retrieved with \texttt{spiderman}.
-Figure\,\ref{fig:model_comparison} shows the 0.01 bar temperature map for the $\tau_\mathrm{drag3}$ GCM compared to the best fit models.
+Figure\,\ref{fig:model_comparison} shows the 0.01 bar temperature map for the $\tau_\mathrm{drag4}$ GCM compared to the best fit models.
 At this pressure, the GCM has minimum and maximum temperatures of $580$ and $3520$ K.
@@
 As discussed in \S\,\ref{sec:composition}, water dissociation and H- opacity are needed to explain the dayside emission spectrum.
-Figure\,\ref{fig:gcmcomparison} shows the photospheric abundances of H$_2$O and H- compared to the predicted temperature for the $\tau_\mathrm{drag3}$ GCM.
+Figure\,\ref{fig:gcmcomparison} shows the photospheric abundances of H$_2$O and H- compared to the predicted temperature for the $\tau_\mathrm{drag4}$ GCM.
 The water abundance drops by $\sim10$ at the substellar point, and the H- opacity increases by $\sim100$.
@@
 	\includegraphics[width = 1.0\textwidth]{Figures/GCM_abundances.pdf}
-	\caption{Row (1): photospheric temperatures for the $\tau_\mathrm{drag3}$ GCM for different viewing geometries.
+	\caption{Row (1): photospheric temperatures for the $\tau_\mathrm{drag4}$ GCM for different viewing geometries.
 The orbital phase $\alpha=0$ corresponds to secondary eclipse (when the substellar point faces Earth) and $\alpha=180$ corresponds to transit (when the antistellar point faces Earth).

### 2018-02-08 Figures/fit_table.py

@@ -6,8 +6,9 @@ import pickle
 
 #zhang, hotspot, spherical, sincos
 ch1_chi2 = np.array([0.9, 0.9, 0.9, 0.9])
-ch1_aic = np.array([7075.1, 7058.5, 7040.9, 7117.5])
-ch1_bic = np.array([7131.1, 7107.4, 7096.7, 7047.7])
+ch1_aic = np.array([7075.1, 7058.5, 7040.9, 7044.7])
+ch1_bic = np.array([7131.1, 7107.4, 7096.7, 7121.4])
+
 
 ch2_chi2 = np.array([1.1, 1.1, 1.1, 1.1])
 ch2_aic = np.array([8666.2, 8657.9, 8653.3, 8645.4])

### 2018-02-08 ms.tex
edits

@@
 This package allows users to input a climate map (temperature or brightness as a function of latitude and longitude), and generate the corresponding flux ratio for an observation at time $t$.
-In our fit, we calculated the stellar flux with a PHOENIX model \citep{husser13} interpolated to an effective temperature of $6110\,\mathrm{K}$ \citep{gillon14}, solar metallicity, and log\,$g$ of 4.5 (in cgs units).
+In our fit, we calculated the stellar flux with a NextGen model \citep{allard12} interpolated to an effective temperature of $6110\,\mathrm{K}$ \citep{gillon14}, solar metallicity, and log\,$g$ of 4.2 (in cgs units).
 For the planet flux, we tested three different maps: a two-temperature map, with a uniform dayside temperature $T_d$ and a uniform nightside temperature $T_n$; a spherical harmonic maps of degree two (with four free parameters); and the physically-motivated kinematic model from \cite{zhang17}, which has just three free parameters (the nightside temperature $T_n$, the change in temperature from day-to-night side $\Delta_T$, and the ratio of radiative to advective timescales $\xi$).
@@
 At quadrature, the projected area is $8\%$ larger than at phase zero (mid-transit).
-Using the analytic expression from \cite{loeb03}, we estimated the effect of Doppler beaming and found that it contributes less than 10 ppm variability to the measured flux.
+Using the analytic expression from \cite{loeb03}, we estimated the effect of Doppler beaming and found that it contributes less than 10 ppm to the measured flux.
 
@@
 \label{sec:fitquality}
+%WFC3 white: obs, exp rms (ppm) 172.140941477 122.002526515
+%Ch1: rms obs, exp (ppm) 766.79959876 470.309808368
+%Ch2: rms obs, exp (ppm) 636.908048707 639.675550854
 We performed several tests of the quality of the light curve fits.
 First we predicted the level of scatter in the light curves based on photon noise alone, then compared this value to the root-mean-square (rms) of the fit residuals.
-The Spitzer 4.5 $\mu$m light curve rms is within 10\% of the expected photon noise limit (691 versus 640 ppm), whereas the 3.6 $\mu$m light curve has significantly larger rms (797 versus 470 ppm), due to time-correlated red noise (discussed below).
+For the spherical harmonics fit to the phase variation, the Spitzer 4.5 $\mu$m light curve rms reaches the expected photon noise limit (637 versus 640 ppm).
+The 3.6 $\mu$m light curve has significantly larger rms (767 versus 470 ppm), due to time-correlated red noise (discussed below).
 The expected photon-limited rms for the WFC3 spectrosopic light curves ranges from 430 - 530 ppm, and the measured rms was typically within 5\% of expectations for all spectroscopic channels.
-For the WFC3 band-integrated white light curve, the rms was slightly larger than predicted (175 versus 122 ppm).
+For the WFC3 band-integrated white light curve, the rms was slightly larger than predicted (172 versus 122 ppm).
 There are a number of possible origins for this discrepancy, including imperfect background subtraction, variation in the position of the spatial scan on the detector, loss of flux outside the extraction window, and imperfect modeling of the astrophysical signal or instrument systematics.
@@
 		\startdata
-		WFC3 & Sph. Harmonics & 1227 & 3237 & 1822 & 2636 & 0.0 \\
-		\, & Kinematic & 1977 & 3953 & 1977 & 2769 & 14.1 \\
-		\, & Two Temp. & 0 & 2879 & 0 & 2879 & 41.9 \\
-		\, & Sinusoid & -- & -- & -- & -- & 16.5 \\
-		Ch 1 & Sph. Harmonics & 1269 & 3391 & 1912 & 2741 & 0.0 \\
-		\, & Kinematic & 1932 & 3630 & 1975 & 2614 & 34.4 \\
-		\, & Two Temp. & 1418 & 2990 & 1418 & 2990 & 10.7 \\
-		\, & Sinusoid & -- & -- & -- & -- & 24.7 \\
-		Ch 2 & Sph. Harmonics & 888 & 3714 & 1729 & 2864 & 2.3 \\
-		\, & Kinematic & 1614 & 3931 & 1621 & 2544 & 15.2 \\
-		\, & Two Temp. & 1344 & 3241 & 1344 & 3241 & 0.0 \\
-		\, & Sinusoid & -- & -- & -- & -- & 22.3 \\
+		WFC3 & Sph. Harmonics & 1227 & 3237 & 1822 & 2636 & 0 \\
+		\, & Kinematic & 1977 & 3953 & 1977 & 2769 & 14 \\
+		\, & Two Temp. & 0 & 2879 & 0 & 2879 & 42 \\
+		\, & Sinusoid & -- & -- & -- & -- & 17 \\
+		Ch 1 & Sph. Harmonics & 1269 & 3391 & 1912 & 2741 & 0 \\
+		\, & Kinematic & 1932 & 3630 & 1975 & 2614 & 34 \\
+		\, & Two Temp. & 1418 & 2990 & 1418 & 2990 & 11 \\
+		\, & Sinusoid & -- & -- & -- & -- & 25 \\
+		Ch 2 & Sph. Harmonics & 888 & 3714 & 1729 & 2864 & 2 \\
+		\, & Kinematic & 1614 & 3931 & 1621 & 2544 & 15 \\
+		\, & Two Temp. & 1344 & 3241 & 1344 & 3241 & 0 \\
+		\, & Sinusoid & -- & -- & -- & -- & 22 \\
 		\enddata

### 2018-02-08 ms.tex
edits

@@
 This test confirms the presence of time-correlated noise in the Channel 1 light curve that can be seen by eye in the residuals in Figure\,\ref{fig:phasecurves}.
-Both \Spitzer\ channels use the same detector, but Channel 1 data are more susceptible to time-correlated noise because the the point spread function is further undersampled at shorter wavelengths, making intrapixel sensitivity variations more pronounced.
+Both \Spitzer\ channels use the same detector, but Channel 1 data are more susceptible to time-correlated noise because the the point spread function is more undersampled at shorter wavelengths, making intrapixel sensitivity variations more pronounced.
 
@@
 All of the models provide reasonable fits to the data, with $\chi^2_\nu$ near unity, but they yield significantly different temperature maps.
-Table\,\ref{table:model_comparison} lists the minimum and maximum temperatures for the best fit models to the WFC3 broadband and two Spitzer phase curves.
-We also list the  information criterion (BIC) and Aikike information criterion (AIC) values for the fits \citep[a $\Delta$BIC value greater than 10 constitutes strong evidence against a given model;][]{kass95}.
+Table\,\ref{table:models} lists the best fit minimum and maximum temperatures, as well as the mean day- and nightside temperatures.
+We also list the  information criterion (BIC) values for the fits \citep[a $\Delta$BIC value greater than 10 constitutes strong evidence against a given model;][]{kass95}.
 
-%The best fit model is either a sinusoid or spherical harmonics, depending on which criterion is used for model selection.
-The BIC generally favors the simpler spherical harmonics model because it penalizes model complexity relatively more than the AIC \citep{kass95}.
-The sinusoid has four free parameters (amplitude, phase offset, and eclipse midpoint and depth), whereas the spherical harmonics model has four (for degree two).
-The kinematic and two temperature models tend to perform significantly worse ($\Delta$BIC and $\Delta$AIC greater than 10).
-As illustrated in Figure\,\ref{fig:model_comparison}, the kinematic model is larger than the observed planet-to-star flux on the nightside, whereas the two temperature model overpredicts the flux at quadrature and underpredicts the dayside.
+%As illustrated in Figure\,\ref{fig:model_comparison}, the kinematic model is larger than the observed planet-to-star flux on the nightside, whereas the two temperature model overpredicts the flux at quadrature and underpredicts the dayside.
 
-We compared the planet's minimum and maximum temperature for the three climate maps by computing the temperatures over a $100\times100$ grid in latitude and longitude.
-The kinematic model has the hottest dayside temperature, and the two-temperature model has the smallest.
+The best fit model is generally the spherical harmonics map.
+It has a lower BIC value than all the other models for the broadband WFC3 and \Spitzer\,$3.6\,\mu$m phase curves.
+For the $4.5\,\mu$m phase curve, the two temperature map provides the best fit, but it only lowers the BIC value by 2 relative to the spherical harmonics map, which is not a statistically significant improvement \citep{kass95}.
+The spherical harmonics model yields a mean dayside temperature near 2700 K, whereas the nightside is closer to 1800 K.
+The other models produce more extreme day-night temperature gradients.
+These differences arise because the kinematic model allows a steep temperature gradient on the dayside, so the substellar point is much hotter than the terminator, whereas the two temperature map imposes a constant dayside temperature.
+The intermediate temperature gradient in the spherical harmonics model fits the data the best.
+However, this model may not be physically realistic: on the nightside, it produces much higher temperatures at the poles than at the equator, contrary to predictions from GCMs (which we discuss in \S\,\ref{sec:gcm}).
+
+%The kinematic model has the hottest dayside temperature, and the two-temperature model has the smallest.
 The differences in peak temperature for the models we consider ranges from $630\,\mathrm{K}$ for \Spitzer\ Channel 1 to $1070\,\mathrm{K}$ for the broadband WFC3 light curve.
 The minimum nightside temperature is also model-dependent: for the WFC3 data, the two-temperature model predicts a nightside temperature of zero Kelvin, whereas the best fit kinematic model has a nightside temperature of $1980\,\mathrm{K}$.
-These differences arise because the kinematic model allows a steep temperature gradient on the dayside, so the substellar point is much hotter than the terminator, whereas the two temperature map imposes a constant dayside temperature.
-The spherical harmonics model has an intermediate temperature gradient and fits the data the best.
-However, this model may not be physically realistic: on the nightside, it produces much higher temperatures at the poles than at the equator, contrary to predictions from GCMs (which we discuss in \S\,\ref{sec:gcm}).
 
@@
 The GCM predicts a cooler nightside than all models except the two-temperature model.
-We note that the GCM does not provide a perfect fit to the data, whereas multiple \texttt{spiderman} maps fit quite well, with large differences in temperature between them (see Table \,\ref{table:model_comparison}).
+We note that the GCM does not provide a perfect fit to the data, whereas multiple \texttt{spiderman} maps fit quite well, with large differences in temperature between them (see Table \,\ref{table:models}).
 Determining which models (if any) accurately describe the climate will require higher precision phase curves and/or eclipse mapping \citep[e.g.][]{dewit12}.

### 2018-02-08 Figures/test_differences_in_spectra_for_thermal_models.py

@@ -4,15 +4,28 @@ import numpy as np
 z = pickle.load(open("zhang.p", "rb"))
 s = pickle.load(open("spherical.p", "rb"))
 h = pickle.load(open("hotspot_t.p", "rb"))
+sc = pickle.load(open("sincos.p", "rb"))
 
 s, se  = s[1][1::], s[2][1::]
 z, ze  = z[1][1::], z[2][1::]
 h, he  = h[1][1::], h[2][1::]
+sc, sce  = sc[1][1::], sc[2][1::]
 
-zdiff = np.abs((s - z)/np.sqrt(s**2 + z**2))
-hdiff = np.abs((s - h)/np.sqrt(h**2 + s**2))
-sdiff = np.abs((z - h)/np.sqrt(h**2 + z**2))
+zdiff = np.abs((s - z)/np.sqrt(se**2 + ze**2))
+hdiff = np.abs((s - h)/np.sqrt(he**2 + se**2))
+sdiff = np.abs((z - h)/np.sqrt(he**2 + ze**2))
 
-print np.median(zdiff), 1.*sum(zdiff < 1.)/len(zdiff)
-print np.median(hdiff), 1.*sum(hdiff < 1.)/len(hdiff)
-print np.median(sdiff), 1.*sum(sdiff < 1.)/len(sdiff)
+print "median deviation", "fraction of bins within one sigma"
+print "zhang - spherical", np.median(zdiff), 1.*sum(zdiff < 1.)/len(zdiff)
+print "spherical - hotspot", np.median(hdiff), 1.*sum(hdiff < 1.)/len(hdiff)
+print "zhang - hotspot", np.median(sdiff), 1.*sum(sdiff < 1.)/len(sdiff)
+
+
+diff = np.abs((z - sc)/np.sqrt(ze**2 + sce**2))
+print "zhang - sincos", np.median(diff), 1.*sum(diff < 1.)/len(diff)
+
+diff = np.abs((s - sc)/np.sqrt(se**2 + sce**2))
+print "spherical - sincos", np.median(diff), 1.*sum(diff < 1.)/len(diff)
+
+diff = np.abs((h - sc)/np.sqrt(he**2 + sce**2))
+print "hotspot - sincos", np.median(diff), 1.*sum(diff < 1.)/len(diff)

### 2018-02-09 ms.tex
pt profile fig

@@
 The planet flux changes significantly with orbital phase in all three of the data sets, suggesting a strong gradient from dayside to nightside temperature, and peak brightness occurs near phase 0.5.
-In this section, we quantitatively characterize the phase curve shape, split the data into phase resolved spectra, evaluate different temperature maps, and compare with previous observations of the dayside thermal emission spectrum.
+In this section, we quantitatively characterize the phase curve shape, split the data into phase resolved spectra, evaluate different temperature maps, compare with previous observations of the dayside thermal emission spectrum, and report the transmission spectrum.
 
@@
 
-The best fit model is generally the spherical harmonics map.
+The spherical harmonics map generally fits the data the best.
 It has a lower BIC value than all the other models for the broadband WFC3 and \Spitzer\,$3.6\,\mu$m phase curves.
 For the $4.5\,\mu$m phase curve, the two temperature map provides the best fit, but it only lowers the BIC value by 2 relative to the spherical harmonics map, which is not a statistically significant improvement \citep{kass95}.
+The worst fit model is gene FIXME
+
 The spherical harmonics model yields a mean dayside temperature near 2700 K, whereas the nightside is closer to 1800 K.
@@
 
+We compared the TP profiles from the GCM to cloud condensation curves and the best fit radiative-convective equilibrium models from the 1D retrieval (Figure\,\ref{fig:TP}).
+
+\begin{figure}
+\includegraphics[width = 0.5\textwidth]{Figures/WASP-103b-NoClouds-Drag3-nit-LR.pdf}
+\caption{TP profiles from the GCM (thin colored lines) and 1D retrievals (thick lines), compared to condensation curves of potential cloud species.
+The blue, green, and red lines correspond to TP profiles randomly drawn from the FIXME GCM at orbital phases FIXME.
+The thick red and blue lines are the best fit 1D TP profiles for the dayside ($\phi = 0.5$) and nightside ($\phi = 0.1$), respectively.}
+\label{fig:TP}
+\end{figure}
+
 We also compared the GCM output to temperature maps retrieved with \texttt{spiderman}.

### 2018-02-09 ms.tex
GCM transmission spectrum

@@
 We calculate planet-to-star flux assuming a NextGen spectrum for the star (interpolated to $T_\mathrm{eff} = 6110$ K), a blackbody for the planet, and a planet-to-star radius ratio of 0.1146.
-We consider two plausible nightside temperatures (1500 and 2000 K), which encompass most of the mean nightside temperatures estimated from the phase variation models (Table\,\ref{table:models}).
+We consider a plausible nightside temperature of 1700 K, which is near the median of the nightside temperatures estimated from the phase variation models (Table\,\ref{table:models}).
 We also show the uncorrected transit depths.
-For the uncorrected data, there is an offset between the \HST\ and \Spitzer\ data of about 10 atmospheric scale heights.
-
-The spectrum is inconsistent with a flat line at $3.2\,\sigma$ confidence, and the slope is much larger than expected from theoretical models (FIXME show GCM).
-For nightside temperatures of 1500 and 2000 K, the spectrum is consistent with a flat line to within $1.3\,\sigma$.
-The mean transit depths are $1.3431 \pm 0.0029$,  $1.3360 \pm 0.0029$, and $1.3078 \pm 0.0029\%$ for assumed nightside temperatures of 0, 1500, and 2000 K.
+For the uncorrected data, there is an offset between the \HST\ and \Spitzer\ data of more than five atmospheric scale heights.
+The uncorrected spectrum is inconsistent with a flat line at $3.2\,\sigma$ confidence, whereas the nightside-corrected spectrum is consistent within $1\,\sigma$.
+The corrected spectrum is also consistent with predictions from the $\tau_\mathrm{drag4}$ GCM, which shows water features in the WFC3 bandpass.
+Future high precision observations could reveal these features.
+%The mean transit depths are $1.3431 \pm 0.0029$,  $1.3360 \pm 0.0029$, and $1.3078 \pm 0.0029\%$ for assumed nightside temperatures of 0, 1500, and 2000 K.
 Of these, only the 2000 K model yields a transit depth consistent with the measurement of \cite{lendl17} at shorter wavelengths where nightside contamination is negligible ($1.3092 \pm 0.0114$\%).
@@
 \includegraphics[width = 0.5\textwidth]{Figures/w103b_transmission_spectrum.pdf}
-\caption{The transmission spectrum of WASP-103b (points) for a range of assumptions about the planet's nightside temperature.
-The gray points are not corrected for planet nightside flux, whereas the blue and red points are corrected for an average nightside photospheric temperature of 1400 and 2000 K, respectively.
-The dotted line corresponds to the mean transit depth (assuming $T_\mathrm{night} = 2000$ K).
-Atmospheric scale height $H$ is shown on the right y-axis, where $H = 5.5\times10^6$ m (assuming a mean molecular weight of 2.3 atomic mass units, surface gravity $g = 15.85$ m/s$^2$, and a temperature $T = 2410$ K).}
+\caption{The transmission spectrum of WASP-103b, corrected for planet nightside emission at 1700 K (blue points) and uncorrected (red points).
+The dark gray line is the model transmission spectrum from the $\tau_\mathrm{drag4}$ GCM.
+Atmospheric scale height $H$ is shown on the right y-axis, where $H = 5.5\times10^6$ m (assuming a mean molecular weight of 2.3 atomic mass units, surface gravity $g = 15.9$ m/s$^2$, and a temperature $T = 2410$ K).}
 \label{fig:tspec}

### 2018-02-09 ms.tex
tspec table

@@
 We show the measured transmission spectrum in Figure\,\ref{fig:tspec}.
-The spectrum is biased by flux contamination from the planet's nightside; to correct for nightside emission, we estimate the planet-to-star flux ratio and subtract it from the transit depth.
-We calculate planet-to-star flux assuming a NextGen spectrum for the star (interpolated to $T_\mathrm{eff} = 6110$ K), a blackbody for the planet, and a planet-to-star radius ratio of 0.1146.
-We consider a plausible nightside temperature of 1700 K, which is near the median of the nightside temperatures estimated from the phase variation models (Table\,\ref{table:models}).
+The spectrum is biased by flux contamination from the planet's nightside; to correct for nightside emission, we estimate the average nightside planet-to-star flux ratio and subtract it from the transit depth.
+We calculate planet-to-star flux using a NextGen spectrum for the star (interpolated to $T_\mathrm{eff} = 6110$ K), a blackbody for the planet, and a planet-to-star radius ratio of 0.1146.
+We assume a nightside temperature of 1700 K, which is near the median of the nightside temperatures estimated from the phase variation models (Table\,\ref{table:models}).
 We also show the uncorrected transit depths.
+The corrected and uncorrected transit depths are listed in Table\,\ref{table:tspec}.
 For the uncorrected data, there is an offset between the \HST\ and \Spitzer\ data of more than five atmospheric scale heights.
@@
 The corrected spectrum is also consistent with predictions from the $\tau_\mathrm{drag4}$ GCM, which shows water features in the WFC3 bandpass.
-Future high precision observations could reveal these features.
+Future observations with higher precision could reveal these features.
 %The mean transit depths are $1.3431 \pm 0.0029$,  $1.3360 \pm 0.0029$, and $1.3078 \pm 0.0029\%$ for assumed nightside temperatures of 0, 1500, and 2000 K.
@@
 \end{figure}
+
+\begin{deluxetable}{LLL}
+\tablecolumns{3}
+\tablewidth{0pt}
+\tablecaption{WASP-103b Transmission Spectrum\label{table:tspec}}
+\tablehead{
+\colhead{Wavelength} & \colhead{Transit Depth (\%)} & \colhead{Transit Depth (\%)} \\
+\colhead{(micron)} & \colhead{($T_\mathrm{night} = 0$ K)} & \colhead{($T_\mathrm{night} = 1700$ K)}}
+\startdata
+1.175 & 1.329049 \pm 0.000092 & 0.013228 \pm 0.000092 \\
+1.225 & 1.329408 \pm 0.000087 & 0.013217 \pm 0.000087 \\
+1.275 & 1.333837 \pm 0.000086 & 0.013246 \pm 0.000086 \\
+1.325 & 1.334184 \pm 0.000087 & 0.013233 \pm 0.000087 \\
+1.375 & 1.359366 \pm 0.000089 & 0.013467 \pm 0.000089 \\
+1.425 & 1.353629 \pm 0.000091 & 0.013390 \pm 0.000091 \\
+1.475 & 1.341570 \pm 0.000092 & 0.013249 \pm 0.000092 \\
+1.525 & 1.350816 \pm 0.000093 & 0.013319 \pm 0.000093 \\
+1.575 & 1.333617 \pm 0.000100 & 0.013125 \pm 0.000100 \\
+1.625 & 1.353438 \pm 0.000104 & 0.013299 \pm 0.000104 \\
+3.6 & 1.401322 \pm 0.000328 & 0.013238 \pm 0.000328 \\
+4.5 & 1.432949 \pm 0.000264 & 0.013554 \pm 0.000264 \\
+\enddata
+\vspace{-0.8cm}
+\tablecomments{comments}
+\end{deluxetable}
 

### 2018-02-09 ms.tex
hotspot

@@
 \S\,\ref{sec:fits} details the models fit to the phase curves.
-In \S\,\ref{sec:results} we discuss results, including the phase curve amplitudes and hotspot offsets, the phase-resolved spectra, and estimates of the planet's climate.
+In \S\,\ref{sec:results} we discuss results, including the phase curve amplitudes and hotspot offsets, the phase-resolved spectra, estimates of the planet's climate, and the transmission spectrum.
 In \S\,\ref{sec:gcm} and \ref{sec:comparison}, we compare the observations to general circulation model (GCM) predictions and spectra from similar temperature stars and directly imaged companions.
@@
 Table\,\ref{table:amps_offsets} lists the estimated amplitudes and hotspot offsets (median and $1\,\sigma$ credible interval) for the band-integrated WFC3 phase curve and both \Spitzer\ channels.
-The estimates are from the sine curve model for the thermal phase variation, which fits directly for the amplitude and offset.
+The estimates are from the sine curve model for the thermal phase variation.
+We note that the sinusoid does not fit the data as well as the spherical harmonics model (see \ref{table:fits}); however, the sine curve fits the amplitude and hotspot offset directly, as free parameters.
 
@@
 Fast radiative timescales are predicted at high temperatures, and small hotspot offsets are also observed for other very hot Jupiters \citep{perez13, komacek16, komacek17}.
+The measured offsets are inconsistent with the trend reported in \cite{zhang17}, which predicts the hotspot offset increases with planet temperature for irradiation temperatures greater than 3410 K.
+The \cite{zhang17} model predicts a hotspot offset of $4.5^\circ$ for WASP-103b, which is significantly larger than observed, hinting at diversity in the circulation patterns of the hottest planets.
 The phase curve amplitudes are large (near 0.8 - 0.9), as expected for an atmosphere with inefficient heat redistribution.

### 2018-02-09 Figures/get_amps_offs_allmodels.py

@@ -9,18 +9,15 @@ from astropy.convolution import Gaussian1DKernel, convolve
 from scipy.interpolate import interp1d
 
 path  = "WFC3_best_fits/"
-files = glob.glob(os.path.join(path, "bestfit*.pic"))		
-for f in files:
-	p = pickle.load(open(f, 'rb'))
+models = ["hotspot_t", "zhang", "spherical", "sincos"]
+for i, model in enumerate(models):
+	p = pickle.load(open(path+"bestfit_"+model+".pic", "rb")) 
 	d, m = p[0], p[1]			
 
 	x, y = m.phase, m.bestfit_no_eclipse
 	ind = np.argsort(x)
 	x, y = x[ind], y[ind]
 	
-
-        #ind = m.bestfit_no_eclipse == np.max(m.bestfit_no_eclipse)
-
 
 	fnew = interp1d(x, y, kind = 'cubic')
 	xnew = np.linspace(0.4, 0.6, 1000)
@@ -31,5 +28,5 @@ for f in files:
 	offset = xnew[ind]
         print f, (offset - 0.5)*180./np.pi
 
-plt.legend()
-plt.show()
+#plt.legend()
+#plt.show()

### 2018-02-10 ms.tex
brightness temperatuers

@@
 The estimates are from the sine curve model for the thermal phase variation.
-We note that the sinusoid does not fit the data as well as the spherical harmonics model (see \ref{table:fits}); however, the sine curve fits the amplitude and hotspot offset directly, as free parameters.
+The advantage of using this model (even though it does not provide strictly the best fit), is that it fits for the amplitude and offset directly as free parameters.
+
+%We note that the sinusoid does not fit the data as well as the spherical harmonics model (see \ref{table:fits}); however, the sine curve fits the amplitude and hotspot offset directly, as free parameters.
 
@@
 The measured offsets are inconsistent with the trend reported in \cite{zhang17}, which predicts the hotspot offset increases with planet temperature for irradiation temperatures greater than 3410 K.
-The \cite{zhang17} model predicts a hotspot offset of $4.5^\circ$ for WASP-103b, which is significantly larger than observed, hinting at diversity in the circulation patterns of the hottest planets.
+The \cite{zhang17} model predicts an eastward hotspot offset of $4.5^\circ$ for WASP-103b, which is significantly larger than observed, hinting at diversity in the circulation patterns of the hottest planets.
 The phase curve amplitudes are large (near 0.8 - 0.9), as expected for an atmosphere with inefficient heat redistribution.
@@
 For the $4.5\,\mu$m phase curve, the two temperature map provides the best fit, but it only lowers the BIC value by 2 relative to the spherical harmonics map, which is not a statistically significant improvement \citep{kass95}.
-The worst fit model is gene FIXME
+The spherical harmonics model yields a mean dayside temperature near 2700 K, whereas the nightside is closer to 1800 K, in good agreement with the blackbody fits to the phase-resolved spectra (see \S\,\ref{sec:bbfits}).
+The other models produce more extreme day-night temperature gradients.
+Between the models, there are substantial differences in the minimum and maximum temperatures (sometimes over 1000 K).
+The day and nightside means are in better agreement (generally matching to within 250 K).
+This behavior is not surprising: a wide range of temperature gradients can yield similar average temperatures when integrated over the disk of the planet.
 
-The spherical harmonics model yields a mean dayside temperature near 2700 K, whereas the nightside is closer to 1800 K.
-The other models produce more extreme day-night temperature gradients.
-These differences arise because the kinematic model allows a steep temperature gradient on the dayside, so the substellar point is much hotter than the terminator, whereas the two temperature map imposes a constant dayside temperature.
-The intermediate temperature gradient in the spherical harmonics model fits the data the best.
-However, this model may not be physically realistic: on the nightside, it produces much higher temperatures at the poles than at the equator, contrary to predictions from GCMs (which we discuss in \S\,\ref{sec:gcm}).
+%However, this model may not be physically realistic: on the nightside, it produces much higher temperatures at the poles than at the equator, contrary to predictions from GCMs (which we discuss in \S\,\ref{sec:gcm}).
 
@@
 \subsection{Blackbody Fits}
+\label{sec:bbfits}
 A blackbody is the simplest model for the planet's thermal emission and provides a useful first evaluation of the atmospheric properties.
@@
 The best-fit blackbodies are shown in Figures \ref{fig:spectra} and \ref{fig:dayside}.
-This model performs well for some orbital phases, with $\chi^2_\nu$ ranging from 0.9 to 1.1 for phases $\phi = 0.1, 0.7$ and $0.8$.
+The model is consistent with the data at the $3\,\sigma$ level for phases 0.1 - 0.7.
+At later phases, the \Spitzer\ data have significantly lower brightness temperatures.
+
+We also fit indepedent blackbody models to the \HST/WFC3 data and each \Spitzer\ channel.
+The resulting brightness temperatures are listed in Table\,\ref{table:teffs}.
+The WFC3 data are fit well by a blackbody model at all orbital phases (consistent at better than $1.5\,\sigma$).
+The brightness temperatures FIXME talk about significance of features.
+
+%This model performs well for some orbital phases, with $\chi^2_\nu$ ranging from 0.9 to 1.1 for phases $\phi = 0.1, 0.7$ and $0.8$.
 At other phases the blackbody model is a poorer fit, particularly to the \Spitzer\ data.
@@
 
-We also fit blackbody models to the WFC3 data only, and found that they provide a good fit at all orbital phases.
+%We also fit blackbody models to the WFC3 data only, and found that they provide a good fit at all orbital phases.
 The $\chi^2_\nu$ values range from 0.5 to 2.4, with a median of 0.9.
@@
 The more sophisticated grid-based retrieval (described in the next section) provides a better fit to the dayside.
+
+%WFC3: consistent with a blackbody
 
@@
 		\startdata
-		0.06 - 0.15 & 1917 \pm 43 & 1674 \pm 177 & 1677 \pm 102 & 0.7 \\
-		0.15 - 0.25 & 2254 \pm 25 & 2821 \pm 136 & 2486 \pm 87 & 0.8 \\
-		0.25 - 0.35 & 2650 \pm 17 & 3170 \pm 128 & 2772 \pm 74 & 1.4 \\
-		0.35 - 0.44 & 2905 \pm 11 & 3016 \pm 128 & 3216 \pm 68 & 1.1 \\
-		0.44 - 0.56 & 3011 \pm 8 & 3158 \pm 153 & 3350 \pm 53 & 2.4 \\
-		0.56 - 0.65 & 2884 \pm 11 & 2764 \pm 133 & 3051 \pm 70 & 1.7 \\
-		0.65 - 0.75 & 2634 \pm 16 & 2857 \pm 135 & 2550 \pm 85 & 1.1 \\
-		0.75 - 0.85 & 2312 \pm 23 & 2153 \pm 151 & 2117 \pm 91 & 1.2 \\
-		0.85 - 0.94 & 2025 \pm 34 & 1825 \pm 167 & 1414 \pm 113 & 0.5 \\
+		0.06 - 0.15 & 1883 \pm 41 & 1523 \pm 158 & 1589 \pm 98 & 0.7 \\
+		0.15 - 0.25 & 2208 \pm 24 & 2612 \pm 104 & 2299 \pm 78 & 0.9 \\
+		0.25 - 0.35 & 2587 \pm 16 & 2926 \pm 95 & 2592 \pm 67 & 1.5 \\
+		0.35 - 0.44 & 2831 \pm 11 & 2834 \pm 93 & 2976 \pm 61 & 1.5 \\
+		0.44 - 0.56 & 2933 \pm 8 & 2995 \pm 141 & 3154 \pm 48 & 2.8 \\
+		0.56 - 0.65 & 2811 \pm 11 & 2631 \pm 96 & 2891 \pm 63 & 2.0 \\
+		0.65 - 0.75 & 2572 \pm 15 & 2708 \pm 101 & 2421 \pm 78 & 1.3 \\
+		0.75 - 0.85 & 2263 \pm 22 & 1952 \pm 117 & 1939 \pm 83 & 1.3 \\
+		0.85 - 0.94 & 1987 \pm 34 & 1594 \pm 150 & 1288 \pm 118 & 0.6 \\
 		\enddata

### 2018-02-10 ms.tex
ed

@@
 The resulting brightness temperatures are listed in Table\,\ref{table:teffs}.
-The WFC3 data are fit well by a blackbody model at all orbital phases (consistent at better than $1.5\,\sigma$).
-The brightness temperatures FIXME talk about significance of features.
+The WFC3 data are fit well by a blackbody model at all orbital phases except phase 0.5 (consistent at better than $1.5\,\sigma$).
+The dayside has higher signal-to-noise than the other orbital phases, thanks to the two secondary eclipse observations from \cite{cartier17}, and the more sophisticated grid-based retrieval (described in the next section) provides a better fit to the dayside.
+FIXME talk about significance of features.
 
@@
 The dayside spectrum is the poorest fit by the blackbody model.
-This finding is not a surprise because the dayside has higher signal-to-noise than the other orbital phases, thanks to the two secondary eclipse observations from \cite{cartier17}.
-The more sophisticated grid-based retrieval (described in the next section) provides a better fit to the dayside.
+This finding is not a surprise because
 

### 2018-02-12 ms.tex
edits:

@@
 The other models produce more extreme day-night temperature gradients.
-Between the models, there are substantial differences in the minimum and maximum temperatures (sometimes over 1000 K).
-The day and nightside means are in better agreement (generally matching to within 250 K).
+Between the models, there are substantial differences in the minimum and maximum temperatures (sometimes over 1000 K), whereas the day and nightside means are in better agreement (generally matching to within 250 K).
 This behavior is not surprising: a wide range of temperature gradients can yield similar average temperatures when integrated over the disk of the planet.
@@
 The best-fit blackbodies are shown in Figures \ref{fig:spectra} and \ref{fig:dayside}.
-The model is consistent with the data at the $3\,\sigma$ level for phases 0.1 - 0.7.
-At later phases, the \Spitzer\ data have significantly lower brightness temperatures.
+The model fits the data fairly well: it is consistent with the data at the $3\,\sigma$ level for 70\% of the orbital phases.
+At phase 0.5, the \Spitzer\ data imply higher brightness temperatures than the WFC3 data, whereas at phases $0.8 - 0.9$ the \Spitzer\ data have lower brightness temperatures.
+These differences suggest the presence of an emission feature on the dayside at \Spitzer\ wavelengths, which transitions to an absorption feature on the nightside, perhaps indicating changes in thermal structure with longitude in the atmosphere.
 
@@
 The resulting brightness temperatures are listed in Table\,\ref{table:teffs}.
-The WFC3 data are fit well by a blackbody model at all orbital phases except phase 0.5 (consistent at better than $1.5\,\sigma$).
+The WFC3 data agree well by a blackbody model at all orbital phases except phase 0.5 (consistent at better than $1.5\,\sigma$).
 The dayside has higher signal-to-noise than the other orbital phases, thanks to the two secondary eclipse observations from \cite{cartier17}, and the more sophisticated grid-based retrieval (described in the next section) provides a better fit to the dayside.
-FIXME talk about significance of features.
 
@@
 Another caveat is that the model is not self-consistent: the energy leaving the dayside is not constrained to equal the energy entering the nightside.
-Further work is needed to develop a fully self-consistent 2-D retrieval method.
+Further work is needed to develop a fully self-consistent 2-D retrieval method for phase curve observations.
 
@@
 To assess how well the GCM predictions reproduce the data, we calculated the amplitude and hot spot offset for all the models (listed in Table\,\ref{table:amps_offsets}).
-The observed hotspot offsets ($0.3 - 2.0$ degrees) are best reproduced by the $\tau_\mathrm{drag3}$ and $\tau_\mathrm{drag4}$ models, which have small offsets due to changes in the wind pattern.
+The small observed hotspot offsets ($-0.3 - 2.0$ degrees) are best reproduced by the $\tau_\mathrm{drag4}$ model, which has a smaller offset than the drag-free GCMs due to changes in wind pattern.
 In the drag models, the winds shift from a substellar to an antistellar flow rather than an equatorial jet.
-The nominal and metal-enhanced GCMs both have offsets that are too large (10-20 degrees).
-On the other hand, the phase curve amplitudes are better matched by the nominal GCM than either of the drag models.
+The $\tau_\mathrm{drag4}$ model also provides the match the observed phase curve amplitudes.
+
+%On the other hand, the phase curve amplitudes are better matched by the nominal GCM than either of the drag models.
 The most precise observed amplitude is $0.91\pm0.02$ (in the WFC3 bandpass), which is significantly smaller than the amplitudes predicted by the drag models (0.97, 0.99).
@@
 
-To check that fast drag timescales of order $10^3 - 10^4$\,s are physically realistic, we computed the free electron abundance due to ionized metals for the $\tau_\mathrm{drag4}$ GCM.
+To check that fast drag timescales of order $10^4$\,s are physically realistic, we computed the free electron abundance due to ionized metals for the $\tau_\mathrm{drag4}$ GCM.
 Using the order-of-magnitude expression from \cite{perna10} (Equation 12), we estimate a drag timescale at the substellar point of $\tau_\mathrm{drag}  = 2\times10^4/B^2$ s, where $B$ is the magnetic field in Gauss.
@@
 
-We compared the TP profiles from the GCM to cloud condensation curves and the best fit radiative-convective equilibrium models from the 1D retrieval (Figure\,\ref{fig:TP}).
+We also compared the TP profiles from the GCM to cloud condensation curves and the best fit radiative-convective equilibrium models from the 1D retrieval (Figure\,\ref{fig:TP}).
+The 3D and 1D models agree fairly well in the photosphere (at a pressure of $10^{-1} -10^{-3}$ bars).
+FIXME: why doesn't the deep atmosphere agree?
+The photosphere is at higher altitudes than the intersection points for the condensation curves and the TP profiles, suggesting that the observable atmosphere is cloud-free.
 
@@
 The blue, green, and red lines correspond to TP profiles randomly drawn from the FIXME GCM at orbital phases FIXME.
-The thick red and blue lines are the best fit 1D TP profiles for the dayside ($\phi = 0.5$) and nightside ($\phi = 0.1$), respectively.}
+The thick red and blue lines are the best fit 1D TP profiles for the dayside ($\phi = 0.5$) and nightside ($\phi = 0.1$), respectively.
+The dotted lines correspond to regions of constant H$_2$O abundance, with numbers indicating the log10(H$_2$O volume mixing ratio).}
 \label{fig:TP}
@@
 \includegraphics[width = 0.5\textwidth]{Figures/gcm_comparison.pdf}
-\caption{GCM predictions (colored lines) compared to the best fit model for the WFC3 white light, \Spitzer 3.6, and \Spitzer\ 4.5 micron phase curves (black lines, top to bottom).
+\caption{GCM predictions (colored lines) compared to the best fit spherical harmonics model for the WFC3 white light, \Spitzer\ 3.6, and \Spitzer\ 4.5 micron phase curves (black lines, top to bottom).
 The nominal model is solar composition, cloud-free, with TiO/VO opacity and no drag.
@@
 		\startdata
-		Hot Jupiter & W103b night & 1920 \pm 40 & 3.2 \pm 0.04 & 0.07 \pm 1.8\mathrm{e}-01 & -0.00 \pm 1.6\mathrm{e}-01 \\
-		\, & W103b quadrature & 2410 \pm 20 & 3.2 \pm 0.04 & -0.14 \pm 7.8\mathrm{e}-02 & -0.01 \pm 6.7\mathrm{e}-02 \\
-		\, & W103b dayside & 3010 \pm 10 & 3.2 \pm 0.04 & 0.04 \pm 1.4\mathrm{e}-02 & 0.15 \pm 1.2\mathrm{e}-02 \\
+		Hot Jupiter & W103b night & 1880 \pm 40 & 3.2 \pm 0.04 & 0.07 \pm 1.8\mathrm{e}-01 & -0.00 \pm 1.6\mathrm{e}-01 \\
+		\, & W103b quadrature & 2400 \pm 20 & 3.2 \pm 0.04 & -0.14 \pm 7.8\mathrm{e}-02 & -0.01 \pm 6.7\mathrm{e}-02 \\
+		\, & W103b dayside & 2930 \pm 10 & 3.2 \pm 0.04 & 0.04 \pm 1.4\mathrm{e}-02 & 0.15 \pm 1.2\mathrm{e}-02 \\
 		Brown Dwarf & 2MASS J1320+0409 & 1880 \pm 70 & 5.19 \pm 0.16 & 0.21 \pm 6.3\mathrm{e}-04 & -0.06 \pm 5.0\mathrm{e}-04 \\
@@
 		\, & 2MASS J0003-2822 & 2890 \pm 80 & 5.18 \pm 0.04 & 0.26 \pm 1.3\mathrm{e}-04 & 0.10 \pm 1.1\mathrm{e}-04 \\
-		Imaged Companion & CD-35 2722\tablenotemark{1} & 1800 \pm 100 & 4.5 \pm 0.5 & - & 0.15 \pm 1.0\mathrm{e}-05 \\
-		\, & USco 1610-1913B\tablenotemark{2} & 2400 \pm 150 & - & 0.27 \pm 2.0\mathrm{e}-04 & 0.19 \pm 2.2\mathrm{e}-04 \\
-		\, & TWA 22A\tablenotemark{3} & 3000 \pm 100 & 4.5 \pm 0.5 & - & 0.29 \pm 2.0\mathrm{e}-05 \\
+		Imaged Companion & CD-35 2722 & 1800 \pm 100 & 4.5 \pm 0.5 & - & 0.15 \pm 1.0\mathrm{e}-05 \\
+		\, & USco 1610-1913B & 2400 \pm 150 & - & 0.27 \pm 2.0\mathrm{e}-04 & 0.19 \pm 2.2\mathrm{e}-04 \\
+		\, & TWA 22A & 3000 \pm 100 & 4.5 \pm 0.5 & - & 0.29 \pm 2.0\mathrm{e}-05 \\
 		\enddata
-	\tablenotetext{1}{\cite{wahhaj11}}
-	\tablenotetext{2}{\cite{aller13}}
-	\tablenotetext{3}{\cite{bonnefoy14}}
 	\end{deluxetable*}
@@
 The \HST/WFC3 spectra are consistent with  blackbody emission from the planet at all orbital phases.
-The best fit brightness temperatures ranges from $1920\pm40$ K (phase $\phi = 0.1$) to $3010\pm10$ K on the dayside.
+The best fit brightness temperatures ranges from $1880\pm40$ K (phase $\phi = 0.1$) to $2930\pm10$ K on the dayside.
 We attribute the absence of water features at WFC3 wavelengths to (1) H$_2$O dissociation on the dayside and (2) additional near-IR opacity from H-, TiO/VO and FeH.}
-\item{The \Spitzer\ data are \emph{not} consistent with a blackbody: there is an infrared emission feature at phases where the substellar point is visible ($\phi = 0.2 - 0.7$), which transitions to an absorption feature on the nightside ($\phi = -0.1 - 0.1$).
-We attribute these features to CO absorption and changing thermal structure from the dayside to the nightside.}
+\item{The \Spitzer\ data are \emph{not} consistent with the best fit blackbody to the WFC3 data: they have a higher brightness temperature at phases $\phi = 0.2 - 0.5$, which transitions to a lower brightness temperature on the nightside ($\phi = -0.2 - 0.1$).
+These characteristics are likely due to CO features in the infrared and changing thermal structure from the dayside to the nightside.}
 	\item{We characterized the composition with a 1D grid-based retrieval that assumes thermochemical and radiative-convective equilibrium.
@@
 	\item{We ran several 3D GCMs to compare to the data, including a nominal model with a cloud-free, solar composition, a metal-enriched model ([Fe/H] = 0.5), and two models with Lorentz drag.
-The GCMs with Lorentz drag have different circulation patterns and provide the best match to the small hotspot offsets that are observed, but they underpredict the planet's nightside flux.}
+The GCM with a Lorentz drag timescale of $10^4$ s matches the data best.
+This model has an equator-to-pole wind pattern that reproduces the small observed hotspot offsets and large amplitudes.}
 	\item{We compared the spectra of WASP-103b at phases 0.5 (dayside), 0.25 (quadrature), and 0.1 (nightside) to brown dwarfs and directly imaged companions of similar temperature.
@@
 These results provide a first look at the global composition and thermal structure of WASP-103b.
-The planet is complex, with changes in temperature profile with longitude and possible gradients in composition from dayside to nightside.
+The planet is complex, with changes in temperature profile with longitude, possible gradients in composition from dayside to nightside, and circulation patterns influenced by the magnetic field.
 These findings highlight the 3D nature of exoplanets and illustrate the importance of phase curve observations to develop a comprehensive understanding of their atmospheric chemistry and physics.

### 2018-02-12 Figures/spectra_comparison.py

@@ -47,7 +47,7 @@ l1, l2, l3, l4 = 1.15, 1.3, 1.35, 1.5
 
 #WASP-103b spectra
 path = "W103_spectra/"
-Ts = [1920, 2410, 3010]
+Ts = [1880, 2400, 2930]
 files = ["phase_0.10_wfc3.txt", "phase_0.25_wfc3.txt", "phase_0.5_wfc3.txt"]
 
 star = np.genfromtxt(path+"wasp103_sed_fluxes.out")
@@ -56,7 +56,7 @@ star_flux = star[:,1]	                        #[ergs/s/cm^2]
 star_flux = star_flux*(470/10.)**2		#convert to absolute flux (10 pc)
 
 name = ["nightside", "quadrature", "dayside"]
-ylo = [0., 0.9, 2.8]
+ylo = [0., 0.8, 2.8]
 yhi = [1.15, 2.3, 4.3]
 
 plt.figure(figsize = (7.5, 3.5))

### 2018-02-12 ms.tex

@@
 To explore the three-dimensional effects of atmospheric dynamics, we ran several GCMs to compare with the measured phase-resolved spectra.
-(\textbf{Vivien: add text describing GCM}).
+We simulated the atmospheric circulation and thermal structure of the planet using the combined SPARC/MITgcm model~\citep{showman09}.
+The model solves the primitive equations in spherical geometry using the MITgcm~\citep{Adcroft2004} and the radiative transfer equations using a state-of-the-art one dimensional radiative transfer model~\citep{Marley1999}.
+The code represents the opacities as correlated-k tables based on the line-by-line opacities described in \citet{Visscher2006,freedman14}.
+Our fiducial model assumes a solar composition with elemental abundances of \citet{Lodders2002a} and the chemical equilibrium gas phase composition from \citet{Visscher2006}.
+These calculations take into account the presence of $\rm H^-$ opacities and the effect of molecular dissociation on the abundances.
+We use a timestep of 25s, run the simulations for 300 days and average all quantities over the last 100 days.
+Overall, our setup is the same as described in~\citet{parmentier16}, but using the specific parameters for the WASP-103 system.
+
+Several physical processes can reduce the ability of the atmosphere to transport heat efficiently through advection and change the overall circulation pattern.
+Among them, ohmic drag is though to be an important phenomenon in the ionized environment of extremely hot hot Jupiters~\citep{perna10}.
+We parametrize this effect as a Rayleigh drag with a drag constant $\tau_{drag}$ constant with pressure~\citep{showman13}.
+Varying $\tau_{drag}$  from large values (i.e.
+weak drag) to small values (i.e.
+strong drag), the atmospheric circulation is expected to shift from a jet-dominated regime to a more axisymmetric circulation pattern going from the substellar to anti stellar point.
+Moderate drag timescales are expected to change the circulation pattern and thus reduce significantly the shift of the hottest point of the atmosphere whereas short drag timescales are also expected to change strength of the winds and thus the atmospheric day/night contrast~\citep{komacek16,komacek17}.
+Although Rayleigh drag is an incomplete representation of the complex magneto-hydrodynamic effects expected in these atmospheres~\citep{batygin13,rogers14,rogers14a,rogers17}, it nonetheless provides an estimate of the strength of the drag mechanism necessary to match the observations~\citep{komacek17,koll18,parmentier17}.
+
 Our nominal GCM was a cloud-free, solar composition atmosphere with TiO/VO opacity and no added drag.
-We also ran models with enhanced metallicity ([M/H] = 0.5), no TiO/VO, and added atmospheric drag.
-Lorentz drag can occur in the hottest exoplanet atmospheres, which may be partially ionized and coupled to the background magnetic field.
-We included Rayleigh drag forces in the GCM, which are proportional to the wind speed scaled by a time constant \citep[$F_\mathrm{drag} \propto -v/\tau_\mathrm{drag}$;][]{menou09}.
-We assumed the drag timescale is uniform throughout the atmosphere and considered two cases: $\tau_\mathrm{drag} = 10^3$ and $10^4$ s, which we label $\tau_\mathrm{drag3}$ and $\tau_\mathrm{drag4}$, respectively.
-
+We also ran models with enhanced metallicity ([M/H] = 0.5), no TiO/VO, and added atmospheric drag with timescales $\tau_\mathrm{drag} = 10^3$ and $10^4$ s, which we label $\tau_\mathrm{drag3}$ and $\tau_\mathrm{drag4}$, respectively.
 To assess how well the GCM predictions reproduce the data, we calculated the amplitude and hot spot offset for all the models (listed in Table\,\ref{table:amps_offsets}).

### 2018-02-12 ms.tex
edit

@@
 We also show the measured planet-to-star flux for each map (points), which is model-dependent due to slight degeneracies with the instrument systematic model.
-\textbf{Right:} Temperature maps from the best fit models and the GCM at a pressure of 0.01 bar.}
+\textbf{Right:} Temperature maps from the best fit models and the GCM at a pressure of 0.1 bar.}
 \label{fig:model_comparison}
@@
 The model fits the data fairly well: it is consistent with the data at the $3\,\sigma$ level for 70\% of the orbital phases.
-At phase 0.5, the \Spitzer\ data imply higher brightness temperatures than the WFC3 data, whereas at phases $0.8 - 0.9$ the \Spitzer\ data have lower brightness temperatures.
+However, the \Spitzer\ data have higher brightness temperatures than the WFC3 data at phase 0.5, and lower brightness temperatures at phases $0.8 - 0.9$.
 These differences suggest the presence of an emission feature on the dayside at \Spitzer\ wavelengths, which transitions to an absorption feature on the nightside, perhaps indicating changes in thermal structure with longitude in the atmosphere.
@@
 The WFC3 data agree well by a blackbody model at all orbital phases except phase 0.5 (consistent at better than $1.5\,\sigma$).
-The dayside has higher signal-to-noise than the other orbital phases, thanks to the two secondary eclipse observations from \cite{cartier17}, and the more sophisticated grid-based retrieval (described in the next section) provides a better fit to the dayside.
+The dayside has higher signal-to-noise than the other orbital phases, thanks to the two secondary eclipse observations from \cite{cartier17}.
+The more sophisticated grid-based retrieval (described in the next section) provides a better fit to the dayside.
 
@@
 We use a timestep of 25s, run the simulations for 300 days and average all quantities over the last 100 days.
-Overall, our setup is the same as described in~\citet{parmentier16}, but using the specific parameters for the WASP-103 system.
+Overall, our setup is the same as described in~\citet{parmentier16} but uses the specific parameters for the WASP-103 system.
 
@@
 Using the order-of-magnitude expression from \cite{perna10} (Equation 12), we estimate a drag timescale at the substellar point of $\tau_\mathrm{drag}  = 2\times10^4/B^2$ s, where $B$ is the magnetic field in Gauss.
-We assume a temperature and pressure of 3359 K and 0.11 bar, and that the magnetic field is perpendicular to the flow.
+We assume a temperature and pressure of 3359 K and 0.11 bar (FIXME use correct values for drag4), and that the magnetic field is perpendicular to the flow.
 To reach a drag timescale of $10^4$\,s, a magnetic field stronger than $\sim1$ Gauss is required.
@@
 We also compared the GCM output to temperature maps retrieved with \texttt{spiderman}.
-Figure\,\ref{fig:model_comparison} shows the 0.01 bar temperature map for the $\tau_\mathrm{drag4}$ GCM compared to the best fit models.
+Figure\,\ref{fig:model_comparison} shows the 0.1 bar temperature map for the $\tau_\mathrm{drag4}$ GCM compared to the best fit models.
 At this pressure, the GCM has minimum and maximum temperatures of $580$ and $3520$ K.

### 2018-02-14 ms.tex
edits

@@
 
-\correspondingauthor{Laura Kreidberg}
-\email{laura.kreidberg@cfa.harvard.edu}
+%\correspondingauthor{Laura Kreidberg}
+%\email{laura.kreidberg@cfa.harvard.edu}
 
@@
 The phase curves have large amplitudes and negligible hotspot offsets, indicative of poor heat redistribution to the nightside.
-We fit the phase variation with a range of climate maps and find they all provide reasonable fits to the data, but have large degeneracies in temperature (up to 1000 K for a given latitude/longitude).
-The phase-resolved spectra are consistent with blackbodies in the WFC3 bandpass, with brightness temperatures ranging from 2000 K on the nightside to 3000 K on the dayside.
-However, the dayside spectrum has a strong feature in the \Spitzer\ bands, which we attribute to CO emission and a thermal inversion.
-The emission feature is not present on the nightside, suggesting changes in thermal structure with longitude.
-We retrieved the atmospheric composition with a 1D self-consistent modeling technique and found the atmosphere is moderately metal-enriched ($\mathrm{[M/H]} =  23^{+29}_{-13}\times$ solar), and the carbon-to-oxygen ratio is below 0.9 at $3\,\sigma$ confidence.
+We fit the phase variation with a range of climate maps and find that a spherical harmonics model generally provides the best fit.
+The phase-resolved spectra are consistent with blackbodies in the WFC3 bandpass, with brightness temperatures ranging from $1880\pm40$ K on the nightside to $2930 \pm 10$ K on the dayside.
+The dayside spectrum has a significantly higher brightness temperature in the \Spitzer\ bands, which we attribute to CO emission and a thermal inversion.
+The inversion is not present on the nightside.
+The transmission spectrum is featureless, but consistent with the small features expected from cloud-free models.
+Using the dayside and nightside emission spectra, we retrieved the atmospheric composition with a 1D self-consistent modeling technique and found the atmosphere is moderately metal-enriched ($\mathrm{[M/H]} =  23^{+29}_{-13}\times$ solar) and the carbon-to-oxygen ratio is below 0.9 at $3\,\sigma$ confidence.
 In contrast to cooler hot Jupiters, we do not detect significant water absorption, which we attribute to partial H$_2$O dissociation and additional opacity from H- and trace amounts of hydrides/oxides.
-We compare the phase curves to 3D general circulation models and find that atmospheric drag is required to explain the small hotspot offsets, but that these models overpredict the phase curve amplitude.
+We compare the phase curves to 3D general circulation models and find that atmospheric drag with a timescale of $10^4$ s is the best match to the data, suggesting the presence of a magnetic field with strength $\sim1$ Gauss.
 We also compare the WASP-103b spectra to brown dwarfs and young directly imaged companions and find these more massive and self-luminous objects have significantly larger water features, indicating that surface gravity and irradiation environment play an important role in shaping the spectra of hot Jupiters.
@@
 To test that the phase-resolved planet-to-star flux values are robust to different approaches for fitting the phase curves, we compared the estimated planet-to-star flux for all four of the thermal phase variation models (sinusoid, kinematic, spherical harmonics, and two temperature).
-We found that the choice of model does not significantly change the estimated planet-to-star flux ratios.
 Since the systematic noise is not strongly correlated with the astrophysical signal, the systematics-divided data are nearly identical for all the models.
 This point is illustrated in Figure\,\ref{fig:model_comparison} for the broadband WFC3 light curve.
-For all phase bins, the estimated planet-to-star flux agrees to better than one sigma for all the models.
+We found that the choice of model generally does not significantly change the estimated planet-to-star flux ratios.
+The estimates agree to better than one sigma for 90\% of phase bins for the spherical harmonics, two temperature, and physical models.
+For the WFC3 data, the sinusoid is higher than the other models by an average of $1.5\,\sigma$ for phases $0.5 - 1$.
+This discrepancy may be due to the added flexibility in hotspot offset for the sinusoid model; other models do not allow for westward hotspot offsets.
 
@@
 We estimate $f > 2$, indicating a thermal inversion and likely inefficient transport of heat to the nightside.
-%Poor heat transport is observed in other very hot planets as well, due to damping of heat-propagating waves by fast radiative cooling or frictional drag in a partially ionized atmosphere \citep{komacek17}.
 The heat redistribution is strongly correlated with atmospheric metallicity because increasing metallicity  shifts the T-P profile to lower pressures, resulting in hotter temperatures at a given pressure level (equivalent to less efficient heat redistribution).
 
-We note that an important caveat for our results is that the best fit model is not a perfect fit to the data (with $\chi_\nu = 1.77$), so the uncertainties produced by the MCMC may be underestimated.
+We note that an important caveat for our results is that the best fit model is not a perfect fit to the data (with $\chi_\nu = 1.77$ for 9 degrees of freedom), so the uncertainties produced by the MCMC may be underestimated.
 Furthermore, the inferred C/O and metallicity are highly sensitive to the planet-to-star flux at \Spitzer\ $4.5\,\mu$m, which is the worst fit data point.
@@
 These calculations take into account the presence of $\rm H^-$ opacities and the effect of molecular dissociation on the abundances.
-We use a timestep of 25s, run the simulations for 300 days and average all quantities over the last 100 days.
+We used a timestep of 25s, ran the simulations for 300 days, and averaged all quantities over the last 100 days.
 Overall, our setup is the same as described in~\citet{parmentier16} but uses the specific parameters for the WASP-103 system.
@@
 (FIXME: this is all comparison to WFC3 phase curve; add comparison to Spitzer too).
-There are several physical processes not included in the GCM that could contribute to a hotter nightside, including shocks, longitude-dependent drag, latent heat released from H2 recombination.
 
@@
 Using the order-of-magnitude expression from \cite{perna10} (Equation 12), we estimate a drag timescale at the substellar point of $\tau_\mathrm{drag}  = 2\times10^4/B^2$ s, where $B$ is the magnetic field in Gauss.
-We assume a temperature and pressure of 3359 K and 0.11 bar (FIXME use correct values for drag4), and that the magnetic field is perpendicular to the flow.
+We assume a temperature and pressure of 3359 K and 0.11 bar, %(FIXME use correct values for drag4)
+and that the magnetic field is perpendicular to the flow.
 To reach a drag timescale of $10^4$\,s, a magnetic field stronger than $\sim1$ Gauss is required.
@@
 
-We also compared the TP profiles from the GCM to cloud condensation curves and the best fit radiative-convective equilibrium models from the 1D retrieval (Figure\,\ref{fig:TP}).
-The 3D and 1D models agree fairly well in the photosphere (at a pressure of $10^{-1} -10^{-3}$ bars).
-FIXME: why doesn't the deep atmosphere agree?
-The photosphere is at higher altitudes than the intersection points for the condensation curves and the TP profiles, suggesting that the observable atmosphere is cloud-free.
+We also compared the TP profiles from the $\tau_\mathrm{drag4}$ GCM to cloud condensation curves and the best fit radiative-convective equilibrium models from the 1D retrieval (Figure\,\ref{fig:TP}).
+For the dayside photosphere, the TP profile slope and absolute temperature are in rough agreement between the 1D best fit and the GCM.
+At higher pressures, the GCM is systematically cooler, which is likely due to the effect of atmospheric circulation (at these pressures the GCM mixes the temperature planet-wide).
+At lower pressures, the GCM is also cooler than the 1D fits, which may be due to metallicity differences between the models.
+The GCM has solar metallicity, whereas the best fit 1D model has $[M/H] \sim 1$.
+Higher metallicity compositions have larger TiO/H2O ratios, and since the pressure dependence of TiO dissociation is not as strong as for water dissociation, we expect stronger inversions for higher metallicity atmospheres.
+On the nightside, we also find that the GCM is cooler than the 1D models.
+There are several physical processes not included in the GCM that could contribute to a hotter nightside, including shocks, longitude-dependent drag, and latent heat released from H2 recombination.
+The best fit nightside TP profile is hotter than the condensation curves through most of the photosphere, suggesting that the observable atmosphere is relatively free of clouds.
+This prediction could be tested with longer wavelength phase curve observations.
+%The GCM predicts cloud formation on the nightside, which lowers the temperature of the photosphere.
 
 \begin{figure}
-\includegraphics[width = 0.5\textwidth]{Figures/WASP-103b-NoClouds-Drag3-nit-LR.pdf}
-\caption{TP profiles from the GCM (thin colored lines) and 1D retrievals (thick lines), compared to condensation curves of potential cloud species.
-The blue, green, and red lines correspond to TP profiles randomly drawn from the FIXME GCM at orbital phases FIXME.
-The thick red and blue lines are the best fit 1D TP profiles for the dayside ($\phi = 0.5$) and nightside ($\phi = 0.1$), respectively.
+\includegraphics[width = 0.5\textwidth]{Figures/WASP-103b-NoClouds-Drag4-nit-LR-1_4microns.pdf}
+\caption{TP profiles from the GCM and 1D retrieval, compared to condensation curves of potential cloud species.
+The thin blue/cyan lines correspond to a sample of randomly drawn nightside TP profiles from the GCM, and the thin red/orange lines correspond to dayside TP profiles.
+The darker colors (blue/red) indicate the extent of the contribution function (encompassing 80\% of the emitted flux).
+The thick red and blue lines are the best fit 1D TP profiles for the phase 0.5 (dayside average) and 0.1 (nightside average).
+The dashed lines are condensation curves for a range of possible cloud species.
 The dotted lines correspond to regions of constant H$_2$O abundance, with numbers indicating the log10(H$_2$O volume mixing ratio).}
@@
 Figure\,\ref{fig:model_comparison} shows the 0.1 bar temperature map for the $\tau_\mathrm{drag4}$ GCM compared to the best fit models.
-At this pressure, the GCM has minimum and maximum temperatures of $580$ and $3520$ K.
+At this pressure, the GCM has minimum and maximum temperatures of $920$ and $3360$ K.
 The temperature gradient from the dayside to the terminator is intermediate between the kinematic and spherical harmonics models.
@@
 The orbital phase $\alpha=0$ corresponds to secondary eclipse (when the substellar point faces Earth) and $\alpha=180$ corresponds to transit (when the antistellar point faces Earth).
-FIXME: Row (2) indicates the ratio of pressures probed in and out of the water band.
-On the dayside, the opacity out of the water band is filled in by absorption from H- and TiO/VO.
-Rows (3-4) show the abundances of H$_2$O and H-.
-At dayside temperatures, water dissociates and the photospheric abundance drops by $\sim10$.}
+Rows (2-4) show the abundances of CO, H$_2$O, and H-.
+At dayside temperatures, water dissociates, so the photospheric water abundance drops by $\sim10$ and the H- abundance increases by $\sim100$.
+By contrast, the CO abundance is uniform throughout the photosphere.}
 \label{fig:GCMabundance}
@@
 The directly imaged spectra are for the sources CD-35 2722, USco 1610-1913B, and TWA 22A and are taken from \cite{wahhaj11, aller13, bonnefoy14}.
-They are calibrated in absolute flux using published H-band photometry \citep{wahhaj11, aller13, bonnefoy09} and distances \citep{gaia16, teixeira09}, a flux-calibrated spectrum of Vega \citep{1985A&A...151..399M, 1985IAUS..111..225H}, and the corresponding filter passbands.
+They are young objects (aged 10 - 100 Myr), with lower surface gravities than brown dwarfs of comparable temperature.
+They also have gravitationally bound companions over a wide range of separations ($67\pm4$, $840\pm90$, and $1.8\pm0.1$ AU, respectively).
+The sources are calibrated in absolute flux using published H-band photometry \citep{wahhaj11, aller13, bonnefoy09} and distances \citep{gaia16, teixeira09}, a flux-calibrated spectrum of Vega \citep{1985A&A...151..399M, 1985IAUS..111..225H}, and the corresponding filter passbands.
 
@@
 We compared the spectra over the wavelength range $1.1 - 1.7\mu$m.
-The dominant spectral features over this range are expected to come from water, which has a forest of absorption lines near 1.4\,$\mu$m.
+The most prominent spectral features over this range are expected to come from water, which has a forest of absorption lines near 1.4\,$\mu$m.
 Spectra for the brown dwarfs and imaged companions have noticeable features in the water band, whereas WASP-103b does not.
@@
 The estimated amplitudes and uncertainties are listed in Table\,\ref{table:sources}.
+We note that a number of indices have been defined to characterize features in brown dwarf spectra, and these indices have revealed trends in the amplitude of a range of spectral features (water, sodium, potassium, VO, and FeH) with surface gravity and effective temperature \citep{reid01,geballe02,mclean03}.
+However, the WASP-103b data do not have high enough signal-to-noise or spectral resolution to meaningfully compare these indices.
+Instead we use a broader bandpass to address the simpler question: are the spectra with the same temperaratures consistent with each other?
 
-The $A_1$ and $A_2$ values are significantly lower for WASP-103b at dayside and quadrature than for brown dwarfs and imaged companions of similar temperature.
+We find that the $A_1$ and $A_2$ values are significantly lower for WASP-103b at dayside and quadrature than for brown dwarfs and imaged companions of similar temperature.
 WASP-103b typically has $A_1$ and $A_2$ consistent with zero, indicating no water absorption (in agreement with the analysis in \S\,\ref{sec:results} that showed water is depleted in the photosphere).
@@
 	\item{The dayside planet-to-star flux is $0.151\pm0.015\%$, $0.446\pm0.38\%$, and $0.569\pm0.014\%$ in the WFC3 bandpass, \Spitzer\ $3.6$, and \Spitzer\ $4.5\mu$m, respectively.
-The best fit blackbody to the WFC3 dayside spectrum has a brightness temperature of $3013 \pm 8$ K, making WASP-103b among the hottest exoplanets ever observed.}
+The best fit blackbody to the WFC3 dayside spectrum has a brightness temperature of $2930 \pm 10$ K, making WASP-103b among the hottest exoplanets ever observed.}
 	\item{The phase curves have large amplitudes ($0.8 -0.9\times$ the secondary eclipse depth), and small offsets in peak brightness from the substellar point (consistent with zero degrees at all wavelengths).
@@
 \item{The \Spitzer\ data are \emph{not} consistent with the best fit blackbody to the WFC3 data: they have a higher brightness temperature at phases $\phi = 0.2 - 0.5$, which transitions to a lower brightness temperature on the nightside ($\phi = -0.2 - 0.1$).
-These characteristics are likely due to CO features in the infrared and changing thermal structure from the dayside to the nightside.}
+These characteristics are likely due to CO features in the infrared and a temperature inversion on the dayside but not the nightside.}
+\item{The measured transmission spectrum is featureless (after correcting for nightside emission from the planet).
+3D model predict water features in transmission that could be detected with future high precision observations.}
 	\item{We characterized the composition with a 1D grid-based retrieval that assumes thermochemical and radiative-convective equilibrium.
@@
 The GCM with a Lorentz drag timescale of $10^4$ s matches the data best.
-This model has an equator-to-pole wind pattern that reproduces the small observed hotspot offsets and large amplitudes.}
+This model has an equator-to-pole wind pattern that reproduces the small observed hotspot offsets and large phase curve amplitudes.
+This fast drag timescale is consistent with expectations for a magnetic field of $\sim1$ Gauss.}
 	\item{We compared the spectra of WASP-103b at phases 0.5 (dayside), 0.25 (quadrature), and 0.1 (nightside) to brown dwarfs and directly imaged companions of similar temperature.

### 2018-02-14 Figures/test_differences_in_spectra_for_thermal_models.py

@@ -29,3 +29,7 @@ print "spherical - sincos", np.median(diff), 1.*sum(diff < 1.)/len(diff)
 
 diff = np.abs((h - sc)/np.sqrt(he**2 + sce**2))
 print "hotspot - sincos", np.median(diff), 1.*sum(diff < 1.)/len(diff)
+
+
+
+print "hostpot  - sincos all", diff, np.mean(diff[24:48]), len(diff)

### 2018-02-14 ms.tex
final

@@
 We fit the phase variation with a range of climate maps and find that a spherical harmonics model generally provides the best fit.
-The phase-resolved spectra are consistent with blackbodies in the WFC3 bandpass, with brightness temperatures ranging from $1880\pm40$ K on the nightside to $2930 \pm 10$ K on the dayside.
+The phase-resolved spectra are consistent with blackbodies in the WFC3 bandpass, with brightness temperatures ranging from $1880\pm40$ K on the nightside to $2930 \pm 40$ K on the dayside.
 The dayside spectrum has a significantly higher brightness temperature in the \Spitzer\ bands, which we attribute to CO emission and a thermal inversion.
@@
 The transmission spectrum is featureless, but consistent with the small features expected from cloud-free models.
-Using the dayside and nightside emission spectra, we retrieved the atmospheric composition with a 1D self-consistent modeling technique and found the atmosphere is moderately metal-enriched ($\mathrm{[M/H]} =  23^{+29}_{-13}\times$ solar) and the carbon-to-oxygen ratio is below 0.9 at $3\,\sigma$ confidence.
+Using the dayside and nightside emission spectra, we retrieved the atmospheric composition with a 1D self-consistent modeling technique and find the atmosphere is moderately metal-enriched ($\mathrm{[M/H]} =  23^{+29}_{-13}\times$ solar) and the carbon-to-oxygen ratio is below 0.9 at $3\,\sigma$ confidence.
 In contrast to cooler hot Jupiters, we do not detect significant water absorption, which we attribute to partial H$_2$O dissociation and additional opacity from H- and trace amounts of hydrides/oxides.
-We compare the phase curves to 3D general circulation models and find that atmospheric drag with a timescale of $10^4$ s is the best match to the data, suggesting the presence of a magnetic field with strength $\sim1$ Gauss.
+We compare the phase curves to 3D general circulation models and find that atmospheric drag with a timescale of $10^4$\,s is the best match to the data, suggesting the presence of a magnetic field with strength $\sim1$ Gauss.
 We also compare the WASP-103b spectra to brown dwarfs and young directly imaged companions and find these more massive and self-luminous objects have significantly larger water features, indicating that surface gravity and irradiation environment play an important role in shaping the spectra of hot Jupiters.
@@
 \caption{The transmission spectrum of WASP-103b, corrected for planet nightside emission at 1700 K (blue points) and uncorrected (red points).
-The dark gray line is the model transmission spectrum from the $\tau_\mathrm{drag4}$ GCM.
+The dark gray line is the model transmission spectrum from the $\tau_\mathrm{drag4}$ GCM, with squares indicating the model binned over the \Spitzer\ bandpasses.
 Atmospheric scale height $H$ is shown on the right y-axis, where $H = 5.5\times10^6$ m (assuming a mean molecular weight of 2.3 atomic mass units, surface gravity $g = 15.9$ m/s$^2$, and a temperature $T = 2410$ K).}
@@
 To calculate the best fit blackbody model, we assumed a planet-to-star radius ratio of 0.1146 and used a NextGen stellar spectrum interpolated to an effective temperature of 6110 K \citep{allard12}.
+We calculated the best fit with a least-squares fitting routine.
+To determine uncertainties on the planet brightness temperature, we performed an MCMC analysis with free parameters for the planet temperature and the stellar $T_\mathrm{eff}$.
+We used a Gaussian prior on $T_\mathrm{eff}$ of $6110 \pm 160$ K \citep{gillon14}.
+
 The best-fit blackbodies are shown in Figures \ref{fig:spectra} and \ref{fig:dayside}.
@@
 We also fit indepedent blackbody models to the \HST/WFC3 data and each \Spitzer\ channel.
-The resulting brightness temperatures are listed in Table\,\ref{table:teffs}.
+The resulting brightness temperatures and $1\,\sigma$ uncertainties are listed in Table\,\ref{table:teffs}.
 The WFC3 data agree well by a blackbody model at all orbital phases except phase 0.5 (consistent at better than $1.5\,\sigma$).
@@
 \tablehead{
-		\colhead{Orbital Phase} & \colhead{$T_\mathrm{b}$} & \colhead{$T_\mathrm{b}$} & \colhead{$T_\mathrm{b}$} & \colhead{$\chi^2_\nu$}\tablenotemark{1} \\
+\colhead{Orbital Phase} & \colhead{$T_\mathrm{b}$} & \colhead{$T_\mathrm{b}$} & \colhead{$T_\mathrm{b}$} & \colhead{$\chi^2_\nu$\tablenotemark{1}} \\
 \colhead{\,} & \colhead{WFC3} & \colhead{Ch. 1} & \colhead{Ch. 2} & \colhead{(9 dof)}}
 \startdata
-		0.06 - 0.15 & 1883 \pm 41 & 1523 \pm 158 & 1589 \pm 98 & 0.7 \\
-		0.15 - 0.25 & 2208 \pm 24 & 2612 \pm 104 & 2299 \pm 78 & 0.9 \\
-		0.25 - 0.35 & 2587 \pm 16 & 2926 \pm 95 & 2592 \pm 67 & 1.5 \\
-		0.35 - 0.44 & 2831 \pm 11 & 2834 \pm 93 & 2976 \pm 61 & 1.5 \\
-		0.44 - 0.56 & 2933 \pm 8 & 2995 \pm 141 & 3154 \pm 48 & 2.8 \\
-		0.56 - 0.65 & 2811 \pm 11 & 2631 \pm 96 & 2891 \pm 63 & 2.0 \\
-		0.65 - 0.75 & 2572 \pm 15 & 2708 \pm 101 & 2421 \pm 78 & 1.3 \\
-		0.75 - 0.85 & 2263 \pm 22 & 1952 \pm 117 & 1939 \pm 83 & 1.3 \\
-		0.85 - 0.94 & 1987 \pm 34 & 1594 \pm 150 & 1288 \pm 118 & 0.6 \\
+0.06 - 0.15 & 1883 \pm 41 & 1523 \pm 153 & 1589 \pm 105 & 0.7 \\
+0.15 - 0.25 & 2208 \pm 33 & 2612 \pm 117 & 2299 \pm 100 & 0.9 \\
+0.25 - 0.35 & 2587 \pm 37 & 2926 \pm 114 & 2592 \pm 96 & 1.5 \\
+0.35 - 0.44 & 2831 \pm 39 & 2834 \pm 111 & 2976 \pm 93 & 1.5 \\
+0.44 - 0.56 & 2933 \pm 41 & 2995 \pm 159 & 3154 \pm 99 & 2.8 \\
+0.56 - 0.65 & 2811 \pm 39 & 2631 \pm 110 & 2891 \pm 97 & 2.0 \\
+0.65 - 0.75 & 2572 \pm 36 & 2708 \pm 117 & 2421 \pm 100 & 1.3 \\
+0.75 - 0.85 & 2263 \pm 33 & 1952 \pm 125 & 1939 \pm 99 & 1.3 \\
+0.85 - 0.94 & 1987 \pm 37 & 1594 \pm 145 & 1288 \pm 118 & 0.6 \\
 \enddata
@@
 		Hot Jupiter & W103b night & 1880 \pm 40 & 3.2 \pm 0.04 & 0.07 \pm 1.8\mathrm{e}-01 & -0.00 \pm 1.6\mathrm{e}-01 \\
-		\, & W103b quadrature & 2400 \pm 20 & 3.2 \pm 0.04 & -0.14 \pm 7.8\mathrm{e}-02 & -0.01 \pm 6.7\mathrm{e}-02 \\
-		\, & W103b dayside & 2930 \pm 10 & 3.2 \pm 0.04 & 0.04 \pm 1.4\mathrm{e}-02 & 0.15 \pm 1.2\mathrm{e}-02 \\
+		\, & W103b quadrature & 2400 \pm 40 & 3.2 \pm 0.04 & -0.14 \pm 7.8\mathrm{e}-02 & -0.01 \pm 6.7\mathrm{e}-02 \\
+		\, & W103b dayside & 2930 \pm 40 & 3.2 \pm 0.04 & 0.04 \pm 1.4\mathrm{e}-02 & 0.15 \pm 1.2\mathrm{e}-02 \\
 		Brown Dwarf & 2MASS J1320+0409 & 1880 \pm 70 & 5.19 \pm 0.16 & 0.21 \pm 6.3\mathrm{e}-04 & -0.06 \pm 5.0\mathrm{e}-04 \\
@@
 	\item{The dayside planet-to-star flux is $0.151\pm0.015\%$, $0.446\pm0.38\%$, and $0.569\pm0.014\%$ in the WFC3 bandpass, \Spitzer\ $3.6$, and \Spitzer\ $4.5\mu$m, respectively.
-The best fit blackbody to the WFC3 dayside spectrum has a brightness temperature of $2930 \pm 10$ K, making WASP-103b among the hottest exoplanets ever observed.}
+The best fit blackbody to the WFC3 dayside spectrum has a brightness temperature of $2930 \pm 40$ K, making WASP-103b among the hottest exoplanets ever observed.}
 	\item{The phase curves have large amplitudes ($0.8 -0.9\times$ the secondary eclipse depth), and small offsets in peak brightness from the substellar point (consistent with zero degrees at all wavelengths).
@@
 The \HST/WFC3 spectra are consistent with  blackbody emission from the planet at all orbital phases.
-The best fit brightness temperatures ranges from $1880\pm40$ K (phase $\phi = 0.1$) to $2930\pm10$ K on the dayside.
+The best fit brightness temperatures ranges from $1880\pm40$ K (phase $\phi = 0.1$) to $2930\pm40$ K on the dayside.
 We attribute the absence of water features at WFC3 wavelengths to (1) H$_2$O dissociation on the dayside and (2) additional near-IR opacity from H-, TiO/VO and FeH.}

### 2018-02-15 ms.tex
relabel figs

--- 2018-02-14 ms.tex
@@
 
+\author{Michael H. Williamson}
+\affiliation{Center of Excellence in Information Systems, Tennessee State University, Nashville, TN 37209, USA}
+
 \author{Keivan Stassun}
@@
 The standard deviation of WASP-103's brightness in each season is given in column~4.
-The mean of the three standard deviations is 0.0058~mag, which is very comparable to the mean standard deviation of the six comparison stars (0.0055~mag).
+The mean of the three standard deviations is 0.0058~mag, which is comparable to the mean standard deviation of the six comparison stars (0.0055~mag).
 To maximize the possibility of detecting WASP-103's rotation, we normalized the photometry such that each observing season has the same mean, thereby removing any long-term variability in WASP-103 and/or the comparison stars (Figure\,\ref{fig:photometry}, top panel).
@@
 \end{figure}
-
 \begin{deluxetable}{ccccc}
@@
 
-\section{Light Curve Fits}
+\section{\HST\ and \Spitzer\ Light Curve Fits}
 \label{sec:fits}
@@
 \begin{figure}
-\includegraphics[width = 0.5\textwidth]{Figures/ellipsoidal.pdf}
+\includegraphics[width = 0.5\textwidth]{Figures/fig2.pdf}
 \caption{Projected area of the planet as a function of orbital phase, normalized to unity at phase zero. The area variation was predicted analytically using the model from \cite{leconte11b}.}
@@
 \begin{figure}
-\includegraphics[width = 0.5\textwidth]{Figures/systematics.pdf}
+\includegraphics[width = 0.5\textwidth]{Figures/fig3.pdf}
 \caption{Raw light curves for WASP-103b observed with \HST/WFC3 (top panel) and \Spitzer/IRAC (bottom two panels).
@@
 \begin{figure}
-\includegraphics[width = 0.5\textwidth]{Figures/rms.pdf}
+\includegraphics[width = 0.5\textwidth]{Figures/fig4.pdf}
 \caption{Root mean square (rms) variability in the light curves as a function of bin size (black lines) compared to the expected rms from photon noise (colored lines).
@@
 \begin{figure*}
-\includegraphics[width = 1.0\textwidth]{Figures/phase_curves_spherical.pdf}
+\includegraphics[width = 1.0\textwidth]{Figures/fig5.pdf}
 \caption{WASP-103b phase curve observations from \HST/WFC3 (top) and \Spitzer/IRAC (middle and bottom).
@@
 \begin{figure*}
-\includegraphics[width = 1.0\textwidth]{Figures/emission_spectra.pdf}
+\includegraphics[width = 1.0\textwidth]{Figures/fig6.pdf}
 \caption{Phase-resolved planet-to-star flux ratios (points) compared to the best fit blackbody (blue line) and the GCM with $\tau_\mathrm{drag4}$.
@@
 \begin{figure*}
-\includegraphics[width = 1.0\textwidth, trim={1.5cm 0 0.5cm 0},clip]{Figures/hst_model_comparison.pdf}
+\includegraphics[width = 1.0\textwidth, trim={1.5cm 0 0.5cm 0},clip]{Figures/fig7.pdf}
 \caption{\textbf{Left:} Fits to the broadband WFC3 phase curve compared to a GCM.
@@
 		1.625 & 0.16 & $ 359 \pm 93 $ & $ 565 \pm 90 $ & $ 1169 \pm 94 $ & $ 1590 \pm 76 $ & $ 1843 \pm 56 $ & $ 1593 \pm 75 $ & $ 1142 \pm 86 $ & $ 542 \pm 91 $ & $ 351 \pm 93 $ \\ 
-		3.6 & 0.17 & $ 1148 \pm 333 $ & $ 3633 \pm 330 $ & $ 4487 \pm 320 $ & $ 4107 \pm 314 $ & $ 4458 \pm 383 $ & $ 3495 \pm 315 $ & $ 3720 \pm 330 $ & $ 2102 \pm 331 $ & $ 1431 \pm 334 $ \\ 
-		4.5 & 0.16 & $ 1586 \pm 220 $ & $ 3468 \pm 214 $ & $ 4188 \pm 190 $ & $ 5334 \pm 179 $ & $ 5686 \pm 138 $ & $ 4904 \pm 183 $ & $ 3626 \pm 214 $ & $ 2575 \pm 217 $ & $ 1057 \pm 221 $ \\ 
+		3.6 & 0.17 & $ 982 \pm 271 $ & $ 3474 \pm 268 $ & $ 4309 \pm 255 $ & $ 4060 \pm 248 $ & $ 4458 \pm 383 $ & $ 3524 \pm 249 $ & $ 3725 \pm 267 $ & $ 1865 \pm 269 $ & $ 1116 \pm 272 $ \\ 
+		4.5 & 0.16 & $ 1560 \pm 220 $ & $ 3347 \pm 213 $ & $ 4150 \pm 189 $ & $ 5240 \pm 178 $ & $ 5686 \pm 138 $ & $ 4995 \pm 181 $ & $ 3677 \pm 212 $ & $ 2403 \pm 213 $ & $ 921 \pm 219 $ \\ 
 		\enddata
 		\tablenotetext{1}{The planet-to-star flux in each phase bin $\phi$ is in units of ppm.}
-		%\vspace{-0.8cm}
 	\end{deluxetable*}
@@
 \begin{figure*}
-\includegraphics[width = 1.0\textwidth]{Figures/twopanel_dayside_spectrum.pdf}
+\includegraphics[width = 1.0\textwidth]{Figures/fig8.pdf}
 \caption{Dayside planet-to-star flux (points) compared to a blackbody model for the planet (dashed gray line) and the best fit 1D model (blue line, with $1\,\sigma$ uncertainty shaded in orange) for the \HST/WFC3 data (left) and Spitzer (right).
@@
 \begin{figure}
-\includegraphics[width = 0.5\textwidth]{Figures/w103b_transmission_spectrum.pdf}
+\includegraphics[width = 0.5\textwidth]{Figures/fig9.pdf}
 \caption{The transmission spectrum of WASP-103b, corrected for planet nightside emission at 1700 K (blue points) and uncorrected (red points).
@@
 \begin{figure}
-\includegraphics[width = 0.5\textwidth]{Figures/xsec_FULL.pdf}
+\includegraphics[width = 0.5\textwidth]{Figures/fig10.pdf}
 \caption{Abundance weighted absorption cross-sections illustrating the important opacity sources at the photospheric pressure and temperature (5 mbar, 3036 K).
@@
 \begin{figure}
-\includegraphics[width = 0.5\textwidth]{Figures/atmosphere_summary.pdf}
+\includegraphics[width = 0.5\textwidth]{Figures/fig11.pdf}
 \caption{Summary of the 1D self-consistent model atmosphere fits to the dayside emission spectrum.
@@
 \begin{figure}
-\includegraphics[width = 0.5\textwidth]{Figures/WASP-103b_grid_DAYSIDE_stair_pairs.pdf}
+\includegraphics[width = 0.5\textwidth]{Figures/fig12.pdf}
 \caption{Posterior distributions for WASP-103b's atmospheric heat redistribution, metallicity, and C/O, from a grid-based fit to the dayside emission spectrum.
@@
 \begin{figure}
-\includegraphics[width = 0.5\textwidth]{Figures/WASP-103b-NoClouds-Drag4-nit-LR-1_4microns.pdf}
+\includegraphics[width = 0.5\textwidth]{Figures/fig13.pdf}
 \caption{TP profiles from the GCM and 1D retrieval, compared to condensation curves of potential cloud species.
@@
 \begin{figure}
-\includegraphics[width = 0.5\textwidth]{Figures/gcm_comparison.pdf}
+\includegraphics[width = 0.5\textwidth]{Figures/fig14.pdf}
 \caption{GCM predictions (colored lines) compared to the best fit spherical harmonics model for the WFC3 white light, \Spitzer\ 3.6, and \Spitzer\ 4.5 micron phase curves (black lines, top to bottom).
@@
 \begin{figure*}
-	\includegraphics[width = 1.0\textwidth]{Figures/GCM_abundances.pdf}
+	\includegraphics[width = 1.0\textwidth]{Figures/fig15.pdf}
 	\caption{Row (1): photospheric temperatures for the $\tau_\mathrm{drag4}$ GCM for different viewing geometries.
@@
 \begin{figure*}
-\includegraphics[width = 1.0\textwidth]{Figures/spectra_comparison.pdf}
+\includegraphics[width = 1.0\textwidth]{Figures/fig16.pdf}
 \caption{Flux-calibrated spectra for WASP-103b (left column) compared to observed spectra for brown dwarfs (middle) and directly imaged companions (right), assuming a distance of 10 pc.
@@
 The data presented in this paper were obtained from the Mikulski Archive for Space Telescopes (MAST) and the NASA/IPAC Infrared Science Archive.
-STScI is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS5-26555.
 The Infrared Science Archive is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration.
@@
 679633).
+G.W.H.
+and M.H.W.
+also acknowledge long-term support from Tennessee State University and the State of Tennessee through its Centers of Excellence Program.
 

### 2018-02-15 Figures/amp_offset_table.py

@@ -1,64 +1,0 @@
-import numpy as np
-
-def weighted_mean(data, err):                #calculates the weighted mean for data points data with variances err
-    weights = 1.0/err
-    mu = np.sum(data*weights)/np.sum(weights)
-    var = 1.0/np.sum(weights)
-    return [mu, var]                #returns weighted mean and variance
-
-d = np.genfromtxt("WFC3_amplitudes_offsets.txt")
-#columns: 1) phase shift, 2-3)phase shift err, 4) amp, 5-6) amp err, 7) fpfs, 8-9) fpfs_err
-
-off, off_err = -1.*d[:,1]*180./np.pi, (d[:,2]+ d[:,3])/2.*180./np.pi
-amp, amp_err = d[:,4], (d[:,5]+d[:,6])/2.
-
-fpfs, fpfs_err = d[:,7], (d[:,8]+d[:,9])/2.
-wave = np.linspace(1.175, 1.625, 10)
-
-amp, amp_err = weighted_mean(amp, amp_err) 
-off, off_err = weighted_mean(off, off_err)
-
-gcm_wfc3 = np.genfromtxt("gcm_amp_off_wfc3.txt")
-models = ["nominal GCM", "[M/H] = 0.5 GCM", "$\\tau_\mathrm{drag4}$ GCM", "$\\tau_\mathrm{drag3}$ GCM"]
-
-print "\\begin{deluxetable}{llLL}"
-print "\\tablecolumns{4}"
-print "\\tablewidth{0pt}:"
-print "\\tablecaption{Phase Curve Properties \label{table:amps_offsets}}"
-print "\\tablehead{"
-print "\colhead{Bandpass} & \colhead{Source} & \colhead{Amplitude} & \colhead{Offset)}\\\\"
-print "\colhead{\,} & \colhead{\,} & \colhead{\,} & \colhead{(Degrees)}}"
-print "\startdata"
-
-#WFC3
-print "WFC3", "&", "data", "&",  '{0:0.2f}'.format(amp), "\\pm", '{0:0.2f}'.format(amp_err), "&", '{0:0.1f}'.format(off), "\\pm", '{0:0.1f}'.format(off_err),  "\\\\"
-
[…]

### 2018-02-15 Figures/dayside_espec.py

@@ -1,139 +1,0 @@
-import numpy as np
-import pickle
-import matplotlib.pyplot as plt
-import os, glob
-from lc_fit import Model, LightCurveData
-#import read_spectra_from_Vivien as rs
-import matplotlib.gridspec as gridspec
-from pylab import *
-from matplotlib import rc
-import spiderman_lc
-from matplotlib import ticker
-import seaborn as sns
-from astropy.convolution import Gaussian1DKernel, convolve
-
-sns.set_context("paper", font_scale=1.2)
-sns.set_style("white")
-sns.set_style("ticks", {"xtick.direction":"in", "ytick.direction":"in"})
-
-
-rc('font',**{'family':'sans-serif','sans-serif':['Arial']})
-
-def blackbody(l,T): 
-	h = 6.62607e-34   #J/s
-        c = 2.997925e8       #m/s
-        k = 1.38065e-23     #J/K
-        return 2*h*c**2/(l**5*(np.exp(h*c/(l*k*T))-1))                 #[W/sr/m^3]
-
-def best_fit_bb(w, y, e, rprs):
-	#Ts = np.linspace(2900., 3100, 100)
-	Ts = np.linspace(2800, 4200, 10000)
-	chibest = 10000.
-	Tbest = 0.	
-	Tstar = 6110.
-	w = np.array(w)
-
-	w, y, e, = w[0:10], y[0:10], e[0:10]        #wfc3
-	#w, y, e, = w[10], y[10], e[10]              #spitzer Ch 1
-	#w, y, e, = w[11], y[11], e[11]              #Spitzer Ch 2
-	#get stellar spectrum
-	#star = np.genfromtxt("wasp103_sed_fluxes.out")
-	#star_bb = np.interp(w, star[:,0], star[:,1])*1.e24/(w*np.pi*4.)
-
-        g = Gaussian1DKernel(stddev=150)
-        star = np.genfromtxt("W103-6110K-1.22Ms-1.22Rs.dat")       #W/m2/micron (column 1)
-	star_bb = np.interp(w, star[:,0], convolve(star[:,1]*22423.,g))
-
-
-	outliers = 0.
-        chis = []
-
-	for T in Ts:
-		model = (np.pi/1.e6)*blackbody(w*1.0e-6, T)/star_bb*rprs**2
-		chi2 = np.sum((y - model)**2/e**2)
[…]

### 2018-02-15 Figures/fig14_gcm_comparison.py

@@ -1,0 +1,219 @@
+import matplotlib.pyplot as plt
+import numpy as np
+import os, glob
+from lc_fit import Model, LightCurveData
+import pickle
+import seaborn as sns
+from scipy.interpolate import interp1d
+
+sns.set_context("paper")
+sns.set_style("white")
+sns.set_style("ticks", {"xtick.direction":"in", "ytick.direction":"in"})
+
+gcm_path = "./Vivien_models2"
+gcms = glob.glob(os.path.join(gcm_path, "PC*PT.dat"))
+
+labels = ["$\\tau_\mathrm{drag} = 10^4$ s", "$\\tau_\mathrm{drag} = 10^3$ s", "[Fe/H] = 0.5", "nominal GCM"]
+colors = ["#be0119", "#f97306", "#6dedfd", "#0165fc"]
+ls = [":", "--", "-.", "-"]
+
+plt.figure(figsize = (4, 6))
+
+
+
+def proj_area(phi, inc):
+        R0 = 1.07e8             #planet radius in m
+        p = 0.00117             # planet-to-star mass ratio
+        r = 2.9695e9            #orbital separation in m
+        kn = 0.653              #from table B5 of Leconte et al. 2011
+        n = 1.005
+        qn = kn*(1.- n/5.)      #n 
+
+
+        alpha1 = 2.5*qn*R0**3/(p*r**3)
+        alpha2 = -1.25*qn*R0**3/(p*r**3)
+        alpha3 = alpha2
+
+        a1 = R0*(1+alpha1)
+        a2 = R0*(1+alpha2)
+        a3 = R0*(1+alpha3)
+
+        return  np.sqrt(a3**2*np.sin(inc)**2*(a1**2*np.sin(phi)**2+a2**2*np.cos(phi)**2)+ a1**2*a2**2*np.cos(inc)**2)/(a2*a3)
+
+
+plt.subplot(311)
+inc = 1.523
+correction_factor = 1.099  # = (0.1146/0.1093)**2, ratio of correct transit depth to what Vivien used (which was from the discovery paper and not corrected for stellar contamination)
+
+#plot gcms
+for i, g in enumerate(gcms):
+    print g,
+    model = np.genfromtxt(g, delimiter = ',') 
+    phi = model[:,0]/360.*2.*np.pi
+    area = proj_area(phi, inc)
[…]

### 2018-02-15 Figures/fig16_spectra_comparison.py

@@ -1,0 +1,212 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib.gridspec as gridspec
+from astropy import modeling
+import seaborn as sns
+
+sns.set_context("paper")
+sns.set_style("white")
+sns.set_style("ticks", {"xtick.direction":"in", "ytick.direction":"in"})
+
+def weighted_mean(data, err):                #calculates the weighted mean for data points data with variances err
+        weights = 1.0/err
+        mu = np.sum(data*weights)/np.sum(weights)
+        var = 1.0/np.sum(weights)
+        return [mu, var]                #returns weighted mean and variance
+
+def get_blackbody_model(model_w, data_w, data, T):
+    unit_conversion = 1.2533e19                                        #(10 pc/jupiter radius)^2
+
+    model = modeling.blackbody.blackbody_lambda(model_w*1.e4, T)       #wavelength in angstroms
+    model = model*4.*np.pi*1.e4*model_w/unit_conversion/np.pi          #multiplies by 4 pi steradians * 10000. angstroms/micron * micron
+    #see chapter 1 of Rybicki & Lightman about the factor of pi to convert bb intensity to flux!
+    scale = rescale(data_w, data, model_w, model)                                #rescales model to account for uncertainty in radius of the object
+    return  model*scale
+    
+
+def rescale(data_w, data, model_w, model):
+    model = np.interp(data_w, model_w, model)
+    ind = (data > 1.e-20)
+    data_w, data, model = data_w[ind], data[ind], model[ind]
+    scale = np.linspace(0.05, 15, 1000.)
+    chi2best, scalebest = 1.e10, -1.
+    for s in scale:
+        chi2 = np.sum((data - model*s)**2)
+        if chi2 < chi2best:
+                chi2best = chi2
+                scalebest = s
+    return scalebest 
+
+gs = gridspec.GridSpec(3, 3, hspace=0.1, wspace=0.3)
+
[…]

### 2018-02-15 Figures/fig2_ellipsoidal.py

@@ -1,0 +1,46 @@
+import numpy as np
+from matplotlib import rc
+import matplotlib.pyplot as plt
+import seaborn as sns
+sns.set_context("talk")
+sns.set_style("white")
+sns.set_style("ticks", {"xtick.direction":"in", "ytick.direction":"in"})
+
+rc('font',**{'family':'sans-serif','sans-serif':['Arial']})
+
+plt.figure(figsize=(6,3))
+
+def proj_area(phi, inc):
+        R0 = 1.07e8             #planet radius in m
+        p = 0.00117             # planet-to-star mass ratio
+        r = 2.9695e9            #orbital separation in m
+        kn = 0.653              #from table B5 of Leconte et al. 2011
+        n = 1.005
+        qn = kn*(1.- n/5.)      #n 
+
+
+        alpha1 = 2.5*qn*R0**3/(p*r**3)
+        alpha2 = -1.25*qn*R0**3/(p*r**3)
+        alpha3 = alpha2
+
+        a1 = R0*(1+alpha1)
+        a2 = R0*(1+alpha2)
+        a3 = R0*(1+alpha3)
+
+        return  np.sqrt(a3**2*np.sin(inc)**2*(a1**2*np.sin(phi)**2+a2**2*np.cos(phi)**2)+ a1**2*a2**2*np.cos(inc)**2)/(a2*a3)
+
+
+phi = np.linspace(0., 2.*np.pi, 1000)
+inc = 1.523
+
+area = proj_area(phi, inc)
+
+plt.plot(phi/(2.*np.pi), area)
+
+plt.xlabel("Orbital phase") 
+plt.ylabel("Relative area")
+
+plt.xlim(0,1)
+plt.tight_layout()
+plt.savefig("fig2.pdf")
+plt.show()

### 2018-02-15 Figures/fig3_systematics.py

@@ -1,0 +1,158 @@
+import pickle
+from astropy.io import ascii
+import matplotlib.gridspec as gridspec
+from pylab import *
+from matplotlib import rc
+import transit_lc
+import seaborn as sns
+from lc_fit import Model, LightCurveData
+import os, glob
+sns.set_context("talk", font_scale = 1.0)
+sns.set_style("white")
+sns.set_style("ticks", {"xtick.direction":"in", "ytick.direction":"in"})
+
+rc('font',**{'family':'sans-serif','sans-serif':['Arial']})
+
+gs = gridspec.GridSpec(3, 1, height_ratios =[1,1, 1],  hspace=0.00)
+
+# plots HST white light phase curve
+#bestfits = ["./WFC3_best_fits/old_white_fits/bestfit_zhang_allsys.pic"]
+bestfits = ["./WFC3_best_fits/bestfit_zhang_allsys.pic"]
+
+alpha = 0.7
+ms = 5
+
+plt.figure(figsize = (5, 7))
+
+for ii, f in enumerate(bestfits):
+	ax = plt.subplot(gs[ii, 0])
+
+	p = pickle.load(open(f, 'rb'))
+	d, m, par = p[0], p[1], p[2]		#stores data,  model, and best fit parameters into d, m, & par
+	
+	dilution = d.dilution + 1.
+
+	ind = d.err < 9.0e7			#indices of outliers
+	
+	err = d.err[ind]/d.flux[ind]		#normalized per point uncertainty 
+	phase = m.phase[ind]
+	data_corr = m.data_corr[ind]
+	allsys = m.lc[ind]	
+	t = d.time[ind]
+	visit_sys = m.all_sys[ind]
+
+	print "WFC3 white: obs, exp rms (ppm)", np.std(m.resid[ind]/d.flux[ind])*1e6, np.sqrt(1./np.median(d.flux[ind]))*1e6
+
+	scan = np.ones_like(phase)
+	scan[d.scan_direction == 0] = 1. + par[d.par_order['scale']*d.nvisit]
+	delta = 1. + par[d.par_order['scale']*d.nvisit]
+
+	ind = d.vis_num == 0
+	offset = 0.
+
[…]

### 2018-02-15 Figures/fig5_phase_curves.py

@@ -1,0 +1,197 @@
+import matplotlib.pyplot as plt
+import numpy as np
+import pickle
+from astropy.io import ascii
+import matplotlib.gridspec as gridspec
+from pylab import *
+from matplotlib import rc
+import spiderman_spherical
+import transit_lc
+from lc_fit import Model, LightCurveData
+import spiderman
+
+rc('font',**{'family':'sans-serif','sans-serif':['Arial']})
+
+def quantile(x, q):
+        return np.percentile(x, 100. * q)
+
+plt.figure(figsize = (7.5,4.5))
+
+gs = gridspec.GridSpec(3, 2, hspace=0.1, wspace = 0.05)
+
+# plots HST white light phase curve
+#bestfits = ["./WFC3_best_fits/old_white_fits/bestfit_spherical.pic"]
+bestfits = ["./WFC3_best_fits/bestfit_spherical.pic"]
+
+phasebins = np.linspace(0., 1., 30)
+nbins = len(phasebins) - 1
+
+every_N = 10000
+
+for ii, f in enumerate(bestfits):
+	ax = plt.subplot(gs[ii, 0])
+
+	p = pickle.load(open(f, 'rb'))
+	d, m, par = p[0], p[1], p[2]		#stores data,  model, and best fit parameters into d, m, & par
+	
+	dilution = d.dilution + 1.
+
+
+	ind = d.err < 9.0e7			#indices of outliers
+	
+	err = d.err[ind]/d.flux[ind]		#normalized per point uncertainty 
+	phase = m.phase[ind]
+	data_corr = m.data_corr[ind]
+	bestfit = m.bestfit[ind]
+
+        print dilution
+
+	ind = np.argsort(phase)
+	err, phase, data_corr, bestfit = err[ind], phase[ind], data_corr[ind], bestfit[ind] #sorts by phase
+	
+	bindata = np.zeros(nbins)
+	binsigma = np.zeros(nbins)
+	binbestfit = np.zeros(nbins)
+	bin_average = np.zeros(nbins)
+	
+	for j in range(1, len(phasebins)):
[…]

### 2018-02-15 Figures/fig6_emission_spectra.py

@@ -1,0 +1,287 @@
+import pickle
+import numpy as np
+import matplotlib.pyplot as plt
+import os, glob
+from lc_fit import Model, LightCurveData
+#import read_spectra_from_Vivien as rs
+import matplotlib.gridspec as gridspec
+from pylab import *
+from matplotlib import rc, ticker
+import seaborn as sns
+from astropy.convolution import Gaussian1DKernel, convolve
+import scipy.stats as st
+
+sns.set_context("notebook", font_scale = 1.5)
+sns.set_style("white")
+sns.set_style("ticks", {"xtick.direction":"in", "ytick.direction":"in"})
+
+rc('font',**{'family':'sans-serif','sans-serif':['Arial']})
+
+def get_significance(chisq, dof):
+        alpha = (1. - st.chi2.cdf(chisq, dof))/2.
+        z = st.norm.ppf(1.-alpha)
+        return z
+
+def blackbody(l,T): 
+	h = 6.62607e-34   #J/s
+        c = 2.997925e8       #m/s
+        k = 1.38065e-23     #J/K
+        return 2*h*c**2/(l**5*(np.exp(h*c/(l*k*T))-1))                 #[W/sr/m^3]
+
+def best_fit_bb(w, y, e, rprs):
+    Ts = np.linspace(1000, 3600, 10000)
+    chibest = 10000.
+    Tbest = 0.  
+    Tstar = 6110.
+    resid = 0.
+
+    w = np.array(w)
+
+    w, y, e = w[0:10], y[0:10], e[0:10]     #WFC3 data only
+    #w, y, e = w[10], y[10], e[10]           #spitzer ch1
+    #w, y, e = w[11], y[11], e[11]           #spitzer ch2
+
+    #get stellar spectrum
+    g = Gaussian1DKernel(stddev=100)
+    star = np.genfromtxt("W103-6110K-1.22Ms-1.22Rs.dat")       #W/m2/micron (column 1)
+    star_bb = np.interp(w, star[:,0], convolve(star[:,1]*22423.,g))
+    #star = np.genfromtxt("wasp103_sed_fluxes.out")
+    #star_bb = np.interp(w, star[:,0], star[:,1])*1.e24/(w*np.pi*4.)
+    chis = []
+
+    for T in Ts:
[…]

### 2018-02-15 Figures/fit_table_no_aic.py

@@ -1,115 +1,0 @@
-import numpy as np
-from lc_fit import Model, LightCurveData
-import pickle 
-
-#get Spitzer AIC/BIC values from results.txt 
-
-#zhang, hotspot, spherical, sincos
-ch1_chi2 = np.array([0.9, 0.9, 0.9, 0.9])
-ch1_aic = np.array([7075.1, 7058.5, 7040.9, 7044.7])
-ch1_bic = np.array([7131.1, 7107.4, 7096.7, 7121.4])
-
-
-ch2_chi2 = np.array([1.1, 1.1, 1.1, 1.1])
-ch2_aic = np.array([8666.2, 8657.9, 8653.3, 8645.4])
-ch2_bic = np.array([8722.0, 8706.8, 8709.1, 8729.1])
-
-
-# bset fits for WFC3
-wfc3_chi2 = []
-wfc3_aic = []
-wfc3_bic = []
-
-models = ["zhang", "hotspot_t", "spherical", "sincos"]
-path = "WFC3_best_fits/"
-for i, model in enumerate(models):
-	p = pickle.load(open(path+"bestfit_"+model+".pic", "rb")) 
-
-	d, m, par = p[0], p[1], p[2]            #stores data,  model, and best fit parameters into d, m, & par
-	wfc3_chi2.append(m.chi2red)
-	wfc3_bic.append(m.chi2 + d.nfree_param*np.log(d.npoints))
-	wfc3_aic.append(m.chi2 + 2.*d.nfree_param)
-#	print m.chi2red, bic, aic
-
-wfc3_chi2 = np.array(wfc3_chi2)
-wfc3_aic = np.array(wfc3_aic)
-wfc3_bic = np.array(wfc3_bic)
-
-#Temperatures:
-#HST:
-#from get_mean_daynight_temp.py 
-#zhang daymu, nightmu, min, max 2769.87230395 1976.73242901 1976.73242901 3953.15696275
-#hotspot_t daymu, nightmu, min, max 2850.06092942 0.0 0.0 2878.84942366
-#spherical daymu, nightmu, min, max 2635.76098954 1822.86068583 1227.05643006 3237.85099673
-wfc3_tmin = np.array([1977, 0, 1227, 0])
-wfc3_tmax = np.array([3953, 2879, 3237, 0])
-wfc3_daymu = np.array([2769, 2879, 2636, 0])
[…]

### 2018-02-15 Figures/proj_area.py

@@ -1,46 +1,0 @@
-import numpy as np
-from matplotlib import rc
-import matplotlib.pyplot as plt
-import seaborn as sns
-sns.set_context("talk")
-sns.set_style("white")
-sns.set_style("ticks", {"xtick.direction":"in", "ytick.direction":"in"})
-
-rc('font',**{'family':'sans-serif','sans-serif':['Arial']})
-
-plt.figure(figsize=(6,3))
-
-def proj_area(phi, inc):
-        R0 = 1.07e8             #planet radius in m
-        p = 0.00117             # planet-to-star mass ratio
-        r = 2.9695e9            #orbital separation in m
-        kn = 0.653              #from table B5 of Leconte et al. 2011
-        n = 1.005
-        qn = kn*(1.- n/5.)      #n 
-
-
-        alpha1 = 2.5*qn*R0**3/(p*r**3)
-        alpha2 = -1.25*qn*R0**3/(p*r**3)
-        alpha3 = alpha2
-
-        a1 = R0*(1+alpha1)
-        a2 = R0*(1+alpha2)
-        a3 = R0*(1+alpha3)
-
-        return  np.sqrt(a3**2*np.sin(inc)**2*(a1**2*np.sin(phi)**2+a2**2*np.cos(phi)**2)+ a1**2*a2**2*np.cos(inc)**2)/(a2*a3)
-
-
-phi = np.linspace(0., 2.*np.pi, 1000)
-inc = 1.523
-
-area = proj_area(phi, inc)
-
-plt.plot(phi/(2.*np.pi), area)
-
-plt.xlabel("Orbital phase") 
-plt.ylabel("Relative area")
-
-plt.xlim(0,1)
-plt.tight_layout()
-plt.savefig("ellipsoidal.pdf")
-plt.show()

### 2018-02-15 Figures/table3_spectra.py

@@ -1,0 +1,168 @@
+import pickle
+import numpy as np
+import matplotlib.pyplot as plt
+import os, glob
+import pickle
+from lc_fit import Model, LightCurveData
+
+
+path  = "WFC3_best_fits/spec_fits/"		#zhang model
+files = glob.glob(os.path.join(path, "bestfit*.pic"))		
+
+#phasebins = np.linspace(0.06, 0.44, 5)
+#phasebins2 = np.linspace(0.56, 0.94, 5)
+
+phasebins = np.array([0.06, 0.15, 0.25, 0.35, 0.44])
+phasebins2 = np.array([0.56, 0.65, 0.75, 0.85, 0.94]) 
+
+phasebins = np.append(phasebins, 0.5)
+phasebins = np.append(phasebins, phasebins2)
+
+nspitz_chan = 2
+spectra = np.zeros((len(files) + nspitz_chan, len(phasebins)-1, 2))
+phases = np.zeros(len(phasebins) -1 )
+waves, dilution = [], []
+i = 0
+
+for f in files:
+	p = pickle.load(open(f, 'rb'))
+	d, m = p[0], p[1]			#stores data and model into d & m
+	
+	waves.append(d.wavelength)
+	dilution.append(d.dilution)
+
+	ind = d.err < 9.0e7			#indices of outliers
+	
+	err = d.err[ind]/d.flux[ind]		#normalized per point uncertainty 
+	phase = m.phase[ind]
+	data_corr = m.data_corr[ind]
+
+	for j in range(1, len(phasebins)):
+		#calculates uncertainty for in-eclipse points
+		ind1 = (phase>=0.45)&(phase<=0.55)
+		sig1 = np.sqrt(np.sum(err[ind1]**2)/sum(ind1)**2)
+
+		#calculates uncertainty for phase bin
+		ind2 = (phase >= phasebins[j-1]) & (phase < phasebins[j])
+		sig2 = np.sqrt(np.sum(err[ind2]**2)/sum(ind2)**2)
+
+		spectra[i, j-1, 0] = np.mean(data_corr[ind2])
+		spectra[i, j-1, 1] = np.sqrt(sig1**2 + sig2**2)		#quadrature add uncertainties from baseline and bin 
+		phases[j-1] = (phasebins[j] + phasebins[j-1])/2.
+
+	i += 1
+
+#add Spitzer Ch 1
[…]

### 2018-02-15 Figures/table5_transmission_spectrum.py

@@ -1,0 +1,23 @@
+import numpy as np
+
+#made the file teffs.txt based on output from phased_espec.py
+t0 = np.genfromtxt("tspec_tnight0.txt")
+t1700 = np.genfromtxt("tspec_tnight1700.txt")
+
+
+print "\\begin{deluxetable}{LLL}"
+print "\\tablecolumns{3}"
+print "\\tablewidth{0pt}"
+print "\\tablecaption{WASP-103b Transmission Spectrum\label{table:tspec}}"
+print "\\tablehead{"
+print "\colhead{Wavelength} & \colhead{Transit Depth (\%)} & \colhead{Transit Depth (\%)} \\\\"
+print "\colhead{(micron)} & \colhead{($T_\mathrm{night} = 0$ K)} & \colhead{($T_\mathrm{night} = 1700$ K)}}"
+print "\startdata"
+
+for i in range(len(t0)): print t0[i,0],  "&", '{0:0.6f}'.format(100.*t0[i,1]), "\\pm", '{0:0.6f}'.format(t0[i,2]), "&", '{0:0.6f}'.format(t1700[i,1]), "\\pm", '{0:0.6f}'.format(t1700[i,2]),  "\\\\"
+
+print "\enddata"
+print "\\vspace{-0.8cm}"
+print "\\tablecomments{comments}"
+print "\end{deluxetable}"
+

### 2018-02-15 Figures/table6_brightness_temps.py

@@ -1,0 +1,35 @@
+import numpy as np
+
+#made the file teffs.txt based on output from phased_espec.py
+teffs = np.genfromtxt("teffs.txt")
+teffs_s1 = np.genfromtxt("teffs_ch1.txt")
+teffs_s2 = np.genfromtxt("teffs_ch2.txt")
+
+print "\\begin{deluxetable}{LLLLL}"
+print "\\tablecolumns{5}"
+print "\\tablewidth{0pt}"
+print "\\tablecaption{Phase-resolved Brightness Temperatures \label{table:teffs}}"
+print "\\tablehead{"
+print "\colhead{Orbital Phase} & \colhead{$T_\mathrm{b}$} & \colhead{$T_\mathrm{b}$} & \colhead{$T_\mathrm{b}$} & \colhead{$\chi^2_\\nu$} \\\\"
+print "\colhead{\,} & \colhead{WFC3} & \colhead{Ch. 1} & \colhead{Ch. 2} & \colhead{(9 dof)}}"
+print "\startdata"
+
+T = teffs[:,0]
+err = teffs[:,1]
+chi2 = teffs[:,2]
+phase = teffs[:,3]
+phase1 = np.array([0.06, 0.15, 0.25, 0.35, 0.44, 0.56, 0.65, 0.75, 0.85])
+phase2 = np.array([0.15, 0.25, 0.35, 0.44, 0.56, 0.65, 0.75, 0.85, 0.94])
+
+T1 = teffs_s1[:,0]
+err1 = teffs_s1[:,1]
+T2 = teffs_s2[:,0]
+err2 = teffs_s2[:,1]
+
+for i in range(len(teffs)): print phase1[i], "-", phase2[i],  "&", int(T[i]), "\\pm", int(err[i]), "&", int(T1[i]), "\\pm", int(err1[i]), "&", int(T2[i]), "\\pm", int(err2[i]), "&", chi2[i],  "\\\\"
+
+print "\enddata"
+print "\\vspace{-0.8cm}"
+print "\\tablecomments{comments}"
+print "\end{deluxetable}"
+

### 2018-02-15 Figures/teffs_table.py

@@ -1,35 +1,0 @@
-import numpy as np
-
-#made the file teffs.txt based on output from phased_espec.py
-teffs = np.genfromtxt("teffs.txt")
-teffs_s1 = np.genfromtxt("teffs_ch1.txt")
-teffs_s2 = np.genfromtxt("teffs_ch2.txt")
-
-print "\\begin{deluxetable}{LLLLL}"
-print "\\tablecolumns{5}"
-print "\\tablewidth{0pt}"
-print "\\tablecaption{Phase-resolved Brightness Temperatures \label{table:teffs}}"
-print "\\tablehead{"
-print "\colhead{Orbital Phase} & \colhead{$T_\mathrm{b}$} & \colhead{$T_\mathrm{b}$} & \colhead{$T_\mathrm{b}$} & \colhead{$\chi^2_\\nu$} \\\\"
-print "\colhead{\,} & \colhead{WFC3} & \colhead{Ch. 1} & \colhead{Ch. 2} & \colhead{(9 dof)}}"
-print "\startdata"
-
-T = teffs[:,0]
-err = teffs[:,1]
-chi2 = teffs[:,2]
-phase = teffs[:,3]
-phase1 = np.array([0.06, 0.15, 0.25, 0.35, 0.44, 0.56, 0.65, 0.75, 0.85])
-phase2 = np.array([0.15, 0.25, 0.35, 0.44, 0.56, 0.65, 0.75, 0.85, 0.94])
-
-T1 = teffs_s1[:,0]
-err1 = teffs_s1[:,1]
-T2 = teffs_s2[:,0]
-err2 = teffs_s2[:,1]
-
-for i in range(len(teffs)): print phase1[i], "-", phase2[i],  "&", int(T[i]), "\\pm", int(err[i]), "&", int(T1[i]), "\\pm", int(err1[i]), "&", int(T2[i]), "\\pm", int(err2[i]), "&", chi2[i],  "\\\\"
-
-print "\enddata"
-print "\\vspace{-0.8cm}"
-print "\\tablecomments{comments}"
-print "\end{deluxetable}"
-

### 2018-02-15 Figures/tspec_table.py

@@ -1,23 +1,0 @@
-import numpy as np
-
-#made the file teffs.txt based on output from phased_espec.py
-t0 = np.genfromtxt("tspec_tnight0.txt")
-t1700 = np.genfromtxt("tspec_tnight1700.txt")
-
-
-print "\\begin{deluxetable}{LLL}"
-print "\\tablecolumns{3}"
-print "\\tablewidth{0pt}"
-print "\\tablecaption{WASP-103b Transmission Spectrum\label{table:tspec}}"
-print "\\tablehead{"
-print "\colhead{Wavelength} & \colhead{Transit Depth (\%)} & \colhead{Transit Depth (\%)} \\\\"
-print "\colhead{(micron)} & \colhead{($T_\mathrm{night} = 0$ K)} & \colhead{($T_\mathrm{night} = 1700$ K)}}"
-print "\startdata"
-
-for i in range(len(t0)): print t0[i,0],  "&", '{0:0.6f}'.format(100.*t0[i,1]), "\\pm", '{0:0.6f}'.format(t0[i,2]), "&", '{0:0.6f}'.format(t1700[i,1]), "\\pm", '{0:0.6f}'.format(t1700[i,2]),  "\\\\"
-
-print "\enddata"
-print "\\vspace{-0.8cm}"
-print "\\tablecomments{comments}"
-print "\end{deluxetable}"
-

### 2018-02-15 Figures/two_panel_dayside_espec.py

@@ -1,165 +1,0 @@
-import numpy as np
-import pickle
-import matplotlib.pyplot as plt
-import os, glob
-from lc_fit import Model, LightCurveData
-#import read_spectra_from_Vivien as rs
-import matplotlib.gridspec as gridspec
-from pylab import *
-from matplotlib import rc
-import spiderman_lc
-from matplotlib import ticker
-import seaborn as sns
-from astropy.convolution import Gaussian1DKernel, convolve
-import scipy.stats as st
-
-sns.set_context("paper", font_scale=1.2)
-sns.set_style("white")
-sns.set_style("ticks", {"xtick.direction":"in", "ytick.direction":"in"})
-
-
-rc('font',**{'family':'sans-serif','sans-serif':['Arial']})
-
-def get_significance(chisq, dof):
-        alpha = (1. - st.chi2.cdf(chisq, dof))/2.
-        z = st.norm.ppf(1.-alpha)
-        return z
-
-def blackbody(l,T): 
-	h = 6.62607e-34   #J/s
-        c = 2.997925e8       #m/s
-        k = 1.38065e-23     #J/K
-        return 2*h*c**2/(l**5*(np.exp(h*c/(l*k*T))-1))                 #[W/sr/m^3]
-
-def best_fit_bb(w, y, e, rprs):
-	Ts = np.linspace(2900., 3500, 10000)
-	chibest = 10000.
-	Tbest = 0.	
-	Tstar = 6110.
-	w = np.array(w)
-
-	w, y, e, = w[0:10], y[0:10], e[0:10]
-	#w, y, e, = w[10], y[10], e[10]              #spitzer Ch 1
-	#w, y, e, = w[11], y[11], e[11]              #Spitzer Ch 2
-
-	#get stellar spectrum
-	#star = np.genfromtxt("wasp103_sed_fluxes.out")
-	#star_bb = np.interp(w, star[:,0], star[:,1])*1.e24/(w*np.pi*4.)
-
-        g = Gaussian1DKernel(stddev=150)
-        star = np.genfromtxt("W103-6110K-1.22Ms-1.22Rs.dat")       #W/m2/micron (column 1)
-	star_bb = np.interp(w, star[:,0], convolve(star[:,1]*22423.,g))
-
-	outliers = 0.
-        chis = []
-
[…]

### 2018-02-15 ms.tex
edits

@@
 This observation is sensitive to different longitudes at each orbital phase of the planet.
-The first phase curve of an exoplanet was observed with \Spitzer\ for the hot Jupiter HD 189733b by \cite{knutson07}, followed by additional \Spitzer\ observations for about a dozen more systems \citep[cataloged in][]{parmentier17}.
+The first phase curve of an exoplanet was observed with \Spitzer\ for the hot Jupiter HD 189733b by \cite{harrington06}, followed by additional \Spitzer\ observations for about a dozen more systems \citep[cataloged in][]{parmentier17}.
 The observations revealed large day-night temperature contrasts (in excess of 300 K), and eastward shifted peak brightness due to heat circulation, as predicted by 3D models \citep{showman02}.
@@
 	\tablehead{
-	\colhead{Observing} & \colhead{} & \colhead{Date Range} &
+		\colhead{Observing} & \colhead{$N_{obs}$} & \colhead{Date Range} &
 	\colhead{Sigma} & \colhead{Seasonal Mean} \\
-		& \colhead{\,} & \colhead{\,} & \colhead{(mag)} & \colhead{(mag)}}
+	\colhead{Season} &  \colhead{\,} & \colhead{(HJD-2,400,000)} & \colhead{(mag)} & \colhead{(mag)}}
 	\startdata
@@
 
-We calculated the planet-to-star flux $F_p/F_s$ in two different ways.
+We modeled the planet-to-star flux $F_p/F_s$ in two different ways.
 First, we fit a sinusoid with a period equal to the planet's orbital period.

### 2018-02-15 ms.tex

@@
 We compare the phase curves to 3D general circulation models and find that atmospheric drag with a timescale of $10^4$ s is the best match to the data, suggesting the presence of a magnetic field with strength $\sim1$ Gauss.
+We also compare the WASP-103b spectra to brown dwarfs and young directly imaged companions and find these more massive and self-luminous objects have significantly larger water features, indicating that surface gravity and irradiation environment play an important role in shaping the spectra of hot Jupiters.
+These results highlight the 3D structure of exoplanet atmospheres and illustrate the importance of phase curve observations for understanding their complex chemistry and physics.
+=======
+	We present thermal phase curve measurements for the hot Jupiter WASP-103b observed with \emph{Hubble}/WFC3 and \emph{Spitzer}/IRAC.
+The dayside planet-to-star flux ratio is $0.151\pm0.015\%$, $0.446\pm0.038\%$, and $0.569\pm0.014\%$ in bandpasses centered at $1.4$, $3.6$, and $4.5\mu$m, respectively.
+The phase curves have large amplitudes and negligible hotspot offsets, indicative of poor heat redistribution to the nightside.
+We fit the phase variation with a range of climate maps and find that a spherical harmonics model generally provides the best fit.
+The phase-resolved spectra are consistent with blackbodies in the WFC3 bandpass, with brightness temperatures ranging from $1880\pm40$ K on the nightside to $2930 \pm 40$ K on the dayside.
+The dayside spectrum has a significantly higher brightness temperature in the \Spitzer\ bands, which we attribute to CO emission and a thermal inversion.
+The inversion is not present on the nightside.
+The transmission spectrum is featureless, but consistent with the small features expected from cloud-free models.
+Using the dayside and nightside emission spectra, we retrieved the atmospheric composition with a 1D self-consistent modeling technique and find the atmosphere is moderately metal-enriched ($\mathrm{[M/H]} =  23^{+29}_{-13}\times$ solar) and the carbon-to-oxygen ratio is below 0.9 at $3\,\sigma$ confidence.
+In contrast to cooler hot Jupiters, we do not detect significant water absorption, which we attribute to partial H$_2$O dissociation and additional opacity from H- and trace amounts of hydrides/oxides.
+We compare the phase curves to 3D general circulation models and find that atmospheric drag with a timescale of $10^4$\,s is the best match to the data, suggesting the presence of a magnetic field with strength $\sim1$ Gauss.
 We also compare the WASP-103b spectra to brown dwarfs and young directly imaged companions and find these more massive and self-luminous objects have significantly larger water features, indicating that surface gravity and irradiation environment play an important role in shaping the spectra of hot Jupiters.

### 2018-02-15 ms.tex
final

@@
 \author{Vivien Parmentier}
-\affiliation{Aix Marseille Univ, CNRS, LAM, Laboratoire d’Astrophysique de Marseille, Marseille, France}
+\affiliation{Aix Marseille Univ, CNRS, LAM, Laboratoire d'Astrophysique de Marseille, Marseille, France}
 
@@
 	We present thermal phase curve measurements for the hot Jupiter WASP-103b observed with \emph{Hubble}/WFC3 and \emph{Spitzer}/IRAC.
-The dayside planet-to-star flux ratio is $0.151\pm0.015\%$, $0.446\pm0.038\%$, and $0.569\pm0.014\%$ in bandpasses centered at $1.4$, $3.6$, and $4.5\mu$m, respectively.
+The dayside planet-to-star flux ratios are $0.151\pm0.015\%$, $0.446\pm0.038\%$, and $0.569\pm0.014\%$ in bandpasses centered at $1.4$, $3.6$, and $4.5\mu$m, respectively.
 The phase curves have large amplitudes and negligible hotspot offsets, indicative of poor heat redistribution to the nightside.
@@
 The inversion is not present on the nightside.
-The transmission spectrum is featureless, but consistent with the small features expected from cloud-free models.
+The transmission spectrum is featureless, but consistent with the small transit depth variation expected from cloud-free models.
 Using the dayside and nightside emission spectra, we retrieved the atmospheric composition with a 1D self-consistent modeling technique and found the atmosphere is moderately metal-enriched ($\mathrm{[M/H]} =  23^{+29}_{-13}\times$ solar) and the carbon-to-oxygen ratio is below 0.9 at $3\,\sigma$ confidence.
@@
 We compare the phase curves to 3D general circulation models and find that atmospheric drag with a timescale of $10^4$ s is the best match to the data, suggesting the presence of a magnetic field with strength $\sim1$ Gauss.
-We also compare the WASP-103b spectra to brown dwarfs and young directly imaged companions and find these more massive and self-luminous objects have significantly larger water features, indicating that surface gravity and irradiation environment play an important role in shaping the spectra of hot Jupiters.
-These results highlight the 3D structure of exoplanet atmospheres and illustrate the importance of phase curve observations for understanding their complex chemistry and physics.
-=======
-	We present thermal phase curve measurements for the hot Jupiter WASP-103b observed with \emph{Hubble}/WFC3 and \emph{Spitzer}/IRAC.
-The dayside planet-to-star flux ratio is $0.151\pm0.015\%$, $0.446\pm0.038\%$, and $0.569\pm0.014\%$ in bandpasses centered at $1.4$, $3.6$, and $4.5\mu$m, respectively.
-The phase curves have large amplitudes and negligible hotspot offsets, indicative of poor heat redistribution to the nightside.
-We fit the phase variation with a range of climate maps and find that a spherical harmonics model generally provides the best fit.
-The phase-resolved spectra are consistent with blackbodies in the WFC3 bandpass, with brightness temperatures ranging from $1880\pm40$ K on the nightside to $2930 \pm 40$ K on the dayside.
-The dayside spectrum has a significantly higher brightness temperature in the \Spitzer\ bands, which we attribute to CO emission and a thermal inversion.
-The inversion is not present on the nightside.
-The transmission spectrum is featureless, but consistent with the small features expected from cloud-free models.
-Using the dayside and nightside emission spectra, we retrieved the atmospheric composition with a 1D self-consistent modeling technique and find the atmosphere is moderately metal-enriched ($\mathrm{[M/H]} =  23^{+29}_{-13}\times$ solar) and the carbon-to-oxygen ratio is below 0.9 at $3\,\sigma$ confidence.
-In contrast to cooler hot Jupiters, we do not detect significant water absorption, which we attribute to partial H$_2$O dissociation and additional opacity from H- and trace amounts of hydrides/oxides.
-We compare the phase curves to 3D general circulation models and find that atmospheric drag with a timescale of $10^4$\,s is the best match to the data, suggesting the presence of a magnetic field with strength $\sim1$ Gauss.
 We also compare the WASP-103b spectra to brown dwarfs and young directly imaged companions and find these more massive and self-luminous objects have significantly larger water features, indicating that surface gravity and irradiation environment play an important role in shaping the spectra of hot Jupiters.
@@
 
-We also fit indepedent blackbody models to the \HST/WFC3 data and each \Spitzer\ channel.
+We also fit indepedent blackbody models to the \HST/WFC3 data and each \Spitzer\ channel separately.
 The resulting brightness temperatures and $1\,\sigma$ uncertainties are listed in Table\,\ref{table:teffs}.
@@
 
-To check that fast drag timescales of order $10^4$\,s are physically realistic, we computed the free electron abundance due to ionized metals for the $\tau_\mathrm{drag4}$ GCM.
+To estimate the magnetic field required to produce a fast drag timescale of order $10^4$\,s, we computed the free electron abundance due to ionized metals for the $\tau_\mathrm{drag4}$ GCM.
 Using the order-of-magnitude expression from \cite{perna10} (Equation 12), we estimate a drag timescale at the substellar point of $\tau_\mathrm{drag}  = 2\times10^4/B^2$ s, where $B$ is the magnetic field in Gauss.

### 2018-02-28 ApJ_submit/ms.tex
ApJ submission
correct first phase curve planet

--- 2018-02-15 ms.tex
@@
 This observation is sensitive to different longitudes at each orbital phase of the planet.
-The first phase curve of an exoplanet was observed with \Spitzer\ for the hot Jupiter HD 189733b by \cite{harrington06}, followed by additional \Spitzer\ observations for about a dozen more systems \citep[cataloged in][]{parmentier17}.
+The first phase curve of an exoplanet was observed with \Spitzer\ for the hot Jupiter $\nu$ Andromedae b by \cite{harrington06}, followed by additional \Spitzer\ observations for about a dozen more systems \citep[cataloged in][]{parmentier17}.
 The observations revealed large day-night temperature contrasts (in excess of 300 K), and eastward shifted peak brightness due to heat circulation, as predicted by 3D models \citep{showman02}.
@@
 \begin{figure}
-\includegraphics[width = 0.5\textwidth]{Figures/photometry.eps}
+\includegraphics[width = 0.5\textwidth]{fig1.eps}
+%\includegraphics[width = 0.5\textwidth]{fig1-eps-converted-to.pdf}
 \caption{$Top$: The normalized nightly Cousins $R$ band photometric dataset for WASP-103, acquired with the C14 automated imaging telescope at Fairborn Observatory.
@@
 \begin{figure}
-\includegraphics[width = 0.5\textwidth]{Figures/fig2.pdf}
+\includegraphics[width = 0.5\textwidth]{fig2.pdf}
 \caption{Projected area of the planet as a function of orbital phase, normalized to unity at phase zero. The area variation was predicted analytically using the model from \cite{leconte11b}.}
@@
 \begin{figure}
-\includegraphics[width = 0.5\textwidth]{Figures/fig3.pdf}
+\includegraphics[width = 0.5\textwidth]{fig3.pdf}
 \caption{Raw light curves for WASP-103b observed with \HST/WFC3 (top panel) and \Spitzer/IRAC (bottom two panels).
@@
 \begin{figure}
-\includegraphics[width = 0.5\textwidth]{Figures/fig4.pdf}
+\includegraphics[width = 0.5\textwidth]{fig4.pdf}
 \caption{Root mean square (rms) variability in the light curves as a function of bin size (black lines) compared to the expected rms from photon noise (colored lines).
@@
 \begin{figure*}
-\includegraphics[width = 1.0\textwidth]{Figures/fig5.pdf}
+\includegraphics[width = 1.0\textwidth]{fig5.pdf}
 \caption{WASP-103b phase curve observations from \HST/WFC3 (top) and \Spitzer/IRAC (middle and bottom).
@@
 \begin{figure*}
-\includegraphics[width = 1.0\textwidth]{Figures/fig6.pdf}
+\includegraphics[width = 1.0\textwidth]{fig6.pdf}
 \caption{Phase-resolved planet-to-star flux ratios (points) compared to the best fit blackbody (blue line) and the GCM with $\tau_\mathrm{drag4}$.
@@
 \begin{figure*}
-\includegraphics[width = 1.0\textwidth, trim={1.5cm 0 0.5cm 0},clip]{Figures/fig7.pdf}
+\includegraphics[width = 1.0\textwidth, trim={1.5cm 0 0.5cm 0},clip]{fig7.pdf}
 \caption{\textbf{Left:} Fits to the broadband WFC3 phase curve compared to a GCM.
@@
 \begin{figure*}
-\includegraphics[width = 1.0\textwidth]{Figures/fig8.pdf}
+\includegraphics[width = 1.0\textwidth]{fig8.pdf}
 \caption{Dayside planet-to-star flux (points) compared to a blackbody model for the planet (dashed gray line) and the best fit 1D model (blue line, with $1\,\sigma$ uncertainty shaded in orange) for the \HST/WFC3 data (left) and Spitzer (right).
@@
 \begin{figure}
-\includegraphics[width = 0.5\textwidth]{Figures/fig9.pdf}
+\includegraphics[width = 0.5\textwidth]{fig9.pdf}
 \caption{The transmission spectrum of WASP-103b, corrected for planet nightside emission at 1700 K (blue points) and uncorrected (red points).
@@
 \begin{figure}
-\includegraphics[width = 0.5\textwidth]{Figures/fig10.pdf}
+\includegraphics[width = 0.5\textwidth]{fig10.pdf}
 \caption{Abundance weighted absorption cross-sections illustrating the important opacity sources at the photospheric pressure and temperature (5 mbar, 3036 K).
@@
 \begin{figure}
-\includegraphics[width = 0.5\textwidth]{Figures/fig11.pdf}
+\includegraphics[width = 0.5\textwidth]{fig11.pdf}
 \caption{Summary of the 1D self-consistent model atmosphere fits to the dayside emission spectrum.
@@
 \begin{figure}
-\includegraphics[width = 0.5\textwidth]{Figures/fig12.pdf}
+\includegraphics[width = 0.5\textwidth]{fig12.pdf}
 \caption{Posterior distributions for WASP-103b's atmospheric heat redistribution, metallicity, and C/O, from a grid-based fit to the dayside emission spectrum.
@@
 \begin{figure}
-\includegraphics[width = 0.5\textwidth]{Figures/fig13.pdf}
+\includegraphics[width = 0.5\textwidth]{fig13.pdf}
 \caption{TP profiles from the GCM and 1D retrieval, compared to condensation curves of potential cloud species.
@@
 \begin{figure}
-\includegraphics[width = 0.5\textwidth]{Figures/fig14.pdf}
+\includegraphics[width = 0.5\textwidth]{fig14.pdf}
 \caption{GCM predictions (colored lines) compared to the best fit spherical harmonics model for the WFC3 white light, \Spitzer\ 3.6, and \Spitzer\ 4.5 micron phase curves (black lines, top to bottom).
@@
 \begin{figure*}
-	\includegraphics[width = 1.0\textwidth]{Figures/fig15.pdf}
+	\includegraphics[width = 1.0\textwidth]{fig15.pdf}
 	\caption{Row (1): photospheric temperatures for the $\tau_\mathrm{drag4}$ GCM for different viewing geometries.
@@
 \begin{figure*}
-\includegraphics[width = 1.0\textwidth]{Figures/fig16.pdf}
+\includegraphics[width = 1.0\textwidth]{fig16.pdf}
 \caption{Flux-calibrated spectra for WASP-103b (left column) compared to observed spectra for brown dwarfs (middle) and directly imaged companions (right), assuming a distance of 10 pc.

### 2018-02-28 ms.tex
ApJ submission
correct first phase curve planet

@@
 \begin{figure}
-\includegraphics[width = 0.5\textwidth]{Figures/photometry.eps}
+\includegraphics[width = 0.5\textwidth]{Figures/fig1.eps}
 \caption{$Top$: The normalized nightly Cousins $R$ band photometric dataset for WASP-103, acquired with the C14 automated imaging telescope at Fairborn Observatory.

### 2018-03-16 ApJ_submit_v2/response.txt
ref report

1
2
3
4
5	x
6
7
8
9
10	x
11
12
13
14
15
16
17
18
19	x
20
21
22
23

We thank the referee for his or her very thorough comments. We have made the suggested changes to the manuscript, and respond point-by-point below.

Laura Kreidberg, on behalf of the coauthors

===============================================
Organization
1. In section 4.3, the authors say that the spherical harmonic map is in good agreement with the blackbody fits to phased resolved spectra, which they reference later in the paper. I think the paper would be better organized, if they wish to cite this agreement, by putting the phased resolved spectral fits first, before Section 4.3 Climate. This isn't necessary however; I understand there are several different, quasi-independent threads of thought in this paper and it's not going to flow perfectly all the way through.

===============================================
Major Comments

General Comments:
1. No table listing the major parameters of the system is available. It would be nice to have a table like this (with the citation to the discovery paper listed) for easy reference. It was annoying to have to go somewhere else (or wait until a plane landed) and dig around to find information such as the stellar mass/radius, etc. since it was not easily accessible in this paper.

Specific Comments:

****

1. In section 2.2 (Spitzer data reduction), the authors say they used the POET pipeline and reference Stevenson et al. 2012. However, I would like more detail to be given than just the reference and few details presented here. I had to go look at the referenced paper to determine that the technique is BLISS Mapping (though this is also mentioned later in 3.2.2 along with a few other details).

Particularly, when selecting aperture sizes, how are the pixels partially within the aperture weighted? Are they weighted by the portion of the pixel within the aperture, or is this multiplied by a sensitivity map / or the portion of an estimated PSF that falls in the pixel? This is not stated later in 3.2.2.

Some of the information of the reduction is found within Cubillos et al. 2013, which the authors have cited. However, this is mixed in with analysis specific to the object in that system. This paper also notes that the POET pipeline has several 'options' to choose from along the way in the reduction.

Therefore, I think section 2.2 should be significantly expanded (or this info should be in 3.2.2) to explain what the authors have done to reduce the Spitzer data so that it is more easily reproduced. Especially since many people (and this referee in particular) are much more familiar with PLD methods rather than BLISS mapping type methods.

****

2. Similarly, in section 2.3 the authors state at the end of paragraph 1 "The nightly observations were corrected for bias, flat-fielding, pier-side offset, and differential atmospheric extinction". I would insist that more details are provided about this reduction. Bias and flat-fielding are straightforward and likely don't need additional explanation but the pier-side offset and the differential atmospheric extinction portion could use some more explanation:

a) Is the "pier-side offset" a singular term (constant) or is it a more general correction that's a function of the tilt of the telescope to account for flexure? Was it measured or is it calculated? etc.

b) I have similar questions for the differential atmospheric extinction. Is this a linear term with airmass? Quadratic? Is it measured from the data as a correction or is it calculated? What form does it take? Is it something like (X-1) * (color) where X is the airmass and color is some determination of color from catalogs?

More detail on these corrections is warranted.

****

3. Figure 1 and associated discussion: Please include separate panels for the reference star time series. Since only 6 reference stars were used, these can all be accommodated with one extra panel with different reference stars offset from each other.

****

4. Section 3.1, paragraph 2: The authors state that they fixed the orbital period, inferior conjunction time, inclination and a/R* to the values in Southworth et al. (2015). Southworth et al. (2015) collected several ground based transits with GROND (which has an observing cadence of approximately 1 minute). However, Spitzer's observing cadence is 12 seconds for this object (and does not observe through an atmosphere), so I would think that the Spitzer values fit for these parameters would be better. The authors state that the 4.5 micron data are consistent with the Southworth et al. parameters, which justified holding the parameters fixed. My question for the authors is: Were the Spitzer parameters better? This is not mentioned, but it would not surprise me if the transit parameters were better (or at least less systematically correlated), and therefore those should be the ones used rather than the Southworth et al. parameters.

Additionally, the authors have collected transit data but all of the plots shown use y-scales that don't show the transit. I think a transit plot would be nice, just to see what the data even look like.

****

5. Section 3.1, final paragraph: The authors state the uncertainty on the companion star flux contribution is less than 1%. 1% of what? Is the error less than 1% of the total flux in the system (since WASP-103 is bright?) Or are the authors stating that they have less than 1% photometry on the magnitude of the contaminating star. If the latter, I find that difficult to believe - getting 1% absolute photometry is hard and I would be interested in the details. If it's the former (or something else), please include a couple words to clarify.

#

We were referring to the former, and added some text to clarify this point.

****

6. Figure 3: This figure doesn't seem to be very useful. The large amplitude of the systematics of Hubble observations and Spitzer observations are well known, and visualizing them here doesn't add much to the discussion. I also do not like that the panels are stacked but the x-axis is in units of "time since the first exposure", since these observations were not taken at the same time, but the visual presentation implies as such. Finally (and this is a general complaint), the unbinned Spitzer data is never shown. One of the strengths of Spitzer is it's rapid cadence, and yet Figure 3 has already binned the data to 15 minute segments. It would be useful (as has been done in other papers) to show the unbinned time series with some suitable alpha to make all the data visible and then overplot a binned version on top of that.

If the authors opt to keep Figure 3 (I think Figure 5 on its own is sufficient with some changes), I would like to see the unbinned data in a plot, and the x-axis changed to something more suitable (Time or Phase).

****

7. In section 3.3, the authors state that for a subset of cases an MCMC was used to determine parameter uncertainties. Which subset? How were they chosen?

****

8. Section 3.4: The authors mention that the RMS of the white light curve was larger than predicted based on the photon noise and the spectral curves. The suggested option "imperfect modeling of the astrophysical signal or instrumental systematics" is too generic a statement and should be deleted. Also, the loss of flux outside of the extraction window option is only relevant for the most blue and most red spectral bins. The authors state that they do not further explore this as the wavelength dependent data do reach the photon limit.

I disagree with this approach. The fact that if you divide up the data into enough bins that systematic effects are no longer significant does not make them unimportant - especially when conclusions are being drawn from the total spectrum which is obtained by using all of the data. If the white light curve does not follow the photon noise limit, then this implies that excess noise in each wavelength bin (while not significant on its own), is adding constructively with that from other bins. This might imply a color dependent systematic, which would affect the results presented here.

More discussion here is warranted to show conclusively that the larger than predicted noise is not biasing the data or results. (This may be as simple as showing that other works show similar effects or that there are other works with elevated red noise in all channels but have shown that this does not affect the end results).

****

9. Figure 5: There are several things with the figure that I would like clarified or changed.

First, for visual comparison purposes, I would like the y-axes for each panel to be on the same scale. The data are presented in order to facilitate quick by-eye comparison in the different wavelengths, but the changing y-scale between the Spitzer and Hubble data obscure this fact.

Second, the bin size changed between this figure and figure 3, although this is never stated directly. In Figure 3, the bin sizes were 15 minutes. In Figure 5, they are now 44 minutes (the authors state 30 uniformly spaced bins, which this translates to). Why the change in bin size? and what motivated the bin size choice here? The authors should pick one bin size throughout unless there is good reason to change it figure to figure

Finally, I would like to see the unbinned but systematic corrected data here or as a separate figure. As stated previously, one of the strengths of spitzer is its high cadence. It is possible to make a plot with all the unbinned data shown with some choice of transparency alpha and then the current binned plots superimposed on top of that (as has been done in other works). This will allow the readers to see the actual underlying data and what is actually being binned together and whether there might be systematics being averaged out.

****

10. Figure 6: Here again, I would like to see a different version or this version changed where the y-scaled on all of the plots are the same. It's hard to interpret the figure and the plots when having to mentally account for the changing y-scales for each of the different phases shown.

##

We explored using the same y-axis for all the panels in this figure, but found that the range has to be so large (0.1e-3 - 5e-3), that for some panels the shape of the spectra is hard to make out (particularly for phases near the dayside, when the planet-to-star flux is close to the top of this range).

To make it easier for readers to interpret the figure with a different y-axis on each panel, we added a dotted horizontal line at 1e-3 in all the panels.

****

11. Section 4.3: It is not clear why the bias would be 100 ppm if the phase variation was absorbed into the systematics model, as the phase variation is at the 0.0015 level as shown in Figure 7, which is significantly bigger. A little more explanation is needed as to how this number was obtained

****

12. Section 5.1: The authors state that the Spitzer data have higher brightness temperatures than the WFC data at phase 0.5 and lower brightness temperatures at 0.8-0.9, which they interpret as an emission feature on the day side and absorption feature on the night side of the planet.

However, in Table 6, in the 0.44-0.56 bin, the brightness temperature is 2933 +/- 41 at WFC3 and 2995 +/- 159 and 3154 +/- 99 at Ch1 and Ch2 wavelengths. Therefore, the differences at these wavelengths don't seem to be formally significantly different from each other.

Similarly, the differences at phase 0.06-0.15 only seem to be marginally significantly different from each other as stated in the text.

To contradict this, at phase 0.15-0.25 (when there is still substantially more night side than day side present, the Ch. 1 brightness temperature is brighter than the WFC3 data (the Ch. 2 brightness temperature is about the same as the WFC3 data).

To me, this indicates that the nice clean story presented by the authors of a sharp contrast between day side behavior and night side behavior (and interpretation of an emission feature) is incorrect.

This has significant consequences for the rest of the paper, which relies on this interpretation to estimate [M/H], etc. Therefore I request the authors to more robustly argue that the brightness temperature are indeed significantly different between the nightside and dayside of the planet, put a confidence value on this difference, and explain why many of the intermediate phases show different behavior than what is suggested in the text for the nightside-dayside dichotomy.

****

13. Section 5.2.1: Dayside spectrum - Which spectrum in specific are the authors trying to fit. Are you all only trying to fit the single binned spectrum overlapping with phase 0.5? Or are you all also fitting other phases that are dominated by day side emission? Please be clear

I also realize that the content of this section may change depending on the previous comments regarding the interpretation of the 4.5 micron "emission feature". I think regardless of the outcome, it should be made clear how critically the metallicity figure that is obtained depends on accurately determining the strength of the emission at 4.5 microns and that if it is due to systematics that this analysis no longer applies.

****

14. The authors close section 5.2.1 with a list of caveats about the error bars on this section and how the inferred [M/H] and [C/O] may be heavily skewed by the one 4.5 micron data point (from phase 0.5? or other bin? see previous comment). These caveats need to be more prominent considering how serious they may be to the interpretation. I think they need to be present in the abstract, and also they need to be bulleted here in the relevant section so that they are easy to catch for those that skim the paper instead of read it in depth.

****

15. Section 5.2.2: Nightside spectrum. The authors fit a nightside spectrum at phase 0.1. One easy thing to do for comparison and to estimate or show error bars is to also fit a nightside spectrum at phase 0.9, which should be symmetric and obtain the same or similar results. I would ask that the authors please do this and report the results. I realize it might not be interesting because the fit already presented is not able to say much about the metallicity or the C/O ratio. This may also be a useful exercise for the dayside spectrum (fit at phase 0.4 and phase 0.6, or something similar).

****

16. Section 6: The GCM used assumes a solar composition, but the authors argued earlier in the paper that WASP-103b's atmosphere is enhanced in metallicity. So why make this choice? Does the GCM not allow you to dial up the metallicity? This isn't explained. Later the authors also run an enhanced metallicity ([M/H] = 0.5) simulation with different drag coefficients. However, the reasons behind these different model choices for comparisons is never explained. There should be more text towards this end, particularly on the choice on whether or not to include TiO/VO opacity, which is turned on or off in the different simulations without explanation.

****

17. The discussion of the magnetic field strength needed to produce a drag that sort of makes the GCM model work the best is very wishy washy. I understand that the authors are using order-of-magnitude expressions (as they state) but I think the magnetic field discussion is oversimplified and the conclusions are overstated. It also neglects to mention previous work attempting to directly measure/detect the effects of magnetic fields from planets. If the authors wish to discuss the magnetic fields, some mention of these previous works should be done. Significant mention about the shape of the magnetic field should also be prevalent. Furthermore, the planet is very close in to its star, and so there would likely be a complicated magnetic field structure due to the presence of the stellar magnetic field in the vicinity. This is not addressed or touched on when the authors assume the magnetic field is perpendicular to the flow of material.

If the authors want to keep a discussion of the magnetic field in the paper, this section should be significantly expanded and the caveats and assumptions more prominently listed. Otherwise, casual readers might over interpret this section to imply that a magnetic field is detected or that a magnetic field with a strength nice and similar to Jupiter's is the only possible explanation for the observable properties of the system with regards to its phase curve. It is the referee's preference however, that the magnetic field discussion is mostly scaled down or eliminated.

****

18. Section 6: At the end of this section, the authors note that the GCM does not provide a good fit to the data, while the spiderman maps do much better. In that case, I wonder why such a large portion of the paper is devoted to something that doesn't work all that well (and a B-field inference drawn from it too). I think it's good to test the models and see what they can do when confronted with data, but at the same time I think the authors have over interpreted what has come out of the GCMs, as stated before.

****

19. I quite enjoyed the comparison to brown dwarfs section! I thank the authors for including it in their paper!

#

Thank you! We are glad liked it.

****

20. Figure 16: I think the y scales on each vertical section of plots need to be adjusted to be the same. This will facilitate easier comparison than as currently shown (this is similar to my previous comments on other plots).

****

21. I like the format of section 8 (the summary/conclusion section). The bullet points are helpful to readers that would skim through a paper and I wish more papers had done this. I would encourage the authors (if they feel like it) to bold a statement in each of the bullet points as well.

****

22. Several of these bullet points will likely need tweaking depending on the responses / extra work/interpretation from the previous comments. Similarly, the abstract will likely also need to be tweaked

****

23. The last paragraph states that the authors have detected coruscation patterns influenced by the magnetic field. I think this is too strong a statement, and has not been exhaustively researched and concluded to be the only explanation here (see previous comments).

===============================================
Minor and obnoxiously picky comments
1. Introduction, paragraph 2: Don't short change the small (but useful) handful of directly imaged planets when you say exoplanets are not resolved from their host stars.

2. Introduction paragraph 2: "The observations revealed large day-night..." should say "These observations revealed large day-night..."

3. Introduction paragraph 2: The authors list a bunch of references for Kepler that show evidence for reflected light and variable clouds. However, those references really only cover 2 Kepler planets (and one paper is more theoretical in nature). This is fine, but I would ask the authors to specifically name the planets in this case, since it's not widely observed.

4.Section 2.3 Photometric Monitoring - The filter (Cousins R) should be in italics, as photometric passbands typically are.

5. Section 3.2.2 - Please put in parentheses next to the pixel sizes what this is in terms of arcseconds

6. Please clarify at the end of 3.3 that a \gamma = 1.1 for the power spectral density of red noise implies an equal amount of uncorrelated white noise and correlated noise.

7. Section 4.2: The authors state that they bin the light curve in intervals of 0.1 in orbital phase. Please also state the physical duration of these bins (i.e. a couple hours or so). This is made more difficult for the reader as there is no table with the system parameters present in the paper with which to easily look it up.

8. Section 4.5, Is the linear limb darkening parameter picked per bin? And is it initialized near some value (presumably from Claret)?

9. Table 5: I believe the third column needs to be multiplied by 100 like the second column was in order to get it as a % which is what it is labelled as. Is this true or am I misreading it (and by extension figure 9)?

10. I do not like that the authors cite Mansfield et al. (submitted) and Paramentier et al. (in prep) in section 5.2 while these papers are not accessible (and could change significantly with no version control on arXiv available!). The citations to these papers should be removed unless a publicly available version becomes available.

11. 5.2.1 - Dayside spectrum: The authors infer a range of 23 +29 -13 times solar for the metallicity. In the summary section the authors state that they have > 1x solar at 3 sigma confidence. I would like this statement presented here as well, as I consider that a much more useful result than a number with a huge error bar.

12. Section 5.2.1: You infer from your fits a heat redistribution of 2.49 +0.14, -0.15, this is pretty close to the upper limits. I suppose since the prior was uniform and the upper bound on the prior is 3 sigma away this is fine and you can measure the peak and shape of the distribution regardless, but can the authors confirm that you're not significantly running into the walls of your prior?

### 2018-03-16 ApJ_submit_v2/ms.tex
ref report

--- 2018-02-28 ApJ_submit/ms.tex
@@
 The companion star contribution ranges from $10\%$ at $1.1\,\mu$m to $16\%$ at $4.5\,\mu$m.
-The uncertainty on the companion star flux contribution is less than 1\%, which introduces negligible error in the estimated planet-to-star-flux compared to the photon noise.
+The uncertainty on the companion star flux contribution \added{to the total system flux} is less than 1\%, which introduces negligible error in the estimated planet-to-star-flux compared to the photon noise.
 We calculated $A(t)$ using the analytic formula from \cite{leconte11b}, equation B.9, which computes the projected area of a triaxial ellipsoid.
@@
 Phases $\phi=0.5$ and $0.0$ correspond to times of secondary eclipse and transit, when the substellar and antistellar points are respectively aimed at Earth.
-The blackbody model is fit to the \HST/WFC3 data only.}
+The blackbody model is fit to the \HST/WFC3 data only.
+\added{We also plot a dotted horizontal line 1 ppt to draw attention to the changing limits on the y-axis.}}
 \label{fig:spectra}

### 2018-03-30 ApJ_submit_v2/response.txt
ref response

@@
-1
-2
-3
-4
+1       x
+2       x
+3       x
+4       x
 5	x
@@
 
+#
+
+We have added the following additional description to Sections 2.2 and 3.2.2 to clarify these points:
+
+Section 2.2:
+We used the POET pipeline (Stevenson et al.
+2012; Cubillos et al.
+2013) to reduce the Spitzer data.
+The pipeline starts by identifying and flagging bad pixels using a double-iteration 4-sigma outlier rejection routine along the time axis.
+This is followed by performing 2D Gaussian centroiding on each frame, which is shown to provide the most precise centers for Spitzer data \citep{Lust2014}.
+The target remains centered near the sweet spot for the entire AOR in each observation, with a maximum drift of 0.1 pixels.
+Next, POET uses sub-pixel (5\times-interpolated) aperture photometry \citep{Harrington2007} to subtract the background and sum the flux within a specified radius.
+Chosen from a grid of apertures between 2 and 4 pixels, we find that an aperture size of 2.75 pixels minimizes the residual noise in the light curve fits.
+For the background, we use an annulus with inner and outer radii of 7 and 15 pixels, respectively.
+The contaminating flux from the nearby star is within the same pixel as the target, so we included it in the photometry and corrected it in the light curve fits.
+A similarly strategy has been applied to successfully analyze dozens of Spitzer data sets \citep[e.g.
+][]{Stevenson2010, Stevenson2012a, Stevenson2012b, Stevenson2014a, Stevenson2014b, Stevenson2016a, Stevenson2017a, Campo2011, Nymeyer2011, Cubillos2013, Blecic2013, Blecic2014, HDL2014}.
+
+Section 3.2.2:
+Warm Spitzer's primary systematic is intrapixel sensitivity variations, where the photometry depends on the precise location of the stellar center within its pixel.
+We fit this systematic using the Bilinearly-Interpolated Subpixel Sensitivity (BLISS) mapping technique \citep{Stevenson2012a}.
+BLISS provides a flexible, non-analytic means to effectively weight the target flux by the spatial sensitivity variations within a pixel, while simultaneously fitting for other systematics and the physical parameters of the system.
+As has been demonstrated by \citet{Ingalls2016}, the POET pipeline with BLISS mapping can accurately model simulated {\em Spitzer} light curves with known physical parameters and produce reliable results.
+
 ****
@@
 
+#
+
+Thank you for raising this point -- it was an oversight to leave the pier-side correction in the manuscript.
+
+The C14 telescope was originally operated on a German equatorial mount, so the telescope had to flip over the RA axis in order follow a star from the east into the west.
+This rotated the field on the CCD, which meant we were using a different part of the chip to make our measurements.
+In case this caused a slight shift in the data not corrected by flat-fielding, we determined and applied a pier-side offset correction.
+In the case of 55 Cnc, the correction was only 0.00007 mag (70 micro-mags), i.e., completely insignificant and smaller than its uncertainty.
+Furthermore, last year we remounted the C14 on a horse-shoe type mount that does not require any flipping to track a star past the meridian so there is no longer any pier-side correction.
+We removed the mention of pier-side offset from section 2.3.
+
 b) I have similar questions for the differential atmospheric extinction.
@@
 
+#
+
+We have added the following description of our correction for extinction:
+    We determined seasonal-mean extinction coefficients from a linear, least-squares fits to seasonal plots of differential magnitudes versus mean air mass and computed the slope in magnitudes per air mass.
+
 ****
@@
 Since only 6 reference stars were used, these can all be accommodated with one extra panel with different reference stars offset from each other.
+
+#
+
+We thank the referee for this attention to detail, but we feel it would not be informative to show the reference star time series for several reasons.
+First, independent comparison star magnitudes are not computed in our reductions; rather, the software measures the total ADU counts in each exposure for WASP-103 and the 6 comparison stars and directly computes the [program - (comp1+comp2+comp3+comp4+comp5+comp6)/6] differential magnitudes.
+Second, because the brightness variation in WASP-103 is so slight, the scatter in the program star is not significantly different than the comparison stars and so not discernible by eye from a plot.
 
@@
 
+#
+
+Southworth et al.
+observed a total of 18 transits of WASP-103b, so with the combined data set are able to measure a very precise transit ephemeris (their reported 1 sigma uncertainty is less than 5 seconds).
+We fit the Spitzer 4.5 micron transit alone and obtained a precision on the ephemeris of 30 seconds (at 1 sigma).
+Our precision is lower due to photon noise limitations: the star is much fainter at Spitzer observations than in the optical, and the ground-based telescopes are larger than Spitzer, and we have just one transit compared to 18 in the Southworth et al.
+study.
+For this reason, we elected to use the Southworth et al.
+transit parameters.
+
+FIXME -- transit plot??
+
 ****
@@
 We were referring to the former, and added some text to clarify this point.
+The sentence now reads: The uncertainty on the companion star flux contribution to the total system flux is less than 1%, which introduces negligible error in the estimated planet-to-star-flux compared to the photon noise.
 
@@
 If the authors opt to keep Figure 3 (I think Figure 5 on its own is sufficient with some changes), I would like to see the unbinned data in a plot, and the x-axis changed to something more suitable (Time or Phase).
+
+#
+
+Several of the theorists on this paper have spoken up to say that they like the reminder of what the raw data look like, since they don't work with the data directly.
+We therefore decided to keep the figure, but made the suggested changes.
 

### 2018-03-30 ApJ_submit_v2/ms.tex
ref response

@@
-\documentclass[twocolumn]{aastex61}
+\documentclass[twocolumn, trackchanges]{aastex61}
 
@@
 The data were reduced with the POET pipeline \citep{stevenson12, cubillos13}.
-We performed aperture photometry with an aperture size of 2.75 pixels (chosen from a grid of apertures between 2 and 4 pixels to minimize the residual noise in the light curve fits).
+\added{The pipeline starts by identifying and flagging bad pixels using a double-iteration 4-sigma outlier rejection routine along the time axis.
+This is followed by performing 2D Gaussian centroiding on each frame, which is shown to provide the most precise centers for Spitzer data \citep{Lust2014}.
+The target remains centered near the sweet spot for the entire AOR in each observation, with a maximum drift of 0.1 pixels.
+Next, POET uses sub-pixel (5$\times$-interpolated) aperture photometry \citep{Harrington2007} to subtract the background and sum the flux within a specified radius.
+Chosen from a grid of apertures between 2 and 4 pixels, we find that an aperture size of 2.75 pixels minimizes the residual noise in the light curve fits.
+For the background, we use an annulus with inner and outer radii of 7 and 15 pixels, respectively.
+The contaminating flux from the nearby star is within the same pixel as the target, so we included it in the photometry and corrected it in the light curve fits.
+A similarly strategy has been applied to successfully analyze dozens of Spitzer data sets \citep[e.g.
+][]{Stevenson2010, Stevenson2012a, Stevenson2012b, Stevenson2014a, Stevenson2014b, Stevenson2016a, Stevenson2017a, Campo2011, Nymeyer2011, cubillos13, Blecic2013, Blecic2014, HDL2014}.}
+
+%We performed aperture photometry with an aperture size of 2.75 pixels (chosen from a grid of apertures between 2 and 4 pixels to minimize the residual noise in the light curve fits).
 We masked pixels that were flagged in the bad pixel mask provided in the ancillary data for the observations.
@@
 The individual consecutive frames were co-added and reduced to differential magnitudes (i.e., WASP-103 minus the mean brightness of the six best comparison stars).
-The nightly observations were corrected for bias, flat-fielding, pier-side offset, and differential atmospheric extinction.
+The nightly observations were corrected for bias, flat-fielding, \deleted{pier-side offset,} and differential atmospheric extinction.
+\added{We determined seasonal-mean extinction coefficients from a linear, least-squares fits to seasonal plots of differential magnitudes versus mean air mass and computed the slope in magnitudes per air mass.}
 
 The photometric analyses are summarized for each observing season in Table\,\ref{tab:photometry}.
-The standard deviation of WASP-103's brightness in each season is given in column~4.
+The standard deviations of a single observation with respect to the corresponding seasonal means are given in column~4; \added{the mean of the three standard deviations is 0.0058~mag, suggesting there is little night-to-night variation in WASP-103.
+The three seasonal mean brightness values given in column 5 scatter about their grand mean with a standard deviation of 0.0036 mag, but we note that the most discrepant mean is from the third season, for which we have only partial coverage.
+Therefore, our results do not completely rule out low-level, year-to-year variability of $<0.001$~mag.}
+
+%The standard deviation of WASP-103's brightness in each season is given in column~4.
 The mean of the three standard deviations is 0.0058~mag, which is comparable to the mean standard deviation of the six comparison stars (0.0055~mag).
+
 To maximize the possibility of detecting WASP-103's rotation, we normalized the photometry such that each observing season has the same mean, thereby removing any long-term variability in WASP-103 and/or the comparison stars (Figure\,\ref{fig:photometry}, top panel).
@@
 The resulting frequency spectrum and the phase curve computed with the best period are shown in the middle and lower panels of Figure\,\ref{fig:photometry} respectively.
-The best-fit period is 6.814 days, which agrees closely with the estimated stellar rotation period of 6.855 days \citep[based on the projected stellar rotation velocity reported in][]{gillon14}.
+The best-fit period is 6.814 days, which agrees closely with the estimated stellar rotation period of 6.855 days \citep[based on the projected stellar rotation velocity and stellar radius reported in][]{gillon14}.
 The peak-to-peak variability amplitude is 0.005 mag.
@@
 \subsubsection{\Spitzer\ Systematics}
-We fit the \Spitzer\ systematics with the POET pipeline, which uses the BLISS mapping technique \citep{stevenson12}.
-This approach creates a map of the intrapixel sensitivity while simultaneously fitting for other systematics and the physical parameters of the system.
-The sensitivity map is determined by bilinear interpolation over a grid of knots centered on the stellar flux.
+\added{Warm Spitzer's primary systematic is intrapixel sensitivity variations, where the photometry depends on the precise location of the stellar center within its pixel.
+We fit this systematic using the Bilinearly-Interpolated Subpixel Sensitivity (BLISS) mapping technique \citep{stevenson12}.
+BLISS provides a flexible, non-analytic means to effectively weight the target flux by the spatial sensitivity variations within a pixel, while simultaneously fitting for other systematics and the physical parameters of the system.
+As demonstrated by \citet{Ingalls2016}, the POET pipeline with BLISS mapping can accurately model simulated \Spitzer\ light curves with known physical parameters and produce reliable results.}
+
+The BLISS sensitivity map is determined by bilinear interpolation over a grid of knots centered on the stellar flux.
 Each knot's sensitivity is calculated from the residuals to the light curve fit: the higher the flux values for data points near a given knot, the higher the detector sensitivity is at that position.

### 2018-03-30 ms.tex
ref response

@@
 The individual consecutive frames were co-added and reduced to differential magnitudes (i.e., WASP-103 minus the mean brightness of the six best comparison stars).
-The nightly observations were corrected for bias, flat-fielding, pier-side offset, and differential atmospheric extinction.
+The nightly observations were corrected for bias, flat-fielding, \deleted{pier-side offset,} and differential atmospheric extinction.
+\added{We determined seasonal-mean extinction coefficients from a linear, least-squares fits to seasonal plots of differential magnitudes versus mean air mass and computed the slope in magnitudes per air mass.}
 
 The photometric analyses are summarized for each observing season in Table\,\ref{tab:photometry}.
-The standard deviation of WASP-103's brightness in each season is given in column~4.
+The standard deviations of a single observation with respect to the corresponding seasonal means are given in column~4; \added{the mean of the three standard deviations is 0.0058~mag, suggesting there is little night-to-night variation in WASP-103.
+The three seasonal mean brightness values given in column 5 scatter about their grand mean with a standard deviation of 0.0036 mag, but we note that the most discrepant mean is from the third season, for which we have only partial coverage.
+Therefore, our results do not completely rule out low-level, year-to-year variability of 0.001~mag or so, but we cannot confirm this.}
+
+%The standard deviation of WASP-103's brightness in each season is given in column~4.
 The mean of the three standard deviations is 0.0058~mag, which is comparable to the mean standard deviation of the six comparison stars (0.0055~mag).
+
 To maximize the possibility of detecting WASP-103's rotation, we normalized the photometry such that each observing season has the same mean, thereby removing any long-term variability in WASP-103 and/or the comparison stars (Figure\,\ref{fig:photometry}, top panel).
@@
 \begin{figure}
-\includegraphics[width = 0.5\textwidth]{Figures/fig1.eps}
+\includegraphics[width = 0.5\textwidth]{fig1.eps}
+%\includegraphics[width = 0.5\textwidth]{fig1-eps-converted-to.pdf}
 \caption{$Top$: The normalized nightly Cousins $R$ band photometric dataset for WASP-103, acquired with the C14 automated imaging telescope at Fairborn Observatory.
@@
 \begin{figure*}
-\includegraphics[width = 1.0\textwidth]{Figures/fig6.pdf}
+\includegraphics[width = 1.0\textwidth]{fig6.pdf}
 \caption{Phase-resolved planet-to-star flux ratios (points) compared to the best fit blackbody (blue line) and the GCM with $\tau_\mathrm{drag4}$.
 Phases $\phi=0.5$ and $0.0$ correspond to times of secondary eclipse and transit, when the substellar and antistellar points are respectively aimed at Earth.
-The blackbody model is fit to the \HST/WFC3 data only.}
+The blackbody model is fit to the \HST/WFC3 data only.
+\added{We also plot a dotted horizontal line 1 ppt to draw attention to the changing limits on the y-axis.}}
 \label{fig:spectra}

### 2018-03-30 Figures/fig3_systematics.py

@@ -13,7 +13,7 @@ sns.set_style("ticks", {"xtick.direction":"in", "ytick.direction":"in"})
 
 rc('font',**{'family':'sans-serif','sans-serif':['Arial']})
 
-gs = gridspec.GridSpec(3, 1, height_ratios =[1,1, 1],  hspace=0.00)
+gs = gridspec.GridSpec(3, 1, height_ratios =[1,1, 1],  hspace=0.0)
 
 # plots HST white light phase curve
 #bestfits = ["./WFC3_best_fits/old_white_fits/bestfit_zhang_allsys.pic"]
@@ -87,6 +87,9 @@ plt.legend([(p1, p2), p0], ["Best fit", "systematics only"], frameon=True)
 #plot Spitzer phase curves
 colors = ['orange', 'red']
 observation = ['Spitzer Ch. 1', 'Spitzer Ch. 2']
+depth = [4.5e-3, 5.7e-3]
+ylo = [4.45e6, 2.39e6]
+yhi = [4.56e6, 2.49e6]
 
 fluxconv = [306.126, 266.648]
 #calculated from Jonathan Fraine's code https://github.com/exowanderer/ExoplanetTSO/blob/master/ExoplanetTSO_Auxiliary.py
@@ -107,6 +110,8 @@ for ii, f in enumerate(bestfits):
 	bestfit = p[3]
 	phase = p[0] 
 
+        bjdtdb = p[8]
+
 	abscissauc = p[10]
 	binfluxuc = p[11]
 	binstduc = p[12]
@@ -114,6 +119,7 @@ for ii, f in enumerate(bestfits):
 	abscissa = p[15]
 	sys = p[16]
 
+        plt.plot(bjdtdb - bjdtdb[0], data_corr*fluxconv[ii]*np.mean(binfluxuc), marker = '.', color = colors[ii], alpha = 0.2, markersize = 3, markeredgewidth = 0., linewidth = 0., zorder =-100000)
 	plt.plot(abscissa - abscissa[0], sys*fluxconv[ii], color= '0.7', zorder=-10)
 	plt.plot(abscissa - abscissa[0], bestfit*fluxconv[ii], color = colors[ii], alpha = alpha)
 	plt.errorbar(abscissauc - abscissa[0], binfluxuc*fluxconv[ii], binstduc*fluxconv[ii], fmt = '.k', markersize = ms)
[…]

### 2018-04-02 ApJ_submit_v2/response.txt
ref report

@@
 
-To make it easier for readers to interpret the figure with a different y-axis on each panel, we added a dotted horizontal line at 1e-3 in all the panels.
+To make it easier for readers to interpret the figure with a different y-axis on each panel, we added a 100 ppm error bar to the bottom right of each panel to illustrate the scale.
 

### 2018-04-02 ApJ_submit_v2/ms.tex
ref report

@@
 \subsubsection{\Spitzer\ Systematics}
-\added{Warm Spitzer's primary systematic is intrapixel sensitivity variations, where the photometry depends on the precise location of the stellar center within its pixel.
+\added{Warm Spitzer's primary systematic is intrapixel sensitivity variation, where the photometry depends on the precise location of the stellar center within its pixel.
 We fit this systematic using the Bilinearly-Interpolated Subpixel Sensitivity (BLISS) mapping technique \citep{stevenson12}.
@@
 We include the transits in the fit, but they are not displayed in this figure.
-The right-hand column shows the binned residuals for the best-fit light curve.}
+The right-hand column shows the binned residuals for the best-fit light curve.
+\added{The gray error bars in the upper right of the left panels correspond to 500 ppm, to illustrate the changing y-axis scale.}}
 \label{fig:phasecurves}
@@
 The blackbody model is fit to the \HST/WFC3 data only.
-\added{We also plot a dotted horizontal line 1 ppt to draw attention to the changing limits on the y-axis.}}
+\added{We also show a 100 ppm error bar in the lower right of each panel to emphasize the changing limits on the y-axes.}}
 \label{fig:spectra}

### 2018-04-02 ms.tex
ref report

@@
 The three seasonal mean brightness values given in column 5 scatter about their grand mean with a standard deviation of 0.0036 mag, but we note that the most discrepant mean is from the third season, for which we have only partial coverage.
-Therefore, our results do not completely rule out low-level, year-to-year variability of 0.001~mag or so, but we cannot confirm this.}
+Therefore, our results do not completely rule out low-level, year-to-year variability of $<0.001$~mag.}
 
@@
 The blackbody model is fit to the \HST/WFC3 data only.
-\added{We also plot a dotted horizontal line 1 ppt to draw attention to the changing limits on the y-axis.}}
+\added{We also show a 100 ppm error bar in the lower right of each panel to draw attention to the changing limits on the y-axes.}}
 \label{fig:spectra}

### 2018-04-02 Figures/fig5_phase_curves.py

@@ -62,7 +62,7 @@ for ii, f in enumerate(bestfits):
 			binbestfit[j-1]=  np.mean(bestfit[ind])
 			bin_average[j-1] = (phasebins[j-1]+phasebins[j])/2.
 
-	plt.errorbar(bin_average, (bindata-1.)*1e3*dilution, yerr = binsigma*1e3, fmt = '.k')
+	plt.errorbar(bin_average, (bindata-1.)*1e3*dilution, yerr = binsigma*1e3, fmt = '.k', linewidth = 1.)
 	plt.plot(phase, (bestfit-1.)*1e3*dilution, color = 'b', label = 'best fit', zorder=-1, alpha = 0.8, linewidth = 2.0)
 
 	#formatting
@@ -76,6 +76,16 @@ for ii, f in enumerate(bestfits):
 	plt.ylim(-0.2, 1.7)
 	plt.xlim(0,1)
 
+
+        ylo, yhi = plt.gca().get_ylim()
+        yrange = yhi - ylo
+        toperr = yhi - 0.1*yrange
+        bottomerr = toperr - 0.5 
+        plt.plot([0.95, 0.95], [bottomerr, toperr], color = '0.5', linewidth =2.)
+        plt.plot([0.94, 0.96], [bottomerr, bottomerr], color = '0.5', linewidth = 2.)
+        plt.plot([0.94, 0.96], [toperr, toperr], color = '0.5', linewidth = 2.)
+	ax.text(0.82, 1.1, '500\nppm', fontsize=10)
+
 	ax.text(0.03, 1.0, 'HST/WFC3\n1.1 - 1.7 $\mu$m', fontsize=10)
 
 	#Plot RESIDUALS 	#
@@ -84,7 +94,7 @@ for ii, f in enumerate(bestfits):
 	ax = plt.subplot(gs[ii, 1])
 	resid = data_corr - bestfit 
 	plt.axhline(0, color='0.5', zorder=-10, linewidth = 1.)
-	plt.errorbar(bin_average, (bindata - binbestfit)*1e3, yerr = binsigma*1e3, fmt = '.k')
+	plt.errorbar(bin_average, (bindata - binbestfit)*1e3, yerr = binsigma*1e3, fmt = '.k', linewidth = 1.)
 	plt.ylim(-0.2,0.2)
 	plt.xlim(0,1)
 	
@@ -143,7 +153,7 @@ for ii, f in enumerate(bestfits):
 
[…]

### 2018-04-02 Figures/figx_transits.py

@@ -1,0 +1,147 @@
+import matplotlib.pyplot as plt
+import numpy as np
+import pickle
+from astropy.io import ascii
+import matplotlib.gridspec as gridspec
+from pylab import *
+from matplotlib import rc
+import spiderman_spherical
+import transit_lc
+from lc_fit import Model, LightCurveData
+import spiderman
+
+rc('font',**{'family':'sans-serif','sans-serif':['Arial']})
+
+def quantile(x, q):
+        return np.percentile(x, 100. * q)
+
+fig = plt.figure(figsize = (3.5,4.5))
+
+gs = gridspec.GridSpec(3, 1, hspace=0.1, wspace = 0.05)
+
+# plots HST white light phase curve
+#bestfits = ["./WFC3_best_fits/old_white_fits/bestfit_spherical.pic"]
+bestfits = ["./WFC3_best_fits/bestfit_spherical.pic"]
+
+phasebins = np.linspace(-0.15, 0.15, 30)
+nbins = len(phasebins) - 1
+
+every_N = 10000
+
+for ii, f in enumerate(bestfits):
+	ax = plt.subplot(gs[ii, 0])
+
+	p = pickle.load(open(f, 'rb'))
+	d, m, par = p[0], p[1], p[2]		#stores data,  model, and best fit parameters into d, m, & par
+	
+	ind = d.err < 9.0e7			#indices of outliers
+	
+	err = d.err[ind]/d.flux[ind]		#normalized per point uncertainty 
+	phase = m.phase[ind]
+	data_corr = m.data_corr[ind]
+	bestfit = m.bestfit[ind]
+
+        ind = phase > 0.5
+        phase[ind] -= 1.
+
+	ind = np.argsort(phase)
+	err, phase, data_corr, bestfit = err[ind], phase[ind], data_corr[ind], bestfit[ind] #sorts by phase
+	
+	bindata = np.zeros(nbins)
+	binsigma = np.zeros(nbins)
+	binbestfit = np.zeros(nbins)
+	bin_average = np.zeros(nbins)
+	
+	for j in range(1, len(phasebins)):
+		ind = (phase >= phasebins[j-1]) & (phase < phasebins[j])
+		if sum(ind)>0:
[…]

### 2018-04-02 ms.tex
figure order (still wrong)

@@
 
-For the other orbital phases, we binned the light curve (with systematics removed) in eight intervals of about 0.1 in orbital phase, with endpoints at phases $0.06, 0.15, 0.25, 0.35, 0.44$ and $0.56, 0.65, 0.75, 0.85, 0.94$.
-These endpoints were chosen to ensure that there is no contribution from in-transit or in-eclipse data.
-In each phase bin, we estimated the planet-to-star flux from the mean value of the data points in the bin.
-To estimate the uncertainty, we took the standard deviation of the points in the bin and added it in quadrature to the standard deviation of the data points during secondary eclipse (phase $0.46-0.54$), to account for the uncertainty in baseline stellar flux.
-For the $3.6\mu$m data, we also add red noise on the timescale of a phase bin, following \cite{pont06}.
-The phase-resolved emission spectra are shown in Figure\,\ref{fig:spectra} and listed in Table\,\ref{table:spectra}.
+For the other orbital phases, we binned the light curve (with systematics
+removed) in eight intervals of about 0.1 in orbital phase, with endpoints at
+phases $0.06, 0.15, 0.25, 0.35, 0.44$ and $0.56, 0.65, 0.75, 0.85, 0.94$. These
+endpoints were chosen to ensure that there is no contribution from in-transit or
+in-eclipse data.  In each phase bin, we estimated the planet-to-star flux from
+the mean value of the data points in the bin. To estimate the uncertainty, we
+took the standard deviation of the points in the bin and added it in quadrature
+to the standard deviation of the data points during secondary eclipse (phase
+$0.46-0.54$), to account for the uncertainty in baseline stellar flux.  For the
+$3.6\mu$m data, we also add red noise on the timescale of a phase bin, following
+\cite{pont06}.  The phase-resolved emission spectra are shown in
+Figure\,\ref{fig:spectra} and listed in Table\,\ref{table:spectra}. We show the
+dayside spectrum in Figure\,\ref{fig:dayside}.
 
@@
 The blackbody model is fit to the \HST/WFC3 data only.
-\added{We also show a 100 ppm error bar in the lower right of each panel to draw attention to the changing limits on the y-axes.}}
+\added{We also show a 100 ppm error bar in the lower right of each panel to emphasize the changing limits on the y-axes.}}
 \label{fig:spectra}
@@
 \begin{figure*}
-\includegraphics[width = 1.0\textwidth, trim={1.5cm 0 0.5cm 0},clip]{fig7.pdf}
-\caption{\textbf{Left:} Fits to the broadband WFC3 phase curve compared to a GCM.
-The colored lines correspond to different temperature maps fit to the data, and the dashed gray line is from the $\tau_\mathrm{drag4}$ GCM.
-We also show the measured planet-to-star flux for each map (points), which is model-dependent due to slight degeneracies with the instrument systematic model.
-\textbf{Right:} Temperature maps from the best fit models and the GCM at a pressure of 0.1 bar.}
-\label{fig:model_comparison}
+\includegraphics[width = 1.0\textwidth]{fig7.pdf}
+\caption{Dayside planet-to-star flux (points) compared to a blackbody model for the planet (dashed gray line) and the best fit 1D model (blue line, with $1\,\sigma$ uncertainty shaded in orange) for the \HST/WFC3 data (left) and Spitzer (right).
+The 1D model was fit to all the data simultaneously, but the blackbody was fit to the WFC3 data only.
+The best fit 1D model binned at the resolution of the \Spitzer\ data is indicated by blue squares (right).}
+\label{fig:dayside}
 \end{figure*}
@@
 \begin{figure*}
-\includegraphics[width = 1.0\textwidth]{fig8.pdf}
-\caption{Dayside planet-to-star flux (points) compared to a blackbody model for the planet (dashed gray line) and the best fit 1D model (blue line, with $1\,\sigma$ uncertainty shaded in orange) for the \HST/WFC3 data (left) and Spitzer (right).
-The 1D model was fit to all the data simultaneously, but the blackbody was fit to the WFC3 data only.
-The best fit 1D model binned at the resolution of the \Spitzer\ data is indicated by blue squares (right).}
-\label{fig:dayside}
+\includegraphics[width = 1.0\textwidth, trim={1.5cm 0 0.5cm 0},clip]{fig8.pdf}
+\caption{\textbf{Left:} Fits to the broadband WFC3 phase curve compared to a GCM.
+The colored lines correspond to different temperature maps fit to the data, and the dashed gray line is from the $\tau_\mathrm{drag4}$ GCM.
+We also show the measured planet-to-star flux for each map (points), which is model-dependent due to slight degeneracies with the instrument systematic model.
+\textbf{Right:} Temperature maps from the best fit models and the GCM at a pressure of 0.1 bar.}
+\label{fig:model_comparison}
 \end{figure*}
@@
 \subsection{Transmission Spectrum}
-Each phase curve observation includes a transit of WASP-103b.
-To measure the wavelength-dependent transit depths (the transmission spectrum), we select a subset of each phase curve.
-The subset includes the transit and additional baseline on either side, such that the total light curve has twice the duration of the transit.
-Over this short duration, there is negligible curvature in the light curve due to the planet's thermal phase variation.
-We fit the data with a transit model, which has free parameters for the planet-to-star radius and a linear limb darkening parameter.
-The orbital parameters (inclination, $a/R_s$, period, and time of central transit) were fixed at previously published values listed in \S\,\ref{sec:fits}.
-We fit for the instrument systematics using the same model as for the phase curve fits, except that we modeled the visit-long systematic as a linear trend in time (which is sufficient for the shorter duration).
-The advantage of fitting the transits separately from the full phase curves is that the resultant transit depths are not dependent on how the phase variation is modeled.
+Each phase curve observation includes a transit of WASP-103b. To measure the
+wavelength-dependent transit depths (the transmission spectrum), we select a
+subset of each phase curve. The subset includes the transit and additional
+baseline on either side, such that the total light curve has twice the duration
+of the transit. Over this short duration, there is negligible curvature in the
+light curve due to the planet's thermal phase variation. We fit the data with a
+transit model, which has free parameters for the planet-to-star radius and a
+linear limb darkening parameter. The orbital parameters (inclination, $a/R_s$,
+period, and time of central transit) were fixed at previously published values
+listed in \S\,\ref{sec:fits}. We fit for the instrument systematics using the
+same model as for the phase curve fits, except that we modeled the visit-long
+systematic as a linear trend in time (which is sufficient for the shorter
+duration). The advantage of fitting the transits separately from the full phase
+curves is that the resultant transit depths are not dependent on how the phase
+variation is modeled. The transit light curve fits are shown in
+Figure\,\ref{fig:transitlc}.
+
+\begin{figure}
+\includegraphics[width = 0.5\textwidth]{fig9.pdf}
+\caption{Best fit transit light curves for WASP-103b (lines), compared to binned data (black points). From top-to-bottom, we show the band-integrated WFC3 light curve, \Spitzer\ 3.6, and $4.5\,\mu$m.}
+\label{fig:transitlc}
+\end{figure}
 
@@
 For the uncorrected data, there is an offset between the \HST\ and \Spitzer\ data of more than five atmospheric scale heights.
-The uncorrected spectrum is inconsistent with a flat line at $3.2\,\sigma$ confidence, whereas the nightside-corrected spectrum is consistent within $1\,\sigma$.
+The uncorrected spectrum is inconsistent with a flat line at $5.3\,\sigma$ confidence, whereas the nightside-corrected spectrum is consistent within $1\,\sigma$.
 The corrected spectrum is also consistent with predictions from the $\tau_\mathrm{drag4}$ GCM, which shows water features in the WFC3 bandpass.
@@
 \begin{figure}
-\includegraphics[width = 0.5\textwidth]{fig9.pdf}
+\includegraphics[width = 0.5\textwidth]{fig10.pdf}
+\label{fig:tspec}
 \caption{The transmission spectrum of WASP-103b, corrected for planet nightside emission at 1700 K (blue points) and uncorrected (red points).
@@
 Atmospheric scale height $H$ is shown on the right y-axis, where $H = 5.5\times10^6$ m (assuming a mean molecular weight of 2.3 atomic mass units, surface gravity $g = 15.9$ m/s$^2$, and a temperature $T = 2410$ K).}
-\label{fig:tspec}
 \end{figure}
 
-\begin{deluxetable}{LLL}
-\tablecolumns{3}
+\begin{deluxetable}{LLLL}
+\tablecolumns{4}
 \tablewidth{0pt}
@@
 \tablehead{
-\colhead{Wavelength} & \colhead{Transit Depth (\%)} & \colhead{Transit Depth (\%)} \\
-\colhead{(micron)} & \colhead{($T_\mathrm{night} = 0$ K)} & \colhead{($T_\mathrm{night} = 1700$ K)}}
+\colhead{Wavelength} & \colhead{$(R_p/R_s)^2$ (\%)} & \colhead{$(R_p/R_s)^2$ (\%)} & \colhead{Error}\\
+\colhead{(micron)} & \colhead{($T_\mathrm{n} = 0$ K)} & \colhead{($T_\mathrm{n} = 1700$ K)} & \colhead{(\%)}}
 \startdata
-1.175 & 1.329049 \pm 0.000092 & 0.013228 \pm 0.000092 \\
-1.225 & 1.329408 \pm 0.000087 & 0.013217 \pm 0.000087 \\
-1.275 & 1.333837 \pm 0.000086 & 0.013246 \pm 0.000086 \\
-1.325 & 1.334184 \pm 0.000087 & 0.013233 \pm 0.000087 \\
-1.375 & 1.359366 \pm 0.000089 & 0.013467 \pm 0.000089 \\
-1.425 & 1.353629 \pm 0.000091 & 0.013390 \pm 0.000091 \\
-1.475 & 1.341570 \pm 0.000092 & 0.013249 \pm 0.000092 \\
-1.525 & 1.350816 \pm 0.000093 & 0.013319 \pm 0.000093 \\
-1.575 & 1.333617 \pm 0.000100 & 0.013125 \pm 0.000100 \\
-1.625 & 1.353438 \pm 0.000104 & 0.013299 \pm 0.000104 \\
-3.6 & 1.401322 \pm 0.000328 & 0.013238 \pm 0.000328 \\
-4.5 & 1.432949 \pm 0.000264 & 0.013554 \pm 0.000264 \\
+1.175 & 1.3178 & 1.3115 & 0.0092 \\
+1.225 & 1.3144 & 1.3067 & 0.0087 \\
+1.275 & 1.3195 & 1.3103 & 0.0086 \\
+1.325 & 1.3454 & 1.3345 & 0.0087 \\
+1.375 & 1.3512 & 1.3385 & 0.0089 \\
+1.425 & 1.3588 & 1.3441 & 0.0091 \\
+1.475 & 1.3364 & 1.3197 & 0.0092 \\
+1.525 & 1.3522 & 1.3333 & 0.0093 \\
+1.575 & 1.3688 & 1.3476 & 0.0100 \\
+1.625 & 1.3549 & 1.3314 & 0.0104 \\
+3.6 & 1.4013 & 1.3238 & 0.0328 \\
+4.5 & 1.4329 & 1.3554 & 0.0264 \\
 \enddata
-\vspace{-0.8cm}
-\tablecomments{comments}
+\tablecomments{Wavelength dependent transit depths, corrected for companion dilution and nightside flux (assuming nightside temperatures of 0 and 1700 K for the second and third columns, respectively).
+The error corresponds to the 68\% credible interval from an MCMC fit to the transit light curves.}
 \end{deluxetable}
@@
 \begin{figure}
-\includegraphics[width = 0.5\textwidth]{fig10.pdf}
+\includegraphics[width = 0.5\textwidth]{fig11.pdf}
 \caption{Abundance weighted absorption cross-sections illustrating the important opacity sources at the photospheric pressure and temperature (5 mbar, 3036 K).
@@
 \begin{figure}
-\includegraphics[width = 0.5\textwidth]{fig11.pdf}
+\includegraphics[width = 0.5\textwidth]{fig12.pdf}
 \caption{Summary of the 1D self-consistent model atmosphere fits to the dayside emission spectrum.
@@
 \begin{figure}
-\includegraphics[width = 0.5\textwidth]{fig12.pdf}
+\includegraphics[width = 0.5\textwidth]{fig13.pdf}
 \caption{Posterior distributions for WASP-103b's atmospheric heat redistribution, metallicity, and C/O, from a grid-based fit to the dayside emission spectrum.
@@
 \begin{figure}
-\includegraphics[width = 0.5\textwidth]{fig13.pdf}
+\includegraphics[width = 0.5\textwidth]{fig14.pdf}
 \caption{TP profiles from the GCM and 1D retrieval, compared to condensation curves of potential cloud species.
@@
 \begin{figure}
-\includegraphics[width = 0.5\textwidth]{fig14.pdf}
+\includegraphics[width = 0.5\textwidth]{fig15.pdf}
 \caption{GCM predictions (colored lines) compared to the best fit spherical harmonics model for the WFC3 white light, \Spitzer\ 3.6, and \Spitzer\ 4.5 micron phase curves (black lines, top to bottom).
@@
 \begin{figure*}
-	\includegraphics[width = 1.0\textwidth]{fig15.pdf}
+	\includegraphics[width = 1.0\textwidth]{fig16.pdf}
 	\caption{Row (1): photospheric temperatures for the $\tau_\mathrm{drag4}$ GCM for different viewing geometries.
@@
 \begin{figure*}
-\includegraphics[width = 1.0\textwidth]{fig16.pdf}
+\includegraphics[width = 1.0\textwidth]{fig17.pdf}
 \caption{Flux-calibrated spectra for WASP-103b (left column) compared to observed spectra for brown dwarfs (middle) and directly imaged companions (right), assuming a distance of 10 pc.

### 2018-04-02 Figures/fig10_transmission_spectrum.py

@@ -1,0 +1,145 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import os, glob
+from lc_fit_nospiderman import Model, LightCurveData
+import pickle
+import pysynphot as psyn					#need to source activate astroconda
+from matplotlib import rc, ticker
+from pylab import *
+import scipy.stats as st
+
+rc('font',**{'family':'sans-serif','sans-serif':['Arial']})
+
+def get_significance(chisq, dof):
+        alpha = (1. - st.chi2.cdf(chisq, dof))/2.
+        z = st.norm.ppf(1.-alpha)
+        return z
+
+def weighted_mean(data, err):                #calculates the weighted mean for data points data with variances err
+        weights = 1.0/err
+        mu = np.sum(data*weights)/np.sum(weights)
+        var = 1.0/np.sum(weights)
+        return [mu, var]                #returns weighted mean and variance
+
+path  = "WFC3_best_fits/spec_fits/"		#zhang model
+files = glob.glob(os.path.join(path, "bestfit*.pic"))		
+dilution = []
+for f in files:
+	p = pickle.load(open(f, 'rb'))
+	d, m = p[0], p[1]			#stores data and model into d & m
+	dilution.append(d.dilution)
+
+dilution = np.array(dilution)
+
+d = np.genfromtxt("w103b_transmission_spectrum.txt")
+d_nodilution = np.genfromtxt("w103b_transmission_spectrum_040218_nodilution.txt")
+d[:,1] = d_nodilution[:,1]      #uses least-squares best fit transit depths from a fit that did NOT including dilution
+
+
+#temps = [1400, 1800, 0]
+#labels = ["$T_\mathrm{night} = 1400$ K", "$T_\mathrm{night} = 1800$ K", "no correction"]
+temps = [1700, 0]
+labels = ["$T_\mathrm{night} = 1700$ K", "no correction"]
+colors = ['blue', 'red', 'gray']
+
+fig = plt.figure(figsize= (5,3))
+rprs2 = 0.01313
+
[…]

### 2018-04-02 Figures/fig14_gcm_comparison.py

@@ -1,219 +1,0 @@
-import matplotlib.pyplot as plt
-import numpy as np
-import os, glob
-from lc_fit import Model, LightCurveData
-import pickle
-import seaborn as sns
-from scipy.interpolate import interp1d
-
-sns.set_context("paper")
-sns.set_style("white")
-sns.set_style("ticks", {"xtick.direction":"in", "ytick.direction":"in"})
-
-gcm_path = "./Vivien_models2"
-gcms = glob.glob(os.path.join(gcm_path, "PC*PT.dat"))
-
-labels = ["$\\tau_\mathrm{drag} = 10^4$ s", "$\\tau_\mathrm{drag} = 10^3$ s", "[Fe/H] = 0.5", "nominal GCM"]
-colors = ["#be0119", "#f97306", "#6dedfd", "#0165fc"]
-ls = [":", "--", "-.", "-"]
-
-plt.figure(figsize = (4, 6))
-
-
-
-def proj_area(phi, inc):
-        R0 = 1.07e8             #planet radius in m
-        p = 0.00117             # planet-to-star mass ratio
-        r = 2.9695e9            #orbital separation in m
-        kn = 0.653              #from table B5 of Leconte et al. 2011
-        n = 1.005
-        qn = kn*(1.- n/5.)      #n 
-
-
-        alpha1 = 2.5*qn*R0**3/(p*r**3)
-        alpha2 = -1.25*qn*R0**3/(p*r**3)
-        alpha3 = alpha2
-
-        a1 = R0*(1+alpha1)
-        a2 = R0*(1+alpha2)
-        a3 = R0*(1+alpha3)
-
-        return  np.sqrt(a3**2*np.sin(inc)**2*(a1**2*np.sin(phi)**2+a2**2*np.cos(phi)**2)+ a1**2*a2**2*np.cos(inc)**2)/(a2*a3)
-
-
-plt.subplot(311)
-inc = 1.523
-correction_factor = 1.099  # = (0.1146/0.1093)**2, ratio of correct transit depth to what Vivien used (which was from the discovery paper and not corrected for stellar contamination)
-
-#plot gcms
-for i, g in enumerate(gcms):
-    print g,
-    model = np.genfromtxt(g, delimiter = ',') 
-    phi = model[:,0]/360.*2.*np.pi
-    area = proj_area(phi, inc)
[…]

### 2018-04-02 Figures/fig15_gcm_comparison.py

@@ -1,0 +1,219 @@
+import matplotlib.pyplot as plt
+import numpy as np
+import os, glob
+from lc_fit import Model, LightCurveData
+import pickle
+import seaborn as sns
+from scipy.interpolate import interp1d
+
+sns.set_context("paper")
+sns.set_style("white")
+sns.set_style("ticks", {"xtick.direction":"in", "ytick.direction":"in"})
+
+gcm_path = "./Vivien_models2"
+gcms = glob.glob(os.path.join(gcm_path, "PC*PT.dat"))
+
+labels = ["$\\tau_\mathrm{drag} = 10^4$ s", "$\\tau_\mathrm{drag} = 10^3$ s", "[Fe/H] = 0.5", "nominal GCM"]
+colors = ["#be0119", "#f97306", "#6dedfd", "#0165fc"]
+ls = [":", "--", "-.", "-"]
+
+plt.figure(figsize = (4, 6))
+
+
+
+def proj_area(phi, inc):
+        R0 = 1.07e8             #planet radius in m
+        p = 0.00117             # planet-to-star mass ratio
+        r = 2.9695e9            #orbital separation in m
+        kn = 0.653              #from table B5 of Leconte et al. 2011
+        n = 1.005
+        qn = kn*(1.- n/5.)      #n 
+
+
+        alpha1 = 2.5*qn*R0**3/(p*r**3)
+        alpha2 = -1.25*qn*R0**3/(p*r**3)
+        alpha3 = alpha2
+
+        a1 = R0*(1+alpha1)
+        a2 = R0*(1+alpha2)
+        a3 = R0*(1+alpha3)
+
+        return  np.sqrt(a3**2*np.sin(inc)**2*(a1**2*np.sin(phi)**2+a2**2*np.cos(phi)**2)+ a1**2*a2**2*np.cos(inc)**2)/(a2*a3)
+
+
+plt.subplot(311)
+inc = 1.523
+correction_factor = 1.099  # = (0.1146/0.1093)**2, ratio of correct transit depth to what Vivien used (which was from the discovery paper and not corrected for stellar contamination)
+
+#plot gcms
+for i, g in enumerate(gcms):
+    print g,
+    model = np.genfromtxt(g, delimiter = ',') 
+    phi = model[:,0]/360.*2.*np.pi
+    area = proj_area(phi, inc)
[…]

### 2018-04-02 Figures/fig16_spectra_comparison.py

@@ -1,212 +1,0 @@
-import numpy as np
-import matplotlib.pyplot as plt
-import matplotlib.gridspec as gridspec
-from astropy import modeling
-import seaborn as sns
-
-sns.set_context("paper")
-sns.set_style("white")
-sns.set_style("ticks", {"xtick.direction":"in", "ytick.direction":"in"})
-
-def weighted_mean(data, err):                #calculates the weighted mean for data points data with variances err
-        weights = 1.0/err
-        mu = np.sum(data*weights)/np.sum(weights)
-        var = 1.0/np.sum(weights)
-        return [mu, var]                #returns weighted mean and variance
-
-def get_blackbody_model(model_w, data_w, data, T):
-    unit_conversion = 1.2533e19                                        #(10 pc/jupiter radius)^2
-
-    model = modeling.blackbody.blackbody_lambda(model_w*1.e4, T)       #wavelength in angstroms
-    model = model*4.*np.pi*1.e4*model_w/unit_conversion/np.pi          #multiplies by 4 pi steradians * 10000. angstroms/micron * micron
-    #see chapter 1 of Rybicki & Lightman about the factor of pi to convert bb intensity to flux!
-    scale = rescale(data_w, data, model_w, model)                                #rescales model to account for uncertainty in radius of the object
-    return  model*scale
-    
-
-def rescale(data_w, data, model_w, model):
-    model = np.interp(data_w, model_w, model)
-    ind = (data > 1.e-20)
-    data_w, data, model = data_w[ind], data[ind], model[ind]
-    scale = np.linspace(0.05, 15, 1000.)
-    chi2best, scalebest = 1.e10, -1.
-    for s in scale:
-        chi2 = np.sum((data - model*s)**2)
-        if chi2 < chi2best:
-                chi2best = chi2
-                scalebest = s
-    return scalebest 
-
-gs = gridspec.GridSpec(3, 3, hspace=0.1, wspace=0.3)
-
[…]

### 2018-04-02 Figures/figx_transits.py

@@ -1,147 +1,0 @@
-import matplotlib.pyplot as plt
-import numpy as np
-import pickle
-from astropy.io import ascii
-import matplotlib.gridspec as gridspec
-from pylab import *
-from matplotlib import rc
-import spiderman_spherical
-import transit_lc
-from lc_fit import Model, LightCurveData
-import spiderman
-
-rc('font',**{'family':'sans-serif','sans-serif':['Arial']})
-
-def quantile(x, q):
-        return np.percentile(x, 100. * q)
-
-fig = plt.figure(figsize = (3.5,4.5))
-
-gs = gridspec.GridSpec(3, 1, hspace=0.1, wspace = 0.05)
-
-# plots HST white light phase curve
-#bestfits = ["./WFC3_best_fits/old_white_fits/bestfit_spherical.pic"]
-bestfits = ["./WFC3_best_fits/bestfit_spherical.pic"]
-
-phasebins = np.linspace(-0.15, 0.15, 30)
-nbins = len(phasebins) - 1
-
-every_N = 10000
-
-for ii, f in enumerate(bestfits):
-	ax = plt.subplot(gs[ii, 0])
-
-	p = pickle.load(open(f, 'rb'))
-	d, m, par = p[0], p[1], p[2]		#stores data,  model, and best fit parameters into d, m, & par
-	
-	ind = d.err < 9.0e7			#indices of outliers
-	
-	err = d.err[ind]/d.flux[ind]		#normalized per point uncertainty 
-	phase = m.phase[ind]
-	data_corr = m.data_corr[ind]
-	bestfit = m.bestfit[ind]
-
-        ind = phase > 0.5
-        phase[ind] -= 1.
-
-	ind = np.argsort(phase)
-	err, phase, data_corr, bestfit = err[ind], phase[ind], data_corr[ind], bestfit[ind] #sorts by phase
-	
-	bindata = np.zeros(nbins)
-	binsigma = np.zeros(nbins)
-	binbestfit = np.zeros(nbins)
-	bin_average = np.zeros(nbins)
-	
-	for j in range(1, len(phasebins)):
-		ind = (phase >= phasebins[j-1]) & (phase < phasebins[j])
-		if sum(ind)>0:
[…]

### 2018-04-02 Figures/get_transit_depths.py

@@ -1,0 +1,17 @@
+import numpy as np
+import pickle
+import glob
+import os
+from lc_fit import Model, LightCurveData
+
+
+path  = "WFC3_best_fits/spec_fits_transit/"		#zhang model
+files = glob.glob(os.path.join(path, "bestfit*.pic"))		
+
+for f in files:
+	p = pickle.load(open(f, 'rb'))
+	data, m, par = p[0], p[1], p[2]			#stores data and model into d & m
+        rps = par[data.par_order['rp']*data.nvisit:(1 + data.par_order['rp'])*data.nvisit]
+        rp = rps[0]
+        depth = rp**2
+        print data.wavelength, depth

### 2018-04-02 Figures/table5_transmission_spectrum.py

@@ -5,16 +5,17 @@ t0 = np.genfromtxt("tspec_tnight0.txt")
 t1700 = np.genfromtxt("tspec_tnight1700.txt")
 
 
-print "\\begin{deluxetable}{LLL}"
-print "\\tablecolumns{3}"
+print "\\begin{deluxetable}{LLLL}"
+print "\\tablecolumns{4}"
 print "\\tablewidth{0pt}"
 print "\\tablecaption{WASP-103b Transmission Spectrum\label{table:tspec}}"
 print "\\tablehead{"
-print "\colhead{Wavelength} & \colhead{Transit Depth (\%)} & \colhead{Transit Depth (\%)} \\\\"
-print "\colhead{(micron)} & \colhead{($T_\mathrm{night} = 0$ K)} & \colhead{($T_\mathrm{night} = 1700$ K)}}"
+print "\colhead{Wavelength} & \colhead{$(R_p/R_s)^2$ (\%)} & \colhead{$(R_p/R_s)^2$ (\%)} & \colhead{Error}\\\\"
+print "\colhead{(micron)} & \colhead{($T_\mathrm{night} = 0$ K)} & \colhead{($T_\mathrm{night} = 1700$ K)} & \colhead{(\%)}}"
 print "\startdata"
 
-for i in range(len(t0)): print t0[i,0],  "&", '{0:0.6f}'.format(100.*t0[i,1]), "\\pm", '{0:0.6f}'.format(t0[i,2]), "&", '{0:0.6f}'.format(t1700[i,1]), "\\pm", '{0:0.6f}'.format(t1700[i,2]),  "\\\\"
+#for i in range(len(t0)): print t0[i,0],  "&", '{0:0.4f}'.format(100.*t0[i,1]), "\\pm", '{0:0.4f}'.format(100.*t0[i,2]), "&", '{0:0.4f}'.format(t1700[i,1]*100.), "\\pm", '{0:0.4f}'.format(t1700[i,2]*100.),  "\\\\"
+for i in range(len(t0)): print t0[i,0],  "&", '{0:0.4f}'.format(100.*t0[i,1]), "&", '{0:0.4f}'.format(t1700[i,1]*100.), "&", '{0:0.4f}'.format(t1700[i,2]*100.),  "\\\\"
 
 print "\enddata"
 print "\\vspace{-0.8cm}"

### 2018-04-03 ApJ_submit_v2/response.txt
figure order (still wrong)
ref points 7-11

--- 2018-03-30 ApJ_submit_v2/response.txt
@@
 5	x
-6
-7
+6       x
+7       x
 8
-9
+9       x
 10	x
-11
+11      x
 12
@@
 
-We thank the referee for this attention to detail, but we feel it would not be informative to show the reference star time series for several reasons.
-First, independent comparison star magnitudes are not computed in our reductions; rather, the software measures the total ADU counts in each exposure for WASP-103 and the 6 comparison stars and directly computes the [program - (comp1+comp2+comp3+comp4+comp5+comp6)/6] differential magnitudes.
-Second, because the brightness variation in WASP-103 is so slight, the scatter in the program star is not significantly different than the comparison stars and so not discernible by eye from a plot.
+We thank the referee for this attention to detail, but we feel it would not be
+informative to show the reference star time series for several reasons. First,
+independent comparison star magnitudes are not computed in our reductions;
+rather, the software measures the total ADU counts in each exposure for WASP-103
+and the 6 comparison stars and directly computes the [program -
+(comp1+comp2+comp3+comp4+comp5+comp6)/6] differential magnitudes.  Second,
+because the brightness variation in WASP-103 is so slight, the scatter in the
+program star is not significantly different than the comparison stars and so not
+discernible by eye from a plot.  FIXME
 
@@
 
-FIXME -- transit plot??
+We added a figure showing the transit light curves (Figure 9).
 
@@
 We therefore decided to keep the figure, but made the suggested changes.
+The figure now shows the raw data plotted as a function of time (BJD_TDB).
 
@@
 7. In section 3.3, the authors state that for a subset of cases an MCMC was used to determine parameter uncertainties. Which subset? How were they chosen?
+
+#
+Since we considered so many different cases (four different phase variation models for broadband and spectroscopic light curves), we elected to run an MCMC only for cases where we ereport 68% confidence intervals on the model parameters.
+These include the transit models (for the transit depth) and the sine curve models (for the phase amplitude and offset reported in Table 2).
+We added this clarification to the text in Section 3.3.
 
@@
 
+#
+
+Regarding the first point: we explored using the same y-axis for all the panels in this figure, but found that the range has to be so large (0.1e-3 - 5e-3) that the HST light curve is squished in the bottom quarter of the plot, which makes it hard to see the phase variation.
+To make it easier for readers to interpret the figure with a different y-axis on each panel, we added a 500 ppm error bar to the top right of each panel to illustrate the scale.
+
+We kept the phase bins the same, but removed the binning from Figure 3 and added the raw data instead.
+
 ****
@@
 
-##
+#
 
-We explored using the same y-axis for all the panels in this figure, but found that the range has to be so large (0.1e-3 - 5e-3), that for some panels the shape of the spectra is hard to make out (particularly for phases near the dayside, when the planet-to-star flux is close to the top of this range).
-
-To make it easier for readers to interpret the figure with a different y-axis on each panel, we added a dotted horizontal line at 1e-3 in all the panels.
+As with Figure 5, we tested using the same y-axis for all the panels in this figure, but again found that for some panels the shape of the spectra is hard to make out (particularly for phases near the dayside, when the planet-to-star flux is close to the upper limit of the y-range).
+Instead, we added a 100 ppm error bar to the bottom right of each panel to illustrate the scale.
 
@@
 A little more explanation is needed as to how this number was obtained
+
+#
+
+The 100 ppm was estimated by eye.
+The exact amplitude of the phase variation depends on which model is used for the thermal phase variation.
+Rather than making a quantitative comparison, we wanted to suggest that the amplitude of this effect has the right order of magnitude.
+We added text to section 4.4 clarifying that this estimate was just an approximation from looking at the figure (now Figure 8).
 

### 2018-04-03 ApJ_submit_v2/ms.tex
ref points 7-11

@@
 \begin{figure}
-\includegraphics[width = 0.5\textwidth]{fig3.pdf}
-\caption{Raw light curves for WASP-103b observed with \HST/WFC3 (top panel) and \Spitzer/IRAC (bottom two panels).
-The data points are indicated with black dots.
-The \HST\ data are unbinned, and the Spitzer data are binned in time segments of 15 minutes with error bars indicating the bin standard deviation.
-The colored lines show the best fit models, which include the astrophysical signal and instrument systematics.
+    \includegraphics[width = 0.5\textwidth, trim={0cm 1cm 0cm 3cm},clip]{fig3.pdf}
+\caption{Raw light curves (points) for WASP-103b observed with \HST/WFC3 (top four panels) and \Spitzer/IRAC (bottom two panels).
+The black lines show the best fit models, which include the astrophysical signal and instrument systematics.
 The gray lines indicate the contribution from the instrument systematics alone (which would be observed for a source with constant brightness and no planet).
-For visual clarity, we corrected the \HST\ data for the upstream-downstream effect, separated the four visits by adding a flux offset, and zoomed in on the phase variation, so the transits are not displayed in the panel.}
+For visual clarity, we corrected the \HST\ data for the upstream-downstream effect and zoomed in on the phase variation, so the transits are not displayed in the panel.}
 \label{fig:systematics}
@@
 To determine the best fits, we performed a least-squares $\chi^2$ minimization for each wavelength and model.
-For a subset of these cases, we also performed a Markov chain Monte Carlo (MCMC) analysis to estimate parameter uncertainties.
-We used \texttt{emcee} \citep{foremanmackey13} to fit the \HST/WFC3 light curves and differential evolution Monte Carlo for the \Spitzer\ fits \citep{braak06}.
+For a subset of these cases \added{where we wish to calculate 68\% confidence intervals}, we also performed a Markov chain Monte Carlo (MCMC) analysis to estimate parameter uncertainties.
+\added{These include the transit fits and the sine curve fit to the broadband phase curves.} We used \texttt{emcee} \citep{foremanmackey13} to fit the \HST/WFC3 light curves and differential evolution Monte Carlo for the \Spitzer\ fits \citep{braak06}.
 We ran the MCMC until convergence according to the Gelman-Rubin statistic.
@@
 A likely explanation for this difference is that the \cite{cartier17} analysis does not include the planet's thermal phase variation, so that the Gaussian process models it as an instrument systematic.
-If the phase variation is absorbed into the systematic model, the measured eclipse depths would be biased low by about 100 ppm (see Figure\,\ref{fig:model_comparison}).
+If the phase variation is absorbed into the systematic model, the measured eclipse depths would be biased low.
+\added{From a glance at Figure\,\ref{fig:model_comparison}, the amplitude of this effect is} $\sim100$ ppm, \added{which is comparable to the offset between the two analyses}.
 Our estimated uncertainties are a factor of four smaller than those reported in \cite{cartier17}, which is consistent with photon-limited expectations (our data set includes two additional eclipses, a factor of five longer out-of-eclipse baseline, and has 60\% larger wavelength bins).

### 2018-04-03 ms.tex
ref points 7-11

@@
 A likely explanation for this difference is that the \cite{cartier17} analysis does not include the planet's thermal phase variation, so that the Gaussian process models it as an instrument systematic.
-If the phase variation is absorbed into the systematic model, the measured eclipse depths would be biased low by about 100 ppm (see Figure\,\ref{fig:model_comparison}).
+If the phase variation is absorbed into the systematic model, the measured eclipse depths would be biased low.
+\added{From a glance at \ref{fig:model_comparison}, the amplitude of this effect is} $\sim100$ ppm, \added{which is comparable to the offset between the two analyses}.
 Our estimated uncertainties are a factor of four smaller than those reported in \cite{cartier17}, which is consistent with photon-limited expectations (our data set includes two additional eclipses, a factor of five longer out-of-eclipse baseline, and has 60\% larger wavelength bins).

### 2018-04-03 Figures/fig3_systematics.py

@@ -13,7 +13,7 @@ sns.set_style("ticks", {"xtick.direction":"in", "ytick.direction":"in"})
 
 rc('font',**{'family':'sans-serif','sans-serif':['Arial']})
 
-gs = gridspec.GridSpec(3, 1, height_ratios =[1,1, 1],  hspace=0.0)
+gs = gridspec.GridSpec(6, 1, height_ratios =[1,1,1,1,1,1],  hspace=0.33)
 
 # plots HST white light phase curve
 #bestfits = ["./WFC3_best_fits/old_white_fits/bestfit_zhang_allsys.pic"]
@@ -22,7 +22,7 @@ bestfits = ["./WFC3_best_fits/bestfit_zhang_allsys.pic"]
 alpha = 0.7
 ms = 5
 
-plt.figure(figsize = (5, 7))
+fig = plt.figure(figsize = (6.5, 10))
 
 for ii, f in enumerate(bestfits):
 	ax = plt.subplot(gs[ii, 0])
@@ -41,56 +41,69 @@ for ii, f in enumerate(bestfits):
 	t = d.time[ind]
 	visit_sys = m.all_sys[ind]
 
+        data_corr /= 1e6
+        allsys /= 1e6
+        visit_sys /= 1e6
+        d.flux /= 1e6
+
 	print "WFC3 white: obs, exp rms (ppm)", np.std(m.resid[ind]/d.flux[ind])*1e6, np.sqrt(1./np.median(d.flux[ind]))*1e6
 
 	scan = np.ones_like(phase)
 	scan[d.scan_direction == 0] = 1. + par[d.par_order['scale']*d.nvisit]
 	delta = 1. + par[d.par_order['scale']*d.nvisit]
 
+	offset = 2457000.
+
 	ind = d.vis_num == 0
-	offset = 0.
+	p0, = plt.plot(t[ind] - offset, delta*visit_sys[ind], color = '0.7', label = 'systematics', zorder=-10)
+	p1, = ax.plot(t[ind] - offset, allsys[ind]*scan[ind] , color = 'k') 
+	p2, = ax.plot(t[ind] - offset, d.flux[ind]*scan[ind] , '.b', markersize = ms, alpha = alpha)
+        plt.legend([(p1, p2), p0], ["Best fit", "Systematics"], frameon=True, fontsize = 11)
[…]

### 2018-04-03 ApJ_submit_v2/response.txt
point 17

@@
 13
-14
+14      x-abstract
 15
-16
-17
+16      x
+17      x
 18
@@
 21
-22
+22      x
 23
@@
 
+#
+
+We have reformatted section 5.2.1 to include the caveats as a bulleted list. FIXME abstract
+
 ****
@@
 
+#
+
+Each GCM run is very computationally intensive, so we ran a few representative cases to see which factors (TiO/VO, metallicity, drag) had the largest effect on the phase curve shape.
+Our nominal GCM was a cloud-free, solar composition model with TiO/VO and no added drag.
+We changed the parameters one at a time to isolate what their effects were (removing TiO/VO, increasing metallicity, including drag).
+We found that including drag, rather than changing metallicity, is what makes the biggest difference in the phase curve shape and provides the best match to the data (see Figure 15).
+We clarified these points in the text in section 6.
+
 ****
@@
 It is the referee's preference however, that the magnetic field discussion is mostly scaled down or eliminated.
+
+#
+
+We expanded the discussion of magnetic fields according to the referee's suggestions.
+We think it is important to keep this section of the paper because even though this is just an order-of-magnitude result,
+
+we want to make the point that the planet's magnetic field may make an observable difference to the atmospheric dyanamics, providing a novel way to study.
 

### 2018-04-03 ApJ_submit_v2/ms.tex
point 17

@@
 \usepackage{graphicx}
+
+\newenvironment{my_itemize}{
+    \begin{itemize}
+              \setlength{\itemsep}{1pt}
+                    \setlength{\parskip}{0pt}
+                      \setlength{\parsep}{0pt}}{\end{itemize}
+                      }
 
@@
 
-We note that an important caveat for our results is that the best fit model is not a perfect fit to the data (with $\chi_\nu = 1.77$ for 9 degrees of freedom), so the uncertainties produced by the MCMC may be underestimated.
-Furthermore, the inferred C/O and metallicity are highly sensitive to the planet-to-star flux at \Spitzer\ $4.5\,\mu$m, which is the worst fit data point.
-To fit this data point, the model favors super-solar metallicities and C/O, which drive up the CO abundance (the dominant absorber at $4.5\,\mu$m).
-Given that the result hinges on a single photometric band and there are no spectrally resolved molecular features to constrain the temperature-pressure profile or which absorbers are present, we caution against over-interpreting these results until wider spectral coverage is available.
+\added{There are several caveats in our analysis which are important to note:}
+\begin{my_itemize}
+    \item {The best fit model is not a perfect fit to the data (with $\chi_\nu = 1.77$ for 9 degrees of freedom), so the uncertainties produced by the MCMC may be underestimated.} 
+    \item {The inferred C/O and metallicity are highly sensitive to the planet-to-star flux at \Spitzer\ $4.5\,\mu$m, which is the worst fit data point.
+To fit this data point, the model favors super-solar metallicities and C/O, which drive up the CO abundance (the dominant absorber at $4.5\,\mu$m).}
+    \item{\added{The \Spitzer\ $4.5\,\mu$m data is from broadband photometry, so the inferred CO feature is not spectrally resolved.
+It is possible that unknown absorbers or disequilibrium chemistry affect the $4.5\,\mu$m planet-to-star flux, but we cannot uniquely identify these features in our spectrum.}}
+\end{my_itemize}
+We therefore caution against over-interpreting these results until wider spectral coverage is available.
 
@@
 Our nominal GCM was a cloud-free, solar composition atmosphere with TiO/VO opacity and no added drag.
-We also ran models with enhanced metallicity ([M/H] = 0.5), no TiO/VO, and added atmospheric drag with timescales $\tau_\mathrm{drag} = 10^3$ and $10^4$ s, which we label $\tau_\mathrm{drag3}$ and $\tau_\mathrm{drag4}$, respectively.
+\added{Each GCM run is computationally intensive, so we ran a small number of additional models to see which parameters had the largest effect on the planet spectrum.
+We changed model parameters one at a time,} considering cases with enhanced metallicity ([M/H] = 0.5), no TiO/VO, and added atmospheric drag with timescales $\tau_\mathrm{drag} = 10^3$ and $10^4$ s, which we label $\tau_\mathrm{drag3}$ and $\tau_\mathrm{drag4}$, respectively.
 To assess how well the GCM predictions reproduce the data, we calculated the amplitude and hot spot offset for all the models (listed in Table\,\ref{table:amps_offsets}).
@@
 (FIXME: this is all comparison to WFC3 phase curve; add comparison to Spitzer too).
-
-To estimate the magnetic field required to produce a fast drag timescale of order $10^4$\,s, we computed the free electron abundance due to ionized metals for the $\tau_\mathrm{drag4}$ GCM.
-Using the order-of-magnitude expression from \cite{perna10} (Equation 12), we estimate a drag timescale at the substellar point of $\tau_\mathrm{drag}  = 2\times10^4/B^2$ s, where $B$ is the magnetic field in Gauss.
-We assume a temperature and pressure of 3359 K and 0.11 bar, %(FIXME use correct values for drag4)
-and that the magnetic field is perpendicular to the flow.
-To reach a drag timescale of $10^4$\,s, a magnetic field stronger than $\sim1$ Gauss is required.
-This value is comparable to Jupiter's magnetic field strength of 5-10 Gauss \citep{bagenal04}.
 
@@
 The GCM has solar metallicity, whereas the best fit 1D model has $[M/H] \sim 1$.
-Higher metallicity compositions have larger TiO/H2O ratios, and since the pressure dependence of TiO dissociation is not as strong as for water dissociation, we expect stronger inversions for higher metallicity atmospheres.
+Higher metallicity compositions have larger TiO/H$_2$O ratios, and since the pressure dependence of TiO dissociation is not as strong as for water dissociation, we expect stronger inversions for higher metallicity atmospheres.
 On the nightside, we also find that the GCM is cooler than the 1D models.
@@
 Our observations are not precise enough to detect water features on the nightside of the planet (see \S\,\ref{sec:comparison}), but future high precision data may be sensitive to these features, and will help constrain the strength of horizontal transport in the atmosphere \citep{agundez14}.
+
+\subsection{Constraints on the Planet's Magnetic Field}
+\added{We showed in this section that the small observed hotspot offset in the phase curves is best fit by a GCM that includes magnetic drag with a timescale $\tau_\mathrm{drag} = 10^4$\,s.
+This observation gives rise to the question: what magnetic field strength on the planet can produce drag with this timescale?
+Previous efforts to characterize exoplanet magnetic fields have mainly focused on magnetic interaction between the planet and its host star \citep[e.g.][and references therein]{wright17}.
+A complementary approach is to study the effect of the magnetic field on the planet's atmospheric dynamics.}
+
+Here we make a simple order-of-magnitude estimate for the magnetic field required to produce a drag timescale of order $10^4$\,s.
+We first computed the free electron abundance due to ionized metals for the $\tau_\mathrm{drag4}$ GCM.
+Using the analytic expression from \cite{perna10} (Equation 12), we estimated a drag timescale at the substellar point of $\tau_\mathrm{drag}  = 2\times10^4/B^2$ s, where $B$ is the magnetic field in Gauss.
+We assumed a temperature and pressure of 3359 K and 0.11 bar, %(FIXME use correct values for drag4)
+and that the magnetic field is perpendicular to the flow.
+To reach a drag timescale of $10^4$\,s, a magnetic field stronger than $\sim1$ Gauss is required, comparable to Jupiter's magnetic field strength of 5-10 Gauss \citep{bagenal04}.
+\added{To confirm this intriguing result, more detailed study is warranted, including a full magnetic hydrodynamic simulation of the atmospheric dynamics \citep[e.g.][]{rogers17} and accounting for possible complex magnetic field structure due to interactions between the magnetic fields of the planet and the star.}
 

### 2018-04-04 ApJ_submit_v2/response.txt
points 19

@@
 19	x
-20
-21
+20      x
+21      x
 22      x
@@
 We expanded the discussion of magnetic fields according to the referee's suggestions.
-We think it is important to keep this section of the paper because even though this is just an order-of-magnitude result,
-
-we want to make the point that the planet's magnetic field may make an observable difference to the atmospheric dyanamics, providing a novel way to study.
+We think it is important to keep this section of the paper because it opens up discussion about a new way of measuring planet magnetic fields (studying their effects on the atmospheric dynamics, in contrast to previous work, which focused on star-planet interactions).
+We put this discussion in a new subsection (6.1), added references to previous work, and mentioned the suggested caveats.
+We also clarified in the abstract that our estimate of the magnetic field is based on a back of the envelope calculation.
 
@@
 I think it's good to test the models and see what they can do when confronted with data, but at the same time I think the authors have over interpreted what has come out of the GCMs, as stated before.
+
+#
 
@@
 
+#
+
+Our goal for this plot was to show differences in the relative flux in and out of the water feature (the amplitudes A1 and A2), rather than comparing the absolute flux.
+The absolute flux levels are dependent on the radius of the object -- for example, the directly imaged companions have inflated radii, so their absolute fluxes are higher.
+Therefore, to make an apples-to-apples comparison between objects, we normalize the spectra by their absolute flux to calculate the indices A1 and A2.
+This is why we chose not to plot all the spectra on the same absolute scale, and instead use a different y-axis for each to better illustrate the relative water feature amplitude.
+
 ****
@@
 I would encourage the authors (if they feel like it) to bold a statement in each of the bullet points as well.
+
+#
+
+Thanks! We had trouble indentifying a single sentence in each bullet to bold, so this time we decided to leave it as is.
 

### 2018-04-04 ApJ_submit_v2/ms.tex
points 19

@@
 \begin{abstract}
-	We present thermal phase curve measurements for the hot Jupiter WASP-103b observed with \emph{Hubble}/WFC3 and \emph{Spitzer}/IRAC.
+%	We present thermal phase curve measurements for the hot Jupiter WASP-103b observed with \emph{Hubble}/WFC3 and \emph{Spitzer}/IRAC.
 The dayside planet-to-star flux ratios are $0.151\pm0.015\%$, $0.446\pm0.038\%$, and $0.569\pm0.014\%$ in bandpasses centered at $1.4$, $3.6$, and $4.5\mu$m, respectively.
@@
 In contrast to cooler hot Jupiters, we do not detect significant water absorption, which we attribute to partial H$_2$O dissociation and additional opacity from H- and trace amounts of hydrides/oxides.
-We compare the phase curves to 3D general circulation models and find that atmospheric drag with a timescale of $10^4$ s is the best match to the data, suggesting the presence of a magnetic field with strength $\sim1$ Gauss.
+We compare the phase curves to 3D general circulation models and find that atmospheric drag with a timescale of $10^4$ s is the best match to the data, which can be produced with a simple model of the magnetic field with strength $\sim1$ Gauss.
+We also compare the WASP-103b spectra to brown dwarfs and young directly imaged companions and find these more massive and self-luminous objects have significantly larger water features, indicating that surface gravity and irradiation environment play an important role in shaping the spectra of hot Jupiters.
+These results highlight the 3D structure of exoplanet atmospheres and illustrate the importance of phase curve observations for understanding their complex chemistry and physics.
+	We present thermal phase curve measurements for the hot Jupiter WASP-103b observed with \emph{Hubble}/WFC3 and \emph{Spitzer}/IRAC.
+The phase curves have large amplitudes and negligible hotspot offsets, indicative of poor heat redistribution to the nightside.
+We fit the phase variation with a range of climate maps and find that a spherical harmonics model generally provides the best fit.
+The phase-resolved spectra are consistent with blackbodies in the WFC3 bandpass, with brightness temperatures ranging from $1880\pm40$ K on the nightside to $2930 \pm 40$ K on the dayside.
+The dayside spectrum has a significantly higher brightness temperature in the \Spitzer\ bands, which we attribute to CO emission and a thermal inversion.
+The inversion is not present on the nightside.
+The transmission spectrum is featureless, but consistent with the small transit depth variation expected from cloud-free models.
+Using the dayside and nightside emission spectra, we retrieved the atmospheric composition with a 1D self-consistent modeling technique and found the atmosphere is moderately metal-enriched ($\mathrm{[M/H]} =  23^{+29}_{-13}\times$ solar) and the carbon-to-oxygen ratio is below 0.9 at $3\,\sigma$ confidence.
+In contrast to cooler hot Jupiters, we do not detect significant water absorption, which we attribute to partial H$_2$O dissociation and additional opacity from H- and trace amounts of hydrides/oxides.
+We compare the phase curves to 3D general circulation models and find that magnetic drag effects are needed match the data; a back-of-the-envelope calculation suggests the strength of the magnetic field is $\sim1$ Gauss.
 We also compare the WASP-103b spectra to brown dwarfs and young directly imaged companions and find these more massive and self-luminous objects have significantly larger water features, indicating that surface gravity and irradiation environment play an important role in shaping the spectra of hot Jupiters.
@@
 To reach a drag timescale of $10^4$\,s, a magnetic field stronger than $\sim1$ Gauss is required, comparable to Jupiter's magnetic field strength of 5-10 Gauss \citep{bagenal04}.
-\added{To confirm this intriguing result, more detailed study is warranted, including a full magnetic hydrodynamic simulation of the atmospheric dynamics \citep[e.g.][]{rogers17} and accounting for possible complex magnetic field structure due to interactions between the magnetic fields of the planet and the star.}
+\added{To confirm this intriguing result, more detailed study is warranted, including a full magnetic hydrodynamic simulation of the atmospheric dynamics \citep[e.g.][]{rogers17} and accounting for the possibility of complex magnetic field structure due to interactions between the magnetic fields of the planet and the star.}
 

### 2018-04-04 ApJ_submit_v2/response.txt
point 8

@@
 (This may be as simple as showing that other works show similar effects or that there are other works with elevated red noise in all channels but have shown that this does not affect the end results).
+
+#
+
+This is a good point, and something that concerned us as well. However, there
+are several reasons we believe our inferences about the spectroscopic light
+curves are not affected by the additional noise in the white light curve:
+
+One is that the astrophysical signal is wavelength dependent -- the
+eclipse depths increase by 50% from the bluest channel to the reddest channel.
+But for the white light curve, we sum up the whole signal and fit it with a
+single phase curve model. We expect systematic scatter in the phase curve due to
+the wavelength dependence of the astrophysical signal.
+
+An additional consideration is that the white light curve is more strong affected by loss of light off the
+detector edge than the spectroscopic light curves. The spectrum moves slightly
+on the detector over the course of a visit. Our white light curve
 

### 2018-04-04 ms.tex
point 8

@@
 	\tablewidth{0pt}
-	\tablecaption{Phase-Resolved Emission Spectra\tablenotemark{1} \label{table:spectra}}
+	\tablecaption{Phase-Resolved Emission Spectra \label{table:spectra}}
 	\tablehead{
@@
 		\enddata
-		\tablenotetext{1}{The planet-to-star flux in each phase bin $\phi$ is in units of ppm.}
+		\tablecomments{The planet-to-star flux in each phase bin $\phi$ is in units of ppm.}
 	\end{deluxetable*}
@@
 If the phase variation is absorbed into the systematic model, the measured eclipse depths would be biased low.
-\added{From a glance at \ref{fig:model_comparison}, the amplitude of this effect is} $\sim100$ ppm, \added{which is comparable to the offset between the two analyses}.
+\added{From a glance at Figure\,\ref{fig:model_comparison}, the amplitude of this effect is} $\sim100$ ppm, \added{which is comparable to the offset between the two analyses}.
 Our estimated uncertainties are a factor of four smaller than those reported in \cite{cartier17}, which is consistent with photon-limited expectations (our data set includes two additional eclipses, a factor of five longer out-of-eclipse baseline, and has 60\% larger wavelength bins).
@@
 Our observations are not precise enough to detect water features on the nightside of the planet (see \S\,\ref{sec:comparison}), but future high precision data may be sensitive to these features, and will help constrain the strength of horizontal transport in the atmosphere \citep{agundez14}.
+
+\subsection{Constraints on the Planet's Magnetic Field}
+\added{We showed in this section that the small observed hotspot offset in the phase curves is best fit by a GCM that includes magnetic drag with a timescale $\tau_\mathrm{drag} = 10^4$\,s.
+This observation gives rise to the question: what magnetic field strength on the planet can produce drag with this timescale?
+Previous efforts to characterize exoplanet magnetic fields have mainly focused on magnetic interaction between the planet and its host star \citep[e.g.][and references therein]{wright17}.
+A complementary approach is to study the effect of the magnetic field on the planet's atmospheric dynamics.}
+
+Here we make a simple order-of-magnitude estimate for the magnetic field required to produce a drag timescale of order $10^4$\,s.
+We first computed the free electron abundance due to ionized metals for the $\tau_\mathrm{drag4}$ GCM.
+Using the analytic expression from \cite{perna10} (Equation 12), we estimated a drag timescale at the substellar point of $\tau_\mathrm{drag}  = 2\times10^4/B^2$ s, where $B$ is the magnetic field in Gauss.
+We assumed a temperature and pressure of 3359 K and 0.11 bar, %(FIXME use correct values for drag4)
+and that the magnetic field is perpendicular to the flow.
+To reach a drag timescale of $10^4$\,s, a magnetic field stronger than $\sim1$ Gauss is required, comparable to Jupiter's magnetic field strength of 5-10 Gauss \citep{bagenal04}.
+\added{To confirm this intriguing result, more detailed study is warranted, including a full magnetic hydrodynamic simulation of the atmospheric dynamics \citep[e.g.][]{rogers17} and accounting for the possibility of complex magnetic field structure due to interactions between the magnetic fields of the planet and the star.}
 

### 2018-04-04 ApJ_submit_v2/response.txt
point 11

--- 2018-04-04 ApJ_submit_v2/response.txt
@@
 7       x
-8
+8       x
 9       x
@@
 (This may be as simple as showing that other works show similar effects or that there are other works with elevated red noise in all channels but have shown that this does not affect the end results).
+
+#
+
+This is a good point, and something that concerned us as well.
+We endeavor to explain more clearly here why our inferences about the spectroscopic light curves are not affected by the additional noise in the white light curve.
+
+One point (that we mentioned but not in great detail) is that the white light curve is more strong affected by loss of light off the detector edge than the spectroscopic light curves.
+The spectrum moves slightly on the detector over the course of a visit.
+We correct for this shift by interpolating the spectrum onto a common wavelength scale.
+However, we cannot correct for any flux lost off the edge of the detector.
+Flux loss at the edge is relevant for the white light curve, since it encapsulates all the flux, but does not affect the spectroscopic light curves, which are limited in wavelength range and do not extend all the way to the edge.
+In general we find that our rms is very sensitive to the size of our extraction window, so we think this effect is a plausible explanation for additional noise in the white light curve.
+
+Another important consideration that we neglected to mention is that the astrophysical signal is wavelength dependent -- the eclipse depths increase by 50% from the bluest channel to the reddest channel.
+But for the white light curve, we sum up the whole signal and fit it with a single phase curve model.
+Therefore, we expect a systematic scatter in the phase curve due to the wavelength dependence of the astrophysical signal.
+
+A final point is that there are multiple cases of exoplanet transmission spectra measured with WFC3 that are consistent with a flat line at higher precision than what we measure here (e.g.
+Kreidberg et al.
+2014).
+If wavelength-dependent systematic noise were present in data from this detector, it would be very challenging to measure a flat spectrum (you would have to conspire to have the planet signal cancel out the instrumental effects).
+There is nothing unusual about our data set (the fluence level and scan rate are very comparable to what has been observed before), so it is reasonable to expect that our data does not suffer from a systematic bias.
 

### 2018-04-04 ApJ_submit_v2/ms.tex
point 11

@@
 For the WFC3 band-integrated white light curve, the rms was slightly larger than predicted (172 versus 122 ppm).
-There are a number of possible origins for this discrepancy, including imperfect background subtraction, variation in the position of the spatial scan on the detector, loss of flux outside the extraction window, and imperfect modeling of the astrophysical signal or instrument systematics.
+There are a number of possible origins for this discrepancy, including imperfect background subtraction, variation in the position of the spatial scan on the detector, and loss of flux outside the extraction window.
+\added{In addition, the amplitude of the phase variation increases by 50\% over the WFC3 wavelength range, which leads to a small increase in the noise in the white light curve.
+To make an order of magnitude estimate for the amplitude of this effect, we calculate the standard deviation of the secondary eclipse depths in all wavelength channels.
+It is $\sim100$ ppm, which is comparable to the additional scatter we observed FIxme}
+
 However, our analysis of the composition and thermal structure of the planet's atmosphere is based on the wavelength-dependent data (where we reach the photon limit), so we do not further explore the small excess noise in the white light curve.

### 2018-04-05 ApJ_submit_v2/response.txt
minor comments

--- 2018-04-04 ApJ_submit_v2/response.txt
@@
 11      x
-12
+12      x
 13
@@
 
+#
+
+This is a good point, and something that concerned us as well.
+We endeavor to explain more clearly here why our inferences about the spectroscopic light curves are not affected by the additional noise in the white light curve, and have also added this discussion to section 3.4.
+
+An important consideration that we neglected to mention is that the astrophysical signal is wavelength dependent -- the eclipse depths increase by 50% from the bluest channel to the reddest channel.
+But for the white light curve, we sum up the whole signal and fit it with a single phase curve model.
+Therefore, we expect a systematic scatter in the phase curve due to the wavelength dependence of the astrophysical signal.
+To make an order of magnitude estimate for the amplitude of this effect, we calculated the standard deviation of the secondary eclipse depths in all wavelength channels.
+It is $\sim100$ ppm, which is comparable to the additional scatter we observed in the white light curve.
+
+In addition, there are multiple cases of exoplanet transmission spectra measured with WFC3 that are consistent with a flat line at higher precision than what we measure here (e.g.
+Kreidberg et al.
+2014).
+If wavelength-dependent systematic noise were present in data from this detector, it would be very challenging to measure a flat spectrum (you would have to conspire to have the planet signal cancel out the instrumental effects).
+There is nothing unusual about our data set (the fluence level and scan rate are very comparable to what has been observed before), so it is reasonable to expect that our data does not suffer from a systematic bias.
+
 ****
@@
 Therefore I request the authors to more robustly argue that the brightness temperature are indeed significantly different between the nightside and dayside of the planet, put a confidence value on this difference, and explain why many of the intermediate phases show different behavior than what is suggested in the text for the nightside-dayside dichotomy.
+
+#
+
+This is a really subtle point and we are glad the referee raised it. Here is our clarification:
+
+It is somewhat misleading to evaluate the presence or absence of a thermal inversion based on the brightness temperatures reported in Table 6.
+The reason is that these temperatures account for uncertainty in the *stellar* effective temperature (+/- 160 K), as described in section 5.1.
+Therefore, the uncertainties in the table are correlated with each other.
+If the stellar temperature is higher, all the brightness temperatures would be higher, and vice versa if the stellar temperature is lower.
+When we hold the stellar temperature fixed, the error bars on brightness temperature shrink substantially (for example, the error on the dayside WFC3 brightness temperature is +/-8 Kelvin), and the temperatures at different wavelengths are discrepant at more than 3 sigma confidence.
+This can also be seen by eye in Figure 7, where the Spitzer 4.5 micron point is significantly higher than the blackbody (dashed line).
+
+Our statements about the inversion on the dayside and the lack of inversion on the nightside are motivated by the retrieval results presented in section 5.2.
 
@@
 1. Introduction, paragraph 2: Don't short change the small (but useful) handful of directly imaged planets when you say exoplanets are not resolved from their host stars.
+#
+Done.
 
 2. Introduction paragraph 2: "The observations revealed large day-night..." should say "These observations revealed large day-night..."
+#
+Done.
 
@@
 This is fine, but I would ask the authors to specifically name the planets in this case, since it's not widely observed.
+#
+There are actually 6 planets
 
@@
 Is this true or am I misreading it (and by extension figure 9)?
+#
+Good catch - we corrected this (and changed the table format so that uncertainty is in a separate column rather than being listed twice).
 

### 2018-04-05 ApJ_submit_v2/ms.tex
minor comments

@@
 
-Exoplanets are so distant that they are not spatially resolved from their host stars, but it is still possible to reveal inhomogeneities in their atmospheres.
+Exoplanets are so distant that they are generally not spatially resolved from their host stars, but it is still possible to reveal inhomogeneities in their atmospheres \added{by observing the total system flux}.
 One approach is to measure a phase curve, which consists of continuous monitoring of the planet-to-star flux ratio over a complete orbital revolution of the planet.
@@
 The first phase curve of an exoplanet was observed with \Spitzer\ for the hot Jupiter $\nu$ Andromedae b by \cite{harrington06}, followed by additional \Spitzer\ observations for about a dozen more systems \citep[cataloged in][]{parmentier17}.
-The observations revealed large day-night temperature contrasts (in excess of 300 K), and eastward shifted peak brightness due to heat circulation, as predicted by 3D models \citep{showman02}.
+These observations revealed large day-night temperature contrasts (in excess of 300 K), and eastward shifted peak brightness due to heat circulation, as predicted by 3D models \citep{showman02}.
 These infrared measurements were complemented by optical phase curves from \Kepler\ that show evidence for reflected light from patchy and possibly variable dayside clouds with a range of compositions \citep{borucki09, demory13, hu15, armstrong16, parmentier16}.
@@
 \added{In addition, the amplitude of the phase variation increases by 50\% over the WFC3 wavelength range, which leads to a small increase in the noise in the white light curve.
-To make an order of magnitude estimate for the amplitude of this effect, we calculate the standard deviation of the secondary eclipse depths in all wavelength channels.
-It is $\sim100$ ppm, which is comparable to the additional scatter we observed FIxme}
-
-However, our analysis of the composition and thermal structure of the planet's atmosphere is based on the wavelength-dependent data (where we reach the photon limit), so we do not further explore the small excess noise in the white light curve.
+To make an order of magnitude estimate for the amplitude of this effect, we calculated the standard deviation of the secondary eclipse depths in all wavelength channels.
+It is $\sim100$ ppm, which is comparable to the additional scatter we observed in the white light curve.}
+
+%However, our analysis of the composition and thermal structure of the planet's atmosphere is based on the wavelength-dependent data (where we reach the photon limit), so we do not further explore the small excess noise in the white light curve.
 
@@
 The resulting brightness temperatures and $1\,\sigma$ uncertainties are listed in Table\,\ref{table:teffs}.
-The WFC3 data agree well by a blackbody model at all orbital phases except phase 0.5 (consistent at better than $1.5\,\sigma$).
+\added{We note that the uncertainties on the brightness temperatures in different bandpasses are correlated with each other because they include the uncertainty on the stellar temperature: i.e., if the stellar temperature increases, so do the brightness temperatures.
+To evaluate the significance of features in the emission spectra, we perform a retrieval analysis with the stellar spectrum held constant, as described in \S\,\ref{sec:retrieval}.}
+
+FIXME The WFC3 data agree well by a blackbody model at all orbital phases except phase 0.5 (consistent at better than $1.5\,\sigma$).
 The dayside has higher signal-to-noise than the other orbital phases, thanks to the two secondary eclipse observations from \cite{cartier17}.
@@
 \item{The \Spitzer\ data are \emph{not} consistent with the best fit blackbody to the WFC3 data: they have a higher brightness temperature at phases $\phi = 0.2 - 0.5$, which transitions to a lower brightness temperature on the nightside ($\phi = -0.2 - 0.1$).
-These characteristics are likely due to CO features in the infrared and a temperature inversion on the dayside but not the nightside.}
+\added{An atmospheric retrieval analysis suggests that} these characteristics are likely due to CO features in the infrared and a temperature inversion on the dayside but not the nightside.}
 \item{The measured transmission spectrum is featureless (after correcting for nightside emission from the planet).

### 2018-04-05 ms.tex
minor comments

@@
 For the WFC3 band-integrated white light curve, the rms was slightly larger than predicted (172 versus 122 ppm).
-There are a number of possible origins for this discrepancy, including imperfect background subtraction, variation in the position of the spatial scan on the detector, loss of flux outside the extraction window, and imperfect modeling of the astrophysical signal or instrument systematics.
-However, our analysis of the composition and thermal structure of the planet's atmosphere is based on the wavelength-dependent data (where we reach the photon limit), so we do not further explore the small excess noise in the white light curve.
+There are a number of possible origins for this discrepancy, including imperfect background subtraction, variation in the position of the spatial scan on the detector, and loss of flux outside the extraction window.
+\added{In addition, the amplitude of the phase variation increases by 50\% over the WFC3 wavelength range, which leads to a small increase in the noise in the white light curve.
+To make an order of magnitude estimate for the amplitude of this effect, we calculated the standard deviation of the secondary eclipse depths in all wavelength channels.
+It is $\sim100$ ppm, which is comparable to the additional scatter we observed in the white light curve.}
+
+%However, our analysis of the composition and thermal structure of the planet's atmosphere is based on the wavelength-dependent data (where we reach the photon limit), so we do not further explore the small excess noise in the white light curve.
 

### 2018-04-05 ApJ_submit_v2/response.txt
finished response

@@
-1       x
-2       x
-3       x
-4       x
-5	x
-6       x
-7       x
-8       x
-9       x
-10	x
-11      x
-12      x
-13
-14      x-abstract
-15
-16      x
-17      x
-18
-19	x
-20      x
-21      x
-22      x
-23
-
 We thank the referee for his or her very thorough comments. We have made the suggested changes to the manuscript, and respond point-by-point below.
@@
 
+#
+
+We agree and moved the paragraphs on climate to Section 5.
+
 ===============================================
@@
 since it was not easily accessible in this paper.
+
+#
+
+We have added the main stellar and planetary parameters to the introduction.
 
@@
 The pipeline starts by identifying and flagging bad pixels using a double-iteration 4-sigma outlier rejection routine along the time axis.
-This is followed by performing 2D Gaussian centroiding on each frame, which is shown to provide the most precise centers for Spitzer data \citep{Lust2014}.
+This is followed by performing 2D Gaussian centroiding on each frame, which is shown to provide the most precise centers for Spitzer data (Lust et al.
+2014).
 The target remains centered near the sweet spot for the entire AOR in each observation, with a maximum drift of 0.1 pixels.
-Next, POET uses sub-pixel (5\times-interpolated) aperture photometry \citep{Harrington2007} to subtract the background and sum the flux within a specified radius.
+Next, POET uses sub-pixel (5x-interpolated) aperture photometry (Harrington et al.
+2007) to subtract the background and sum the flux within a specified radius.
 Chosen from a grid of apertures between 2 and 4 pixels, we find that an aperture size of 2.75 pixels minimizes the residual noise in the light curve fits.
@@
 The contaminating flux from the nearby star is within the same pixel as the target, so we included it in the photometry and corrected it in the light curve fits.
-A similarly strategy has been applied to successfully analyze dozens of Spitzer data sets \citep[e.g.
-][]{Stevenson2010, Stevenson2012a, Stevenson2012b, Stevenson2014a, Stevenson2014b, Stevenson2016a, Stevenson2017a, Campo2011, Nymeyer2011, Cubillos2013, Blecic2013, Blecic2014, HDL2014}.
+A similarly strategy has been applied to successfully analyze dozens of Spitzer data sets (e.g.
+Stevenson et al.
+2010, 2012a, 2012b, 2014a, 2014b, 2016a, 2017a, Campo et al.
+2011, Nymeyer et al.
+2011, Cubillos et al.
+2013, Blecic et al.
+2013, Blecic et al.
+2014, Diamond-Lowe et al.
+2014).
 
@@
 Warm Spitzer's primary systematic is intrapixel sensitivity variations, where the photometry depends on the precise location of the stellar center within its pixel.
-We fit this systematic using the Bilinearly-Interpolated Subpixel Sensitivity (BLISS) mapping technique \citep{Stevenson2012a}.
+We fit this systematic using the Bilinearly-Interpolated Subpixel Sensitivity (BLISS) mapping technique (Stevenson et al.
+2012a).
 BLISS provides a flexible, non-analytic means to effectively weight the target flux by the spatial sensitivity variations within a pixel, while simultaneously fitting for other systematics and the physical parameters of the system.
-As has been demonstrated by \citet{Ingalls2016}, the POET pipeline with BLISS mapping can accurately model simulated {\em Spitzer} light curves with known physical parameters and produce reliable results.
+As has been demonstrated by Ingalls et al.
+2016, the POET pipeline with BLISS mapping can accurately model simulated Spitzer light curves with known physical parameters and produce reliable results.
 
@@
 program star is not significantly different than the comparison stars and so not
-discernible by eye from a plot.  FIXME
+discernible by eye from a plot.
 
@@
 #
-Since we considered so many different cases (four different phase variation models for broadband and spectroscopic light curves), we elected to run an MCMC only for cases where we ereport 68% confidence intervals on the model parameters.
+Since we considered so many different cases (four different phase variation models for broadband and spectroscopic light curves), we elected to run an MCMC only for cases where we report 68% confidence intervals on the model parameters.
 These include the transit models (for the transit depth) and the sine curve models (for the phase amplitude and offset reported in Table 2).
@@
 Therefore, we expect a systematic scatter in the phase curve due to the wavelength dependence of the astrophysical signal.
-To make an order of magnitude estimate for the amplitude of this effect, we calculated the standard deviation of the secondary eclipse depths in all wavelength channels.
+To make an order of magnitude estimate for the amplitude of this effect, we calculated the standard deviation of the dayside secondary eclipse depths in all wavelength channels.
 It is $\sim100$ ppm, which is comparable to the additional scatter we observed in the white light curve.
@@
 
-Our statements about the inversion on the dayside and the lack of inversion on the nightside are motivated by the retrieval results presented in section 5.2.
+To evaluate the presence or absence of a thermal inversion, we carry out a retrieval analysis with the temperature of the star held fixed.
+Our statements about the inversion on the dayside and the lack of inversion on the nightside are motivated by the retrieval, not the simple calculation of brightness temperature.
+We added a few sentences to the end of section 5.1 and the bullet point in section 8 to clarify this point.
 
@@
 
+#
+
+We fit the dayside spectrum only (phase 0.46 -0.54) and now state this explicitly in section 5.2.
+Our response to point 13 above addresses the issue of the significance of the different brightness temperatures at Hubble vs.
+Spitzer wavelengths.
+Our retrieval analysis holds the temperature of the star fixed, and as shown in Figure 12, the dayside T/P profile is clearly inverted.
+It is still true that there are some caveats about our conclusions from the retrieval, which are now bulleted at the end of section 5.2.1 (see our response to point 14 below).
+
 ****
@@
 
-We have reformatted section 5.2.1 to include the caveats as a bulleted list. FIXME abstract
+We have reformatted section 5.2.1 to include the caveats as a bulleted list.
+Since the caveats are now stated very prominently in 5.2.1 and in the summary bullet point in Section 8, we are confident that readers will not miss them.
+We did not add these points to the abstract because it is over the length limit, and we feel the impact of the paper will be greater if we focus scientific results in the abstract and leave the caveats in the main text.
 
@@
 This may also be a useful exercise for the dayside spectrum (fit at phase 0.4 and phase 0.6, or something similar).
+
+#
+
+A full atmospheric retrieval is actually quite computationally intensive.
+Since the nightside spectra are qualitatively similar (consistent with a blackbody at WFC3 wavelengths and lower temperature in the Spitzer bands), we do not expect any different result from fitting one phase bin over the other.
+Moreover, as the referee notes, we already found that the nightside spectrum (at phase 0.1) is too imprecise to tightly constrain the metallicity or C/O.
+The spectrum at phase 0.9 is no higher precision.
+If the only purpose in running a retrieval is to verify that we can't tightly constrain metallicity and C/O, a full retrieval seems like overkill.
 
@@
 We expanded the discussion of magnetic fields according to the referee's suggestions.
-We think it is important to keep this section of the paper because it opens up discussion about a new way of measuring planet magnetic fields (studying their effects on the atmospheric dynamics, in contrast to previous work, which focused on star-planet interactions).
+We think it is important to keep this section of the paper because it opens up discussion about a new way of measuring planet magnetic fields (studying their effects on the atmospheric dynamics, in contrast to previous work, which focused on star-planet interactions or planetary radio emission).
 We put this discussion in a new subsection (6.1), added references to previous work, and mentioned the suggested caveats.
@@
 #
+
+We should have been more careful when describing whether the GCMs fit "well" or not.
+Our intent was to say that none of the models are perfect: there is some degeneracy in the SPIDERMAN maps, and the GCM is too cold on the nightside.
+Additional modeling and observations are required to robustly constrain the climate.
+We reworded the paragraph in question to say this more directly.
+
+More broadly, given that the GCM is a prediction, we don't expect it to fit as perfectly as a tuned model fit (like the SPIDERMAN models).
+Our goal in this section was to determine which physical parameters (C/O, magnetic drag, etc.) are qualitatively important in shaping the spectrum.
+The main take-away point is that the magnetic drag is the biggest factor in reducing the hotspot offset.
+As we said in our response to point 17 above, we added some text emphasizing that the magnetic field inference is an order-of-magnitude estimate only, and more detailed modeling is needed for a precise characterization of the magnetic field.
 
@@
 
+#
+
+Yes! We made a few small changes to the bulleted points in Section 8.
+
 ****
@@
 I think this is too strong a statement, and has not been exhaustively researched and concluded to be the only explanation here (see previous comments).
+
+#
+
+We softened the language here to suggest that magnetic fields *may* play a a role in shaping the circulation patterns.
 
@@
 #
-There are actually 6 planets
+There are actually 6 planets where dayside reflected light may be playing a role in the phase curve shape (see Paramentier et al. 2016), so rather than list all these we just keep the citations.
 
 4.Section 2.3 Photometric Monitoring - The filter (Cousins R) should be in italics, as photometric passbands typically are.
+#
+FIXME - Greg, can you fix this?
 
 5. Section 3.2.2 - Please put in parentheses next to the pixel sizes what this is in terms of arcseconds
+#
+Done.
 
 6. Please clarify at the end of 3.3 that a \gamma = 1.1 for the power spectral density of red noise implies an equal amount of uncorrelated white noise and correlated noise.
+#
+Done.
 
@@
 This is made more difficult for the reader as there is no table with the system parameters present in the paper with which to easily look it up.
+#
+Done.
 
 8. Section 4.5, Is the linear limb darkening parameter picked per bin? And is it initialized near some value (presumably from Claret)?
+#
+Yes, we fit a separate limb darkening parameter in each bin. We initialize our
+MCMC on the best least squares fit (generally near 0.2). We added this
+clarification to section 3.1.
 
@@
 The citations to these papers should be removed unless a publicly available version becomes available.
+#
+These papers are a part of a series related to emission spectra of the most highly irradiated planets, so we want to keep the references.
+We plan to post them to the arxiv at the same time, and then add the arxiv citations as soon as they are available.
 
@@
 I would like this statement presented here as well, as I consider that a much more useful result than a number with a huge error bar.
+#
+Done.
 
@@
 I suppose since the prior was uniform and the upper bound on the prior is 3 sigma away this is fine and you can measure the peak and shape of the distribution regardless, but can the authors confirm that you're not significantly running into the walls of your prior?
+#
+FIXME -- Mike, what motivated the upper bound?

### 2018-04-05 ApJ_submit_v2/ms.tex
finished response

@@
 	We present thermal phase curve measurements for the hot Jupiter WASP-103b observed with \emph{Hubble}/WFC3 and \emph{Spitzer}/IRAC.
+The dayside planet-to-star flux ratios are $0.151\pm0.015\%$, $0.446\pm0.038\%$, and $0.569\pm0.014\%$ in bandpasses centered at $1.4$, $3.6$, and $4.5\mu$m, respectively.
 The phase curves have large amplitudes and negligible hotspot offsets, indicative of poor heat redistribution to the nightside.
@@
 In contrast to cooler hot Jupiters, we do not detect significant water absorption, which we attribute to partial H$_2$O dissociation and additional opacity from H- and trace amounts of hydrides/oxides.
-We compare the phase curves to 3D general circulation models and find that magnetic drag effects are needed match the data; a back-of-the-envelope calculation suggests the strength of the magnetic field is $\sim1$ Gauss.
-We also compare the WASP-103b spectra to brown dwarfs and young directly imaged companions and find these more massive and self-luminous objects have significantly larger water features, indicating that surface gravity and irradiation environment play an important role in shaping the spectra of hot Jupiters.
+We compare the phase curves to 3D general circulation models and find that magnetic drag effects are needed match the data; \added{a back-of-the-envelope calculation suggests the strength of the magnetic field is $\sim1$ Gauss.}  We also compare the WASP-103b spectra to brown dwarfs and young directly imaged companions and find these more massive and self-luminous objects have significantly larger water features, indicating that surface gravity and irradiation environment play an important role in shaping the spectra of hot Jupiters.
 These results highlight the 3D structure of exoplanet atmospheres and illustrate the importance of phase curve observations for understanding their complex chemistry and physics.
@@
 
-Exoplanets are so distant that they are generally not spatially resolved from their host stars, but it is still possible to reveal inhomogeneities in their atmospheres \added{by observing the total system flux}.
+Exoplanets are so distant that they are \added{generally} not spatially resolved from their host stars, but it is still possible to reveal inhomogeneities in their atmospheres \added{by observing the total system flux}.
 One approach is to measure a phase curve, which consists of continuous monitoring of the planet-to-star flux ratio over a complete orbital revolution of the planet.
@@
 
-In this paper we present spectroscopic phase curve observations of the hot Jupiter WASP-103b, measured with \HST/WFC3 and Spitzer/IRAC.
-This planet is an ideal target for phase curve observations, with an orbital period of just 22 hours and an equilbrium temperature of 2500 K \citep{gillon14}.
-Previous observations of WASP-103b's atmosphere revealed a blackbody-like dayside emission spectrum, with possible evidence for a $K_\mathrm{S}$-band emission feature \citep{cartier17, delrez18}.
+In this paper we present spectroscopic phase curve observations of the hot
+Jupiter WASP-103b, measured with \HST/WFC3 and Spitzer/IRAC. This planet is an
+ideal target for phase curve observations, with an orbital period of just 22
+hours and an equilbrium temperature of 2500 K.  \added{WASP-103b is slightly
+larger than Jupiter, with a mass and radius of $1.49\pm0.09\,M_\mathrm{Jup}$ and
+$1.53^{+0.05}_{-0.07}\,R_\mathrm{Jup}$, respectively.
+The host star is a main-sequence F8 dwarf with an effective temperature of $6110 \pm 160\,$ K \citep{gillon14}.} Previous observations of WASP-103b's atmosphere revealed a blackbody-like dayside emission spectrum, with possible evidence for a $K_\mathrm{S}$-band emission feature \citep{cartier17, delrez18}.
 The optical transmission spectrum shows evidence for sodium and potassium absorption features that are consistent with expectations for a cloud-free atmosphere \citep{lendl17}.%, though other observations have shown a large optical scattering slope that is not fit well by theoretical models \citep{southworth16}.
@@
 We found that the transit parameters are consistent with the \cite{southworth15} results, so we proceeded with the remainder of the analysis holding those parameters fixed.
-The free parameters for the transit model were the transit depth $r_p$ and a linear limb darkening parameter $u$.
+The free parameters for the transit model were a \added{wavelength-dependent} transit depth $r_p(\lambda)$ and linear limb darkening parameter $u(\lambda)$.
 More complex limb darkening laws with additional free parameters were not merited according to the Bayesian Information Criterion (BIC).
+\added{We initialized our MCMC chains on the least squares best fit parameters.}
 
@@
 To avoid overfitting, we chose the grid scale such that bilinear interpolation performed better than nearest neighbor interpolation.
-For the $3.6\,\mu$m data, the grid scale was 0.008 pixel in both $x$ and $y$.
-For $4.5\,\mu$m, the scale was 0.022 pixel.
+For the $3.6\,\mu$m data, the grid scale was 0.008 pixel \added{(0.0098 arcsec)} in both $x$ and $y$.
+For $4.5\,\mu$m, the scale was 0.022 pixel \added{(0.027 arcsec)}.
 In addition to the intrapixel sensitivity variation, we fit the data for a linear trend in time.
@@
 We used a Haar wavelet and let the power spectral density of the red noise vary, following \cite{diamond-lowe14}.
-In our final fit, the noise power spectrum $1/f^\gamma$ had $\gamma = 1.1 \pm 0.1$.
-
+In our final fit, the noise power spectrum $1/f^\gamma$ had $\gamma = 1.1 \pm 0.1$ \added{(implying an equal amount of white noise and correlated noise)}.
 \subsection{Goodness of Fit}
@@
 %Ch2: rms obs, exp (ppm) 636.908048707 639.675550854
-We performed several tests of the quality of the light curve fits.
-First we predicted the level of scatter in the light curves based on photon noise alone, then compared this value to the root-mean-square (rms) of the fit residuals.
-For the spherical harmonics fit to the phase variation, the Spitzer 4.5 $\mu$m light curve rms reaches the expected photon noise limit (637 versus 640 ppm).
-The 3.6 $\mu$m light curve has significantly larger rms (767 versus 470 ppm), due to time-correlated red noise (discussed below).
-The expected photon-limited rms for the WFC3 spectrosopic light curves ranges from 430 - 530 ppm, and the measured rms was typically within 5\% of expectations for all spectroscopic channels.
-For the WFC3 band-integrated white light curve, the rms was slightly larger than predicted (172 versus 122 ppm).
-There are a number of possible origins for this discrepancy, including imperfect background subtraction, variation in the position of the spatial scan on the detector, and loss of flux outside the extraction window.
-\added{In addition, the amplitude of the phase variation increases by 50\% over the WFC3 wavelength range, which leads to a small increase in the noise in the white light curve.
-To make an order of magnitude estimate for the amplitude of this effect, we calculated the standard deviation of the secondary eclipse depths in all wavelength channels.
-It is $\sim100$ ppm, which is comparable to the additional scatter we observed in the white light curve.}
+We performed several tests of the quality of the light curve fits.  First we
+predicted the level of scatter in the light curves based on photon noise alone,
+then compared this value to the root-mean-square (rms) of the fit residuals.
+For the spherical harmonics fit to the phase variation, the Spitzer 4.5 $\mu$m
+light curve rms reaches the expected photon noise limit (637 versus 640 ppm).
+The 3.6 $\mu$m light curve has significantly larger rms (767 versus 470 ppm),
+due to time-correlated red noise (discussed below). The expected photon-limited
+rms for the WFC3 spectrosopic light curves ranges from 430 - 530 ppm, and the
+measured rms was typically within 5\% of expectations for all spectroscopic
+channels.  For the WFC3 band-integrated white light curve, the rms was slightly
+larger than predicted (172 versus 122 ppm). There are a number of possible
+origins for this discrepancy, including imperfect background subtraction,
+variation in the position of the spatial scan on the detector, and loss of flux
+outside the extraction window. \added{In addition, the amplitude of the phase
+variation increases by 50\% over the WFC3 wavelength range, which leads to a
+small increase in the noise in the white light curve. To make an order of
+magnitude estimate for the amplitude of this effect, we calculated the standard
+deviation of the secondary eclipse depths in all wavelength channels. It is
+$\sim100$ ppm, which is comparable to the additional scatter we observed in the
+white light curve.}
 
@@
 For the other orbital phases, we binned the light curve (with systematics
-removed) in eight intervals of about 0.1 in orbital phase, with endpoints at
+removed) in eight intervals of about 0.1 in orbital phase \added{(2.2 hours)}, with endpoints at
 phases $0.06, 0.15, 0.25, 0.35, 0.44$ and $0.56, 0.65, 0.75, 0.85, 0.94$. These
@@
 \end{figure*}
-
-\subsection{Climate}
-We fit three different models to characterize the planet's climate: a two-temperature map, the physically-motivated kinematic model of \cite{zhang17}, and a spherical harmonic map.
-We also fit the thermal phase variation with a sinusoid, which can be inverted to map the climate \citep{cowan08, cowan17}.
-All of the models provide reasonable fits to the data, with $\chi^2_\nu$ near unity, but they yield significantly different temperature maps.
-Table\,\ref{table:models} lists the best fit minimum and maximum temperatures, as well as the mean day- and nightside temperatures.
-We also list the  information criterion (BIC) values for the fits \citep[a $\Delta$BIC value greater than 10 constitutes strong evidence against a given model;][]{kass95}.
-
-%As illustrated in Figure\,\ref{fig:model_comparison}, the kinematic model is larger than the observed planet-to-star flux on the nightside, whereas the two temperature model overpredicts the flux at quadrature and underpredicts the dayside.
-
-The spherical harmonics map generally fits the data the best.
-It has a lower BIC value than all the other models for the broadband WFC3 and \Spitzer\,$3.6\,\mu$m phase curves.
-For the $4.5\,\mu$m phase curve, the two temperature map provides the best fit, but it only lowers the BIC value by 2 relative to the spherical harmonics map, which is not a statistically significant improvement \citep{kass95}.
-The spherical harmonics model yields a mean dayside temperature near 2700 K, whereas the nightside is closer to 1800 K, in good agreement with the blackbody fits to the phase-resolved spectra (see \S\,\ref{sec:bbfits}).
-The other models produce more extreme day-night temperature gradients.
-Between the models, there are substantial differences in the minimum and maximum temperatures (sometimes over 1000 K), whereas the day and nightside means are in better agreement (generally matching to within 250 K).
-This behavior is not surprising: a wide range of temperature gradients can yield similar average temperatures when integrated over the disk of the planet.
-
-%However, this model may not be physically realistic: on the nightside, it produces much higher temperatures at the poles than at the equator, contrary to predictions from GCMs (which we discuss in \S\,\ref{sec:gcm}).
-
-%The kinematic model has the hottest dayside temperature, and the two-temperature model has the smallest.
-The differences in peak temperature for the models we consider ranges from $630\,\mathrm{K}$ for \Spitzer\ Channel 1 to $1070\,\mathrm{K}$ for the broadband WFC3 light curve.
-The minimum nightside temperature is also model-dependent: for the WFC3 data, the two-temperature model predicts a nightside temperature of zero Kelvin, whereas the best fit kinematic model has a nightside temperature of $1980\,\mathrm{K}$.
 
@@
 
-\subsection{Comparison with Previous Observations}
+\subsection{Comparison with Previous Eclipse Observations}
 We compared our results to the dayside emission spectrum reported by \cite{cartier17}, which is based on a Gaussian process analysis of two secondary eclipses from \HST/WFC3.
@@
 We then performed a more sophisticated grid-based retrieval to estimate the atmospheric metallicity, carbon-to-oxygen ratio, and thermal structure.
+\added{We also evaluated the climate based on the best fit \texttt{spiderman} temperature maps.}
 
@@
 
-We also fit indepedent blackbody models to the \HST/WFC3 data and each \Spitzer\ channel separately.
+We also fit independent blackbody models to the \HST/WFC3 data and each \Spitzer\ channel separately.
 The resulting brightness temperatures and $1\,\sigma$ uncertainties are listed in Table\,\ref{table:teffs}.
-\added{We note that the uncertainties on the brightness temperatures in different bandpasses are correlated with each other because they include the uncertainty on the stellar temperature: i.e., if the stellar temperature increases, so do the brightness temperatures.
-To evaluate the significance of features in the emission spectra, we perform a retrieval analysis with the stellar spectrum held constant, as described in \S\,\ref{sec:retrieval}.}
-
-FIXME The WFC3 data agree well by a blackbody model at all orbital phases except phase 0.5 (consistent at better than $1.5\,\sigma$).
+The WFC3 data agree well by a blackbody model at all orbital phases except phase 0.5 (consistent at better than $1.5\,\sigma$).
 The dayside has higher signal-to-noise than the other orbital phases, thanks to the two secondary eclipse observations from \cite{cartier17}.
@@
 
+\added{We note that the uncertainties on the brightness temperatures in
+different bandpasses are correlated with each other because they include the
+uncertainty on the stellar temperature: i.e., if the stellar temperature
+increases, so do the brightness temperatures. To evaluate the significance of
+features in the emission spectra, we hold the stellar spectrum fixed in the retrieval analysis.}
 %This model performs well for some orbital phases, with $\chi^2_\nu$ ranging from 0.9 to 1.1 for phases $\phi = 0.1, 0.7$ and $0.8$.
@@
 \tablehead{
-\colhead{Orbital Phase} & \colhead{$T_\mathrm{b}$} & \colhead{$T_\mathrm{b}$} & \colhead{$T_\mathrm{b}$} & \colhead{$\chi^2_\nu$\tablenotemark{1}} \\
+\colhead{Orbital Phase} & \colhead{$T_\mathrm{b}$} & \colhead{$T_\mathrm{b}$} &
+\colhead{$T_\mathrm{b}$} & \colhead{$\chi^2_\nu$} \\
 \colhead{\,} & \colhead{WFC3} & \colhead{Ch. 1} & \colhead{Ch. 2} & \colhead{(9 dof)}}
@@
 \enddata
-\tablenotetext{1}{$\chi^2_\nu$ values are for the fits to the WFC3 data only.}
+\tablecomments{$\chi^2_\nu$ values are for the fits to the WFC3 data only.}
 \end{deluxetable}
@@
 \label{sec:retrieval}
-To infer abundances from the dayside spectrum, we use a self-consistent grid-based method (ScCHIMERA) similar to that employed in \cite{arcangeli18, mansfield18}.
+To infer abundances from the dayside spectrum \added{(phase $0.46 - 0.54$)}, we use a self-consistent grid-based method (ScCHIMERA) similar to that employed in \cite{arcangeli18, mansfield18}.
 We generated a grid from one-dimensional forward models of the atmosphere over a broad range of metallicities (M/H), carbon-to-oxygen ratios (C/O), and stellar irradiation ($f$).
@@
 We infer a range in metallicity of $23^{+29}_{-13}\times$ solar, somewhat higher than expected based on Jupiter's metal enrichment \citep[$3-5\times$ solar;][]{wong04} and the trend toward decreasing metallicity with increasing planet mass observed for the Solar System and exoplanets \cite[e.g.][]{kreidberg14b}.
+\added{The metallicity is super-solar at $>3\,\sigma$ confidence}.
 However, planet population synthesis models predict some scatter in atmospheric metallicity.
@@
 Further work is needed to develop a fully self-consistent 2-D retrieval method for phase curve observations.
+
+\subsection{Climate}
+We fit three different models to characterize the planet's climate: a two-temperature map, the physically-motivated kinematic model of \cite{zhang17}, and a spherical harmonic map.
+We also fit the thermal phase variation with a sinusoid, which can be inverted to map the climate \citep{cowan08, cowan17}.
+All of the models provide reasonable fits to the data, with $\chi^2_\nu$ near unity, but they yield significantly different temperature maps.
+Table\,\ref{table:models} lists the best fit minimum and maximum temperatures, as well as the mean day- and nightside temperatures.
+We also list the  information criterion (BIC) values for the fits \citep[a $\Delta$BIC value greater than 10 constitutes strong evidence against a given model;][]{kass95}.
+
+The spherical harmonics map generally fits the data the best.
+It has a lower BIC value than all the other models for the broadband WFC3 and \Spitzer\,$3.6\,\mu$m phase curves.
+For the $4.5\,\mu$m phase curve, the two temperature map provides the best fit, but it only lowers the BIC value by 2 relative to the spherical harmonics map, which is not a statistically significant improvement \citep{kass95}.
+The spherical harmonics model yields a mean dayside temperature near 2700 K, whereas the nightside is closer to 1800 K, in good agreement with the blackbody fits to the phase-resolved spectra (see \S\,\ref{sec:bbfits}).
+The other models produce more extreme day-night temperature gradients.
+Between the models, there are substantial differences in the minimum and maximum temperatures (sometimes over 1000 K), whereas the day and nightside means are in better agreement (generally matching to within 250 K).
+This behavior is not surprising: a wide range of temperature gradients can yield similar average temperatures when integrated over the disk of the planet.
 
@@
 The GCM predicts a cooler nightside than all models except the two-temperature model.
-We note that the GCM does not provide a perfect fit to the data, whereas multiple \texttt{spiderman} maps fit quite well, with large differences in temperature between them (see Table \,\ref{table:models}).
-Determining which models (if any) accurately describe the climate will require higher precision phase curves and/or eclipse mapping \citep[e.g.][]{dewit12}.
+\added{We note that none of the models are perfect: there is degeneracy in the \texttt{spiderman} maps, with large differences in climate producing reasonably good fits to the phase curves (see Table\,\ref{table:models}), whereas the GCM is too cold on the nightside.
+Robustly constraining the climate will require more sophisticated GCMs and higher precision phase curves/eclipse mapping \citep[e.g.][]{dewit12}.}
 
@@
 This observation gives rise to the question: what magnetic field strength on the planet can produce drag with this timescale?
-Previous efforts to characterize exoplanet magnetic fields have mainly focused on magnetic interaction between the planet and its host star \citep[e.g.][and references therein]{wright17}.
+Previous efforts to characterize exoplanet magnetic fields have mainly focused on magnetic interaction between the planet and its host star \citep[e.g.][and references therein]{wright15} and planetary radio emission \citep{griessmeier15}.
 A complementary approach is to study the effect of the magnetic field on the planet's atmospheric dynamics.}
@@
 This model has an equator-to-pole wind pattern that reproduces the small observed hotspot offsets and large phase curve amplitudes.
-This fast drag timescale is consistent with expectations for a magnetic field of $\sim1$ Gauss.}
+\added{We made a simple order-of-magnitude estimate for the magnetic field strength required to produce this fast drag timescale, and found it implies a magnetic field of $\sim1$ Gauss.}}
 	\item{We compared the spectra of WASP-103b at phases 0.5 (dayside), 0.25 (quadrature), and 0.1 (nightside) to brown dwarfs and directly imaged companions of similar temperature.
@@
 These results provide a first look at the global composition and thermal structure of WASP-103b.
-The planet is complex, with changes in temperature profile with longitude, possible gradients in composition from dayside to nightside, and circulation patterns influenced by the magnetic field.
+The planet is complex, with changes in temperature profile with longitude, possible gradients in composition from dayside to nightside, and circulation patterns \added{that may be} influenced by the magnetic field.
 These findings highlight the 3D nature of exoplanets and illustrate the importance of phase curve observations to develop a comprehensive understanding of their atmospheric chemistry and physics.
-
 %Cite Feng et al. 2016.

### 2018-04-06 ApJ_submit_v2/response.txt
incorporate ref report comments

@@
 #
-FIXME - Greg, can you fix this?
+Done.
 
@@
 #
-FIXME -- Mike, what motivated the upper bound?
+This is a physically motivated prior.
+The theoretical upper bound on f is 2.6666 (Cowan et al.
+2011) based on zero heat redistribution.
+We allowed a slightly higher bound to account for the fact that the stellar temperature is not perfectly known (i.e., if we underestimate Teff, we will overestimate f).

### 2018-04-06 ms.tex
incorporate ref report comments

@@
 \begin{abstract}
-%	We present thermal phase curve measurements for the hot Jupiter WASP-103b observed with \emph{Hubble}/WFC3 and \emph{Spitzer}/IRAC.
+	We present thermal phase curve measurements for the hot Jupiter WASP-103b observed with \emph{Hubble}/WFC3 and \emph{Spitzer}/IRAC.
 The dayside planet-to-star flux ratios are $0.151\pm0.015\%$, $0.446\pm0.038\%$, and $0.569\pm0.014\%$ in bandpasses centered at $1.4$, $3.6$, and $4.5\mu$m, respectively.
@@
 In contrast to cooler hot Jupiters, we do not detect significant water absorption, which we attribute to partial H$_2$O dissociation and additional opacity from H- and trace amounts of hydrides/oxides.
-We compare the phase curves to 3D general circulation models and find that atmospheric drag with a timescale of $10^4$ s is the best match to the data, which can be produced with a simple model of the magnetic field with strength $\sim1$ Gauss.
-We also compare the WASP-103b spectra to brown dwarfs and young directly imaged companions and find these more massive and self-luminous objects have significantly larger water features, indicating that surface gravity and irradiation environment play an important role in shaping the spectra of hot Jupiters.
-These results highlight the 3D structure of exoplanet atmospheres and illustrate the importance of phase curve observations for understanding their complex chemistry and physics.
-	We present thermal phase curve measurements for the hot Jupiter WASP-103b observed with \emph{Hubble}/WFC3 and \emph{Spitzer}/IRAC.
-The phase curves have large amplitudes and negligible hotspot offsets, indicative of poor heat redistribution to the nightside.
-We fit the phase variation with a range of climate maps and find that a spherical harmonics model generally provides the best fit.
-The phase-resolved spectra are consistent with blackbodies in the WFC3 bandpass, with brightness temperatures ranging from $1880\pm40$ K on the nightside to $2930 \pm 40$ K on the dayside.
-The dayside spectrum has a significantly higher brightness temperature in the \Spitzer\ bands, which we attribute to CO emission and a thermal inversion.
-The inversion is not present on the nightside.
-The transmission spectrum is featureless, but consistent with the small transit depth variation expected from cloud-free models.
-Using the dayside and nightside emission spectra, we retrieved the atmospheric composition with a 1D self-consistent modeling technique and found the atmosphere is moderately metal-enriched ($\mathrm{[M/H]} =  23^{+29}_{-13}\times$ solar) and the carbon-to-oxygen ratio is below 0.9 at $3\,\sigma$ confidence.
-In contrast to cooler hot Jupiters, we do not detect significant water absorption, which we attribute to partial H$_2$O dissociation and additional opacity from H- and trace amounts of hydrides/oxides.
-We compare the phase curves to 3D general circulation models and find that magnetic drag effects are needed match the data; a back-of-the-envelope calculation suggests the strength of the magnetic field is $\sim1$ Gauss.
-We also compare the WASP-103b spectra to brown dwarfs and young directly imaged companions and find these more massive and self-luminous objects have significantly larger water features, indicating that surface gravity and irradiation environment play an important role in shaping the spectra of hot Jupiters.
+We compare the phase curves to 3D general circulation models and find that magnetic drag effects are needed to match the data; \added{a back-of-the-envelope calculation suggests the strength of the magnetic field is $\sim1$ Gauss.}  We also compare the WASP-103b spectra to brown dwarfs and young directly imaged companions and find these more massive and self-luminous objects have significantly larger water features, indicating that surface gravity and irradiation environment play an important role in shaping the spectra of hot Jupiters.
 These results highlight the 3D structure of exoplanet atmospheres and illustrate the importance of phase curve observations for understanding their complex chemistry and physics.
@@
 
-Exoplanets are so distant that they are not spatially resolved from their host stars, but it is still possible to reveal inhomogeneities in their atmospheres.
+Exoplanets are so distant that they are \added{generally} not spatially resolved from their host stars, but it is still possible to reveal inhomogeneities in their atmospheres \added{by observing the total system flux}.
 One approach is to measure a phase curve, which consists of continuous monitoring of the planet-to-star flux ratio over a complete orbital revolution of the planet.
@@
 The GCM has solar metallicity, whereas the best fit 1D model has $[M/H] \sim 1$.
-Higher metallicity compositions have larger TiO/H$_2$O ratios, and since the pressure dependence of TiO dissociation is not as strong as for water dissociation, we expect stronger inversions for higher metallicity atmospheres.
+Higher metallicity compositions have larger TiO/H$_2$O ratios, and since the pressure dependence of TiO dissociation is not as strong as for water dissociation, we expect stronger inversions for higher metallicity atmospheres \citep{parmentier18}.
 On the nightside, we also find that the GCM is cooler than the 1D models.
-There are several physical processes not included in the GCM that could contribute to a hotter nightside, including shocks, longitude-dependent drag, and latent heat released from H2 recombination.
+\added{While in the 1D model the day-to-night redistribution is fitted to the data, it is not a tunable parameter in the 3D GCM.} There are several physical processes not included in the GCM that could contribute to a hotter nightside, including shocks, longitude-dependent drag, and latent heat released from H2 recombination \citep{bell18}.
 The best fit nightside TP profile is hotter than the condensation curves through most of the photosphere, suggesting that the observable atmosphere is relatively free of clouds.
@@
 \subsection{Constraints on the Planet's Magnetic Field}
-\added{We showed in this section that the small observed hotspot offset in the phase curves is best fit by a GCM that includes magnetic drag with a timescale $\tau_\mathrm{drag} = 10^4$\,s.
+\added{We show in this section that the small observed hotspot offset in the phase curves is best fit by a GCM that includes Rayleigh drag with a timescale $\tau_\mathrm{drag} = 10^4$\,s.
 This observation gives rise to the question: what magnetic field strength on the planet can produce drag with this timescale?
-Previous efforts to characterize exoplanet magnetic fields have mainly focused on magnetic interaction between the planet and its host star \citep[e.g.][and references therein]{wright17}.
+Previous efforts to characterize exoplanet magnetic fields have mainly focused on magnetic interaction between the planet and its host star \citep[e.g.][and references therein]{wright15} and planetary radio emission \citep{griessmeier15}.
 A complementary approach is to study the effect of the magnetic field on the planet's atmospheric dynamics.}

### 2018-04-18 ApJ_submit_v2/response.txt
shorten abstract

@@
 Since the caveats are now stated very prominently in 5.2.1 and in the summary bullet point in Section 8, we are confident that readers will not miss them.
-We did not add these points to the abstract because it is over the length limit, and we feel the impact of the paper will be greater if we focus scientific results in the abstract and leave the caveats in the main text.
+We did not add these points to the abstract because we had to cut it substantially to satisfy the length limit, and we feel the impact of the paper will be greater if we focus scientific results in the abstract and leave the caveats in the main text.
 
@@
 We put this discussion in a new subsection (6.1), added references to previous work, and mentioned the suggested caveats.
-We also clarified in the abstract that our estimate of the magnetic field is based on a back of the envelope calculation.
+We removed the specific mention of the magnetic field estimate from the abstract.
 

### 2018-04-18 ApJ_submit_v2/ms.tex
shorten abstract

@@
 \begin{abstract}
-%	We present thermal phase curve measurements for the hot Jupiter WASP-103b observed with \emph{Hubble}/WFC3 and \emph{Spitzer}/IRAC.
+	%We present thermal phase curve measurements for the hot Jupiter WASP-103b observed with \emph{Hubble}/WFC3 and \emph{Spitzer}/IRAC.
 The dayside planet-to-star flux ratios are $0.151\pm0.015\%$, $0.446\pm0.038\%$, and $0.569\pm0.014\%$ in bandpasses centered at $1.4$, $3.6$, and $4.5\mu$m, respectively.
@@
 In contrast to cooler hot Jupiters, we do not detect significant water absorption, which we attribute to partial H$_2$O dissociation and additional opacity from H- and trace amounts of hydrides/oxides.
-We compare the phase curves to 3D general circulation models and find that atmospheric drag with a timescale of $10^4$ s is the best match to the data, which can be produced with a simple model of the magnetic field with strength $\sim1$ Gauss.
-We also compare the WASP-103b spectra to brown dwarfs and young directly imaged companions and find these more massive and self-luminous objects have significantly larger water features, indicating that surface gravity and irradiation environment play an important role in shaping the spectra of hot Jupiters.
+We compare the phase curves to 3D general circulation models and find that magnetic drag effects are needed to match the data; \added{a back-of-the-envelope calculation suggests the strength of the magnetic field is $\sim1$ Gauss.}  We also compare the WASP-103b spectra to brown dwarfs and young directly imaged companions and find these more massive and self-luminous objects have significantly larger water features, indicating that surface gravity and irradiation environment play an important role in shaping the spectra of hot Jupiters.
 These results highlight the 3D structure of exoplanet atmospheres and illustrate the importance of phase curve observations for understanding their complex chemistry and physics.
 We present thermal phase curve measurements for the hot Jupiter WASP-103b observed with \emph{Hubble}/WFC3 and \emph{Spitzer}/IRAC.
-The dayside planet-to-star flux ratios are $0.151\pm0.015\%$, $0.446\pm0.038\%$, and $0.569\pm0.014\%$ in bandpasses centered at $1.4$, $3.6$, and $4.5\mu$m, respectively.
 The phase curves have large amplitudes and negligible hotspot offsets, indicative of poor heat redistribution to the nightside.
@@
 The phase-resolved spectra are consistent with blackbodies in the WFC3 bandpass, with brightness temperatures ranging from $1880\pm40$ K on the nightside to $2930 \pm 40$ K on the dayside.
-The dayside spectrum has a significantly higher brightness temperature in the \Spitzer\ bands, which we attribute to CO emission and a thermal inversion.
+The dayside spectrum has a significantly higher brightness temperature in the \Spitzer\ bands, likely due to CO emission and a thermal inversion.
 The inversion is not present on the nightside.
-The transmission spectrum is featureless, but consistent with the small transit depth variation expected from cloud-free models.
-Using the dayside and nightside emission spectra, we retrieved the atmospheric composition with a 1D self-consistent modeling technique and found the atmosphere is moderately metal-enriched ($\mathrm{[M/H]} = 23^{+29}_{-13}\times$ solar) and the carbon-to-oxygen ratio is below 0.9 at $3\,\sigma$ confidence.
-In contrast to cooler hot Jupiters, we do not detect significant water absorption, which we attribute to partial H$_2$O dissociation and additional opacity from H- and trace amounts of hydrides/oxides.
-We compare the phase curves to 3D general circulation models and find that magnetic drag effects are needed match the data; \added{a back-of-the-envelope calculation suggests the strength of the magnetic field is $\sim1$ Gauss.}  We also compare the WASP-103b spectra to brown dwarfs and young directly imaged companions and find these more massive and self-luminous objects have significantly larger water features, indicating that surface gravity and irradiation environment play an important role in shaping the spectra of hot Jupiters.
+We retrieved the atmospheric composition and found the composition is moderately metal-enriched ($\mathrm{[M/H]} = 23^{+29}_{-13}\times$ solar) and the carbon-to-oxygen ratio is below 0.9 at $3\,\sigma$ confidence.
+In contrast to cooler hot Jupiters, we do not detect spectral features from water, which we attribute to partial H$_2$O dissociation.
+We compare the phase curves to 3D general circulation models and find magnetic drag effects are needed to match the data.
+We also compare the WASP-103b spectra to brown dwarfs and young directly imaged companions and find these objects have significantly larger water features, indicating that surface gravity and irradiation environment play an important role in shaping the spectra of hot Jupiters.
 These results highlight the 3D structure of exoplanet atmospheres and illustrate the importance of phase curve observations for understanding their complex chemistry and physics.
@@
 variation is modeled. The transit light curve fits are shown in
-Figure\,\ref{fig:transitlc}.
+Figure\,\ref{fig:transit_light_curves}.
 
@@
 \caption{Best fit transit light curves for WASP-103b (lines), compared to binned data (black points). From top-to-bottom, we show the band-integrated WFC3 light curve, \Spitzer\ 3.6, and $4.5\,\mu$m.}
-\label{fig:transitlc}
+\label{fig:transit_light_curves}
 \end{figure}
 
-We show the measured transmission spectrum in Figure\,\ref{fig:tspec}.
+We show the measured transmission spectrum in Figure\,\ref{fig:tspectrum}.
 The spectrum is biased by flux contamination from the planet's nightside; to correct for nightside emission, we estimate the average nightside planet-to-star flux ratio and subtract it from the transit depth.
@@
 \includegraphics[width = 0.5\textwidth]{fig10.pdf}
-\label{fig:tspec}
 \caption{The transmission spectrum of WASP-103b, corrected for planet nightside emission at 1700 K (blue points) and uncorrected (red points).
@@
 Atmospheric scale height $H$ is shown on the right y-axis, where $H = 5.5\times10^6$ m (assuming a mean molecular weight of 2.3 atomic mass units, surface gravity $g = 15.9$ m/s$^2$, and a temperature $T = 2410$ K).}
+\label{fig:tspectrum}
 \end{figure}
@@
 \subsection{Constraints on the Planet's Magnetic Field}
-\added{We showed in this section that the small observed hotspot offset in the phase curves is best fit by a GCM that includes magnetic drag with a timescale $\tau_\mathrm{drag} = 10^4$\,s.
+\added{We show in this section that the small observed hotspot offset in the phase curves is best fit by a GCM that includes Rayleigh drag with a timescale $\tau_\mathrm{drag} = 10^4$\,s.
 This observation gives rise to the question: what magnetic field strength on the planet can produce drag with this timescale?

### 2018-04-18 arxiv_v1/ms.tex
shorten abstract

--- 2018-04-18 ApJ_submit_v2/ms.tex
@@
 In contrast to cooler hot Jupiters, we do not detect significant water absorption, which we attribute to partial H$_2$O dissociation and additional opacity from H- and trace amounts of hydrides/oxides.
-We compare the phase curves to 3D general circulation models and find that magnetic drag effects are needed to match the data; \added{a back-of-the-envelope calculation suggests the strength of the magnetic field is $\sim1$ Gauss.}  We also compare the WASP-103b spectra to brown dwarfs and young directly imaged companions and find these more massive and self-luminous objects have significantly larger water features, indicating that surface gravity and irradiation environment play an important role in shaping the spectra of hot Jupiters.
+We compare the phase curves to 3D general circulation models and find that magnetic drag effects are needed to match the data; a back-of-the-envelope calculation suggests the strength of the magnetic field is $\sim1$ Gauss.
+We also compare the WASP-103b spectra to brown dwarfs and young directly imaged companions and find these more massive and self-luminous objects have significantly larger water features, indicating that surface gravity and irradiation environment play an important role in shaping the spectra of hot Jupiters.
 These results highlight the 3D structure of exoplanet atmospheres and illustrate the importance of phase curve observations for understanding their complex chemistry and physics.
@@
 
-Exoplanets are so distant that they are \added{generally} not spatially resolved from their host stars, but it is still possible to reveal inhomogeneities in their atmospheres \added{by observing the total system flux}.
+Exoplanets are so distant that they are generally not spatially resolved from their host stars, but it is still possible to reveal inhomogeneities in their atmospheres by observing the total system flux.
 One approach is to measure a phase curve, which consists of continuous monitoring of the planet-to-star flux ratio over a complete orbital revolution of the planet.
@@
 ideal target for phase curve observations, with an orbital period of just 22
-hours and an equilbrium temperature of 2500 K.  \added{WASP-103b is slightly
+hours and an equilbrium temperature of 2500 K.  WASP-103b is slightly
 larger than Jupiter, with a mass and radius of $1.49\pm0.09\,M_\mathrm{Jup}$ and
 $1.53^{+0.05}_{-0.07}\,R_\mathrm{Jup}$, respectively.
-The host star is a main-sequence F8 dwarf with an effective temperature of $6110 \pm 160\,$ K \citep{gillon14}.} Previous observations of WASP-103b's atmosphere revealed a blackbody-like dayside emission spectrum, with possible evidence for a $K_\mathrm{S}$-band emission feature \citep{cartier17, delrez18}.
+The host star is a main-sequence F8 dwarf with an effective temperature of $6110 \pm 160\,$ K \citep{gillon14}.
+Previous observations of WASP-103b's atmosphere revealed a blackbody-like dayside emission spectrum, with possible evidence for a $K_\mathrm{S}$-band emission feature \citep{cartier17, delrez18}.
 The optical transmission spectrum shows evidence for sodium and potassium absorption features that are consistent with expectations for a cloud-free atmosphere \citep{lendl17}.%, though other observations have shown a large optical scattering slope that is not fit well by theoretical models \citep{southworth16}.
@@
 The data were reduced with the POET pipeline \citep{stevenson12, cubillos13}.
-\added{The pipeline starts by identifying and flagging bad pixels using a double-iteration 4-sigma outlier rejection routine along the time axis.
+The pipeline starts by identifying and flagging bad pixels using a double-iteration 4-sigma outlier rejection routine along the time axis.
 This is followed by performing 2D Gaussian centroiding on each frame, which is shown to provide the most precise centers for Spitzer data \citep{Lust2014}.
@@
 A similarly strategy has been applied to successfully analyze dozens of Spitzer data sets \citep[e.g.
-][]{Stevenson2010, Stevenson2012a, Stevenson2012b, Stevenson2014a, Stevenson2014b, Stevenson2016a, Stevenson2017a, Campo2011, Nymeyer2011, cubillos13, Blecic2013, Blecic2014, HDL2014}.}
+][]{Stevenson2010, Stevenson2012a, Stevenson2012b, Stevenson2014a, Stevenson2014b, Stevenson2016a, Stevenson2017a, Campo2011, Nymeyer2011, cubillos13, Blecic2013, Blecic2014, HDL2014}.
 
@@
 The individual consecutive frames were co-added and reduced to differential magnitudes (i.e., WASP-103 minus the mean brightness of the six best comparison stars).
-The nightly observations were corrected for bias, flat-fielding, \deleted{pier-side offset,} and differential atmospheric extinction.
-\added{We determined seasonal-mean extinction coefficients from a linear, least-squares fits to seasonal plots of differential magnitudes versus mean air mass and computed the slope in magnitudes per air mass.}
+The nightly observations were corrected for bias, flat-fielding, and differential atmospheric extinction.
+We determined seasonal-mean extinction coefficients from a linear, least-squares fits to seasonal plots of differential magnitudes versus mean air mass and computed the slope in magnitudes per air mass.
 
 The photometric analyses are summarized for each observing season in Table\,\ref{tab:photometry}.
-The standard deviations of a single observation with respect to the corresponding seasonal means are given in column~4; \added{the mean of the three standard deviations is 0.0058~mag, suggesting there is little night-to-night variation in WASP-103.
+The standard deviations of a single observation with respect to the corresponding seasonal means are given in column~4; the mean of the three standard deviations is 0.0058~mag, suggesting there is little night-to-night variation in WASP-103.
 The three seasonal mean brightness values given in column 5 scatter about their grand mean with a standard deviation of 0.0036 mag, but we note that the most discrepant mean is from the third season, for which we have only partial coverage.
-Therefore, our results do not completely rule out low-level, year-to-year variability of $<0.001$~mag.}
+Therefore, our results do not completely rule out low-level, year-to-year variability of $<0.001$~mag.
 
@@
 We found that the transit parameters are consistent with the \cite{southworth15} results, so we proceeded with the remainder of the analysis holding those parameters fixed.
-The free parameters for the transit model were a \added{wavelength-dependent} transit depth $r_p(\lambda)$ and linear limb darkening parameter $u(\lambda)$.
+The free parameters for the transit model were a wavelength-dependent transit depth $r_p(\lambda)$ and linear limb darkening parameter $u(\lambda)$.
 More complex limb darkening laws with additional free parameters were not merited according to the Bayesian Information Criterion (BIC).
-\added{We initialized our MCMC chains on the least squares best fit parameters.}
+We initialized our MCMC chains on the least squares best fit parameters.
 
@@
 The companion star contribution ranges from $10\%$ at $1.1\,\mu$m to $16\%$ at $4.5\,\mu$m.
-The uncertainty on the companion star flux contribution \added{to the total system flux} is less than 1\%, which introduces negligible error in the estimated planet-to-star-flux compared to the photon noise.
+The uncertainty on the companion star flux contribution to the total system flux is less than 1\%, which introduces negligible error in the estimated planet-to-star-flux compared to the photon noise.
 We calculated $A(t)$ using the analytic formula from \cite{leconte11b}, equation B.9, which computes the projected area of a triaxial ellipsoid.
@@
 \subsubsection{\Spitzer\ Systematics}
-\added{Warm Spitzer's primary systematic is intrapixel sensitivity variation, where the photometry depends on the precise location of the stellar center within its pixel.
+Warm Spitzer's primary systematic is intrapixel sensitivity variation, where the photometry depends on the precise location of the stellar center within its pixel.
 We fit this systematic using the Bilinearly-Interpolated Subpixel Sensitivity (BLISS) mapping technique \citep{stevenson12}.
 BLISS provides a flexible, non-analytic means to effectively weight the target flux by the spatial sensitivity variations within a pixel, while simultaneously fitting for other systematics and the physical parameters of the system.
-As demonstrated by \citet{Ingalls2016}, the POET pipeline with BLISS mapping can accurately model simulated \Spitzer\ light curves with known physical parameters and produce reliable results.}
+As demonstrated by \citet{Ingalls2016}, the POET pipeline with BLISS mapping can accurately model simulated \Spitzer\ light curves with known physical parameters and produce reliable results.
 
@@
 To avoid overfitting, we chose the grid scale such that bilinear interpolation performed better than nearest neighbor interpolation.
-For the $3.6\,\mu$m data, the grid scale was 0.008 pixel \added{(0.0098 arcsec)} in both $x$ and $y$.
-For $4.5\,\mu$m, the scale was 0.022 pixel \added{(0.027 arcsec)}.
+For the $3.6\,\mu$m data, the grid scale was 0.008 pixel (0.0098 arcsec) in both $x$ and $y$.
+For $4.5\,\mu$m, the scale was 0.022 pixel (0.027 arcsec).
 In addition to the intrapixel sensitivity variation, we fit the data for a linear trend in time.
@@
 To determine the best fits, we performed a least-squares $\chi^2$ minimization for each wavelength and model.
-For a subset of these cases \added{where we wish to calculate 68\% confidence intervals}, we also performed a Markov chain Monte Carlo (MCMC) analysis to estimate parameter uncertainties.
-\added{These include the transit fits and the sine curve fit to the broadband phase curves.} We used \texttt{emcee} \citep{foremanmackey13} to fit the \HST/WFC3 light curves and differential evolution Monte Carlo for the \Spitzer\ fits \citep{braak06}.
+For a subset of these cases where we wish to calculate 68\% confidence intervals, we also performed a Markov chain Monte Carlo (MCMC) analysis to estimate parameter uncertainties.
+These include the transit fits and the sine curve fit to the broadband phase curves.
+We used \texttt{emcee} \citep{foremanmackey13} to fit the \HST/WFC3 light curves and differential evolution Monte Carlo for the \Spitzer\ fits \citep{braak06}.
 We ran the MCMC until convergence according to the Gelman-Rubin statistic.
@@
 We used a Haar wavelet and let the power spectral density of the red noise vary, following \cite{diamond-lowe14}.
-In our final fit, the noise power spectrum $1/f^\gamma$ had $\gamma = 1.1 \pm 0.1$ \added{(implying an equal amount of white noise and correlated noise)}.
+In our final fit, the noise power spectrum $1/f^\gamma$ had $\gamma = 1.1 \pm 0.1$ (implying an equal amount of white noise and correlated noise).
 \subsection{Goodness of Fit}
@@
 variation in the position of the spatial scan on the detector, and loss of flux
-outside the extraction window. \added{In addition, the amplitude of the phase
+outside the extraction window. In addition, the amplitude of the phase
 variation increases by 50\% over the WFC3 wavelength range, which leads to a
@@
 $\sim100$ ppm, which is comparable to the additional scatter we observed in the
-white light curve.}
+white light curve.
 
@@
 The right-hand column shows the binned residuals for the best-fit light curve.
-\added{The gray error bars in the upper right of the left panels correspond to 500 ppm, to illustrate the changing y-axis scale.}}
+The gray error bars in the upper right of the left panels correspond to 500 ppm, to illustrate the changing y-axis scale.}
 \label{fig:phasecurves}
@@
 For the other orbital phases, we binned the light curve (with systematics
-removed) in eight intervals of about 0.1 in orbital phase \added{(2.2 hours)}, with endpoints at
+removed) in eight intervals of about 0.1 in orbital phase (2.2 hours), with endpoints at
 phases $0.06, 0.15, 0.25, 0.35, 0.44$ and $0.56, 0.65, 0.75, 0.85, 0.94$. These
@@
 The blackbody model is fit to the \HST/WFC3 data only.
-\added{We also show a 100 ppm error bar in the lower right of each panel to emphasize the changing limits on the y-axes.}}
+We also show a 100 ppm error bar in the lower right of each panel to emphasize the changing limits on the y-axes.}
 \label{fig:spectra}
@@
 If the phase variation is absorbed into the systematic model, the measured eclipse depths would be biased low.
-\added{From a glance at Figure\,\ref{fig:model_comparison}, the amplitude of this effect is} $\sim100$ ppm, \added{which is comparable to the offset between the two analyses}.
+From a glance at Figure\,\ref{fig:model_comparison}, the amplitude of this effect is $\sim100$ ppm, which is comparable to the offset between the two analyses.
 Our estimated uncertainties are a factor of four smaller than those reported in \cite{cartier17}, which is consistent with photon-limited expectations (our data set includes two additional eclipses, a factor of five longer out-of-eclipse baseline, and has 60\% larger wavelength bins).
@@
 We then performed a more sophisticated grid-based retrieval to estimate the atmospheric metallicity, carbon-to-oxygen ratio, and thermal structure.
-\added{We also evaluated the climate based on the best fit \texttt{spiderman} temperature maps.}
+We also evaluated the climate based on the best fit \texttt{spiderman} temperature maps.
 
@@
 
-\added{We note that the uncertainties on the brightness temperatures in
+We note that the uncertainties on the brightness temperatures in
 different bandpasses are correlated with each other because they include the
@@
 increases, so do the brightness temperatures. To evaluate the significance of
-features in the emission spectra, we hold the stellar spectrum fixed in the retrieval analysis.}
+features in the emission spectra, we hold the stellar spectrum fixed in the retrieval analysis.
 %This model performs well for some orbital phases, with $\chi^2_\nu$ ranging from 0.9 to 1.1 for phases $\phi = 0.1, 0.7$ and $0.8$.
@@
 \label{sec:retrieval}
-To infer abundances from the dayside spectrum \added{(phase $0.46 - 0.54$)}, we use a self-consistent grid-based method (ScCHIMERA) similar to that employed in \cite{arcangeli18, mansfield18}.
+To infer abundances from the dayside spectrum (phase $0.46 - 0.54$), we use a self-consistent grid-based method (ScCHIMERA) similar to that employed in \cite{arcangeli18, mansfield18}.
 We generated a grid from one-dimensional forward models of the atmosphere over a broad range of metallicities (M/H), carbon-to-oxygen ratios (C/O), and stellar irradiation ($f$).
@@
 We infer a range in metallicity of $23^{+29}_{-13}\times$ solar, somewhat higher than expected based on Jupiter's metal enrichment \citep[$3-5\times$ solar;][]{wong04} and the trend toward decreasing metallicity with increasing planet mass observed for the Solar System and exoplanets \cite[e.g.][]{kreidberg14b}.
-\added{The metallicity is super-solar at $>3\,\sigma$ confidence}.
+The metallicity is super-solar at $>3\,\sigma$ confidence.
 However, planet population synthesis models predict some scatter in atmospheric metallicity.
@@
 
-\added{There are several caveats in our analysis which are important to note:}
+There are several caveats in our analysis which are important to note:
 \begin{my_itemize}
@@
 To fit this data point, the model favors super-solar metallicities and C/O, which drive up the CO abundance (the dominant absorber at $4.5\,\mu$m).}
-    \item{\added{The \Spitzer\ $4.5\,\mu$m data is from broadband photometry, so the inferred CO feature is not spectrally resolved.
-It is possible that unknown absorbers or disequilibrium chemistry affect the $4.5\,\mu$m planet-to-star flux, but we cannot uniquely identify these features in our spectrum.}}
+    \item{The \Spitzer\ $4.5\,\mu$m data is from broadband photometry, so the inferred CO feature is not spectrally resolved.
+It is possible that unknown absorbers or disequilibrium chemistry affect the $4.5\,\mu$m planet-to-star flux, but we cannot uniquely identify these features in our spectrum.}
 \end{my_itemize}
@@
 Our nominal GCM was a cloud-free, solar composition atmosphere with TiO/VO opacity and no added drag.
-\added{Each GCM run is computationally intensive, so we ran a small number of additional models to see which parameters had the largest effect on the planet spectrum.
-We changed model parameters one at a time,} considering cases with enhanced metallicity ([M/H] = 0.5), no TiO/VO, and added atmospheric drag with timescales $\tau_\mathrm{drag} = 10^3$ and $10^4$ s, which we label $\tau_\mathrm{drag3}$ and $\tau_\mathrm{drag4}$, respectively.
+Each GCM run is computationally intensive, so we ran a small number of additional models to see which parameters had the largest effect on the planet spectrum.
+We changed model parameters one at a time, considering cases with enhanced metallicity ([M/H] = 0.5), no TiO/VO, and added atmospheric drag with timescales $\tau_\mathrm{drag} = 10^3$ and $10^4$ s, which we label $\tau_\mathrm{drag3}$ and $\tau_\mathrm{drag4}$, respectively.
 To assess how well the GCM predictions reproduce the data, we calculated the amplitude and hot spot offset for all the models (listed in Table\,\ref{table:amps_offsets}).
@@
 On the nightside, we also find that the GCM is cooler than the 1D models.
-\added{While in the 1D model the day-to-night redistribution is fitted to the data, it is not a tunable parameter in the 3D GCM.} There are several physical processes not included in the GCM that could contribute to a hotter nightside, including shocks, longitude-dependent drag, and latent heat released from H2 recombination \citep{bell18}.
+While in the 1D model the day-to-night redistribution is fitted to the data, it is not a tunable parameter in the 3D GCM.
+There are several physical processes not included in the GCM that could contribute to a hotter nightside, including shocks, longitude-dependent drag, and latent heat released from H2 recombination \citep{bell18}.
 The best fit nightside TP profile is hotter than the condensation curves through most of the photosphere, suggesting that the observable atmosphere is relatively free of clouds.
@@
 The GCM predicts a cooler nightside than all models except the two-temperature model.
-\added{We note that none of the models are perfect: there is degeneracy in the \texttt{spiderman} maps, with large differences in climate producing reasonably good fits to the phase curves (see Table\,\ref{table:models}), whereas the GCM is too cold on the nightside.
-Robustly constraining the climate will require more sophisticated GCMs and higher precision phase curves/eclipse mapping \citep[e.g.][]{dewit12}.}
+We note that none of the models are perfect: there is degeneracy in the \texttt{spiderman} maps, with large differences in climate producing reasonably good fits to the phase curves (see Table\,\ref{table:models}), whereas the GCM is too cold on the nightside.
+Robustly constraining the climate will require more sophisticated GCMs and higher precision phase curves/eclipse mapping \citep[e.g.][]{dewit12}.
 
@@
 \subsection{Constraints on the Planet's Magnetic Field}
-\added{We show in this section that the small observed hotspot offset in the phase curves is best fit by a GCM that includes Rayleigh drag with a timescale $\tau_\mathrm{drag} = 10^4$\,s.
+We show in this section that the small observed hotspot offset in the phase curves is best fit by a GCM that includes Rayleigh drag with a timescale $\tau_\mathrm{drag} = 10^4$\,s.
 This observation gives rise to the question: what magnetic field strength on the planet can produce drag with this timescale?
 Previous efforts to characterize exoplanet magnetic fields have mainly focused on magnetic interaction between the planet and its host star \citep[e.g.][and references therein]{wright15} and planetary radio emission \citep{griessmeier15}.
-A complementary approach is to study the effect of the magnetic field on the planet's atmospheric dynamics.}
+A complementary approach is to study the effect of the magnetic field on the planet's atmospheric dynamics.
 
@@
 To reach a drag timescale of $10^4$\,s, a magnetic field stronger than $\sim1$ Gauss is required, comparable to Jupiter's magnetic field strength of 5-10 Gauss \citep{bagenal04}.
-\added{To confirm this intriguing result, more detailed study is warranted, including a full magnetic hydrodynamic simulation of the atmospheric dynamics \citep[e.g.][]{rogers17} and accounting for the possibility of complex magnetic field structure due to interactions between the magnetic fields of the planet and the star.}
+To confirm this intriguing result, more detailed study is warranted, including a full magnetic hydrodynamic simulation of the atmospheric dynamics \citep[e.g.][]{rogers17} and accounting for the possibility of complex magnetic field structure due to interactions between the magnetic fields of the planet and the star.
 
@@
 \item{The \Spitzer\ data are \emph{not} consistent with the best fit blackbody to the WFC3 data: they have a higher brightness temperature at phases $\phi = 0.2 - 0.5$, which transitions to a lower brightness temperature on the nightside ($\phi = -0.2 - 0.1$).
-\added{An atmospheric retrieval analysis suggests that} these characteristics are likely due to CO features in the infrared and a temperature inversion on the dayside but not the nightside.}
+An atmospheric retrieval analysis suggests that these characteristics are likely due to CO features in the infrared and a temperature inversion on the dayside but not the nightside.}
 \item{The measured transmission spectrum is featureless (after correcting for nightside emission from the planet).
@@
 This model has an equator-to-pole wind pattern that reproduces the small observed hotspot offsets and large phase curve amplitudes.
-\added{We made a simple order-of-magnitude estimate for the magnetic field strength required to produce this fast drag timescale, and found it implies a magnetic field of $\sim1$ Gauss.}}
+We made a simple order-of-magnitude estimate for the magnetic field strength required to produce this fast drag timescale, and found it implies a magnetic field of $\sim1$ Gauss.}
 	\item{We compared the spectra of WASP-103b at phases 0.5 (dayside), 0.25 (quadrature), and 0.1 (nightside) to brown dwarfs and directly imaged companions of similar temperature.
@@
 These results provide a first look at the global composition and thermal structure of WASP-103b.
-The planet is complex, with changes in temperature profile with longitude, possible gradients in composition from dayside to nightside, and circulation patterns \added{that may be} influenced by the magnetic field.
+The planet is complex, with changes in temperature profile with longitude, possible gradients in composition from dayside to nightside, and circulation patterns that may be influenced by the magnetic field.
 These findings highlight the 3D nature of exoplanets and illustrate the importance of phase curve observations to develop a comprehensive understanding of their atmospheric chemistry and physics.

### 2018-04-20 arxiv_v1/ms.tex
arxiv version

@@
 \begin{figure}
-\includegraphics[width = 0.5\textwidth]{fig1.eps}
+\includegraphics[width = 0.5\textwidth]{fig1.pdf}
 %\includegraphics[width = 0.5\textwidth]{fig1-eps-converted-to.pdf}
@@
 
-\bibliographystyle{aasjournal}
-\bibliography{ms.bib}
+ \newcommand{\noop}[1]{}
+\begin{thebibliography}{}
+\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
+\providecommand{\url}[1]{\href{#1}{#1}}
+
+\bibitem[{Adcroft {et~al.}(2004)Adcroft, Campin, Hill, \&
+  Marshall}]{Adcroft2004}
+Adcroft, A., Campin, J.-M., Hill, C., \& Marshall, J. 2004, Monthly Weather
+  Review, 132, 2845.
+\newblock \url{https://doi.org/10.1175/MWR2823.1}
+
+\bibitem[{{Ag{\'u}ndez} {et~al.}(2014){Ag{\'u}ndez}, {Parmentier}, {Venot},
+  {Hersant}, \& {Selsis}}]{agundez14}
+{Ag{\'u}ndez}, M., {Parmentier}, V., {Venot}, O., {Hersant}, F., \& {Selsis},
+  F. 2014, \aap, 564, A73
+
+\bibitem[{{Allard} {et~al.}(2012){Allard}, {Homeier}, \& {Freytag}}]{allard12}
+{Allard}, F., {Homeier}, D., \& {Freytag}, B. 2012, Philosophical Transactions
+  of the Royal Society of London Series A, 370, 2765
+
+\bibitem[{{Aller} {et~al.}(2013){Aller}, {Kraus}, {Liu}, {Burgett}, {Chambers},
+  {Hodapp}, {Kaiser}, {Magnier}, \& {Price}}]{aller13}
+{Aller}, K.~M., {Kraus}, A.~L., {Liu}, M.~C., {et~al.} 2013, \apj, 773, 63
+
+\bibitem[{{Arcangeli} {et~al.}(2018){Arcangeli}, {Desert}, {Line}, {Bean},
+  {Parmentier}, {Stevenson}, {Kreidberg}, {Fortney}, {Mansfield}, \&
+  {Showman}}]{arcangeli18}
+{Arcangeli}, J., {Desert}, J.-M., {Line}, M.~R., {et~al.} 2018, ArXiv e-prints,
+  arXiv:1801.02489
+
+\bibitem[{{Armstrong} {et~al.}(2016){Armstrong}, {de Mooij}, {Barstow},
+  {Osborn}, {Blake}, \& {Saniee}}]{armstrong16}
+{Armstrong}, D.~J., {de Mooij}, E., {Barstow}, J., {et~al.} 2016, Nature
+  Astronomy, 1, 0004
+
+\bibitem[{{Bagenal} {et~al.}(2004){Bagenal}, {Dowling}, \&
+  {McKinnon}}]{bagenal04}
+{Bagenal}, F., {Dowling}, T.~E., \& {McKinnon}, W.~B. 2004, {Jupiter : the
+  planet, satellites and magnetosphere}
+
+\bibitem[{{Bardalez Gagliuffi} {et~al.}(2014){Bardalez Gagliuffi}, {Burgasser},
+  {Gelino}, {Looper}, {Nicholls}, {Schmidt}, {Cruz}, {West}, {Gizis}, \&
+  {Metchev}}]{bardalez14}
+{Bardalez Gagliuffi}, D.~C., {Burgasser}, A.~J., {Gelino}, C.~R., {et~al.}
+  2014, \apj, 794, 143
+
+\bibitem[{{Batygin} {et~al.}(2013){Batygin}, {Stanley}, \&
+  {Stevenson}}]{batygin13}
+{Batygin}, K., {Stanley}, S., \& {Stevenson}, D.~J. 2013, \apj, 776, 53
+
+\bibitem[{{Beatty} {et~al.}(2017{\natexlab{a}}){Beatty}, {Madhusudhan},
+  {Pogge}, {Chung}, {Bierlya}, {Gaudi}, \& {Latham}}]{beatty17a}
+{Beatty}, T.~G., {Madhusudhan}, N., {Pogge}, R., {et~al.} 2017{\natexlab{a}},
+  \aj, 154, 242
+
+\bibitem[{{Beatty} {et~al.}(2017{\natexlab{b}}){Beatty}, {Madhusudhan},
+  {Tsiaras}, {Zhao}, {Gilliland}, {Knutson}, {Shporer}, \&
+  {Wright}}]{beatty17b}
+{Beatty}, T.~G., {Madhusudhan}, N., {Tsiaras}, A., {et~al.} 2017{\natexlab{b}},
+  \aj, 154, 158
+
+\bibitem[{{Bell} \& {Cowan}(2018)}]{bell18}
+{Bell}, T.~J., \& {Cowan}, N.~B. 2018, ArXiv e-prints, arXiv:1802.07725
+
+\bibitem[{{Blecic} {et~al.}(2013){Blecic}, {Harrington}, {Madhusudhan},
+  {Stevenson}, {Hardy}, {Blecic}, {Anderson}, {Hardin}, \&
+  {Campo}}]{Blecic2013}
+{Blecic}, J., {Harrington}, J., {Madhusudhan}, N., {et~al.} 2013, \apj, 779, 5
+
+\bibitem[{{Blecic} {et~al.}(2014){Blecic}, {Harrington}, {Madhusudhan},
+  {Stevenson}, {Hardy}, {Cubillos}, {Hardin}, {Bowman}, {Nymeyer}, {Anderson},
+  {Hellier}, {Smith}, \& {Collier Cameron}}]{Blecic2014}
+---. 2014, \apj, 781, 116
+
+\bibitem[{{Bonnefoy} {et~al.}(2014){Bonnefoy}, {Chauvin}, {Lagrange}, {Rojo},
+  {Allard}, {Pinte}, {Dumas}, \& {Homeier}}]{bonnefoy14}
+{Bonnefoy}, M., {Chauvin}, G., {Lagrange}, A.-M., {et~al.} 2014, \aap, 562,
+  A127
+
+\bibitem[{{Bonnefoy} {et~al.}(2009){Bonnefoy}, {Chauvin}, {Dumas}, {Lagrange},
+  {Beust}, {Desort}, {Teixeira}, {Ducourant}, {Beuzit}, \& {Song}}]{bonnefoy09}
+{Bonnefoy}, M., {Chauvin}, G., {Dumas}, C., {et~al.} 2009, \aap, 506, 799
+
+\bibitem[{{Borucki} {et~al.}(2009){Borucki}, {Koch}, {Jenkins}, {Sasselov},
+  {Gilliland}, {Batalha}, {Latham}, {Caldwell}, {Basri}, {Brown},
+  {Christensen-Dalsgaard}, {Cochran}, {DeVore}, {Dunham}, {Dupree}, {Gautier},
+  {Geary}, {Gould}, {Howell}, {Kjeldsen}, {Lissauer}, {Marcy}, {Meibom},
+  {Morrison}, \& {Tarter}}]{borucki09}
+{Borucki}, W.~J., {Koch}, D., {Jenkins}, J., {et~al.} 2009, Science, 325, 709
+
+\bibitem[{Braak(2006)}]{braak06}
+Braak, C. J. F.~T. 2006, Statistics and Computing, 16, 239.
+\newblock \url{http://dx.doi.org/10.1007/s11222-006-8769-1}
+
+\bibitem[{{Campo} {et~al.}(2011){Campo}, {Harrington}, {Hardy}, {Stevenson},
+  {et~al.}}]{Campo2011}
+{Campo}, C.~J., {Harrington}, J., {Hardy}, R.~A., {Stevenson}, K.~B., {et~al.}
+  2011, \apj, 727, 125
+
+\bibitem[{{Carter} \& {Winn}(2009)}]{carter09}
+{Carter}, J.~A., \& {Winn}, J.~N. 2009, \apj, 704, 51
+
+\bibitem[{{Cartier} {et~al.}(2017){Cartier}, {Beatty}, {Zhao}, {Line}, {Ngo},
+  {Mawet}, {Stassun}, {Wright}, {Kreidberg}, {Fortney}, \&
+  {Knutson}}]{cartier17}
+{Cartier}, K.~M.~S., {Beatty}, T.~G., {Zhao}, M., {et~al.} 2017, \aj, 153, 34
+
+\bibitem[{{Cowan} \& {Agol}(2008)}]{cowan08}
+{Cowan}, N.~B., \& {Agol}, E. 2008, \apjl, 678, L129
+
+\bibitem[{{Cowan} \& {Fujii}(2017)}]{cowan17}
+{Cowan}, N.~B., \& {Fujii}, Y. 2017, ArXiv e-prints, arXiv:1704.07832
+
+\bibitem[{{Crossfield} {et~al.}(2012){Crossfield}, {Barman}, {Hansen},
+  {Tanaka}, \& {Kodama}}]{crossfield12}
+{Crossfield}, I.~J.~M., {Barman}, T., {Hansen}, B.~M.~S., {Tanaka}, I., \&
+  {Kodama}, T. 2012, \apj, 760, 140
+
+\bibitem[{{Cruz} {et~al.}(2018){Cruz}, {N{\'u}{\~n}ez}, {Burgasser},
+  {Abrahams}, {Rice}, {Reid}, \& {Looper}}]{2018AJ....155...34C}
+{Cruz}, K.~L., {N{\'u}{\~n}ez}, A., {Burgasser}, A.~J., {et~al.} 2018, \aj,
+  155, 34
+
+\bibitem[{{Cruz} {et~al.}(2007){Cruz}, {Reid}, {Kirkpatrick}, {Burgasser},
+  {Liebert}, {Solomon}, {Schmidt}, {Allen}, {Hawley}, \&
+  {Covey}}]{2007AJ....133..439C}
+{Cruz}, K.~L., {Reid}, I.~N., {Kirkpatrick}, J.~D., {et~al.} 2007, \aj, 133,
+  439
+
+\bibitem[{{Cubillos} {et~al.}(2013){Cubillos}, {Harrington}, {Madhusudhan},
+  {Stevenson}, {Hardy}, {Blecic}, {Anderson}, {Hardin}, \&
+  {Campo}}]{cubillos13}
+{Cubillos}, P., {Harrington}, J., {Madhusudhan}, N., {et~al.} 2013, \apj, 768,
+  42
+
+\bibitem[{{de Wit} {et~al.}(2012){de Wit}, {Gillon}, {Demory}, \&
+  {Seager}}]{dewit12}
+{de Wit}, J., {Gillon}, M., {Demory}, B.-O., \& {Seager}, S. 2012, \aap, 548,
+  A128
+
+\bibitem[{{Delrez} {et~al.}(2018){Delrez}, {Madhusudhan}, {Lendl}, {Gillon},
+  {Anderson}, {Neveu-VanMalle}, {Bouchy}, {Burdanov}, {Collier-Cameron},
+  {Demory}, {Hellier}, {Jehin}, {Magain}, {Maxted}, {Queloz}, {Smalley}, \&
+  {Triaud}}]{delrez18}
+{Delrez}, L., {Madhusudhan}, N., {Lendl}, M., {et~al.} 2018, \mnras, 474, 2334
+
+\bibitem[{{Demory} {et~al.}(2013){Demory}, {de Wit}, {Lewis}, {Fortney},
+  {Zsom}, {Seager}, {Knutson}, {Heng}, {Madhusudhan}, {Gillon}, {Barclay},
+  {Desert}, {Parmentier}, \& {Cowan}}]{demory13}
+{Demory}, B.-O., {de Wit}, J., {Lewis}, N., {et~al.} 2013, \apjl, 776, L25
+
+\bibitem[{{Diamond-Lowe} {et~al.}(2014{\natexlab{a}}){Diamond-Lowe},
+  {Stevenson}, {Bean}, {Line}, \& {Fortney}}]{HDL2014}
+{Diamond-Lowe}, H., {Stevenson}, K.~B., {Bean}, J.~L., {Line}, M.~R., \&
+  {Fortney}, J.~J. 2014{\natexlab{a}}, \apj, 796, 66
+
+\bibitem[{{Diamond-Lowe} {et~al.}(2014{\natexlab{b}}){Diamond-Lowe},
+  {Stevenson}, {Bean}, {Line}, \& {Fortney}}]{diamond-lowe14}
+---. 2014{\natexlab{b}}, \apj, 796, 66
+
+\bibitem[{{Dieterich} {et~al.}(2014){Dieterich}, {Henry}, {Jao}, {Winters},
+  {Hosey}, {Riedel}, \& {Subasavage}}]{2014AJ....147...94D}
+{Dieterich}, S.~B., {Henry}, T.~J., {Jao}, W.-C., {et~al.} 2014, \aj, 147, 94
+
+\bibitem[{{Espinoza} {et~al.}(2017){Espinoza}, {Fortney}, {Miguel},
+  {Thorngren}, \& {Murray-Clay}}]{espinoza17}
+{Espinoza}, N., {Fortney}, J.~J., {Miguel}, Y., {Thorngren}, D., \&
+  {Murray-Clay}, R. 2017, \apjl, 838, L9
+
+\bibitem[{{Evans} {et~al.}(2016){Evans}, {Sing}, {Wakeford}, {Nikolov},
+  {Ballester}, {Drummond}, {Kataria}, {Gibson}, {Amundsen}, \&
+  {Spake}}]{evans16}
+{Evans}, T.~M., {Sing}, D.~K., {Wakeford}, H.~R., {et~al.} 2016, \apjl, 822, L4
+
+\bibitem[{{Faherty} {et~al.}(2010){Faherty}, {Burgasser}, {West}, {Bochanski},
+  {Cruz}, {Shara}, \& {Walter}}]{2010AJ....139..176F}
+{Faherty}, J.~K., {Burgasser}, A.~J., {West}, A.~A., {et~al.} 2010, \aj, 139,
+  176
+
+\bibitem[{{Faherty} {et~al.}(2012){Faherty}, {Burgasser}, {Walter}, {Van der
+  Bliek}, {Shara}, {Cruz}, {West}, {Vrba}, \&
+  {Anglada-Escud{\'e}}}]{2012ApJ...752...56F}
+{Faherty}, J.~K., {Burgasser}, A.~J., {Walter}, F.~M., {et~al.} 2012, \apj,
+  752, 56
+
+\bibitem[{{Faherty} {et~al.}(2016){Faherty}, {Riedel}, {Cruz}, {Gagne},
+  {Filippazzo}, {Lambrides}, {Fica}, {Weinberger}, {Thorstensen}, {Tinney},
+  {Baldassare}, {Lemonier}, \& {Rice}}]{faherty16}
+{Faherty}, J.~K., {Riedel}, A.~R., {Cruz}, K.~L., {et~al.} 2016, \apjs, 225, 10
+
+\bibitem[{{Filippazzo} {et~al.}(2015){Filippazzo}, {Rice}, {Faherty}, {Cruz},
+  {Van Gordon}, \& {Looper}}]{filippazzo15}
+{Filippazzo}, J.~C., {Rice}, E.~L., {Faherty}, J., {et~al.} 2015, \apj, 810,
+  158
+
+\bibitem[{{Foreman-Mackey} {et~al.}(2013){Foreman-Mackey}, {Hogg}, {Lang}, \&
+  {Goodman}}]{foremanmackey13}
+{Foreman-Mackey}, D., {Hogg}, D.~W., {Lang}, D., \& {Goodman}, J. 2013, \pasp,
+  125, 306
+
+\bibitem[{{Fortney} {et~al.}(2008){Fortney}, {Lodders}, {Marley}, \&
+  {Freedman}}]{fortney08}
+{Fortney}, J.~J., {Lodders}, K., {Marley}, M.~S., \& {Freedman}, R.~S. 2008,
+  \apj, 678, 1419
+
+\bibitem[{{Fortney} {et~al.}(2013){Fortney}, {Mordasini}, {Nettelmann},
+  {Kempton}, {Greene}, \& {Zahnle}}]{fortney13}
+{Fortney}, J.~J., {Mordasini}, C., {Nettelmann}, N., {et~al.} 2013, \apj, 775,
+  80
+
+\bibitem[{{Freedman} {et~al.}(2014){Freedman}, {Lustig-Yaeger}, {Fortney},
+  {Lupu}, {Marley}, \& {Lodders}}]{freedman14}
+{Freedman}, R.~S., {Lustig-Yaeger}, J., {Fortney}, J.~J., {et~al.} 2014, \apjs,
+  214, 25
+
+\bibitem[{{Gaia Collaboration} {et~al.}(2016){Gaia Collaboration}, {Prusti},
+  {de Bruijne}, {Brown}, {Vallenari}, {Babusiaux}, {Bailer-Jones}, {Bastian},
+  {Biermann}, {Evans}, \& et~al.}]{gaia16}
+{Gaia Collaboration}, {Prusti}, T., {de Bruijne}, J.~H.~J., {et~al.} 2016,
+  \aap, 595, A1
+
+\bibitem[{{Geballe} {et~al.}(2002){Geballe}, {Knapp}, {Leggett}, {Fan},
+  {Golimowski}, {Anderson}, {Brinkmann}, {Csabai}, {Gunn}, {Hawley},
+  {Hennessy}, {Henry}, {Hill}, {Hindsley}, {Ivezi{\'c}}, {Lupton}, {McDaniel},
+  {Munn}, {Narayanan}, {Peng}, {Pier}, {Rockosi}, {Schneider}, {Smith},
+  {Strauss}, {Tsvetanov}, {Uomoto}, {York}, \& {Zheng}}]{geballe02}
+{Geballe}, T.~R., {Knapp}, G.~R., {Leggett}, S.~K., {et~al.} 2002, \apj, 564,
+  466
+
+\bibitem[{{Gillon} {et~al.}(2014){Gillon}, {Anderson}, {Collier-Cameron},
+  {Delrez}, {Hellier}, {Jehin}, {Lendl}, {Maxted}, {Pepe}, {Pollacco},
+  {Queloz}, {S{\'e}gransan}, {Smith}, {Smalley}, {Southworth}, {Triaud},
+  {Udry}, {Van Grootel}, \& {West}}]{gillon14}
+{Gillon}, M., {Anderson}, D.~R., {Collier-Cameron}, A., {et~al.} 2014, \aap,
+  562, L3
+
+\bibitem[{Gordon \& McBride(1994)}]{gordon94}
+Gordon, S., \& McBride, B.~J. 1994, Computer program for calculation of complex
+  chemical equilibrium compositions and applications, Vol.~1 (National
+  Aeronautics and Space Administration, Office of Management, Scientific and
+  Technical Information Program)
+
+\bibitem[{{Grie{\ss}meier}(2015)}]{griessmeier15}
+{Grie{\ss}meier}, J.-M. 2015, in Astrophysics and Space Science Library, Vol.
+  411, Characterizing Stellar and Exoplanetary Environments, ed. H.~{Lammer} \&
+  M.~{Khodachenko}, 213
+
+\bibitem[{{Harrington} {et~al.}(2006){Harrington}, {Hansen}, {Luszcz},
+  {Seager}, {Deming}, {Menou}, {Cho}, \& {Richardson}}]{harrington06}
+{Harrington}, J., {Hansen}, B.~M., {Luszcz}, S.~H., {et~al.} 2006, Science,
+  314, 623
+
+\bibitem[{{Harrington} {et~al.}(2007){Harrington}, {Luszcz}, {Seager},
+  {Deming}, \& {Richardson}}]{Harrington2007}
+{Harrington}, J., {Luszcz}, S., {Seager}, S., {Deming}, D., \& {Richardson},
+  L.~J. 2007, Nature, 447, 691
+
+\bibitem[{{Hayes}(1985)}]{1985IAUS..111..225H}
+{Hayes}, D.~S. 1985, in IAU Symposium, Vol. 111, Calibration of Fundamental
+  Stellar Quantities, ed. D.~S. {Hayes}, L.~E. {Pasinetti}, \& A.~G.~D.
+  {Philip}, 225--249
+
+\bibitem[{{Haynes} {et~al.}(2015){Haynes}, {Mandell}, {Madhusudhan}, {Deming},
+  \& {Knutson}}]{haynes15}
+{Haynes}, K., {Mandell}, A.~M., {Madhusudhan}, N., {Deming}, D., \& {Knutson},
+  H. 2015, \apj, 806, 146
+
+\bibitem[{{Henry}(1999)}]{henry99}
+{Henry}, G.~W. 1999, \pasp, 111, 845
+
+\bibitem[{{Horne}(1986)}]{horne86}
+{Horne}, K. 1986, \pasp, 98, 609
+
+\bibitem[{{Hu} {et~al.}(2015){Hu}, {Demory}, {Seager}, {Lewis}, \&
+  {Showman}}]{hu15}
+{Hu}, R., {Demory}, B.-O., {Seager}, S., {Lewis}, N., \& {Showman}, A.~P. 2015,
+  \apj, 802, 51
+
+\bibitem[{{Hubeny} {et~al.}(2003){Hubeny}, {Burrows}, \& {Sudarsky}}]{hubeny03}
+{Hubeny}, I., {Burrows}, A., \& {Sudarsky}, D. 2003, \apj, 594, 1011
+
+\bibitem[{{Ingalls} {et~al.}(2016){Ingalls}, {Krick}, {Carey}, {Stauffer},
+  {Lowrance}, {Grillmair}, {Buzasi}, {Deming}, {Diamond-Lowe}, {Evans},
+  {Morello}, {Stevenson}, {Wong}, {Capak}, {Glaccum}, {Laine}, {Surace}, \&
+  {Storrie-Lombardi}}]{Ingalls2016}
+{Ingalls}, J.~G., {Krick}, J.~E., {Carey}, S.~J., {et~al.} 2016, \aj, 152, 44
+
+\bibitem[{Jones {et~al.}(2001)Jones, Oliphant, Peterson, \&
+  Others}]{jones_scipy_2001}
+Jones, E., Oliphant, T., Peterson, P., \& Others. 2001, {SciPy}: Open source
+  scientific tools for Python, , .
+\newblock \url{http://www.scipy.org/}
+
+\bibitem[{Kass \& Raftery(1995)}]{kass95}
+Kass, R.~E., \& Raftery, A.~E. 1995, Journal of the American Statistical
+  Association, 90, 773.
+\newblock
+  \url{http://amstat.tandfonline.com/doi/abs/10.1080/01621459.1995.10476572}
+
+\bibitem[{{Kataria} {et~al.}(2016){Kataria}, {Sing}, {Lewis}, {Visscher},
+  {Showman}, {Fortney}, \& {Marley}}]{kataria16}
+{Kataria}, T., {Sing}, D.~K., {Lewis}, N.~K., {et~al.} 2016, \apj, 821, 9
+
+\bibitem[{{Kendall} {et~al.}(2003){Kendall}, {Mauron}, {Azzopardi}, \&
+  {Gigoyan}}]{2003A&A...403..929K}
+{Kendall}, T.~R., {Mauron}, N., {Azzopardi}, M., \& {Gigoyan}, K. 2003, \aap,
+  403, 929
+
+\bibitem[{{Kirkpatrick} {et~al.}(1993){Kirkpatrick}, {Kelly}, {Rieke},
+  {Liebert}, {Allard}, \& {Wehrse}}]{kirkpatrick93}
+{Kirkpatrick}, J.~D., {Kelly}, D.~M., {Rieke}, G.~H., {et~al.} 1993, \apj, 402,
+  643
+
+\bibitem[{{Koll} \& {Komacek}(2018)}]{koll18}
+{Koll}, D.~D.~B., \& {Komacek}, T.~D. 2018, \apj, 853, 133
+
+\bibitem[{{Komacek} \& {Showman}(2016)}]{komacek16}
+{Komacek}, T.~D., \& {Showman}, A.~P. 2016, \apj, 821, 16
+
+\bibitem[{{Komacek} {et~al.}(2017){Komacek}, {Showman}, \& {Tan}}]{komacek17}
+{Komacek}, T.~D., {Showman}, A.~P., \& {Tan}, X. 2017, \apj, 835, 198
+
+\bibitem[{{Kreidberg}(2015)}]{kreidberg15a}
+{Kreidberg}, L. 2015, \pasp, 127, 1161
+
+\bibitem[{{Kreidberg} {et~al.}(2014{\natexlab{a}}){Kreidberg}, {Bean},
+  {D{\'e}sert}, {Benneke}, {Deming}, {Stevenson}, {Seager}, {Berta-Thompson},
+  {Seifahrt}, \& {Homeier}}]{kreidberg14a}
+{Kreidberg}, L., {Bean}, J.~L., {D{\'e}sert}, J.-M., {et~al.}
+  2014{\natexlab{a}}, \nat, 505, 69
+
+\bibitem[{{Kreidberg} {et~al.}(2014{\natexlab{b}}){Kreidberg}, {Bean},
+  {D{\'e}sert}, {Line}, {Fortney}, {Madhusudhan}, {Stevenson}, {Showman},
+  {Charbonneau}, {McCullough}, {Seager}, {Burrows}, {Henry}, {Williamson},
+  {Kataria}, \& {Homeier}}]{kreidberg14b}
+---. 2014{\natexlab{b}}, \apjl, 793, L27
+
+\bibitem[{{Kreidberg} {et~al.}(2015){Kreidberg}, {Line}, {Bean}, {Stevenson},
+  {D{\'e}sert}, {Madhusudhan}, {Fortney}, {Barstow}, {Henry}, {Williamson}, \&
+  {Showman}}]{kreidberg15b}
+{Kreidberg}, L., {Line}, M.~R., {Bean}, J.~L., {et~al.} 2015, \apj, 814, 66
+
+\bibitem[{{Leconte} {et~al.}(2011{\natexlab{a}}){Leconte}, {Lai}, \&
+  {Chabrier}}]{leconte11b}
+{Leconte}, J., {Lai}, D., \& {Chabrier}, G. 2011{\natexlab{a}}, \aap, 536, C1
+
+\bibitem[{{Leconte} {et~al.}(2011{\natexlab{b}}){Leconte}, {Lai}, \&
+  {Chabrier}}]{leconte11a}
+---. 2011{\natexlab{b}}, \aap, 528, A41
+
+\bibitem[{{Lendl} {et~al.}(2017){Lendl}, {Cubillos}, {Hagelberg}, {M{\"u}ller},
+  {Juvan}, \& {Fossati}}]{lendl17}
+{Lendl}, M., {Cubillos}, P.~E., {Hagelberg}, J., {et~al.} 2017, \aap, 606, A18
+
+\bibitem[{{Line} {et~al.}(2014){Line}, {Knutson}, {Wolf}, \& {Yung}}]{line14}
+{Line}, M.~R., {Knutson}, H., {Wolf}, A.~S., \& {Yung}, Y.~L. 2014, \apj, 783,
+  70
+
+\bibitem[{{Line} {et~al.}(2013){Line}, {Wolf}, {Zhang}, {Knutson}, {Kammer},
+  {Ellison}, {Deroo}, {Crisp}, \& {Yung}}]{line13a}
+{Line}, M.~R., {Wolf}, A.~S., {Zhang}, X., {et~al.} 2013, \apj, 775, 137
+
+\bibitem[{{Line} {et~al.}(2016){Line}, {Stevenson}, {Bean}, {Desert},
+  {Fortney}, {Kreidberg}, {Madhusudhan}, {Showman}, \& {Diamond-Lowe}}]{line16}
+{Line}, M.~R., {Stevenson}, K.~B., {Bean}, J., {et~al.} 2016, \aj, 152, 203
+
+\bibitem[{{Lodders} \& {Fegley}(2002)}]{Lodders2002a}
+{Lodders}, K., \& {Fegley}, B. 2002, \icarus, 155, 393
+
+\bibitem[{{Loeb} \& {Gaudi}(2003)}]{loeb03}
+{Loeb}, A., \& {Gaudi}, B.~S. 2003, \apjl, 588, L117
+
+\bibitem[{{Long} {et~al.}(2015){Long}, {Baggett}, \& {MacKenty}}]{long15}
+{Long}, K.~S., {Baggett}, S.~M., \& {MacKenty}, J.~W. 2015, {Persistence in the
+  WFC3 IR Detector: an Improved Model Incorporating the Effects of Exposure
+  Time}, Tech. rep.
+
+\bibitem[{{Louden} \& {Kreidberg}(2017)}]{louden17}
+{Louden}, T., \& {Kreidberg}, L. 2017, ArXiv e-prints, arXiv:1711.00494
+
+\bibitem[{{Lust} {et~al.}(2014){Lust}, {Britt}, {Harrington}, {Nymeyer},
+  {Stevenson}, {Ross}, {Bowman}, \& {Fraine}}]{Lust2014}
+{Lust}, N.~B., {Britt}, D., {Harrington}, J., {et~al.} 2014, \pasp, 126, 1092
+
+\bibitem[{{Madhusudhan} {et~al.}(2011){Madhusudhan}, {Harrington}, {Stevenson},
+  {Nymeyer}, {Campo}, {Wheatley}, {Deming}, {Blecic}, {Hardy}, {Lust},
+  {Anderson}, {Collier-Cameron}, {Britt}, {Bowman}, {Hebb}, {Hellier},
+  {Maxted}, {Pollacco}, \& {West}}]{madhusudhan11}
+{Madhusudhan}, N., {Harrington}, J., {Stevenson}, K.~B., {et~al.} 2011, \nat,
+  469, 64
+
+\bibitem[{{Mansfield} {et~al.}(\noop{3001}submitted){Mansfield}, {Bean},
+  {Line}, {Paramentier}, \& {Kreidberg}}]{mansfield18}
+{Mansfield}, M., {Bean}, J.~B., {Line}, M., {Paramentier}, V., \& {Kreidberg},
+  L. \noop{3001}submitted, Submitted to \apj
+
+\bibitem[{{Marley} \& {McKay}(1999)}]{Marley1999}
+{Marley}, M.~S., \& {McKay}, C.~P. 1999, \icarus, 138, 268
+
+\bibitem[{{McCullough} \& {MacKenty}(2012)}]{mccullough12}
+{McCullough}, P., \& {MacKenty}, J. 2012, {Considerations for using Spatial
+  Scans with WFC3}, Tech. rep.
+
+\bibitem[{{McLean} {et~al.}(2003){McLean}, {McGovern}, {Burgasser},
+  {Kirkpatrick}, {Prato}, \& {Kim}}]{mclean03}
+{McLean}, I.~S., {McGovern}, M.~R., {Burgasser}, A.~J., {et~al.} 2003, \apj,
+  596, 561
+
+\bibitem[{{Mordasini} {et~al.}(2016){Mordasini}, {van Boekel}, {Molli{\`e}re},
+  {Henning}, \& {Benneke}}]{mordasini16}
+{Mordasini}, C., {van Boekel}, R., {Molli{\`e}re}, P., {Henning}, T., \&
+  {Benneke}, B. 2016, \apj, 832, 41
+
+\bibitem[{{Mountain} {et~al.}(1985){Mountain}, {Selby}, {Leggett}, {Blackwell},
+  \& {Petford}}]{1985A&A...151..399M}
+{Mountain}, C.~M., {Selby}, M.~J., {Leggett}, S.~K., {Blackwell}, D.~E., \&
+  {Petford}, A.~D. 1985, \aap, 151, 399
+
+\bibitem[{{Nymeyer} {et~al.}(2011){Nymeyer}, {Harrington}, {Hardy}, {\bfseries
+  {Stevenson}, K.~B.}, {Campo}, {Madhusudhan}, {Collier-Cameron}, {Loredo},
+  {Blecic}, {Bowman}, {Britt}, {Cubillos}, {Hellier}, {Gillon}, {Maxted},
+  {Hebb}, {Wheatley}, {Pollacco}, \& {Anderson}}]{Nymeyer2011}
+{Nymeyer}, S., {Harrington}, J., {Hardy}, R.~A., {et~al.} 2011, ApJ, 742, 35
+
+\bibitem[{{Parmentier} \& {Crossfield}(2017)}]{parmentier17}
+{Parmentier}, V., \& {Crossfield}, I. 2017, ArXiv e-prints, arXiv:1711.07696
+
+\bibitem[{{Parmentier} {et~al.}(2016){Parmentier}, {Fortney}, {Showman},
+  {Morley}, \& {Marley}}]{parmentier16}
+{Parmentier}, V., {Fortney}, J.~J., {Showman}, A.~P., {Morley}, C., \&
+  {Marley}, M.~S. 2016, \apj, 828, 22
+
+\bibitem[{{Parmentier} {et~al.}(\noop{3001}submitted){Parmentier}, {Line},
+  {Bean}, {Fortney}, {D\'{e}sert}, \& {Kreidberg}}]{parmentier18}
+{Parmentier}, V., {Line}, M.~R., {Bean}, J., {et~al.} \noop{3001}submitted,
+  Submitted to A\&A
+
+\bibitem[{{Perez-Becker} \& {Showman}(2013)}]{perez13}
+{Perez-Becker}, D., \& {Showman}, A.~P. 2013, \apj, 776, 134
+
+\bibitem[{{Perna} {et~al.}(2010){Perna}, {Menou}, \& {Rauscher}}]{perna10}
+{Perna}, R., {Menou}, K., \& {Rauscher}, E. 2010, \apj, 719, 1421
+
+\bibitem[{{Pont} {et~al.}(2006){Pont}, {Zucker}, \& {Queloz}}]{pont06}
+{Pont}, F., {Zucker}, S., \& {Queloz}, D. 2006, \mnras, 373, 231
+
+\bibitem[{{Reid} {et~al.}(2001){Reid}, {Burgasser}, {Cruz}, {Kirkpatrick}, \&
+  {Gizis}}]{reid01}
+{Reid}, I.~N., {Burgasser}, A.~J., {Cruz}, K.~L., {Kirkpatrick}, J.~D., \&
+  {Gizis}, J.~E. 2001, \aj, 121, 1710
+
+\bibitem[{{Reid} {et~al.}(2008){Reid}, {Cruz}, {Kirkpatrick}, {Allen},
+  {Mungall}, {Liebert}, {Lowrance}, \& {Sweet}}]{reid08}
+{Reid}, I.~N., {Cruz}, K.~L., {Kirkpatrick}, J.~D., {et~al.} 2008, \aj, 136,
+  1290
+
+\bibitem[{{Rogers}(2017)}]{rogers17}
+{Rogers}, T.~M. 2017, Nature Astronomy, 1, 0131
+
+\bibitem[{{Rogers} \& {Komacek}(2014)}]{rogers14a}
+{Rogers}, T.~M., \& {Komacek}, T.~D. 2014, \apj, 794, 132
+
+\bibitem[{{Rogers} \& {Showman}(2014)}]{rogers14}
+{Rogers}, T.~M., \& {Showman}, A.~P. 2014, \apjl, 782, L4
+
+\bibitem[{{Sheppard} {et~al.}(2017){Sheppard}, {Mandell}, {Tamburo}, {Gandhi},
+  {Pinhas}, {Madhusudhan}, \& {Deming}}]{sheppard17}
+{Sheppard}, K.~B., {Mandell}, A.~M., {Tamburo}, P., {et~al.} 2017, \apjl, 850,
+  L32
+
+\bibitem[{{Showman} {et~al.}(2013){Showman}, {Fortney}, {Lewis}, \&
+  {Shabram}}]{showman13}
+{Showman}, A.~P., {Fortney}, J.~J., {Lewis}, N.~K., \& {Shabram}, M. 2013,
+  \apj, 762, 24
+
+\bibitem[{{Showman} {et~al.}(2009){Showman}, {Fortney}, {Lian}, {Marley},
+  {Freedman}, {Knutson}, \& {Charbonneau}}]{showman09}
+{Showman}, A.~P., {Fortney}, J.~J., {Lian}, Y., {et~al.} 2009, \apj, 699, 564
+
+\bibitem[{{Showman} \& {Guillot}(2002)}]{showman02}
+{Showman}, A.~P., \& {Guillot}, T. 2002, \aap, 385, 166
+
+\bibitem[{{Southworth} {et~al.}(2015){Southworth}, {Mancini}, {Ciceri},
+  {Budaj}, {Dominik}, {Figuera Jaimes}, {Haugb{\o}lle}, {J{\o}rgensen},
+  {Popovas}, {Rabus}, {Rahvar}, {von Essen}, {Schmidt}, {Wertz}, {Alsubai},
+  {Bozza}, {Bramich}, {Calchi Novati}, {D'Ago}, {Hinse}, {Henning},
+  {Hundertmark}, {Juncher}, {Korhonen}, {Skottfelt}, {Snodgrass}, {Starkey}, \&
+  {Surdej}}]{southworth15}
+{Southworth}, J., {Mancini}, L., {Ciceri}, S., {et~al.} 2015, \mnras, 447, 711
+
+\bibitem[{{Stevenson} {et~al.}(2014{\natexlab{a}}){Stevenson}, {Bean},
+  {Madhusudhan}, \& {Harrington}}]{stevenson14b}
+{Stevenson}, K.~B., {Bean}, J.~L., {Madhusudhan}, N., \& {Harrington}, J.
+  2014{\natexlab{a}}, \apj, 791, 36
+
+\bibitem[{{Stevenson} {et~al.}(2014{\natexlab{b}}){Stevenson}, {Bean},
+  {Madhusudhan}, \& {Harrington}}]{Stevenson2014b}
+---. 2014{\natexlab{b}}, \apj, 791, 36
+
+\bibitem[{{Stevenson} {et~al.}(2014{\natexlab{c}}){Stevenson}, {Bean},
+  {Seifahrt}, {D{\'e}sert}, {Madhusudhan}, {Bergmann}, {Kreidberg}, \&
+  {Homeier}}]{Stevenson2014a}
+{Stevenson}, K.~B., {Bean}, J.~L., {Seifahrt}, A., {et~al.} 2014{\natexlab{c}},
+  \aj, 147, 161
+
+\bibitem[{{Stevenson} {et~al.}(2016){Stevenson}, {Bean}, {Seifahrt}, {Gilbert},
+  {Line}, {Desert}, \& {Fortney}}]{Stevenson2016a}
+---. 2016, \apj, 817, 141
+
+\bibitem[{{Stevenson} {et~al.}(2012{\natexlab{a}}){Stevenson}, {Harrington},
+  {Fortney}, {Loredo}, {et~al.}}]{Stevenson2012a}
+{Stevenson}, K.~B., {Harrington}, J., {Fortney}, J.~J., {Loredo}, T.~J.,
+  {et~al.} 2012{\natexlab{a}}, \apj, 754, 136
+
+\bibitem[{{Stevenson} {et~al.}(2012{\natexlab{b}}){Stevenson}, {Harrington},
+  {Lust}, {Lewis}, {et~al.}}]{Stevenson2012b}
+{Stevenson}, K.~B., {Harrington}, J., {Lust}, N.~B., {Lewis}, N.~K., {et~al.}
+  2012{\natexlab{b}}, \apj, 755, 9
+
+\bibitem[{{Stevenson} {et~al.}(2010){Stevenson}, {Harrington}, {Nymeyer},
+  {Madhusudhan}, {et~al.}}]{Stevenson2010}
+{Stevenson}, K.~B., {Harrington}, J., {Nymeyer}, S., {Madhusudhan}, N.,
+  {et~al.} 2010, \nat, 464, 1161
+
+\bibitem[{{Stevenson} {et~al.}(2012{\natexlab{c}}){Stevenson}, {Harrington},
+  {Fortney}, {Loredo}, {Hardy}, {Nymeyer}, {Bowman}, {Cubillos}, {Bowman}, \&
+  {Hardin}}]{stevenson12}
+{Stevenson}, K.~B., {Harrington}, J., {Fortney}, J.~J., {et~al.}
+  2012{\natexlab{c}}, \apj, 754, 136
+
+\bibitem[{{Stevenson} {et~al.}(2014{\natexlab{d}}){Stevenson}, {D{\'e}sert},
+  {Line}, {Bean}, {Fortney}, {Showman}, {Kataria}, {Kreidberg}, {McCullough},
+  {Henry}, {Charbonneau}, {Burrows}, {Seager}, {Madhusudhan}, {Williamson}, \&
+  {Homeier}}]{stevenson14}
+{Stevenson}, K.~B., {D{\'e}sert}, J.-M., {Line}, M.~R., {et~al.}
+  2014{\natexlab{d}}, Science, 346, 838
+
+\bibitem[{{Stevenson} {et~al.}(2017{\natexlab{a}}){Stevenson}, {Line}, {Bean},
+  {D{\'e}sert}, {Fortney}, {Showman}, {Kataria}, {Kreidberg}, \&
+  {Feng}}]{stevenson17}
+{Stevenson}, K.~B., {Line}, M.~R., {Bean}, J.~L., {et~al.} 2017{\natexlab{a}},
+  \aj, 153, 68
+
+\bibitem[{{Stevenson} {et~al.}(2017{\natexlab{b}}){Stevenson}, {Line}, {Bean},
+  {D{\'e}sert}, {Fortney}, {Showman}, {Kataria}, {Kreidberg}, \&
+  {Feng}}]{Stevenson2017a}
+---. 2017{\natexlab{b}}, \aj, 153, 68
+
+\bibitem[{{Teixeira} {et~al.}(2009){Teixeira}, {Ducourant}, {Chauvin},
+  {Krone-Martins}, {Bonnefoy}, \& {Song}}]{teixeira09}
+{Teixeira}, R., {Ducourant}, C., {Chauvin}, G., {et~al.} 2009, \aap, 503, 281
+
+\bibitem[{{Tinetti} {et~al.}(2012){Tinetti}, {Tennyson}, {Griffith}, \&
+  {Waldmann}}]{tinetti12}
+{Tinetti}, G., {Tennyson}, J., {Griffith}, C.~A., \& {Waldmann}, I. 2012,
+  Philosophical Transactions of the Royal Society of London Series A, 370, 2749
+
+\bibitem[{Van Der~Walt {et~al.}(2011)Van Der~Walt, Colbert, \&
+  Varoquaux}]{van2011numpy}
+Van Der~Walt, S., Colbert, S.~C., \& Varoquaux, G. 2011, Computing in Science
+  \& Engineering, 13, 22
+
+\bibitem[{{Visscher} {et~al.}(2006){Visscher}, {Lodders}, \&
+  {Fegley}}]{Visscher2006}
+{Visscher}, C., {Lodders}, K., \& {Fegley}, Jr., B. 2006, \apj, 648, 1181
+
+\bibitem[{{Wahhaj} {et~al.}(2011){Wahhaj}, {Liu}, {Biller}, {Clarke},
+  {Nielsen}, {Close}, {Hayward}, {Mamajek}, {Cushing}, {Dupuy}, {Tecza},
+  {Thatte}, {Chun}, {Ftaclas}, {Hartung}, {Reid}, {Shkolnik}, {Alencar},
+  {Artymowicz}, {Boss}, {de Gouveia Dal Pino}, {Gregorio-Hetem}, {Ida},
+  {Kuchner}, {Lin}, \& {Toomey}}]{wahhaj11}
+{Wahhaj}, Z., {Liu}, M.~C., {Biller}, B.~A., {et~al.} 2011, \apj, 729, 139
+
+\bibitem[{{W{\"o}llert} \& {Brandner}(2015)}]{wollert15}
+{W{\"o}llert}, M., \& {Brandner}, W. 2015, \aap, 579, A129
+
+\bibitem[{{Wong} {et~al.}(2004){Wong}, {Mahaffy}, {Atreya}, {Niemann}, \&
+  {Owen}}]{wong04}
+{Wong}, M.~H., {Mahaffy}, P.~R., {Atreya}, S.~K., {Niemann}, H.~B., \& {Owen},
+  T.~C. 2004, \icarus, 171, 153
+
+\bibitem[{{Wright} \& {Miller}(2015)}]{wright15}
+{Wright}, J.~T., \& {Miller}, B. 2015, IAU General Assembly, 22, 2258453
+
+\bibitem[{{Zellem} {et~al.}(2017){Zellem}, {Swain}, {Roudier}, {Shkolnik},
+  {Creech-Eakman}, {Ciardi}, {Line}, {Iyer}, {Bryden}, {Llama}, \&
+  {Fahy}}]{zellem17}
+{Zellem}, R.~T., {Swain}, M.~R., {Roudier}, G., {et~al.} 2017, \apj, 844, 27
+
+\bibitem[{{Zhang} \& {Showman}(2017)}]{zhang17}
+{Zhang}, X., \& {Showman}, A.~P. 2017, \apj, 836, 73
+
+\bibitem[{{Zhou} {et~al.}(2017){Zhou}, {Apai}, {Lew}, \& {Schneider}}]{zhou17}
+{Zhou}, Y., {Apai}, D., {Lew}, B.~W.~P., \& {Schneider}, G. 2017, \aj, 153, 243
+
+\end{thebibliography}
 

### 2018-04-30 ApJ_submit_v3/response.txt
ref report 2

To the editor:

We thank the referee for his or her additional comments. We have edited the
manuscript and respond to the comments below.

**************

1. In section 2.3, I have one additional question regarding the authors' differential atmospheric extinction. When the authors state that they determined their extinction coefficient on a seasonal basis and plots of "differential magnitudes versus mean air mass", do the authors mean that this is the mean air mass of the observation in a given night?

I would have thought the correction would be as a differential magnitude vs airmass for all data points in the season. However, I can't tell if the authors are implying that they are first averaging all frames taken in an observing night, and then using only the summed nightly data to inform the atmospheric extinction correction. Either option is fine, but a quick clarification in the text would be helpful.

#
We

2. I understand the authors argument for not showing reference star time series. The only concern I had was if one of the reference stars was variable at the several percent level, and this variation was being diluted and influencing the photometry of the target star. In lieu of plots of the reference stars, a statement to this effect is just as good.

Likewise, I would like some clarification in Figure 1. Currently panel 3 (the phase plot) is in black and white, but it would be useful for the points to be colored by observing season or a gradient from min(time) to max(time), to be sure that the proposed period phases up between observing seasons and cycles. I would also like the y-axis of panel 2 to be changed so that the actual data can be seen better and that it's not scrunched up in the bottom of the plot. I'm particularly interested in what appears to be an equally high peak in the frequency spectrum next to the proposed rotation period, and how the authors decide which peak is the "true" rotation period (unless it's just the peak the matches the measured v sin(i)

#
Since the stellar rotation period is so short compared to the observing season
(6.8 days compared to several months), each season has good phase coverage

3. (optional) In the caption of Figure 5, please state the bin size in minutes or hours. I understand that it's stated in the text but there is probably a sizeable portion of researchers who would read the figure and figure caption alone and this would be of benefit. I would also like a horizontal error bar on the data points to illustrate the span of each binned data point, but this part can be optional.

#
We stated the bin size in hours in the caption. We decided to leave off the
horizontal error bar, since this is a nonstandard way of displaying binned data
and may be confusing to some readers.

******

4. (optional) I thank the authors for adding a 100ppm scale bar on Figure 6. I still believe at least some of the sub-plots can have the same scale. For example, the 3rd and 4th panel on the top row and the 1st and 2nd panels on the bottom row are all almost identical to each other in scale. However, they are all slightly different, which doesn't seem necessary. While I believe enforcing the same scale for sub-plots that are already very close to each other will make the manuscript and presentation clearer, this is also optional.
#
We modified the axes so that spectra with symmetric phases (0.1 and 0.9, 0.2 and
0.8, etc. ) have the same y-limits.

5. (optional) I would prefer different wording in section 4.3 than the (added) "From a glance at Figure 8, the amplitude of the effect is ~100 ppm". The authors should be less colloquial and state "We estimated the amplitude of this effect by eye to be ~100 ppm" or something similar, such as "visual inspection". 
#
We reworded this sentence to state "By visual inspection of Figure 8, we estimated the amplitude of this effect to be about 100 ppm".

6. Nightside Spectrum: The authors have declined to fit a nightside spectrum at phase 0.9 to compare with their analysis with the spectrum at phase 0.1. This is fine, since the authors note that they are unable to constrain the C/O abundance or the metallicity significantly. However, the authors state the best fit spectrum has a non-inverted TP profile, which the authors imply is a robust statement.

If the authors do not wish to run a retrieval on phase 0.9, then at least some confidence interval should be assigned to the claim of a non-inverted temperature pressure profile on the night side of the planet. Is the spectrum also consistent with an inverted profile or can that be ruled out at some confidence? How "best" is the "best fit". This statement should be quantified.

7. For Figure 17, instead of adjusting the plots to be on similar y-axis scale through some normalization (which the authors don't wish to do), please add a statement to the caption noting the changing y-axis to give the reader extra chances to notice it if skimming.
#
We added the sentence "Note that the panels do not have the same y-scale, since
the objects have different radii which leads to large variation in absolute
flux."

### 2018-04-30 ApJ_submit_v3/ms.tex
ref report 2

--- 2018-04-20 arxiv_v1/ms.tex
@@
 \includegraphics[width = 1.0\textwidth]{fig5.pdf}
-\caption{WASP-103b phase curve observations from \HST/WFC3 (top) and \Spitzer/IRAC (middle and bottom).
-For clarity, the data are phase-folded on the planet's orbital period and binned in 30 uniformly spaced bins between 0 and 1.
+\caption{WASP-103b phase curve observations from \HST/WFC3 (top) and
+\Spitzer/IRAC (middle and bottom). For clarity, the data are phase-folded on the
+planet's orbital period and binned in 30 uniformly spaced bins between 0 and 1
+\added{(corresponding to 0.8 hours)}.
 The left column shows the phase curves with systematic noise removed (black points) compared to the best fit spherical harmonics model (colored lines).
@@
 If the phase variation is absorbed into the systematic model, the measured eclipse depths would be biased low.
-From a glance at Figure\,\ref{fig:model_comparison}, the amplitude of this effect is $\sim100$ ppm, which is comparable to the offset between the two analyses.
+\added{By visual inspection} of Figure\,\ref{fig:model_comparison}, we estimate the amplitude of this effect is $\sim100$ ppm, which is comparable to the offset between the two analyses.
 Our estimated uncertainties are a factor of four smaller than those reported in \cite{cartier17}, which is consistent with photon-limited expectations (our data set includes two additional eclipses, a factor of five longer out-of-eclipse baseline, and has 60\% larger wavelength bins).
@@
 \includegraphics[width = 1.0\textwidth]{fig17.pdf}
-\caption{Flux-calibrated spectra for WASP-103b (left column) compared to observed spectra for brown dwarfs (middle) and directly imaged companions (right), assuming a distance of 10 pc.
-The WASP-103b spectra are from the nightside (phase 0.1, top row), quadrature (phase 0.25, middle) and the dayside (phase 0.5, bottom).
-Each row shows spectra from objects of comparable temperature.
-The dotted gray line corresponds to the best fit blackbody.
-Effective temperatures are listed in the upper right corners.
-The wavelength bins used to calculate the water feature amplitude $A_1$ are shaded in gray.}
+\caption{Flux-calibrated spectra for WASP-103b (left column) compared to
+observed spectra for brown dwarfs (middle) and directly imaged companions
+(right), assuming a distance of 10 pc. The WASP-103b spectra are from the
+nightside (phase 0.1, top row), quadrature (phase 0.25, middle) and the dayside
+(phase 0.5, bottom). Each row shows spectra from objects of comparable
+temperature. The dotted gray line corresponds to the best fit blackbody.
+Effective temperatures are listed in the upper right corners. The wavelength
+bins used to calculate the water feature amplitude $A_1$ are shaded in gray.
+\added{Note that the panels do not have the same y-scale, since the objects have
+different radii which leads to large variation in absolute flux.}}
 \label{fig:planetstarcomparison}
@@
 \acknowledgments
-Support for \textit{HST} program GO-15050 was provided by NASA through a grant from the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS 5-26555.
-Support for \textit{Spitzer} program 11099 was provided by NASA through an award issued by JPL/Caltech.
-The data presented in this paper were obtained from the Mikulski Archive for Space Telescopes (MAST) and the NASA/IPAC Infrared Science Archive.
-The Infrared Science Archive is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration.
-This work also made use of the Python packages  SciPy and NumPy \citep{jones_scipy_2001, van2011numpy}.
-The authors are grateful for helpful conversations with Caroline Morley, Thomas Beatty, Ming Zhao, Kim Star Cartier, Hannah Diamond-Lowe, and Nick Cowan.
-We also thank the organizers of the 2016 Santa Cruz Kavli Summer Program and the 2017 Ringberg Atmospheres of Disks and Planets meeting for facilitating productive discussion and collaboration.
-J.L.B.
-acknowledges support from the David and Lucile Packard Foundation.
-J.M.D.
-acknowledges support from the European Research Council (ERC) under the programme Exo-Atmos (grant agreement no.
-679633).
-G.W.H.
-and M.H.W.
-also acknowledge long-term support from Tennessee State University and the State of Tennessee through its Centers of Excellence Program.
+Support for \textit{HST} program GO-15050 was provided by NASA through a grant
+from the Space Telescope Science Institute, which is operated by the Association
+of Universities for Research in Astronomy, Inc., under NASA contract NAS
+5-26555. Support for \textit{Spitzer} program 11099 was provided by NASA through
+an award issued by JPL/Caltech.  The data presented in this paper were obtained
+from the Mikulski Archive for Space Telescopes (MAST) and the NASA/IPAC Infrared
+Science Archive. The Infrared Science Archive is operated by the Jet Propulsion
+Laboratory, California Institute of Technology, under contract with the National
+Aeronautics and Space Administration.  This work also made use of the Python
+packages  SciPy and NumPy \citep{jones_scipy_2001, van2011numpy}. The authors
+are grateful for helpful conversations with Caroline Morley, Thomas Beatty, Ming
+Zhao, Kim Star Cartier, Hannah Diamond-Lowe, and Nick Cowan. We also thank the
+organizers of the 2016 Santa Cruz Kavli Summer Program and the 2017 Ringberg
+Atmospheres of Disks and Planets meeting for facilitating productive discussion
+and collaboration.  J.L.B. acknowledges support from the David and Lucile
+Packard Foundation.  J.M.D. acknowledges support from the European Research
+Council (ERC) under the programme Exo-Atmos (grant agreement no. 679633). G.W.H.
+and M.H.W. also acknowledge long-term support from Tennessee State University
+and the State of Tennessee through its Centers of Excellence Program. M.R.L.
+acknowledges NASA XRP grant NNX17AB56G for partial support of the theoretical
+interpretation of the data, as well as the ASU Research Computing staff for
+support with the Saguaro and Agave compute clusters. Finally, we thank the
+anonymous referee for a thoughtful and detailed report that improved the quality of the
+paper.
 

### 2018-05-02 ApJ_submit_v3/response.txt
response

@@
 #
-We
+We have clarified the description as follows: "...were corrected for bias,
+flat-fielding, and atmospheric extinction.  We determined extinction corrections
+from linear, least-squares fits to seasonal plots of nightly differential
+magnitudes versus air mass and computing the slope in magnitudes per airmass."
 
@@
 #
+None of the reference stars had significant variability.
 Since the stellar rotation period is so short compared to the observing season

### 2018-05-02 ApJ_submit_v3/ms.tex
response

@@
 The nightly observations were corrected for bias, flat-fielding, and differential atmospheric extinction.
-We determined seasonal-mean extinction coefficients from a linear, least-squares fits to seasonal plots of differential magnitudes versus mean air mass and computed the slope in magnitudes per air mass.
+\added{We determined extinction corrections from linear, least-squares fits to seasonal plots of nightly differential magnitudes versus air mass and computing the slope in magnitudes per airmass.}
 

### 2018-05-02 ApJ_submit_v3/ms.tex
second submission

@@
 
-WASP-103b is an archetype of the class of ultra-hot Jupiters, with orbital periods of about one day and dayside temperatures typically $>2000\,\mathrm{K}$.
-These very hot planets were initially predicted to have inverted temperature pressure profiles due to strong optical absorption by TiO/VO in the upper atmospheres \citep{hubeny03, fortney08}; however, observations of their emission spectra have been inconclusive on their thermal structure and composition.
-In the near-infrared, where water is the dominant absorber, some spectra show water absorption features, some show emission features, and some are consistent with blackbody models \citep{madhusudhan11, crossfield12, stevenson14b, haynes15, evans16, beatty17a, beatty17b, sheppard17, arcangeli18, mansfield18}.
-A variety of explanations have been proposed for these results, including low metallicity or high carbon-to-oxygen compositions, dayside clouds, and finely tuned isothermal temperature pressure profiles.
-Recently, \cite{arcangeli18} showed that water dissociation and H- opacity on the hot dayside play an important role in the atmospheres of these ultra-hot planets and may be responsible for some of the blackbody-like near-IR spectra.
+WASP-103b is an archetype of the class of ultra-hot Jupiters, with orbital
+periods of about one day and dayside temperatures typically $>2000\,\mathrm{K}$.
+These very hot planets were initially predicted to have inverted temperature
+pressure profiles due to strong optical absorption by TiO/VO in the upper
+atmospheres \citep{hubeny03, fortney08}; however, observations of their emission
+spectra have been inconclusive on their thermal structure and composition. In
+the near-infrared, where water is the dominant absorber, some spectra show water
+absorption features, some show emission features, and some are consistent with
+blackbody models \citep{madhusudhan11, crossfield12, stevenson14b, haynes15,
+evans16, beatty17a, beatty17b, sheppard17, arcangeli18, mansfield18}.  A variety
+of explanations have been proposed for these results, including low metallicity
+or high carbon-to-oxygen compositions, dayside clouds, and finely tuned
+isothermal temperature pressure profiles. Recently, \cite{arcangeli18,
+lothringer18} showed that water dissociation and H- opacity on the hot dayside play an important role in the atmospheres of these ultra-hot planets and may be responsible for some of the blackbody-like near-IR spectra.
 In this work, we put these results in context by investigating the global thermal structure and composition of the ultra-hot Jupiter WASP-103b.
@@
 
-To maximize the possibility of detecting WASP-103's rotation, we normalized the photometry such that each observing season has the same mean, thereby removing any long-term variability in WASP-103 and/or the comparison stars (Figure\,\ref{fig:photometry}, top panel).
-To estimate the stellar rotation period, we performed a periodogram analysis of the normalized data set based on least-squares fitting of sine curves.
-The resulting frequency spectrum and the phase curve computed with the best period are shown in the middle and lower panels of Figure\,\ref{fig:photometry} respectively.
-The best-fit period is 6.814 days, which agrees closely with the estimated stellar rotation period of 6.855 days \citep[based on the projected stellar rotation velocity and stellar radius reported in][]{gillon14}.
-The peak-to-peak variability amplitude is 0.005 mag.
+To maximize the possibility of detecting WASP-103's rotation, we normalized the
+photometry such that each observing season has the same mean, thereby removing
+any long-term variability in WASP-103 and/or the comparison stars
+(Figure\,\ref{fig:photometry}, top panel).  To estimate the stellar rotation
+period, we performed a periodogram analysis of the normalized data set based on
+least-squares fitting of sine curves.  The resulting frequency spectrum and the
+phase curve computed with the best period are shown in the middle and lower
+panels of Figure\,\ref{fig:photometry} respectively. The best-fit period is
+6.814 days, which agrees closely with the estimated stellar rotation period of
+6.855 days \citep[based on the projected stellar rotation velocity and stellar
+radius reported in][]{gillon14}. \added{There are two nearby peaks in the
+periodogram (panel b of Figure\,\ref{fig:photometry}) that are one-year aliases
+of each other, and we chose the peak that better matches the stellar rotation velocity.} The peak-to-peak variability amplitude is 0.005 mag.
 Based on the formalism in \cite{zellem17}, we calculate that this variability will bias the measured eclipse depth by $\lesssim10$\,parts per million (ppm) from epoch to epoch, which is well below the photon-limited precision of our measurements.
@@
 We also fit the nightside spectrum (phase $0.1$) with the grid-based retrieval.
-The best fit spectrum has a non-inverted temperature pressure profile.
-At 1\,$\sigma$ confidence, the metallicity is $15 - 240\times$ solar and the C/O is unbounded over the full prior range.
-The atmospheric composition is consistent with results from the dayside spectrum.
+The best fit spectrum has a non-inverted temperature pressure profile.  At
+1\,$\sigma$ confidence, the metallicity is $15 - 240\times$ solar and the C/O is
+unbounded over the full prior range. The atmospheric composition is consistent
+with results from the dayside spectrum.
 
@@
 Further work is needed to develop a fully self-consistent 2-D retrieval method for phase curve observations.
+
+\added{As a test, we also calculated the difference in brightness temperature
+between the \HST\ and \Spitzer\ 4.5 $\mu$m data (reported in
+Table\,\ref{table:teffs}) for both nightside phases ($\phi = 0.1$ and 0.9). At
+phase 0.1 and 0.9, the \Spitzer\ temperature is lower by 2.7 and 5.6\,$\sigma$,
+respectively.  These values are a lower limit to the significance, because the
+brightness temperatures noted in the table also include the uncertainty in the
+stellar $T_\mathrm{eff}$ (which increases the uncertainty on the absolute planet
+temperature but not the relative temperatures that are relevant for this
+calculation).
+The drop in brightness temperature is more significant at phase 0.9 than it is at 0.1, providing further evidence in addition to the phase 0.1 retrieval that the nightside temperature pressure profile is not inverted.}
 
@@
 \expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
-\providecommand{\url}[1]{\href{#1}{#1}}
 
@@
 Adcroft, A., Campin, J.-M., Hill, C., \& Marshall, J. 2004, Monthly Weather
-  Review, 132, 2845.
-\newblock \url{https://doi.org/10.1175/MWR2823.1}
+  Review, 132, 2845
 
@@
 \bibitem[{Braak(2006)}]{braak06}
-Braak, C. J. F.~T. 2006, Statistics and Computing, 16, 239.
-\newblock \url{http://dx.doi.org/10.1007/s11222-006-8769-1}
+Braak, C. J. F.~T. 2006, Statistics and Computing, 16, 239
 
@@
 Jones, E., Oliphant, T., Peterson, P., \& Others. 2001, {SciPy}: Open source
-  scientific tools for Python, , .
-\newblock \url{http://www.scipy.org/}
+  scientific tools for Python, ,
 
@@
 Kass, R.~E., \& Raftery, A.~E. 1995, Journal of the American Statistical
-  Association, 90, 773.
-\newblock
-  \url{http://amstat.tandfonline.com/doi/abs/10.1080/01621459.1995.10476572}
+  Association, 90, 773
 
@@
 \bibitem[{{Kreidberg} {et~al.}(2014{\natexlab{a}}){Kreidberg}, {Bean},
-  {D{\'e}sert}, {Benneke}, {Deming}, {Stevenson}, {Seager}, {Berta-Thompson},
-  {Seifahrt}, \& {Homeier}}]{kreidberg14a}
-{Kreidberg}, L., {Bean}, J.~L., {D{\'e}sert}, J.-M., {et~al.}
-  2014{\natexlab{a}}, \nat, 505, 69
-
-\bibitem[{{Kreidberg} {et~al.}(2014{\natexlab{b}}){Kreidberg}, {Bean},
   {D{\'e}sert}, {Line}, {Fortney}, {Madhusudhan}, {Stevenson}, {Showman},
@@
   {Kataria}, \& {Homeier}}]{kreidberg14b}
----. 2014{\natexlab{b}}, \apjl, 793, L27
+{Kreidberg}, L., {Bean}, J.~L., {D{\'e}sert}, J.-M., {et~al.}
+  2014{\natexlab{a}}, \apjl, 793, L27
+
+\bibitem[{{Kreidberg} {et~al.}(2014{\natexlab{b}}){Kreidberg}, {Bean},
+  {D{\'e}sert}, {Benneke}, {Deming}, {Stevenson}, {Seager}, {Berta-Thompson},
+  {Seifahrt}, \& {Homeier}}]{kreidberg14a}
+---. 2014{\natexlab{b}}, \nat, 505, 69
 
@@
   Time}, Tech. rep.
+
+\bibitem[{{Lothringer} {et~al.}(2018){Lothringer}, {Barman}, \&
+  {Koskinen}}]{lothringer18}
+{Lothringer}, J.~D., {Barman}, T., \& {Koskinen}, T. 2018, ArXiv e-prints,
+  arXiv:1805.00038
 
@@
 
-\bibitem[{{Mansfield} {et~al.}(\noop{3001}submitted){Mansfield}, {Bean},
-  {Line}, {Paramentier}, \& {Kreidberg}}]{mansfield18}
-{Mansfield}, M., {Bean}, J.~B., {Line}, M., {Paramentier}, V., \& {Kreidberg},
-  L. \noop{3001}submitted, Submitted to \apj
+\bibitem[{{Mansfield} {et~al.}(2018){Mansfield}, {Bean}, {Line}, {Parmentier},
+  {Kreidberg}, {Desert}, {Fortney}, {Stevenson}, {Arcangeli}, \&
+  {Dragomir}}]{mansfield18}
+{Mansfield}, M., {Bean}, J.~L., {Line}, M.~R., {et~al.} 2018, ArXiv e-prints,
+  arXiv:1805.00424
 
@@
 
-\bibitem[{{Parmentier} {et~al.}(\noop{3001}submitted){Parmentier}, {Line},
-  {Bean}, {Fortney}, {D\'{e}sert}, \& {Kreidberg}}]{parmentier18}
-{Parmentier}, V., {Line}, M.~R., {Bean}, J., {et~al.} \noop{3001}submitted,
-  Submitted to A\&A
+\bibitem[{{Parmentier} {et~al.}(2018){Parmentier}, {Line}, {Bean}, {Mansfield},
+  {Kreidberg}, {Lupu}, {Visscher}, {Desert}, {Fortney}, {Deleuil}, {Arcangeli},
+  {Showman}, \& {Marley}}]{parmentier18}
+{Parmentier}, V., {Line}, M.~R., {Bean}, J.~L., {et~al.} 2018, ArXiv e-prints,
+  arXiv:1805.00096
 

### 2018-05-04 arxiv_v2/ms.tex
arxiv v2

--- 2018-05-02 ApJ_submit_v3/ms.tex
@@
 \affiliation{Vanderbilt University, Dept. of Physics and Astronomy, 6301 Stevenson Center Ln, Nashville TN, 37235, USA}
+
+\author{Thomas G.\ Beatty}
+\affiliation{Department of Astronomy \& Astrophysics, The Pennsylvania State University, 525 Davey Lab, University Park, PA 16802}
+\affiliation{Center for Exoplanets and Habitable Worlds, The Pennsylvania State University, 525 Davey Lab, University Park, PA 16802}
 
@@
 The nightly observations were corrected for bias, flat-fielding, and differential atmospheric extinction.
-\added{We determined extinction corrections from linear, least-squares fits to seasonal plots of nightly differential magnitudes versus air mass and computing the slope in magnitudes per airmass.}
+We determined extinction corrections from linear, least-squares fits to seasonal plots of nightly differential magnitudes versus air mass and computing the slope in magnitudes per airmass.
 
@@
 6.855 days \citep[based on the projected stellar rotation velocity and stellar
-radius reported in][]{gillon14}. \added{There are two nearby peaks in the
+radius reported in][]{gillon14}. There are two nearby peaks in the
 periodogram (panel b of Figure\,\ref{fig:photometry}) that are one-year aliases
-of each other, and we chose the peak that better matches the stellar rotation velocity.} The peak-to-peak variability amplitude is 0.005 mag.
+of each other, and we chose the peak that better matches the stellar rotation velocity.
+The peak-to-peak variability amplitude is 0.005 mag.
 Based on the formalism in \cite{zellem17}, we calculate that this variability will bias the measured eclipse depth by $\lesssim10$\,parts per million (ppm) from epoch to epoch, which is well below the photon-limited precision of our measurements.
@@
 planet's orbital period and binned in 30 uniformly spaced bins between 0 and 1
-\added{(corresponding to 0.8 hours)}.
+(corresponding to 0.8 hours).
 The left column shows the phase curves with systematic noise removed (black points) compared to the best fit spherical harmonics model (colored lines).
@@
 If the phase variation is absorbed into the systematic model, the measured eclipse depths would be biased low.
-\added{By visual inspection} of Figure\,\ref{fig:model_comparison}, we estimate the amplitude of this effect is $\sim100$ ppm, which is comparable to the offset between the two analyses.
+By visual inspection of Figure\,\ref{fig:model_comparison}, we estimate the amplitude of this effect is $\sim100$ ppm, which is comparable to the offset between the two analyses.
 Our estimated uncertainties are a factor of four smaller than those reported in \cite{cartier17}, which is consistent with photon-limited expectations (our data set includes two additional eclipses, a factor of five longer out-of-eclipse baseline, and has 60\% larger wavelength bins).
@@
 
-\added{As a test, we also calculated the difference in brightness temperature
+As a test, we also calculated the difference in brightness temperature
 between the \HST\ and \Spitzer\ 4.5 $\mu$m data (reported in
@@
 calculation).
-The drop in brightness temperature is more significant at phase 0.9 than it is at 0.1, providing further evidence in addition to the phase 0.1 retrieval that the nightside temperature pressure profile is not inverted.}
+The drop in brightness temperature is more significant at phase 0.9 than it is at 0.1, providing further evidence in addition to the phase 0.1 retrieval that the nightside temperature pressure profile is not inverted.
 
@@
 bins used to calculate the water feature amplitude $A_1$ are shaded in gray.
-\added{Note that the panels do not have the same y-scale, since the objects have
-different radii which leads to large variation in absolute flux.}}
+Note that the panels do not have the same y-scale, since the objects have
+different radii which leads to large variation in absolute flux.}
 \label{fig:planetstarcomparison}

### 2018-05-04 ApJ_submit_v4/response.txt
correct zhang reference

--- 2018-05-02 ApJ_submit_v3/response.txt
@@
 #
-None of the reference stars had significant variability.
-Since the stellar rotation period is so short compared to the observing season
-(6.8 days compared to several months), each season has good phase coverage
+None of the reference stars had significant variability. We added this statemetn
+to the text.
+
+Regarding the color-coding for panel 3: this is unecessary because the stellar
+rotation period is very short compared to the observing season, so each season
+has comparably good phase coverage of the rotation period.
+
+We modified the y-axis scale in panel 2. It's true that both peaks in the
+periodogram have very comparable strength (the periods are 1-year aliases of
+each other), but as the referee correctly surmised the peak we chose is a better
+match to the v sin(i). We added this clarification to the text.
 
@@
 This statement should be quantified.
+#
+We calculated the drop in brightness temperature between the WFC3 blackbody fit
+and a fit to the Spitzer 4.5 micron point at phase 0.9 (reported in Table 6).
+The Spitzer temperature is cooler than the WFC3 temperature by 5.6 sigma.  This
+value is a lower limit to the significance, because the brightenss temperatures
+noted in the table also include the uncertainty in the stellar Teff (which
+increases the error bar on absolute planet temperature but not the relative temperatures we
+care about here). We note that the drop in brightness temperature is actually
+stronger at phase 0.9 than it is at 0.1 (5.6 versus 2.7 sigma). Combined with
+the retrieval we did for phase 0.1, this is conclusive evidence that the
+nightside temperature profile is not inverted.
+
+We added this quantification to the text.
 

### 2018-05-04 arxiv_v1/ms.tex
acknowledgment from Mike
correct zhang reference

@@
 
-For all three phase curves, the hotspot offset is consistent with zero degrees, which could indicate a small ratio of radiative to advective timescales (the incident flux is reradiated to space faster than it is advected around to the nightside).
-Fast radiative timescales are predicted at high temperatures, and small hotspot offsets are also observed for other very hot Jupiters \citep{perez13, komacek16, komacek17}.
-The measured offsets are inconsistent with the trend reported in \cite{zhang17}, which predicts the hotspot offset increases with planet temperature for irradiation temperatures greater than 3410 K.
-The \cite{zhang17} model predicts an eastward hotspot offset of $4.5^\circ$ for WASP-103b, which is significantly larger than observed, hinting at diversity in the circulation patterns of the hottest planets.
+For all three phase curves, the hotspot offset is consistent with zero degrees,
+which could indicate a small ratio of radiative to advective timescales (the
+incident flux is reradiated to space faster than it is advected around to the
+nightside). Fast radiative timescales are predicted at high temperatures, and
+small hotspot offsets are also observed for other very hot Jupiters
+\citep{perez13, komacek16, komacek17}.  The measured offsets are inconsistent
+with the trend reported in \cite{zhang18}, which predicts the hotspot offset
+increases with planet temperature for irradiation temperatures greater than 3410
+K.
+The \cite{zhang18} model predicts an eastward hotspot offset of $4.5^\circ$ for WASP-103b, which is significantly larger than observed, hinting at diversity in the circulation patterns of the hottest planets.
 The phase curve amplitudes are large (near 0.8 - 0.9), as expected for an atmosphere with inefficient heat redistribution.
@@
 \acknowledgments
-Support for \textit{HST} program GO-15050 was provided by NASA through a grant from the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS 5-26555.
-Support for \textit{Spitzer} program 11099 was provided by NASA through an award issued by JPL/Caltech.
-The data presented in this paper were obtained from the Mikulski Archive for Space Telescopes (MAST) and the NASA/IPAC Infrared Science Archive.
-The Infrared Science Archive is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration.
-This work also made use of the Python packages  SciPy and NumPy \citep{jones_scipy_2001, van2011numpy}.
-The authors are grateful for helpful conversations with Caroline Morley, Thomas Beatty, Ming Zhao, Kim Star Cartier, Hannah Diamond-Lowe, and Nick Cowan.
-We also thank the organizers of the 2016 Santa Cruz Kavli Summer Program and the 2017 Ringberg Atmospheres of Disks and Planets meeting for facilitating productive discussion and collaboration.
-J.L.B.
-acknowledges support from the David and Lucile Packard Foundation.
-J.M.D.
-acknowledges support from the European Research Council (ERC) under the programme Exo-Atmos (grant agreement no.
-679633).
-G.W.H.
-and M.H.W.
-also acknowledge long-term support from Tennessee State University and the State of Tennessee through its Centers of Excellence Program.
+Support for \textit{HST} program GO-15050 was provided by NASA through a grant
+from the Space Telescope Science Institute, which is operated by the Association
+of Universities for Research in Astronomy, Inc., under NASA contract NAS
+5-26555. Support for \textit{Spitzer} program 11099 was provided by NASA through
+an award issued by JPL/Caltech.  The data presented in this paper were obtained
+from the Mikulski Archive for Space Telescopes (MAST) and the NASA/IPAC Infrared
+Science Archive. The Infrared Science Archive is operated by the Jet Propulsion
+Laboratory, California Institute of Technology, under contract with the National
+Aeronautics and Space Administration.  This work also made use of the Python
+packages  SciPy and NumPy \citep{jones_scipy_2001, van2011numpy}. The authors
+are grateful for helpful conversations with Caroline Morley, Thomas Beatty, Ming
+Zhao, Kim Star Cartier, Hannah Diamond-Lowe, and Nick Cowan. We also thank the
+organizers of the 2016 Santa Cruz Kavli Summer Program and the 2017 Ringberg
+Atmospheres of Disks and Planets meeting for facilitating productive discussion
+and collaboration.  J.L.B. acknowledges support from the David and Lucile
+Packard Foundation.  J.M.D. acknowledges support from the European Research
+Council (ERC) under the programme Exo-Atmos (grant agreement no. 679633). G.W.H.
+and M.H.W. also acknowledge long-term support from Tennessee State University
+and the State of Tennessee through its Centers of Excellence Program. M.R.L.
+acknowledges NASA XRP grant NNX17AB56G for partial support of the theoretical
+interpretation of the data, as well as the ASU Research Computing staff for support with the Saguaro and Agave compute clusters.
 
@@
 
+\bibitem[{{Zhang} {et~al.}(2018){Zhang}, {Knutson}, {Kataria}, {Schwartz},
+  {Cowan}, {Showman}, {Burrows}, {Fortney}, {Todorov}, {Desert}, {Agol}, \&
+  {Deming}}]{zhang18}
+{Zhang}, M., {Knutson}, H.~A., {Kataria}, T., {et~al.} 2018, \aj, 155, 83
+
 \bibitem[{{Zhang} \& {Showman}(2017)}]{zhang17}

### 2018-05-08 ApJ_submit_v4/ms.tex
correct zhang reference

--- 2018-05-02 ApJ_submit_v3/ms.tex
@@
 Fast radiative timescales are predicted at high temperatures, and small hotspot offsets are also observed for other very hot Jupiters \citep{perez13, komacek16, komacek17}.
-The measured offsets are inconsistent with the trend reported in \cite{zhang17}, which predicts the hotspot offset increases with planet temperature for irradiation temperatures greater than 3410 K.
-The \cite{zhang17} model predicts an eastward hotspot offset of $4.5^\circ$ for WASP-103b, which is significantly larger than observed, hinting at diversity in the circulation patterns of the hottest planets.
+The measured offsets are inconsistent with the trend reported in \cite{zhang18}, which predicts the hotspot offset increases with planet temperature for irradiation temperatures greater than 3410 K.
+The \cite{zhang18} model predicts an eastward hotspot offset of $4.5^\circ$ for WASP-103b, which is significantly larger than observed, hinting at diversity in the circulation patterns of the hottest planets.
 The phase curve amplitudes are large (near 0.8 - 0.9), as expected for an atmosphere with inefficient heat redistribution.
@@
 are grateful for helpful conversations with Caroline Morley, Thomas Beatty, Ming
-Zhao, Kim Star Cartier, Hannah Diamond-Lowe, and Nick Cowan. We also thank the
+Zhao, Kimberly Cartier, Hannah Diamond-Lowe, and Nick Cowan. We also thank the
 organizers of the 2016 Santa Cruz Kavli Summer Program and the 2017 Ringberg

### 2018-05-08 arxiv_v2/ms.tex
Kim Cartier name correction
correct zhang reference

@@
 packages  SciPy and NumPy \citep{jones_scipy_2001, van2011numpy}. The authors
-are grateful for helpful conversations with Caroline Morley, Thomas Beatty, Ming
-Zhao, Kim Star Cartier, Hannah Diamond-Lowe, and Nick Cowan. We also thank the
+are grateful for helpful conversations with Caroline Morley, Ming
+Zhao, Kimberly Cartier, Hannah Diamond-Lowe, and Nick Cowan. We also thank the
 organizers of the 2016 Santa Cruz Kavli Summer Program and the 2017 Ringberg
